### 2018-07-09 two_dim_majoranas_report/progress.tex
Add report

\documentclass[10pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{glossaries}
\usepackage{float}

\newcommand{\kx}{k_x}
\newcommand{\ky}{k_y}
\newcommand{\meff}{m_\text{eff}}

\newcommand{\img}{./images}
\loadglsentries{glossary.tex}
\makeglossaries
\begin{document}
\title{Progress}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{System description}
	\begin{figure}[H]
		\includegraphics[width=\linewidth]{\img/system.png}
		\caption{System overview}
	\end{figure}

	\begin{align}
		H &= H_0(\tau_z \otimes \sigma_0) + 
		H_\text{Z} (\tau_0 \otimes \sigma_z) +
		(\tau_z \otimes H_\text{SO}) +
	 H_\text{SC}(\tau_y \otimes \sigma_0) \\
		H_0 &= \frac{\hbar^2}{2\meff}\left(\kx^2 + \ky^2\right) - \mu \\
		H_\text{Z} &= g \mu_B B  \left(\Theta(-x) - \Theta(L_m-x)\right)  \\
		H_\text{SO} &= \alpha \left( \ky \sigma_x - \kx \sigma_y \right)\\
		H_\text{SC} &= \Delta \exp \left(i \theta \Theta(x-L_m) \right)
	\end{align}

	Where: 
	\begin{equation}
	\Theta(x) = 
	\begin{cases}
	1,& x>0\\
	0,& \text{otherwise}
	\end{cases}
	\end{equation}

	\subsection{System parameters}
	\begin{table}
		\begin{tabular}{|c|c|c|c|}
			\hline 
			Variable & Description & Typical value & Default value \\ 
			\hline 
			$g_\text{factor}$ & Magnetic g-factor of material & ~10 & 10 \\ 
			\hline 
			$\mu$ & Chemical potential &  10 - 30 meV & 1 meV\\ 
			\hline 
			$\alpha$ & Spin orbit coupling strength &  30 meV nm & 30 meV nm \\ 
			\hline 
			$\Delta$ & Superconducting gap & 0.2 - 0.3 meV & 0.18 meV\\ 
			\hline 
			$B$ & In-plane magnetic field strength along stripe direction(y) & 0 - 1 T & 0.2 T \\ 
			\hline 
			$\phi$ & Relative phase between superconductors &  0 - 2$\pi$ & $\pi$\\ 
			\hline 
			$\text{L}_\text{l}$ & Width of left superconductor & $\infty$ & 500 nm \\
			\hline 
			$\text{L}_\text{m}$ & Width of right superconductor & $\infty$ & 500 nm \\
			\hline
			$\text{L}_\text{r}$ & Width of middle "normal" strip & 100 - 1000 nm & 250 nm \\
			\hline
			$\text{L}_\text{y}$ & Height of system & \textgreater1000 nm & 4000 nm\\
			\hline
		\end{tabular} 
	\caption{Description of system parameters, along with typical valuses, as well as a default value which is the used value when no other value has been specified.}
	\label{tbl:system_pars}
	\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Topological overview of the system}
%------------------%
	\subsection{important metrics}
		\begin{itemize}
			\item \Gls{Ethouless}
				\begin{align}\label{eq:thouless}
				E_\text{Th} = TN\delta
				, && \delta = \frac{\hbar^2 \pi^2}
				{2 m_e \left( 2 L_m \right)^2}
				\end{align}
			Where $T$ is the transparancy of the junction, and N the number of bands.
			\item Pfaffian sign
			\item Topological energy gap
			\item (critical) current, phase offset in current-phase relationship
		\end{itemize}
%------------------%
	\subsection{Varying magnetic field strength and superconducting phase}
		From the Pientka paper, we would expect an image plot of whether the system is topological or not, with axes superconducting phase and magnetic field, to form diamond structures repeating along the magnetic field axis, spaced apart with a distance equal to the Thouless energy.

		We indeed find this to be the case. We however find that beyond a certain magnetic field strength the bands cross, and the model becomes unphysical.
%------------------%		
	\subsection{Varying chemical potential and magnetic field strength}
		From the Pientka paper, we would expect 
			\begin{figure}[H]
				\includegraphics[width=0.3\textwidth]{muB0.png}
				\includegraphics[width=0.3\textwidth]{muB5.png}
				\includegraphics[width=0.3\textwidth]{muB1.png}
				\caption{Topological regime(blue is topological) vs chemical potential and magnetic field strength.}
			\end{figure}
%------------------%	
	\subsection{Varying spin-orbit}
		\begin{figure}[H]
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a30.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a33.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a36.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a40.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a43.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a46.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a50.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a53.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a56.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a60.png}
			\caption{Phase zeeman plot with increasing spin orbit}
		\end{figure}
%------------------%	
	\subsection{Varying superconducting gap}
		\begin{figure}[H]
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d02.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d045.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d067.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d089.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d11.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d133.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d155.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d178.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d200.png}
			\caption{Phase zeeman plot with increasing spin orbit}
		\end{figure}
%------------------%
	\subsection{Varying system dimensions}
		Widening the junction lowers the Thouless energy, which makes the topological regime accesible at lower magnetic fields, but at the same moment lowering the energy gap.
			\begin{table}[H]
				\centering
				\begin{tabular}{|c|c|}
					\hline 
					$L_\text{m} (nm)$ & $E_\text{Th} (meV)$ \\ 
					\hline 
					250 & 1.05 \\ 
					\hline 
					500 & 0.523 \\ 
					\hline 
					1000 & .262 \\ 
					\hline 
					5000 & .0523 \\ 
					\hline 
				\end{tabular} 
				\caption{Thouless energy for different system widths calculated using \ref{eq:thouless}, asssuming unit transparency.}
				\label{table:thouless}
			\end{table}

			\begin{figure}[H]
				\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB250.png}
				\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB500.png}
				\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB1000.png}
				\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB2000.png}
				\caption{Topological regime(blue is topological) vs superconducting phase and magnetic field strength, for different strip widths. The lines indicate integer multiples of the Thouless energy, see table \ref{table:thouless}}
			\end{figure}

			\begin{figure}[H]
				\includegraphics[width=0.5\textwidth]{\img/lmgap/lm100.png}
				\includegraphics[width=0.5\textwidth]{\img/lmgap/lm150.png}
				\includegraphics[width=0.5\textwidth]{\img/lmgap/lm200.png}
				\includegraphics[width=0.5\textwidth]{\img/lmgap/lm250.png}
%				\includegraphics[width=0.24\textwidth]{\img/lmgap/lm500.png}
				\caption{Topological regime(blue is topological) vs superconducting phase and magnetic field strength, for different strip widths. The lines indicate integer multiples of the Thouless energy, see table \ref{table:thouless}}
			\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\printglossaries
\end{document}

### 2018-07-10 distributed_sns.py
Add option for zeeman field in sc

@@ -2,7 +2,9 @@ import itertools
 import copy
 import collections
 
-def f_adaptive(xy, keys, params, syst_pars, transverse_soi=True):
+def f_adaptive(xy, keys, params, syst_pars,
+                     transverse_soi=True,
+                     zeeman_in_superconductor=False):
     import sns_system, topology
 
     params.update(dict(**sns_system.constants))
@@ -10,7 +12,7 @@ def f_adaptive(xy, keys, params, syst_pars, transverse_soi=True):
     for k, val in zip(keys, xy):
         params[k] = val
     params[keys[0]], params[keys[1]] = xy
-    syst = sns_system.make_sns_system(**syst_pars, transverse_soi = transverse_soi)
+    syst = sns_system.make_sns_system(**syst_pars, transverse_soi=transverse_soi, zeeman_in_superconductor=zeeman_in_superconductor)
     return topology.get_pfaffian(syst, params)
 
 

### 2018-07-10 sns_system.py

@@ -13,7 +13,7 @@ constants = dict(
     cos=cmath.cos,
     sin=cmath.sin)
 
-def get_template_strings(transverse_soi):
+def get_template_strings(transverse_soi, zeeman_in_superconductor=False):
     if transverse_soi:
         ham_str = """
         (hbar^2 / (2*m_eff) * (k_x^2 + k_y^2) - mu) * kron(sigma_z, sigma_0) + 
@@ -24,18 +24,26 @@ def get_template_strings(transverse_soi):
         alpha * kron(sigma_z, sigma_x) * k_y"""
 
     ham_sc_left = ham_str + " + Delta * kron(sigma_y, sigma_0)"
+
+
     ham_sc_right = ham_str + """ + cos(phase) * Delta * kron(sigma_y, sigma_0) + 
                                     + sin(phase) * Delta * kron(sigma_x, sigma_0)
     """
     ham_normal = ham_str + """ + 
                                 g_factor*mu_B*B * kron(sigma_0, sigma_y)
     """
+    if zeeman_in_superconductor:
+        ham_sc_left  += "+ g_factor*mu_B*B * kron(sigma_0, sigma_y)"
+        ham_sc_right += "+ g_factor*mu_B*B * kron(sigma_0, sigma_y)"
+        
     template_strings = dict(ham_normal=ham_normal,
                             ham_sc_right=ham_sc_right,
                             ham_sc_left=ham_sc_left)
     return template_strings
 
-def make_sns_system(a, Lm, Lr, Ll, Ly, transverse_soi = True, with_hopping = False):
+def make_sns_system(a, Lm, Lr, Ll, Ly,
+                    transverse_soi = True,
+                    zeeman_in_superconductor = False):
     """ 
     Builds and returns finalized 2dim sns system
     
@@ -63,7 +71,7 @@ def make_sns_system(a, Lm, Lr, Ll, Ly, transverse_soi = True, with_hopping = Fal
     """
 
     #     HAMILTONIAN DEFINITIONS
-    template_strings = get_template_strings(transverse_soi)
+    template_strings = get_template_strings(transverse_soi, zeeman_in_superconductor)
 
     # TURN HAMILTONIAN STRINGS INTO TEMPLATES
     template_normal = kwant.continuum.discretize(template_strings['ham_normal'], grid_spacing=a)
[…]

### 2018-07-11 two_dim_majoranas_report/progress.tex
Change folder git

@@
 
-		We indeed find this to be the case. We however find that beyond a certain magnetic field strength the bands cross, and the model becomes unphysical.
+		We indeed find this to be the case(figure \ref{fig:lmZPpfaf}). We however find that beyond a certain magnetic field strength the bands cross, and the model becomes unphysical.
+	%------------------%
+	\subsection{Varying system dimensions}
+	Widening the junction lowers the Thouless energy, which makes the topological regime accesible at lower magnetic fields, but at the same moment lowering the energy gap.
+	\begin{table}[H]
+		\centering
+		\begin{tabular}{|c|c|}
+			\hline 
+			$L_\text{m} (nm)$ & $E_\text{Th} (meV)$ \\ 
+			\hline 
+			250 & 1.05 \\ 
+			\hline 
+			500 & 0.523 \\ 
+			\hline 
+			1000 & .262 \\ 
+			\hline 
+			5000 & .0523 \\ 
+			\hline 
+		\end{tabular} 
+		\caption{Thouless energy for different system widths calculated using \ref{eq:thouless}, asssuming unit transparency.}
+		\label{table:thouless}
+	\end{table}
+
+	\begin{figure}[H]
+		\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB250.png}
+		\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB500.png}
+		\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB1000.png}
+		\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB2000.png}
+		\caption{Topological regime(blue is topological) vs superconducting phase and magnetic field strength, for different strip widths.
+The lines indicate integer multiples of the Thouless energy, see table \ref{table:thouless}}
+		\label{fig:lmZPpfaf}
+	\end{figure}
+
+	\begin{figure}[H]
+		\includegraphics[width=0.5\textwidth]{\img/lmgap/lm100.png}
+		\includegraphics[width=0.5\textwidth]{\img/lmgap/lm150.png}
+		\includegraphics[width=0.5\textwidth]{\img/lmgap/lm200.png}
+		\includegraphics[width=0.5\textwidth]{\img/lmgap/lm250.png}
+		%				\includegraphics[width=0.24\textwidth]{\img/lmgap/lm500.png}
+		\caption{Topological regime(blue is topological) vs superconducting phase and magnetic field strength, for different strip widths.
+The lines indicate integer multiples of the Thouless energy, see table \ref{table:thouless}}
+		\label{fig:lmZPcurr}
+	\end{figure}
 %------------------%		
@@
 				\includegraphics[width=0.3\textwidth]{muB1.png}
-				\caption{Topological regime(blue is topological) vs chemical potential and magnetic field strength.}
+				\caption{Topological regime(blue is topological) vs chemical potential and magnetic field strength, assuming zeeman field in the superconductor}
 			\end{figure}
@@
 		\end{figure}
-%------------------%
-	\subsection{Varying system dimensions}
-		Widening the junction lowers the Thouless energy, which makes the topological regime accesible at lower magnetic fields, but at the same moment lowering the energy gap.
-			\begin{table}[H]
-				\centering
-				\begin{tabular}{|c|c|}
-					\hline 
-					$L_\text{m} (nm)$ & $E_\text{Th} (meV)$ \\ 
-					\hline 
-					250 & 1.05 \\ 
-					\hline 
-					500 & 0.523 \\ 
-					\hline 
-					1000 & .262 \\ 
-					\hline 
-					5000 & .0523 \\ 
-					\hline 
-				\end{tabular} 
-				\caption{Thouless energy for different system widths calculated using \ref{eq:thouless}, asssuming unit transparency.}
-				\label{table:thouless}
-			\end{table}
 
-			\begin{figure}[H]
-				\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB250.png}
-				\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB500.png}
-				\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB1000.png}
-				\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB2000.png}
-				\caption{Topological regime(blue is topological) vs superconducting phase and magnetic field strength, for different strip widths.
-The lines indicate integer multiples of the Thouless energy, see table \ref{table:thouless}}
-			\end{figure}
-
-			\begin{figure}[H]
-				\includegraphics[width=0.5\textwidth]{\img/lmgap/lm100.png}
-				\includegraphics[width=0.5\textwidth]{\img/lmgap/lm150.png}
-				\includegraphics[width=0.5\textwidth]{\img/lmgap/lm200.png}
-				\includegraphics[width=0.5\textwidth]{\img/lmgap/lm250.png}
-%				\includegraphics[width=0.24\textwidth]{\img/lmgap/lm500.png}
-				\caption{Topological regime(blue is topological) vs superconducting phase and magnetic field strength, for different strip widths.
-The lines indicate integer multiples of the Thouless energy, see table \ref{table:thouless}}
-			\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-07-12 two_dim_majoranas_report/progress.tex
Updated version of report

@@
 	\end{align}
-
 	Where: 
@@
 	\end{equation}
-
+	\subsection{Assumptions and limitations of model}
+		[TODO: LIST ASSUMPTIONS AND LIMITATIONS: SPIN ORBIT DRESSELHAUS, SC MODEL, ETC.]
 	\subsection{System parameters}
@@
 	\end{table}
+	Describe parameters provided by experimentalists(electron density 3e15-3e16, effective mass 0.04me)
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 		From the Pientka paper, we would expect an image plot of whether the system is topological or not, with axes superconducting phase and magnetic field, to form diamond structures repeating along the magnetic field axis, spaced apart with a distance equal to the Thouless energy.
+We indeed find this to be the case(figure \ref{fig:lmZPpfaf}).
+We however find that beyond a certain magnetic field strength the bands cross, and the model becomes unphysical(and the diamonds are lost).
 
-		We indeed find this to be the case(figure \ref{fig:lmZPpfaf}). We however find that beyond a certain magnetic field strength the bands cross, and the model becomes unphysical.
+		If we apply a magnetic field in the superconducting leads as well[SHOW THAT TOPOLOGICAL MAP CONFORMS TO FIG4 OF PIENTKA]
+
 	%------------------%
 	\subsection{Varying system dimensions}
-	Widening the junction lowers the Thouless energy, which makes the topological regime accesible at lower magnetic fields, but at the same moment lowering the energy gap.
+	 Widening the junction lowers the Thouless energy, which makes the topological regime accesible at lower magnetic fields.
+Conversely, lowering the Thouless energy has a negative effect on the energy gap: The system is a long to intermediate junction, meaning $E_\text{Th} \gtrapprox \Delta$ or $E_\text{Th} \gg \Delta$[CITE VUIK].
+This implies that the induced gap $\Delta_\text{ind} \propto E_\text{Th}$.
 	\begin{table}[H]
@@
 		%				\includegraphics[width=0.24\textwidth]{\img/lmgap/lm500.png}
-		\caption{Topological regime(blue is topological) vs superconducting phase and magnetic field strength, for different strip widths.
-The lines indicate integer multiples of the Thouless energy, see table \ref{table:thouless}}
+		\caption{Energy gap vs superconducting phase and magnetic field strength, for different strip widths.}
 		\label{fig:lmZPcurr}
@@
 		From the Pientka paper, we would expect
-			\begin{figure}[H]
-				\includegraphics[width=0.3\textwidth]{muB0.png}
-				\includegraphics[width=0.3\textwidth]{muB5.png}
-				\includegraphics[width=0.3\textwidth]{muB1.png}
-				\caption{Topological regime(blue is topological) vs chemical potential and magnetic field strength, assuming zeeman field in the superconductor}
+
+			\begin{figure}
+			\begin{tabular}{cc}
+				\includegraphics[width=0.35\textwidth]{\img/pfafmuZ_zinsc/muB0.png}&
+				\includegraphics[width=0.45\textwidth]{\img/gapmuZ_zinsc/00_gap_muZ.png}\\
+				&
+				\includegraphics[width=0.45\textwidth]{\img/gapmuZ_zinsc/25_gap_muZ.png}\\
+				\includegraphics[width=0.35\textwidth]{\img/pfafmuZ_zinsc/muB5.png}&
+				\includegraphics[width=0.45\textwidth]{\img/gapmuZ_zinsc/50_gap_muZ.png}\\
+				&
+				\includegraphics[width=0.45\textwidth]{\img/gapmuZ_zinsc/75_gap_muZ.png}\\
+				\includegraphics[width=0.35\textwidth]{\img/pfafmuZ_zinsc/muB1.png}&
+				\includegraphics[width=0.45\textwidth]{\img/gapmuZ_zinsc/1_gap_muZ.png}\\
+			\end{tabular}
+		\caption{Topological regime(blue is topological) and energy gap vs chemical potential and magnetic field strength, assuming zeeman field persists in the superconductor}
 			\end{figure}
+
+%			\begin{figure}[H]
+%				\caption{Topological regime(blue is topological) vs chemical potential and magnetic field strength, assuming zeeman field persists in the superconductor}
+%			\end{figure}
+%			\begin{figure}[H]
+%				
+%				\caption{Energy gap vs chemical potential and magnetic field strength, assuming zeeman field persists in the superconductor}
+%			\end{figure}
+\begin{figure}
+	\begin{tabular}{cc}
+				\includegraphics[width=0.4\textwidth]{\img/pfafmuZ_noZinsc/00pfafmuZnoZinSC.png}&
+			\includegraphics[width=0.4\textwidth]{\img/gapmuZ_noZinsc/0gapmuZ.png}\\
+				\includegraphics[width=0.4\textwidth]{\img/pfafmuZ_noZinsc/25pfafmuZnoZinSC.png}&
+			\includegraphics[width=0.4\textwidth]{\img/gapmuZ_noZinsc/25gapmuZ.png}\\
+				\includegraphics[width=0.4\textwidth]{\img/pfafmuZ_noZinsc/50pfafmuZnoZinSC.png}&
+			\includegraphics[width=0.4\textwidth]{\img/gapmuZ_noZinsc/50gapmuZ.png}\\
+				\includegraphics[width=0.4\textwidth]{\img/pfafmuZ_noZinsc/75pfafmuZnoZinSC.png}&
+			\includegraphics[width=0.4\textwidth]{\img/gapmuZ_noZinsc/75gapmuZ.png}\\
+				\includegraphics[width=0.4\textwidth]{\img/pfafmuZ_noZinsc/1pfafmuZnoZinSC.png}&
+			\includegraphics[width=0.4\textwidth]{\img/gapmuZ_noZinsc/1gapmuZ.png}\\
+	\end{tabular}\label{fig:muZnosc}
+		\caption{Topological invariant and energy gap vs chemical potential and magnetic field strength, assuming zeeman field persists in the superconductor}
+\end{figure}
+
 %------------------%

### 2018-07-13 sns_system.py
Add wrapped current calculation and system creation

@@ -71,7 +71,7 @@ def make_sns_system(a, Lm, Lr, Ll, Ly,
     """
 
     #     HAMILTONIAN DEFINITIONS
-    template_strings = get_template_strings(transverse_soi, zeeman_in_superconductor)
+    template_strings = get_template_strings(transverse_soi, )
 
     # TURN HAMILTONIAN STRINGS INTO TEMPLATES
     template_normal = kwant.continuum.discretize(template_strings['ham_normal'], grid_spacing=a)
@@ -185,6 +185,45 @@ def make_junction(a, Lm, Ly, transverse_soi = True, **pars):
     
     return syst.finalized()
 
+def make_wrapped_system(a, Lm, Lr, Ll, Ly, Lw, transverse_soi=True, zeeman_in_superconductor=False):
+    template_strings = get_template_strings(transverse_soi, zeeman_in_superconductor)
+
+    # TURN HAMILTONIAN STRINGS INTO TEMPLATES
+    template_normal = kwant.continuum.discretize(template_strings['ham_normal'], grid_spacing=a)
+    template_sc_left = kwant.continuum.discretize(template_strings['ham_sc_left'], grid_spacing=a)
+    template_sc_right = kwant.continuum.discretize(template_strings['ham_sc_right'], grid_spacing=a)
+
+    # SHAPE FUNCTIONS
+    def shape_normal(site):
+        (x, y) = site.pos
+        return 0 <= x < Lm
+
+    def shape_left_sc(site):
+        (x, y) = site.pos
+        return -Ll <= x < 0
+
+    def shape_right_sc(site):
+        (x, y) = site.pos
+        return Lm <= x < Lm + Lr
+    
+    def shape_lead(x1, x2):
+        def shape(site):
+            (x, y) = site.pos
+            return  x1 <= x < x2
+        return shape
+
+    # BUILD FINITE SYSTEM
+    sym = kwant.TranslationalSymmetry((0, a))
+    syst = kwant.Builder(symmetry=sym)
+
+    syst.fill(template_normal, shape_normal, (0,0))
+    if Ll>=a:
+        syst.fill(template_sc_left, shape_left_sc, (-Ll,0))
+    if Lr>=a:
+        syst.fill(template_sc_right, shape_right_sc, (Lm,0))
+
+    syst = kwant.wraparound.wraparound(syst)
+    return syst.finalized()
 
[…]

### 2018-07-13 supercurrent.py

@@ -5,6 +5,7 @@ import spectrum
 import numbers
 import warnings
 from functools import partial
+import adaptive
 
 sigz = kwant.continuum.discretizer.ta.array([[1,0,0,0],
                                              [0,1,0,0],
@@ -19,7 +20,62 @@ def fermi_dirac(e, params):
     minbetae = np.minimum(100, -beta*e)
     return np.exp(minbetae)/(1+np.exp(minbetae))
 
-            
+def wrapped_current_k(k, syst_pars, params, cut_tag=0, direction=0):
+    syst_wrapped = sns_system.make_wrapped_system(**syst_pars)
+    
+    (cut_indices, cut_sites) = get_cut_sites_and_indices(syst_wrapped, cut_tag, direction)
+    current_operator = kwant.operator.Current(syst_wrapped,
+                                              onsite=sigz,
+                                              where=cut_sites)
+    
+    I = 0
+   
+    p = dict(k_x=k, **params)
+
+    ham = syst_wrapped.hamiltonian_submatrix(params=p)
+    (en, evs) = np.linalg.eigh(ham)
+
+    for (e, ev) in zip(en, evs.T):
+        I += fermi_dirac(e.real, p) * current_operator(ev, params=p)
+
+    return sum(I)*params['e']/params['hbar']
+
+def wrapped_current(syst_pars, params, tol=0.01, max_iterations=1e3):
+    syst_wrapped = sns_system.make_wrapped_system(**syst_pars)
+    cut_tag=0
+    direction=0
+
+    (cut_indices, cut_sites) = get_cut_sites_and_indices(syst_wrapped, cut_tag, direction)
+    current_operator = kwant.operator.Current(syst_wrapped,
+                                              onsite=sigz,
+                                              where=cut_sites)
+
+
+
+    def f(k):
+        I = 0
+        p = dict(k_x=k, **params)
+        ham = syst_wrapped.hamiltonian_submatrix(params=p)
+        (en, evs) = np.linalg.eigh(ham)
+
+        for (e, ev) in zip(en, evs.T):
+            I += fermi_dirac(e.real, p) * current_operator(ev, params=p)
+        return sum(I)*params['e']/params['hbar']
+
+    learner = adaptive.IntegratorLearner(f, [0, np.pi], tol)
+    iterations = 0
+    while (not learner.done()) and (iterations<max_iterations):
+        k = learner.ask(1)[0][0]
+        I = f(k)
+        learner.tell(k, I)
[…]

### 2018-07-13 two_dim_majoranas_report/progress.tex
Updated version of report, cleaner notebook

@@
 			\hline
-			$\text{L}_\text{y}$ & Height of system & \textgreater1000 nm & 4000 nm\\
+			$\text{L}_\text{y}$ & Length of system & \textgreater1000 nm & 4000 nm\\
+			\hline
+			$T$ & Temperature of system & 0.25 - 1.2K & 0 K\\
 			\hline
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Topological overview of the system}
+\section{Parametric overview of the system}
 %------------------%
-	\subsection{important metrics}
+	\subsection{Important metrics}
+	We study the influence of the different parameters on the physics of the system by considering a handful of metrics.
+We list them below, along with how they are computed and what their physical significance is.
 		\begin{itemize}
@@
 			Where $T$ is the transparancy of the junction, and N the number of bands.
-			\item Pfaffian sign
+			\item Topological invariant: Pfaffian sign
+				\subitem The system is extended to infinity and the Pfaffian allows us compute the parity of number of states with positive energy of the system, disregarding the holes.
+If the resulting topological invariant is -1, we can conclude that if the system were to be made finite, it could potentially support majorana bound states.
+
 			\item Topological energy gap
+				\subitem The system is again extended to infinity, and the energy difference between the majorana bound states(energy 0) and the next lowest lying band is calculated, using the bisection method.
+
 			\item (critical) current, phase offset in current-phase relationship
+				\subitem The system is extended to infinity, and the current density is calculated at a cut in the non-superconducting section.
+
+			\item Junction transparency
+				\subitem The transparency is using kwant. It gives an indication of 
 		\end{itemize}
@@
 		\end{figure}
+%------------------%	
+	\subsection{Varying temperature}
+		\begin{figure}
+			\begin{tabular}{rcc}
+				a, T=0.025K&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm200_T0025.png}&
+				\includegraphics[width=0.4\textwidth]{\img/current/curr_lm200_T0025.png}\\
+				\hline
+				b, T=0.2K&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm200_T02.png}&
+				\includegraphics[width=0.4\textwidth]{\img/current/curr_lm200_T02.png}\\
+				\hline
+				c, T=0.6K&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm200_T06.png}&
+				\includegraphics[width=0.4\textwidth]{\img/current/curr_lm200_T06.png}\\
+				\hline
+			\end{tabular}
+			\caption{Critical current(maximum minus minimum current) and current versus phase and magnetic field strength, assuming zeeman field does not persists in the superconductor.
+Width of normal strip is 200nm.
+Temperatures of a, b and c respectively: 0.025 K, 0.2K, 0.6K}
+		\end{figure}
 
+	\subsection{Varying temperature}
+		\begin{figure}
+			\begin{tabular}{rcc}
+				a, T=0.025K&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm250_T0025.png}&
+				\includegraphics[width=0.4\textwidth]{\img/current/curr_lm250_T0025.png}\\
+				\hline
+				b, T=0.2K&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm250_T02.png}&
+				\includegraphics[width=0.4\textwidth]{\img/current/curr_lm250_T02.png}\\
+				\hline
+				c, T=0.6K&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm250_T06.png}&
+				\includegraphics[width=0.4\textwidth]{\img/current/curr_lm250_T06.png}\\
+				\hline
+			\end{tabular}
+			\caption{Critical current(maximum minus minimum current) and current versus phase and magnetic field strength, assuming zeeman field does not persists in the superconductor.
+Width of normal strip is 250nm.
+Temperatures of a, b and c respectively: 0.025 K, 0.2K, 0.6K}
+		\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-07-14 supercurrent.py
Add option for zeeman in sc for current

@@ -40,8 +40,8 @@ def wrapped_current_k(k, syst_pars, params, cut_tag=0, direction=0):
 
     return sum(I)*params['e']/params['hbar']
 
-def wrapped_current(syst_pars, params, tol=0.01, max_iterations=1e3):
-    syst_wrapped = sns_system.make_wrapped_system(**syst_pars)
+def wrapped_current(syst_pars, params, tol=0.01, max_iterations=1e3, , transverse_soi=True, zeeman_in_superconductor=False):
+    syst_wrapped = sns_system.make_wrapped_system(**syst_pars, transverse_soi, zeeman_in_superconductor)
     cut_tag=0
     direction=0
 

### 2018-07-14 supercurrent.py
Add option for zeeman in sc for current

@@ -40,7 +40,7 @@ def wrapped_current_k(k, syst_pars, params, cut_tag=0, direction=0):
 
     return sum(I)*params['e']/params['hbar']
 
-def wrapped_current(syst_pars, params, tol=0.01, max_iterations=1e3, , transverse_soi=True, zeeman_in_superconductor=False):
+def wrapped_current(syst_pars, params, tol=0.01, max_iterations=1e3, transverse_soi=True, zeeman_in_superconductor=False):
     syst_wrapped = sns_system.make_wrapped_system(**syst_pars, transverse_soi, zeeman_in_superconductor)
     cut_tag=0
     direction=0

### 2018-07-14 supercurrent.py
Add option for zeeman in sc for current

@@ -41,7 +41,9 @@ def wrapped_current_k(k, syst_pars, params, cut_tag=0, direction=0):
     return sum(I)*params['e']/params['hbar']
 
 def wrapped_current(syst_pars, params, tol=0.01, max_iterations=1e3, transverse_soi=True, zeeman_in_superconductor=False):
-    syst_wrapped = sns_system.make_wrapped_system(**syst_pars, transverse_soi, zeeman_in_superconductor)
+    syst_wrapped = sns_system.make_wrapped_system(**syst_pars,
+     transverse_soi=transverse_soi,
+     zeeman_in_superconductor=zeeman_in_superconductor)
     cut_tag=0
     direction=0
 

### 2018-07-16 two_dim_majoranas_report/progress.tex
Updated version of report

@@
 	\subsection{Assumptions and limitations of model}
-		[TODO: LIST ASSUMPTIONS AND LIMITATIONS: SPIN ORBIT DRESSELHAUS, SC MODEL, ETC.]
+%		[TODO: LIST ASSUMPTIONS AND LIMITATIONS: SPIN ORBIT DRESSELHAUS, SC MODEL, ETC.]
 	\subsection{System parameters}
@@
 %------------------%
+\newpage
 	\subsection{Varying magnetic field strength and superconducting phase}
-		From the Pientka paper, we would expect an image plot of whether the system is topological or not, with axes superconducting phase and magnetic field, to form diamond structures repeating along the magnetic field axis, spaced apart with a distance equal to the Thouless energy.
+		In this section, we vary the Zeeman field strength and superconducting phase, calculating the topological invariant. 
+		From the Pientka paper, we would expect diamond like structures to appear along the magnetic field axis, spaced apart with a distance equal to the Thouless energy.
 We indeed find this to be the case(figure \ref{fig:lmZPpfaf}).
-We however find that beyond a certain magnetic field strength the bands cross, and the model becomes unphysical(and the diamonds are lost).
+By varying the width of the middle strip we adjust the Thouless energy, and we see clearly find the diamonds shaped apart by the Thouless energy.
 
-		If we apply a magnetic field in the superconducting leads as well[SHOW THAT TOPOLOGICAL MAP CONFORMS TO FIG4 OF PIENTKA]
+		Beyond a certain Zeeman field, we see(although not shown in the figure) that the diamond pattern ceases and turns into stripes independent of phase.
+At this point, the magnetic field is so strong that bands cross, and our model becomes unphysical.
+Applying a magnetic field in the superconducting leads as well, lowers the field where this happens.
+
+		We will use this phase-Zeeman plot throughout the report as both parameters are easily tunable whem compared to the rest, and the diamond structure gives us an analysable feature.
+
+	\begin{figure}[H]
+		\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB250.png}
+		\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB500.png}
+		\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB1000.png}
+		\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB2000.png}
+		\caption{Topological regime(blue is topological) vs superconducting phase and magnetic field strength, for different strip widths.
+The lines indicate integer multiples of the Thouless energy, see table \ref{table:thouless}}
+		\label{fig:lmZPpfaf}
+	\end{figure}
 
@@
 	\subsection{Varying system dimensions}
-	 Widening the junction lowers the Thouless energy, which makes the topological regime accesible at lower magnetic fields.
-Conversely, lowering the Thouless energy has a negative effect on the energy gap: The system is a long to intermediate junction, meaning $E_\text{Th} \gtrapprox \Delta$ or $E_\text{Th} \gg \Delta$[CITE VUIK].
-This implies that the induced gap $\Delta_\text{ind} \propto E_\text{Th}$.
+	 As mentioned before, widening the junction lowers the Thouless energy, which makes the topological regime accesible at lower magnetic fields.
+We are however also interested in how big the resulting topological gap is.
+
+	 In figure \ref{fig:lmZPgap}, we plot the energy gap around zero energy.
+We see that increasing the middle strip width has the effect of lowering the gap in the topological region.
+The system we are considering is considered an intermediate to long junction: $E_\text{Th} \gtrapprox \Delta$ or $E_\text{Th} \gg \Delta$.
+This implies that the relation between the induced gap and the Thouless energy and superconducting gap is $\Delta_\text{ind} \propto E_\text{Th}$[VUIK].
+It would be interesting to investigate wether the gap indeed varies proportionally to the Thouless energy.
+
+	 We see that width of the gapless strips along the topological borders are quite wide, requiring very high magnetic field to reach a gapped topological state of the system.
 	\begin{table}[H]
@@
 	\begin{figure}[H]
-		\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB250.png}
-		\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB500.png}
-		\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB1000.png}
-		\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB2000.png}
-		\caption{Topological regime(blue is topological) vs superconducting phase and magnetic field strength, for different strip widths.
-The lines indicate integer multiples of the Thouless energy, see table \ref{table:thouless}}
-		\label{fig:lmZPpfaf}
-	\end{figure}
-
-	\begin{figure}[H]
 		\includegraphics[width=0.5\textwidth]{\img/lmgap/lm100.png}
@@
 		\caption{Energy gap vs superconducting phase and magnetic field strength, for different strip widths.}
-		\label{fig:lmZPcurr}
+		\label{fig:lmZPgap}
 	\end{figure}
 %------------------%	
+\newpage	
 	\subsection{Varying chemical potential and magnetic field strength}
-		From the Pientka paper, we would expect
+		We vary the chemical potential and zeeman field plotting both the topology as well as the energy gap of the system. We do this for two situations; with and without zeeman field in the leads.
 
-			\begin{figure}
+		In figure \ref{fig:muZ_zinsc}, we consider the system with zeeman field in the superconducting part.
+We see a chainlike structures as described in the Pientka paper.
+The first chain opens up as a function of phase, and forms a large strip where the system is topological for a wide range of chemical potential.
+We see from the energy gap plots that only the first 'chain' has is gapless.
+
+		In figure \ref{fig:muZnosc}, we plot the system without magnetic field in the leads.
+With respect to the system with zeeman in the leads, it almost seems like the plot has undergone rescaling.
+The other diamond chains are not visible in this plot, and only appear when we greatly adjust the axes(not shown).
+We also see that although we can clearly see the gap closing bands(topological borders) in the gap plots, the underlying gap size does not seem greatly affected by being in topological region or not.
+
+			\begin{figure}[H]
 			\begin{tabular}{cc}
@@
 			\end{tabular}
-		\caption{Topological regime(blue is topological) and energy gap vs chemical potential and magnetic field strength, assuming zeeman field persists in the superconductor}
+		\caption{Topological regime(blue is topological) and energy gap vs chemical potential and magnetic field strength, assuming zeeman field persists in the superconductor}\label{fig:muZ_zinsc}
 			\end{figure}
 
-%			\begin{figure}[H]
-%				\caption{Topological regime(blue is topological) vs chemical potential and magnetic field strength, assuming zeeman field persists in the superconductor}
-%			\end{figure}
-%			\begin{figure}[H]
-%				
-%				\caption{Energy gap vs chemical potential and magnetic field strength, assuming zeeman field persists in the superconductor}
-%			\end{figure}
-\begin{figure}
+\begin{figure}[H]
 	\begin{tabular}{cc}
@@
 %------------------%
+\newpage
 	\subsection{Varying spin-orbit}
+	In figure \ref{fig:pfaf_pB_soi} and \ref{fig:gap_pB_soi} we plot topology and energy gap respectively as a function of phase and magnetic field, for different values of the spin orbit coupling.
+From the topology, wee see that variation of SOI influences both the shape of the diamonds as well as offsets their position.
+From the Pientka paper, we know that both are also symptoms of non unit junction transparency.
+It would be interesting to indeed investigate this.
+
+	The influence of varying spin orbit coupling seems to be limited.
+Although at lower spin orbit couplings, we see strands of gap-closings, which would be interesting to investigate, the energy gap in the topological region does not vary much.
 		\begin{figure}[H]
@@
 			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a60.png}
-			\caption{Phase zeeman plot with increasing spin orbit}
+			\caption{Phase zeeman topology plot with increasing spin orbit. $L_\text{m}=500$nm}
+			\label{fig:pfaf_pB_soi}
+		\end{figure}
+
+		\begin{figure}[H]
+			\begin{tabular}{ccc}
+				\includegraphics[width=0.33\textwidth]{\img/spinorbitGap/gap_pB_alpha10.png}&
+				\includegraphics[width=0.33\textwidth]{\img/spinorbitGap/gap_pB_alpha20.png}&
+				\includegraphics[width=0.33\textwidth]{\img/spinorbitGap/gap_pB_alpha30.png}\\
+				\includegraphics[width=0.33\textwidth]{\img/spinorbitGap/gap_pB_alpha40.png}&
+				\includegraphics[width=0.33\textwidth]{\img/spinorbitGap/gap_pB_alpha50.png}&
+				\includegraphics[width=0.33\textwidth]{\img/spinorbitGap/gap_pB_alpha60.png}\\
+			\end{tabular}
+			\caption{Phase zeeman energy gap plot with increasing spin orbit. $L_\text{m}=500$nm}
+			\label{fig:gap_pB_soi}
 		\end{figure}
 %------------------%
+\newpage	
 	\subsection{Varying superconducting gap}
+	Increasing the superconducting gap has the effect of reducing the energy gap somewhat. We also again see the appearance of gapless bands through the regions.
 		\begin{figure}[H]
@@
 %------------------%	
+\newpage
 	\subsection{Varying temperature}
-		\begin{figure}
+	We 
+		\begin{figure}[H]
 			\begin{tabular}{rcc}
@@
 
-	\subsection{Varying temperature}
-		\begin{figure}
+		\begin{figure}[H]
 			\begin{tabular}{rcc}

### 2018-07-16 two_dim_majoranas_report/progress.tex
switch l_m <-> l_r
put sentences on seperate lines

@@
 			\hline 
-			$\text{L}_\text{m}$ & Width of right superconductor & $\infty$ & 500 nm \\
+			$\text{L}_\text{r}$ & Width of right superconductor & $\infty$ & 500 nm \\
 			\hline
-			$\text{L}_\text{r}$ & Width of middle "normal" strip & 100 - 1000 nm & 250 nm \\
+			$\text{L}_\text{m}$ & Width of middle "normal" strip & 100 - 1000 nm & 250 nm \\
 			\hline
@@
 				\end{align}
-			Where $T$ is the transparancy of the junction, and N the number of bands.
-			\item Topological invariant: Pfaffian sign
+			Where $T$ is the transparancy of the junction and $N$ the number of bands.
+			\item Topological invariant: the sign of the Pfaffian
 				\subitem The system is extended to infinity and the Pfaffian allows us compute the parity of number of states with positive energy of the system, disregarding the holes.
@@
 		From the Pientka paper, we would expect diamond like structures to appear along the magnetic field axis, spaced apart with a distance equal to the Thouless energy.
-We indeed find this to be the case(figure \ref{fig:lmZPpfaf}).
+		We indeed find this to be the case (figure \ref{fig:lmZPpfaf}).
 		By varying the width of the middle strip we adjust the Thouless energy, and we see clearly find the diamonds shaped apart by the Thouless energy.
 
-		Beyond a certain Zeeman field, we see(although not shown in the figure) that the diamond pattern ceases and turns into stripes independent of phase.
+		Beyond a certain Zeeman field, we see (although not shown in the figure) that the diamond pattern ceases and turns into stripes independent of phase.
 		At this point, the magnetic field is so strong that bands cross, and our model becomes unphysical.
@@
 	\subsection{Varying chemical potential and magnetic field strength}
-		We vary the chemical potential and zeeman field plotting both the topology as well as the energy gap of the system. We do this for two situations; with and without zeeman field in the leads.
+		We vary the chemical potential and zeeman field plotting both the topology as well as the energy gap of the system.
+		We do this for two situations; with and without zeeman field in the leads.
 
@@
 		The other diamond chains are not visible in this plot, and only appear when we greatly adjust the axes(not shown).
-We also see that although we can clearly see the gap closing bands(topological borders) in the gap plots, the underlying gap size does not seem greatly affected by being in topological region or not.
+		We also see that although we can clearly see the gap closing bands (topological borders) in the gap plots, the underlying gap size does not seem greatly affected by being in topological region or not.
 

### 2018-07-16 two_dim_majoranas_report/progress.tex
several changes to the text

@@
 \usepackage{float}
+\usepackage{siunitx}
 
@@
 			\hline 
-			$B$ & In-plane magnetic field strength along stripe direction(y) & 0 - 1 T & 0.2 T \\ 
+			$B$ & In-plane magnetic field strength along stripe direction (y) & 0 - 1 T & 0.2 T \\ 
 			\hline 
@@
 			\hline
-			$T$ & Temperature of system & 0.25 - 1.2K & 0 K\\
+			$T$ & Temperature of system & 0.25 - 1.2 K & 0 K\\
 			\hline
@@
 	\end{table}
-	Describe parameters provided by experimentalists(electron density 3e15-3e16, effective mass 0.04me)
+	Describe parameters provided by experimentalists (electron density $3e15$-$3e16$, effective mass $\SI{0.04}{\electronmass}$)
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 			\item Topological energy gap
-				\subitem The system is again extended to infinity, and the energy difference between the majorana bound states(energy 0) and the next lowest lying band is calculated, using the bisection method.
+				\subitem The system is again extended to infinity, and the energy difference between the majorana bound states (energy 0) and the next lowest lying band is calculated, using the bisection method.
 
@@
 		\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB2000.png}
-		\caption{Topological regime(blue is topological) vs superconducting phase and magnetic field strength, for different strip widths.
+		\caption{Topological regime (blue is topological) vs superconducting phase and magnetic field strength, for different strip widths.
 The lines indicate integer multiples of the Thouless energy, see table \ref{table:thouless}}
@@
 			\hline 
-			$L_\text{m} (nm)$ & $E_\text{Th} (meV)$ \\ 
+			$L_\text{m} \; [\si{\nm}]$ & $E_\text{Th} \; [\si{\meV}]$ \\ 
 			\hline 
@@
 	\subsection{Varying chemical potential and magnetic field strength}
-		We vary the chemical potential and zeeman field plotting both the topology as well as the energy gap of the system.
-		We do this for two situations; with and without zeeman field in the leads.
+		We vary the chemical potential and Zeeman field plotting both the topology as well as the energy gap of the system.
+		We do this for two situations; with and without Zeeman field in the leads.
 
-		In figure \ref{fig:muZ_zinsc}, we consider the system with zeeman field in the superconducting part.
+		In figure \ref{fig:muZ_zinsc}, we consider the system with Zeeman field in the superconducting part.
 		We see a chainlike structures as described in the Pientka paper.
@@
 		In figure \ref{fig:muZnosc}, we plot the system without magnetic field in the leads.
-		With respect to the system with zeeman in the leads, it almost seems like the plot has undergone rescaling.
-		The other diamond chains are not visible in this plot, and only appear when we greatly adjust the axes(not shown).
+		With respect to the system with Zeeman in the leads, it almost seems like the plot has undergone rescaling.
+		The other diamond chains are not visible in this plot, and only appear when we greatly adjust the axes (not shown).
 		We also see that although we can clearly see the gap closing bands (topological borders) in the gap plots, the underlying gap size does not seem greatly affected by being in topological region or not.
@@
 			\end{tabular}
-		\caption{Topological regime(blue is topological) and energy gap vs chemical potential and magnetic field strength, assuming zeeman field persists in the superconductor}\label{fig:muZ_zinsc}
+		\caption{Topological regime (blue is topological) and energy gap vs chemical potential and magnetic field strength, assuming Zeeman field persists in the superconductor}\label{fig:muZ_zinsc}
 			\end{figure}
@@
 	\end{tabular}\label{fig:muZnosc}
-		\caption{Topological invariant and energy gap vs chemical potential and magnetic field strength, assuming zeeman field persists in the superconductor}
+		\caption{Topological invariant and energy gap vs chemical potential and magnetic field strength, assuming Zeeman field persists in the superconductor}
 \end{figure}
@@
 			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a60.png}
-			\caption{Phase zeeman topology plot with increasing spin orbit. $L_\text{m}=500$nm}
+			\caption{Phase Zeeman topology plot with increasing spin orbit. $L_\text{m}=\SI{500}{\nm}$}
 			\label{fig:pfaf_pB_soi}
@@
 			\end{tabular}
-			\caption{Phase zeeman energy gap plot with increasing spin orbit. $L_\text{m}=500$nm}
+			\caption{Phase Zeeman energy gap plot with increasing spin orbit. $L_\text{m}=\SI{500}{\nm}$}
 			\label{fig:gap_pB_soi}
@@
 	\subsection{Varying superconducting gap}
-	Increasing the superconducting gap has the effect of reducing the energy gap somewhat. We also again see the appearance of gapless bands through the regions.
+	Increasing the superconducting gap has the effect of reducing the energy gap somewhat.
+	We also again see the appearance of gapless bands through the regions.
 		\begin{figure}[H]
@@
 			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d200.png}
-			\caption{Phase zeeman plot with increasing spin orbit}
+			\caption{Phase Zeeman plot with increasing spin orbit}
 		\end{figure}
@@
 			\begin{tabular}{rcc}
-				a, T=0.025K&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm200_T0025.png}&
+				a, $T=\SI{0.025}{\K}$&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm200_T0025.png}&
 				\includegraphics[width=0.4\textwidth]{\img/current/curr_lm200_T0025.png}\\
 				\hline
-				b, T=0.2K&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm200_T02.png}&
+				b, $T=\SI{0.2}{\K}$&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm200_T02.png}&
 				\includegraphics[width=0.4\textwidth]{\img/current/curr_lm200_T02.png}\\
 				\hline
-				c, T=0.6K&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm200_T06.png}&
+				c, $T=\SI{0.6}{\K}$&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm200_T06.png}&
 				\includegraphics[width=0.4\textwidth]{\img/current/curr_lm200_T06.png}\\
@@
 			\end{tabular}
-			\caption{Critical current(maximum minus minimum current) and current versus phase and magnetic field strength, assuming zeeman field does not persists in the superconductor.
-Width of normal strip is 200nm.
-Temperatures of a, b and c respectively: 0.025 K, 0.2K, 0.6K}
+			\caption{Critical current (maximum minus minimum current) and current versus phase and magnetic field strength, assuming Zeeman field does not persists in the superconductor.
+Width of normal strip is 200 nm.
+Temperatures of a, b and c respectively: $\SI{0.025}{\K}$, $\SI{0.2}{\K}$, $\SI{0.6}{\K}$}
 		\end{figure}
@@
 			\begin{tabular}{rcc}
-				a, T=0.025K&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm250_T0025.png}&
+				a, $T=\SI{0.025}{\K}$&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm250_T0025.png}&
 				\includegraphics[width=0.4\textwidth]{\img/current/curr_lm250_T0025.png}\\
 				\hline
-				b, T=0.2K&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm250_T02.png}&
+				b, $T=\SI{0.2}{\K}$&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm250_T02.png}&
 				\includegraphics[width=0.4\textwidth]{\img/current/curr_lm250_T02.png}\\
 				\hline
-				c, T=0.6K&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm250_T06.png}&
+				c, $T=\SI{0.6}{\K}$&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm250_T06.png}&
 				\includegraphics[width=0.4\textwidth]{\img/current/curr_lm250_T06.png}\\
@@
 			\end{tabular}
-			\caption{Critical current(maximum minus minimum current) and current versus phase and magnetic field strength, assuming zeeman field does not persists in the superconductor.
-Width of normal strip is 250nm.
-Temperatures of a, b and c respectively: 0.025 K, 0.2K, 0.6K}
+			\caption{Critical current (maximum minus minimum current) and current versus phase and magnetic field strength, assuming Zeeman field does not persists in the superconductor.
+Width of normal strip is 250 nm.
+Temperatures of a, b and c respectively: $\SI{0.025}{\K}$, $\SI{0.2}{\K}$, $\SI{0.6}{\K}$}
 		\end{figure}

### 2018-07-18 two_dim_majoranas_report/progress.tex
Add SimulationSet object

--- 2018-07-16 two_dim_majoranas_report/progress.tex
@@
 
+		\subsubsection{Anna\&Bas}
+		Independence of phase should indeed appear beyond a certain magnetic field, when normal reflection becomes very big.
+When Zeeman is turned on in leads, in a system with infinite sc leads($L_l, L_r \rightarrow \infty$), only a single half diamond appears.
+
 	\begin{figure}[H]
@@
 	 We see that width of the gapless strips along the topological borders are quite wide, requiring very high magnetic field to reach a gapped topological state of the system.
+ 	\subsubsection{Anna\&Bas}
+ 	Relation between topological gap and thouless is given in the paper. Investigate what regime we are in(short, long intermediate junction). Higher chemical potential would also be a thing
 	\begin{table}[H]
@@
 We also see that although we can clearly see the gap closing bands(topological borders) in the gap plots, the underlying gap size does not seem greatly affected by being in topological region or not.
+	\subsubsection{Anna\&Bas}
+	Experiment was run at very small chemical potential, which could cause you to see discretization of the leads.
+It also matters whether the system is 2d infinite or not.
+The diamond chains are caused by gap closings of the different bands.
+If the system is 2d infinite, the gap is always closed.
 
@@
 	The influence of varying spin orbit coupling seems to be limited.
-Although at lower spin orbit couplings, we see strands of gap-closings, which would be interesting to investigate, the energy gap in the topological region does not vary much.
+Although at lower spin orbit couplings, we see strands of gap-closings, which would be interesting to investigate, the energy gap in the topological region does not vary much.		\subsubsection{Anna\&Bas}
+	Effects seen could be due to not counting chemical potential from the bottom of the band, accounting for the term $\propto m\alpha^2$.
+Check ifthis is indeed the case.
+Check if this is indeed the case.
+
+	The gap closing might be due to BD1 symmetry.
+Note that the phase diagram there is $4\pi$ symmetric.
+Shifting phase by $\pi$ causes overall gauge of -1.
+Change gap on left and right lead to break symmetry, see if gap closings persist.
+
 		\begin{figure}[H]
@@
 	Increasing the superconducting gap has the effect of reducing the energy gap somewhat. We also again see the appearance of gapless bands through the regions.
+
+	\subsubsection{Anna\&Bas}
+	Increase width of leads, and rerun experiments. It is weird that gap would decrease as $\Delta$ is increased. Look at band structure.
 		\begin{figure}[H]
@@
 	\subsection{Varying temperature}
-	We 
+	\subsubsection{Anna\&Bas}
+	It is normal to see non block wave phase minimizing current. The current can be split into two contributions. 
+	Due to spin orbit coupling, in 2d infinite system, we have two circular fermi surfaces.
+The values for $\kx,\ky$ which lie on both fermi surfaces, are responsible for the block wave pattern.
+The region outside of that is responsible for a more sinosoidal pattern.
+	So for low spin orbit coupling, the radii are almost the same, and it is all block wave.
 		\begin{figure}[H]

### 2018-07-18 sns_system.py

@@ -122,7 +122,9 @@ def make_sns_system(a, Lm, Lr, Ll, Ly,
 
     return syst
 
-def make_junction(a, Lm, Ly, transverse_soi = True, **pars):
+def make_junction_system(a, Lm, Lr, Ll, Ly,
+                         transverse_soi = True,
+                         zeeman_in_superconductor = False):
     """ 
     Builds and returns finalized junction of the sns system
     
@@ -185,7 +187,9 @@ def make_junction(a, Lm, Ly, transverse_soi = True, **pars):
     
     return syst.finalized()
 
-def make_wrapped_system(a, Lm, Lr, Ll, Ly, Lw, transverse_soi=True, zeeman_in_superconductor=False):
+def make_wrapped_system(a, Lm, Lr, Ll, Ly,
+                        transverse_soi = True,
+                        zeeman_in_superconductor = False):
     template_strings = get_template_strings(transverse_soi, zeeman_in_superconductor)
 
     # TURN HAMILTONIAN STRINGS INTO TEMPLATES

### 2018-07-18 spectrum.py

@@ -55,16 +55,29 @@ def calc_dos_lowest_state(syst, params, syst_pars):
     wf = sns_system.to_site_ph_spin(syst_pars, wfs[:,0])
     return (abs(energies[0]), energy_gap, np.sum(np.abs(wf)**2, axis=2))
 
-def find_gap(lead, params, energy_precision):
+def find_gap_of_lead(lead, params, energy_precision, energy_ub=None, energy_prediction=None):
+    if energy_prediction is not None:
+        assert 0 < energy_prediction < energy_ub
+
     def has_bands(energy):
         smds = lead.modes(energy=energy, params=params)[1]
         return smds.nmodes>0
     
-    energy_ub = params['Delta']
+    if energy_ub is None:
+        energy_ub = params['Delta']
     energy_lb = 0
     
-    ub_has_bands = has_bands(energy_ub)
-    lb_has_bands = has_bands(energy_lb)
+    if energy_prediction is None:
+        ub_has_bands = has_bands(energy_ub)
+        lb_has_bands = has_bands(energy_lb)
+
+    else:
+        energy_prediction_has_bands = has_bands(energy_prediction)
+        if energy_prediction_has_bands:
+            energy_ub = energy_prediction_has_bands
+        else:
+            energy_lb = energy_prediction_has_bands
+
 
     while(energy_ub - energy_lb > energy_precision):
         energy_middle = (energy_ub + energy_lb) / 2

### 2018-07-18 supercurrent.py

@@ -40,10 +40,12 @@ def wrapped_current_k(k, syst_pars, params, cut_tag=0, direction=0):
 
     return sum(I)*params['e']/params['hbar']
 
-def wrapped_current(syst_pars, params, tol=0.01, max_iterations=1e3, transverse_soi=True, zeeman_in_superconductor=False):
-    syst_wrapped = sns_system.make_wrapped_system(**syst_pars,
-     transverse_soi=transverse_soi,
-     zeeman_in_superconductor=zeeman_in_superconductor)
+def wrapped_current(syst_pars, params, tol=0.01, max_iterations=1e3, syst_wrapped=None, transverse_soi=True, zeeman_in_superconductor=False):
+    if syst_wrapped is None:
+        syst_wrapped = sns_system.make_wrapped_system(**syst_pars,
+                                                      transverse_soi=transverse_soi,
+                                                      zeeman_in_superconductor=zeeman_in_superconductor)
+
     cut_tag=0
     direction=0
 

### 2018-07-18 distributed_sns.py
Fixed pickle bug

@@ -62,6 +62,62 @@ def get_list_of_parameter_dictionaries(params_mutable):
 
     return (iterable_keys, param_list)
 
+
+def pfaffian_function(_, syst_total, syst_wrapped, syst_junction, syst_pars, params):
+    return topology.get_pfaffian(syst_total, params)
+
+
+def current_function(current_params, syst_total, syst_wrapped, syst_junction, syst_pars, params):
+    return supercurrent.wrapped_current(syst_pars=syst_pars,
+                                 params=params,
+                                 syst_wrapped=syst_wrapped,
+                                 **current_params)
+
+
+def energy_gap_function(energy_gap_params, syst_total, syst_wrapped, syst_junction, syst_pars, params):
+    return spectrum.find_gap_of_lead(lead=syst_total.leads[0],
+                              params=params,
+                              **energy_gap_params)
+
+
+def transparency_function(self, transparency_params):
+    return None
+
+def bandstructure_function(self, bandstructure_params):
+    return None
+
+def get_correct_metric_function(metric_key, metric_params):
+    options = {
+        'pfaffian': pfaffian_function,
+        'current': current_function,
+        'transparency': transparency_function,
+        'bandstructure': bandstructure_function,
+        'energy_gap': energy_gap_function,
+    }
+    return partial(options[metric_key], metric_params)
+
+def total_function(xy, syst_pars, params, keys_with_bounds, metric_params_dict):
+    syst_total    = sns_system.make_sns_system(**syst_pars)
+    syst_wrapped  = sns_system.make_wrapped_system(**syst_pars)
+    syst_junction = sns_system.make_junction_system(**syst_pars)
+
+    results = np.zeros(len(metric_params_dict))
+
+    keys = keys_with_bounds.keys()
+    params_local = params.copy()
+    for k, val in zip(keys_with_bounds, xy):
+        params_local[k] = val
+    
+    for idx, (metric_key, metric_params) in enumerate(metric_params_dict.items()):
+        metric_function = get_correct_metric_function(metric_key, metric_params)
+        results[idx] = metric_function(syst_total,
+                                       syst_wrapped,
+                                       syst_junction,
+                                       syst_pars,
+                                       params_local)
+        
+    return results
+
 class SimulationSet():
     def __init__(self,
                  keys_with_bounds,
@@ -80,74 +136,14 @@ class SimulationSet():
[…]

### 2018-07-19 two_dim_majoranas_report/progress.tex
Resolved merge conflict

--- 2018-07-16 two_dim_majoranas_report/progress.tex
@@
 
+	\subsubsection{Anna\&Bas}
+	Experiment was run at very small chemical potential, which could cause you to see discretization of the leads.
+It also matters whether the system is 2d infinite or not.
+The diamond chains are caused by gap closings of the different bands.
+If the system is 2d infinite, the gap is always closed.
+
 			\begin{figure}[H]
@@
 	Although at lower spin orbit couplings, we see strands of gap-closings, which would be interesting to investigate, the energy gap in the topological region does not vary much.
+	\subsubsection{Anna\&Bas}
+	Effects seen could be due to not counting chemical potential from the bottom of the band, accounting for the term $\propto m\alpha^2$.
+Check ifthis is indeed the case.
+Check if this is indeed the case.
+
+	The gap closing might be due to BD1 symmetry.
+Note that the phase diagram there is $4\pi$ symmetric.
+Shifting phase by $\pi$ causes overall gauge of -1.
+Change gap on left and right lead to break symmetry, see if gap closings persist.
+
 		\begin{figure}[H]
@@
 	We also again see the appearance of gapless bands through the regions.
+
+	\subsubsection{Anna\&Bas}
+	Increase width of leads, and rerun experiments. It is weird that gap would decrease as $\Delta$ is increased. Look at band structure.
 		\begin{figure}[H]

### 2018-07-19 distributed_sns.py

@@ -1,6 +1,10 @@
 import itertools
 import copy
 import collections
+from functools import partial
+import numpy as np
+import sns_system, topology, spectrum, supercurrent
+import adaptive
 
 def f_adaptive(xy, keys, params, syst_pars,
                      transverse_soi=True,
@@ -57,3 +61,108 @@ def get_list_of_parameter_dictionaries(params_mutable):
         param_list.append(param_element)
 
     return (iterable_keys, param_list)
+
+class SimulationSet():
+    def __init__(self,
+                 keys_with_bounds,
+                 syst_pars,
+                 params,
+                 metric_params_dict):
+
+        self.keys_with_bounds = keys_with_bounds.copy()
+        
+        self.bounds = list(keys_with_bounds.values())
+
+        self.syst_pars = syst_pars.copy()
+        self.params    = params.copy()
+        self.params.update(dict(**sns_system.constants))
+
+        self.metric_index_dict = {metric_key:idx for (idx, metric_key) in enumerate(metric_params_dict.keys())}
+        self.metric_params_dict = metric_params_dict
+
+    def get_correct_metric_function(self, metric_key):
+        metric_params = self.metric_params_dict[metric_key]
+        if metric_key=="pfaffian":
+            return self.get_pfaffian_function(metric_params)
+        elif metric_key=="current":
+            return self.get_current_function(metric_params)
+        elif metric_key=="transparency":
+            return self.get_transparency_function(metric_params)
+        elif metric_key=="bandstructure":
+            return self.get_bandstructure_function(metric_params)
+        elif metric_key=="energy_gap":
+            return self.get_energy_gap_function(metric_params)
+        else:
+            raise ValueError(metric_key + " is not a valid metric")
+
+    def get_pfaffian_function(self, pfaffian_params):
+        def pfaffian_function(syst_total, syst_wrapped, syst_junction, syst_pars, params):
+            return topology.get_pfaffian(syst_total, params)
+
+        return pfaffian_function
+
+    def get_current_function(self, current_params):
+        def current_function(syst_total, syst_wrapped, syst_junction, syst_pars, params):
+            return supercurrent.wrapped_current(syst_pars=syst_pars,
+                                         params=params,
+                                         syst_wrapped=syst_wrapped,
+                                         **current_params)
+
+        return current_function
+
+    def get_energy_gap_function(self, energy_gap_params):
+        def energy_gap_function(syst_total, syst_wrapped, syst_junction, syst_pars, params):
[…]

### 2018-07-19 supercurrent.py
Add bind to current operator

@@ -61,9 +61,10 @@ def wrapped_current(syst_pars, params, tol=0.01, max_iterations=1e3, syst_wrappe
         p = dict(k_x=k, **params)
         ham = syst_wrapped.hamiltonian_submatrix(params=p)
         (en, evs) = np.linalg.eigh(ham)
-
+        
+        local_current_operator = current_operator.bind(params=p)
         for (e, ev) in zip(en, evs.T):
-            I += fermi_dirac(e.real, p) * current_operator(ev, params=p)
+            I += fermi_dirac(e.real, p) * local_current_operator(ev)
         return sum(I)*params['e']/params['hbar']
 
     learner = adaptive.IntegratorLearner(f, [0, np.pi], tol)

### 2018-07-19 distributed_sns.py
Add newaxis to solve broadcating issue in loss function

@@ -155,7 +155,7 @@ class SimulationSet():
             metric_scale = np.max(ip.values, 0)-np.min(ip.values, 0)
             metric_scale[metric_scale==0] = 1
             
-            dev = np.sum(deviations(ip)/metric_scale, axis=0)
+            dev = np.sum(deviations(ip)/metric_scale[:,np.newaxis], axis=0)
             A = areas(ip)
             losses = dev * np.sqrt(A) + 0.3 * A
             return losses

### 2018-07-19 distributed_sns.py
Added plotting capabilities and pfaffian contoru

@@ -5,6 +5,7 @@ from functools import partial
 import numpy as np
 import sns_system, topology, spectrum, supercurrent
 import adaptive
+import holoviews as hv
 
 def f_adaptive(xy, keys, params, syst_pars,
                      transverse_soi=True,
@@ -133,8 +134,28 @@ class SimulationSet():
         self.params    = params.copy()
         self.params.update(dict(**sns_system.constants))
 
-        self.metric_index_dict = {metric_key:idx for (idx, metric_key) in enumerate(metric_params_dict.keys())}
         self.metric_params_dict = metric_params_dict
+
+    @property
+    def xscale(self):
+        return abs(self.bounds[0][0]-self.bounds[0][1])
+    
+    @property
+    def yscale(self):
+        return abs(self.bounds[1][0]-self.bounds[1][1])
+
+    @property
+    def xcenter(self):
+        return (self.bounds[0][0]+self.bounds[0][1])/2
+   
+    @property
+    def ycenter(self):
+        return (self.bounds[1][0]+self.bounds[1][1])/2
+
+    def unnormalize(self, x, y):
+        x_unscaled = self.xscale * x + self.xcenter
+        y_unscaled = self.yscale * y + self.ycenter
+        return(x_unscaled, y_unscaled)
 
     def get_total_function(self):
         return partial(total_function,
@@ -159,5 +180,38 @@ class SimulationSet():
 
     def get_learner(self):
         f = self.get_total_function()
-        learner = adaptive.Learner2D(f, bounds=self.bounds, loss_per_triangle=self.default_metric())
-        return learner
+        self.learner = adaptive.Learner2D(f, bounds=self.bounds, loss_per_triangle=self.default_metric())
+        return self.learner
+
+    def plot(self, n=200, pfaffian_contour=True):
+        plot_dictionary = self.get_plot_dictionary(n)
+        map_plot = hv.HoloMap(plot_dictionary,
+                              kdims='Metric').opts(norm=dict(framewise=True))
+        if pfaffian_contour:
+            xy = get_pfaffian_contour(plot_dictionary)
+            contour_pfaffian = hv.Path(xy)
+            return map_plot*contour_pfaffian
+        else:
+            return map_plot
+
+    def get_plot_dictionary(self, n):
+        ip = self.learner.ip()
+        normalized_dim = np.linspace(-.5,.5, n)
[…]

### 2018-07-19 distributed_sns.py
Added ASS class

@@ -2,6 +2,7 @@ import itertools
 import copy
 import collections
 from functools import partial
+from itertools import product
 import numpy as np
 import sns_system, topology, spectrum, supercurrent
 import adaptive
@@ -187,12 +188,15 @@ class SimulationSet():
         plot_dictionary = self.get_plot_dictionary(n)
         map_plot = hv.HoloMap(plot_dictionary,
                               kdims='Metric').opts(norm=dict(framewise=True))
+
+        keys = list(self.keys_with_bounds.keys())
+
         if pfaffian_contour:
             xy = get_pfaffian_contour(plot_dictionary)
             contour_pfaffian = hv.Path(xy)
-            return map_plot*contour_pfaffian
+            return (map_plot*contour_pfaffian).redim(x=keys[0], y=keys[1])
         else:
-            return map_plot
+            return map_plot.redim(x=keys[0], y=keys[1])
 
     def get_plot_dictionary(self, n):
         ip = self.learner.ip()
@@ -201,7 +205,6 @@ class SimulationSet():
 
         gridx, gridy = np.meshgrid(normalized_dim, normalized_dim)
         gridded_results = ip(gridx, gridy)
-
 
         plot_dictionary = dict()
         for idx, metric_key in enumerate(self.metric_params_dict):
@@ -215,3 +218,58 @@ def get_pfaffian_contour(plot_dictionary):
         xdata = contour_pfaffian.data[0]['x']
         ydata = contour_pfaffian.data[0]['y']
         return (xdata, ydata)
+
+class AggregatesSimulationSet:
+    def __init__(self,
+                 keys_with_bounds,
+                 syst_pars,
+                 params,
+                 metric_params_dict):
+
+        self.syst_pars_dimensions = {}
+        self.params_dimensions = {}
+        
+
+        self.keys_with_bounds = keys_with_bounds.copy()
+        
+        self.bounds = list(keys_with_bounds.values())
+
+        self.syst_pars = syst_pars.copy()
+        self.params    = params.copy()
+        self.params.update(dict(**sns_system.constants))
+
+        self.metric_params_dict = metric_params_dict
+
+    
+    def add_dimension(self, dimension_name, dimension_values):
+        if self.syst_pars.get(dimension_name):
+            self.syst_pars_dimensions[dimension_name] = dimension_values
+        elif self.params.get(dimension_name):
+            self.params_dimensions[dimension_name] = dimension_values
+        else:
[…]

### 2018-07-20 distributed_sns.py
Add plotting to Aggregate simulation set

@@ -219,6 +219,14 @@ def get_pfaffian_contour(plot_dictionary):
         ydata = contour_pfaffian.data[0]['y']
         return (xdata, ydata)
 
+def loss_enough_points(loss_function, enough_points):
+    def loss_f(ip):
+        from adaptive.learner.learner2D import areas
+        loss = loss_function(ip)
+        dim = areas(ip).shape[0]
+        return 1e8 * loss / dim if dim < enough_points else loss
+    return loss_f
+
 class AggregatesSimulationSet:
     def __init__(self,
                  keys_with_bounds,
@@ -231,17 +239,18 @@ class AggregatesSimulationSet:
         
 
         self.keys_with_bounds = keys_with_bounds.copy()
-        
-        self.bounds = list(keys_with_bounds.values())
+        self.keys = tuple(keys_with_bounds.keys())
+        self.bounds = tuple(keys_with_bounds.values())
 
         self.syst_pars = syst_pars.copy()
         self.params    = params.copy()
         self.params.update(dict(**sns_system.constants))
 
         self.metric_params_dict = metric_params_dict
-
     
     def add_dimension(self, dimension_name, dimension_values):
+        assert dimension_name != self.keys[0] and dimension_name != self.keys[1]
+
         if self.syst_pars.get(dimension_name):
             self.syst_pars_dimensions[dimension_name] = dimension_values
         elif self.params.get(dimension_name):
@@ -265,11 +274,34 @@ class AggregatesSimulationSet:
 
         self.simulation_set_list = simulation_set_list
 
-    def make_learners(self):
+    def make_learners(self, enough_points):
         self.make_simulation_sets()
         self.learners = [ss.get_learner() for ss in self.simulation_set_list]
+        for learner in self.learners:
+            loss_function = learner.loss_per_triangle
+            learner.loss_per_triangle = loss_enough_points(loss_function, enough_points)
 
-    def get_balancing_learner(self):
-        self.make_learners()
+    def get_balancing_learner(self, enough_points=1):
+        self.make_learners(enough_points)
         return adaptive.BalancingLearner(self.learners)
 
+    def get_plot_dict(self, n, contour_pfaffian=False):
+        plot_dict = dict()
+        kdims = list(self.params_dimensions.keys())+ list(self.syst_pars_dimensions.keys()) + ['Metric']
+
+        for ss in self.simulation_set_list:
+            local_plot_dict = ss.get_plot_dictionary(n)
+            if contour_pfaffian is not False:
[…]

### 2018-07-31 distributed_sns.py
Created test directory, and fixed bigs from consistent_hash and simulation set

@@ -319,10 +319,10 @@ class AggregatesSimulationSet():
         hash_dict = {}
         hash_func = lambda dictionary: hex(consistent_hash(dictionary) % 2**(4*n_digits))[2:]
         hash_str = '<KB_' + hash_func(self.keys_with_bounds) + '_>'
-        hash_str += '<PRMS_' + hash_func([(k, v) for k,v in self.params.items() if type(v) is float or type(v) is int]) + '_>'
-        hash_str += '<PARS_' + hash_func([(k, v) for k,v in self.syst_pars.items() if type(v) is float or type(v) is int]) + '_>'
-        hash_str += '<METR_' + hash_func([(k, tuple(v.items())) for k,v in self.metric_params_dict.items()]) + '_>'
-        hash_str += '<DIM_' + hash_func(self.dimension_dict.keys()) + '_>'
+        hash_str += '<PRMS_' + hash_func(self.params) + '_>'
+        hash_str += '<PARS_' + hash_func(self.syst_pars) + '_>'
+        hash_str += '<METR_' + hash_func(self.metric_params_dict) + '_>'
+        hash_str += '<DIM_' + hash_func(self.dimension_dict) + '_>'
         return hash_str
 
     def add_dimension(self, dimension_name, dimension_functions):
@@ -411,14 +411,14 @@ class AggregatesSimulationSet():
         self.make_balancing_learner(enough_points)
         self.learner.load(folder, fname_pattern=self.learner_file_prefix + self.hash_str + '{}')
 
-    def load_from_file(fname, folder=''):
+    def load_from_file(fname, folder, enough_points):
         fname = os.path.join(folder, AggregatesSimulationSet.aggregate_simulation_set_file_prefix + fname)
 
         with open(fname, 'rb') as f:
-                (self.input_params, self.dimension_dict) = dill.load(f)
+                (input_params, dimension_dict) = dill.load(f)
 
-        ass = SimulationSet(*input_params)
+        ass = AggregatesSimulationSet(*input_params)
         for k,v in dimension_dict.items():
             ass.add_dimension(k, v)
-        ass.load(folder)
-        return ss
+        ass.load(folder, enough_points)
+        return ass

### 2018-07-31 utils.py

@@ -3,6 +3,7 @@ import dill
 import hashlib
 import types
 import inspect
+import functools
 
 def hash_dict(dictionary):
     temp_dict = dict()
@@ -45,6 +46,12 @@ def hash_str(obj):
 def hash_function(obj):
     return consistent_hash(inspect.getsource(obj))
 
+def hash_builtin_function(obj):
+	return consistent_hash(obj.__name__)
+
+def hash_partial_function(obj):
+	return consistent_hash(obj.func)
+
 def consistent_hash(obj):
     hash_funcs = {
         dict:hash_dict,
@@ -53,7 +60,10 @@ def consistent_hash(obj):
         int:hash_int,
         float:hash_float,
         str:hash_str,
-        types.FunctionType:hash_function
+        types.FunctionType:hash_function,
+        types.BuiltinFunctionType:hash_builtin_function,
+        bool:hash_int,
+        functools.partial:hash_partial_function
     }
     return hash_funcs[type(obj)](obj)
 
@@ -61,4 +71,3 @@ def consistent_hash(obj):
 
 
 
-    

### 2018-08-01 Notebooks/low_spin_orbit_current/rename_bunch.sh
Changed hash_str of dims, and added fermi surface to plots

@@ -1,0 +1,31 @@
+prefix=""
+for f in learner_data_\<KB_c0a2a5_\>\<PRMS_84abf4_\>\<PARS_382836_\>\<METR_29c1a_\>\<DIM_*;
+do
+	common=${f:0:-4}
+	echo $common
+	prefix=${f:0:13}
+	echo $prefix
+	
+	kb_hash=${f:13:12}
+	echo $kb_hash
+
+	prms_hash=${f:25:14}
+	echo $prms_hash
+	
+	pars_hash=${f:39:14}
+	echo $pars_hash
+	
+	metr_hash=${f:53:13}
+	echo $metr_hash
+		
+	dim_hash=${f:66:13}
+	echo $dim_hash
+	
+
+	suffix=${f:79:4}
+	echo $suffix
+
+	echo $prefix$kb_hash$prms_hash$pars_hash$metr_hash"<DIM_8d79d7_>"$suffix
+	echo $f
+	mv -v $f $prefix$kb_hash$prms_hash$pars_hash$metr_hash"<DIM_8d79d7_>"$suffix
+done;

### 2018-08-01 distributed_sns.py

@@ -322,7 +322,7 @@ class AggregatesSimulationSet():
         hash_str += '<PRMS_' + hash_func(self.params) + '_>'
         hash_str += '<PARS_' + hash_func(self.syst_pars) + '_>'
         hash_str += '<METR_' + hash_func(self.metric_params_dict) + '_>'
-        hash_str += '<DIM_' + hash_func(self.dimension_dict) + '_>'
+        hash_str += '<DIM_' + hash_func({k:len(v) for k,v in self.dimension_dict.items()}) + '_>'
         return hash_str
 
     def add_dimension(self, dimension_name, dimension_functions):

### 2018-08-02 distributed_sns.py
Add table to plots, and added dispersion reloation to spectum.py

@@ -103,6 +103,7 @@ def get_correct_metric_function(metric_key, metric_params):
     }
     return partial(options[metric_key], metric_params)
 
+
 def total_function(xy, syst_pars, params, keys_with_bounds, metric_params_dict):
     syst_total    = sns_system.make_sns_system(**syst_pars)
     syst_wrapped  = sns_system.make_wrapped_system(**syst_pars)
@@ -152,6 +153,12 @@ class SimulationSet():
                 self.syst_pars,
                 self.params,
                 self.metric_params_dict)
+    
+    @property
+    def table_dicts(self):
+        params = {k:v for k,v in self.params.items() if ((k in sns_system.dummy_params_raw) and (k not in self.keys_with_bounds))}
+        return (self.syst_pars, params)
+
     @property
     def hash_str(self):
         n_digits=6
@@ -278,6 +285,11 @@ def loss_enough_points(loss_function, enough_points):
         return 1e30 * loss / dim if dim < enough_points else loss
     return loss_f
 
+def ptable(dictionary):
+    return hv.Table({'Parameter name':list(dictionary.keys()),
+          'Value':list(dictionary.values())},['Parameter name', 'Value'])
+
+
 class AggregatesSimulationSet():
     learner_file_prefix = 'learner_data_'
     aggregate_simulation_set_file_prefix = 'aggregate_simulation_set_data_'
@@ -313,6 +325,10 @@ class AggregatesSimulationSet():
     def learners(self):
         return self.learner.learners
     
+    @property
+    def simulation_set_dict(self):
+            return {tuple(ss.dimension_values):ss for ss in self.simulation_set_list}
+
     @property
     def hash_str(self):
         n_digits=6
@@ -366,10 +382,22 @@ class AggregatesSimulationSet():
     
     def get_balancing_learner(self):
         return self.learner
-    
-    def get_plot_dict(self, n, contour_pfaffian=False):
+
+    def get_parameter_table_dicts(self):
+        table_dict_params = {}
+        table_dict_syst_pars = {}
+        for ss_key, ss in self.simulation_set_dict.items():
+            for metric_key in self.metric_params_dict:
+                syst_pars, params_raw = ss.table_dicts
+                table_dict_params[(*ss_key, metric_key)] = ptable(params_raw)
+                table_dict_syst_pars[(*ss_key, metric_key)] = ptable(syst_pars)
+        return (table_dict_syst_pars, table_dict_params)
+
[…]

### 2018-08-02 sns_system.py

@@ -13,19 +13,21 @@ constants = dict(
     cos=cmath.cos,
     sin=cmath.sin)
 
+dummy_params_raw = dict(g_factor_middle=1,
+                        g_factor_left=2,
+                        g_factor_right=3,
+                        mu=4,
+                        alpha_middle=5,
+                        alpha_left=6,
+                        alpha_right=7,
+                        Delta_left=8,
+                        Delta_right=9,
+                        B=10,
+                        phase=11,
+                        T=12)
+
 dummy_params = dict(**constants,
-                    g_factor_middle=1,
-                    g_factor_left=2,
-                    g_factor_right=3,
-                    mu=4,
-                    alpha_middle=5,
-                    alpha_left=6,
-                    alpha_right=7,
-                    Delta_left=8,
-                    Delta_right=9,
-                    B=10,
-                    phase=11,
-                    T=12)
+                    **dummy_params_raw)
 
 def get_template_strings(transverse_soi, mu_from_bottom_of_spin_orbit_bands=True):
     if mu_from_bottom_of_spin_orbit_bands:

### 2018-08-02 spectrum.py

@@ -4,6 +4,11 @@ import scipy.sparse as sp
 import scipy.sparse.linalg as sla
 import sns_system
 
+def dispersion(kx, ky, params):
+    Ekin  = params['hbar']**2/(2*params['m_eff']) * (kx**2 + ky**2) - params['mu'] + params['m_eff'] * params['alpha_middle']**2 / (2 * params['hbar']**2)
+    Erest = np.sqrt(params['alpha_middle']**2 * ky**2 + (params['alpha_middle']*kx - params['g_factor_middle'] * params['mu_B'] * params['B'])**2)
+    return (Ekin + Erest, Ekin - Erest)
+    
 def sparse_diag(matrix, k, sigma, **kwargs):
     """Call sla.eigsh with mumps support.
 

### 2018-08-02 distributed_sns.py
reverted to old hashing function style

@@ -338,7 +338,7 @@ class AggregatesSimulationSet():
         hash_str += '<PRMS_' + hash_func(self.params) + '_>'
         hash_str += '<PARS_' + hash_func(self.syst_pars) + '_>'
         hash_str += '<METR_' + hash_func(self.metric_params_dict) + '_>'
-        hash_str += '<DIM_' + hash_func({k:len(v) for k,v in self.dimension_dict.items()}) + '_>'
+        hash_str += '<DIM_' + hash_func(self.dimension_dict) + '_>'
         return hash_str
 
     def add_dimension(self, dimension_name, dimension_functions):

### 2018-09-06 thesis_report/theory.tex
Report basis

\chapter{Theory}

%%--------------------------------------------------------------------------
%% Topology in solid state physics
%%-----------------------includeonly---------------------------------------------------
\section{Topology in solid state physics}
The Wikipedia definition of mathematical topology is as follows: \quote{Topology can be formally defined as "the study of qualitative properties of certain objects (called topological spaces) that are invariant under a certain kind of transformation}\cite{wiki:topology}\\
Hello

### 2018-09-06 thesis_report/title.tex
Report basis

\begin{titlepage}

\begin{center}

%% Insert the TU Delft logo at the bottom of the page.

%% Print the title in cyan.
{\makeatletter
\largetitlestyle\fontsize{64}{94}\selectfont\@title
%\largetitlestyle\color{tudelft-cyan}\Huge\@title
\makeatother}

%% Print the optional subtitle in black.
{\makeatletter
\ifx\@subtitle\undefined\else
    \bigskip
   {\tudsffamily\fontsize{22}{32}\selectfont\@subtitle}    
    %\titlefont\titleshape\LARGE\@subtitle
\fi
\makeatother}

\bigskip
\bigskip

by
%door

\bigskip
\bigskip

%% Print the name of the author.
{\makeatletter
%\largetitlefont\Large\bfseries\@author
\largetitlestyle\fontsize{26}{26}\selectfont\@author
\makeatother}

\bigskip
\bigskip

to obtain the degree of Master of Science
%ter verkrijging van de graad van Master of Science

at the Delft University of Technology,
%aan de Technische Universiteit Delft,

to be defended publicly on Tuesday January 1, 2013 at 10:00 AM.
%in het openbaar de verdedigen op dinsdag 1 januari om 10:00 uur.

\vfill

\begin{tabular}{lll}
    Student number: & 4247078 \\
    Project duration: & \multicolumn{2}{l}{March 1, 2018 -- November 28, 2018} \\
    Thesis committee: & dr.\ A.\ Akhmerov, & TU Delft, supervisor \\
        & MSc.\ B.\ Nijholt, & TU Delft \\
\end{tabular}
%% Only include the following lines if confidentiality is applicable.

\bigskip
\bigskip

An electronic version of this thesis is available at \url{http://repository.tudelft.nl/}.

\end{center}

\begin{tikzpicture}[remember picture, overlay]
    \node at (current page.south)[anchor=south,inner sep=0pt]{
        \includegraphics{cover/logo_black}
    };
\end{tikzpicture}

\end{titlepage}

### 2018-09-13 formulas.py
Added general formulas like thouless and kf

@@ -1,0 +1,17 @@
+import scipy.constants
+import numpy as np
+
+HBAR 	 	= scipy.constants.hbar
+HBAR_MEV	= scipy.constants.hbar / (scipy.constants.eV * 1e-3)
+PI 			= np.pi
+M_EV_NM 	= scipy.constants.m_e / (scipy.constants.eV * 1e-3) / 1e18
+
+def thouless_energy(vF, W):
+	 return HBAR_MEV*(PI/2)*vF/W
+
+def fermi_wavenumber(mu, m_eff):
+	return np.sqrt(2 * (m_eff*M_EV_NM) * mu)/HBAR_MEV
+
+def fermi_velocity(mu, m_eff):
+	kf = fermi_wavenumber(mu, m_eff)
+	return HBAR_MEV * kf / (m_eff*M_EV_NM)

### 2018-09-13 thesis_report/theory.tex
Add makefile to compile latex on io. Add snippets.

@@
+% Momentum operators
+\newcommand{\kx}{k_x}
+\newcommand{\ky}{k_y}
+
+% Pauli matrices
+\newcommand{\sigx}{\sigma_x}
+\newcommand{\sigy}{\sigma_y}
+\newcommand{\sigz}{\sigma_z}
+\newcommand{\sigi}{\sigma_0}
+\newcommand{\taux}{\tau_x}
+\newcommand{\tauy}{\tau_y}
+\newcommand{\tauz}{\tau_z}
+\newcommand{\taui}{\tau_0}
 \chapter{Theory}
 
+%%██████████████████████████████████████████████████████████████████████████
+%%██ General Physics
+%%██████████████████████████████████████████████████████████████████████████
+\section{General Physics}
 %%--------------------------------------------------------------------------
-%% Topology in solid state physics
-%%-----------------------includeonly---------------------------------------------------
-\section{Topology in solid state physics}
-The Wikipedia definition of mathematical topology is as follows: \quote{Topology can be formally defined as "the study of qualitative properties of certain objects (called topological spaces) that are invariant under a certain kind of transformation}\cite{wiki:topology}\\
-Hello
+%%  Spin-orbit coupling
+    \subsection{Spin-orbit coupling}
+    Rashba spin orbit coupling:
+    \begin{equation}
+    	H_\text{Rashba} = \alpha (\ky \sigx - \kx \sigy) 
+    \end{equation}
+
+%%--------------------------------------------------------------------------
+%%  Supercurrent
+    \subsection{Supercurrent}
+    As the field we are describing is 
+%%▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓
+
+%%██████████████████████████████████████████████████████████████████████████
+%%██ Tight binding
+%%██████████████████████████████████████████████████████████████████████████
+\section{Tight binding}
+
+%%▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓
+
+%%██████████████████████████████████████████████████████████████████████████
+%%██ Topology in solid state physics
+%%██████████████████████████████████████████████████████████████████████████
+\section{Topology in solid state physics}     The Wikipedia definition of
+mathematical topology is as follows: \quote{Topology can be formally defined as
+"the study of qualitative properties of certain objects (called topological
+spaces) that are invariant under a certain kind of
+transformation}\cite{wiki:topology}\\
+
+%%-------------------------------------------------------------------------- 
+%% Symmetries     
+\subsection{Symmetries}
+
+%%▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓

### 2018-09-13 thesis_report/latex_utils/put_snippets_into_config.sh

@@ -1,0 +1,2 @@
+#!/bin/bash
+cp -a ./ ~/.config/sublime-text-3/Packages/User/

### 2018-09-13 sns_system.py
Add notebooks, and added option for kx=0 in sc

@@ -40,7 +40,7 @@ dummy_params = dict(**constants,
 
 @lru_cache()
 def get_template_strings(
-        transverse_soi, mu_from_bottom_of_spin_orbit_bands=True):
+        transverse_soi, mu_from_bottom_of_spin_orbit_bands=True, k_x_in_sc=False):
     if mu_from_bottom_of_spin_orbit_bands:
         ham_str = "(hbar^2 / (2*m_eff) * (k_y^2 + k_x^2) - mu + m_eff*alpha_middle^2 / (2 * hbar^2)) * kron(sigma_0, sigma_z) "
     else:
@@ -71,6 +71,10 @@ def get_template_strings(
     ham_sc_left += "+ g_factor_left * mu_B * B * kron(sigma_x, sigma_0)"
     ham_sc_right += "+ g_factor_right * mu_B * B * kron(sigma_x, sigma_0)"
 
+    if not k_x_in_sc:
+        ham_sc_right = ham_sc_right.replace('k_x', '0')
+        ham_sc_left = ham_sc_left.replace('k_x', '0')
+
     template_strings = dict(ham_barrier=ham_barrier,
                             ham_normal=ham_normal,
                             ham_sc_right=ham_sc_right,
@@ -83,7 +87,8 @@ def get_template_strings(
 def make_sns_leaded_system(a, L_m, L_x,
                     transverse_soi=True,
                     mu_from_bottom_of_spin_orbit_bands=True,
-                    with_vlead=False, **_):
+                    k_x_in_sc=False,
+                    with_vlead=False, k_x_in_sc=False, **_):
     """
     Builds and returns finalized 2dim sns system
 
@@ -110,14 +115,15 @@ def make_sns_leaded_system(a, L_m, L_x,
         transverse_soi, mu_from_bottom_of_spin_orbit_bands)
 
     # TURN HAMILTONIAN STRINGS INTO TEMPLATES
+    kwargs = dict(coords=('x', 'y'), grid_spacing=a)
     template_barrier = kwant.continuum.discretize(
-        template_strings['ham_barrier'], grid_spacing=a)
+        template_strings['ham_barrier'], **kwargs)
     template_normal = kwant.continuum.discretize(
-        template_strings['ham_normal'], grid_spacing=a)
+        template_strings['ham_normal'], **kwargs)
     template_sc_left = kwant.continuum.discretize(
-        template_strings['ham_sc_left'], grid_spacing=a)
+        template_strings['ham_sc_left'], **kwargs)
[…]

### 2018-09-25 formulas.py
Add zigzag and L-systems

@@ -15,3 +15,6 @@ def fermi_wavenumber(mu, m_eff):
 def fermi_velocity(mu, m_eff):
 	kf = fermi_wavenumber(mu, m_eff)
 	return HBAR_MEV * kf / (m_eff*M_EV_NM)
+
+def density_to_mu(density, m_eff):
+	return HBAR_MEV**2 * PI * density/ (m_eff*M_EV_NM)

### 2018-09-25 plotting_results.py

@@ -10,7 +10,7 @@ import holoviews as hv
 
 
 def plot_syst(syst_pars=None, params=None, a_new=None,
-              num_lead_cells=4, syst=None):
+              num_lead_cells=4, syst=None, **args):
     if syst is None:
         a = syst_pars['a'] if a_new is None else a_new
         L_down = syst_pars['L_down']
@@ -21,13 +21,13 @@ def plot_syst(syst_pars=None, params=None, a_new=None,
         syst, _ = sns_system.make_sns_system(a=a, L_down=L_down, L_m=L_m, L_up=L_up, L_x=L_x)
 
     def delta(sites):
-        return [np.abs(syst.hamiltonian(i, i, params=params)[1, 0])
+        return [np.sum(np.abs(syst.hamiltonian(i, i, params=params)))
                 for i, site in enumerate(sites)]
 
     return kwant.plot(syst, num_lead_cells=num_lead_cells,
                       site_color=delta(syst.sites),
                       fig_size=(5, 5),
-                      show=False)
+                      show=False, **args)
 
 
 def plot_pfaffian(params, results, figsize=(5, 5)):

### 2018-11-14 paper/snakemajoranas.tex
add paper template and add it to the CI

\documentclass[english, twocolumn, 10pt, aps, superscriptaddress, floatfix, prb, citeautoscript]{revtex4-1}
\pdfoutput=1
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{verbatim}
\usepackage{units}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{wasysym}
\usepackage{layouts}
\usepackage{siunitx}
\usepackage{bm}
\usepackage{xcolor}
\usepackage[colorlinks, citecolor={blue!50!black}, urlcolor={blue!50!black}, linkcolor={red!50!black}]{hyperref}
\usepackage{bookmark}
\usepackage{tabularx}
\usepackage{microtype}
\usepackage{babel}
\hypersetup{pdfauthor={T. Laeven and friends},pdftitle={Increasing the topological gap by an order of magnitude through the geomerty for Majorana SNS junctions.}}

\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{4}

\DeclareMathOperator{\e}{e}
\DeclareMathOperator{\de}{d\!}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\diag}{diag}
\DeclareMathOperator{\Res}{Res}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\Pf}{Pf}
\DeclareMathOperator{\Det}{Det}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\im}{Im}
\DeclareMathOperator{\re}{Re}

\renewcommand{\comment}[2]{#2}
% Uncomment the following line for paragraph descriptions to appear in the file.
\renewcommand{\comment}{\paragraph}

\DeclarePairedDelimiter\abs{\lvert}{\rvert}
\DeclarePairedDelimiter\norm{\lVert}{\rVert}

\makeatletter
\let\oldabs\abs
\def\abs{\@ifstar{\oldabs}{\oldabs*}}
\let\oldnorm\norm
\def\norm{\@ifstar{\oldnorm}{\oldnorm*}}
\makeatother

\newcommand{\ev}[1]{\langle#1\rangle}
\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\bracket}[2]{\langle#1|#2\rangle}

\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}

\begin{document}

\title{Increasing the topological gap by an order of magnitude through the geomerty for Majorana SNS junctions.}

\author{Tom Laeven}
\affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
\email[Electronic address: ]{tlaeven@hotmail.com}

\author{Bas Nijholt}
\affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
\email[Electronic address: ]{bas@nijho.lt}

\author{Michael Wimmer}
\affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
\affiliation{QuTech, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
\email[Electronic address: ]{m.t.wimmer@tudelft.nl}

\author{Anton R. Akhmerov}
\email[Electronic address: ]{snakemajoranas@antonakhmerov.org}
\affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}

\date{\today}

\begin{abstract}
We are solving a problem of soft gap in high density SNS Majorana junctions \cite{pientka2017topological}.
We do this by introducing a zigzag geometry.
This works because the maximum trajactory length is cut-off due to the geomerty and therefore the minimal energy gap is given by a simple formula, which we also verify using numerics.
In addition to having a large minimum energy gap, the abscence of long length trajectories means that the localization length is very short as well.
\end{abstract}

\maketitle

\section{Introduction}

\comment{The gap is small because of long trajectories.}

\begin{figure}
% \includegraphics[width=0.95\columnwidth]{figures/SOME_FIGURE}
\caption{Setups. Figure of a straight and zigzag system, including trajectories.
\label{fig:setup}}
\end{figure}

\section{Analytical estimate}

Quasi classical short junction calculation explaination.
Include all, later move stuff to the appendix if necessary.

\section{Numerical bandstructures}

\comment{We consider a 2D SNS junction with a Rashba-BdG Hamiltonian.}

\comment{We discretize the model and simulate it with Kwant.}

\section{Calculating the bandstuctures.}

\section{Calculating the topological phase diagram.}

\comment{We use a generalized eigenvalue problem to find all phase boundaries at once.}

\comment{We calculate the gap by finding the minimum energy in the spectrum.}

\begin{figure}
% \includegraphics[width=0.95\columnwidth]{figures/SOME_FIGURE}
\caption{Figure of the bandstuctures.
Where the lines are (blue) $\phi=0$, $B=0$ and (red) $\phi=\pi$, $B \ne 0$.
and the subplots (a) $z_y=0$, (b) $z_y=\frac{W}{2}$, and (c) $z_y=W$, where $W$ is the junction width.
\label{fig:bandstuctures}}
\end{figure}

\begin{figure}
% \includegraphics[width=0.95\columnwidth]{figures/SOME_FIGURE}
\caption{Phase diagrams of a straight system (a, b) and zigzag system (c, d), where (a, c) are $E(\mu, B)$ and (b, d) are $E(\phi, B)$.
We use a generalized eigenvalue problem to find all phase boundaries at once and find the minimal energy gap by finding the minimum in the spectrum: $\min{E(k)}$.
\label{fig:phasediagrams}}
\end{figure}

\section{Localization lengths and shape effect}

\comment{We find the Majorana lengths by calculating the slowest decaying mode.}

\begin{figure}
% \includegraphics[width=0.95\columnwidth]{figures/SOME_FIGURE}
\caption{Wavefunctions for different sizes and geometries.
With (a) a straight system, (b) a zigzag sytem, (c) a system where the normal region is defined by two parallel sine waves, and (d) a system with the Laeven shape.
Inside the figure we indicate the Majorana lenght (or coherence length) $\xi$ and the topological energy gap $E_\textrm{gap}.$
We observe that $\xi$ for (a) is orders of magnitude longer and $E_\textrm{gap}$ orders of magnitude smaller than for (b, c, d), meaning that the details of the geometry do not matter.
\label{fig:wavefunctions}}
\end{figure}

\section{Discussion and Conclusions}

\comment{Extensions: we omit several physical effects, disorder, electrostatics, etc.}

\comment{Outlook: how to cope with the complications.}

\comment{Acknowledgments}

We are grateful to M. Irfan, L. P. Kouwenhoven, R. M. Lutchyn, C. M. Marcus, T. Ö. Rosdahl, S. Rubbert, D. Sticlet, and D. Varjas for useful discussions.
This work was supported by the Netherlands Organization for Scientific Research (NWO/OCW), as part of the Frontiers of Nanoscience program, the Foundation for Fundamental Research on Matter (FOM), and an ERC Starting Grant STATOPINS 638760.

\bibliographystyle{apsrev4-1}
\bibliography{snakemajoranas}
\end{document}

### 2018-11-14 paper/snakemajoranas.tex
add paragraphs (Anton's suggestion)
add bandstructures plot
fix the bandstructure plot

@@
 
+\comment{Majoranas are mostly made in hybrid NS structures.}
+\comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
 \comment{The gap is small because of long trajectories.}
+\comment{We show that zigzag geometry solves this problem in a controllable manner.}
 
@@
 \begin{figure}
-% \includegraphics[width=0.95\columnwidth]{figures/SOME_FIGURE}
+\includegraphics[width=0.95\columnwidth]{figures/bandstructures}
 \caption{Figure of the bandstuctures.
 Where the lines are (blue) $\phi=0$, $B=0$ and (red) $\phi=\pi$, $B \ne 0$.
-and the subplots (a) $z_y=0$, (b) $z_y=\frac{W}{2}$, and (c) $z_y=W$, where $W$ is the junction width.
+and the subplots (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W$ is the junction width.
+We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
 \label{fig:bandstuctures}}

### 2018-11-15 paper/snakemajoranas.tex
remove authors and acknowledgments

@@
 \usepackage{babel}
-\hypersetup{pdfauthor={T. Laeven and friends},pdftitle={Increasing the topological gap by an order of magnitude through the geomerty for Majorana SNS junctions.}}
+\hypersetup{pdfauthor={Quantum Tinkerer},pdftitle={Increasing the topological gap by an order of magnitude through the geomerty for Majorana SNS junctions.}}
 
@@
 
-\author{Tom Laeven}
+\author{Quantum Tinkerer}
 \affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
-\email[Electronic address: ]{tlaeven@hotmail.com}
-
-\author{Bas Nijholt}
-\affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
-\email[Electronic address: ]{bas@nijho.lt}
-
-\author{Michael Wimmer}
-\affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
-\affiliation{QuTech, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
-\email[Electronic address: ]{m.t.wimmer@tudelft.nl}
-
-\author{Anton R. Akhmerov}
-\email[Electronic address: ]{snakemajoranas@antonakhmerov.org}
-\affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
+\email[Electronic address: ]{quantumtinkerer@tudelft.nl}
 
@@
 
-We are grateful to M. Irfan, L. P. Kouwenhoven, R. M. Lutchyn, C. M. Marcus, T. Ö. Rosdahl, S. Rubbert, D. Sticlet, and D. Varjas for useful discussions.
+We are grateful to "people" for useful discussions.
 This work was supported by the Netherlands Organization for Scientific Research (NWO/OCW), as part of the Frontiers of Nanoscience program, the Foundation for Fundamental Research on Matter (FOM), and an ERC Starting Grant STATOPINS 638760.

### 2018-11-20 sns_system.py
add some wavefunction figures

@@ -260,8 +260,7 @@ def to_site_ph_spin(syst_pars, wf):
 
 @lru_cache()
 def make_system(L_m, L_x, L_sc_up, L_sc_down, z_x, z_y, a,
-                sawtooth,
-                parallel_curve,
+                shape,
                 transverse_soi,
                 mu_from_bottom_of_spin_orbit_bands,
                 k_x_in_sc,
@@ -272,7 +271,9 @@ def make_system(L_m, L_x, L_sc_up, L_sc_down, z_x, z_y, a,
     ######################
     ## Define templates ##
     ######################
-    assert((sawtooth and parallel_curve) is not True)
+    parallel_curve = sawtooth = False
+    parallel_curve = (shape == 'parallel_curve')
+    sawtooth = (shape == 'sawtooth')
     
     template_barrier, template_normal, template_sc_left, template_sc_right = get_templates(
         a, transverse_soi, mu_from_bottom_of_spin_orbit_bands, k_x_in_sc)

### 2018-11-27 spectrum.py
rename sparse_diag to mumps_eigsh

@@ -23,11 +23,11 @@ def calc_lowest_state(syst_pars_params, syst=None):
         syst = sns_system.make_zigzag_system(**syst_pars)
 
     ham = syst.hamiltonian_submatrix(sparse=True, params=params)
-    e, ev = sparse_diag(ham, 4, 0)
+    e, ev = mumps_eigsh(ham, 4, 0)
     return np.sort(np.abs(e))[::2]
 
 
-def sparse_diag(matrix, k, sigma, **kwargs):
+def mumps_eigsh(matrix, k, sigma, **kwargs):
     """Call sla.eigsh with mumps support.
 
     Please see scipy.sparse.linalg.eigsh for documentation.
@@ -50,7 +50,7 @@ def sparse_diag(matrix, k, sigma, **kwargs):
 
 def calc_spectrum(syst, params, k=20):
     ham = syst.hamiltonian_submatrix(params=params, sparse=True)
-    (energies, wfs) = sparse_diag(ham, k=k, sigma=0)
+    (energies, wfs) = mumps_eigsh(ham, k=k, sigma=0)
     return (energies, wfs)
 
 

### 2018-11-27 spectrum.py
add phase boundary finding algo (doesn't work yet)

@@ -188,3 +188,42 @@ def find_gap_of_lead(lead, params, tol=1e-6):
                 lim[0] = energy
         gap = sum(lim) / 2
     return gap
+
+
+def phase_bounds_operator(lead, params, k_x=0):
+    params['mu'] = 0
+    h_k = lead.hamiltonian_submatrix(params=dict(params, k_x=k_x),
+        sparse=True)
+    sigma_z = sp.csc_matrix(np.array([[1, 0], [0, -1]]))
+    _operator = sp.kron(sp.eye(h_k.shape[0] // 2), sigma_z) @ h_k
+    return _operator
+
+
+def find_phase_bounds(lead, params, k_x=0, num_bands=20):
+    """Find the phase boundaries.
+    Solve an eigenproblem that finds values of chemical potential at which the
+    gap closes at momentum k=0. We are looking for all real solutions of the
+    form H*psi=0 so we solve sigma_0 * tau_z H * psi = mu * psi.
+
+    Parameters
+    -----------
+    lead : kwant.builder.InfiniteSystem object
+        The finalized infinite system.
+    params : dict
+        A dictionary that is used to store Hamiltonian parameters.
+    k_x : float
+        Momentum value, by default set to 0.
+
+    Returns
+    --------
+    chemical_potential : numpy array
+        Twenty values of chemical potential at which a bandgap closes at k=0.
+    """
+    chemical_potentials = phase_bounds_operator(lead, params, k_x)
+
+    if num_bands is None:
+        mus = np.linalg.eigvals(chemical_potentials)
+    else:
+        mus = sla.eigs(chemical_potentials, k=num_bands, sigma=0)[0]
+
+    return np.sort(mus.real), mus

### 2018-11-28 sns_system.py
small changes to the paper figures

@@ -13,7 +13,6 @@ from scipy.optimize import fsolve
 import peierls
 import supercurrent
 import supercurrent_matsubara
-import topology
 from shape import *
 
 

### 2018-11-28 spectrum.py

@@ -191,15 +191,21 @@ def find_gap_of_lead(lead, params, tol=1e-6):
 
 
 def phase_bounds_operator(lead, params, k_x=0):
-    params['mu'] = 0
-    h_k = lead.hamiltonian_submatrix(params=dict(params, k_x=k_x),
+    h_k = lead.hamiltonian_submatrix(params=dict(params, mu=0, k_x=k_x),
         sparse=True)
     sigma_z = sp.csc_matrix(np.array([[1, 0], [0, -1]]))
     _operator = sp.kron(sp.eye(h_k.shape[0] // 2), sigma_z) @ h_k
     return _operator
 
 
-def find_phase_bounds(lead, params, k_x=0, num_bands=20):
+# def phase_bounds_operator(lead, params, k_x=0):
+#     h_k = lead.hamiltonian_submatrix(params=dict(params, mu=0, k_x=k_x),
+#         sparse=True)
+#     sigma_z = np.array([[1, 0], [0, -1]])
+#     _operator = np.kron(np.eye(len(h) // 2), sigma_z) @ h_k
+#     return _operator
+
+def find_phase_bounds(lead, params, k_x=0, num_bands=20, sigma=0):
     """Find the phase boundaries.
     Solve an eigenproblem that finds values of chemical potential at which the
     gap closes at momentum k=0. We are looking for all real solutions of the
@@ -222,8 +228,10 @@ def find_phase_bounds(lead, params, k_x=0, num_bands=20):
     chemical_potentials = phase_bounds_operator(lead, params, k_x)
 
     if num_bands is None:
-        mus = np.linalg.eigvals(chemical_potentials)
+        mus = np.linalg.eigvals(chemical_potentials.todense())
     else:
-        mus = sla.eigs(chemical_potentials, k=num_bands, sigma=0)[0]
+        mus = sla.eigs(chemical_potentials, k=num_bands, sigma=sigma)[0]
 
-    return np.sort(mus.real), mus
+    mus[mus.imag > 1e-14] = np.nan
+
+    return np.sort(mus.real)

### 2018-11-28 spectrum.py
fix CI

@@ -198,13 +198,6 @@ def phase_bounds_operator(lead, params, k_x=0):
     return _operator
 
 
-# def phase_bounds_operator(lead, params, k_x=0):
-#     h_k = lead.hamiltonian_submatrix(params=dict(params, mu=0, k_x=k_x),
-#         sparse=True)
-#     sigma_z = np.array([[1, 0], [0, -1]])
-#     _operator = np.kron(np.eye(len(h) // 2), sigma_z) @ h_k
-#     return _operator
-
 def find_phase_bounds(lead, params, k_x=0, num_bands=20, sigma=0):
     """Find the phase boundaries.
     Solve an eigenproblem that finds values of chemical potential at which the
@@ -232,6 +225,7 @@ def find_phase_bounds(lead, params, k_x=0, num_bands=20, sigma=0):
     else:
         mus = sla.eigs(chemical_potentials, k=num_bands, sigma=sigma)[0]
 
+    inds = np.argsort(mus.real)
     mus[mus.imag > 1e-14] = np.nan
 
-    return np.sort(mus.real)
+    return mus.real[inds]

### 2018-11-28 paper/snakemajoranas.tex
add basic phase diagram figure
add some wavefunction figures
keep figures in place
introduction first attempt written

@@
 \section{Introduction}
+In order to create a stable platform for quantum computing, Majorana bound states are one of the contenders currently being pursued.
+Currently, most efforts to create pairs of Majorana's are based on hybrid NS structures, where a lengthy strip of semiconductor is interfaced with one, or two superconductor structures.
+Assuming the right parameters, the semiconductor becomes topological and Majorana bound states appear at the ends of the segment.
+In practice however, multiple problems arise making even the observation, let alone the manipulation of Majorana's difficult.
+
+We claim that one of the problems lying in the way of a stable system, is the appearance of a soft gap; the gap is greatly reduced for states with momentum directed along the length of the strip.
+We claim that this is due to, from a semiclassical perspective, long paths through the semiconductor without interruption by the superconductor.
+We show that introducing a zigzag or snake like geometry for the semiconductor removes these long trajectories and avoids the appearance of a soft gap.
 
@@
 
-\begin{figure}
+\begin{figure}[!htb]
 % \includegraphics[width=0.95\columnwidth]{figures/SOME_FIGURE}
@@
 
-\begin{figure}
+\begin{figure}[!htb]
 \includegraphics[width=0.95\columnwidth]{figures/bandstructures}
@@
 
-\begin{figure}
-% \includegraphics[width=0.95\columnwidth]{figures/SOME_FIGURE}
+\begin{figure}[!htb]
+\includegraphics[width=0.95\columnwidth]{figures/phasediagrams}
 \caption{Phase diagrams of a straight system (a, b) and zigzag system (c, d), where (a, c) are $E(\mu, B)$ and (b, d) are $E(\phi, B)$.
@@
 
-\begin{figure}
-% \includegraphics[width=0.95\columnwidth]{figures/SOME_FIGURE}
+\begin{figure}[!htb]
+\includegraphics[width=0.95\columnwidth]{figures/wavefunctions}
 \caption{Wavefunctions for different sizes and geometries.

### 2018-11-28 spectrum.py
discard the correct eigenvalues

@@ -226,6 +226,6 @@ def find_phase_bounds(lead, params, k_x=0, num_bands=20, sigma=0):
         mus = sla.eigs(chemical_potentials, k=num_bands, sigma=sigma)[0]
 
     inds = np.argsort(mus.real)
-    mus[mus.imag > 1e-14] = np.nan
+    mus[abs(mus.imag) > 1e-14] = np.nan
 
     return mus.real[inds]

### 2018-11-28 paper/snakemajoranas.tex
Add formulas for analytics to paper

@@
 
-\comment{Majoranas are mostly made in hybrid NS structures.}
-\comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
-\comment{The gap is small because of long trajectories.}
-\comment{We show that zigzag geometry solves this problem in a controllable manner.}
-
 \begin{figure}[!htb]
@@
 \section{Analytical estimate}
+\begin{align}
+    &S = 
+    &\left(
+    \begin{array}{cc}
+    r & t\\
+    t & e^{-2 i q W} r\\
+    \end{array}
+    \right) 
+    \\
+    &r = &\left(
+    \begin{array}{rr}
+    e^{i \nu_{\arg}}\left(\omega_+ - \omega_-\right) & (\omega _+ + \omega _-)\\
+    -(\omega _+ + \omega _-) & - e^{-i \nu _{\arg }} \left(\omega _+ - \omega _-\right)\\
+    \end{array}
+    \right)
+    \\
+    &t = e^{-i q W} &\left(
+    \begin{array}{rr}
+    e^{i \nu_{\arg}}\left(\beta_+ - \beta_-\right) & (\beta_+ + \beta_-)\\
+    -(\beta_+ + \beta_-) & - e^{-i \nu _{\arg }} \left(\beta_+ - \beta_-\right)\\
+    \end{array}
+    \right)
+\end{align}
 
-Quasi classical short junction calculation explaination.
-Include all, later move stuff to the appendix if necessary.
-
+\begin{align}
+    \omega_\pm = \frac{1}{4} \left(\gamma _{\pm}+\delta _{\pm}\right)
+    \\
+    \beta_\pm = \frac{1}{4} \left(\gamma _{\pm}-\delta _{\pm}\right)
+\end{align}
+\begin{align}
+    \gamma_\pm = \frac{q+i k_{\pm} \tan \left(\frac{W k_{\pm}}{2}\right)}{q-i k_{\pm} \tan \left(\frac{W k_{\pm}}{2}\right)} \\
+    \delta_\pm = \frac{q-i k_{\pm} \cot \left(\frac{W k_{\pm}}{2}\right)}{q+i k_{\pm} \cot \left(\frac{W k_{\pm}}{2}\right)}
+\end{align}
 \section{Numerical bandstructures}

### 2018-11-28 paper/snakemajoranas.tex
Change form of formulas to make more compact

--- 2018-11-28 paper/snakemajoranas.tex
@@
 \section{Analytical estimate}
+\begin{align}
+    &S = 
+    &\left(
+    \begin{array}{cc}
+    \beta_+ & e^{-i q W} \beta_-\\
+    e^{-i q W} \beta_- & e^{-2 i q W} \beta_+\\
+    \end{array}
+    \right) 
+    \\
+    &\beta_\pm = &\left(
+    \begin{array}{rr}
+    e^{i \nu_{\arg}}\left(\omega^\pm_1 - \omega^\pm_2\right) & (\omega^\pm _1 + \omega^\pm _2)\\
+    -(\omega^\pm _1 + \omega^\pm _2) & - e^{-i \nu _{\arg }} \left(\omega^\pm _1 - \omega^\pm _2\right)\\
+    \end{array}
+    \right)\\
+    &\omega^\pm_j = \frac{1}{4} \left(\gamma _{j} \pm \delta _{j}\right)
+\end{align}
 
-Quasi classical short junction calculation explaination.
-Include all, later move stuff to the appendix if necessary.
-
+\begin{align}
+    \gamma_j = \frac{q+i k_{j} \tan \left(\frac{W k_{j}}{2}\right)}{q-i k_{j} \tan \left(\frac{W k_{j}}{2}\right)} \\
+    \delta_j = \frac{q-i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}{q+i k_{j} \cot \left(\frac{W k_{\pm}}{2}\right)}
+\end{align}
 \section{Numerical bandstructures}

### 2018-11-28 paper/snakemajoranas.tex
Temporarily change yml because notebook is screwing up
commented out plot to prevent error
added some more formulas and reverted the yml

--- 2018-11-28 paper/snakemajoranas.tex
@@
 \section{Analytical estimate}
+\begin{align}
+    S &= \left(
+    \begin{array}{rr}
+    r_{ll}&t_{rl}\\
+    t_{lr}&r_{rr}\\
+    \end{array}
+    \right) =
+    \left(
+    \begin{array}{rr}
+    \beta_+ & e^{-i q W} \beta_-\\
+    e^{-i q W} \beta_- & e^{-2 i q W} \beta_+\\
+    \end{array}
+    \right) 
+    \\
+    \beta_\pm &= \left(
+    \begin{array}{rr}
+    e^{i \nu_{\arg}}\left(\omega^\pm_1 - \omega^\pm_2\right) & (\omega^\pm _1 + \omega^\pm _2)\\
+    -(\omega^\pm _1 + \omega^\pm _2) & e^{-i \nu _{\arg }} \left(\omega^\pm _2 - \omega^\pm _1\right)\\
+    \end{array}
+    \right)\\
+    \omega^\pm_j &= \frac{1}{4} \left(\gamma _{j} \pm \delta _{j}\right)
+\end{align}
 
-Quasi classical short junction calculation explaination.
-Include all, later move stuff to the appendix if necessary.
+\begin{align}
+    \gamma_j &= \frac{q+i k_{j} \tan \left(\frac{W k_{j}}{2}\right)}{q-i k_{j} \tan \left(\frac{W k_{j}}{2}\right)} \\
+    \delta_j &= \frac{q-i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}{q+i k_{j} \cot \left(\frac{W k_{\pm}}{2}\right)}\\
+    e^{i \nu_{\arg}} &= \frac{E_\text{z} e^{i \theta }-i \alpha  k_x}{\sqrt{E_\text{z}^2+\alpha  k_x \left(\alpha  k_x-2 E_\text{z} \sin (\theta )\right)}}
+\end{align}
 
+\begin{align}
+    q &= \sqrt{\frac{2 m_\ast}{\hbar ^2}\left(\mu_s + E\right) - k_x^2}\\
+    k_1 &= \sqrt{\frac{2 m_\ast}{\hbar^2} \left(\mu_n+ E-\sqrt{\text{Ez}^2-2 \alpha  \text{Ez} \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 }\\
+    k_2 &= \sqrt{\frac{2 m_\ast}{\hbar^2} \left(\mu_n+ E+\sqrt{\text{Ez}^2-2 \alpha  \text{Ez} \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 }
+\end{align}
 \section{Numerical bandstructures}
@@
 \begin{figure}[!htb]
-\includegraphics[width=0.95\columnwidth]{figures/wavefunctions}
+% \includegraphics[width=0.95\columnwidth]{figures/wavefunctions}
 \caption{Wavefunctions for different sizes and geometries.

### 2018-11-29 paper/snakemajoranas.tex
Descreased font size a bit
Added comment decorations for sections
Added some introduction to the analytics

@@
 
+%%██████████████████████████████████████████████████████████████████████████
+%%██ Introduction
+%%██████████████████████████████████████████████████████████████████████████
 \section{Introduction}
@@
 
+%%██████████████████████████████████████████████████████████████████████████
+%%██ Analytical estimate
+%%██████████████████████████████████████████████████████████████████████████
 \section{Analytical estimate}
+We claim that the hardening of the gap is due to the cutoff of long trajectories. 
+In order to verify this is the case, we take a ribbon SNS junction with magnetic field rotated such that it corresponds to a rising section of the zigzag.
+We then compute the scattering matrix to find the Andreev bound spectrum as a function of the momentum along the strip direction.
+We cut off the spectrum at the momentum corresponding to the proposed cutoff in the zigzag, and compare it to the numerically obtained gap for a true zigzag system.
+
 \begin{align}
@@
     \gamma_j &= \frac{q+i k_{j} \tan \left(\frac{W k_{j}}{2}\right)}{q-i k_{j} \tan \left(\frac{W k_{j}}{2}\right)} \\
-    \delta_j &= \frac{q-i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}{q+i k_{j} \cot \left(\frac{W k_{\pm}}{2}\right)}\\
+    \delta_j &= \frac{q-i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}{q+i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}\\
     e^{i \nu_{\arg}} &= \frac{E_\text{z} e^{i \theta }-i \alpha  k_x}{\sqrt{E_\text{z}^2+\alpha  k_x \left(\alpha  k_x-2 E_\text{z} \sin (\theta )\right)}}
 \end{align}
+\begin{footnotesize}
+\begin{align}
+    q &= \left[ \frac{2 m_\ast}{\hbar ^2}\left(\mu_s\right) - k_x^2 \right]^\frac{1}{2}\\
+    k_1 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n-\sqrt{\text{Ez}^2-2 \alpha  \text{Ez} \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}\\
+    k_2 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n+\sqrt{\text{Ez}^2-2 \alpha  \text{Ez} \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}
+\end{align}
+\end{footnotesize}
 
-\begin{align}
-    q &= \sqrt{\frac{2 m_\ast}{\hbar ^2}\left(\mu_s + E\right) - k_x^2}\\
-    k_1 &= \sqrt{\frac{2 m_\ast}{\hbar^2} \left(\mu_n+ E-\sqrt{\text{Ez}^2-2 \alpha  \text{Ez} \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 }\\
-    k_2 &= \sqrt{\frac{2 m_\ast}{\hbar^2} \left(\mu_n+ E+\sqrt{\text{Ez}^2-2 \alpha  \text{Ez} \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 }
-\end{align}
+%%██████████████████████████████████████████████████████████████████████████
+%%██ Numerical bandstructures
+%%██████████████████████████████████████████████████████████████████████████
 \section{Numerical bandstructures}
@@
 
+%%██████████████████████████████████████████████████████████████████████████
+%%██ Calculating the bandstuctures
+%%██████████████████████████████████████████████████████████████████████████
 \section{Calculating the bandstuctures.}
 
+%%██████████████████████████████████████████████████████████████████████████
+%%██ Calculating the topological phase diagram
+%%██████████████████████████████████████████████████████████████████████████
 \section{Calculating the topological phase diagram.}
@@
 
+%%██████████████████████████████████████████████████████████████████████████
+%%██ Localization lengths and shape effect
+%%██████████████████████████████████████████████████████████████████████████
 \section{Localization lengths and shape effect}
@@
 
+%%██████████████████████████████████████████████████████████████████████████
+%%██ Discussion and Conclusions
+%%██████████████████████████████████████████████████████████████████████████
 \section{Discussion and Conclusions}

### 2018-11-30 paper/snakemajoranas.tex
Add tikz file for system
Uncomment wavefunction figure
Added hamiltonian
fix notation
Add small piece of physical picture text
Added a bunch of text to the manuscript

@@
 \DeclareMathOperator{\re}{Re}
+\newcommand{\kx}{k_x}
+\newcommand{\ky}{k_y}
+\newcommand{\meff}{m_\text{eff}}
 
@@
 
+%%██████████████████████████████████████████████████████████████████████████
+%%██ Physical picture
+%%██████████████████████████████████████████████████████████████████████████
+\section{Physical picture}
+We consider a system [\ref{fig:setup}] consisting of a two dimensional strip of semiconductor, with superconductors adjacent on both sides.
+A magnetic field pointed along the x direction is applied.
+We model the system with a BdG hamiltonian; the normal part also has Rashba spin-orbit coupling and a Zeeman field, and the superconductors differ in superconducting phase.
+For the zigzag geometry, we take a sawtooth like pattern wher $z_x$ is periodicity, $z_y$ the amplitude and W the width of the junction.
+\begin{small}
+\begin{align}
+    H = \left(\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right)\tau_z+
+        E_\text{z} \sigma_z+
+        \alpha \left( \ky \sigma_x - \kx \sigma_y \right) \tau_z +
+        \Delta \tau_y
+\end{align}
+\label{eq:hamiltonian}
+\end{small}
+
 \begin{figure}[!htb]
-% \includegraphics[width=0.95\columnwidth]{figures/SOME_FIGURE}
+\includegraphics[width=0.95\columnwidth]{figures/systemPicture.pdf}
 \caption{Setups. Figure of a straight and zigzag system, including trajectories.
@@
     q &= \left[ \frac{2 m_\ast}{\hbar ^2}\left(\mu_s\right) - k_x^2 \right]^\frac{1}{2}\\
-    k_1 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n-\sqrt{\text{Ez}^2-2 \alpha  \text{Ez} \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}\\
-    k_2 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n+\sqrt{\text{Ez}^2-2 \alpha  \text{Ez} \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}
+    k_1 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n-\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}\\
+    k_2 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n+\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}
 \end{align}
@@
 \section{Calculating the bandstuctures.}
+In figure \ref{fig:bandstuctures}, We calculate the bandstructure for a zigzag system with varying amplitude using Kwant.
+As the zigzag introduces super cell, we see a folded bandstructure.
+For comparisons sake, we take the same cell size for the ribbon structure so the bandstructure is folded in the same way.
+The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size is increased tenfolds.
+We claim this effect is due to the fact that the modes where the gap is smallest, when the momentum is almost completely focused along the strip ($k_x=k_F$), are cut off by the zigzag geometry.
+Additionally in the presence of normal reflection, due to the availability of NS interfaces at a wide range of slopes, the reflected part will eventually ``find'' a surface with which it is perpendicular to.
+Also apparent is the reduction of group velocity; the slope of the bands is greatly reduced. This has an effect on the Majorana coherence length, as described later on in the manuscript.
 
@@
 \section{Calculating the topological phase diagram.}
+In order to create a topological phase diagram we would normally compute the topolical invariant(pfaffian).
+For a ribbon this is possible, but computing the invariant of the supercell is too computationally expensive.
+Using a generalized eigenvalue problem also proved unsuccesful due to numerical errors, so we resort to simply calculating the gap and noting the gap closings.
 
+Similar to what is described in Pientka et. al [\cite{pientka2017topological}], we see that the ribbon topology has a diamond like structure as a function of phase and Zeeman field.
+We also see some additional gap closings which are due to the BDI symmetry class, creating quite an unstable region.
+As expected, for the zigzag system, the magnitude of the gap is significantly improved, whilst maintaining the diamond like shape.
+As the zigzag shape destroys the additional symmetry, moving it to class D, we see a more clean toplogical region.
 \comment{We use a generalized eigenvalue problem to find all phase boundaries at once.}
@@
 \section{Localization lengths and shape effect}
-
+Using the tight-binding package kwant, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinosoids.
+We then superimpose them onto the geometry, as in figure \ref{fig:wavefunctions}.
+For the ribbon system, we see that the Majorana coherence length is relatively large, not showing the decolalized nature sought after.
+All of the zigzag type geometries however show greatly reduced coherence length.\tabularnewline
+This can be explained by two effects: the increase in topological gap, but also the beforementioned reduction of the group velocity.
 \comment{We find the Majorana lengths by calculating the slowest decaying mode.}
@@
 \begin{figure}[!htb]
-% \includegraphics[width=0.95\columnwidth]{figures/wavefunctions}
+\includegraphics[width=0.95\columnwidth]{figures/wavefunctions}
 \caption{Wavefunctions for different sizes and geometries.

### 2018-12-04 paper/snakemajoranas.tex
Removed parentheses from mu
Added some topology talk

@@
 A magnetic field pointed along the x direction is applied.
-We model the system with a BdG hamiltonian; the normal part also has Rashba spin-orbit coupling and a Zeeman field, and the superconductors differ in superconducting phase.
-For the zigzag geometry, we take a sawtooth like pattern wher $z_x$ is periodicity, $z_y$ the amplitude and W the width of the junction.
+We model the system with a BdG Hamiltonian[\ref{eq:hamiltonian}]; the normal part also has Rashba spin-orbit coupling and a Zeeman field, and the superconductors differ in superconducting phase.
+For the zigzag geometry, we take a sawtooth like pattern wher $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
+We know from [\cite{pientka2017topological}] that the non-zigzag system is in class BDI.
+Using the software package qsymm, we evaluate the symmetry class of the system to be D.
+
 \begin{small}
@@
 \begin{align}
-    q &= \left[ \frac{2 m_\ast}{\hbar ^2}\left(\mu_s\right) - k_x^2 \right]^\frac{1}{2}\\
+    q &= \left[ \frac{2 m_\ast}{\hbar ^2}\mu_s - k_x^2 \right]^\frac{1}{2}\\
     k_1 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n-\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}\\

### 2018-12-04 paper/snakemajoranas.tex
add explaination on how to find the spectrum from the S-matrix

@@
 \begin{align}
+\label{eq:smatrix}
     S &= \left(
@@
 \end{footnotesize}
+
+In order to get the spectrum from the S-matrix [Eq.~\eqref{eq:smatrix}] we use the main result from Ref.~\onlinecite{beenakker1991universal} and start with a determinantal equation for the bound state energies in a SNS-junction:
+
+\begin{equation}
+\det\left[1+\alpha^{2}\left(E\right)r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)\right]=0
+\end{equation}
+
+We rewrite this as a characteristic polynomial problem $\det\left[A-\lambda I\right]=0$, as
+
+\begin{equation}
+\det\left[r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)-\frac{-1}{\alpha^{2}\left(E\right)}I\right]=0
+\end{equation}
+
+with
+\begin{equation}
+\lambda=-\frac{1}{\alpha^{2}\left(E\right)},\;A=r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right).
+\end{equation}
+
+Where $\lambda$ are the eigenvalues of $A$.
+Inverting $\alpha\left(E\right)\equiv\exp\left(-i\arccos\left(E/\Delta\right)\right)$ gives $\frac{E}{\Delta}=\frac{\alpha^{2}+1}{2\alpha}=\frac{1}{2}\left(\alpha+\alpha^{-1}\right)$, and since $\alpha$ is unitary and only defined in the postitive imagionary plane, $E_{i}=\textrm{real}\left(\pm\sqrt{1/\lambda_{i}}\right)$.
+% TODO: add the mathematical notation for taking the lambda.imag > 0.
+Using this result and Eq.~\eqref{eq:smatrix}, we numerically find the Andreev spectrum.
 

### 2018-12-04 paper/snakemajoranas.tex
improve spectrum algo text

@@
 In order to verify this is the case, we take a ribbon SNS junction with magnetic field rotated such that it corresponds to a rising section of the zigzag.
-We then compute the scattering matrix to find the Andreev bound spectrum as a function of the momentum along the strip direction.
+We then compute the scattering matrix [Eq.~\eqref{eq:smatrix}] to find the Andreev bound spectrum as a function of the momentum along the strip direction.
 We cut off the spectrum at the momentum corresponding to the proposed cutoff in the zigzag, and compare it to the numerically obtained gap for a true zigzag system.
@@
 
-Where $\lambda$ are the eigenvalues of $A$.
-Inverting $\alpha\left(E\right)\equiv\exp\left(-i\arccos\left(E/\Delta\right)\right)$ gives $\frac{E}{\Delta}=\frac{\alpha^{2}+1}{2\alpha}=\frac{1}{2}\left(\alpha+\alpha^{-1}\right)$, and since $\alpha$ is unitary and only defined in the postitive imagionary plane, $E_{i}=\textrm{real}\left(\pm\sqrt{1/\lambda_{i}}\right)$.
-% TODO: add the mathematical notation for taking the lambda.imag > 0.
+Where $\lambda_i$ are the eigenvalues of $A$.
+Inverting $\alpha\left(E\right)\equiv\exp\left(-i\arccos\left(E/\Delta\right)\right)$ gives $\frac{E}{\Delta}=\frac{\alpha^{2}+1}{2\alpha}=\frac{1}{2}\left(\alpha+\alpha^{-1}\right)=\textrm{Re}(\alpha)$, where the last equality holds because $\alpha$ is unitary.
+Then, since $\alpha$ is only defined in the postitive imagionary plane, the energies are $\frac{E_{i}}{\Delta}=\textrm{Re}\left(\sqrt{-1/\lambda_{i}}\right)$ where we take the root which has a postitive imagionary part.
 Using this result and Eq.~\eqref{eq:smatrix}, we numerically find the Andreev spectrum.

### 2018-12-04 paper/snakemajoranas.tex
fix spelling

@@
 Inverting $\alpha\left(E\right)\equiv\exp\left(-i\arccos\left(E/\Delta\right)\right)$ gives $\frac{E}{\Delta}=\frac{\alpha^{2}+1}{2\alpha}=\frac{1}{2}\left(\alpha+\alpha^{-1}\right)=\textrm{Re}(\alpha)$, where the last equality holds because $\alpha$ is unitary.
-Then, since $\alpha$ is only defined in the postitive imagionary plane, the energies are $\frac{E_{i}}{\Delta}=\textrm{Re}\left(\sqrt{-1/\lambda_{i}}\right)$ where we take the root which has a postitive imagionary part.
+Then, since $\alpha$ is only defined in the positive imaginary plane, the energies are $\frac{E_{i}}{\Delta}=\textrm{Re}\left(\sqrt{-1/\lambda_{i}}\right)$ where we take the root which has a positive imaginary part.
 Using this result and Eq.~\eqref{eq:smatrix}, we numerically find the Andreev spectrum.

### 2018-12-05 paper/snakemajoranas.tex
put sentences on different lines

@@
 Where $\lambda_i$ are the eigenvalues of $A$.
-Inverting $\alpha\left(E\right)\equiv\exp\left(-i\arccos\left(E/\Delta\right)\right)$ gives $\frac{E}{\Delta}=\frac{\alpha^{2}+1}{2\alpha}=\frac{1}{2}\left(\alpha+\alpha^{-1}\right)=\textrm{Re}(\alpha)$, where the last equality holds because $\alpha$ is unitary.
+Inverting $\alpha\left(E\right)\equiv\exp\left(-i\arccos\left(E/\Delta\right)\right)$ yields $\frac{E}{\Delta}=\frac{\alpha^{2}+1}{2\alpha}=\frac{1}{2}\left(\alpha+\alpha^{-1}\right)=\textrm{Re}(\alpha)$, where the last equality holds because $\alpha$ is unitary.
 Then, since $\alpha$ is only defined in the positive imaginary plane, the energies are $\frac{E_{i}}{\Delta}=\textrm{Re}\left(\sqrt{-1/\lambda_{i}}\right)$ where we take the root which has a positive imaginary part.
@@
 Additionally in the presence of normal reflection, due to the availability of NS interfaces at a wide range of slopes, the reflected part will eventually ``find'' a surface with which it is perpendicular to.
-Also apparent is the reduction of group velocity; the slope of the bands is greatly reduced. This has an effect on the Majorana coherence length, as described later on in the manuscript.
+Also apparent is the reduction of group velocity; the slope of the bands is greatly reduced.
+This has an effect on the Majorana coherence length, as described later on in the manuscript.
 

### 2018-12-05 paper/snakemajoranas.tex
small changes to the text and adding citations

@@
 
-\title{Increasing the topological gap by an order of magnitude through the geomerty for Majorana SNS junctions.}
+\title{Increasing the topological gap by an order of magnitude through the geometry for Majorana SNS junctions.}
 
@@
 We do this by introducing a zigzag geometry.
-This works because the maximum trajactory length is cut-off due to the geomerty and therefore the minimal energy gap is given by a simple formula, which we also verify using numerics.
-In addition to having a large minimum energy gap, the abscence of long length trajectories means that the localization length is very short as well.
+This works because the maximum trajectory length is cut-off due to the geometry and therefore the minimal energy gap is given by a simple formula, which we also verify using numerics.
+In addition to having a large minimum energy gap, the absence of long length trajectories means that the localization length is very short as well.
 \end{abstract}
@@
 \section{Introduction}
-In order to create a stable platform for quantum computing, Majorana bound states are one of the contenders currently being pursued.
-Currently, most efforts to create pairs of Majorana's are based on hybrid NS structures, where a lengthy strip of semiconductor is interfaced with one, or two superconductor structures.
-Assuming the right parameters, the semiconductor becomes topological and Majorana bound states appear at the ends of the segment.
-In practice however, multiple problems arise making even the observation, let alone the manipulation of Majorana's difficult.
+Majorana bound states (MBSs) are a promising candidate to form the basis of a stable platform for topological quantum computing.
+The current experimental effort is focused on creating pairs of MBSs in hybrid normal-superconductor (NS) structures, where a lengthy strip (or wire) of semiconductor is interfaced with a \cite{lutchyn_majorana_2010,oreg_helical_2010} superconductor.
+Within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple wire), the semiconductor becomes topological and MBSs appear at the ends of the segment.
+Recently, a system with a slight modification has been proposed\cite{pientka2017topological}, where instead of having one superconductor, there are two superconductors, creating a superconductors-normal-superconductor (SNS) junction.
+This adds an extra knob to adjust, the superconducting phase difference $\phi$, and this should make it easier to tune the system into the topological phase.
+In practice, multiple problems arise making even the observation, let alone the manipulation of Majoranas difficult.
 
 We claim that one of the problems lying in the way of a stable system, is the appearance of a soft gap; the gap is greatly reduced for states with momentum directed along the length of the strip.
-We claim that this is due to, from a semiclassical perspective, long paths through the semiconductor without interruption by the superconductor.
+We claim that this is due to, from a semi classical perspective, long paths through the semiconductor without interruption by the superconductor.
 We show that introducing a zigzag or snake like geometry for the semiconductor removes these long trajectories and avoids the appearance of a soft gap.
@@
 We model the system with a BdG Hamiltonian[\ref{eq:hamiltonian}]; the normal part also has Rashba spin-orbit coupling and a Zeeman field, and the superconductors differ in superconducting phase.
-For the zigzag geometry, we take a sawtooth like pattern wher $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
+For the zigzag geometry, we take a sawtooth like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
 We know from [\cite{pientka2017topological}] that the non-zigzag system is in class BDI.
-Using the software package qsymm, we evaluate the symmetry class of the system to be D.
+Using the software package Qsymm\cite{varjas2018qsymm}, we evaluate the symmetry class of the system to be D.
 
@@
 \section{Calculating the topological phase diagram.}
-In order to create a topological phase diagram we would normally compute the topolical invariant(pfaffian).
+In order to create a topological phase diagram we would normally compute the topological invariant(pfaffian).
 For a ribbon this is possible, but computing the invariant of the supercell is too computationally expensive.
-Using a generalized eigenvalue problem also proved unsuccesful due to numerical errors, so we resort to simply calculating the gap and noting the gap closings.
+Using a generalized eigenvalue problem also proved unsuccessful due to numerical errors, so we resort to simply calculating the gap and noting the gap closings.
 
@@
 As expected, for the zigzag system, the magnitude of the gap is significantly improved, whilst maintaining the diamond like shape.
-As the zigzag shape destroys the additional symmetry, moving it to class D, we see a more clean toplogical region.
+As the zigzag shape destroys the additional symmetry, moving it to class D, we see a more clean topological region.
 \comment{We use a generalized eigenvalue problem to find all phase boundaries at once.}
@@
 \section{Localization lengths and shape effect}
-Using the tight-binding package kwant, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinosoids.
+Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinusoids.
 We then superimpose them onto the geometry, as in figure \ref{fig:wavefunctions}.
@@
 \caption{Wavefunctions for different sizes and geometries.
-With (a) a straight system, (b) a zigzag sytem, (c) a system where the normal region is defined by two parallel sine waves, and (d) a system with the Laeven shape.
-Inside the figure we indicate the Majorana lenght (or coherence length) $\xi$ and the topological energy gap $E_\textrm{gap}.$
+With (a) a straight system, (b) a zigzag system, (c) a system where the normal region is defined by two parallel sine waves, and (d) a system with the Laeven shape.
+Inside the figure we indicate the Majorana length (or coherence length) $\xi$ and the topological energy gap $E_\textrm{gap}.$
 We observe that $\xi$ for (a) is orders of magnitude longer and $E_\textrm{gap}$ orders of magnitude smaller than for (b, c, d), meaning that the details of the geometry do not matter.

### 2018-12-05 paper/snakemajoranas.tex
use onlinecite

@@
 \section{Physical picture}
-We consider a system [\ref{fig:setup}] consisting of a two dimensional strip of semiconductor, with superconductors adjacent on both sides.
+We consider a system (Fig.~\ref{fig:setup}) consisting of a two dimensional strip of semiconductor, with superconductors adjacent on both sides.
 A magnetic field pointed along the x direction is applied.
-We model the system with a BdG Hamiltonian[\ref{eq:hamiltonian}]; the normal part also has Rashba spin-orbit coupling and a Zeeman field, and the superconductors differ in superconducting phase.
+We model the system with a BdG Hamiltonian Eq.~\eqref{eq:hamiltonian}; the normal part also has Rashba spin-orbit coupling and a Zeeman field, and the superconductors differ in superconducting phase.
 For the zigzag geometry, we take a sawtooth like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
-We know from [\cite{pientka2017topological}] that the non-zigzag system is in class BDI.
+We know from \onlinecite{pientka2017topological} that the non-zigzag system is in class BDI.
 Using the software package Qsymm\cite{varjas2018qsymm}, we evaluate the symmetry class of the system to be D.
@@
 In order to verify this is the case, we take a ribbon SNS junction with magnetic field rotated such that it corresponds to a rising section of the zigzag.
-We then compute the scattering matrix [Eq.~\eqref{eq:smatrix}] to find the Andreev bound spectrum as a function of the momentum along the strip direction.
+We then compute the scattering matrix Eq.~\eqref{eq:smatrix} to find the Andreev bound spectrum as a function of the momentum along the strip direction.
 We cut off the spectrum at the momentum corresponding to the proposed cutoff in the zigzag, and compare it to the numerically obtained gap for a true zigzag system.

### 2018-12-10 paper/snakemajoranas.tex
merged introduction changes

@@
 Majorana bound states (MBSs) are a promising candidate to form the basis of a stable platform for topological quantum computing.
+\comment{Majoranas are mostly made in hybrid NS structures.}
 The current experimental effort is focused on creating pairs of MBSs in hybrid normal-superconductor (NS) structures, where a lengthy strip (or wire) of semiconductor is interfaced with a \cite{lutchyn_majorana_2010,oreg_helical_2010} superconductor.
@@
 
+\comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
 We claim that one of the problems lying in the way of a stable system, is the appearance of a soft gap; the gap is greatly reduced for states with momentum directed along the length of the strip.
+\comment{The gap is small because of long trajectories.}
 We claim that this is due to, from a semi classical perspective, long paths through the semiconductor without interruption by the superconductor.
+\comment{We show that zigzag geometry solves this problem in a controllable manner.}
 We show that introducing a zigzag or snake like geometry for the semiconductor removes these long trajectories and avoids the appearance of a soft gap.
@@
     H = \left(\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right)\tau_z+
-        E_\text{z} \sigma_z+
+        E_\text{z} \sigma_x+
         \alpha \left( \ky \sigma_x - \kx \sigma_y \right) \tau_z +

### 2018-12-11 paper/snakemajoranas.tex
update paragraph structure (unfinished)

@@
 
+\comment{The gap is small because of long trajectories.}
+From a semiclassical perspective, long paths through the semiconductor without interruption by the superconductor.
+
 \comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
 We claim that one of the problems lying in the way of a stable system, is the appearance of a soft gap; the gap is greatly reduced for states with momentum directed along the length of the strip.
-\comment{The gap is small because of long trajectories.}
-We claim that this is due to, from a semi classical perspective, long paths through the semiconductor without interruption by the superconductor.
-\comment{We show that zigzag geometry solves this problem in a controllable manner.}
+
+\comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
 We show that introducing a zigzag or snake like geometry for the semiconductor removes these long trajectories and avoids the appearance of a soft gap.
@@
 %%██████████████████████████████████████████████████████████████████████████
+%%██ Numerical bandstructures
+%%██████████████████████████████████████████████████████████████████████████
+\section{Numerical bandstructures}
+
+\comment{We consider a 2D SNS junction with a Rashba-BdG Hamiltonian and zigzag geometry.}
+
+\comment{We discretize the model and simulate it with Kwant.}
+
+%%██████████████████████████████████████████████████████████████████████████
+%%██ Calculating the bandstuctures
+%%██████████████████████████████████████████████████████████████████████████
+\section{Calculating the bandstuctures.}
+In figure \ref{fig:bandstuctures}, We calculate the bandstructure for a zigzag system with varying amplitude using Kwant.
+As the zigzag introduces super cell, we see a folded bandstructure.
+For comparisons sake, we take the same cell size for the ribbon structure so the bandstructure is folded in the same way.
+The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size is increased tenfolds.
+We claim this effect is due to the fact that the modes where the gap is smallest, when the momentum is almost completely focused along the strip ($k_x=k_F$), are cut off by the zigzag geometry.
+Additionally in the presence of normal reflection, due to the availability of NS interfaces at a wide range of slopes, the reflected part will eventually ``find'' a surface with which it is perpendicular to.
+Also apparent is the reduction of group velocity; the slope of the bands is greatly reduced.
+This has an effect on the Majorana coherence length, as described later on in the manuscript.
+
+%%██████████████████████████████████████████████████████████████████████████
+%%██ Calculating the topological phase diagram
+%%██████████████████████████████████████████████████████████████████████████
+\section{Calculating the topological phase diagram.}
+In order to create a topological phase diagram we would normally compute the topological invariant(pfaffian).
+For a ribbon this is possible, but computing the invariant of the supercell is too computationally expensive.
+Using a generalized eigenvalue problem also proved unsuccessful due to numerical errors, so we resort to simply calculating the gap and noting the gap closings.
+
+Similar to what is described in Pientka et. al [\cite{pientka2017topological}], we see that the ribbon topology has a diamond like structure as a function of phase and Zeeman field.
+We also see some additional gap closings which are due to the BDI symmetry class, creating quite an unstable region.
+As expected, for the zigzag system, the magnitude of the gap is significantly improved, whilst maintaining the diamond like shape.
+As the zigzag shape destroys the additional symmetry, moving it to class D, we see a more clean topological region.
+\comment{We use a generalized eigenvalue problem to find all phase boundaries at once.}
+
+\comment{We calculate the gap by finding the minimum energy in the spectrum.}
+
+\begin{figure}[!htb]
+\includegraphics[width=0.95\columnwidth]{figures/bandstructures}
+\caption{Figure of the bandstuctures.
+Where the lines are (blue) $\phi=0$, $B=0$ and (red) $\phi=\pi$, $B \ne 0$.
+and the subplots (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W$ is the junction width.
+We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
+\label{fig:bandstuctures}}
+\end{figure}
+
+\begin{figure}[!htb]
+\includegraphics[width=0.95\columnwidth]{figures/phasediagrams}
+\caption{Phase diagrams of a straight system (a, b) and zigzag system (c, d), where (a, c) are $E(\mu, B)$ and (b, d) are $E(\phi, B)$.
+We use a generalized eigenvalue problem to find all phase boundaries at once and find the minimal energy gap by finding the minimum in the spectrum: $\min{E(k)}$.
+\label{fig:phasediagrams}}
+\end{figure}
+
+%%██████████████████████████████████████████████████████████████████████████
 %%██ Analytical estimate
 %%██████████████████████████████████████████████████████████████████████████
-\section{Analytical estimate}
+\section{Analytical estimate of the band gap}
+
+\comment{To compute the effect of cutoff consider a single segment of the zigzag and obtain the spectrum analytically (this allows to use translation invariance).}
+
+\comment{We use a short junction approximation and neglect transverse SO.}
+
+\comment{The lowest energy at $|k| < k_\textrm{cutoff}$ sets the band gap.}
+
 We claim that the hardening of the gap is due to the cutoff of long trajectories.
@@
 %%██████████████████████████████████████████████████████████████████████████
-%%██ Numerical bandstructures
-%%██████████████████████████████████████████████████████████████████████████
-\section{Numerical bandstructures}
-
-\comment{We consider a 2D SNS junction with a Rashba-BdG Hamiltonian.}
-
-\comment{We discretize the model and simulate it with Kwant.}
-
-%%██████████████████████████████████████████████████████████████████████████
-%%██ Calculating the bandstuctures
-%%██████████████████████████████████████████████████████████████████████████
-\section{Calculating the bandstuctures.}
-In figure \ref{fig:bandstuctures}, We calculate the bandstructure for a zigzag system with varying amplitude using Kwant.
-As the zigzag introduces super cell, we see a folded bandstructure.
-For comparisons sake, we take the same cell size for the ribbon structure so the bandstructure is folded in the same way.
-The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size is increased tenfolds.
-We claim this effect is due to the fact that the modes where the gap is smallest, when the momentum is almost completely focused along the strip ($k_x=k_F$), are cut off by the zigzag geometry.
-Additionally in the presence of normal reflection, due to the availability of NS interfaces at a wide range of slopes, the reflected part will eventually ``find'' a surface with which it is perpendicular to.
-Also apparent is the reduction of group velocity; the slope of the bands is greatly reduced.
-This has an effect on the Majorana coherence length, as described later on in the manuscript.
-
-%%██████████████████████████████████████████████████████████████████████████
-%%██ Calculating the topological phase diagram
-%%██████████████████████████████████████████████████████████████████████████
-\section{Calculating the topological phase diagram.}
-In order to create a topological phase diagram we would normally compute the topological invariant(pfaffian).
-For a ribbon this is possible, but computing the invariant of the supercell is too computationally expensive.
-Using a generalized eigenvalue problem also proved unsuccessful due to numerical errors, so we resort to simply calculating the gap and noting the gap closings.
-
-Similar to what is described in Pientka et. al [\cite{pientka2017topological}], we see that the ribbon topology has a diamond like structure as a function of phase and Zeeman field.
-We also see some additional gap closings which are due to the BDI symmetry class, creating quite an unstable region.
-As expected, for the zigzag system, the magnitude of the gap is significantly improved, whilst maintaining the diamond like shape.
-As the zigzag shape destroys the additional symmetry, moving it to class D, we see a more clean topological region.
-\comment{We use a generalized eigenvalue problem to find all phase boundaries at once.}
-
-\comment{We calculate the gap by finding the minimum energy in the spectrum.}
-
-\begin{figure}[!htb]
-\includegraphics[width=0.95\columnwidth]{figures/bandstructures}
-\caption{Figure of the bandstuctures.
-Where the lines are (blue) $\phi=0$, $B=0$ and (red) $\phi=\pi$, $B \ne 0$.
-and the subplots (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W$ is the junction width.
-We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
-\label{fig:bandstuctures}}
-\end{figure}
-
-\begin{figure}[!htb]
-\includegraphics[width=0.95\columnwidth]{figures/phasediagrams}
-\caption{Phase diagrams of a straight system (a, b) and zigzag system (c, d), where (a, c) are $E(\mu, B)$ and (b, d) are $E(\phi, B)$.
-We use a generalized eigenvalue problem to find all phase boundaries at once and find the minimal energy gap by finding the minimum in the spectrum: $\min{E(k)}$.
-\label{fig:phasediagrams}}
-\end{figure}
-
-%%██████████████████████████████████████████████████████████████████████████
 %%██ Localization lengths and shape effect
@@
 \section{Localization lengths and shape effect}
+
+\comment{We find the Majorana lengths by calculating the slowest decaying mode.}
+
+\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag.}
+
+\comment{We also confirm that the specific shape does not matter.}
+
 Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinusoids.
@@
 This can be explained by two effects: the increase in topological gap, but also the beforementioned reduction of the group velocity.
-\comment{We find the Majorana lengths by calculating the slowest decaying mode.}
 

### 2018-12-11 paper/snakemajoranas.tex
fixed merge conflict

@@
 We consider a system (Fig.~\ref{fig:setup}) consisting of a two dimensional strip of semiconductor, with superconductors adjacent on both sides.
-A magnetic field pointed along the x direction is applied.
-We model the system with a BdG Hamiltonian Eq.~\eqref{eq:hamiltonian}; the normal part also has Rashba spin-orbit coupling and a Zeeman field, and the superconductors differ in superconducting phase.
+As seen in the figure, we modulate the shape of the normal region, which can be either zigzag as depicted, or a more smooth snake like shape.
+Just as the normal system[\cite{pientka2017topological}], a magnetic field pointed along the x direction is applied.
+We model the system with a BdG Hamiltonian Eq.~\eqref{eq:hamiltonian}; the normal part has Rashba spin-orbit coupling and a Zeeman field, and apart from the kinetic term, the superconductors only have a superconducting term differ in superconducting phase.
 For the zigzag geometry, we take a sawtooth like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
@@
 %%██████████████████████████████████████████████████████████████████████████
-%%██ Numerical bandstructures
-%%██████████████████████████████████████████████████████████████████████████
-\section{Numerical bandstructures}
-
-\comment{We consider a 2D SNS junction with a Rashba-BdG Hamiltonian and zigzag geometry.}
-
-\comment{We discretize the model and simulate it with Kwant.}
-
-%%██████████████████████████████████████████████████████████████████████████
 %%██ Calculating the bandstuctures
@@
 \section{Calculating the bandstuctures.}
+
+\comment{We consider a 2D SNS junction with a Rashba-BdG Hamiltonian.}
+We consider the model described in section II; a two dimensional SNS junction with a Rashba BdG Hamiltonian.
+
+\comment{We discretize the model and simulate it with Kwant.}
 In figure \ref{fig:bandstuctures}, We calculate the bandstructure for a zigzag system with varying amplitude using Kwant.
@@
 For comparisons sake, we take the same cell size for the ribbon structure so the bandstructure is folded in the same way.
-The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size is increased tenfolds.
-We claim this effect is due to the fact that the modes where the gap is smallest, when the momentum is almost completely focused along the strip ($k_x=k_F$), are cut off by the zigzag geometry.
+The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size is increased more than an order of magnitude.
+This effect is due to the fact that the modes where the gap is smallest, when the momentum is almost completely focused along the strip ($k_x=k_F$), are cut off by the zigzag geometry.
 Additionally in the presence of normal reflection, due to the availability of NS interfaces at a wide range of slopes, the reflected part will eventually ``find'' a surface with which it is perpendicular to.

### 2018-12-12 paper/snakemajoranas.tex
Cleaned up first three sections of report

@@
 Majorana bound states (MBSs) are a promising candidate to form the basis of a stable platform for topological quantum computing.
+
 \comment{Majoranas are mostly made in hybrid NS structures.}
@@
 
+\comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
+
 \comment{The gap is small because of long trajectories.}
-From a semiclassical perspective, long paths through the semiconductor without interruption by the superconductor.
-
-\comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
-We claim that one of the problems lying in the way of a stable system, is the appearance of a soft gap; the gap is greatly reduced for states with momentum directed along the length of the strip.
+One of the problems lying in the way of a stable system, is the appearance of a soft gap; the gap is greatly reduced for states with momentum directed along the length of the strip.
+From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
 
 \comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
-We show that introducing a zigzag or snake like geometry for the semiconductor removes these long trajectories and avoids the appearance of a soft gap.
+We show that introducing a zigzag or snake like geometry for the semiconductor removes these long trajectories and prevents the appearance of a soft gap.
 
@@
 \section{Physical picture}
+
+\comment{We consider a two-dimensional system with zigzag.}
 We consider a system (Fig.~\ref{fig:setup}) consisting of a two dimensional strip of semiconductor, with superconductors adjacent on both sides.
@@
 For the zigzag geometry, we take a sawtooth like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
+
+\comment{The symmetry class of the system is D.}
 We know from \onlinecite{pientka2017topological} that the non-zigzag system is in class BDI.
@@
 \comment{We consider a 2D SNS junction with a Rashba-BdG Hamiltonian.}
-We consider the model described in section II; a two dimensional SNS junction with a Rashba BdG Hamiltonian.
 
-\comment{We discretize the model and simulate it with Kwant.}
-In figure \ref{fig:bandstuctures}, We calculate the bandstructure for a zigzag system with varying amplitude using Kwant.
+\comment{We discretize the model described in section II and simulate it with Kwant.}
+We implement a tightbinding version of the model described in section II (a two dimensional SNS junction with a Rashba BdG Hamiltonian) using Kwant.
+
+\comment{We calculate the bandstructure for varying amount of zigzag.}
+In figure \ref{fig:bandstuctures}, the bandstructure for zigzag systems with varying amplitude is displayed.
 As the zigzag introduces super cell, we see a folded bandstructure.
 For comparisons sake, we take the same cell size for the ribbon structure so the bandstructure is folded in the same way.
+
+\comment{The bandstructures show that modulation of the geometry increases the gap by an order of magnitude, as well as reduce the group velocity.}
 The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size is increased more than an order of magnitude.
 This effect is due to the fact that the modes where the gap is smallest, when the momentum is almost completely focused along the strip ($k_x=k_F$), are cut off by the zigzag geometry.
-Additionally in the presence of normal reflection, due to the availability of NS interfaces at a wide range of slopes, the reflected part will eventually ``find'' a surface with which it is perpendicular to.
 Also apparent is the reduction of group velocity; the slope of the bands is greatly reduced.
@@
 
+Additionally in the presence of normal reflection, due to the availability of NS interfaces at a wide range of slopes, the reflected part will eventually ``find'' a surface with which it is perpendicular to.
+
 \comment{Extensions: we omit several physical effects, disorder, electrostatics, etc.}

### 2018-12-12 paper/snakemajoranas.tex
Added and reorganized analytics (section V)

@@
 
-\comment{We consider a 2D SNS junction with a Rashba-BdG Hamiltonian.}
-
 \comment{We discretize the model described in section II and simulate it with Kwant.}
@@
 \section{Calculating the topological phase diagram.}
-In order to create a topological phase diagram we would normally compute the topological invariant(pfaffian).
-For a ribbon this is possible, but computing the invariant of the supercell is too computationally expensive.
-Using a generalized eigenvalue problem also proved unsuccessful due to numerical errors, so we resort to simply calculating the gap and noting the gap closings.
 
+\comment{We calculate the topological phase diagram using the gap size.}
+We calculate the gap from the bandstructure (minimum energy in the spectrum) using the same method described in comment III.
+Noting the gap closings and the fact we know the topology for the non-zigzag system, we can infer the topology of the system with zigzag modulation.
+
+\comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry. }
 Similar to what is described in Pientka et. al [\cite{pientka2017topological}], we see that the ribbon topology has a diamond like structure as a function of phase and Zeeman field.
@@
 As the zigzag shape destroys the additional symmetry, moving it to class D, we see a more clean topological region.
-\comment{We use a generalized eigenvalue problem to find all phase boundaries at once.}
-
-\comment{We calculate the gap by finding the minimum energy in the spectrum.}
 
@@
 \comment{To compute the effect of cutoff consider a single segment of the zigzag and obtain the spectrum analytically (this allows to use translation invariance).}
+We establish that the cutoff of long trajectories is the driving mechanism behind the order of magnitude gap improvement using an analytical approach.
+We derive the Andreev spectrum for a single (diagonal) segment of the zigzag, and define the gap of the system as the minimum of the spectrum occurring before the cutoff corresponding to the particular geometry.
+The system under consideration is thus a ribbon SNS junction with tilted magnetic field.
+
+\comment{The definition of the cutoff... }
 
 \comment{We use a short junction approximation and neglect transverse SO.}
-
-\comment{The lowest energy at $|k| < k_\textrm{cutoff}$ sets the band gap.}
-
-We claim that the hardening of the gap is due to the cutoff of long trajectories.
-In order to verify this is the case, we take a ribbon SNS junction with magnetic field rotated such that it corresponds to a rising section of the zigzag.
-We then compute the scattering matrix Eq.~\eqref{eq:smatrix} to find the Andreev bound spectrum as a function of the momentum along the strip direction.
-We cut off the spectrum at the momentum corresponding to the proposed cutoff in the zigzag, and compare it to the numerically obtained gap for a true zigzag system.
+We derive the spectrum by calculating the scattering matrix for the normal region and applying the Andreev bound state condition for the short junction limit\cite{beenakker1991universal, sticlet_robustness_2017}.
+For deriviation of the scattering matrix, we neglect SOI in the transverse direction, which is valid for $W<l_\text{so}$.
+The result is specified in Eqs. \ref{eq:smatrix} to \ref{eq:momenta_short_junction}.
 
@@
 \end{align}
+
 \begin{footnotesize}
@@
     k_2 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n+\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}
+\label{eq:momenta_short_junction}
 \end{align}
@@
 Using this result and Eq.~\eqref{eq:smatrix}, we numerically find the Andreev spectrum.
+
+\comment{The lowest energy at $|k| < k_\textrm{cutoff}$ sets the band gap.}
+We cut off the spectrum at the momentum corresponding to the proposed cutoff in the zigzag, and compare it to the numerically obtained gap for a true zigzag system.
 

### 2018-12-12 paper/snakemajoranas.tex
Rearanged and added to section VI(localization effects)

@@
 \comment{The gap is small because of long trajectories.}
-One of the problems lying in the way of a stable system, is the appearance of a soft gap; the gap is greatly reduced for states with momentum directed along the length of the strip.
+One of the biggest challenges in constructing stable Majoranas is the appearance of a soft gap; where the gap in the density of states is greatly reduced for states with momentum directed along the length of the strip.
 From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
+Additionally, these long trajectories have long flight times $\tau_f$ and equivalenly small Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$, resulting in a small gap.
 
 \comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
-We show that introducing a zigzag or snake like geometry for the semiconductor removes these long trajectories and prevents the appearance of a soft gap.
+In this paper we show that introducing a zigzag or snake like geometry for the semiconductor eliminates these long trajectories and prevents the appearance of a soft gap.
 
@@
 \comment{We consider a two-dimensional system with zigzag.}
-We consider a system (Fig.~\ref{fig:setup}) consisting of a two dimensional strip of semiconductor, with superconductors adjacent on both sides.
-As seen in the figure, we modulate the shape of the normal region, which can be either zigzag as depicted, or a more smooth snake like shape.
-Just as the normal system[\cite{pientka2017topological}], a magnetic field pointed along the x direction is applied.
-We model the system with a BdG Hamiltonian Eq.~\eqref{eq:hamiltonian}; the normal part has Rashba spin-orbit coupling and a Zeeman field, and apart from the kinetic term, the superconductors only have a superconducting term differ in superconducting phase.
+We consider a system (Fig.~\ref{fig:setup}) consisting of a two dimensional strip of semiconductor, with superconductors on both sides.
+We modulate the shape of the normal region, which can be either zigzag as depicted, or a more smooth sinusoidal like shape.
+Similar to the straight system \cite{pientka2017topological}, a magnetic field $B_x$ pointed along the $x$ direction is applied.
+We model the system with a BdG Hamiltonian Eq.~\eqref{eq:hamiltonian}; the normal part has Rashba spin-orbit coupling and a Zeeman field, and apart from the kinetic term, the superconductors only have a superconducting term with a superconducting phase.
 For the zigzag geometry, we take a sawtooth like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
@@
 This has an effect on the Majorana coherence length, as described later on in the manuscript.
+
+\comment{The introduction of an SN interface at many angles also increases performance.}
+Additionally in the presence of normal reflection, due to the availability of NS interfaces at a wide range of slopes, the reflected part will eventually ``find'' a surface with which it is perpendicular to.
+The transparency of the SN interface is thus improved for transversal modes.
 
@@
 
-\comment{We find the Majorana lengths by calculating the slowest decaying mode.}
-
 \comment{In a zigzag geometry Majoranas are localized within one segment of zigzag.}
 
+\comment{We find the Majorana lengths by calculating the slowest decaying mode.}
+Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinusoids.
+In figure \ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.
+For the ribbon system, we see that the Majorana coherence length is relatively large, not showing the decolalized nature sought after.
+All of the zigzag type geometries however show greatly reduced coherence length.
+This can be explained by two effects: the increase in topological gap, but also the before mentioned reduction of the group velocity.
+
 \comment{We also confirm that the specific shape does not matter.}
-
-Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinusoids.
-We then superimpose them onto the geometry, as in figure \ref{fig:wavefunctions}.
-For the ribbon system, we see that the Majorana coherence length is relatively large, not showing the decolalized nature sought after.
-All of the zigzag type geometries however show greatly reduced coherence length.\tabularnewline
-This can be explained by two effects: the increase in topological gap, but also the beforementioned reduction of the group velocity.
+Also note the similarity between the various shapes, sharp corners or more smoothlike, the effect is the same.
 
@@
 \caption{Wavefunctions for different sizes and geometries.
-With (a) a straight system, (b) a zigzag system, (c) a system where the normal region is defined by two parallel sine waves, and (d) a system with the Laeven shape.
+With (a) a straight system, (b) a zigzag system, (c) a system where the normal region is defined by lines parallel to a sinosoid, and (d) a system with vertically offset sinosoids.
 Inside the figure we indicate the Majorana length (or coherence length) $\xi$ and the topological energy gap $E_\textrm{gap}.$
@@
 \section{Discussion and Conclusions}
-
-Additionally in the presence of normal reflection, due to the availability of NS interfaces at a wide range of slopes, the reflected part will eventually ``find'' a surface with which it is perpendicular to.
 

### 2018-12-18 paper/snakemajoranas.tex
Add new system figure
Updated system image, as well as additions to results/discussion

--- 2018-12-12 paper/snakemajoranas.tex
@@
 \begin{figure}[!htb]
-\includegraphics[width=0.95\columnwidth]{figures/systemPicture.pdf}
+\includegraphics[width=0.95\columnwidth]{figures/zigzag.pdf}
 \caption{Setups. Figure of a straight and zigzag system, including trajectories.
@@
 %%██████████████████████████████████████████████████████████████████████████
-\section{Localization lengths and shape effect}
+\section{Localization lengths and shape effects}
 
@@
 
+\comment{The zigzag geometry is a useful tool in hardening the gap and decreasing majorana length, now experimental verification necessary}
+Modulating the geometry of the normal ribbon solves the problems of gap softening and majorana length in an effective and controllable manner.
+Additionally, the breaking of BDI symmetry into D symmetry results in a cleaner phase diagram.
+
+\comment{Current fabrication techniques seem compatible with the proposed geometry, and experimental verification should point out whether it holds up to its promise.}
+Current fabrication techniques seem compatible with the proposed geometry, and experimental efforts are already on their way.
+Apart from optimizing the geometry for gap and Majorana length, the same freedom of geometry we use can additionally be applied to ease experimental implementation.
+Slight modifications to the geometry, for example to ease measurement, should not have large implications on the physics.
+
+\comment{It would be interesting to study what geometry creates an optimal environment for Majorana modes to exist.}
+We have studied sawtooth, snake like and offset sinosoid modulation of the semicondctor region, but perhaps a more exotic shape will be optimal.
+A systematic study of the effect of specific geometrical features would be interesting to study.
+
 \comment{Extensions: we omit several physical effects, disorder, electrostatics, etc.}
+We omit several physical effects, such as: disorder, electrostatics, the orbital effect, etc..
+Experimental verification, along with further study of the proposed system is required to see whether their omittance obscure the improvements in the model studied in this manuscript.
 

### 2018-12-19 paper/snakemajoranas.tex
updated figure and made some changes in discussion

@@
 \comment{The zigzag geometry is a useful tool in hardening the gap and decreasing majorana length, now experimental verification necessary}
-Modulating the geometry of the normal ribbon solves the problems of gap softening and majorana length in an effective and controllable manner.
-Additionally, the breaking of BDI symmetry into D symmetry results in a cleaner phase diagram.
+The introduction of a zigzag geometry increases the topological gap by over an order of magnitude, as well as offering a substantial reduction of the Majorana length.
+Additionally, the breaking of BDI symmetry into D symmetry results in a cleaner topological region.
 
 \comment{Current fabrication techniques seem compatible with the proposed geometry, and experimental verification should point out whether it holds up to its promise.}
-Current fabrication techniques seem compatible with the proposed geometry, and experimental efforts are already on their way.
-Apart from optimizing the geometry for gap and Majorana length, the same freedom of geometry we use can additionally be applied to ease experimental implementation.
+Current fabrication techniques seem compatible with the proposed geometry; zigzag devices have already been created.
 Slight modifications to the geometry, for example to ease measurement, should not have large implications on the physics.
@@
 We have studied sawtooth, snake like and offset sinosoid modulation of the semicondctor region, but perhaps a more exotic shape will be optimal.
-A systematic study of the effect of specific geometrical features would be interesting to study.
+A study optimizing the geometry for supporting Majorana's would be an interesting continuation.
 
@@
 We omit several physical effects, such as: disorder, electrostatics, the orbital effect, etc..
-Experimental verification, along with further study of the proposed system is required to see whether their omittance obscure the improvements in the model studied in this manuscript.
-
-\comment{Outlook: how to cope with the complications.}
+Further study, as well as experimental verification, are required to see whether the conclusions of this model are valid for the real case.
 

### 2018-12-19 paper/snakemajoranas.tex
Minor changes to manuscript

@@
 \date{\today}
-
 \begin{abstract}
@@
 
-\comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
-
 \comment{The gap is small because of long trajectories.}
@@
 Additionally, these long trajectories have long flight times $\tau_f$ and equivalenly small Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$, resulting in a small gap.
+
+\comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
+Currently proposed workarounds are low density or disorder~\cite{haim_double-edge_2018}, but both have drawbacks.
 
@@
 \section{Physical picture}
-
 \comment{We consider a two-dimensional system with zigzag.}
@@
 \comment{We calculate the bandstructure for varying amount of zigzag.}
-In figure \ref{fig:bandstuctures}, the bandstructure for zigzag systems with varying amplitude is displayed.
+In figure~\ref{fig:bandstuctures}, the bandstructure for zigzag systems with varying amplitude is displayed.
 As the zigzag introduces super cell, we see a folded bandstructure.
@@
 \comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry. }
-Similar to what is described in Pientka et. al [\cite{pientka2017topological}], we see that the ribbon topology has a diamond like structure as a function of phase and Zeeman field.
+Similar to what is described in Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond like structure as a function of phase and Zeeman field.
 We also see some additional gap closings which are due to the BDI symmetry class, creating quite an unstable region.
@@
 For deriviation of the scattering matrix, we neglect SOI in the transverse direction, which is valid for $W<l_\text{so}$.
-The result is specified in Eqs. \ref{eq:smatrix} to \ref{eq:momenta_short_junction}.
+The result is specified in Eqs.~\eqref{eq:smatrix} to~\eqref{eq:momenta_short_junction}.
 
@@
 Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinusoids.
-In figure \ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.
+In figure~\ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.
 For the ribbon system, we see that the Majorana coherence length is relatively large, not showing the decolalized nature sought after.

### 2018-12-20 paper/snakemajoranas.tex
read and revise until L181

@@
 \comment{The gap is small because of long trajectories.}
-One of the biggest challenges in constructing stable Majoranas is the appearance of a soft gap; where the gap in the density of states is greatly reduced for states with momentum directed along the length of the strip.
+One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap; where the gap in the density of states is greatly reduced for states with the momentum directed along the length of the strip.
 From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
@@
 \comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
-Currently proposed workarounds are low density or disorder~\cite{haim_double-edge_2018}, but both have drawbacks.
+Currently, proposed workarounds are low density or disorder~\cite{haim_double-edge_2018}, but both have drawbacks.
 
 \comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
-In this paper we show that introducing a zigzag or snake like geometry for the semiconductor eliminates these long trajectories and prevents the appearance of a soft gap.
+In this paper we show that introducing a zigzag or snake like geometry for the semiconductor eliminates these long trajectories and prevents the appearance of a soft gap while also increasing the topological gap by an order of magnitude.
 
@@
 \comment{We consider a two-dimensional system with zigzag.}
-We consider a system (Fig.~\ref{fig:setup}) consisting of a two dimensional strip of semiconductor, with superconductors on both sides.
+We consider a Josephson junction (JJ)(Fig.~\ref{fig:setup}) consisting of a two dimensional strip of semiconductor, with superconductors on both sides.
 We modulate the shape of the normal region, which can be either zigzag as depicted, or a more smooth sinusoidal like shape.
-Similar to the straight system \cite{pientka2017topological}, a magnetic field $B_x$ pointed along the $x$ direction is applied.
-We model the system with a BdG Hamiltonian Eq.~\eqref{eq:hamiltonian}; the normal part has Rashba spin-orbit coupling and a Zeeman field, and apart from the kinetic term, the superconductors only have a superconducting term with a superconducting phase.
-For the zigzag geometry, we take a sawtooth like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
+Similar to the conventional straight system \cite{pientka2017topological}, a magnetic field $B_x$ perpendicular to the junction is applied.
+We model the system with a BdG Hamiltonian Eq.~\eqref{eq:hamiltonian}; the normal part has a linear Rashba spin-orbit coupling term characterized by $\alpha$ and a Zeeman field with $E_z=\frac{1}{2}mu_B g B_x$.
+The superconductor has a superconducting coupling term $\Delta$ with a superconducting phase $\exp{\pm i \phi/2}$.
+Both parts have a kinetic term and chemical potential $\mu$. 
+For the zigzag geometry, we first consider a sawtooth like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
+Later in this manuscript we show that the exact details of the shape are not important and consider different zigzag geometries also parametrized by $z_x, \; z_y, \; W$.
 
 \comment{The symmetry class of the system is D.}
-We know from \onlinecite{pientka2017topological} that the non-zigzag system is in class BDI.
-Using the software package Qsymm\cite{varjas2018qsymm}, we evaluate the symmetry class of the system to be D.
+The non-zigzag system is in the symmetry class BDI \cite{pientka2017topological}.
+Using the software package Qsymm\cite{varjas2018qsymm}, we find that the symmetry class of our system to be $\mathcal{D}$ because we break the chiral symmetry $\mathcal{C}$ resulting from the mirror symmetric junction.
 
@@
 \comment{We discretize the model described in section II and simulate it with Kwant.}
-We implement a tightbinding version of the model described in section II (a two dimensional SNS junction with a Rashba BdG Hamiltonian) using Kwant.
+We discretize our continuum Hamiltonian \eqref{eq:hamiltonian} and implement a tight-binding model using Kwant~\cite{groth_kwant:_2014}.
+The resulting Hamiltonians are large because instead of having a single slice of sites that is translationally invariant in the $x$-direction, we create a long supercell in order to make the structure periodic.
+To speed up these expensive simualtions we employ an adaptive sampling strategy, using the Python package Adaptive. % TODO: add citation
 
@@
 In figure~\ref{fig:bandstuctures}, the bandstructure for zigzag systems with varying amplitude is displayed.
-As the zigzag introduces super cell, we see a folded bandstructure.
-For comparisons sake, we take the same cell size for the ribbon structure so the bandstructure is folded in the same way.
+Because the discretized zigzag system is modeled using a super cell, we can only plot a folded bandstructure.
+For comparisons sake, we take the same cell size for the ribbon structure such that the bandstructure is folded in the same way.
 
 \comment{The bandstructures show that modulation of the geometry increases the gap by an order of magnitude, as well as reduce the group velocity.}
-The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size is increased more than an order of magnitude.
-This effect is due to the fact that the modes where the gap is smallest, when the momentum is almost completely focused along the strip ($k_x=k_F$), are cut off by the zigzag geometry.
-Also apparent is the reduction of group velocity; the slope of the bands is greatly reduced.
-This has an effect on the Majorana coherence length, as described later on in the manuscript.
+The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size is increased by more than an order of magnitude.
+This happens because in a straight system, long trajectories are possible, these have a momentum that is directed along the strip and consequently, $k_x \approx k_F$.
+The smallest gap in a straight system occurs around $k_F$ and because the zigzag cuts off long trajectories, the gap size is increased. 
+Besides this, the velocity of the modes is greatly reduced, which has a positive effect on the Majorana coherence length, as described later in section XXX. % TODO: add ref
 
 \comment{The introduction of an SN interface at many angles also increases performance.}
-Additionally in the presence of normal reflection, due to the availability of NS interfaces at a wide range of slopes, the reflected part will eventually ``find'' a surface with which it is perpendicular to.
-The transparency of the SN interface is thus improved for transversal modes.
+Additionally, in the presence of normal reflection, due to the presence of NS interfaces at a wide range of angles, the reflected part will eventually scatter with a perpendicular surface.
+This means that for transversal modes the transparency of the NS interface will increase.
 
@@
 \comment{We calculate the topological phase diagram using the gap size.}
-We calculate the gap from the bandstructure (minimum energy in the spectrum) using the same method described in comment III.
-Noting the gap closings and the fact we know the topology for the non-zigzag system, we can infer the topology of the system with zigzag modulation.
+We calculate the gap by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{|E(k)|}$.
+Noting the gap closings and the fact we know the topology for the non-zigzag system, we can infer the topology of the system with zigzag modulation. % Bas: I don't understand what is written here
 
 \comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry. }
-Similar to what is described in Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond like structure as a function of phase and Zeeman field.
+Similar to what is described by Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond like structure as a function of phase and Zeeman field.
 We also see some additional gap closings which are due to the BDI symmetry class, creating quite an unstable region.

### 2019-01-07 thesis_report/discussion.tex
Outline of thesis

\chapter{Discussion \& Results}

	\comment{We see that the introduction of a zigzag leads to a reduction of the gap}
	\section{Gap/bandstructure as a function of zigzagginess}
		\comment{We discretize the model described in section II and simulate it with Kwant.}
		We implement a tightbinding version of the model described in section II (a two dimensional SNS junction with a Rashba BdG Hamiltonian) using Kwant.

		\begin{figure}[!htb]
		\includegraphics[width=0.95\columnwidth]{figures/bandstructures}
		\caption{Figure of the bandstuctures.
		Where the lines are (blue) $\phi=0$, $B=0$ and (red) $\phi=\pi$, $B \ne 0$.
		and the subplots (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W$ is the junction width.
		We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
		\label{fig:bandstuctures}}
		\end{figure}

		\comment{We calculate the bandstructure for varying amount of zigzag.}
		In figure~\ref{fig:bandstuctures}, the bandstructure for zigzag systems with varying amplitude is displayed.
		As the zigzag introduces super cell, we see a folded bandstructure.
		For comparisons sake, we take the same cell size for the ribbon structure so the bandstructure is folded in the same way.

		\comment{The bandstructures show that modulation of the geometry increases the gap by an order of magnitude, as well as reduce the group velocity.}
		The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size is increased more than an order of magnitude.
		This effect is due to the fact that the modes where the gap is smallest, when the momentum is almost completely focused along the strip ($k_x=k_F$), are cut off by the zigzag geometry.
		Also apparent is the reduction of group velocity; the slope of the bands is greatly reduced.
		This has an effect on the Majorana coherence length, as described later on in the manuscript.

		\comment{The introduction of an SN interface at many angles also increases performance.}
		Additionally in the presence of normal reflection, due to the availability of NS interfaces at a wide range of slopes, the reflected part will eventually ``find'' a surface with which it is perpendicular to. The transparency of the SN interface is thus improved for transversal modes.

	\section{Majorana decay length}
	\section{Phase diagram for zigzaggy system}
	\section{Analytical estimate}

### 2019-01-07 thesis_report/introduction.tex
Outline of thesis

\chapter{Introduction}

\comment{We propose that the introduction of a zigzag-shaped modulation of the junction region leads to an increased topological gap, as well as a reduction of the Majorana coherence length.}
\comment{We hypothesize that the gap improvement is the result of the elimination of long trajectories}

### 2019-01-07 thesis_report/methods.tex
Outline of thesis

\chapter{Methods}

\section{Sparse eigendecomposition of kwant system}
	\subsection{Wrapped system}
	\subsection{Finite system}

\section{Scattering matrix formalism}

### 2019-01-07 thesis_report/theory.tex
Add zigzag and L-systems
Outline of thesis

@@
+% UNCOMMENT SO YOU CAN LINK PAPERS EASILY WITH SUBLIME TEXT
+% \bibliography{report}
+
 % Momentum operators
@@
 
-%%██████████████████████████████████████████████████████████████████████████
-%%██ General Physics
-%%██████████████████████████████████████████████████████████████████████████
 \section{General Physics}
-%%--------------------------------------------------------------------------
-%%  Spin-orbit coupling
+	\subsection{Boguliubov de Gennes Hamiltonian}
+
     \subsection{Spin-orbit coupling}
@@
 
-%%--------------------------------------------------------------------------
-%%  Supercurrent
     \subsection{Supercurrent}
-    As the field we are describing is 
-%%▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓
+	The current
 
-%%██████████████████████████████████████████████████████████████████████████
-%%██ Tight binding
-%%██████████████████████████████████████████████████████████████████████████
-\section{Tight binding}
+	\subsection{Tight binding}
 
-%%▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓
+		\subsection{Topology in solid state physics}
+		The Wikipedia definition of mathematical topology is as follows:
 
-%%██████████████████████████████████████████████████████████████████████████
-%%██ Topology in solid state physics
-%%██████████████████████████████████████████████████████████████████████████
-\section{Topology in solid state physics}     The Wikipedia definition of
-mathematical topology is as follows: \quote{Topology can be formally defined as
-"the study of qualitative properties of certain objects (called topological
-spaces) that are invariant under a certain kind of
-transformation}\cite{wiki:topology}\\
+		\quote{Topology can be formally defined as "the study of qualitative properties of certain objects (called topological spaces) that are invariant under a certain kind of transformation}\cite{noauthor_topology_2018}
 
-%%-------------------------------------------------------------------------- 
-%% Symmetries     
-\subsection{Symmetries}
+			\subsubsection{Symmetries}
 
-%%▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓
+\section{Majorana bound states}
+	\subsection{General properties}
+	\subsection{Decay length}
+	\subsection{Topological gap}
+
+\section{Two dimensional platform for Majoranas}
+	\subsection{Phase diagram}
+	\subsection{Current phase relationship}
+	\subsection{Thouless energy}
+
+\section{Scattering matrix formalism}

### 2019-01-10 thesis_report/methods.tex
Updated thesis

@@
 \chapter{Methods}
+% UNCOMMENT TO USE LaTeXing autocomplete for refereces
+% \bibliography{report}
 
-\section{Sparse eigendecomposition of kwant system}
-	\subsection{Wrapped system}
-	\subsection{Finite system}
+\comment{We propose a method to verify that elimination of long trajectories is responsible for the increased topological gap in a zigzag system.}
+\section{Quasiclassical estimation of the topological gap}
+	\comment{To compute the effect of cutoff consider a single segment of the zigzag and obtain the spectrum analytically (this allows to use translation invariance).}
+	In order to establish that the elimination of long trajectories is the driving mechanism behind the order of magnitude gap improvement, we use an analytical approach.
+	We estimate the gap of the zigzag system by the minimum energy occuring in the Andreev spectrum of a single (diagonal) segment of zigzag.
+	The spectrum of the zigzag segment we define as the spectrum of an infinite ribbon SNS junction with tilted-magnetic field. 
+	The finite length of the segment is modeled by not including momenta corresponding to long trajectories when taking the minimum over the spectrum.
 
-\section{Scattering matrix formalism}
+	\comment{The spectrum is derived using a scattering matrix, and we consider multiple ways to eliminate long trajectory momenta.}
+
+	Estimating the gap is a two-step process: derivation of the Andreev spectrum, and taking the minimum energy over a particular set of allowed momenta.
+	The first is derived using scattering matrix formalism and the Andreev bound state condition\cite{beenakker1991universal, sticlet_robustness_2017}.
+	The second step is mostly trivial, but the difficulty lies with identifying the set of allowed  momenta to take the minimum over.
+
+	\subsection{Analytical estimate of Andreev spectrum for a straight junction}
+
+		\comment{We use a short junction approximation and neglect transverse SO.}
+		We derive the spectrum by calculating the scattering matrix for the normal region and applying the Andreev bound state condition for the short junction limit\cite{beenakker1991universal, sticlet_robustness_2017}.
+		For deriviation of the scattering matrix, we neglect SOI in the transverse direction, which is valid for $W<l_\text{so}$.
+		The result is specified in Eqs.~\eqref{eq:smatrix} to~\eqref{eq:momenta_short_junction}.
+
+		In order to get the spectrum from the S-matrix [Eq.~\eqref{eq:smatrix}] we use the main result from Ref.~\cite{beenakker1991universal} and start with a determinantal equation for the bound state energies in a SNS-junction:
+
+		\begin{equation}
+		\det\left[1+\alpha^{2}\left(E\right)r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)\right]=0
+		\end{equation}
+
+		We rewrite this as a characteristic polynomial problem $\det\left[A-\lambda I\right]=0$, as
+
+		\begin{equation}
+		\det\left[r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)-\frac{-1}{\alpha^{2}\left(E\right)}I\right]=0
+		\end{equation}
+
+		with
+		\begin{equation}
+		\lambda=-\frac{1}{\alpha^{2}\left(E\right)},\;A=r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right).
+		\end{equation}
+
+		Where $\lambda_i$ are the eigenvalues of $A$.
+		Inverting $\alpha\left(E\right)\equiv\exp\left(-i\arccos\left(E/\Delta\right)\right)$ yields $\frac{E}{\Delta}=\frac{\alpha^{2}+1}{2\alpha}=\frac{1}{2}\left(\alpha+\alpha^{-1}\right)=\textrm{Re}(\alpha)$, where the last equality holds because $\alpha$ is unitary.
+		Then, since $\alpha$ is only defined in the positive imaginary plane, the energies are $\frac{E_{i}}{\Delta}=\textrm{Re}\left(\sqrt{-1/\lambda_{i}}\right)$ where we take the root which has a positive imaginary part.
+		Using this result and Eq.~\eqref{eq:smatrix}, we numerically find the Andreev spectrum.
+
+		\subsubsection{Derivation of the scattering matrix}
+			We consider the scattering problem defined by Fig. \ref{fig:scattering}, the corresponding system of equations given in Eq. \eqref{eq:scattering_matrix_problem}, and
+			continuity and flux conservation(continuity of first derivative) at the normal-superconductor interfaces.
+			The Hamiltonians of the respective regions are given by Eqs. \eqref{eq:ham_smat_normal,eq:ham_smat_superconducting}.
+			The Hamiltonian of the superconducting region does not include the superconducting term because we implement Andreev reflection seperately: this way we halve the dimensionality of the problem.
+
+			\begin{equation}
+			\begin{bmatrix} 
+			b_{1,L}\\
+			b_{2,L}\\
+			b_{1,R}\\
+			b_{2,R}
+			\end{bmatrix} 
+			= S_\text{sns} \cdot 
+			\begin{bmatrix} 
+			a_{1,L}\\
+			a_{2,L}\\
+			a_{1,R}\\
+			a_{2,R}
+			\end{bmatrix}
+			\label{eq:scattering_matrix_problem}
+			\end{equation}
+
+			\begin{align}
+			H_\text{N} &= \left[ \frac{\hbar^2}{2 \meff} \left(\kx^2 + \ky^2\right) -\mu_n\right]\sigi +
+						 \alpha \kx \sigy +
+						 E_z \left[ \cos(\theta) \sigx + \sin(\theta) \sigy \right]
+			\label{eq:ham_smat_normal} 
+			\\
+			H_\text{S} &= \left[\frac{\hbar^2}{2 \meff} \left(\kx^2 + \ky^2\right) -\mu_s\right]\sigi
+			\label{eq:ham_smat_superconducting}
+			\end{align}
+
+			\begin{figure}[!htb]
+			\includegraphics[width=0.95\columnwidth]{images/scattering}
+			\caption{Basis for scattering matrix. `S' region corresponds to the superconductor Hamiltonian without the superconducting term.}
+			\label{fig:scattering}
+			\end{figure}
+
+			The resulting scattering matrix:
+
+			\begin{align}
+			\label{eq:smatrix}
+		    S &= \left(
+		    \begin{array}{rr}
+		    r_{ll}&t_{rl}\\
+		    t_{lr}&r_{rr}\\
+		    \end{array}
+		    \right) =
+		    \left(
+		    \begin{array}{rr}
+		    \beta_+ & e^{-i q W} \beta_-\\
+		    e^{-i q W} \beta_- & e^{-2 i q W} \beta_+\\
+		    \end{array}
+		    \right)
+		    \\
+		    \beta_\pm &= \left(
+		    \begin{array}{rr}
+		    e^{i \nu_{\arg}}\left(\omega^\pm_1 - \omega^\pm_2\right) & (\omega^\pm _1 + \omega^\pm _2)\\
+		    -(\omega^\pm _1 + \omega^\pm _2) & e^{-i \nu _{\arg }} \left(\omega^\pm _2 - \omega^\pm _1\right)\\
+		    \end{array}
+		    \right)\\
+		    \omega^\pm_j &= \frac{1}{4} \left(\gamma _{j} \pm \delta _{j}\right)
+			\end{align}
+
+			\begin{align}
+			    \gamma_j &= \frac{q+i k_{j} \tan \left(\frac{W k_{j}}{2}\right)}{q-i k_{j} \tan \left(\frac{W k_{j}}{2}\right)} \\
+			    \delta_j &= \frac{q-i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}{q+i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}\\
+			    e^{i \nu_{\arg}} &= \frac{E_\text{z} e^{i \theta }-i \alpha  k_x}{\sqrt{E_\text{z}^2+\alpha  k_x \left(\alpha  k_x-2 E_\text{z} \sin (\theta )\right)}}
+			\end{align}
+
+			\begin{footnotesize}
+			\begin{align}
+			    q &= \left[ \frac{2 m_\ast}{\hbar ^2}\mu_s - k_x^2 \right]^\frac{1}{2}\\
+			    k_1 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n-\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}\\
+			    k_2 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n+\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}
+			\label{eq:momenta_short_junction}
+			\end{align}
+			\end{footnotesize}
+
+		\subsubsection{Resulting spectrum}
+			In order to get the spectrum from the S-matrix [Eq.~\eqref{eq:smatrix}] we use the main result from Ref.~\cite{beenakker1991universal} and start with a determinantal equation for the bound state energies in a SNS-junction:
+
+			\begin{equation}
+			\det\left[1+\alpha^{2}\left(E\right)r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)\right]=0
+			\end{equation}
+
+			We rewrite this as a characteristic polynomial problem $\det\left[A-\lambda I\right]=0$, as
+
+			\begin{equation}
+			\det\left[r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)-\frac{-1}{\alpha^{2}\left(E\right)}I\right]=0
+			\end{equation}
+
+			with
+			\begin{equation}
+			\lambda=-\frac{1}{\alpha^{2}\left(E\right)},\;A=r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right).
+			\end{equation}
+
+			Where $\lambda_i$ are the eigenvalues of $A$.
+			Inverting $\alpha\left(E\right)\equiv\exp\left(-i\arccos\left(E/\Delta\right)\right)$ yields $\frac{E}{\Delta}=\frac{\alpha^{2}+1}{2\alpha}=\frac{1}{2}\left(\alpha+\alpha^{-1}\right)=\textrm{Re}(\alpha)$, where the last equality holds because $\alpha$ is unitary.
+			Then, since $\alpha$ is only defined in the positive imaginary plane, the energies are $\frac{E_{i}}{\Delta}=\textrm{Re}\left(\sqrt{-1/\lambda_{i}}\right)$ where we take the root which has a positive imaginary part.
+			Using this result and Eq.~\eqref{eq:smatrix}, we numerically find the Andreev spectrum.
+
+	\subsection{Eliminating long trajectories}
+		\comment{We devise two different ways to define the cutoff of momentum.}
+
+		\begin{figure}[!htb]
+		\centering
+		\includegraphics[width=0.75\columnwidth]{images/zigzag.pdf}
+		\caption{Setups. Figure of a straight and zigzag system, including trajectories.
+		\label{fig:setup}}
+		\end{figure}
+
+		\subsubsection{Momentum cutoff}
+			We take the longest trajectory possible in a zigzag segment
+		\subsubsection{Angular cutoff}

### 2019-01-10 thesis_report/results.tex
Updated thesis

--- 2018-12-19 paper/snakemajoranas.tex
@@
-\documentclass[english, twocolumn, 10pt, aps, superscriptaddress, floatfix, prb, citeautoscript]{revtex4-1}
-\pdfoutput=1
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{verbatim}
-\usepackage{units}
-\usepackage{mathtools}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\usepackage{wasysym}
-\usepackage{layouts}
-\usepackage{siunitx}
-\usepackage{bm}
-\usepackage{xcolor}
-\usepackage[colorlinks, citecolor={blue!50!black}, urlcolor={blue!50!black}, linkcolor={red!50!black}]{hyperref}
-\usepackage{bookmark}
-\usepackage{tabularx}
-\usepackage{microtype}
-\usepackage{babel}
-\hypersetup{pdfauthor={Quantum Tinkerer},pdftitle={Increasing the topological gap by an order of magnitude through the geomerty for Majorana SNS junctions.}}
+\chapter{Results \& Discussion}
 
-\setcounter{secnumdepth}{4}
-\setcounter{tocdepth}{4}
-
-\DeclareMathOperator{\e}{e}
-\DeclareMathOperator{\de}{d\!}
-\DeclareMathOperator{\Tr}{Tr}
-\DeclareMathOperator{\diag}{diag}
-\DeclareMathOperator{\Res}{Res}
-\DeclareMathOperator{\sgn}{sgn}
-\DeclareMathOperator{\Pf}{Pf}
-\DeclareMathOperator{\Det}{Det}
-\DeclareMathOperator{\rank}{rank}
-\DeclareMathOperator{\im}{Im}
-\DeclareMathOperator{\re}{Re}
-\newcommand{\kx}{k_x}
-\newcommand{\ky}{k_y}
-\newcommand{\meff}{m_\text{eff}}
-
-\renewcommand{\comment}[2]{#2}
-% Uncomment the following line for paragraph descriptions to appear in the file.
-\renewcommand{\comment}{\paragraph}
-
-\DeclarePairedDelimiter\abs{\lvert}{\rvert}
-\DeclarePairedDelimiter\norm{\lVert}{\rVert}
-
-\makeatletter
-\let\oldabs\abs
-\def\abs{\@ifstar{\oldabs}{\oldabs*}}
-\let\oldnorm\norm
-\def\norm{\@ifstar{\oldnorm}{\oldnorm*}}
-\makeatother
-
-\newcommand{\ev}[1]{\langle#1\rangle}
-\newcommand{\bra}[1]{\langle#1|}
-\newcommand{\ket}[1]{|#1\rangle}
-\newcommand{\bracket}[2]{\langle#1|#2\rangle}
-
-\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
-\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
-\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
-
-\begin{document}
-
-\title{Increasing the topological gap by an order of magnitude through the geometry for Majorana SNS junctions.}
-
-\author{Quantum Tinkerer}
-\affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
-\email[Electronic address: ]{quantumtinkerer@tudelft.nl}
-
-\date{\today}
-\begin{abstract}
-We are solving a problem of soft gap in high density SNS Majorana junctions \cite{pientka2017topological}.
-We do this by introducing a zigzag geometry.
-This works because the maximum trajectory length is cut-off due to the geometry and therefore the minimal energy gap is given by a simple formula, which we also verify using numerics.
-In addition to having a large minimum energy gap, the absence of long length trajectories means that the localization length is very short as well.
-\end{abstract}
-
-\maketitle
-
-%%██████████████████████████████████████████████████████████████████████████
-%%██ Introduction
-%%██████████████████████████████████████████████████████████████████████████
-\section{Introduction}
-Majorana bound states (MBSs) are a promising candidate to form the basis of a stable platform for topological quantum computing.
-
-\comment{Majoranas are mostly made in hybrid NS structures.}
-The current experimental effort is focused on creating pairs of MBSs in hybrid normal-superconductor (NS) structures, where a lengthy strip (or wire) of semiconductor is interfaced with a \cite{lutchyn_majorana_2010,oreg_helical_2010} superconductor.
-Within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple wire), the semiconductor becomes topological and MBSs appear at the ends of the segment.
-Recently, a system with a slight modification has been proposed\cite{pientka2017topological}, where instead of having one superconductor, there are two superconductors, creating a superconductors-normal-superconductor (SNS) junction.
-This adds an extra knob to adjust, the superconducting phase difference $\phi$, and this should make it easier to tune the system into the topological phase.
-In practice, multiple problems arise making even the observation, let alone the manipulation of Majoranas difficult.
-
-\comment{The gap is small because of long trajectories.}
-One of the biggest challenges in constructing stable Majoranas is the appearance of a soft gap; where the gap in the density of states is greatly reduced for states with momentum directed along the length of the strip.
-From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
-Additionally, these long trajectories have long flight times $\tau_f$ and equivalenly small Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$, resulting in a small gap.
-
-\comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
-Currently proposed workarounds are low density or disorder~\cite{haim_double-edge_2018}, but both have drawbacks.
-
-\comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
-In this paper we show that introducing a zigzag or snake like geometry for the semiconductor eliminates these long trajectories and prevents the appearance of a soft gap.
-
-%%██████████████████████████████████████████████████████████████████████████
-%%██ Physical picture
-%%██████████████████████████████████████████████████████████████████████████
-\section{Physical picture}
-\comment{We consider a two-dimensional system with zigzag.}
-We consider a system (Fig.~\ref{fig:setup}) consisting of a two dimensional strip of semiconductor, with superconductors on both sides.
-We modulate the shape of the normal region, which can be either zigzag as depicted, or a more smooth sinusoidal like shape.
-Similar to the straight system \cite{pientka2017topological}, a magnetic field $B_x$ pointed along the $x$ direction is applied.
-We model the system with a BdG Hamiltonian Eq.~\eqref{eq:hamiltonian}; the normal part has Rashba spin-orbit coupling and a Zeeman field, and apart from the kinetic term, the superconductors only have a superconducting term with a superconducting phase.
-For the zigzag geometry, we take a sawtooth like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
-
-\comment{The symmetry class of the system is D.}
-We know from \onlinecite{pientka2017topological} that the non-zigzag system is in class BDI.
-Using the software package Qsymm\cite{varjas2018qsymm}, we evaluate the symmetry class of the system to be D.
-
-\begin{small}
-\begin{align}
-    H = \left(\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right)\tau_z+
-        E_\text{z} \sigma_x+
-        \alpha \left( \ky \sigma_x - \kx \sigma_y \right) \tau_z +
-        \Delta \tau_y
-\end{align}
-\label{eq:hamiltonian}
-\end{small}
+	\comment{We see that the introduction of a zigzag leads to a reduction of the gap}
+	\section{Gap/bandstructure as a function of zigzagginess}
+		\comment{We discretize the model described in section II and simulate it with Kwant.}
+		We implement a tightbinding version of the model described in the Methods section (a two dimensional SNS junction with a Rashba BdG Hamiltonian) using Kwant.
 
 		\begin{figure}[!htb]
-\includegraphics[width=0.95\columnwidth]{figures/zigzag.pdf}
-\caption{Setups. Figure of a straight and zigzag system, including trajectories.
-\label{fig:setup}}
+		\includegraphics[width=0.95\columnwidth]{figures/bandstructures}
+		\caption{Figure of the bandstuctures.
+		Where the lines are (blue) $\phi=0$, $B=0$ and (red) $\phi=\pi$, $B \ne 0$.
+		and the subplots (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W$ is the junction width.
+		We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
+		\label{fig:bandstuctures}}
 		\end{figure}
-
-%%██████████████████████████████████████████████████████████████████████████
-%%██ Calculating the bandstuctures
-%%██████████████████████████████████████████████████████████████████████████
-\section{Calculating the bandstuctures.}
-
-\comment{We discretize the model described in section II and simulate it with Kwant.}
-We implement a tightbinding version of the model described in section II (a two dimensional SNS junction with a Rashba BdG Hamiltonian) using Kwant.
 
@@
 
-%%██████████████████████████████████████████████████████████████████████████
-%%██ Calculating the topological phase diagram
-%%██████████████████████████████████████████████████████████████████████████
-\section{Calculating the topological phase diagram.}
-
-\comment{We calculate the topological phase diagram using the gap size.}
-We calculate the gap from the bandstructure (minimum energy in the spectrum) using the same method described in comment III.
-Noting the gap closings and the fact we know the topology for the non-zigzag system, we can infer the topology of the system with zigzag modulation.
-
-\comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry. }
-Similar to what is described in Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond like structure as a function of phase and Zeeman field.
-We also see some additional gap closings which are due to the BDI symmetry class, creating quite an unstable region.
-As expected, for the zigzag system, the magnitude of the gap is significantly improved, whilst maintaining the diamond like shape.
-As the zigzag shape destroys the additional symmetry, moving it to class D, we see a more clean topological region.
-
-\begin{figure}[!htb]
-\includegraphics[width=0.95\columnwidth]{figures/bandstructures}
-\caption{Figure of the bandstuctures.
-Where the lines are (blue) $\phi=0$, $B=0$ and (red) $\phi=\pi$, $B \ne 0$.
-and the subplots (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W$ is the junction width.
-We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
-\label{fig:bandstuctures}}
-\end{figure}
-
-\begin{figure}[!htb]
-\includegraphics[width=0.95\columnwidth]{figures/phasediagrams}
-\caption{Phase diagrams of a straight system (a, b) and zigzag system (c, d), where (a, c) are $E(\mu, B)$ and (b, d) are $E(\phi, B)$.
-We use a generalized eigenvalue problem to find all phase boundaries at once and find the minimal energy gap by finding the minimum in the spectrum: $\min{E(k)}$.
-\label{fig:phasediagrams}}
-\end{figure}
-
-%%██████████████████████████████████████████████████████████████████████████
-%%██ Analytical estimate
-%%██████████████████████████████████████████████████████████████████████████
-\section{Analytical estimate of the band gap}
-
-\comment{To compute the effect of cutoff consider a single segment of the zigzag and obtain the spectrum analytically (this allows to use translation invariance).}
-We establish that the cutoff of long trajectories is the driving mechanism behind the order of magnitude gap improvement using an analytical approach.
-We derive the Andreev spectrum for a single (diagonal) segment of the zigzag, and define the gap of the system as the minimum of the spectrum occurring before the cutoff corresponding to the particular geometry.
-The system under consideration is thus a ribbon SNS junction with tilted magnetic field.
-
-\comment{The definition of the cutoff... }
-
-\comment{We use a short junction approximation and neglect transverse SO.}
-We derive the spectrum by calculating the scattering matrix for the normal region and applying the Andreev bound state condition for the short junction limit\cite{beenakker1991universal, sticlet_robustness_2017}.
-For deriviation of the scattering matrix, we neglect SOI in the transverse direction, which is valid for $W<l_\text{so}$.
-The result is specified in Eqs.~\eqref{eq:smatrix} to~\eqref{eq:momenta_short_junction}.
-
-\begin{align}
-\label{eq:smatrix}
-    S &= \left(
-    \begin{array}{rr}
-    r_{ll}&t_{rl}\\
-    t_{lr}&r_{rr}\\
-    \end{array}
-    \right) =
-    \left(
-    \begin{array}{rr}
-    \beta_+ & e^{-i q W} \beta_-\\
-    e^{-i q W} \beta_- & e^{-2 i q W} \beta_+\\
-    \end{array}
-    \right)
-    \\
-    \beta_\pm &= \left(
-    \begin{array}{rr}
-    e^{i \nu_{\arg}}\left(\omega^\pm_1 - \omega^\pm_2\right) & (\omega^\pm _1 + \omega^\pm _2)\\
-    -(\omega^\pm _1 + \omega^\pm _2) & e^{-i \nu _{\arg }} \left(\omega^\pm _2 - \omega^\pm _1\right)\\
-    \end{array}
-    \right)\\
-    \omega^\pm_j &= \frac{1}{4} \left(\gamma _{j} \pm \delta _{j}\right)
-\end{align}
-
-\begin{align}
-    \gamma_j &= \frac{q+i k_{j} \tan \left(\frac{W k_{j}}{2}\right)}{q-i k_{j} \tan \left(\frac{W k_{j}}{2}\right)} \\
-    \delta_j &= \frac{q-i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}{q+i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}\\
-    e^{i \nu_{\arg}} &= \frac{E_\text{z} e^{i \theta }-i \alpha  k_x}{\sqrt{E_\text{z}^2+\alpha  k_x \left(\alpha  k_x-2 E_\text{z} \sin (\theta )\right)}}
-\end{align}
-
-\begin{footnotesize}
-\begin{align}
-    q &= \left[ \frac{2 m_\ast}{\hbar ^2}\mu_s - k_x^2 \right]^\frac{1}{2}\\
-    k_1 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n-\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}\\
-    k_2 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n+\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}
-\label{eq:momenta_short_junction}
-\end{align}
-\end{footnotesize}
-
-In order to get the spectrum from the S-matrix [Eq.~\eqref{eq:smatrix}] we use the main result from Ref.~\onlinecite{beenakker1991universal} and start with a determinantal equation for the bound state energies in a SNS-junction:
-
-\begin{equation}
-\det\left[1+\alpha^{2}\left(E\right)r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)\right]=0
-\end{equation}
-
-We rewrite this as a characteristic polynomial problem $\det\left[A-\lambda I\right]=0$, as
-
-\begin{equation}
-\det\left[r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)-\frac{-1}{\alpha^{2}\left(E\right)}I\right]=0
-\end{equation}
-
-with
-\begin{equation}
-\lambda=-\frac{1}{\alpha^{2}\left(E\right)},\;A=r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right).
-\end{equation}
-
-Where $\lambda_i$ are the eigenvalues of $A$.
-Inverting $\alpha\left(E\right)\equiv\exp\left(-i\arccos\left(E/\Delta\right)\right)$ yields $\frac{E}{\Delta}=\frac{\alpha^{2}+1}{2\alpha}=\frac{1}{2}\left(\alpha+\alpha^{-1}\right)=\textrm{Re}(\alpha)$, where the last equality holds because $\alpha$ is unitary.
-Then, since $\alpha$ is only defined in the positive imaginary plane, the energies are $\frac{E_{i}}{\Delta}=\textrm{Re}\left(\sqrt{-1/\lambda_{i}}\right)$ where we take the root which has a positive imaginary part.
-Using this result and Eq.~\eqref{eq:smatrix}, we numerically find the Andreev spectrum.
-
-\comment{The lowest energy at $|k| < k_\textrm{cutoff}$ sets the band gap.}
-We cut off the spectrum at the momentum corresponding to the proposed cutoff in the zigzag, and compare it to the numerically obtained gap for a true zigzag system.
-
-%%██████████████████████████████████████████████████████████████████████████
-%%██ Localization lengths and shape effect
-%%██████████████████████████████████████████████████████████████████████████
-\section{Localization lengths and shape effects}
-
+	\comment{Introduction of a zigzag leads to localization of the Majorana's}
+	\section{Majorana decay length}
 		\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag.}
@@
 
-%%██████████████████████████████████████████████████████████████████████████
-%%██ Discussion and Conclusions
-%%██████████████████████████████████████████████████████████████████████████
-\section{Discussion and Conclusions}
+	\comment{Zigzag Majorana's have a cleaner phase diagram due to the reduction in symmetry class}
+	\section{Phase diagram}
+		\comment{We calculate the topological phase diagram using the gap size.}
+		We calculate the gap by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{|E(k)|}$.
+		Noting the gap closings and the fact we know the topology for the non-zigzag system, we can infer the topology of the system with zigzag modulation. % Bas: I don't understand what is written here
 
-\comment{The zigzag geometry is a useful tool in hardening the gap and decreasing majorana length, now experimental verification necessary}
-The introduction of a zigzag geometry increases the topological gap by over an order of magnitude, as well as offering a substantial reduction of the Majorana length.
-Additionally, the breaking of BDI symmetry into D symmetry results in a cleaner topological region.
+		\comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry. }
+		Similar to what is described by Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond like structure as a function of phase and Zeeman field.
+		We also see some additional gap closings which are due to the BDI symmetry class, creating quite an unstable region.
+		As expected, for the zigzag system, the magnitude of the gap is significantly improved, whilst maintaining the diamond like shape.
+		As the zigzag shape destroys the additional symmetry, moving it to class D, we see a more clean topological region.
 
-\comment{Current fabrication techniques seem compatible with the proposed geometry, and experimental verification should point out whether it holds up to its promise.}
-Current fabrication techniques seem compatible with the proposed geometry; zigzag devices have already been created.
-Slight modifications to the geometry, for example to ease measurement, should not have large implications on the physics.
+		\begin{figure}[!htb]
+		\includegraphics[width=0.95\columnwidth]{figures/phasediagrams}
+		\caption{Phase diagrams of a straight system (a, b) and zigzag system (c, d), where (a, c) are $E(\mu, B)$ and (b, d) are $E(\phi, B)$.
+		We use a generalized eigenvalue problem to find all phase boundaries at once and find the minimal energy gap by finding the minimum in the spectrum: $\min{E(k)}$.
+		\label{fig:phasediagrams}}
+		\end{figure}
 
-\comment{It would be interesting to study what geometry creates an optimal environment for Majorana modes to exist.}
-We have studied sawtooth, snake like and offset sinosoid modulation of the semicondctor region, but perhaps a more exotic shape will be optimal.
-A study optimizing the geometry for supporting Majorana's would be an interesting continuation.
-
-\comment{Extensions: we omit several physical effects, disorder, electrostatics, etc.}
-We omit several physical effects, such as: disorder, electrostatics, the orbital effect, etc..
-Further study, as well as experimental verification, are required to see whether the conclusions of this model are valid for the real case.
-
-\comment{Acknowledgments}
-
-We are grateful to "people" for useful discussions.
-This work was supported by the Netherlands Organization for Scientific Research (NWO/OCW), as part of the Frontiers of Nanoscience program, the Foundation for Fundamental Research on Matter (FOM), and an ERC Starting Grant STATOPINS 638760.
-
-\bibliographystyle{apsrev4-1}
-\bibliography{snakemajoranas}
-\end{document}
+	\comment{We use our analytical bandstructure to }
+	\section{Analytical estimate}

### 2019-01-10 thesis_report/theory.tex
Updated thesis

@@
 
-% Momentum operators
-\newcommand{\kx}{k_x}
-\newcommand{\ky}{k_y}
-
-% Pauli matrices
-\newcommand{\sigx}{\sigma_x}
-\newcommand{\sigy}{\sigma_y}
-\newcommand{\sigz}{\sigma_z}
-\newcommand{\sigi}{\sigma_0}
-\newcommand{\taux}{\tau_x}
-\newcommand{\tauy}{\tau_y}
-\newcommand{\tauz}{\tau_z}
-\newcommand{\taui}{\tau_0}
 \chapter{Theory}
@@
 \section{General Physics}
-	\subsection{Boguliubov de Gennes Hamiltonian}
+
+    \subsection{Zeeman interaction}
+    	The energy splitting of the two electron spin species due to magnetic field is called the Zeeman interaction.
+    	It is modeled by:
+    	\begin{equation}
+    	H_\text{Z} = g \mu_B \vec{B} \cdot \vec{\sigma}
+    	\end{equation}
 
     \subsection{Spin-orbit coupling}
-    Rashba spin orbit coupling:
+	    An electron mvoing in an electric field will experience a small Zeeman field in its inertial frame as a relativistic effect~\cite{petersen_simple_2000}.
+	    The resulting interaction is known as spin orbit coupling.
+	    Spin-orbit coupling can be approximated with adding a Rashba spin orbit coupling term in the Hamiltonian:
 	    \begin{equation}
@@
 
-    \subsection{Supercurrent}
-	The current
+    \subsection{Superconductivity}
+		Superconductivity manifests itself as the complete lack of electrical resistance of a material.
+		It is the result of the pairing of electrons close to the Fermi-energy, condensing into so-called Cooper pairs.
+		Because all electrons within a distance of the superconducting order parameter of the Fermi-energy are depleted in this way, charge transport only takes place via these quasiparticles.
+		Scattering of these Cooper pairs is not allowed, resulting in perfect conduction.
 
-	\subsection{Tight binding}
+		For the purpose of creating Majorana's, we are interested in two main aspects of superconductivity: the energy gap surrounding the Fermi energy (due to the depletion of states), and the electron-hole (/particle-hole) symmetry.
+		We are thus not interested in the paired up electrons (Cooper pairs), and only wish to model the electronic (unpaired) modes.
+		This can be achieved by modeling superconductivity with the Boguliubov de Gennes Hamiltonian:
 
+		\begin{equation}
+		\mathbf{H}_\text{BdG} = \begin{bmatrix} H & \Delta \\ \Delta^\dagger & H \end{bmatrix}
+		\end{equation}
+
+		The block matrix restricts the structure of the system in the electron-hole basis, and ensures particle-hole symmetry.
+		For $\Delta \neq 0$ one indeed induces a identically sized gap in the spectrum.
+
+		\subsubsection{Andreev scattering}
+			At the interface between a normal and superconducting region, electrons with energies below the superconducting gap undergo Andreev scattering.
+			The quasiclassical microscopic explanation for this is as follows.
+			An electron in the normal region with energy below the superconducting gap, incident on the normal-superconductor (NS) interface, is retro-reflected as a hole.
+			This phenomenon is known as Andreev scattering, and occurs due to the coupling of electrons in a superconductor.
+			Although a single electron initially enters the superconductor, it draws another electron (with opposite momentum) into the superconductor: forming a Cooper pair.
+			The drawn in electron leaves behind a hole in the normal conductor, which essentially backtracks the motion of the initial electron, hence the term retro-reflection.
+			The same effect, but opposite in particle type, holds for a hole entering the superconductor.
+
+		\subsubsection{Josephson junctions and supercurrent}
+
+\section{Topology and Majorana bound states}
 	\subsection{Topology in solid state physics}
@@
 
-\section{Majorana bound states}
 	\subsection{General properties}
@@
 	\subsection{Thouless energy}
+	\subsection{Transparency at NS interface}
 

### 2019-01-11 thesis_report/theory.tex
Updated theory

@@
 		It is the result of the pairing of electrons close to the Fermi-energy, condensing into so-called Cooper pairs.
+		The main parameter defining superconductivity is known as the superconducting order parameter, a complex number.
+		The phase of this parameter is a macroscopic potential relative to ones choice of gauge.
+		The magnitude of the superconducting order parameter, also referred to as the superconducting gap, quantifies the range around the Fermi-energy condensed into Cooper pairs.
 		Because all electrons within a distance of the superconducting order parameter of the Fermi-energy are depleted in this way, charge transport only takes place via these quasiparticles.
@@
 
-		\subsubsection{Andreev scattering}
+		\subsubsection{Andreev scattering and bound states}
 			At the interface between a normal and superconducting region, electrons with energies below the superconducting gap undergo Andreev scattering.
@@
 
-		\subsubsection{Josephson junctions and supercurrent}
+		\subsubsection{Josephson junctions, Andreev bound states, and supercurrent}
+			An important device in the field of condensed matter physics is the Josephson junction.
+			A Josephson junction consists of a normal region sandwhiched in between two superconductors (SNS junction).
+			Electrons within the normal region, with energies below the superconducting gap, experience Andreev scattering from both superconductors.
+			The eigen modes of the sandwiched system, with energies below the gap, are known as Andreev bound states.
+			It is these Andreev bound states which exhibit interesting physics, and make the Josephson junction such an important device.
+
+			Although superconducting phase is relative to the choice of gauge, the difference of phase between two superconductors is in fact a physical quantity.
+			A difference in superconducting phase results in a flow of current from one superconductor to the other, known as a supercurrent.
+			The relationship between superconducting phase and current is known as the current-phase relationship, and is in the most simple case a sinosoid.
+			This relationship is exploited by experimentalist to control the phase difference between the two superconductors.
+			The amplitude of the current variation due to variation of phase is known as the critical current, and is the relatively trivial physical quantity to measure.
+
+			Josephson junctions are relevant to this thesis as the primary device studied is a Josephson junction itself.
 
 \section{Topology and Majorana bound states}
-	\subsection{Topology in solid state physics}
+
 	The Wikipedia definition of mathematical topology is as follows:
 
-	\quote{Topology can be formally defined as "the study of qualitative properties of certain objects (called topological spaces) that are invariant under a certain kind of transformation}\cite{noauthor_topology_2018}
+	\begin{quote}Topology can be formally defined as "the study of qualitative properties of certain objects (called topological spaces) that are invariant under a certain kind of transformation
+	\cite{noauthor_topology_2018}
+	\end{quote}
 
-		\subsubsection{Symmetries}
+	Similarly, in condensed matter physics, topology refers to the study of properties of a system, which do not change within a particular range of parameters.
+	Topology is relevant to the context of the system under study, because the emergence of seperated Majorana's is guaranteed within a continuous range of parameters.
+	The precense of Majorana's is therefore \emph{topologically protected}, as they will be unpurturbed by variations of parameters, within a certain range.
+	For an infinite system, the system is said to be topological if Majorana's would emerge if the system is cut to finite length.
+	The system is trivial if the converse is true.
 
-	\subsection{General properties}
-	\subsection{Decay length}
+	\subsection{Majorana bound states}
+		In the context of condensed matter physics, Majorana
+
+	\subsection{Decay/Coherence length}
+		The decay or coherence length of a Majorana pair is an important measure signifying the seperation of the two half-particles.
+		A decay length larger or of equal size to the system dimensions will lead to overlap of the Majorana's, diminishing the desired robustness of the state.
+
 	\subsection{Topological gap}
+		The topological gap is defined as the energy gap between the Majorana state -- conveniently located at zero energy -- and the first available state.
+		It's magnitude governs the protection of the system against perturbations causing the system to be lifted out of its ground state: the Majorana state.
 
 \section{Two dimensional platform for Majoranas}
+
 	\subsection{Phase diagram}
+
 	\subsection{Current phase relationship}
+
 	\subsection{Thouless energy}
 	\subsection{Transparency at NS interface}
-
-\section{Scattering matrix formalism}

### 2019-01-14 thesis_report/preface.tex
Updated thesis

% -*- root: ./report.tex -*-
\chapter*{Preface}
\setheader{Preface}

Preface\ldots

\begin{flushright}
{\makeatletter\itshape
    \@author \\
    Delft, January 2013
\makeatother}
\end{flushright}

### 2019-01-14 thesis_report/theory.tex
Updated thesis

@@
-% UNCOMMENT SO YOU CAN LINK PAPERS EASILY WITH SUBLIME TEXT
-% \bibliography{report}
+% -*- root: ./report.tex -*-
 
@@
 \section{General Physics}
+	We give a brief description of the interactions and physics present in the system under study.
 
@@
 
+		\subsubsection{Thouless energy}
+
 \section{Topology and Majorana bound states}
@@
 	\subsection{Majorana bound states}
-		In the context of condensed matter physics, Majorana
+		We will give a very pragmatic description of Majorana bound states, insofar their relevance to this work.
+
+		The Majorana state is a superposition of electrons and holes, and is its own anti-particle: exchanging electrons and holes yields the same state.
+		The Majorana state carries no spin, charge, or energy, giving almost no degrees of freedom for it to interact with the environment.
+		The Majorana state constitutes a single fermion, but is comprised of two Majorana's.
+		In a finite, topological system, these two Majorana's are physically seperated, appearing at the edges.
+
+		The lack of interaction, as well as the physical seperation of the state, makes it very robust against perturbations, but also difficult to detect.
+		Luckily, the state's presence itself is measurable: the availability of a state contributes to the conduction at that energy.
+		When measuring the conduction through a system with Majorana's present, one should thus encounter a rise in the conductance at zero energy: the zero bias peak.
 
@@
 		A decay length larger or of equal size to the system dimensions will lead to overlap of the Majorana's, diminishing the desired robustness of the state.
+		An overlap of the Majorana's will in fact lead to the system having a non-zero energy, its magnitude depending on the amount of overlap.
+		A crude estimation of the size of an individual Majorana is:
+		\begin{equation}
+			\xi = \hbar \frac{v_\text{F}}{\Delta}
+		\end{equation}
 
@@
 
+	\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.5\columnwidth]{figures/pientka_system}
+	\caption{System overview. Source\cite{pientka_topological_2017}}
+	\label{fig:pientka_system}
+	\end{figure}
+
+	The earliest devices used to create a seperated pair of Majorana's were nanowires deposited onto a slab of superconducting material.
+	A relatively new proposal is that of creating Majorana's in a planar Josephson junction~\cite{pientka_topological_2017}.
+	An advantage of this system is that the phase difference between the superconductors can be used as a knob to switch the system from the topological state to the trivial state. 
+	In addition, the presence of the second superconductor increases the topological gap of the system due to the proximity effect.
+
 	\subsection{Phase diagram}
+	As mentioned, the superconducting phase difference plays a critical role in the physics of the device.
+	The topological phase diagram, as a function of magnetic field and superconducting phase, is depicted in Fig. \ref{fig:pientka_phase_diagram}.
+	Without normal reflection (perfect Andreev reflection), the diagram has a diamond-like shape.
+	The system is always topological when the superconducting phase is $pi$, or when the magnetic field is tuned to $(2N-1)$ times the Thouless energy (With exception of the corners of the diamonds).
+
+	\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.5\columnwidth]{figures/pientka_phase_diagram}
+	\caption{Phase vs. Magnetic field. Source\cite{pientka_topological_2017}}
+	\label{fig:pientka_phase_diagram}
+	\end{figure}
 
@@
 
-	\subsection{Thouless energy}
 	\subsection{Transparency at NS interface}

### 2019-01-14 thesis_report/theory.tex
Start of new structure for theory

@@
 \chapter{Theory}
+The topological quantum computer uses pairs of Majorana particles as its unit of computation (qubit).
+In order to host Majorana modes in a system, one needs a material which has properties from a superconducting material, as well as from a semi-conducting material.
+As this material does not seem to exist on its own, one creates a heterogeneous system.
+I simple terms, this consists of a slab of superconductor and a strip of semiconductor.
+By interfacing the two, one creates a region where all the necessary ingredients are present to realize Majorana's.
+
+In this chapter, we first give a description of the normal (semi-conductor) and superconducting regions.
+We then focus on what happens in a system where the two are interfaced.
+Following that, we briefly explain what Majorana are, before introducing the implementation mainly relevant to this thesis.
 
 \section{General Physics}
-	We give a brief description of the interactions and physics present in the system under study.
 
@@
     \subsection{Spin-orbit coupling}
-	    An electron mvoing in an electric field will experience a small Zeeman field in its inertial frame as a relativistic effect~\cite{petersen_simple_2000}.
+	    An electron moving in an electric field will experience a small Zeeman field in its inertial frame as a relativistic effect~\cite{petersen_simple_2000}.
 	    The resulting interaction is known as spin orbit coupling.
@@
 
-	\subsection{Current phase relationship}
-
 	\subsection{Transparency at NS interface}

### 2019-01-15 thesis_report/theory.tex
Updated theory and added sns bandstructure plot to thesis figures

@@
 
-\section{General Physics}
+\section{Normal region}
+	Two important ingredients required for realizing Majorana fermions are strong spin-orbit coupling, and a strong interaction with the applied magnetic field.
+	It is the normal conductor which brings these two physical effects to the mix.
+	Note that the Hamiltonian of the normal region is the same for electrons and holes, except for the sign.
+	The Hamiltonian terms provided in this section are relevant to the electron states.
 
@@
 	    An electron moving in an electric field will experience a small Zeeman field in its inertial frame as a relativistic effect~\cite{petersen_simple_2000}.
-	    The resulting interaction is known as spin orbit coupling.
-	    Spin-orbit coupling can be approximated with adding a Rashba spin orbit coupling term in the Hamiltonian:
+	    The resulting interaction, coupling the momentum and spin of electron, is known as spin orbit coupling.
+	    Spin-orbit coupling can be approximated by adding a Rashba spin orbit coupling term in the Hamiltonian:
 	    \begin{equation}
@@
 	    \end{equation}
+
+\section{Superconducting region}
+    The superconductor is responsible for ensuring particle-hole symmetry, as well as providing a `gapped' area in the bandstructure, isolating the zero-energy state.
+    Superconductivity is a very complicated phenomenon, so we again provide only the background required for the understanding of this work.
 
@@
 
-		\subsubsection{Andreev scattering and bound states}
+\section{Normal-superconducting junctions}
+	As mentioned, the interesting physics occur when a normal conductor is interfaced with a superconductor.
+	A single interface between a normal conductor and a superconductor is known as a NS junction.
+	When one creates a sandwich, superconductor - normal - superconducting, we speak of a SNS junction.
+	Even not considering topological phases, which are only present if the normal regions meets certain conditions, both have interesting physics which will be discussed first.
+
+	\subsection{Andreev scattering}
 		At the interface between a normal and superconducting region, electrons with energies below the superconducting gap undergo Andreev scattering.
@@
 
-		\subsubsection{Josephson junctions, Andreev bound states, and supercurrent}
+	\subsection{Andreev bound states}
+		If the normal region is finite in the direction normal to the NS/SN interface, Andreev bound states form.
+		This is true for both SNS and SN junctions.
+		Quasiclassically, one can imagine electrons (and holes) in the normal region, with energies below the gap, bouncing back and forth the system.
+		The corresponding eigenstates have energies below the gap, and are thus bound to the normal region.
+
+	\subsection{Josephson junctions and supercurrent}
 		An important device in the field of condensed matter physics is the Josephson junction.
-			A Josephson junction consists of a normal region sandwhiched in between two superconductors (SNS junction).
-			Electrons within the normal region, with energies below the superconducting gap, experience Andreev scattering from both superconductors.
-			The eigen modes of the sandwiched system, with energies below the gap, are known as Andreev bound states.
-			It is these Andreev bound states which exhibit interesting physics, and make the Josephson junction such an important device.
+		A Josephson junction consists of a normal region sandwiched in between two superconductors (SNS junction).
+		The resulting Andreev bound states exhibit interesting physics, making the Josephson junction an important device.
 
 		Although superconducting phase is relative to the choice of gauge, the difference of phase between two superconductors is in fact a physical quantity.
-			A difference in superconducting phase results in a flow of current from one superconductor to the other, known as a supercurrent.
+		A difference in superconducting phase in a Josephson junction, results in a flow of current between the two superconductors: a supercurrent.
 		The relationship between superconducting phase and current is known as the current-phase relationship, and is in the most simple case a sinosoid.
-			This relationship is exploited by experimentalist to control the phase difference between the two superconductors.
-			The amplitude of the current variation due to variation of phase is known as the critical current, and is the relatively trivial physical quantity to measure.
+		This relationship can be exploited to control the phase difference: it is a matter of inducing a current.
 
-			Josephson junctions are relevant to this thesis as the primary device studied is a Josephson junction itself.
-
-		\subsubsection{Thouless energy}
+		An important measure in a Josephson junction is the Thouless energy.
+		In the context of this work, the Thouless energy is inversely proportional to the travel time of an electron in a system, without interacting with the superconductor(s).
+		As an example of its relevance, in a SNS junction with magnetic field, if the Zeeman field has an energy comparable to the Thouless energy, as the electron traverses the system from supercondcutor to superconductor, the spin will be flipped.
 
@@
 
-	\subsection{Transparency at NS interface}
+	\subsection{Bandstructure of a typical system}

### 2019-01-15 thesis_report/methods.tex
Updated thesis
Updated methods, and figure of scattering matrix basis

@@
+% -*- root: ./report.tex -*-
 \chapter{Methods}
-% UNCOMMENT TO USE LaTeXing autocomplete for refereces
-% \bibliography{report}
 
@@
 		\subsubsection{Derivation of the scattering matrix}
-			We consider the scattering problem defined by Fig. \ref{fig:scattering}, the corresponding system of equations given in Eq. \eqref{eq:scattering_matrix_problem}, and
-			continuity and flux conservation(continuity of first derivative) at the normal-superconductor interfaces.
-			The Hamiltonians of the respective regions are given by Eqs. \eqref{eq:ham_smat_normal,eq:ham_smat_superconducting}.
-			The Hamiltonian of the superconducting region does not include the superconducting term because we implement Andreev reflection seperately: this way we halve the dimensionality of the problem.
+
+			\begin{figure}[!htb]
+			\includegraphics[width=0.95\columnwidth]{images/scattering}
+			\caption{Basis for scattering matrix. 
+			The `S' region corresponds to the superconductor Hamiltonian without the superconducting term, Eq.~\eqref{eq:ham_smat_superconducting}, `N' to the normal region, Eq.~\eqref{eq:ham_smat_normal}. 
+			The coefficients represent the amplitude of the modes present in the system, at a particular energy.
+			The different color arrows correspond to the two different spinors in each region.
+			For example, $a_{1,L}$ is the amplitude of the rightmoving incoming mode, $\vec{\psi}_1 \exp\left(i k_{1,L} x\right)$}
+			\label{fig:scattering}
+			\end{figure}
+
+			\begin{align}
+			H_\text{N} &= \left[ \frac{\hbar^2}{2 \meff} \left(\kx^2 + \ky^2\right) -\mu_n\right]\sigi +
+						 \alpha \kx \sigy +
+						 E_z \left[ \cos(\theta) \sigx + \sin(\theta) \sigy \right]
+			\label{eq:ham_smat_normal} \\
+			H_\text{S} &= \left[\frac{\hbar^2}{2 \meff} \left(\kx^2 + \ky^2\right) -\mu_s\right]\sigi
+			\label{eq:ham_smat_superconducting}
+			\end{align}
+
+			We consider the scattering region as depicted in Fig. \ref{fig:scattering}.
+			There are three regions in the system, one normal system (N), with Hamiltonian given by Eq.~\eqref{eq:ham_smat_superconducting}, and two superconducting regions (S), with Hamiltonian given by Eq.~\eqref{eq:ham_smat_superconducting}.
+			Not that Eq.~\eqref{eq:ham_smat_superconducting} region does not include the superconducting term ($\Delta \tau_y$), because we implement Andreev reflection seperately: this way we avoid doubling (electron and hole) the dimensionality of the problem.
+			We set the energy of the system, and find the planar waves propogating in each region.
+			Because the plane waves can go in two directions, and the additional degree of freedom introduced due to spin, each region has four propogating waves.
+			The idea of the scattering matrix is to set the vector $\vec{a}$, containing the amplitudes of the planar waves coming in to the scattering region, and find the amplitudes of the modes exiting the scattering region.
+			This is captured by a system of linear equations, displayed in Eq.~\eqref{eq:scattering_matrix_problem}
 
@@
 			\end{bmatrix} 
-			= S_\text{sns} \cdot 
+			= S_\text{sns}(\epsilon) \cdot 
 			\begin{bmatrix} 
@@
 
+			In order to find the coefficients of the matrix $S_\text{sns}(\epsilon)$, we take the wavefunction $u(x)$ and apply the boundary equations (continuity and flux conservation): specified in Eqs.~\eqref{eq:scattering_equations} through \eqref{eq:scattering_boundary_eqs}.
+			Note that because we neglect spin-orbit coupling in the x-direction, the velocity operator $\hat{\mathbf{v}}$ can be simplified to the first derivative.
+			Although omitted to keep the expression compact, the momenta $k_i, q$ and spinors $\vec{\Psi_{i, L/R}}$ are energy dependent.
+
 			\begin{align}
-			H_\text{N} &= \left[ \frac{\hbar^2}{2 \meff} \left(\kx^2 + \ky^2\right) -\mu_n\right]\sigi +
-						 \alpha \kx \sigy +
-						 E_z \left[ \cos(\theta) \sigx + \sin(\theta) \sigy \right]
-			\label{eq:ham_smat_normal} 
-			\\
-			H_\text{S} &= \left[\frac{\hbar^2}{2 \meff} \left(\kx^2 + \ky^2\right) -\mu_s\right]\sigi
-			\label{eq:ham_smat_superconducting}
+				&u(x) = 
+				\begin{cases}
+				u_L(x) = a_{1,L} \vec{\Psi} _{s,1} \exp (i q y) + a_{2,L} \vec{\Psi} _{s,2} \exp (i q y) + b_{1,L} \vec{\Psi} _{s,1} \exp (-i q y) + b_{2,L} \vec{\Psi} _{s,2} \exp (-i q y)  & x \leq 0\\
+				u_m(x) = d_{1,l} \vec{\Psi} _{n,1} \exp \left(-i k_1 y\right) + d_{1,r} \vec{\Psi} _{n,1} \exp \left(i k_1 y\right) + d_{2,l} \vec{\Psi} _{n,2} \exp \left(-i k_2 y\right) + d_{2,r} \vec{\Psi} _{n,2} \exp \left(i k_2 y\right)  & 0 \geq x \leq W\\
+				u_R(x) = a_{1,R} \vec{\Psi} _{s,1} \exp (-i q y) + a_{2,R} \vec{\Psi} _{s,2} \exp (-i q y) + b_{1,R} \vec{\Psi} _{s,1} \exp (i q y) + b_{2,R} \vec{\Psi} _{s,2} \exp (i q y)  & W \geq x
+				\end{cases}
+				\label{eq:scattering_equations}
 			\end{align}
 
-			\begin{figure}[!htb]
-			\includegraphics[width=0.95\columnwidth]{images/scattering}
-			\caption{Basis for scattering matrix. `S' region corresponds to the superconductor Hamiltonian without the superconducting term.}
-			\label{fig:scattering}
-			\end{figure}
+			Where $a_{i, L/R}$ are the coefficients of the incoming modes, $b_{i, L/R}$ are those of the outgoing modes, and $d_{i, l/r}$ are the modes in the middle region: see Fig.\ref{fig:scattering}.
+			The symbols $\vec{\Psi}_{n/s, i}$ and $k_i, q$ are respectively the spinors and corresponding momenta belonging to each region.
+			Both are energy dependent.\\
 
-			The resulting scattering matrix:
+			The boundary conditions are,
+			\begin{align}
+				& u(x) \text{ is continuous}\\
+				&\hat{\mathbf{v}} u(x) \text{ is continuous, where $\hat{\mathbf{v}}$ is the velocity operator}\label{eq:scattering_boundary_eqs}
+			\end{align}
 
+			To solve the system analytically, we use the Short Junction limit: we set the energy to zero.
+			By applying the boundary conditions and solving the resulting linear system of equations, the resulting solution is given by Eqs.~\eqref{eq:smatrix} through ~\eqref{eq:momenta_short_junction}.\\
+
+			Scattering matrix, in block matrix format:
 			\begin{align}
@@
 
+			Subexpressions:
 			\begin{align}
@@
 
-			\begin{footnotesize}
+			Momenta:
 			\begin{align}
@@
 			\end{align}
-			\end{footnotesize}
 

### 2019-01-15 thesis_report/methods.tex
Cleaned up spectrum calculation: it is near completion

@@
 
-		\comment{We use a short junction approximation and neglect transverse SO.}
 		We derive the spectrum by calculating the scattering matrix for the normal region and applying the Andreev bound state condition for the short junction limit\cite{beenakker1991universal, sticlet_robustness_2017}.
+		The short junction limit is valid for [TODO: WHEN IS THE SHORT JUNCTION LIMIT VALID]
 		For deriviation of the scattering matrix, we neglect SOI in the transverse direction, which is valid for $W<l_\text{so}$.
-		The result is specified in Eqs.~\eqref{eq:smatrix} to~\eqref{eq:momenta_short_junction}.
-
-		In order to get the spectrum from the S-matrix [Eq.~\eqref{eq:smatrix}] we use the main result from Ref.~\cite{beenakker1991universal} and start with a determinantal equation for the bound state energies in a SNS-junction:
-
-		\begin{equation}
-		\det\left[1+\alpha^{2}\left(E\right)r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)\right]=0
-		\end{equation}
-
-		We rewrite this as a characteristic polynomial problem $\det\left[A-\lambda I\right]=0$, as
-
-		\begin{equation}
-		\det\left[r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)-\frac{-1}{\alpha^{2}\left(E\right)}I\right]=0
-		\end{equation}
-
-		with
-		\begin{equation}
-		\lambda=-\frac{1}{\alpha^{2}\left(E\right)},\;A=r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right).
-		\end{equation}
-
-		Where $\lambda_i$ are the eigenvalues of $A$.
-		Inverting $\alpha\left(E\right)\equiv\exp\left(-i\arccos\left(E/\Delta\right)\right)$ yields $\frac{E}{\Delta}=\frac{\alpha^{2}+1}{2\alpha}=\frac{1}{2}\left(\alpha+\alpha^{-1}\right)=\textrm{Re}(\alpha)$, where the last equality holds because $\alpha$ is unitary.
-		Then, since $\alpha$ is only defined in the positive imaginary plane, the energies are $\frac{E_{i}}{\Delta}=\textrm{Re}\left(\sqrt{-1/\lambda_{i}}\right)$ where we take the root which has a positive imaginary part.
-		Using this result and Eq.~\eqref{eq:smatrix}, we numerically find the Andreev spectrum.
 
@@
 			To solve the system analytically, we use the Short Junction limit: we set the energy to zero.
-			By applying the boundary conditions and solving the resulting linear system of equations, the resulting solution is given by Eqs.~\eqref{eq:smatrix} through ~\eqref{eq:momenta_short_junction}.\\
+			By applying the boundary conditions and solving the resulting linear system of equations, the resulting solution is given by Eqs.~\eqref{eq:smatrix} through ~\eqref{eq:momenta_short_junction}.
+			\emph{Important note: In order to use the Andreev bound state condition, the scattering matrix must be in the [TODO: NAME OF BASIS] basis.
+This basis transformation has already been applied in Eqs.
+~\eqref{eq:smatrix} through ~\eqref{eq:momenta_short_junction}}\\
 

### 2019-01-16 thesis_report/methods.tex
updated methods

@@
 	\subsection{Eliminating long trajectories}
-		\comment{We devise two different ways to define the cutoff of momentum.}
 
@@
 
+		\comment{We make an analogy between the cutoff of long trajectories to the cutoff of high momenta.}
+		We hypothesize that the increase of the topological gap in a zigzag is due to the cutoff of long trajectories.
+		In order to make substantiate that this is indeed the driving mechanism behind the improvement, we propose an analogy using the bandstructure of a regular SNS junction.
+
+		\comment{We map the zigzag to an infinite SNS junction with tilted magnetic field and a range of forbidden momenta.}
+		We essentially take a single diagonal section of a zigzag, and map it to a normal, infinite SNS junction.
+		The new coordinate system is depicted by the set of axes with $x^\prime$ and $y^\prime$ in Fig.~\ref{fig:setup}.
+		Note that the magnetic field has an angle $\theta$ with respect to the $x^\prime$ axis.
+		We identify trajectories cut off by the zigzag with a particular range of forbidden momenta.
+		By then analysing the bandstructure of this infinite SNS junction, ignoring the forbidden momenta, we can give an estimate the resulting gap of the device.
+		As the system is only momentum localized in the $x$ direction (the translationally invariant direction), we only control $\kx$.
+		Denoting the set of allowed momenta by $\Omega$, the equation for the estimated topological gap becomes,
+
+		\begin{equation}
+			\Delta_\text{topological} = \min_{\kx\in\Omega} \left\rvert E(\kx) \right\rvert
+			\label{eq:definition_gap}
+		\end{equation}
+
+		\comment{We first link the long trajectories to a maximum allowed angle.}
+		In the infinite system, the long trajectories have a small angle with respect to the $x^\prime$$ axis.
+		By defining a minimum angle, we thus can filter out the long trajectories.
+		We define this angle by identifying the angle
+
 		\subsubsection{Momentum cutoff}
+			\comment{We link the allowed angle by estimating it by $k_x = k_F \cos(\alpha)$}
 			We take the longest trajectory possible in a zigzag segment
+
 		\subsubsection{Angular cutoff}
+            \begin{equation}
+            \sin (\alpha_\text{max}) = \frac{v_y}{v_x} = \frac{ \frac{\de E}{\de k_y} }{ \frac{\de E}{\de k_x} }
+            \end{equation}

### 2019-01-16 thesis_report/methods.tex
changed alpha max to alpha min

@@
 		\centering
-		\includegraphics[width=0.75\columnwidth]{images/zigzag.pdf}
+		\includegraphics[width=0.75\columnwidth]{images/zigzag_methods.pdf}
 		\caption{Setups. Figure of a straight and zigzag system, including trajectories.
@@
 		\comment{We first link the long trajectories to a maximum allowed angle.}
-		In the infinite system, the long trajectories have a small angle with respect to the $x^\prime$$ axis.
+		In the infinite system, the long trajectories have a small angle with respect to the $x^\prime$ axis.
 		By defining a minimum angle, we thus can filter out the long trajectories.
-		We define this angle by identifying the angle
+		We define this angle by identifying it with the angle of the longest trajectory from one side of the superconductor to the other.
 

### 2019-01-16 thesis_report/methods.tex
Added some angle stuff

@@
 		\caption{Setups. Figure of a straight and zigzag system, including trajectories.
-		\label{fig:setup}}
+		\label{fig:zigzag_methods}}
 		\end{figure}
@@
 		\comment{We make an analogy between the cutoff of long trajectories to the cutoff of high momenta.}
-		We hypothesize that the increase of the topological gap in a zigzag is due to the cutoff of long trajectories.
+		We hypothesize that the increase of the topological gap in a zigzag is due to the cutoff of modes on the Fermi surface with long trajectories.
 		In order to make substantiate that this is indeed the driving mechanism behind the improvement, we propose an analogy using the bandstructure of a regular SNS junction.
@@
 		We essentially take a single diagonal section of a zigzag, and map it to a normal, infinite SNS junction.
-		The new coordinate system is depicted by the set of axes with $x^\prime$ and $y^\prime$ in Fig.~\ref{fig:setup}.
+		We assume that the zigzag is shaped such that there is no straight trajectory possible through the system anymore.
+		The system is depicted in Fig.~\ref{fig:zigzag_methods}, along with the set of axes with $x^\prime$ and $y^\prime$.
 		Note that the magnetic field has an angle $\theta$ with respect to the $x^\prime$ axis.
@@
 		By defining a minimum angle, we thus can filter out the long trajectories.
-		We define this angle by identifying it with the angle of the longest trajectory from one side of the superconductor to the other.
+		We define this angle $\alpha_\text{min}$ by identifying it with the angle of the longest trajectory from one side of the superconductor to the other: see Fig.~\ref{fig:zigzag_methods}.
+		Note that longer trajectories exist, by `grazing' the concave corners of the zigzag.
+		We suspect that this `grazing' leads to physics which cannot be captured in this simple model, and we thus choose to restrict this method for systems where the chosen trajectory is indeed a good approximation of the longest path.
 
-		\subsubsection{Momentum cutoff}
-			\comment{We link the allowed angle by estimating it by $k_x = k_F \cos(\alpha)$}
-			We take the longest trajectory possible in a zigzag segment
+        We estimate the restriction of the domain for the momentum by defining the angle for the various
 
-		\subsubsection{Angular cutoff}
         \begin{equation}
-            \sin (\alpha_\text{max}) = \frac{v_y}{v_x} = \frac{ \frac{\de E}{\de k_y} }{ \frac{\de E}{\de k_x} }
+        \tan (\alpha) = \frac{v_y}{v_x}\bigr{\rvert_{E=E_F}} = \frac{ \frac{\de E}{\de k_y} }{ \frac{\de E}{\de k_x} } \Biggr\rvert_{E=E_F}=
+        \begin{cases}
+        \frac{\hbar ^2 k_y}{\frac{\alpha  m_s \left(\alpha  k_x-\text{Ez} \sin (\theta )\right)}{\sqrt{\text{Ez}^2+\alpha  k_x \left(\alpha  k_x-2 \text{Ez} \sin (\theta )\right)}}+\hbar ^2 k_x} & \text{band 1}\\
+        \frac{\hbar ^2 k_y}{\frac{\alpha  m_s \left(\text{Ez} \sin (\theta )-\alpha  k_x\right)}{\sqrt{\text{Ez}^2+\alpha  k_x \left(\alpha  k_x-2 \text{Ez} \sin (\theta )\right)}}+\hbar ^2 k_x} & \text{band 2}
+        \end{cases}
         \end{equation}

### 2019-01-21 thesis_report/methods.tex
updated thesis

@@
 \chapter{Methods}
+
+\section{Tight binding simulation}
+
+	\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.95\columnwidth]{figures/kwant_system}
+	\caption{Figure of the simulated system in Kwant.
+	Lattice spacing is made smaller to make the discretization visible.
+	The two golden regions are both superconducting, but differ in phase.
+	The blue and black regions form the semiconductor, but the black region has an optional potential offset to model an imperfect interface, increasing the amount of normal reflection.}
+	\label{fig:kwant_system}
+	\end{figure}
 
@@
 			\begin{figure}[!htb]
-			\includegraphics[width=0.95\columnwidth]{images/scattering}
+			\centering
+			\includegraphics[width=0.75\columnwidth]{images/scattering}
 			\caption{Basis for scattering matrix. 
@@
 		\includegraphics[width=0.75\columnwidth]{images/zigzag_methods.pdf}
-		\caption{Setups. Figure of a straight and zigzag system, including trajectories.
+		\caption{Schematic of the system, along with relevant dimensions, and the quasiclassical approach.
+		The $x^\prime, y^\prime$ axis depicts the rotated frame for the quasiclassical estimate.
+		The white trajectory indicates the estimate taken for the longest trajectory allowed by a zigzag.
 		\label{fig:zigzag_methods}}
@@
 		By defining a minimum angle, we thus can filter out the long trajectories.
-		We define this angle $\alpha_\text{min}$ by identifying it with the angle of the longest trajectory from one side of the superconductor to the other: see Fig.~\ref{fig:zigzag_methods}.
+		We define this angle $\beta\text{min}$ by identifying it with the angle of the longest trajectory from one side of the superconductor to the other: see Fig.~\ref{fig:zigzag_methods}.
 		Note that longer trajectories exist, by `grazing' the concave corners of the zigzag.
@@
 
-        We estimate the restriction of the domain for the momentum by defining the angle for the various
+        We identify the momentum with its angle by defining it through the reciprocal of the component velocities, given by Eq.~\eqref{eq:methods_angle_of_state}.
+Note that $k_1$ and $k_2$ are the momenta as defined in Eq.~\eqref{eq:momenta_short_junction}.
 
         \begin{equation}
-        \tan (\alpha) = \frac{v_y}{v_x}\bigr{\rvert_{E=E_F}} = \frac{ \frac{\de E}{\de k_y} }{ \frac{\de E}{\de k_x} } \Biggr\rvert_{E=E_F}=
+        \tan (\beta) = \frac{v_y}{v_x}\bigr{\rvert_{E=E_F}} = \frac{ \frac{\de E}{\de k_y} }{ \frac{\de E}{\de k_x} } \Biggr\rvert_{E=E_F}=
         \begin{cases}
-        \frac{\hbar ^2 k_y}{\frac{\alpha  m_s \left(\alpha  k_x-\text{Ez} \sin (\theta )\right)}{\sqrt{\text{Ez}^2+\alpha  k_x \left(\alpha  k_x-2 \text{Ez} \sin (\theta )\right)}}+\hbar ^2 k_x} & \text{band 1}\\
-        \frac{\hbar ^2 k_y}{\frac{\alpha  m_s \left(\text{Ez} \sin (\theta )-\alpha  k_x\right)}{\sqrt{\text{Ez}^2+\alpha  k_x \left(\alpha  k_x-2 \text{Ez} \sin (\theta )\right)}}+\hbar ^2 k_x} & \text{band 2}
+        \frac{\hbar ^2 k_1}{\frac{\alpha  \meff \left(\alpha  k_x-\text{Ez} \sin (\theta )\right)}{\sqrt{\text{Ez}^2+\alpha  k_x \left(\alpha  k_x-2 \text{Ez} \sin (\theta )\right)}}+\hbar ^2 k_x} & \text{band 1}\\
+        \frac{\hbar ^2 k_2}{\frac{\alpha  \meff \left(\text{Ez} \sin (\theta )-\alpha  k_x\right)}{\sqrt{\text{Ez}^2+\alpha  k_x \left(\alpha  k_x-2 \text{Ez} \sin (\theta )\right)}}+\hbar ^2 k_x} & \text{band 2}
         \end{cases}
+        \label{eq:methods_angle_of_state}
         \end{equation}
+
+        We estimate the restriction of the domain for the momentum by geometrically calculating the minimum angle, as depicted in Fig.\ref{fig:zigzag_methods}. The result:
+
+        \begin{align}
+        	\tan \left(\beta_\text{min} \right) = \frac{W}{\sqrt{D^2 - W^2}} \label{eq:beta_min}\\
+        	D = \sqrt{z_x^2 + \left(z_y + W \sqrt{1 + \left(\frac{z_y}{z_x}\right)^2}\right)^2} \nonumber
+        \end{align}
+
+        The condition for the restricted momentum becomes:
+        \begin{equation}
+        	\tan \left(\beta\right) \geq \tan \left(\beta_\text{min}\right)
+        	\label{eq:restriction_momentum}
+        \end{equation}

### 2019-01-25 sns_system.py
proper transversal soi

@@ -80,13 +80,13 @@ def get_template_strings(
     if not with_k_z:
         ham_str = ham_str.replace('k_z', '0')
 
-    spin_orbit = """+ alpha_{} * kron(sigma_x, sigma_z) * k_y"""
+    spin_orbit = "- alpha_{} * kron(sigma_y, sigma_z) * k_x"
     ham_normal = ham_str + spin_orbit.format('middle')
     ham_sc_left = ham_str + spin_orbit.format('left')
     ham_sc_right = ham_str + spin_orbit.format('right')
 
     if transverse_soi:
-        tr_spin_orbit = "- alpha_{} * kron(sigma_y, sigma_z) * k_x"
+        tr_spin_orbit = """+ alpha_{} * kron(sigma_x, sigma_z) * k_y"""
         ham_normal += tr_spin_orbit.format('middle')
         ham_sc_left += tr_spin_orbit.format('left')
         ham_sc_right += tr_spin_orbit.format('right')

### 2019-01-25 thesis_report/methods.tex
Added some stuff about kwant in the methods

@@
 	\includegraphics[width=0.95\columnwidth]{figures/kwant_system}
-	\caption{Figure of the simulated system in Kwant.
+	\caption{Figure of different examples of simulated systems in Kwant.
 	Lattice spacing is made smaller to make the discretization visible.
@@
 	\end{figure}
+
+	\comment{We use kwant to make systems and extract the eigenstates}
+	We use a tight-binding model, implemented using Kwant, to simulate various properties of the system.
+	The model consists of a two-dimensional square lattice of sites.
+	Each site has two orbitals: spin and electron-hole.
+	There are four different types of sites (and thus four different Hamiltonians): the top superconductor, the bottom superconductor, the normal region, and a normal region with a variable potential offset, forming a barrier to simulated an imperfect NS interface.
+	A schematic of such kwant systems is depicted in Fig.~\ref{fig:kwant_system}.
+	After the system is specified, we can extract the total Hamiltonian of the system, allowing analysis of the eigenstates.
+
+	\comment{We extract the gap by either taking the lowest energy state for an infinite system, or the difference between the lowest two eigenstates.}
 

### 2019-01-26 thesis_report/conclusion.tex
Added comparison of spectral calculations

% -*- root: ./report.tex -*-
\chapter{Conclusion}

\section{Feasability of implementation}

### 2019-01-26 thesis_report/results.tex
Updated thesis
Added comparison of spectral calculations

@@
+% -*- root: ./report.tex -*-
 \chapter{Results \& Discussion}
+	\comment{Introduction of a zigzag opens up the gap, creates a more stable topological phase diagram, and decreases coherence length of Majorana's}
+	\section{Increased isolation and stability of the Majorana state}
 
 	\comment{We see that the introduction of a zigzag leads to a reduction of the gap}
-	\section{Gap/bandstructure as a function of zigzagginess}
+		\subsection{Gap/bandstructure as a function of zigzagginess}
 			\comment{We discretize the model described in section II and simulate it with Kwant.}
@@
 			\begin{figure}[!htb]
-		\includegraphics[width=0.95\columnwidth]{figures/bandstructures}
+			\centering
+			\includegraphics[width=0.55\columnwidth]{figures/bandstructures}
 			\caption{Figure of the bandstuctures.
@@
 		\comment{Introduction of a zigzag leads to localization of the Majorana's}
-	\section{Majorana decay length}
+		\subsection{Majorana decay length}
 			\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag.}
@@
 			\begin{figure}[!htb]
-		\includegraphics[width=0.95\columnwidth]{figures/wavefunctions}
+			\centering
+			\includegraphics[width=0.55\columnwidth]{figures/wavefunctions}
 			\caption{Wavefunctions for different sizes and geometries.
@@
 		\comment{Zigzag Majorana's have a cleaner phase diagram due to the reduction in symmetry class}
-	\section{Phase diagram}
+		\subsection{Phase diagram}
 			\comment{We calculate the topological phase diagram using the gap size.}
@@
 			\begin{figure}[!htb]
-		\includegraphics[width=0.95\columnwidth]{figures/phasediagrams}
+			\centering
+			\includegraphics[width=0.75\columnwidth]{figures/phasediagrams}
 			\caption{Phase diagrams of a straight system (a, b) and zigzag system (c, d), where (a, c) are $E(\mu, B)$ and (b, d) are $E(\phi, B)$.
@@
 
+	\section{Finding the mechanism responsible for the increased gap}
 		\comment{We use our analytical bandstructure to }
-	\section{Analytical estimate}
+		\subsection{Verification of analytical estimate}
+			\begin{figure}[!htb]
+			\centering
+			\includegraphics[width=0.95\columnwidth]{figures/spectrum_calculation_comparison}
+			\caption{Andreev Bound State spectrum of a SNS junction with a tilted in-plane magnetic field, computed using four different methods.}.
+			\label{fig:spectrum_calculation_comparison}
+			\end{figure}
+
+		\subsection{Estimation of the gap through momentum cutoff}

### 2019-01-26 thesis_report/results.tex
Added to bandstructures and wavefunctions.

@@
 \chapter{Results \& Discussion}
+		In this chapter, we show how the properties of the system change under introduction of the zigzag geometry.
+		Additionally, we attempt to isolate the mechanism behind the improved properties by estimating the gap size through the quasiclassical model introduced in the Methods chapter.
+
 	\comment{Introduction of a zigzag opens up the gap, creates a more stable topological phase diagram, and decreases coherence length of Majorana's}
@@
 		\subsection{Gap/bandstructure as a function of zigzagginess}
-			\comment{We discretize the model described in section II and simulate it with Kwant.}
+			\comment{We discretize the model described in the methods and simulate it with Kwant.}
 			We implement a tightbinding version of the model described in the Methods section (a two dimensional SNS junction with a Rashba BdG Hamiltonian) using Kwant.
@@
 			\comment{We calculate the bandstructure for varying amount of zigzag.}
-			In figure~\ref{fig:bandstuctures}, the bandstructure for zigzag systems with varying amplitude is displayed.
+			In figure~\ref{fig:bandstuctures}, the bandstructure for zigzag systems (sawtooth shape) with varying amplitude is displayed.
 			As the zigzag introduces super cell, we see a folded bandstructure.
@@
 			This effect is due to the fact that the modes where the gap is smallest, when the momentum is almost completely focused along the strip ($k_x=k_F$), are cut off by the zigzag geometry.
-			Also apparent is the reduction of group velocity; the slope of the bands is greatly reduced.
-			This has an effect on the Majorana coherence length, as described later on in the manuscript.
+			Also apparent is the significant reduction of group velocity; the slope of the bands is virtually zero.
+			The size of the gap, together with the velocity, directly relate to the Majorana coherence length (Eq.~\eqref{eq:majorana_coherence_length}), the effect of which is seen in the following section.
 
 			\comment{The introduction of an SN interface at many angles also increases performance.}
-			Additionally in the presence of normal reflection, due to the availability of NS interfaces at a wide range of slopes, the reflected part will eventually ``find'' a surface with which it is perpendicular to.
-The transparency of the SN interface is thus improved for transversal modes.
+			Additionally we note that, in the presence of normal reflection, due to the availability of NS interfaces at a wide range of slopes, a zigzag system will perform more favorable.
+			One can imagine that the normally reflected part of a wavefunction will, in a zigzag system, eventually ``find'' a surface with which it is perpendicular to.
+			The transparency of the SN interface is thus improved for non-transversal modes.
 
@@
 		\subsection{Majorana decay length}
-			\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag.}
-
-			\comment{We find the Majorana lengths by calculating the slowest decaying mode.}
-			Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinusoids.
-			In figure~\ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.
-			For the ribbon system, we see that the Majorana coherence length is relatively large, not showing the decolalized nature sought after.
-			All of the zigzag type geometries however show greatly reduced coherence length.
-			This can be explained by two effects: the increase in topological gap, but also the before mentioned reduction of the group velocity.
-
-			\comment{We also confirm that the specific shape does not matter.}
-			Also note the similarity between the various shapes, sharp corners or more smoothlike, the effect is the same.
 
@@
 			\end{figure}
+
+			\comment{We calculate the lowest eigenfunction and plot the density.}
+			Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinusoids.
+			In figure~\ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.
+			Also displayed in the figure are the energies $\E_M$, corresponding to the plotted Majorana wavefunctions, as well as $E_1$: the energies corresponding to the next lowest state.
+
+			\comment{In a straight system, the Majorana's are very poorly localized.}
+			For the ribbon system, we see that the decay of the density is slow: the wavefunction clearly extends to the middle of the system, not showing the delocalization sought after.
+			Apart from the density, as mentioned in the Theory chapter, overlap of Majorana's leads to a non-zero energy of the state.
+			Taking this into consideration, we see that the energy of the Majorana state in the straight system is only barely below the next lowest lying eigenstate: the Majorana's are very poorly localized, and topological protection against perturbations is minimal.
+
+			\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag.}
+			All of the zigzag type geometries show a greatly reduced coherence length.
+			The delocalized nature of the wavefunctions is clearly visible through the density plots.
+			Quantitatively, the improvement in localization of the Majorana's is also distinctly apparent: the energies of the Majorana states are orders of magnitude lower than the energy of the second lowest lying wavefunctions.
+			As mentioned in the previous section, this can be attributed due to the way the gap and velocity factor into the Majorana coherence length.
+
+			\comment{We also confirm that the specific shape does not matter.}
+			The shape of the wavefunctions does not seem to change much depending on the details of the shape.
+			The sharp corners of the sawtooth versus the smooth shape of the snakelike system do not seem to have great impact upon the shape of the wavefunction.
 

### 2019-01-26 thesis_report/results.tex
Fixed small mistake making latex crash

@@
 			With (a) a straight system, (b) a zigzag system, (c) a system where the normal region is defined by lines parallel to a sinosoid, and (d) a system with vertically offset sinosoids.
-			Inside the figure we indicate the Majorana length (or coherence length) $\xi$ and the topological energy gap $E_\textrm{gap}.$
-			We observe that $\xi$ for (a) is orders of magnitude longer and $E_\textrm{gap}$ orders of magnitude smaller than for (b, c, d), meaning that the details of the geometry do not matter.
+			Inside the figure we indicate the Majorana length (or coherence length) $\xi$ and the topological energy gap $E_\textrm{gap}$.
+			We observe that $\xi$ for (a) is orders of magnitude longer and $E_\textrm{gap} = E_\textrm{1} - E_M$ orders of magnitude smaller than for (b, c, d), meaning that the details of the geometry do not matter.
 			\label{fig:wavefunctions}}
@@
 			In figure~\ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.
-			Also displayed in the figure are the energies $\E_M$, corresponding to the plotted Majorana wavefunctions, as well as $E_1$: the energies corresponding to the next lowest state.
+			Also displayed in the figure are the energies $E_M$, corresponding to the plotted Majorana wavefunctions, as well as $E_1$: the energies corresponding to the next lowest state.
 

### 2019-01-27 thesis_report/results.tex
New parts added to results

@@
 		\subsection{Gap/bandstructure as a function of zigzagginess}
-			\comment{We discretize the model described in the methods and simulate it with Kwant.}
-			We implement a tightbinding version of the model described in the Methods section (a two dimensional SNS junction with a Rashba BdG Hamiltonian) using Kwant.
 
@@
 			\end{figure}
-
 			\comment{We calculate the bandstructure for varying amount of zigzag.}
+			We implement a tightbinding version of the model described in the Methods section (a two dimensional SNS junction with a Rashba BdG Hamiltonian) using Kwant.
 			In figure~\ref{fig:bandstuctures}, the bandstructure for zigzag systems (sawtooth shape) with varying amplitude is displayed.
@@
 
+			\comment{We calculate the lowest eigenfunction and plot the density.}
+			Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinusoids.
+			In figure~\ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.
+			Also displayed in the figure are the energies $E_M$, corresponding to the plotted Majorana wavefunctions, as well as $E_1$: the energies corresponding to the next lowest state.
+
 			\begin{figure}[!htb]
@@
 			\end{figure}
-
-			\comment{We calculate the lowest eigenfunction and plot the density.}
-			Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinusoids.
-			In figure~\ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.
-			Also displayed in the figure are the energies $E_M$, corresponding to the plotted Majorana wavefunctions, as well as $E_1$: the energies corresponding to the next lowest state.
 
@@
 		\subsection{Phase diagram}
+
 			\comment{We calculate the topological phase diagram using the gap size.}
-			We calculate the gap by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{|E(k)|}$.
-			Noting the gap closings and the fact we know the topology for the non-zigzag system, we can infer the topology of the system with zigzag modulation. % Bas: I don't understand what is written here
-
-			\comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry. }
-			Similar to what is described by Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond like structure as a function of phase and Zeeman field.
-			We also see some additional gap closings which are due to the BDI symmetry class, creating quite an unstable region.
-			As expected, for the zigzag system, the magnitude of the gap is significantly improved, whilst maintaining the diamond like shape.
-			As the zigzag shape destroys the additional symmetry, moving it to class D, we see a more clean topological region.
+			Due to the size of the system, we cannot use full spectrum methods (the Pfaffian in this case) to compute the topological phase of our system.
+			Instead, we calculate the gap by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{|E(k)|}$.
+			Noting the gap closings, and the fact we know the topological phase for the non-zigzag system (e.g.
+for magnetic field vs.
+phase difference it is diamond shaped: Fig.~\ref{fig:pientka_phase_diagram}), we can infer the topology of the system with zigzag modulation.
+			In Figure ~\ref{fig:phasediagrams}, the energy gap as a function of magnetic field, chemical potential, and superconducting phase difference is displayed, for both a straight system (a and b), and a zigzag system (c and d).
 
@@
 
+			\comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry. }
+			Similar to what is described by Pientka et.
+al~\cite{pientka2017topological} (see Fig.~\ref{fig:pientka_phase_diagram}), we see that the straight geometry, as a function of superconducting phase difference and Zeeman field (b), has a diamond shaped phase diagram.
+			The additional gap closings visible within the diamond are due to the system belonging to the BDI symmetry class, and cause the region of interest, where there is a single pair of Majoranas, to be relatively small.
+
+			For the zigzag system, the magnitude of the gap is significantly improved, as expected.
+			The diamond like shape of the phase-Zeeman plot is retained, and there is no significant change in its size either.
+			We expect a cleaner phase diagram due to the system belonging to the D symmetry class, which is partially reflected in the diagram: there is a large and stable (no gap closings) central region, but near 0 and 2$\pi$ phase difference, in the corner of the diamond, we see a chaotic collection of gap closings.
+			We are unsure of the nature of these gap closings, but they can perhaps be attributed to the symmetry breaking being relatively weak.
+
 	\section{Finding the mechanism responsible for the increased gap}
-		\comment{We use our analytical bandstructure to }
+		\comment{We compare different techniques to calculate the bandstructure of a 1D system.}
+		We verify the validity of the analytic model described in the Methods, to compute the bandstructure of a straight system in a tilted magnetic field. 
+		In Fig.\ref{fig:spectrum_calculation_comparison}, we compare the analytical model with bandstructures obtained using three different methods, implemented in Kwant.
+		To show that the model has been correctly implemented, we compute the Kwant scattering matrix of the identical model used in the analytics, and substitute it into the bound state condition\eqref{eq:bound_state_condition_sjl} (labeled Kwant without SOI SJL).
+		To show the validity of neglecting spin orbit in the transverse direction, we also compute the scattering matrix including the additional term, and again use the bound state condition to obtain the spectrum (labeled Kwant with SOI SJL).
+		We also perform the fully accurate calculation of the spectrum by simply computing the bandstructure of the corresponding Kwant system (labeled Full 1D kwant system): this result serves as the benchmark for the other techniques.
+
 		\subsection{Verification of analytical estimate}
@@
 
+			All three of the scattering matrix approaches agree almost perfectly with each other.
+			We must note that ignoring spin orbit coupling in the transverse direction is only valid if the spin orbit length is sufficiently small compared to the width of the system.
+			What is also clear from the plot is that the domain of the scattering matrix methods is limited.
+			This is a result of the zero energy approximation  used to compute the momenta in the short junction limit: this assumption yields no solutions beyond the Fermi surface.
+
+			When comparing the scattering matrix approach to the full bandstructure calculation, we see that it holds only approximately: the shape of the bands is similar, but the magnitude differs significantly.
+			We attribute this to the loose compliance with the short junction limit: one needs both a long superconducting coherence length, as well as the energies in the spectrum to be near zero.
+			As we find the accuracy of the analytical spectrum to be relatively weak, we continue estimation of the gap in a zigzag system using the spectrum calculated with the full Kwant system.
+
 		\subsection{Estimation of the gap through momentum cutoff}
+			As explained in the Methods chapter, we estimate the topological gap using a quasiclassical estimate.
+			We keep the ratio $4\dfrac{z_x}{z_y}$ constant, and vary $z_y$.
+
+			\begin{figure}[!htb]
+			\centering
+			\includegraphics[width=0.95\columnwidth]{figures/quasiclassical_approximation}
+			\caption{Andreev Bound State spectrum of a SNS junction with a tilted in-plane magnetic field, computed using four different methods.}.
+			\label{fig:quasiclassical_approximation}
+			\end{figure}

### 2019-01-27 thesis_report/results.tex
updated results

@@
 			As explained in the Methods chapter, we estimate the topological gap using a quasiclassical estimate.
-			We keep the ratio $4\dfrac{z_x}{z_y}$ constant, and vary $z_y$.
+			We keep the ratio $4\dfrac{z_x}{z_y}$ constant, and compute the gap as a function of $z_y$.
+			In Figure \ref{fig:quasiclassical_approximation}, the result is shown, comparing numerical gap calculations of the full zigzag system (full lines), with the result of the quasiclassical estimation.
+			Note that the quasiclassics are only valid once the zigzag cuts off all trajectories which extend infinitely.
 
@@
 			\includegraphics[width=0.95\columnwidth]{figures/quasiclassical_approximation}
-			\caption{Andreev Bound State spectrum of a SNS junction with a tilted in-plane magnetic field, computed using four different methods.}.
+			\caption{Comparison of the topological gap computed using a full zigzag system implemented in Kwant with the quasiclassical estimate.
+The ratio $4\dfrac{z_x}{z_y}$ is kept constant at three different values, and the gap is calculated for varying $z_y$.
+			The full lines represent  the numerical gap calculations of the full zigzag system, the dashed lines represent the quasiclassical estimation.}
 			\label{fig:quasiclassical_approximation}
 			\end{figure}
+
+			We would expect that the maximum gap improvement would occur near where the zigzag amplitude $z_y$ is large enough to cut off any angle in the system.
+			This point is different for the three ratios, but can be identified by where the gap is largest for the quasiclassical estimate (dashed lines).
+			Increasing $z_y$ further would only allow longer trajectories, which would seem extra undesirable due to the magnetic field not being aligned with the diagonal sections.
+			Considering the lines corresponding to the full zigzag systems, we see that, for the lower ratios (and thus steeper slopes), the optimal value lies far beyond the cutoff point.
+			This is unexpected,

### 2019-01-28 thesis_report/results.tex
Added to results

@@
 			Note that the quasiclassics are only valid once the zigzag cuts off all trajectories which extend infinitely.
+			Also important to note is that for the quasiclassical estimate, we set the longest trajectory to be the trajectory that does not include the corners, as depicted in Fig.~\ref{fig:longest_trajectory_wo_corners}
+
+			\begin{figure}
+			\centering
+			\includegraphics[width=0.45\columnwidth]{images/longest_trajectory_wo_corners}
+			\caption{Diagram depicting quasiclassical estimate of a zigzag system, but now with the longest trajectory chosen to avoid the corners of the zigzag.}
+			\label{fig:quasiclassical_approximation}
+			\end{figure}
 
@@
 			Increasing $z_y$ further would only allow longer trajectories, which would seem extra undesirable due to the magnetic field not being aligned with the diagonal sections.
+
 			Considering the lines corresponding to the full zigzag systems, we see that, for the lower ratios (and thus steeper slopes), the optimal value lies far beyond the cutoff point.
-			This is unexpected,
+			This is unexpected, and it weakens the validity of the idea that the gap is mostly determined by the length of the trajectories.
+			A possible explanation is that for lower ratios, the length of the diagonal sections is smaller, and  it is easier for the wavefunction to tunnel through the superconductor.
+			In any case, this phenomenon requires additional explanation.
+
+			The quasiclassical estimate, indicated by the dashed lines, seems to consistently under estimate the gap.
+			We also see that the gap declines monotonically with respect to the zigzag amplitude, which is by design: increasing the zigzag amplitude corresponds to increasing the domain of permitted trajectories, and thus the minimum can only decrease.
+			Even so, we see that the decline of the gap with respect to $z_y$ is much quicker than with an actual zigzag.
+			A possible reason that the quasiclassical model sketches a darker picture than full zigzag, is due to the fact that in that model, long trajectories also correspond to grazing angles of incidence at the NS interface.
+
+			We conclude that the proposed model to estimate the gap does not capture the physics of the zigzag very well: the model merely gives a lower bound for the topological gap.

### 2019-01-28 thesis_report/introduction.tex
Updated thesis
updated thesis
Semi-acceptable version of methods and resutls

@@
+% -*- root: ./report.tex -*-
 \chapter{Introduction}
+% \comment{We propose that the introduction of a zigzag-shaped modulation of the junction region leads to an increased topological gap, as well as a reduction of the Majorana coherence length.}
+% \comment{We hypothesize that the gap improvement is the result of the elimination of long trajectories}
 
-\comment{We propose that the introduction of a zigzag-shaped modulation of the junction region leads to an increased topological gap, as well as a reduction of the Majorana coherence length.}
-\comment{We hypothesize that the gap improvement is the result of the elimination of long trajectories}
+Majorana bound states (MBSs) are a promising candidate to form the basis of a stable platform for topological quantum computing.
+
+\comment{Majoranas are mostly made in hybrid NS structures.}
+The current experimental effort is focused on creating pairs of MBSs in hybrid normal-superconductor (NS) structures, where a lengthy strip (or wire) of semiconductor is interfaced with a \cite{lutchyn_majorana_2010,oreg_helical_2010} superconductor.
+Within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple wire), the semiconductor becomes topological and MBSs appear at the ends of the segment.
+Recently, a system with a slight modification has been proposed\cite{pientka2017topological}, where instead of having one superconductor, there are two superconductors, creating a superconductors-normal-superconductor (SNS) junction.
+This adds an extra knob to adjust, the superconducting phase difference $\phi$, and this should make it easier to tune the system into the topological phase.
+In practice, multiple problems arise making even the observation, let alone the manipulation of Majoranas difficult.
+
+\comment{The gap is small because of long trajectories.}
+One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap; where the gap in the density of states is greatly reduced for states with the momentum directed along the length of the strip.
+From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
+Additionally, these long trajectories have long flight times $\tau_f$ and equivalenly small Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$, resulting in a small gap.
+
+\comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
+Currently, proposed workarounds are low density or disorder~\cite{haim_double-edge_2018}, but both have drawbacks.
+
+\comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
+In this paper we show that introducing a zigzag or snake like geometry for the semiconductor eliminates these long trajectories and prevents the appearance of a soft gap while also increasing the topological gap by an order of magnitude.

### 2019-01-28 thesis_report/methods.tex
Added to bandstructures and wavefunctions.
New parts added to results
Semi-acceptable version of methods and resutls

@@
 
-\section{Tight binding simulation}
+\section{Physical picture}
+	\comment{We consider a two-dimensional system with zigzag.}
+	We consider a Josephson junction (JJ)(Fig.~\ref{fig:setup}) consisting of a two dimensional strip of semiconductor, with superconductors on both sides.
+	We modulate the shape of the normal region, which can be either zigzag as depicted, or a more smooth sinusoidal like shape.
+	Similar to the conventional straight system \cite{pientka2017topological}, a magnetic field $B_x$ perpendicular to the junction is applied.
+	We model the system with a BdG Hamiltonian Eq.~\eqref{eq:hamiltonian}; the normal part has a linear Rashba spin-orbit coupling term characterized by $\alpha$ and a Zeeman field with $E_z=\frac{1}{2}mu_B g B_x$.
+	The superconductor has a superconducting coupling term $\Delta$ with a superconducting phase $\exp{\pm i \phi/2}$.
+	Both parts have a kinetic term and chemical potential $\mu$ (counted from the bottom spin-orbit band). 
+	For the zigzag geometry, we first consider a sawtooth like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
 
@@
 	\centering
-	\includegraphics[width=0.95\columnwidth]{figures/kwant_system}
-	\caption{Figure of different examples of simulated systems in Kwant.
-	Lattice spacing is made smaller to make the discretization visible.
-	The two golden regions are both superconducting, but differ in phase.
-	The blue and black regions form the semiconductor, but the black region has an optional potential offset to model an imperfect interface, increasing the amount of normal reflection.}
-	\label{fig:kwant_system}
+	\includegraphics[width=0.5\columnwidth]{images/zigzag.pdf}
+	\caption{Setups. Figure of a straight and zigzag system, including trajectories.
+	\label{fig:setup}}
 	\end{figure}
+
+	\comment{The symmetry class of the system is D.}
+	The non-zigzag system is in the symmetry class BDI \cite{pientka2017topological}.
+	Using the software package Qsymm\cite{varjas2018qsymm}, we find that the symmetry class of our system to be $\mathcal{D}$ because we break the chiral/time-reversal resulting from the mirror symmetric junction.
+
+	\begin{small}
+	\begin{align}
+	    H = \left(\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu + \frac{\meff \alpha^2}{2 \hbar^2} \right)\tau_z+
+	        E_\text{z} \sigma_x+
+	        \alpha \left( \ky \sigma_x - \kx \sigma_y \right) \tau_z +
+	        \Delta \tau_y
+	\end{align}
+	\label{eq:hamiltonian}
+	\end{small}
+
+\section{Tight binding simulation}
 
@@
 	A schematic of such kwant systems is depicted in Fig.~\ref{fig:kwant_system}.
-	After the system is specified, we can extract the total Hamiltonian of the system, allowing analysis of the eigenstates.
+	We can also make the system infinite in for example the $x$ direction by connecting the sites on the left border with those on the right border with a $\kx$ dependent hopping.
+
+	\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.95\columnwidth]{figures/kwant_system}
+	\caption{Figure of different examples of simulated systems in Kwant.
+	Lattice spacing is made bigger to make the discretization visible.
+	The two golden regions are both superconducting, but differ in phase.
+	The blue and black regions form the semiconductor, but the black region has an optional potential offset to model an imperfect interface, increasing the amount of normal reflection.}
+	\label{fig:kwant_system}
+	\end{figure}
 
 	\comment{We extract the gap by either taking the lowest energy state for an infinite system, or the difference between the lowest two eigenstates.}
+	After the system is specified, we can extract the total Hamiltonian of the system, allowing analysis of the eigenstates.
+	For example, calculating the bandstructure of a system is performed by taking a translationally invariant system and calculating the eigenvalues for different momenta.
 
@@
 		We derive the spectrum by calculating the scattering matrix for the normal region and applying the Andreev bound state condition for the short junction limit\cite{beenakker1991universal, sticlet_robustness_2017}.
-		The short junction limit is valid for [TODO: WHEN IS THE SHORT JUNCTION LIMIT VALID]
+		The short junction limit is valid for $W<\xi$, where $\xi$ is the superconducting coherence length.
 		For deriviation of the scattering matrix, we neglect SOI in the transverse direction, which is valid for $W<l_\text{so}$.
@@
 			By applying the boundary conditions and solving the resulting linear system of equations, the resulting solution is given by Eqs.~\eqref{eq:smatrix} through ~\eqref{eq:momenta_short_junction}.
-			\emph{Important note: In order to use the Andreev bound state condition, the scattering matrix must be in the [TODO: NAME OF BASIS] basis.
-This basis transformation has already been applied in Eqs.
-~\eqref{eq:smatrix} through ~\eqref{eq:momenta_short_junction}}\\
+			\emph{Important note: In order to use the Andreev bound state condition, the scattering matrix must be in the correct basis.
+The relevant basis transformation has already been applied in Eqs.
+~\eqref{eq:smatrix} through ~\eqref{eq:momenta_short_junction}}.\\
 
@@
 			\det\left[1+\alpha^{2}\left(E\right)r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)\right]=0
+			\label{eq:bound_state_condition_sjl}
 			\end{equation}

### 2019-01-28 thesis_report/theory.tex
Added to bandstructures and wavefunctions.
Added to theory

@@
 
+	\subsection{Proximity effect}
+		In order to create Majorana's, one needs a material with properties unique to both superconductors and semiconductors.
+		However, if a superconductor is interfaced with a normal conductor, some of the properties belonging to the superconductor transfer to normal material.
+		This effective transfer of properties to the normal material is known as the proximity effect.
+		The characteristic distance governing the decay of the superconducting behavior is given by the superconducting coherence length, Eq.\eqref{eq:theory_sc_coherence_length}
+
+		\begin{equation}
+			\xi = \hbar \frac{v_\text{F}}{\Delta}
+			\label{eq:theory_sc_coherence_length}
+		\end{equation}
+
 \section{Normal-superconducting junctions}
@@
 
-\section{Topology and Majorana bound states}
+\section{Topology, Symmetry, and Majorana bound states}
 
@@
 
-	Similarly, in condensed matter physics, topology refers to the study of properties of a system, which do not change within a particular range of parameters.
+	Similarly, in condensed matter physics, topology refers to the study of properties of a system, which are guaranteed by particular symmetries of the Hamiltonian.
+	These symmetries are present within a particular range of parameters, and any variation of those parameters within that range does not destroy these \emph{topologically protected} properties.
+
 	Topology is relevant to the context of the system under study, because the emergence of seperated Majorana's is guaranteed within a continuous range of parameters.
-	The precense of Majorana's is therefore \emph{topologically protected}, as they will be unpurturbed by variations of parameters, within a certain range.
-	For an infinite system, the system is said to be topological if Majorana's would emerge if the system is cut to finite length.
-	The system is trivial if the converse is true.
+	The presence of Majorana's is therefore topologically protected, as they will be unpurturbed by variations of parameters, within a certain range.
+	For an infinite system, the system is said to be in the topological phase if Majorana's emerge once the system is cut to finite length.
+	The system is considered to be in its trivial phase if the converse is true.
+	The allocation of a system into one of its phases (in this case two) is quantitatively captured by its topological invariant.
+	The relevant topological invariant is dependent on the symmetry class the system belongs to.
+	In the case of the what is studied in this manuscript, the systems discussed belong to either symmetry class BDI or D.
+	Any system which is in the BDI class is also contained within class D.
+	The topological invariant of a class D system is binary: $-1$, corresponding to the topological phase, and $1$, corresponding to the trivial phase.
+	The invariant of a BDI system can be any integer number, which also means there are more than two topological phases.
+	More importantly, the transition of the system from one topological phase to the other means the system must undergo a gap closing.
 
@@
 
+	\subsection{Topological gap}
+		The topological gap is defined as the energy gap between the Majorana state -- conveniently located at zero energy -- and the first available state.
+		It's magnitude governs the protection of the system against perturbations causing the system to be lifted out of its ground state: the Majorana state.
+
 	\subsection{Decay/Coherence length}
@@
 		\begin{equation}
-			\xi = \hbar \frac{v_\text{F}}{\Delta}
+			\xi = \hbar \frac{v_\text{F}}{\Delta_\text{topological}}
+			\label{eq:majorana_coherence_length}
 		\end{equation}
 
-	\subsection{Topological gap}
-		The topological gap is defined as the energy gap between the Majorana state -- conveniently located at zero energy -- and the first available state.
-		It's magnitude governs the protection of the system against perturbations causing the system to be lifted out of its ground state: the Majorana state.
+		When the system is cut to a finite length, any overlap of the two Majorana's will lead to a non-zero energy.
+		This decreases the robustness of the topological state and it is thus desirable that the Majorana decay length is significantly smaller than the system size.
 
@@
 		Without normal reflection (perfect Andreev reflection), the diagram has a diamond-like shape.
-		The system is always topological when the superconducting phase is $pi$, or when the magnetic field is tuned to $(2N-1)$ times the Thouless energy (With exception of the corners of the diamonds).
+		The system is always topological when the superconducting phase is $pi$, or when the magnetic field is tuned to $(2N-1)$ times the Thouless energy(Eq. \ref{eq:theory:E_th})
+		\begin{equation}
+			E_\text{Th} = \frac{\hbar^2 \pi^2}{2 \meff \left( 2 W \right)^2}
+			\label{eq:theory_E_th}
+		\end{equation}
 

### 2019-01-29 thesis_report/theory.tex
First draft of theory+methods+results

@@
 	\subsection{Bandstructure of a typical system}
+		In Figure \ref{fig:pientka_bandstructure}, the bandstructure is displayed for the SNS system.
+		Note that the gap is lowest at the Rashba/Zeeman split fermi-surface, where the momentum in the x direction equals $k_{F,1}$ or $k_{F,2}$.
+		It is at these momenta that the wavefunctions are completely parallel to the translationally invariant direction, causing weak couipling with the superconductors.
+
+		\begin{figure}[!htb]
+		\centering
+		\includegraphics[width=0.5\columnwidth]{figures/pientka_bandstructure}
+		\caption{Bandstructure of a straight SNS system~\cite{pientka_topological_2017}.
+		Note that the gap is smallest at $k_{F,1}$ and $k_{F,2}$, which correspond to the two different Fermi momenta.}
+		\label{fig:pientka_bandstructure}
+		\end{figure}

### 2019-01-30 thesis_report/introduction.tex
Added introduction of the introduction

--- 2019-01-07 thesis_report/introduction.tex
@@
+% -*- root: ./report.tex -*-
 \chapter{Introduction}
 
-\comment{We propose that the introduction of a zigzag-shaped modulation of the junction region leads to an increased topological gap, as well as a reduction of the Majorana coherence length.}
-\comment{We hypothesize that the gap improvement is the result of the elimination of long trajectories}
+\comment{The history of quantum computing and why QC is important}
+	The idea to use coherent quantum states as a means to perform complex calculations first appeared in the beginning of the 80's.
+	A handful of papers had already been published on the matter, Nobel laureate Richard Feynman suggested its importance with respect to physics simulations during a keynote speech at the California Institute of Technology.
+	To put things in very simple terms, calculating the quantum mechanical state of a system on a conventional computer scales exponentially with respect to the system size.
+	The idea of a quantum computer is that this scaling becomes polynomial.
+	Beyond physics, quantum computers have been suggested to be used for tasks such as cryptography, optimization and search algorithms.
+	With the potential applications in mind, a lot of resources and effort has been put into realising such a quantum computer in recent years.
+	Apart from quantum computing being a largely publicly funded effort, the private sector has also started to recognize the potential of the technology: large companies such as Microsoft, Google and IBM are investing into the development of a quantum computer.
+	As of this moment, working quantum computers have been realized on a very small scale: calculations of meaningful scale are still not possible.
+
+\comment{It is still an open question what the implementation for a qubit will be, but majorana's are one of the contenders}
+	If we consider the evolution of the regular computer, we see that the technological/physical platform for the bit, something which can be in either of two states, 1 or 0, has been constantly changing.
+	For the earliest computers, it was complex mechanical systems with gears and cogs.
+	Then later, switching to electronics, binary states were implemented in the form of vacuum tubes, and later, up to today, it is the transistor which acts as the basic unit of computation.
+	Similarly, because quantum computing is still in its infancy, there are still many contenders for what the underlying technology will be: what physical system will form the basis for the quantum bit, the qubit.
+	Some of the current platforms for implementing a qubit being pursued are the transmon qubit, NV-centers, quantum dots, and Majorana bound states.
+	Majorana bound states (MBSs) are a promising candidate to form the basis of a stable platform for topological quantum computing, and the specific way to create them are the topic of study in this manuscript.
+
+\section{Majorana bound states as qubits}
+
+	\comment{What are Majorana bound states}
+
+	\comment{Ways to make Majorana's: nanowires \& sns system}
+
+\section{The Josephson }
+	\comment{Current experimental progress}
+
+	\comment{The challenges encountered}
+
+% \comment{We show that by adding a zigzag geometry, small gap and poor localization is combatted by eliminating the long trajectories.}
+% In this paper we show that introducing a zigzag or snake like geometry for the semiconductor eliminates these long trajectories and prevents the appearance of a soft gap while also increasing the topological gap by an order of magnitude.
+
+% \comment{Majoranas are mostly made in hybrid NS structures.}
+% The current experimental effort is focused on creating pairs of MBSs in hybrid normal-superconductor (NS) structures, where a lengthy strip (or wire) of semiconductor is interfaced with a \cite{lutchyn_majorana_2010,oreg_helical_2010} superconductor.
+% Within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple wire), the semiconductor becomes topological and MBSs appear at the ends of the segment.
+% Recently, a system with a slight modification has been proposed\cite{pientka2017topological}, where instead of having one superconductor, there are two superconductors, creating a superconductors-normal-superconductor (SNS) junction.
+% This adds an extra knob to adjust, the superconducting phase difference $\phi$, and this should make it easier to tune the system into the topological phase.
+% In practice, multiple problems arise making even the observation, let alone the manipulation of Majoranas difficult.
+
+% \comment{The gap is small because of long trajectories.}
+% One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap; where the gap in the density of states is greatly reduced for states with the momentum directed along the length of the strip.
+% From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
+% Additionally, these long trajectories have long flight times $\tau_f$ and equivalenly small Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$, resulting in a small gap.
+
+% \comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
+% Currently, proposed workarounds are low density or disorder~\cite{haim_double-edge_2018}, but both have drawbacks.
+
+% \comment{We propose that the introduction of a zigzag-shaped modulation of the junction region leads to an increased topological gap, as well as a reduction of the Majorana coherence length.}
+% \comment{We hypothesize that the gap improvement is the result of the elimination of long trajectories}

### 2019-01-30 paper/snakemajoranas.tex
small changes to the paper

@@
 \comment{The introduction of an SN interface at many angles also increases performance.}
-Additionally, in the presence of normal reflection, due to the presence of NS interfaces at a wide range of angles, the reflected part will eventually scatter with a perpendicular surface.
+Additionally, in the presence of normal reflection, due to the presence of NS interfaces at a wide range of angles, the reflected part will eventually scatter with a near perpendicular surface.
 This means that for transversal modes the transparency of the NS interface will increase.
@@
 \comment{We calculate the topological phase diagram using the gap size.}
-We calculate the gap by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{|E(k)|}$.
+We calculate the gap $E_\textrm{gap}$ by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{|E(k)|}$.
 Noting the gap closings and the fact we know the topology for the non-zigzag system, we can infer the topology of the system with zigzag modulation. % Bas: I don't understand what is written here
@@
 \comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry. }
-Similar to what is described by Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond like structure as a function of phase and Zeeman field.
-We also see some additional gap closings which are due to the BDI symmetry class, creating quite an unstable region.
-As expected, for the zigzag system, the magnitude of the gap is significantly improved, whilst maintaining the diamond like shape.
+Similar to what is described by Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond like structure as a function of phase $\phi$ and Zeeman field $E_Z$.
+We also observe additional gap closings which are due to the BDI symmetry that is present.
+As expected for the zigzag system, the magnitude of the gap is significantly improved, whilst maintaining the diamond like shape.
 As the zigzag shape destroys the additional symmetry, moving it to class D, we see a more clean topological region.

### 2019-01-30 thesis_report/introduction.tex
updated into

@@
 	The idea to use coherent quantum states as a means to perform complex calculations first appeared in the beginning of the 80's.
-	A handful of papers had already been published on the matter, Nobel laureate Richard Feynman suggested its importance with respect to physics simulations during a keynote speech at the California Institute of Technology.
-	To put things in very simple terms, calculating the quantum mechanical state of a system on a conventional computer scales exponentially with respect to the system size.
-	The idea of a quantum computer is that this scaling becomes polynomial.
-	Beyond physics, quantum computers have been suggested to be used for tasks such as cryptography, optimization and search algorithms.
+	A handful of papers had already been published on the matter, when, during a keynote speech at the California Institute of Technology, Nobel laureate Richard Feynman suggested its importance with respect to physics simulations .
+	To put his idea in very simple terms, calculating the quantum mechanical state of a system on a conventional computer scales exponentially with respect to the system size.
+	By making a computer that is based on quantum states itself, and making a mapping between those states and the system you want to simulate, the idea is that this scaling becomes polynomial.
+	Beyond its significance in physics simulations, quantum computers have been suggested to be used for other, perhaps more pragmatic tasks, including topics like cryptography, optimization and search algorithms.
 	With the potential applications in mind, a lot of resources and effort has been put into realising such a quantum computer in recent years.
-	Apart from quantum computing being a largely publicly funded effort, the private sector has also started to recognize the potential of the technology: large companies such as Microsoft, Google and IBM are investing into the development of a quantum computer.
+	Recently, apart from being a largely publicly funded effort, the private sector has also started to recognize the potential of the technology: large companies such as Microsoft, Google and IBM are investing into the development of a quantum computer.
 	As of this moment, working quantum computers have been realized on a very small scale: calculations of meaningful scale are still not possible.
@@
 	\comment{What are Majorana bound states}
+	Majorana particles are particles that always come in pairs: one pair of Majorana's forms a single electronic state.
+	Disambiguating electrons and holes into their Majorana counterparts is often analogized with splitting a complex number into its real and imaginary part.
+	In terms of the creation and annihilation operators of electrons, respectively $\hat{c}^\dagger$ and $\hat{c}$, we write,
+	\begin{align}
+		\hat{c} =  \frac{1}{2} \left( \gamma_1 - i\gamma_2 \right) && \hat{c}^\dagger = \frac{1}{2} \left( \gamma_1 + i\gamma_2 \right)
+	\end{align}
 
 	\comment{Ways to make Majorana's: nanowires \& sns system}
+	A realistic experimental implementation of Kitaev's model did not emerge until two papers were published around the same time by both Lutchyn et.
+al\cite{lutchyn_majorana_2010} and Oreg et.
+al\cite{ oreg_helical_2010}, where they proposed an experiment composed of a semiconducting nanowire deposited onto a superconductor.
+	They predicted that, if the semiconductor has strong spin-orbit coupling, a magnetic field applied along the wire axis, as well as a carefully tuned chemical potential, Majoranas would appear at the ends of the nanowire.
+	The experiment proved to be sufficiently practical to perform in the lab and the first signatures of Majorana bound states were found using the setup by Mourik et. al~\cite{mourik_signatures_2012}.
 
-\section{The Josephson }
+	\comment{Why are SNS junctions potentially better?}
+
+	\comment{Why do }
+
+\section{Majoranas in a Josephson junction}
 	\comment{Current experimental progress}

### 2019-02-01 thesis_report/introduction.tex
Simple terms figure, updated theory and introduction

@@
 
-	\comment{Ways to make Majorana's: nanowires \& sns system}
-	A realistic experimental implementation of Kitaev's model did not emerge until two papers were published around the same time by both Lutchyn et.
+	\comment{Forming a kitaev chain}
+	Without going into to much detail, and at the cost of making gross oversimplifications, one can suppose that an electron consists of two Majorana particles.
+	Borrowing an analogy with domino stones from the online course Topology in Condensed Matter\cite{noauthor_topology_2015}, we can see an electron as a domino stone: the two ends, seperated by a line, each correspond to a Majorona particle.
+	In the figure below\cite{noauthor_topology_2015}, the dominoes, and thus electrons, have been placed in a chain:\\
+
+	\begin{centering}
+	\includegraphics[width=0.95\columnwidth]{images/majorana_dominoes}
+	\end{centering}
+
+	In a regular system, the Majoranas on each end of stone are paired locally, as depicted in the figure below:\\
+
+	\begin{centering}
+	\includegraphics[width=0.95\columnwidth]{images/trivial_dominoes}
+	\end{centering}
+
+	Now suppose one would be able to shift the pairing, such that the Majoranas form pairs with the Majoranas on adjacent stones:\\
+
+	\begin{centering}
+	\includegraphics[width=0.95\columnwidth]{images/topological_dominoes}
+	\end{centering}
+
+	As is apparent from the above image, this would leave two unpaired Majoranas at the ends of the chain.
+	This is the state we are interested in: the Majorana state, where two Majoranas are seperated in space.
+	This physical seperation has the effect of not allowing simple local perturbations to disturb the system.
+
+\section{Ways to make Majorana's: nanowires \& sns system}
+	A realistic experimental implementation of Kitaev's model did not emerge until the similar works of Lutchyn et.
 al\cite{lutchyn_majorana_2010} and Oreg et.
@@
 
-	\comment{Why are SNS junctions potentially better?}
-
-	\comment{Why do }
+	For the same reasons Majoranas are inherently protected against decoherence, it is notoriously difficult to prove their existence.
+	Perhaps the most direct way to detect their presence is through the observation of a so-called zero bias peak.
+	When performing a tunneling conductance experiment, measuring the conductance through the nanowire, the zero-energy (with respect to the Fermi energy) Majorana state provides a resonant tunneling state when no bias is applied, appearing as a peak in conductance.
+	There are however also other physical phenomena which can be responsible for such a conductance peak, and thus it is not unique to the Majorana state.
 
 \section{Majoranas in a Josephson junction}
-	\comment{Current experimental progress}
+	\comment{Why are SNS junctions potentially better?}
+	A more convincing case could be made if one could control the system in such a way that the presence of Majoranas can be turned on or off.
+	This feature is realized in a relatively recent proposal by Pientka et. al\cite{pientka_topological_2017}, where, instead of a nanowire, a two-dimensional strip of semiconductor is used.
+	On each side of the strip a superconductor is placed, forming a Josephson junction.
+	Using the Josephson junction, one can use the supercurrent which flows between the two superconductors to control whether the system is in a topological phase (meaning it contains Majoranas), or not.
+	The system has addition advantages, namely the system allows for Majorana's to be created at lower magnetic fields, the system is more compatible with convential semiconductor technology, and the Josephson junction allows for new ways to detect the topological phase of the system.
+
+	% \comment{Current experimental progress}
+	% Two papers that claimed they have observed signs of topological behavior.
+	% Soft gap, questionable results.
 
 	\comment{The challenges encountered}
+	One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap; where the gap in the density of states is greatly reduced for states with the momentum directed along the length of the strip.
+	From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
+	Additionally, these long trajectories have long flight times $\tau_f$ and equivalenly small Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$, resulting in a small gap. 
+	Currently, proposed workarounds are low density or disorder~\cite{haim_double-edge_2018}, but both have drawbacks.
 
-% \comment{We show that by adding a zigzag geometry, small gap and poor localization is combatted by eliminating the long trajectories.}
-% In this paper we show that introducing a zigzag or snake like geometry for the semiconductor eliminates these long trajectories and prevents the appearance of a soft gap while also increasing the topological gap by an order of magnitude.
-
-% \comment{Majoranas are mostly made in hybrid NS structures.}
-% The current experimental effort is focused on creating pairs of MBSs in hybrid normal-superconductor (NS) structures, where a lengthy strip (or wire) of semiconductor is interfaced with a \cite{lutchyn_majorana_2010,oreg_helical_2010} superconductor.
-% Within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple wire), the semiconductor becomes topological and MBSs appear at the ends of the segment.
-% Recently, a system with a slight modification has been proposed\cite{pientka2017topological}, where instead of having one superconductor, there are two superconductors, creating a superconductors-normal-superconductor (SNS) junction.
-% This adds an extra knob to adjust, the superconducting phase difference $\phi$, and this should make it easier to tune the system into the topological phase.
-% In practice, multiple problems arise making even the observation, let alone the manipulation of Majoranas difficult.
-
-% \comment{The gap is small because of long trajectories.}
-% One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap; where the gap in the density of states is greatly reduced for states with the momentum directed along the length of the strip.
-% From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
-% Additionally, these long trajectories have long flight times $\tau_f$ and equivalenly small Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$, resulting in a small gap.
-
-% \comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
-% Currently, proposed workarounds are low density or disorder~\cite{haim_double-edge_2018}, but both have drawbacks.
-
-% \comment{We propose that the introduction of a zigzag-shaped modulation of the junction region leads to an increased topological gap, as well as a reduction of the Majorana coherence length.}
-% \comment{We hypothesize that the gap improvement is the result of the elimination of long trajectories}
+	We propose that the introduction of a zigzag-shaped modulation of the junction region leads to an increased topological gap, as well as a reduction of the Majorana coherence length.
+	Furthermore, we hypothesize that the gap improvement is the result of the elimination of long trajectories

### 2019-02-01 thesis_report/methods.tex
Added to methods and theory

@@
 	Similar to the conventional straight system \cite{pientka2017topological}, a magnetic field $B_x$ perpendicular to the junction is applied.
-	We model the system with a BdG Hamiltonian Eq.~\eqref{eq:hamiltonian}; the normal part has a linear Rashba spin-orbit coupling term characterized by $\alpha$ and a Zeeman field with $E_z=\frac{1}{2}mu_B g B_x$.
+	We model the system with a BdG Hamiltonian, Eqs.~\eqref{eq:hamiltonian_n}-~\eqref{eq:hamiltonian_s}  ; the normal part has a linear Rashba spin-orbit coupling term characterized by $\alpha$ and a Zeeman field with $E_z=\frac{1}{2}mu_B g B_x$.
 	The superconductor has a superconducting coupling term $\Delta$ with a superconducting phase $\exp{\pm i \phi/2}$.
@@
 
+	\begin{align}
+	    H_\text{N} &= \left(\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu + \frac{\meff \alpha^2}{2 \hbar^2} \right) \left( \sigi \otimes \tauz \right)+
+	        E_\text{z} \left(\sigx \otimes \tauz \right) +
+	        \alpha \left( \ky \sigx - \kx \sigma_y \right) \otimes \tauz \label{eq:hamiltonian_n} \\
+	    H_\text{SC} &= \left(\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu \right) \left(\sigi \otimes \tauz \right) +
+	        \Delta \left(\sigi \otimes \tau_{\pm \phi /2}\right)
+	\label{eq:hamiltonian_s}
+	\end{align}
+	where,
+	\begin{equation}
+	    \tau_{\pm \phi /2} = \cos\left( \pm \phi /2 \right) \taux + \sin\left( \pm \phi /2 \right) \tauy \nonumber
+	\end{equation}
+
+\subsection{Symmetry class of system}
 	\comment{The symmetry class of the system is D.}
-	The non-zigzag system is in the symmetry class BDI \cite{pientka2017topological}.
-	Using the software package Qsymm\cite{varjas2018qsymm}, we find that the symmetry class of our system to be $\mathcal{D}$ because we break the chiral/time-reversal resulting from the mirror symmetric junction.
-
-	\begin{small}
-	\begin{align}
-	    H = \left(\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu + \frac{\meff \alpha^2}{2 \hbar^2} \right)\tau_z+
-	        E_\text{z} \sigma_x+
-	        \alpha \left( \ky \sigma_x - \kx \sigma_y \right) \tau_z +
-	        \Delta \tau_y
-	\end{align}
-	\label{eq:hamiltonian}
-	\end{small}
+	The non-zigzag system is in the symmetry class BDI \cite{pientka2017topological}, unless the additional symmetries are broken due to for example a difference in superconducting gap magnitude between the two superconductors.
+	Using the software package Qsymm\cite{varjas2018qsymm}, we find that the symmetry class of our system to be $\mathcal{D}$, because we break this chiral/time-reversal symmetry resulting from the mirror symmetric junction.
 
@@
 	Each site has two orbitals: spin and electron-hole.
-	There are four different types of sites (and thus four different Hamiltonians): the top superconductor, the bottom superconductor, the normal region, and a normal region with a variable potential offset, forming a barrier to simulated an imperfect NS interface.
+	There are four different types of sites (and thus four different Hamiltonians): the top superconductor, the bottom superconductor, the normal region, and a normal region with a variable potential offset, forming a barrier to simulate an imperfect NS interface.
 	A schematic of such kwant systems is depicted in Fig.~\ref{fig:kwant_system}.
-	We can also make the system infinite in for example the $x$ direction by connecting the sites on the left border with those on the right border with a $\kx$ dependent hopping.
+
+	\comment{The model hamiltonian is converted into the tight binding form by substitution}
+	In order to turn the set of Hamiltonians, Eqs.\eqref{eq:hamiltonian_n} and \eqref{eq:hamiltonian_s} into a tight binding model, we write the equations into differential form by substituting $k_\alpha \rightarrow - i \partial_\alpha$, $\alpha \in \left\{ x, y \right\}$, and thereafter discretize on a rectangular grid.
+	In practice, this is implemented using the Kwant discretizer module.
 
@@
 	For example, calculating the bandstructure of a system is performed by taking a translationally invariant system and calculating the eigenvalues for different momenta.
+	The system is made translationally invariant, in for example the $x$ direction, by connecting the sites on the left border with those on the right border with a $\kx$ dependent hopping.
 

### 2019-02-01 thesis_report/theory.tex
Simple terms figure, updated theory and introduction
Added to methods and theory

@@
 
-\chapter{Theory}
+\chapter{Theoretical Background}
 The topological quantum computer uses pairs of Majorana particles as its unit of computation (qubit).
@@
 	Two important ingredients required for realizing Majorana fermions are strong spin-orbit coupling, and a strong interaction with the applied magnetic field.
-	It is the normal conductor which brings these two physical effects to the mix.
+	It is the semiconductor which brings these two physical effects to the mix.
 	Note that the Hamiltonian of the normal region is the same for electrons and holes, except for the sign.
 	The Hamiltonian terms provided in this section are relevant to the electron states.
+	In figure \ref{fig:ham_simple_terms}, the effect of the various terms in the Hamiltonian on the dispersion relation is shown.
+
+	\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.95\columnwidth]{figures/simple_terms}
+	\caption{Energy dispersion of electrons with different physical effects (spin orbit and magnetic field).
+	The dashed line in the figure with both spin orbit coupling and zeeman field corresponds to the case when magnetic field is not aligned with the spin orbit direction.}
+	\label{fig:ham_simple_terms}
+	\end{figure}
+
+	\subsection{Kinetic term}
+		We rewrite the kinetic term in the Schrodinger equation into it's momentum form by noting $- i \partial_x \rightarrow \kx$:
+		\begin{equation}
+			H_\text{kin} = - \frac{\hbar^2}{2 \meff} \nabla^2 = \frac{\hbar^2}{2 \meff} \left( \kx^2 + \ky^2 \right)
+		\end{equation}
+		The effective mass is a way of capturing the periodic potential of the crystal lattice into a single term.
+		Its value differs per material.
 
@@
 
+	\subsection{Superconducting Hamiltonian}
 		For the purpose of creating Majorana's, we are interested in two main aspects of superconductivity: the energy gap surrounding the Fermi energy (due to the depletion of states), and the electron-hole (/particle-hole) symmetry.
 		We are thus not interested in the paired up electrons (Cooper pairs), and only wish to model the electronic (unpaired) modes.
-		This can be achieved by modeling superconductivity with the Boguliubov de Gennes Hamiltonian:
+		This can be achieved by modeling superconductivity with the Boguliubov de Gennes Hamiltonian, which ensures particle-hole symmetry:
 
 		\begin{equation}
-		\mathbf{H}_\text{BdG} = \begin{bmatrix} H & \Delta \\ \Delta^\dagger & H \end{bmatrix}
+		\mathbf{H}_\text{BdG} = \begin{bmatrix} H & \Delta \\ \Delta^\dagger & -H \end{bmatrix}
+		\label{eq:bdg}
 		\end{equation}
 
-		The block matrix restricts the structure of the system in the electron-hole basis, and ensures particle-hole symmetry.
-		For $\Delta \neq 0$ one indeed induces a identically sized gap in the spectrum.
+		Note that Eq.\eqref{eq:bdg} describes a block matrix: both $H$ and $\Delta$ can be matrices themselves, where the degrees of freedom correspond to for example spin, or discretized positions.
+		Using this basis, one is able to describe a heterogeneous system, containing both superconducting and normal regions.
+		As an example, we write the Hamiltonian of a heterogeneous 1D system, consisting of a superconductor extending from $x = -\infty$ to $0$, and a normal system from  $x = 0$ to $\infty$:
+
+		\begin{equation}
+			\mathbf{H} =  \Theta \left(-x\right) \begin{bmatrix} H_\text{SC, kin} & \Delta \\ \Delta^\dagger & -H_\text{SC, kin} \end{bmatrix} + \Theta \left(x\right)  \left( \tau_z \otimes H_\text{normal} \right)
+			\end{equation}
+		where, 
+		\begin{equation}
+			\Theta(x) = \begin{cases} 1 & x \geq 0 \\ 0 & x < 0 \end{cases}
+		\end{equation}
 

### 2019-02-01 sns_system.py
add the disordered shapes

@@ -43,7 +43,7 @@ dummy_params_raw = dict(g_factor_middle=1,
 dummy_params = dict(**constants,
                     **dummy_params_raw)
 
-def create_parallel_sine(distance, z_x, z_y):
+def create_parallel_sine(distance, z_x, z_y, rough_edge=None):
     def _parallel_sine(x, distance, z_x, z_y):
         g       = lambda t: z_y * math.sin(2*np.pi/z_x*t)
         g_prime = lambda t: z_y * 2*np.pi/z_x*math.cos(2*np.pi/z_x*t)
@@ -56,12 +56,36 @@ def create_parallel_sine(distance, z_x, z_y):
         t = fsolve(_x, x)
         return y(t)
 
-    xdim = np.linspace(0, z_x, 1000)
-    ydim = [_parallel_sine(x, distance, z_x, z_y) for x in xdim]
-    
-    parallel_sine = scipy.interpolate.interp1d(xdim, ydim)
-    
+    xs = np.linspace(0, z_x, 1000)
+    ys = [_parallel_sine(x, distance, z_x, z_y) for x in xs]
+
+    if rough_edge is not None:
+        X, Y, salt = rough_edge
+
+        # Calculate the unit vector to the sine
+        tck = scipy.interpolate.splrep(xs, ys)
+        dydx = scipy.interpolate.splev(xs, tck, der=1)
+        unit_vectors = 1 / (1 + dydx**2) * np.array([-dydx, np.ones_like(dydx)])
+
+        # Generate a disordered boundary parameterized by (X, Y, salt)
+        rand = lambda i: X * kwant.digest.uniform(str(i), salt=str(salt))
+        rands = [rand(i) for i in range(int(z_x / Y) - 2)]
+        rands = [0, *rands, 0]  # make sure that it starts and ends with 0 (for periodicity)
+        ys_disorder = scipy.interpolate.interp1d(
+            np.linspace(0, z_x, len(rands)), rands, kind='quadratic')(xs)
+        ys_disorder -= ys_disorder.mean()
+
+        # Disorder in the direction normal to the sine
+        dxys = ys_disorder * unit_vectors
+
+        # Modify xs and ys to include the disorder
+        xs[1:-1] += dxys[0, 1:-1]
+        ys[1:-1] += dxys[1, 1:-1]
+
+    parallel_sine = scipy.interpolate.interp1d(xs, ys)
+
[…]

### 2019-02-01 thesis_report/results.tex
Added everything to the thesis figures notebook

@@
 	\section{Finding the mechanism responsible for the increased gap}
-		\comment{We compare different techniques to calculate the bandstructure of a 1D system.}
+		\comment{We compare different techniques to calculate the bandstructure of a straight system.}
 		We verify the validity of the analytic model described in the Methods, to compute the bandstructure of a straight system in a tilted magnetic field. 
@@
 		To show the validity of neglecting spin orbit in the transverse direction, we also compute the scattering matrix including the additional term, and again use the bound state condition to obtain the spectrum (labeled Kwant with SOI SJL).
-		We also perform the fully accurate calculation of the spectrum by simply computing the bandstructure of the corresponding Kwant system (labeled Full 1D kwant system): this result serves as the benchmark for the other techniques.
+		We also perform the fully accurate calculation of the spectrum by simply computing the bandstructure of the corresponding Kwant system (labeled Full ribbon kwant system): this result serves as the benchmark for the other techniques.
 

### 2019-02-01 thesis_report/theory.tex
Added everything to the thesis figures notebook

@@
 \section{Topology, Symmetry, and Majorana bound states}
-
-	The Wikipedia definition of mathematical topology is as follows:
-
-	\begin{quote}Topology can be formally defined as "the study of qualitative properties of certain objects (called topological spaces) that are invariant under a certain kind of transformation
-	\cite{noauthor_topology_2018}
-	\end{quote}
-
-	Similarly, in condensed matter physics, topology refers to the study of properties of a system, which are guaranteed by particular symmetries of the Hamiltonian.
+	In condensed matter physics, topology refers to the study of properties of a system, which are guaranteed by particular symmetries of the Hamiltonian.
 	These symmetries are present within a particular range of parameters, and any variation of those parameters within that range does not destroy these \emph{topologically protected} properties.

### 2019-02-01 thesis_report/results.tex
fixed thesis fig for ci

@@
 \chapter{Results \& Discussion}
-		In this chapter, we show how the properties of the system change under introduction of the zigzag geometry.
-		Additionally, we attempt to isolate the mechanism behind the improved properties by estimating the gap size through the quasiclassical model introduced in the Methods chapter.
+		In this chapter, we show how some properties of the system change by introduction of the zigzag geometry.
+		Additionally, we attempt to isolate the mechanism behind the improved properties by estimating the gap size through the quasiclassical model introduced in the Methods chapter\ref{}.
 

### 2019-02-01 thesis_report/results.tex
Changed QC image

--- 2019-02-01 thesis_report/results.tex
@@
 % -*- root: ./report.tex -*-
-\chapter{Results \& Discussion}
-		In this chapter, we show how the properties of the system change under introduction of the zigzag geometry.
-		Additionally, we attempt to isolate the mechanism behind the improved properties by estimating the gap size through the quasiclassical model introduced in the Methods chapter.
+\chapter{Results \& Discussion}\label{chap:results}
+		In this chapter, we show how some properties of the system change by introduction of the zigzag geometry.
+		Additionally, we attempt to isolate the mechanism behind the improved properties by estimating the gap size through the quasiclassical model introduced in chapter \ref{chap:methods}.
 
@@
 			\centering
-			\includegraphics[width=0.95\columnwidth]{figures/quasiclassical_approximation}
+			\includegraphics[width=0.95\columnwidth]{figures/z_y_vs_E_gap}
 			\caption{Comparison of the topological gap computed using a full zigzag system implemented in Kwant with the quasiclassical estimate.

### 2019-02-02 thesis_report/results.tex
Added Bass corrections

@@
 			\includegraphics[width=0.55\columnwidth]{figures/bandstructures}
-			\caption{Figure of the bandstuctures.
-			Where the lines are (blue) $\phi=0$, $B=0$ and (red) $\phi=\pi$, $B \ne 0$.
-			and the subplots (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W$ is the junction width.
+			\caption{Figure of the bandstuctures corresponding to the system in Fig.~\ref{fig:zigzag_methods}.
+			Blue lines correspond to $\phi=0$, $B=0$, red lines to $\phi=\pi$, $B = 1$.
+			Thre three subplots are for different amplitudes of zigzag: (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W=200$\si{\nm} is the junction width.
 			We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
+			The value of the remaining parameters are, $\alpha=20$ \si{\milli \eV \nm}, $g=26$, $\meff=0.02$\si{\electronmass}, $\mu=20$ \si{\milli \eV}, $\Delta=1$ \si{\milli \eV}.
 			\label{fig:bandstuctures}}
 			\end{figure}
+
 			\comment{We calculate the bandstructure for varying amount of zigzag.}
-			We implement a tightbinding version of the model described in the Methods section (a two dimensional SNS junction with a Rashba BdG Hamiltonian) using Kwant.
-			In figure~\ref{fig:bandstuctures}, the bandstructure for zigzag systems (sawtooth shape) with varying amplitude is displayed.
-			As the zigzag introduces super cell, we see a folded bandstructure.
+			We implement a tight-binding version of the model described in the section \ref{sec:physical_picture}(a two dimensional SNS junction with a Rashba BdG Hamiltonian) using Kwant.
+			In figure~\ref{fig:bandstuctures}, the bandstructure for zigzag systems~\ref{fig:zigzag_methods} (sawtooth shape) with varying amplitude is displayed.
+			Because the zigzag has to be modeled using a super cell, we see a folded bandstructure.
 			For comparisons sake, we take the same cell size for the ribbon structure so the bandstructure is folded in the same way.
@@
 			The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size is increased more than an order of magnitude.
-			This effect is due to the fact that the modes where the gap is smallest, when the momentum is almost completely focused along the strip ($k_x=k_F$), are cut off by the zigzag geometry.
-			Also apparent is the significant reduction of group velocity; the slope of the bands is virtually zero.
-			The size of the gap, together with the velocity, directly relate to the Majorana coherence length (Eq.~\eqref{eq:majorana_coherence_length}), the effect of which is seen in the following section.
+			This happens because the modes where the gap is the smallest, when the momentum is almost completely focused along the strip ($k_x=k_F$), are cut off in a zigzag geometry.
+			There is also a significant reduction of the group velocity where in Fig.~\ref{fig:bandstuctures} (c) the bands are almost completely flat.
+			The size of the gap, together with the velocity, directly relate to the Majorana coherence length (Eq.~\eqref{eq:majorana_coherence_length}), which will be discussed in the following section.
 
 			\comment{The introduction of an SN interface at many angles also increases performance.}
-			Additionally we note that, in the presence of normal reflection, due to the availability of NS interfaces at a wide range of slopes, a zigzag system will perform more favorable.
-			One can imagine that the normally reflected part of a wavefunction will, in a zigzag system, eventually ``find'' a surface with which it is perpendicular to.
-			The transparency of the SN interface is thus improved for non-transversal modes.
+			Finally, in the presence of normal reflection, due to the availability of NS interfaces at a wide range of slopes, a zigzag system has an increased effective transmission.
+			In a zigzag system, the normally reflected part of a wavefunction will eventually intersect a surface with which it is nearly perpendicular to.
+			The transparency of the NS interface is thus improved for non-transversal modes.
 
@@
 			\comment{We calculate the lowest eigenfunction and plot the density.}
-			Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinusoids.
+			Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve, and vertically offset sinusoids.
 			In figure~\ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.

### 2019-02-03 thesis_report/conclusion.tex
Conclusion

@@
 \chapter{Conclusion}
+In the studied model, the introduction of a zigzag geometry increases the topological gap by over an order of magnitude, as well as offering a substantial reduction of the Majorana length.
+Additionally, the breaking of BDI symmetry into D symmetry results in a cleaner topological phase.
+Together, these improvements directly affect the robustness of the Majorana state, potentially bringing us closer to reliably create topological devices.
 
-\section{Feasability of implementation}
+\comment{With the current quasiclassical analogy, we are not able to explain the improvements of zigzag.}
+The current used quasiclassical analogy, applied in the most lenient form, is not able to explain the increased gap of a zigzag system.
+Furthermore, numerical simulation points out that the optimal geometry does not always coincide with the minimal trajectory length.
+It is therefore unsure whether the improvement of the gap can be fully attributed to the elimination of long trajectories, or, if the arising phenomena are due to other mechanisms.
+In any case, the improvements are stable under a wide range of parameters, and the topological gap varies gradually as a function of geometry, indicating the effect is not merely coincidental.
+Further study should be devoted to isolating the working principle behind the improvements of the zigzag geometry.
+
+\comment{Extensions: we omit several physical effects, disorder, electrostatics, etc.}
+In the model used, we omit several physical effects, such as, disorder, electrostatics, the orbital effect, etc.
+Apart from experimental verification, further study is required to see whether the conclusions of this model are valid.
+
+\comment{Current fabrication techniques seem compatible with the proposed geometry, and experimental verification should point out whether it holds up to its promise.}
+Current fabrication techniques seem compatible with the proposed geometry, and experimental verification should point out whether it holds up to its promise.
+We note that slight modifications to the geometry, for example to ease measurement, should not have large implications on the physics.
+Currently, experimental groups have already fabricated zigzag devices (e.g. the image on the cover of this thesis), and measurements are underway.
+
+\comment{It would be interesting to study what geometry creates an optimal environment for Majorana modes to exist.}
+We have studied sawtooth, snake like and offset sinosoid modulation of the semiconductor region, but perhaps a more exotic shape will be optimal.
+A study optimizing the geometry for supporting Majorana's would be an interesting continuation.

### 2019-02-03 thesis_report/introduction.tex
updated intro with new images

@@
 	Disambiguating electrons and holes into their Majorana counterparts is often analogized with splitting a complex number into its real and imaginary part.
-	In terms of the creation and annihilation operators of electrons, respectively $\hat{c}^\dagger$ and $\hat{c}$, we write,
+	We write the Majorana operators in terms of the creation(annihilation) and annihilation(creation) operators of electrons(holes), respectively $\hat{c}^\dagger$ and $\hat{c}$:
+
 	\begin{align}
 		\hat{c} =  \frac{1}{2} \left( \gamma_1 - i\gamma_2 \right) && \hat{c}^\dagger = \frac{1}{2} \left( \gamma_1 + i\gamma_2 \right)
+		\label{eq:intro_ferm2maj}
 	\end{align}
 
-	\comment{Forming a kitaev chain}
-	Without going into to much detail, and at the cost of making gross oversimplifications, one can suppose that an electron consists of two Majorana particles.
-	Borrowing an analogy with domino stones from the online course Topology in Condensed Matter\cite{noauthor_topology_2015}, we can see an electron as a domino stone: the two ends, seperated by a line, each correspond to a Majorona particle.
+	Inverting this, we get,
+	\begin{align}
+		\gamma_1 = \hat{c} + \hat{c}^\dagger && \gamma_2 = i \left( \hat{c} - \hat{c}^\dagger \right)
+		\label{eq:intro_maj2ferm}
+	\end{align}
+
+	Note that the basic excitation is still a fermion (electron/hole); one cannot have just one Majorana, they always come in pairs.
+	The idea is to create a system where we have a single pair of Majoranas which is seperated in space.
+
+	A system in which this seperation can be accomplished was first proposed by Kitaev\cite{kitaev_unpaired_2001}.
+	We consider a one dimensional chain of sites which can host a single fermion, and thus a pair of Majoranas.
+	Suppose that the occupation of a site by a fermion comes at the cost of energy $\mu$.
+	Also, we consider the situation where there is an interaction energy between neighboring sites: $t$ quantifies the energy cost of one site being occupied while the adjacent isn't, and $\Delta$ is the gain in energy if adjacent sites are both occupied or empty.
+	This leads to the following Hamiltonian:
+
+	\begin{equation}
+		H = -\mu \sum_n \hat{c}_n^\dagger \hat{c}_n
+		- t \sum_n \left( \hat{c}_{n+1}^\dagger \hat{c}_n +\text{h.c.} \right) 
+		+ \Delta \sum_n \left( \hat{c}_n \hat{c}_{n+1} +\text{h.c.} \right) 
+	\end{equation}
+
+	Considering equation \eqref{eq:intro_ferm2maj} we can also write the Hamiltonian above using Majorana operators.
+	In this way, we get a Hamiltonian describing pairing energies between Majoranas on adjacent sites.
+	In figure, we discern two extremes:
+	one is the situation where the pairing energy is minimal for Majorana pairs on the same site, the other is when the energy is minimal for pairing between of Majoranas from adjacent sites.
+
+	Borrowing the analogy from the online course Topology in Condensed Matter\cite{noauthor_topology_2015}, we can see an electron as a domino stone: the two ends, seperated by a line, each correspond to a Majorona particle.
 	In the figure below\cite{noauthor_topology_2015}, the dominoes, and thus electrons, have been placed in a chain:\\
@@
 	\end{centering}
+
+	Corresponding to the system above, we have a Hamiltonian describing the physics of the system.
 

### 2019-02-03 thesis_report/introduction.tex
updated intro

@@
 	In this way, we get a Hamiltonian describing pairing energies between Majoranas on adjacent sites.
-	In figure, we discern two extremes:
-	one is the situation where the pairing energy is minimal for Majorana pairs on the same site, the other is when the energy is minimal for pairing between of Majoranas from adjacent sites.
+	In figure, we discern two extremes, one is the situation where the pairing energy is minimal for Majorana pairs on the same site:
+	\begin{figure}[htb!]
+	\centering
+	\includegraphics[width=0.95\columnwidth]{images/majorana_trivial_pairing}
+	\caption{Trivial Majorana pairing in a Kitaev chain}
+	\label{fig:trivial_majoranas}
+	\end{figure}
 
-	Borrowing the analogy from the online course Topology in Condensed Matter\cite{noauthor_topology_2015}, we can see an electron as a domino stone: the two ends, seperated by a line, each correspond to a Majorona particle.
-	In the figure below\cite{noauthor_topology_2015}, the dominoes, and thus electrons, have been placed in a chain:\\
-
-	\begin{centering}
-	\includegraphics[width=0.95\columnwidth]{images/majorana_dominoes}
-	\end{centering}
-
-	Corresponding to the system above, we have a Hamiltonian describing the physics of the system.
-
-	In a regular system, the Majoranas on each end of stone are paired locally, as depicted in the figure below:\\
-
-	\begin{centering}
-	\includegraphics[width=0.95\columnwidth]{images/trivial_dominoes}
-	\end{centering}
-
-	Now suppose one would be able to shift the pairing, such that the Majoranas form pairs with the Majoranas on adjacent stones:\\
-
-	\begin{centering}
-	\includegraphics[width=0.95\columnwidth]{images/topological_dominoes}
-	\end{centering}
+	The other is when the energy is minimal for pairing between of Majoranas from adjacent sites:
+	\begin{figure}[htb!]
+	\centering
+	\includegraphics[width=0.95\columnwidth]{images/majorana_topological_pairing}
+	\caption{Topological Majorana pairing in a Kitaev chain}
+	\label{fig:topological_majoranas}
+	\end{figure}
 
@@
 	This is the state we are interested in: the Majorana state, where two Majoranas are seperated in space.
-	This physical seperation has the effect of not allowing simple local perturbations to disturb the system.
+	This physical seperation has the effect of not allowing simple local perturbations to disturb the system, thus inherently protecting the system against decoherence.
 

### 2019-02-03 thesis_report/introduction.tex
updated references

@@
 	The idea to use coherent quantum states as a means to perform complex calculations first appeared in the beginning of the 80's.
-	A handful of papers had already been published on the matter, when, during a keynote speech at the California Institute of Technology, Nobel laureate Richard Feynman suggested its importance with respect to physics simulations .
+	A handful of papers had already been published on the matter, when, during a keynote speech\cite{feynman_simulating_1982} at the California Institute of Technology, Nobel laureate Richard Feynman suggested its importance with respect to physics simulations .
 	To put his idea in very simple terms, calculating the quantum mechanical state of a system on a conventional computer scales exponentially with respect to the system size.
@@
 	With the potential applications in mind, a lot of resources and effort has been put into realising such a quantum computer in recent years.
-	Recently, apart from being a largely publicly funded effort, the private sector has also started to recognize the potential of the technology: large companies such as Microsoft, Google and IBM are investing into the development of a quantum computer.
+	Recently, apart from being a largely publicly funded effort, the private sector has also started to recognize the potential of the technology: large companies such as Microsoft\cite{noauthor_why_nodate}, Google\cite{noauthor_quantum_nodate} and IBM\cite{noauthor_ibm_2018} are investing into the development of a quantum computer.
 	As of this moment, working quantum computers have been realized on a very small scale: calculations of meaningful scale are still not possible.
@@
 	Then later, switching to electronics, binary states were implemented in the form of vacuum tubes, and later, up to today, it is the transistor which acts as the basic unit of computation.
-	Similarly, because quantum computing is still in its infancy, there are still many contenders for what the underlying technology will be: what physical system will form the basis for the quantum bit, the qubit.
-	Some of the current platforms for implementing a qubit being pursued are the transmon qubit, NV-centers, quantum dots, and Majorana bound states.
+	Similarly, because quantum computing is still in its infancy, there are still many contenders for what the underlying technology will be: what physical system will form the basis for the quantum bit, the qubit?
+	Some of the current platforms for implementing a qubit being pursued are the transmon qubit\cite{wendin_quantum_2017}, NV-centers\cite{childress_diamond_2013}, quantum dots\cite{kloeffel_prospects_2013}, and Majorana bound states\cite{wendin_quantum_2017}.
 	Majorana bound states (MBSs) are a promising candidate to form the basis of a stable platform for topological quantum computing, and the specific way to create them are the topic of study in this manuscript.

### 2019-02-03 thesis_report/theory.tex
updated references

@@
 \section{Normal region}
-	Two important ingredients required for realizing Majorana fermions are strong spin-orbit coupling, and a strong interaction with the applied magnetic field.
+	Two important ingredients required for realizing Majorana fermions are strong spin-orbit coupling, and a strong interaction with the applied magnetic field~\cite{lutchyn_majorana_2018}.
 	It is the semiconductor which brings these two physical effects to the mix.

### 2019-02-04 thesis_report/introduction.tex
updated intro, addition of thesis committee

@@
 \comment{The history of quantum computing and why QC is important}
-	The idea to use coherent quantum states as a means to perform complex calculations first appeared in the beginning of the 80's.
-	A handful of papers had already been published on the matter, when, during a keynote speech\cite{feynman_simulating_1982} at the California Institute of Technology, Nobel laureate Richard Feynman suggested its importance with respect to physics simulations .
+	The idea of using coherent quantum states as a means to perform complex calculations first appeared in the beginning of the 80's.
+	A handful of papers had already been published on the matter, when, during a keynote speech~\cite{feynman_simulating_1982} at the California Institute of Technology, Nobel laureate Richard Feynman suggested its importance with respect to physics simulations.
 	To put his idea in very simple terms, calculating the quantum mechanical state of a system on a conventional computer scales exponentially with respect to the system size.
-	By making a computer that is based on quantum states itself, and making a mapping between those states and the system you want to simulate, the idea is that this scaling becomes polynomial.
-	Beyond its significance in physics simulations, quantum computers have been suggested to be used for other, perhaps more pragmatic tasks, including topics like cryptography, optimization and search algorithms.
-	With the potential applications in mind, a lot of resources and effort has been put into realising such a quantum computer in recent years.
-	Recently, apart from being a largely publicly funded effort, the private sector has also started to recognize the potential of the technology: large companies such as Microsoft\cite{noauthor_why_nodate}, Google\cite{noauthor_quantum_nodate} and IBM\cite{noauthor_ibm_2018} are investing into the development of a quantum computer.
-	As of this moment, working quantum computers have been realized on a very small scale: calculations of meaningful scale are still not possible.
+	By making a computer that is based on quantum states itself, and creating a mapping between those states and the system you want to simulate, this scaling becomes polynomial.
+	Beyond their significance in physics simulations, quantum computers could be used in a more pragmatic way, for implementing cryptography, optimization and search algorithms.
+	With the potential applications in mind, a lot of resources and effort have been put into building such a quantum computer in the last years.
+	Recently, apart from being a largely publicly funded effort, the private sector has also started to recognize the potential of this technology: large companies such as Microsoft~\cite{noauthor_why_nodate}, Google~\cite{noauthor_quantum_nodate} and IBM~\cite{noauthor_ibm_2018} are investing into the development of a quantum computer.
+	As of this moment, functional quantum computers have been realized on a very small scale: calculations of meaningful magnitude are still not possible.
 
 \comment{It is still an open question what the implementation for a qubit will be, but majorana's are one of the contenders}
-	If we consider the evolution of the regular computer, we see that the technological/physical platform for the bit, something which can be in either of two states, 1 or 0, has been constantly changing.
-	For the earliest computers, it was complex mechanical systems with gears and cogs.
-	Then later, switching to electronics, binary states were implemented in the form of vacuum tubes, and later, up to today, it is the transistor which acts as the basic unit of computation.
+	If we consider the evolution of the regular computer, we see that the technological/physical platform for the bit, the binary unit of information, has been constantly changing.
+	For the earliest computers, complex electromechanical systems with gears and cogs fulfilled this role.
+	Soon after, binary states were implemented in the form of vacuum tubes, and nowadays it is the transistor which acts as the basic unit of computation.
 	Similarly, because quantum computing is still in its infancy, there are still many contenders for what the underlying technology will be: what physical system will form the basis for the quantum bit, the qubit?
-	Some of the current platforms for implementing a qubit being pursued are the transmon qubit\cite{wendin_quantum_2017}, NV-centers\cite{childress_diamond_2013}, quantum dots\cite{kloeffel_prospects_2013}, and Majorana bound states\cite{wendin_quantum_2017}.
-	Majorana bound states (MBSs) are a promising candidate to form the basis of a stable platform for topological quantum computing, and the specific way to create them are the topic of study in this manuscript.
+	The platforms which are currently explored for the implementation of a qubit include the transmon qubit~\cite{wendin_quantum_2017}, NV-centers~\cite{childress_diamond_2013}, quantum dots~\cite{kloeffel_prospects_2013}, and Majorana bound states~\cite{wendin_quantum_2017}.
+	The main problem with most of the quantum computing platforms is that it is very difficult to keep the qubit from decohering.
+	To counteract this, apart from trying to reduce the decoherance rate of the qubit, much effort is put into devising quantum error correction codes: devise strategies such that potential errors can be detected and corrected for.
+	For topological quantum computers, employing Majorana bound states as qubits, information is encoded in such a way that it is inherently protected against decoherence.
+	This \emph{topological} protection of the quantum states makes Majorana bound states (MBSs) a promising candidate as a stable platform for quantum computing.
+	However, the implementation of such Majorana bound states has proven elusive, and much research is being done on designing a device that reliably and unequivocally hosts Majoranas.
+	In this manuscript, we devise a novel way to improve the reliability of such devices, while remaining compatible with current fabrication techniques.
 
@@
 
-	A system in which this seperation can be accomplished was first proposed by Kitaev\cite{kitaev_unpaired_2001}.
+	A system in which this seperation can be accomplished was first proposed by Kitaev~\cite{kitaev_unpaired_2001}.
 	We consider a one dimensional chain of sites which can host a single fermion, and thus a pair of Majoranas.
@@
 	A realistic experimental implementation of Kitaev's model did not emerge until the similar works of Lutchyn et.
-al\cite{lutchyn_majorana_2010} and Oreg et.
-al\cite{ oreg_helical_2010}, where they proposed an experiment composed of a semiconducting nanowire deposited onto a superconductor.
+al~\cite{lutchyn_majorana_2010} and Oreg et.
+al~\cite{ oreg_helical_2010}, where they proposed an experiment composed of a semiconducting nanowire deposited onto a superconductor.
 	They predicted that, if the semiconductor has strong spin-orbit coupling, a magnetic field applied along the wire axis, as well as a carefully tuned chemical potential, Majoranas would appear at the ends of the nanowire.
@@
 	A more convincing case could be made if one could control the system in such a way that the presence of Majoranas can be turned on or off.
-	This feature is realized in a relatively recent proposal by Pientka et. al\cite{pientka_topological_2017}, where, instead of a nanowire, a two-dimensional strip of semiconductor is used.
+	This feature is realized in a relatively recent proposal by Pientka et. al~\cite{pientka_topological_2017}, where, instead of a nanowire, a two-dimensional strip of semiconductor is used.
 	On each side of the strip a superconductor is placed, forming a Josephson junction.

### 2019-02-04 thesis_report/title.tex
Updated thesis
updated intro, addition of thesis committee

@@
+% -*- root: ./report.tex -*-
 \begin{titlepage}
@@
     Project duration: & \multicolumn{2}{l}{March 1, 2018 -- November 28, 2018} \\
-    Thesis committee: & dr.\ A.\ Akhmerov, & TU Delft, supervisor \\
-        & MSc.\ B.\ Nijholt, & TU Delft \\
+    Thesis committee: & dr.\ A.\ Akhmerov, & TU Delft \\
+                      & MSc.\ B.\ Nijholt, & TU Delft\\
+                      & Prof.\ dr.\ G.A.\ Steele, & TU Delft \\
+                      & dr.\ M.T.\ Wimmer, & TU Delft \\
 \end{tabular}

### 2019-02-04 thesis_report/introduction.tex
remove output ipynb

@@
 	Majorana particles are particles that always come in pairs: one pair of Majorana's forms a single electronic state.
-	Disambiguating electrons and holes into their Majorana counterparts is often analogized with splitting a complex number into its real and imaginary part.
-	We write the Majorana operators in terms of the creation(annihilation) and annihilation(creation) operators of electrons(holes), respectively $\hat{c}^\dagger$ and $\hat{c}$:
+	Disambiguating electrons and holes into their Majorana counterparts is analogous to splitting a complex number into its real and imaginary part.
+	We write the Majorana operators in terms of the creation (annihilation) and annihilation (creation) operators of electrons (holes), respectively $\hat{c}^\dagger$ and $\hat{c}$:
 
@@
 
-	Inverting this, we get,
+	Inverting this, we obtain,
 	\begin{align}
@@
 	Note that the basic excitation is still a fermion (electron/hole); one cannot have just one Majorana, they always come in pairs.
-	The idea is to create a system where we have a single pair of Majoranas which is seperated in space.
+	The idea is to create a system where we have a single pair of Majoranas which is separated in space.
 
-	A system in which this seperation can be accomplished was first proposed by Kitaev~\cite{kitaev_unpaired_2001}.
+	A system in which this separation can be accomplished was first proposed by Kitaev~\cite{kitaev_unpaired_2001}.
 	We consider a one dimensional chain of sites which can host a single fermion, and thus a pair of Majoranas.
 	Suppose that the occupation of a site by a fermion comes at the cost of energy $\mu$.
-	Also, we consider the situation where there is an interaction energy between neighboring sites: $t$ quantifies the energy cost of one site being occupied while the adjacent isn't, and $\Delta$ is the gain in energy if adjacent sites are both occupied or empty.
+	Also, we consider the situation where there is an interaction energy between neighboring sites: $t$ quantifies the energy cost of one site being occupied while the adjacent is not, and $\Delta$ is the gain in energy if adjacent sites are both occupied or empty.
 	This leads to the following Hamiltonian:
@@
 	In this way, we get a Hamiltonian describing pairing energies between Majoranas on adjacent sites.
-	In figure, we discern two extremes, one is the situation where the pairing energy is minimal for Majorana pairs on the same site:
+	We discern two extremes: In figure \ref{fig:trivial_majoranas}, the situation where the pairing energy is minimal for Majorana pairs on the same site:
 	\begin{figure}[htb!]
@@
 	As is apparent from the above image, this would leave two unpaired Majoranas at the ends of the chain.
-	This is the state we are interested in: the Majorana state, where two Majoranas are seperated in space.
-	This physical seperation has the effect of not allowing simple local perturbations to disturb the system, thus inherently protecting the system against decoherence.
+	This is the state we are interested in: the Majorana state, where two Majoranas are separated in space.
+	This physical separation has the effect of not allowing simple local perturbations to disturb the system, thus inherently protecting the system against decoherence.
 

### 2019-02-04 thesis_report/introduction.tex
Majorana's -> Majoranas

@@
 
-\comment{It is still an open question what the implementation for a qubit will be, but majorana's are one of the contenders}
+\comment{It is still an open question what the implementation for a qubit will be, but Majoranas are one of the contenders}
 	If we consider the evolution of the regular computer, we see that the technological/physical platform for the bit, the binary unit of information, has been constantly changing.
@@
 	\comment{What are Majorana bound states}
-	Majorana particles are particles that always come in pairs: one pair of Majorana's forms a single electronic state.
+	Majorana particles are particles that always come in pairs: one pair of Majoranas forms a single electronic state.
 	Disambiguating electrons and holes into their Majorana counterparts is analogous to splitting a complex number into its real and imaginary part.
@@
 
-\section{Ways to make Majorana's: nanowires \& sns system}
+\section{Ways to make Majoranas: nanowires \& sns system}
 	A realistic experimental implementation of Kitaev's model did not emerge until the similar works of Lutchyn et.
@@
 	Using the Josephson junction, one can use the supercurrent which flows between the two superconductors to control whether the system is in a topological phase (meaning it contains Majoranas), or not.
-	The system has addition advantages, namely the system allows for Majorana's to be created at lower magnetic fields, the system is more compatible with convential semiconductor technology, and the Josephson junction allows for new ways to detect the topological phase of the system.
+	The system has addition advantages, namely the system allows for Majoranas to be created at lower magnetic fields, the system is more compatible with convential semiconductor technology, and the Josephson junction allows for new ways to detect the topological phase of the system.
 

### 2019-02-04 thesis_report/results.tex
Majorana's -> Majoranas

@@
 
-	\comment{Introduction of a zigzag opens up the gap, creates a more stable topological phase diagram, and decreases coherence length of Majorana's}
+	\comment{Introduction of a zigzag opens up the gap, creates a more stable topological phase diagram, and decreases coherence length of Majoranas}
 	\section{Increased isolation and stability of the Majorana state}
@@
 
-		\comment{Introduction of a zigzag leads to localization of the Majorana's}
+		\comment{Introduction of a zigzag leads to localization of the Majoranas}
 		\subsection{Majorana decay length}
@@
 
-			\comment{In a straight system, the Majorana's are very poorly localized.}
+			\comment{In a straight system, the Majoranas are very poorly localized.}
 			For the ribbon system, we see that the decay of the density is slow: the wavefunction clearly extends to the middle of the system, not showing the delocalization sought after.
-			Apart from the density, as mentioned in the Theory chapter, overlap of Majorana's leads to a non-zero energy of the state.
-			Taking this into consideration, we see that the energy of the Majorana state in the straight system is only barely below the next lowest lying eigenstate: the Majorana's are very poorly localized, and topological protection against perturbations is minimal.
+			Apart from the density, as mentioned in the Theory chapter, overlap of Majoranas leads to a non-zero energy of the state.
+			Taking this into consideration, we see that the energy of the Majorana state in the straight system is only barely below the next lowest lying eigenstate: the Majoranas are very poorly localized, and topological protection against perturbations is minimal.
 
@@
 			The delocalized nature of the wavefunctions is clearly visible through the density plots.
-			Quantitatively, the improvement in localization of the Majorana's is also distinctly apparent: the energies of the Majorana states are orders of magnitude lower than the energy of the second lowest lying wavefunctions.
+			Quantitatively, the improvement in localization of the Majoranas is also distinctly apparent: the energies of the Majorana states are orders of magnitude lower than the energy of the second lowest lying wavefunctions.
 			As mentioned in the previous section, this can be attributed due to the way the gap and velocity factor into the Majorana coherence length.
@@
 
-		\comment{Zigzag Majorana's have a cleaner phase diagram due to the reduction in symmetry class}
+		\comment{Zigzag Majoranas have a cleaner phase diagram due to the reduction in symmetry class}
 		\subsection{Phase diagram}

### 2019-02-04 thesis_report/theory.tex
Majorana's -> Majoranas

@@
 I simple terms, this consists of a slab of superconductor and a strip of semiconductor.
-By interfacing the two, one creates a region where all the necessary ingredients are present to realize Majorana's.
+By interfacing the two, one creates a region where all the necessary ingredients are present to realize Majoranas.
 
@@
 	\subsection{Superconducting Hamiltonian}
-		For the purpose of creating Majorana's, we are interested in two main aspects of superconductivity: the energy gap surrounding the Fermi energy (due to the depletion of states), and the electron-hole (/particle-hole) symmetry.
+		For the purpose of creating Majoranas, we are interested in two main aspects of superconductivity: the energy gap surrounding the Fermi energy (due to the depletion of states), and the electron-hole (/particle-hole) symmetry.
 		We are thus not interested in the paired up electrons (Cooper pairs), and only wish to model the electronic (unpaired) modes.
@@
 	\subsection{Proximity effect}
-		In order to create Majorana's, one needs a material with properties unique to both superconductors and semiconductors.
+		In order to create Majoranas, one needs a material with properties unique to both superconductors and semiconductors.
 		However, if a superconductor is interfaced with a normal conductor, some of the properties belonging to the superconductor transfer to normal material.
@@
 
-	Topology is relevant to the context of the system under study, because the emergence of seperated Majorana's is guaranteed within a continuous range of parameters.
-	The presence of Majorana's is therefore topologically protected, as they will be unpurturbed by variations of parameters, within a certain range.
-	For an infinite system, the system is said to be in the topological phase if Majorana's emerge once the system is cut to finite length.
+	Topology is relevant to the context of the system under study, because the emergence of seperated Majoranas is guaranteed within a continuous range of parameters.
+	The presence of Majoranas is therefore topologically protected, as they will be unpurturbed by variations of parameters, within a certain range.
+	For an infinite system, the system is said to be in the topological phase if Majoranas emerge once the system is cut to finite length.
 	The system is considered to be in its trivial phase if the converse is true.
@@
 		The Majorana state carries no spin, charge, or energy, giving almost no degrees of freedom for it to interact with the environment.
-		The Majorana state constitutes a single fermion, but is comprised of two Majorana's.
-		In a finite, topological system, these two Majorana's are physically seperated, appearing at the edges.
+		The Majorana state constitutes a single fermion, but is comprised of two Majoranas.
+		In a finite, topological system, these two Majoranas are physically seperated, appearing at the edges.
 
@@
 		Luckily, the state's presence itself is measurable: the availability of a state contributes to the conduction at that energy.
-		When measuring the conduction through a system with Majorana's present, one should thus encounter a rise in the conductance at zero energy: the zero bias peak.
+		When measuring the conduction through a system with Majoranas present, one should thus encounter a rise in the conductance at zero energy: the zero bias peak.
 
@@
 		The decay or coherence length of a Majorana pair is an important measure signifying the seperation of the two half-particles.
-		A decay length larger or of equal size to the system dimensions will lead to overlap of the Majorana's, diminishing the desired robustness of the state.
-		An overlap of the Majorana's will in fact lead to the system having a non-zero energy, its magnitude depending on the amount of overlap.
+		A decay length larger or of equal size to the system dimensions will lead to overlap of the Majoranas, diminishing the desired robustness of the state.
+		An overlap of the Majoranas will in fact lead to the system having a non-zero energy, its magnitude depending on the amount of overlap.
 		A crude estimation of the size of an individual Majorana is:
@@
 
-		When the system is cut to a finite length, any overlap of the two Majorana's will lead to a non-zero energy.
+		When the system is cut to a finite length, any overlap of the two Majoranas will lead to a non-zero energy.
 		This decreases the robustness of the topological state and it is thus desirable that the Majorana decay length is significantly smaller than the system size.
@@
 
-	The earliest devices used to create a seperated pair of Majorana's were nanowires deposited onto a slab of superconducting material.
-	A relatively new proposal is that of creating Majorana's in a planar Josephson junction~\cite{pientka_topological_2017}.
+	The earliest devices used to create a seperated pair of Majoranas were nanowires deposited onto a slab of superconducting material.
+	A relatively new proposal is that of creating Majoranas in a planar Josephson junction~\cite{pientka_topological_2017}.
 	An advantage of this system is that the phase difference between the superconductors can be used as a knob to switch the system from the topological state to the trivial state. 

### 2019-02-04 thesis_report/introduction.tex
Majorana particles -> Majorana bound states

@@
 	\comment{What are Majorana bound states}
-	Majorana particles are particles that always come in pairs: one pair of Majoranas forms a single electronic state.
+	Majorana bound states are quasi-particles that always come in pairs: one pair of Majoranas forms a single electronic state.
 	Disambiguating electrons and holes into their Majorana counterparts is analogous to splitting a complex number into its real and imaginary part.

### 2019-02-04 thesis_report/theory.tex
Majorana particles -> Majorana bound states

@@
 \chapter{Theoretical Background}
-The topological quantum computer uses pairs of Majorana particles as its unit of computation (qubit).
+A topological quantum computer uses pairs of Majorana bound states as its unit of computation (qubit).
 In order to host Majorana modes in a system, one needs a material which has properties from a superconducting material, as well as from a semi-conducting material.
@@
 We then focus on what happens in a system where the two are interfaced.
-Following that, we briefly explain what Majorana are, before introducing the implementation mainly relevant to this thesis.
+Following that, we briefly explain what Majoranas are, before introducing the implementation mainly relevant to this thesis.
 

### 2019-02-04 thesis_report/results.tex
spell check

@@
 \chapter{Results \& Discussion}\label{chap:results}
-		In this chapter, we show how some properties of the system change by introduction of the zigzag geometry.
+		In this chapter, we show how some properties of the system change by the introduction of a zigzag geometry.
 		Additionally, we attempt to isolate the mechanism behind the improved properties by estimating the gap size through the quasiclassical model introduced in chapter \ref{chap:methods}.
@@
 			\comment{We calculate the bandstructure for varying amount of zigzag.}
-			We implement a tight-binding version of the model described in the section \ref{sec:physical_picture}(a two dimensional SNS junction with a Rashba BdG Hamiltonian) using Kwant.
+			We implement a tight-binding version of the model described in section \ref{sec:physical_picture}(a two dimensional SNS junction with a Rashba BdG Hamiltonian) using Kwant.
 			In figure~\ref{fig:bandstuctures}, the bandstructure for zigzag systems~\ref{fig:zigzag_methods} (sawtooth shape) with varying amplitude is displayed.
-			Because the zigzag has to be modeled using a super cell, we see a folded bandstructure.
-			For comparisons sake, we take the same cell size for the ribbon structure so the bandstructure is folded in the same way.
+			Because the zigzag has to be modeled using a supercell, we see a folded bandstructure.
+			For comparison's sake, we take the same cell size for the ribbon structure so the bandstructure is folded in the same way.
 
-			\comment{The bandstructures show that modulation of the geometry increases the gap by an order of magnitude, as well as reduce the group velocity.}
+			\comment{The band structures show that modulation of the geometry increases the gap by an order of magnitude, as well as reduce the group velocity.}
 			The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size is increased more than an order of magnitude.
-			This happens because the modes where the gap is the smallest, when the momentum is almost completely focused along the strip ($k_x=k_F$), are cut off in a zigzag geometry.
+			This happens because the modes where the gap is the smallest when the momentum is almost completely focused along the strip ($k_x=k_F$), are cut off in a zigzag geometry.
 			There is also a significant reduction of the group velocity where in Fig.~\ref{fig:bandstuctures} (c) the bands are almost completely flat.
@@
 			\caption{Wavefunctions for different sizes and geometries.
-			With (a) a straight system, (b) a zigzag system, (c) a system where the normal region is defined by lines parallel to a sinosoid, and (d) a system with vertically offset sinosoids.
-			Inside the figure we indicate the Majorana length (or coherence length) $\xi$ and the topological energy gap $E_\textrm{gap}$.
+			With (a) a straight system, (b) a zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) a system with vertically offset sinusoids.
+			Inside the figure, we indicate the Majorana length (or coherence length) $\xi$ and the topological energy gap $E_\textrm{gap}$.
 			We observe that $\xi$ for (a) is orders of magnitude longer and $E_\textrm{gap} = E_\textrm{1} - E_M$ orders of magnitude smaller than for (b, c, d), meaning that the details of the geometry do not matter.
@@
 			The delocalized nature of the wavefunctions is clearly visible through the density plots.
-			Quantitatively, the improvement in localization of the Majoranas is also distinctly apparent: the energies of the Majorana states are orders of magnitude lower than the energy of the second lowest lying wavefunctions.
+			Quantitatively, the improvement in the localization of the Majoranas is also distinctly apparent: the energies of the Majorana states are orders of magnitude lower than the energy of the second lowest-lying wavefunctions.
 			As mentioned in the previous section, this can be attributed due to the way the gap and velocity factor into the Majorana coherence length.
@@
 			The shape of the wavefunctions does not seem to change much depending on the details of the shape.
-			The sharp corners of the sawtooth versus the smooth shape of the snakelike system do not seem to have great impact upon the shape of the wavefunction.
+			The sharp corners of the sawtooth versus the smooth shape of the snakelike system do not seem to have a great impact on the shape of the wavefunction.
 
@@
 phase difference it is diamond shaped: Fig.~\ref{fig:pientka_phase_diagram}), we can infer the topology of the system with zigzag modulation.
-			In Figure ~\ref{fig:phasediagrams}, the energy gap as a function of magnetic field, chemical potential, and superconducting phase difference is displayed, for both a straight system (a and b), and a zigzag system (c and d).
+			In Figure ~\ref{fig:phasediagrams}, the energy gap as a function of magnetic field, chemical potential, and the superconducting phase difference is displayed, for both a straight system (a and b) and a zigzag system (c and d).
 
@@
 			Similar to what is described by Pientka et.
-al~\cite{pientka2017topological} (see Fig.~\ref{fig:pientka_phase_diagram}), we see that the straight geometry, as a function of superconducting phase difference and Zeeman field (b), has a diamond shaped phase diagram.
-			The additional gap closings visible within the diamond are due to the system belonging to the BDI symmetry class, and cause the region of interest, where there is a single pair of Majoranas, to be relatively small.
+al~\cite{pientka2017topological} (see Fig.~\ref{fig:pientka_phase_diagram}), we see that the straight geometry, as a function of superconducting phase difference and Zeeman field (b), has a diamond-shaped phase diagram.
+			The additional gap closings visible within the diamond are due to the system belonging to the BDI symmetry class and cause the region of interest, where there is a single pair of Majoranas, to be relatively small.
 
 			For the zigzag system, the magnitude of the gap is significantly improved, as expected.
-			The diamond like shape of the phase-Zeeman plot is retained, and there is no significant change in its size either.
+			The diamond-like shape of the phase-Zeeman plot is retained, and there is no significant change in its size either.
 			We expect a cleaner phase diagram due to the system belonging to the D symmetry class, which is partially reflected in the diagram: there is a large and stable (no gap closings) central region, but near 0 and 2$\pi$ phase difference, in the corner of the diamond, we see a chaotic collection of gap closings.
@@
 	\section{Finding the mechanism responsible for the increased gap}
-		\comment{We compare different techniques to calculate the bandstructure of a straight system.}
+		\comment{We compare different techniques to calculate the band structure of a straight system.}
 		We verify the validity of the analytic model described in the Methods, to compute the bandstructure of a straight system in a tilted magnetic field. 
-		In Fig.\ref{fig:spectrum_calculation_comparison}, we compare the analytical model with bandstructures obtained using three different methods, implemented in Kwant.
-		To show that the model has been correctly implemented, we compute the Kwant scattering matrix of the identical model used in the analytics, and substitute it into the bound state condition\eqref{eq:bound_state_condition_sjl} (labeled Kwant without SOI SJL).
-		To show the validity of neglecting spin orbit in the transverse direction, we also compute the scattering matrix including the additional term, and again use the bound state condition to obtain the spectrum (labeled Kwant with SOI SJL).
-		We also perform the fully accurate calculation of the spectrum by simply computing the bandstructure of the corresponding Kwant system (labeled Full ribbon kwant system): this result serves as the benchmark for the other techniques.
+		In Fig.\ref{fig:spectrum_calculation_comparison}, we compare the analytical model with band structures obtained using three different methods, implemented in Kwant.
+		To show that the model has been correctly implemented, we compute the Kwant scattering matrix of the identical model used in the analytics and substitute it into the bound state condition\eqref{eq:bound_state_condition_sjl} (labeled Kwant without SOI SJL).
+		To show the validity of neglecting spin-orbit in the transverse direction, we also compute the scattering matrix including the additional term and again use the bound state condition to obtain the spectrum (labeled Kwant with SOI SJL).
+		We also perform the fully accurate calculation of the spectrum by simply computing the bandstructure of the corresponding Kwant system (labeled Full ribbon Kwant system): this result serves as the benchmark for the other techniques.
 
@@
 			All three of the scattering matrix approaches agree almost perfectly with each other.
-			We must note that ignoring spin orbit coupling in the transverse direction is only valid if the spin orbit length is sufficiently small compared to the width of the system.
+			We must note that ignoring spin-orbit coupling in the transverse direction is only valid if the spin-orbit length is sufficiently small compared to the width of the system.
 			What is also clear from the plot is that the domain of the scattering matrix methods is limited.
@@
 			As explained in the Methods chapter, we estimate the topological gap using a quasiclassical estimate.
-			We keep the ratio $4\dfrac{z_x}{z_y}$ constant, and compute the gap as a function of $z_y$.
+			We keep the ratio $4\dfrac{z_x}{z_y}$ constant and compute the gap as a function of $z_y$.
 			In Figure \ref{fig:quasiclassical_approximation}, the result is shown, comparing numerical gap calculations of the full zigzag system (full lines), with the result of the quasiclassical estimation.
-			Note that the quasiclassics are only valid once the zigzag cuts off all trajectories which extend infinitely.
+			Note that the quasi-classics are only valid once the zigzag cuts off all trajectories which extend infinitely.
 			Also important to note is that for the quasiclassical estimate, we set the longest trajectory to be the trajectory that does not include the corners, as depicted in Fig.~\ref{fig:longest_trajectory_wo_corners}
@@
 			We would expect that the maximum gap improvement would occur near where the zigzag amplitude $z_y$ is large enough to cut off any angle in the system.
-			This point is different for the three ratios, but can be identified by where the gap is largest for the quasiclassical estimate (dashed lines).
+			This point is different for the three ratios but can be identified by where the gap is largest for the quasiclassical estimate (dashed lines).
 			Increasing $z_y$ further would only allow longer trajectories, which would seem extra undesirable due to the magnetic field not being aligned with the diagonal sections.
@@
 
-			The quasiclassical estimate, indicated by the dashed lines, seems to consistently under estimate the gap.
+			The quasiclassical estimate, indicated by the dashed lines, seems to consistently underestimate the gap.
 			We also see that the gap declines monotonically with respect to the zigzag amplitude, which is by design: increasing the zigzag amplitude corresponds to increasing the domain of permitted trajectories, and thus the minimum can only decrease.

### 2019-02-04 thesis_report/results.tex
style changes

@@
 			\comment{We calculate the bandstructure for varying amount of zigzag.}
-			We implement a tight-binding version of the model described in section \ref{sec:physical_picture}(a two dimensional SNS junction with a Rashba BdG Hamiltonian) using Kwant.
+			We implement a tight-binding version of the model described in section \ref{sec:physical_picture}.
 			In figure~\ref{fig:bandstuctures}, the bandstructure for zigzag systems~\ref{fig:zigzag_methods} (sawtooth shape) with varying amplitude is displayed.
@@
 phase difference it is diamond shaped: Fig.~\ref{fig:pientka_phase_diagram}), we can infer the topology of the system with zigzag modulation.
-			In Figure ~\ref{fig:phasediagrams}, the energy gap as a function of magnetic field, chemical potential, and the superconducting phase difference is displayed, for both a straight system (a and b) and a zigzag system (c and d).
+			In Figure ~\ref{fig:phasediagrams}, the energy gap as a function of magnetic field, chemical potential, and the superconducting phase difference is displayed, for both a straight system [(a) and (b)] and a zigzag system [(c) and (d)].
 
@@
 			\includegraphics[width=0.75\columnwidth]{figures/phasediagrams}
-			\caption{Phase diagrams of a straight system (a, b) and zigzag system (c, d), where (a, c) are $E(\mu, B)$ and (b, d) are $E(\phi, B)$.
+			\caption{Phase diagrams of a straight system (a), (b) and zigzag system (c), (d), where (a), (c) are $E(\mu, B)$ and (b), (d) are $E(\phi, B)$.
 			We use a generalized eigenvalue problem to find all phase boundaries at once and find the minimal energy gap by finding the minimum in the spectrum: $\min{E(k)}$.

### 2019-02-04 thesis_report/results.tex
review results.tex

@@
 			We implement a tight-binding version of the model described in section \ref{sec:physical_picture}.
-			In figure~\ref{fig:bandstuctures}, the bandstructure for zigzag systems~\ref{fig:zigzag_methods} (sawtooth shape) with varying amplitude is displayed.
+			In figure~\ref{fig:bandstuctures}, the bandstructure for saw toothed zigzag systems [Fig.~\ref{fig:zigzag_methods}] with varying amplitude is displayed.
 			Because the zigzag has to be modeled using a supercell, we see a folded bandstructure.
@@
 			Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve, and vertically offset sinusoids.
-			In figure~\ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.
-			Also displayed in the figure are the energies $E_M$, corresponding to the plotted Majorana wavefunctions, as well as $E_1$: the energies corresponding to the next lowest state.
+			In figure~\ref{fig:wavefunctions} the wavefunctions superimposed upon their respective geometry are displayed including the corresponding Majorana energies $E_M$, as well as $E_1$: the energies corresponding to the next lowest state.
 
@@
 			\comment{In a straight system, the Majoranas are very poorly localized.}
-			For the ribbon system, we see that the decay of the density is slow: the wavefunction clearly extends to the middle of the system, not showing the delocalization sought after.
-			Apart from the density, as mentioned in the Theory chapter, overlap of Majoranas leads to a non-zero energy of the state.
-			Taking this into consideration, we see that the energy of the Majorana state in the straight system is only barely below the next lowest lying eigenstate: the Majoranas are very poorly localized, and topological protection against perturbations is minimal.
+			For the ribbon system [Fig.~\ref{fig:wavefunction}(a)], we see that the decay of the density is long compared to the system size.
+			We see that the wavefunction extends to the center of the system, not showing the delocalization sought after.
+			Apart from the density, as discussed in chapter \ref{chap:theory}, overlap of Majoranas leads to a non-zero energy of the state.
+			Taking this into consideration, we see that the energy of the Majorana state in the straight system is only barely below the next lowest lying eigenstate: the Majoranas are very poorly localized and topological protection against perturbations is minimal.
 
@@
 			The delocalized nature of the wavefunctions is clearly visible through the density plots.
-			Quantitatively, the improvement in the localization of the Majoranas is also distinctly apparent: the energies of the Majorana states are orders of magnitude lower than the energy of the second lowest-lying wavefunctions.
-			As mentioned in the previous section, this can be attributed due to the way the gap and velocity factor into the Majorana coherence length.
+			Quantitatively, the improvement in the localization of the Majoranas is also distinctly apparent: the energies of the Majorana states are three orders of magnitude lower than the energy of the second lowest-lying wavefunctions.
+			As mentioned in the previous section, this can be attributed to the way the gap and velocity factor into the Majorana coherence length.
 
 			\comment{We also confirm that the specific shape does not matter.}
-			The shape of the wavefunctions does not seem to change much depending on the details of the shape.
-			The sharp corners of the sawtooth versus the smooth shape of the snakelike system do not seem to have a great impact on the shape of the wavefunction.
+			The shape of the wavefunctions does not change significantly depending on the details of the shape.
+			The sharp corners of the sawtooth versus the smooth shape of the snakelike system do not have a great impact on the shape of the wavefunction.
 
@@
 			\comment{We calculate the topological phase diagram using the gap size.}
-			Due to the size of the system, we cannot use full spectrum methods (the Pfaffian in this case) to compute the topological phase of our system.
+			Due to the size of the system, we cannot use full spectrum methods (the Pfaffian in this case) to compute the topological invariant of our system.
 			Instead, we calculate the gap by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{|E(k)|}$.
-			Noting the gap closings, and the fact we know the topological phase for the non-zigzag system (e.g.
+			Noting the gap closings, and that we know the topological phase for the non-zigzag system (e.g.
 for magnetic field vs.
 phase difference it is diamond shaped: Fig.~\ref{fig:pientka_phase_diagram}), we can infer the topology of the system with zigzag modulation.
-			In Figure ~\ref{fig:phasediagrams}, the energy gap as a function of magnetic field, chemical potential, and the superconducting phase difference is displayed, for both a straight system [(a) and (b)] and a zigzag system [(c) and (d)].
+			In figure ~\ref{fig:phasediagrams}, we plot the energy gap as a function of magnetic field, chemical potential, and the superconducting phase difference for both a straight system [(a) and (b)] and a zigzag system [(c) and (d)].
 

### 2019-02-04 thesis_report/introduction.tex
updated introduction

@@
 \comment{The history of quantum computing and why QC is important}
-	The idea of using coherent quantum states as a means to perform complex calculations first appeared in the beginning of the 80's.
+	The idea of using coherent quantum states as a means to perform complex calculations first appeared at the beginning of the `80s.
 	A handful of papers had already been published on the matter, when, during a keynote speech~\cite{feynman_simulating_1982} at the California Institute of Technology, Nobel laureate Richard Feynman suggested its importance with respect to physics simulations.
@@
 
-\comment{It is still an open question what the implementation for a qubit will be, but Majoranas are one of the contenders}
+\comment{It is still an open question what the implementation for a qubit will be, but Majorana's are one of the contenders}
 	If we consider the evolution of the regular computer, we see that the technological/physical platform for the bit, the binary unit of information, has been constantly changing.
@@
 	The main problem with most of the quantum computing platforms is that it is very difficult to keep the qubit from decohering.
-	To counteract this, apart from trying to reduce the decoherance rate of the qubit, much effort is put into devising quantum error correction codes: devise strategies such that potential errors can be detected and corrected for.
+	To counteract this, apart from trying to reduce the decoherence rate of the qubit, much effort is put into devising quantum error correction codes: devise strategies such that potential errors can be detected and corrected for.
 	For topological quantum computers, employing Majorana bound states as qubits, information is encoded in such a way that it is inherently protected against decoherence.
@@
 	A system in which this separation can be accomplished was first proposed by Kitaev~\cite{kitaev_unpaired_2001}.
-	We consider a one dimensional chain of sites which can host a single fermion, and thus a pair of Majoranas.
+	We consider a one-dimensional chain of sites which can host a single fermion, and thus a pair of Majoranas.
 	Suppose that the occupation of a site by a fermion comes at the cost of energy $\mu$.
-	Also, we consider the situation where there is an interaction energy between neighboring sites: $t$ quantifies the energy cost of one site being occupied while the adjacent is not, and $\Delta$ is the gain in energy if adjacent sites are both occupied or empty.
+	Also, we consider the situation where there is interaction energy between neighboring sites: $t$ quantifies the energy cost of one site being occupied while the adjacent is not, and $\Delta$ is the gain in energy if adjacent sites are both occupied or empty.
 	This leads to the following Hamiltonian:
@@
 	In this way, we get a Hamiltonian describing pairing energies between Majoranas on adjacent sites.
-	We discern two extremes: In figure \ref{fig:trivial_majoranas}, the situation where the pairing energy is minimal for Majorana pairs on the same site:
+	We discern two extremes.
+	In figure \ref{fig:trivial_majoranas}, the situation is displayed where the pairing energy is minimal for Majorana pairs on the same site:
 	\begin{figure}[htb!]
@@
 
-	The other is when the energy is minimal for pairing between of Majoranas from adjacent sites:
+	In figure \ref{fig:topological_majoranas}, the other extreme is displayed, when the energy is minimal for pairing between of Majoranas from adjacent sites:
 	\begin{figure}[htb!]
@@
 
-	As is apparent from the above image, this would leave two unpaired Majoranas at the ends of the chain.
+	As it is apparent from figure \ref{fig:topological_majoranas}, this would leave two unpaired Majoranas at the ends of the chain.
 	This is the state we are interested in: the Majorana state, where two Majoranas are separated in space.
@@
 
-\section{Ways to make Majoranas: nanowires \& sns system}
+\section{Ways to make Majorana's: Nanowires and SNS system}
+
 	A realistic experimental implementation of Kitaev's model did not emerge until the similar works of Lutchyn et.
@@
 al~\cite{ oreg_helical_2010}, where they proposed an experiment composed of a semiconducting nanowire deposited onto a superconductor.
-	They predicted that, if the semiconductor has strong spin-orbit coupling, a magnetic field applied along the wire axis, as well as a carefully tuned chemical potential, Majoranas would appear at the ends of the nanowire.
-	The experiment proved to be sufficiently practical to perform in the lab and the first signatures of Majorana bound states were found using the setup by Mourik et. al~\cite{mourik_signatures_2012}.
+	They predicted that, if the semiconductor has a strong spin-orbit coupling, a magnetic field applied along the wire axis, as well as a carefully tuned chemical potential, Majoranas would appear at the ends of the nanowire.
+	The experiment proved to be sufficiently practical to be performed in the lab and the first signatures of Majorana bound states were found using the setup by Mourik et.
+al~\cite{mourik_signatures_2012}.
 
-	For the same reasons Majoranas are inherently protected against decoherence, it is notoriously difficult to prove their existence.
+	The inherent protection against decoherence, in part due to the absence of properties such as spin or charge, also makes it notoriously difficult to detect and prove their existence.
 	Perhaps the most direct way to detect their presence is through the observation of a so-called zero bias peak.
@@
 	On each side of the strip a superconductor is placed, forming a Josephson junction.
-	Using the Josephson junction, one can use the supercurrent which flows between the two superconductors to control whether the system is in a topological phase (meaning it contains Majoranas), or not.
-	The system has addition advantages, namely the system allows for Majoranas to be created at lower magnetic fields, the system is more compatible with convential semiconductor technology, and the Josephson junction allows for new ways to detect the topological phase of the system.
-
-	% \comment{Current experimental progress}
-	% Two papers that claimed they have observed signs of topological behavior.
-	% Soft gap, questionable results.
+	Taking advantage of the current-phase relationship existing in such a device, control of the current can be used to change the system from the trivial phase (no Majoranas), to the topological phase (does contain Majoranas).
+	The system has additional advantages: it allows for Majorana's to be created at lower magnetic fields, it is more compatible with convential semiconductor technology, and the Josephson junction provides new ways to detect the topological phase of the system.
 
 	\comment{The challenges encountered}
-	One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap; where the gap in the density of states is greatly reduced for states with the momentum directed along the length of the strip.
+	One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap, where the gap in the density of states is greatly reduced for states with the momentum directed along the length of the strip.
 	From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
@@
 
-	We propose that the introduction of a zigzag-shaped modulation of the junction region leads to an increased topological gap, as well as a reduction of the Majorana coherence length.
+	In this thesis we show that the introduction of a zigzag-shaped modulation of the junction region leads to an increased topological gap, as well as the reduction of the Majorana coherence length.
 	Furthermore, we hypothesize that the gap improvement is the result of the elimination of long trajectories

### 2019-02-04 thesis_report/introduction.tex
intro updated

@@
 	On each side of the strip a superconductor is placed, forming a Josephson junction.
-	Taking advantage of the current-phase relationship existing in such a device, control of the current can be used to change the system from the trivial phase (no Majoranas), to the topological phase (does contain Majoranas).
+	Taking advantage of the current-phase relationship existing in such a device, control of the current can be used to change the system from the trivial phase (no Majoranas) to the topological phase (does contain Majoranas).
 	The system has additional advantages: it allows for Majorana's to be created at lower magnetic fields, it is more compatible with convential semiconductor technology, and the Josephson junction provides new ways to detect the topological phase of the system.

### 2019-02-04 thesis_report/results.tex
use a active voice instead of passive

@@
 			We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
-			The value of the remaining parameters are, $\alpha=20$ \si{\milli \eV \nm}, $g=26$, $\meff=0.02$\si{\electronmass}, $\mu=20$ \si{\milli \eV}, $\Delta=1$ \si{\milli \eV}.
+			The value of the remaining parameters are $\alpha=20$ \si{\milli \eV \nm}, $g=26$, $\meff=0.02$\si{\electronmass}, $\mu=20$ \si{\milli \eV}, $\Delta=1$ \si{\milli \eV}.
 			\label{fig:bandstuctures}}
@@
 			We implement a tight-binding version of the model described in section \ref{sec:physical_picture}.
-			In figure~\ref{fig:bandstuctures}, the bandstructure for saw toothed zigzag systems [Fig.~\ref{fig:zigzag_methods}] with varying amplitude is displayed.
-			Because the zigzag has to be modeled using a supercell, we see a folded bandstructure.
-			For comparison's sake, we take the same cell size for the ribbon structure so the bandstructure is folded in the same way.
+			In figure~\ref{fig:bandstuctures}, the bandstructure for saw-toothed zigzag systems [Fig.~\ref{fig:zigzag_methods}] with varying amplitude is displayed.
+			Because the zigzag has to be modelled using a supercell, we see a folded bandstructure.
+			For comparison's sake, we take the same cell size for the ribbon structure, so the bandstructure folds in the same way.
 
 			\comment{The band structures show that modulation of the geometry increases the gap by an order of magnitude, as well as reduce the group velocity.}
-			The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size is increased more than an order of magnitude.
-			This happens because the modes where the gap is the smallest when the momentum is almost completely focused along the strip ($k_x=k_F$), are cut off in a zigzag geometry.
-			There is also a significant reduction of the group velocity where in Fig.~\ref{fig:bandstuctures} (c) the bands are almost completely flat.
-			The size of the gap, together with the velocity, directly relate to the Majorana coherence length (Eq.~\eqref{eq:majorana_coherence_length}), which will be discussed in the following section.
+			The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size increases more than an order of magnitude.
+			This increase happens because the modes where the gap is the smallest when the momentum almost entirely focuses along the strip ($k_x=k_F$), are cut off in a zigzag geometry.
+			There is also a significant reduction of the group velocity where in Fig.~\ref{fig:bandstuctures} (c) the bands are nearly completely flat.
+			The size of the gap, together with the velocity, directly relate to the Majorana coherence length (Eq.~\eqref{eq:majorana_coherence_length}), which we discuss in the following section.
 
@@
 			In a zigzag system, the normally reflected part of a wavefunction will eventually intersect a surface with which it is nearly perpendicular to.
-			The transparency of the NS interface is thus improved for non-transversal modes.
+			The transparency of the NS interface thus improves for non-transversal modes.
 
@@
 			Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve, and vertically offset sinusoids.
-			In figure~\ref{fig:wavefunctions} the wavefunctions superimposed upon their respective geometry are displayed including the corresponding Majorana energies $E_M$, as well as $E_1$: the energies corresponding to the next lowest state.
+			In figure~\ref{fig:wavefunctions} displays the wavefunctions superimposed upon their respective geometry including the corresponding Majorana energies $E_M$, as well as $E_1$: the energies corresponding to the next lowest state.
 
@@
 			With (a) a straight system, (b) a zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) a system with vertically offset sinusoids.
-			Inside the figure, we indicate the Majorana length (or coherence length) $\xi$ and the topological energy gap $E_\textrm{gap}$.
-			We observe that $\xi$ for (a) is orders of magnitude longer and $E_\textrm{gap} = E_\textrm{1} - E_M$ orders of magnitude smaller than for (b, c, d), meaning that the details of the geometry do not matter.
+			Inside the figure, we indicate the Majorana length (or coherence length) $\lambda_\textrm{M}$ and the topological energy gap $E_\textrm{gap}$.
+			We observe that $\xi$ for (a) is orders of magnitude longer and $E_\textrm{gap} = E_\textrm{1} - E_M$ orders of magnitude smaller than for (b), (c), and (d), meaning that the details of the geometry do not matter for the improvements to occur.
 			\label{fig:wavefunctions}}
@@
 			For the ribbon system [Fig.~\ref{fig:wavefunction}(a)], we see that the decay of the density is long compared to the system size.
-			We see that the wavefunction extends to the center of the system, not showing the delocalization sought after.
-			Apart from the density, as discussed in chapter \ref{chap:theory}, overlap of Majoranas leads to a non-zero energy of the state.
+			We see that the wavefunction extends to the centre of the system, not showing the delocalization sought after.
+			Apart from the density, as discussed in chapter \ref{chap:theory}, an overlap of Majoranas leads to a non-zero energy of the state.
 			Taking this into consideration, we see that the energy of the Majorana state in the straight system is only barely below the next lowest lying eigenstate: the Majoranas are very poorly localized and topological protection against perturbations is minimal.
@@
 			\comment{We calculate the topological phase diagram using the gap size.}
-			Due to the size of the system, we cannot use full spectrum methods (the Pfaffian in this case) to compute the topological invariant of our system.
+			Due to the size of the system, we cannot use full spectrum methods (the Pfaffian) to compute the topological invariant of our system.
 			Instead, we calculate the gap by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{|E(k)|}$.
@@
 al~\cite{pientka2017topological} (see Fig.~\ref{fig:pientka_phase_diagram}), we see that the straight geometry, as a function of superconducting phase difference and Zeeman field (b), has a diamond-shaped phase diagram.
-			The additional gap closings visible within the diamond are due to the system belonging to the BDI symmetry class and cause the region of interest, where there is a single pair of Majoranas, to be relatively small.
+			The additional gap closings visible within the diamond are because of the presence of a chiral symmetry which classifies the system as BDI and causes the region of interest, where there is a single pair of Majoranas, to be relatively small.
 
@@
 			The diamond-like shape of the phase-Zeeman plot is retained, and there is no significant change in its size either.
-			We expect a cleaner phase diagram due to the system belonging to the D symmetry class, which is partially reflected in the diagram: there is a large and stable (no gap closings) central region, but near 0 and 2$\pi$ phase difference, in the corner of the diamond, we see a chaotic collection of gap closings.
+			We expect a cleaner phase diagram due to the system belonging to the D symmetry class, which is partially reflected in the diagram: there is a large and stable (no gap closings) central region, but near 0 and 2$\pi$ phase difference, in the corner of the diamond, we see a chaotic region of gap closings.
 			We are unsure of the nature of these gap closings, but they can perhaps be attributed to the symmetry breaking being relatively weak.
@@
 		\comment{We compare different techniques to calculate the band structure of a straight system.}
-		We verify the validity of the analytic model described in the Methods, to compute the bandstructure of a straight system in a tilted magnetic field.
-		In Fig.\ref{fig:spectrum_calculation_comparison}, we compare the analytical model with band structures obtained using three different methods, implemented in Kwant.
-		To show that the model has been correctly implemented, we compute the Kwant scattering matrix of the identical model used in the analytics and substitute it into the bound state condition\eqref{eq:bound_state_condition_sjl} (labeled Kwant without SOI SJL).
-		To show the validity of neglecting spin-orbit in the transverse direction, we also compute the scattering matrix including the additional term and again use the bound state condition to obtain the spectrum (labeled Kwant with SOI SJL).
-		We also perform the fully accurate calculation of the spectrum by simply computing the bandstructure of the corresponding Kwant system (labeled Full ribbon Kwant system): this result serves as the benchmark for the other techniques.
+		We verify the validity of the analytic model described in chapter \ref{chap:methods} and compute the bandstructure of a straight system in a tilted magnetic field.
+		In figure \ref{fig:spectrum_calculation_comparison}, we compare the analytical model with band structures obtained using three different methods, implemented in Kwant.
+		To show that the model has been correctly implemented, we compute the Kwant scattering matrix of the identical model used in the analytics and substitute it into the bound state condition\eqref{eq:bound_state_condition_sjl} (labelled Kwant without SOI SJL).
+		To show the validity of neglecting spin-orbit in the transverse direction, we also compute the scattering matrix including the additional term and again use the bound state condition to obtain the spectrum (labelled Kwant with SOI SJL).
+		We also perform the fully accurate calculation of the spectrum by simply computing the bandstructure of the corresponding Kwant system (labelled Full ribbon Kwant system): this result serves as the benchmark for the other techniques.
 

### 2019-02-04 thesis_report/results.tex
more changes to results.tex

@@
 			\caption{Wavefunctions for different sizes and geometries.
-			With (a) a straight system, (b) a zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) a system with vertically offset sinusoids.
+			With (a) a straight system, (b) a zigzag system, (c) a system where lines parallel to a sinusoid defines the normal region, and (d) a system with vertically offset sinusoids.
 			Inside the figure, we indicate the Majorana length (or coherence length) $\lambda_\textrm{M}$ and the topological energy gap $E_\textrm{gap}$.
@@
 			The shape of the wavefunctions does not change significantly depending on the details of the shape.
-			The sharp corners of the sawtooth versus the smooth shape of the snakelike system do not have a great impact on the shape of the wavefunction.
+			The sharp corners of the sawtooth versus the smooth shape of the snakelike system do not have a significant impact on the shape of the wavefunction.
 
@@
 		To show the validity of neglecting spin-orbit in the transverse direction, we also compute the scattering matrix including the additional term and again use the bound state condition to obtain the spectrum (labelled Kwant with SOI SJL).
-		We also perform the fully accurate calculation of the spectrum by simply computing the bandstructure of the corresponding Kwant system (labelled Full ribbon Kwant system): this result serves as the benchmark for the other techniques.
+		We also perform the full calculation of the spectrum by computing the bandstructure of the corresponding Kwant system (labelled Full ribbon Kwant system): this result serves as the benchmark for the other techniques.
 
@@
 			Considering the lines corresponding to the full zigzag systems, we see that, for the lower ratios (and thus steeper slopes), the optimal value lies far beyond the cutoff point.
-			This is unexpected, and it weakens the validity of the idea that the gap is mostly determined by the length of the trajectories.
+			This is unexpected, and it weakens the validity of the idea that the length of the trajectories mostly determines the gap.
 			A possible explanation is that for lower ratios, the length of the diagonal sections is smaller, and it is easier for the wavefunction to tunnel through the superconductor.
@@
 
-			The quasiclassical estimate, indicated by the dashed lines, seems to consistently underestimate the gap.
+			The quasiclassical estimate, indicated by the dashed lines, seems to underestimate the gap consistently.
 			We also see that the gap declines monotonically with respect to the zigzag amplitude, which is by design: increasing the zigzag amplitude corresponds to increasing the domain of permitted trajectories, and thus the minimum can only decrease.
 			Even so, we see that the decline of the gap with respect to $z_y$ is much quicker than with an actual zigzag.
-			A possible reason that the quasiclassical model sketches a darker picture than full zigzag, is due to the fact that in that model, long trajectories also correspond to grazing angles of incidence at the NS interface.
+			A possible reason that the quasiclassical model sketches a darker picture than full zigzag, is because in that model, long trajectories also correspond to grazing angles of incidence at the NS interface.
 

### 2019-02-04 thesis_report/results.tex
done with results.tex

@@
 		\subsection{Estimation of the gap through momentum cutoff}
-			As explained in the Methods chapter, we estimate the topological gap using a quasiclassical estimate.
+			As explained in chapter \ref{chap:methods}, we estimate the topological gap using a quasiclassical estimate.
 			We keep the ratio $4\dfrac{z_x}{z_y}$ constant and compute the gap as a function of $z_y$.
-			In Figure \ref{fig:quasiclassical_approximation}, the result is shown, comparing numerical gap calculations of the full zigzag system (full lines), with the result of the quasiclassical estimation.
+			In figure \ref{fig:quasiclassical_approximation}, the result is shown, comparing numerical gap calculations of the full zigzag system (full lines), with the result of the quasiclassical estimation.
 			Note that the quasi-classics are only valid once the zigzag cuts off all trajectories which extend infinitely.
@@
 
-			We conclude that the proposed model to estimate the gap does not capture the physics of the zigzag very well: the model merely gives a lower bound for the topological gap.
+			We conclude that the proposed model to estimate the gap does not capture all the physics of the zigzag very well: the model merely gives a lower bound for the topological gap.

### 2019-02-04 thesis_report/conclusion.tex
Majorana's -> Majoranas
updated methods, spell check conclusions

@@
 Furthermore, numerical simulation points out that the optimal geometry does not always coincide with the minimal trajectory length.
-It is therefore unsure whether the improvement of the gap can be fully attributed to the elimination of long trajectories, or, if the arising phenomena are due to other mechanisms.
+It is therefore unsure whether the improvement of the gap can be fully attributed to the elimination of long trajectories, or if the arising phenomena are due to other mechanisms.
 In any case, the improvements are stable under a wide range of parameters, and the topological gap varies gradually as a function of geometry, indicating the effect is not merely coincidental.
@@
 \comment{Extensions: we omit several physical effects, disorder, electrostatics, etc.}
-In the model used, we omit several physical effects, such as, disorder, electrostatics, the orbital effect, etc.
+In the model used, we omit several physical effects, such as disorder, electrostatics, the orbital effect, etc.
 Apart from experimental verification, further study is required to see whether the conclusions of this model are valid.
@@
 Current fabrication techniques seem compatible with the proposed geometry, and experimental verification should point out whether it holds up to its promise.
-We note that slight modifications to the geometry, for example to ease measurement, should not have large implications on the physics.
+We note that slight modifications to the geometry, for example, to ease measurement, should not have large implications on the physics.
 Currently, experimental groups have already fabricated zigzag devices (e.g. the image on the cover of this thesis), and measurements are underway.
@@
 \comment{It would be interesting to study what geometry creates an optimal environment for Majorana modes to exist.}
-We have studied sawtooth, snake like and offset sinosoid modulation of the semiconductor region, but perhaps a more exotic shape will be optimal.
-A study optimizing the geometry for supporting Majorana's would be an interesting continuation.
+We have studied sawtooth, snake-like and offset sinusoidal modulation of the semiconductor region, but perhaps a more exotic shape will be optimal.
+A study optimizing the geometry for supporting Majoranas would be an interesting continuation.

### 2019-02-04 thesis_report/methods.tex
Changed QC image
Added Bass corrections
updated methods, spell check conclusions

@@
 % -*- root: ./report.tex -*-
-\chapter{Methods}
+\chapter{Methods}\label{chap:methods}
 
-\section{Physical picture}
+\section{Physical picture}\label{sec:physical_picture}
 	\comment{We consider a two-dimensional system with zigzag.}
@@
 	We modulate the shape of the normal region, which can be either zigzag as depicted, or a more smooth sinusoidal like shape.
-	Similar to the conventional straight system \cite{pientka2017topological}, a magnetic field $B_x$ perpendicular to the junction is applied.
-	We model the system with a BdG Hamiltonian, Eqs.~\eqref{eq:hamiltonian_n}-~\eqref{eq:hamiltonian_s}  ; the normal part has a linear Rashba spin-orbit coupling term characterized by $\alpha$ and a Zeeman field with $E_z=\frac{1}{2}mu_B g B_x$.
-	The superconductor has a superconducting coupling term $\Delta$ with a superconducting phase $\exp{\pm i \phi/2}$.
+	Similar to the conventional straight system \cite{pientka_topological_2017}, a magnetic field $B_x$ is applied, along the x-axis.
+	We model the system with a BdG Hamiltonian, Eqs.~\eqref{eq:hamiltonian_n}-~\eqref{eq:hamiltonian_s}  ; the normal part has a linear Rashba spin-orbit coupling term characterized by the spin-orbit strength $\alpha$ , and a Zeeman energy $E_z= mu_B g B_x$.
+	The superconductor has a superconducting coupling term $\Delta$ with a superconducting phase $\pm\phi/2$ (the phase difference between the superconductors is $\phi$).
 	Both parts have a kinetic term and chemical potential $\mu$ (counted from the bottom spin-orbit band). 
-	For the zigzag geometry, we first consider a sawtooth like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
+	For the zigzag geometry, we first consider a sawtooth like pattern where $z_y$ is the amplitude, $z_x$ is the period, and $W$ the width of the junction.
 
@@
 	\includegraphics[width=0.5\columnwidth]{images/zigzag.pdf}
-	\caption{Setups. Figure of a straight and zigzag system, including trajectories.
+	\caption{Figure of a zigzag system.
+	$z_x$, $z_y$ and $W$ describe the geometry of the zigzag junction.
+	$H_\text{K}$ describes the kinetic part of the Hamiltonian, $H_\text{SOI}$ is the spin-orbit term, $H_\text{Z}$ is the Zeeman coupling, and $H_\Delta$ represents the superconducting term.
+	The magnetic field (B) points along the x-axis.
 	\label{fig:setup}}
@@
 	\comment{The symmetry class of the system is D.}
-	The non-zigzag system is in the symmetry class BDI \cite{pientka2017topological}, unless the additional symmetries are broken due to for example a difference in superconducting gap magnitude between the two superconductors.
-	Using the software package Qsymm\cite{varjas2018qsymm}, we find that the symmetry class of our system to be $\mathcal{D}$, because we break this chiral/time-reversal symmetry resulting from the mirror symmetric junction.
+	The non-zigzag system is in the symmetry class BDI \cite{pientka_topological_2017}, unless the additional symmetries are broken due to for example a difference in superconducting gap magnitude between the two superconductors.
+	Using the software package Qsymm\cite{varjas_qsymm_2018}, we find that the symmetry class of our system to be D, because we break this chiral/time-reversal symmetry resulting from the mirror symmetric junction.
 
@@
 	Each site has two orbitals: spin and electron-hole.
-	There are four different types of sites (and thus four different Hamiltonians): the top superconductor, the bottom superconductor, the normal region, and a normal region with a variable potential offset, forming a barrier to simulate an imperfect NS interface.
+	There are four different types of sites (and thus four different Hamiltonians): the top superconductor, the bottom superconductor, the normal region, and a normal region with an optional potential offset, acting as a barrier to simulate an imperfect NS interface.
 	A schematic of such kwant systems is depicted in Fig.~\ref{fig:kwant_system}.
@@
 	\comment{The model hamiltonian is converted into the tight binding form by substitution}
-	In order to turn the set of Hamiltonians, Eqs.\eqref{eq:hamiltonian_n} and \eqref{eq:hamiltonian_s} into a tight binding model, we write the equations into differential form by substituting $k_\alpha \rightarrow - i \partial_\alpha$, $\alpha \in \left\{ x, y \right\}$, and thereafter discretize on a rectangular grid.
+	In order to turn the set of Hamiltonians, Eqs.\eqref{eq:hamiltonian_n} and \eqref{eq:hamiltonian_s} into a tight binding model, we write the equations into differential form by substituting $k_\alpha \rightarrow - i \partial_\sigma$, $\sigma \in \left\{ x, y \right\}$, and thereafter discretize on a rectangular grid.
 	In practice, this is implemented using the Kwant discretizer module.
@@
 	\comment{To compute the effect of cutoff consider a single segment of the zigzag and obtain the spectrum analytically (this allows to use translation invariance).}
-	In order to establish that the elimination of long trajectories is the driving mechanism behind the order of magnitude gap improvement, we use an analytical approach.
-	We estimate the gap of the zigzag system by the minimum energy occuring in the Andreev spectrum of a single (diagonal) segment of zigzag.
-	The spectrum of the zigzag segment we define as the spectrum of an infinite ribbon SNS junction with tilted-magnetic field. 
+	To establish that the elimination of long trajectories is indeed the driving mechanism behind the improvement of the gap, we use an analytical model in an effort to isolate the gap-trajectory dependence.
+	We estimate the gap of the zigzag system by the minimum energy occuring in the Andreev spectrum of a single (diagonal) segment of zigzag (see Fig.~\ref{fig:zigzag_methods}).
+	We define the spectrum of a single zigzag segment by identifying it with the spectrum of an infinite ribbon SNS junction with tilted-magnetic field.
 	The finite length of the segment is modeled by not including momenta corresponding to long trajectories when taking the minimum over the spectrum.
@@
 	\comment{The spectrum is derived using a scattering matrix, and we consider multiple ways to eliminate long trajectory momenta.}
-
-	Estimating the gap is a two-step process: derivation of the Andreev spectrum, and taking the minimum energy over a particular set of allowed momenta.
-	The first is derived using scattering matrix formalism and the Andreev bound state condition\cite{beenakker1991universal, sticlet_robustness_2017}.
-	The second step is mostly trivial, but the difficulty lies with identifying the set of allowed  momenta to take the minimum over.
+	Estimating the gap is a two-step process: first, derivation of the Andreev spectrum, and second, taking the absolute minimum of that spectrum over the set of momenta allowed by the specific geometry.
+	An analytic expression for the spectrum is derived using scattering matrix formalism and the Andreev bound state condition\cite{beenakker1991universal, sticlet_robustness_2017}.
+	For the second step, the difficulty lies with identifying the set of allowed momenta in a particular geometry.
 

### 2019-02-04 thesis_report/theory.tex
review results.tex
updated methods, spell check conclusions

@@
 
-\chapter{Theoretical Background}
+\chapter{Theoretical Background}\label{chap:theory}
 A topological quantum computer uses pairs of Majorana bound states as its unit of computation (qubit).
@@
 	    \end{equation}
-
+	    Where $\alpha$ is known as the spin-orbit coupling strength.
+	    Using this coupling strenght $\alpha$, we can also define the spin-orbit length~\cite{van_weperen_spin-orbit_2015}:
+	    \begin{equation}
+	    	l_\text{so} = \frac{\hbar^2}{2\meff \alpha}
+	    	\label{eq:l_so}
+	    \end{equation}
+	    In a two-dimensional system, if $l_\text{so}$ is smaller than the length of the system, then spin-orbit interaction will not have a large impact upon the physics.
 \section{Superconducting region}

### 2019-02-04 paper/snakemajoranas.tex
Majorana's -> Majoranas
go through the paper

@@
 \comment{Majoranas are mostly made in hybrid NS structures.}
-The current experimental effort is focused on creating pairs of MBSs in hybrid normal-superconductor (NS) structures, where a lengthy strip (or wire) of semiconductor is interfaced with a \cite{lutchyn_majorana_2010,oreg_helical_2010} superconductor.
-Within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple wire), the semiconductor becomes topological and MBSs appear at the ends of the segment.
+The current experimental effort is focuses on creating pairs of MBSs in hybrid normal-superconductor (NS) structures, where a long strip (or wire) of a semiconductor is interfaced with a \cite{lutchyn_majorana_2010,oreg_helical_2010} superconductor.
+Within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple wire), the semiconductor becomes topological while MBSs appear at the ends of the segment.
 Recently, a system with a slight modification has been proposed\cite{pientka2017topological}, where instead of having one superconductor, there are two superconductors, creating a superconductors-normal-superconductor (SNS) junction.
@@
 \comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
-Currently, proposed workarounds are low density or disorder~\cite{haim_double-edge_2018}, but both have drawbacks.
+Currently, proposed workarounds are to work at low density \cite{nijholt2015orbital} or to have disorder~\cite{haim_double-edge_2018}, but both have drawbacks.
 
 \comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
-In this paper we show that introducing a zigzag or snake like geometry for the semiconductor eliminates these long trajectories and prevents the appearance of a soft gap while also increasing the topological gap by an order of magnitude.
+In this paper, we show that introducing a zigzag or snake-like geometry for the semiconductor eliminates these long trajectories and prevents the appearance of a soft gap while also increasing the topological gap by an order of magnitude.
 
@@
 \comment{We consider a two-dimensional system with zigzag.}
-We consider a Josephson junction (JJ)(Fig.~\ref{fig:setup}) consisting of a two dimensional strip of semiconductor, with superconductors on both sides.
-We modulate the shape of the normal region, which can be either zigzag as depicted, or a more smooth sinusoidal like shape.
+We consider a Josephson junction (JJ)(Fig.~\ref{fig:setup}) consisting of a two-dimensional strip of semiconductor, with superconductors on both sides.
+We modulate the shape of the normal region, which can be either zigzag as depicted, or a more smooth sinusoidal-like shape.
 Similar to the conventional straight system \cite{pientka2017topological}, a magnetic field $B_x$ perpendicular to the junction is applied.
@@
 Both parts have a kinetic term and chemical potential $\mu$. 
-For the zigzag geometry, we first consider a sawtooth like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
-Later in this manuscript we show that the exact details of the shape are not important and consider different zigzag geometries also parametrized by $z_x, \; z_y, \; W$.
+For the zigzag geometry, we first consider a sawtooth-like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
+Later in this manuscript, we show that the exact details of the shape are not important and consider different zigzag geometries also parametrized by $z_x, \; z_y, \; W$.
 
@@
 We discretize our continuum Hamiltonian \eqref{eq:hamiltonian} and implement a tight-binding model using Kwant~\cite{groth_kwant:_2014}.
-The resulting Hamiltonians are large because instead of having a single slice of sites that is translationally invariant in the $x$-direction, we create a long supercell in order to make the structure periodic.
-To speed up these expensive simualtions we employ an adaptive sampling strategy, using the Python package Adaptive. % TODO: add citation
+The resulting Hamiltonians are large because instead of having a single slice of sites that is translationally invariant in the $x$-direction, we create a long supercell to make the structure periodic.
+To speed up these expensive simulations we employ an adaptive sampling strategy, using the Python package Adaptive. % TODO: add a citation
 
@@
 In figure~\ref{fig:bandstuctures}, the bandstructure for zigzag systems with varying amplitude is displayed.
-Because the discretized zigzag system is modeled using a super cell, we can only plot a folded bandstructure.
-For comparisons sake, we take the same cell size for the ribbon structure such that the bandstructure is folded in the same way.
+Because the discretized zigzag system is modeled using a supercell, we can only plot a folded bandstructure.
+For comparison's sake, we take the same cell size for the ribbon structure such that the bandstructure folds in the same way.
 
-\comment{The bandstructures show that modulation of the geometry increases the gap by an order of magnitude, as well as reduce the group velocity.}
-The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size is increased by more than an order of magnitude.
-This happens because in a straight system, long trajectories are possible, these have a momentum that is directed along the strip and consequently, $k_x \approx k_F$.
-The smallest gap in a straight system occurs around $k_F$ and because the zigzag cuts off long trajectories, the gap size is increased. 
-Besides this, the velocity of the modes is greatly reduced, which has a positive effect on the Majorana coherence length, as described later in section XXX. % TODO: add ref
+\comment{The band structures show that modulation of the geometry increases the gap by an order of magnitude, as well as reduce the group velocity.}
+The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size increases by more than an order of magnitude.
+This happens because in a straight system long trajectories are possible, these have a momentum that is directed along the strip and consequently, $k_x \approx k_F$.
+The smallest gap in a straight system occurs around $k_F$, and because the zigzag cuts off long trajectories, the gap size increases. 
+Besides this, the velocity of the modes greatly reduces, which has a positive effect on the Majorana coherence length, as described later in section XXX. % TODO: add ref
 
@@
 \comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry. }
-Similar to what is described by Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond like structure as a function of phase $\phi$ and Zeeman field $E_Z$.
+Similar to what is described by Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond-like structure as a function of phase $\phi$ and Zeeman field $E_Z$.
 We also observe additional gap closings which are due to the BDI symmetry that is present.
-As expected for the zigzag system, the magnitude of the gap is significantly improved, whilst maintaining the diamond like shape.
-As the zigzag shape destroys the additional symmetry, moving it to class D, we see a more clean topological region.
+As expected for the zigzag system, the magnitude of the gap is significantly improved, while maintaining the diamond-like shape.
+As the zigzag shape destroys the additional symmetry, moving it to class D, we see a cleaner topological region.
 
@@
 We derive the Andreev spectrum for a single (diagonal) segment of the zigzag, and define the gap of the system as the minimum of the spectrum occurring before the cutoff corresponding to the particular geometry.
-The system under consideration is thus a ribbon SNS junction with tilted magnetic field.
+The system under consideration is thus a ribbon SNS junction with a tilted magnetic field.
 
@@
 We derive the spectrum by calculating the scattering matrix for the normal region and applying the Andreev bound state condition for the short junction limit\cite{beenakker1991universal, sticlet_robustness_2017}.
-For deriviation of the scattering matrix, we neglect SOI in the transverse direction, which is valid for $W<l_\text{so}$.
+For derivation of the scattering matrix, we neglect SOI in the transverse direction, which is valid for $W<l_\text{so}$.
 The result is specified in Eqs.~\eqref{eq:smatrix} to~\eqref{eq:momenta_short_junction}.
@@
 In figure~\ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.
-For the ribbon system, we see that the Majorana coherence length is relatively large, not showing the decolalized nature sought after.
-All of the zigzag type geometries however show greatly reduced coherence length.
-This can be explained by two effects: the increase in topological gap, but also the before mentioned reduction of the group velocity.
+For the ribbon system, we see that the Majorana coherence length is relatively large, not showing the delocalized nature sought after.
+All of the zigzag type geometries, however, show significantly reduced coherence length.
+Two effects can explain this: the increase in the topological gap, but also the before mentioned reduction of the group velocity.
 
 \comment{We also confirm that the specific shape does not matter.}
-Also note the similarity between the various shapes, sharp corners or more smoothlike, the effect is the same.
+Also note the similarity between the various shapes, sharp corners or a smoother system, the effect is the same.
 
@@
 \caption{Wavefunctions for different sizes and geometries.
-With (a) a straight system, (b) a zigzag system, (c) a system where the normal region is defined by lines parallel to a sinosoid, and (d) a system with vertically offset sinosoids.
-Inside the figure we indicate the Majorana length (or coherence length) $\xi$ and the topological energy gap $E_\textrm{gap}.$
+With (a) a straight system, (b) a zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) a system with vertically offset sinusoids.
+Inside the figure, we indicate the Majorana length (or coherence length) $\xi$ and the topological energy gap $E_\textrm{gap}.$
 We observe that $\xi$ for (a) is orders of magnitude longer and $E_\textrm{gap}$ orders of magnitude smaller than for (b, c, d), meaning that the details of the geometry do not matter.
@@
 
-\comment{The zigzag geometry is a useful tool in hardening the gap and decreasing majorana length, now experimental verification necessary}
+\comment{The zigzag geometry is a useful tool in hardening the gap and decreasing Majorana length, now experimental verification necessary}
 The introduction of a zigzag geometry increases the topological gap by over an order of magnitude, as well as offering a substantial reduction of the Majorana length.
@@
 Current fabrication techniques seem compatible with the proposed geometry; zigzag devices have already been created.
-Slight modifications to the geometry, for example to ease measurement, should not have large implications on the physics.
+Slight modifications to the geometry, for example to ease measurement, should not have significant implications on the physics.
 
 \comment{It would be interesting to study what geometry creates an optimal environment for Majorana modes to exist.}
-We have studied sawtooth, snake like and offset sinosoid modulation of the semicondctor region, but perhaps a more exotic shape will be optimal.
-A study optimizing the geometry for supporting Majorana's would be an interesting continuation.
+We have studied sawtooth, snake-like and offset sinusoidal modulation of the semiconductor region, but perhaps a more exotic shape will be optimal.
+A study optimizing the geometry for supporting Majoranas would be an interesting continuation.
 
 \comment{Extensions: we omit several physical effects, disorder, electrostatics, etc.}
-We omit several physical effects, such as: disorder, electrostatics, the orbital effect, etc..
+We exclude several physical effects, such as disorder, electrostatics, the orbital effect, etc..
 Further study, as well as experimental verification, are required to see whether the conclusions of this model are valid for the real case.

### 2019-02-04 thesis_report/methods.tex
go through the paper
Modified methods

@@
 	\comment{We propose a method to verify that elimination of long trajectories is responsible for the increased topological gap in a zigzag system.}
+
 \section{Quasiclassical estimation of the topological gap}
@@
 
-		We derive the spectrum by calculating the scattering matrix for the normal region and applying the Andreev bound state condition for the short junction limit\cite{beenakker1991universal, sticlet_robustness_2017}.
+		We derive the spectrum by calculating the scattering matrix for the normal region and applying the Andreev bound state condition for the short junction limit\cite{beenakker_universal_1991,sticlet_robustness_2017}..
 		The short junction limit is valid for $W<\xi$, where $\xi$ is the superconducting coherence length.
@@
 			The `S' region corresponds to the superconductor Hamiltonian without the superconducting term, Eq.~\eqref{eq:ham_smat_superconducting}, `N' to the normal region, Eq.~\eqref{eq:ham_smat_normal}. 
-			The coefficients represent the amplitude of the modes present in the system, at a particular energy.
+			The coefficients (corresponding to the scattering problem outlined in Eqs.~\ref{eq:scattering_matrix_problem} and \ref{eq:scattering_equations}) represent the amplitude of the modes present in the system, at a particular energy.
 			The different color arrows correspond to the two different spinors in each region.
@@
 			We consider the scattering region as depicted in Fig. \ref{fig:scattering}.
-			There are three regions in the system, one normal system (N), with Hamiltonian given by Eq.~\eqref{eq:ham_smat_superconducting}, and two superconducting regions (S), with Hamiltonian given by Eq.~\eqref{eq:ham_smat_superconducting}.
-			Not that Eq.~\eqref{eq:ham_smat_superconducting} region does not include the superconducting term ($\Delta \tau_y$), because we implement Andreev reflection seperately: this way we avoid doubling (electron and hole) the dimensionality of the problem.
+			There are three regions in the system, one normal system (N), with Hamiltonian given by Eq.~\eqref{eq:ham_smat_normal}, and two superconducting regions (S), with Hamiltonian given by Eq.~\eqref{eq:ham_smat_superconducting}.
+			Note that Eq.~\eqref{eq:ham_smat_superconducting} region does not include the superconducting term ($\Delta \tau_y$), because we implement Andreev reflection seperately (see Eq.~\eqref{eq:andreev_scat_mat})~\cite{beenakker_universal_1991}: this way we avoid doubling (electron and hole) the dimensionality of the problem.
+
 			We set the energy of the system, and find the planar waves propogating in each region.
@@
 			The idea of the scattering matrix is to set the vector $\vec{a}$, containing the amplitudes of the planar waves coming in to the scattering region, and find the amplitudes of the modes exiting the scattering region.
-			This is captured by a system of linear equations, displayed in Eq.~\eqref{eq:scattering_matrix_problem}
+			This is captured by a system of linear equations, displayed in Eq.~\eqref{eq:scattering_matrix_problem}.
 
@@
 
-			To solve the system analytically, we use the Short Junction limit: we set the energy to zero.
+			To solve the system analytically, we use the Short Junction limit: we set $E=0$ in Eq.~\eqref{eq:scattering_matrix_problem}.
 			By applying the boundary conditions and solving the resulting linear system of equations, the resulting solution is given by Eqs.~\eqref{eq:smatrix} through ~\eqref{eq:momenta_short_junction}.
@@
 			\end{equation}
+			Where the Andreev scattering is captured by the matrix in Eq.~\ref{eq:andreev_scat_mat}, where $\phi_1$ and $phi_2$ are the phases of the respective superconductors.
+
+			\begin{equation}
+				r = \left[\begin{array}{llll}
+		    		e^{i \phi_1}&0&0&0\\
+		    		0&e^{i \phi_1}&0&0\\
+		    		0&0&e^{i \phi_2}&0\\
+		    		0&0&0&e^{i \phi_2}
+		    		\end{array}\right]
+				\label{eq:andreev_scat_mat}
+			\end{equation}
 
@@
 			with
-			\begin{equation}
-			\lambda=-\frac{1}{\alpha^{2}\left(E\right)},\;A=r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right).
-			\end{equation}
+			\begin{align}
+			\lambda_i=-\frac{1}{\alpha^{2}\left(E\right)},&&A=r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right).
+			\end{align}
 
@@
 		We hypothesize that the increase of the topological gap in a zigzag is due to the cutoff of modes on the Fermi surface with long trajectories.
-		In order to make substantiate that this is indeed the driving mechanism behind the improvement, we propose an analogy using the bandstructure of a regular SNS junction.
+		In order to substantiate that this is indeed the driving mechanism behind the improvement, we propose an analogy using the bandstructure of a regular SNS junction.
 
 		\comment{We map the zigzag to an infinite SNS junction with tilted magnetic field and a range of forbidden momenta.}
-		We essentially take a single diagonal section of a zigzag, and map it to a normal, infinite SNS junction.
+		We take a single diagonal section of a zigzag, and map it to a normal, infinite SNS junction.
 		We assume that the zigzag is shaped such that there is no straight trajectory possible through the system anymore.
@@
 		We identify trajectories cut off by the zigzag with a particular range of forbidden momenta.
-		By then analysing the bandstructure of this infinite SNS junction, ignoring the forbidden momenta, we can give an estimate the resulting gap of the device.
+		By then analysing the bandstructure of this infinite SNS junction, we can give an estimate the resulting gap of the device.
 		As the system is only momentum localized in the $x$ direction (the translationally invariant direction), we only control $\kx$.
@@
 		\begin{equation}
-			\Delta_\text{topological} = \min_{\kx\in\Omega} \left\rvert E(\kx) \right\rvert
+			\Delta_\text{topological} = \min_{\kx\in\Omega} \left| E(\kx) \right|
 			\label{eq:definition_gap}
@@
 		By defining a minimum angle, we thus can filter out the long trajectories.
-		We define this angle $\beta\text{min}$ by identifying it with the angle of the longest trajectory from one side of the superconductor to the other: see Fig.~\ref{fig:zigzag_methods}.
+		We define this angle $\beta_\text{min}$ by identifying it with the angle of the longest trajectory from one side of the superconductor to the other: see Fig.~\ref{fig:zigzag_methods}.
 		Note that longer trajectories exist, by `grazing' the concave corners of the zigzag.
@@
         \begin{equation}
-        \tan (\beta) = \frac{v_y}{v_x}\bigr{\rvert_{E=E_F}} = \frac{ \frac{\de E}{\de k_y} }{ \frac{\de E}{\de k_x} } \Biggr\rvert_{E=E_F}=
-        \begin{cases}
+        \tan (\beta) = \left.\frac{v_y}{v_x}\right|_{E=E_F} = \left.\frac{ \frac{\de E}{\de k_y} }{ \frac{\de E}{\de k_x} } \right|_{E=E_F}=
+        \begin{dcases}
         \frac{\hbar ^2 k_1}{\frac{\alpha  \meff \left(\alpha  k_x-\text{Ez} \sin (\theta )\right)}{\sqrt{\text{Ez}^2+\alpha  k_x \left(\alpha  k_x-2 \text{Ez} \sin (\theta )\right)}}+\hbar ^2 k_x} & \text{band 1}\\
         \frac{\hbar ^2 k_2}{\frac{\alpha  \meff \left(\text{Ez} \sin (\theta )-\alpha  k_x\right)}{\sqrt{\text{Ez}^2+\alpha  k_x \left(\alpha  k_x-2 \text{Ez} \sin (\theta )\right)}}+\hbar ^2 k_x} & \text{band 2}
-        \end{cases}
+        \end{dcases}
         \label{eq:methods_angle_of_state}

### 2019-02-04 thesis_report/results.tex
Modified methods

@@
 		\subsection{Estimation of the gap through momentum cutoff}
-			As explained in chapter \ref{chap:methods}, we estimate the topological gap using a quasiclassical estimate.
+			As explained in chapter \ref{chap:methods}, we estimate the topological gap using a quasiclassical estimate (See Eqs.~\eqref{eq:definition_gap} and \eqref{eq:restriction_momentum}).
 			We keep the ratio $4\dfrac{z_x}{z_y}$ constant and compute the gap as a function of $z_y$.

### 2019-02-04 thesis_report/theory.tex
Grammarly vs. theory

@@
 As this material does not seem to exist on its own, one creates a heterogeneous system.
-I simple terms, this consists of a slab of superconductor and a strip of semiconductor.
+In simple terms, this consists of a slab of superconductor and a strip of semiconductor.
 By interfacing the two, one creates a region where all the necessary ingredients are present to realize Majoranas.
 
-In this chapter, we first give a description of the normal (semi-conductor) and superconducting regions.
+In this chapter, we first give a description of the normal (semiconductor) and superconducting regions.
 We then focus on what happens in a system where the two are interfaced.
@@
 \section{Normal region}
-	Two important ingredients required for realizing Majorana fermions are strong spin-orbit coupling, and a strong interaction with the applied magnetic field~\cite{lutchyn_majorana_2018}.
+    Two important ingredients required for realizing Majorana fermions are strong spin-orbit coupling and a strong interaction with the applied magnetic field~\cite{lutchyn_majorana_2018}.
     It is the semiconductor which brings these two physical effects to the mix.
@@
     \caption{Energy dispersion of electrons with different physical effects (spin orbit and magnetic field).
-	The dashed line in the figure with both spin orbit coupling and zeeman field corresponds to the case when magnetic field is not aligned with the spin orbit direction.}
+    The dashed line in the figure with both spin-orbit coupling and Zeeman field corresponds to the case when the magnetic field is not aligned with the spin-orbit direction.}
     \label{fig:ham_simple_terms}
@@
     \subsection{Zeeman interaction}
-    	The energy splitting of the two electron spin species due to magnetic field is called the Zeeman interaction.
+        The energy splitting of the two electron spin species due to the magnetic field is called the Zeeman interaction.
         It is modeled by:
@@
         An electron moving in an electric field will experience a small Zeeman field in its inertial frame as a relativistic effect~\cite{petersen_simple_2000}.
-	    The resulting interaction, coupling the momentum and spin of electron, is known as spin orbit coupling.
+        The resulting interaction, coupling the momentum and spin of an electron, is known as spin-orbit coupling.
         Spin-orbit coupling can be approximated by adding a Rashba spin orbit coupling term in the Hamiltonian:
@@
     \subsection{Superconductivity}
-		Superconductivity manifests itself as the complete lack of electrical resistance of a material.
-		It is the result of the pairing of electrons close to the Fermi-energy, condensing into so-called Cooper pairs.
+        Superconductivity manifests itself as the complete absence of electrical resistance of a material.
+        It results from the pairing of electrons close to the Fermi-energy, condensing into so-called Cooper pairs.
         The main parameter defining superconductivity is known as the superconducting order parameter, a complex number.
-		The phase of this parameter is a macroscopic potential relative to ones choice of gauge.
+        The phase of this parameter is a macroscopic potential relative to the choice of gauge.
         The magnitude of the superconducting order parameter, also referred to as the superconducting gap, quantifies the range around the Fermi-energy condensed into Cooper pairs.
@@
 \section{Normal-superconducting junctions}
-	As mentioned, the interesting physics occur when a normal conductor is interfaced with a superconductor.
-	A single interface between a normal conductor and a superconductor is known as a NS junction.
-	When one creates a sandwich, superconductor - normal - superconducting, we speak of a SNS junction.
-	Even not considering topological phases, which are only present if the normal regions meets certain conditions, both have interesting physics which will be discussed first.
+    As mentioned, interesting physics occur when a normal conductor is interfaced with a superconductor.
+    A single interface between a normal conductor and a superconductor is known as an NS junction.
+    When one creates a sandwich, superconductor - normal - superconducting, we speak of an SNS junction.
+    Even when topological phases are not considered -- which are only present if the normal regions meet certain conditions -- both have interesting physics which will be discussed first.
 
@@
         An electron in the normal region with energy below the superconducting gap, incident on the normal-superconductor (NS) interface, is retro-reflected as a hole.
-		This phenomenon is known as Andreev scattering, and occurs due to the coupling of electrons in a superconductor.
+        This phenomenon is known as Andreev scattering and occurs due to the coupling of electrons in a superconductor.
         Although a single electron initially enters the superconductor, it draws another electron (with opposite momentum) into the superconductor: forming a Cooper pair.
@@
     \subsection{Andreev bound states}
-		If the normal region is finite in the direction normal to the NS/SN interface, Andreev bound states form.
+        If the normal region is finite in the direction normal to the NS interface, Andreev bound states form.
         This is true for both SNS and SN junctions.
         Quasiclassically, one can imagine electrons (and holes) in the normal region, with energies below the gap, bouncing back and forth the system.
-		The corresponding eigenstates have energies below the gap, and are thus bound to the normal region.
+        The corresponding eigenstates have energies below the gap and are thus bound to the normal region.
 
@@
 
-		Although superconducting phase is relative to the choice of gauge, the difference of phase between two superconductors is in fact a physical quantity.
-		A difference in superconducting phase in a Josephson junction, results in a flow of current between the two superconductors: a supercurrent.
-		The relationship between superconducting phase and current is known as the current-phase relationship, and is in the most simple case a sinosoid.
+        Although the superconducting phase is relative to the choice of gauge, the difference of phase between two superconductors is, however, a physical quantity.
+        A difference in superconducting phase in a Josephson junction results in a flow of current between the two superconductors: a supercurrent.
+        The relationship between superconducting phase and current is known as the current-phase relationship, and is for the most simple case a sinusoid.
         This relationship can be exploited to control the phase difference: it is a matter of inducing a current.
@@
         In the context of this work, the Thouless energy is inversely proportional to the travel time of an electron in a system, without interacting with the superconductor(s).
-		As an example of its relevance, in a SNS junction with magnetic field, if the Zeeman field has an energy comparable to the Thouless energy, as the electron traverses the system from supercondcutor to superconductor, the spin will be flipped.
+        As an example of its relevance, in an SNS junction with a magnetic field, if the Zeeman field has an energy comparable to the Thouless energy, as the electron traverses the system from superconductor to superconductor, the spin will be flipped.
 
@@
 
-	Topology is relevant to the context of the system under study, because the emergence of seperated Majoranas is guaranteed within a continuous range of parameters.
-	The presence of Majoranas is therefore topologically protected, as they will be unpurturbed by variations of parameters, within a certain range.
+    Topology is relevant to the context of the system under study because the emergence of separated Majoranas is guaranteed within a continuous range of parameters.
+    The presence of Majoranas is therefore topologically protected, as they will be unperturbed by variations of parameters, within a certain range.
     For an infinite system, the system is said to be in the topological phase if Majoranas emerge once the system is cut to finite length.
@@
     The relevant topological invariant is dependent on the symmetry class the system belongs to.
-	In the case of the what is studied in this manuscript, the systems discussed belong to either symmetry class BDI or D.
+    In the case of what is studied in this manuscript, the systems discussed belong to either symmetry class BDI or D.
     Any system which is in the BDI class is also contained within class D.
@@
         The Majorana state carries no spin, charge, or energy, giving almost no degrees of freedom for it to interact with the environment.
-		The Majorana state constitutes a single fermion, but is comprised of two Majoranas.
-		In a finite, topological system, these two Majoranas are physically seperated, appearing at the edges.
+        The Majorana state constitutes a single fermion but is comprised of two Majoranas.
+        In a finite, topological system, these two Majoranas are physically separated, appearing at the edges.
 
-		The lack of interaction, as well as the physical seperation of the state, makes it very robust against perturbations, but also difficult to detect.
+        The lack of interaction, as well as the physical separation of the state, makes it very robust against perturbations, but also difficult to detect.
         Luckily, the state's presence itself is measurable: the availability of a state contributes to the conduction at that energy.
@@
         The topological gap is defined as the energy gap between the Majorana state -- conveniently located at zero energy -- and the first available state.
-		It's magnitude governs the protection of the system against perturbations causing the system to be lifted out of its ground state: the Majorana state.
+        Its magnitude governs the protection of the system against perturbations causing the system to be lifted out of its ground state: the Majorana state.
 
     \subsection{Decay/Coherence length}
-		The decay or coherence length of a Majorana pair is an important measure signifying the seperation of the two half-particles.
+        The decay or coherence length of a Majorana pair is an important measure signifying the separation of the two half-particles.
         A decay length larger or of equal size to the system dimensions will lead to overlap of the Majoranas, diminishing the desired robustness of the state.
-		An overlap of the Majoranas will in fact lead to the system having a non-zero energy, its magnitude depending on the amount of overlap.
+        An overlap of the Majoranas will lead to the system having non-zero energy, its magnitude depending on the amount of overlap.
         A crude estimation of the size of an individual Majorana is:
@@
 
-		When the system is cut to a finite length, any overlap of the two Majoranas will lead to a non-zero energy.
+        When the system is cut to a finite length, any overlap of the two Majoranas will lead to non-zero energy.
         This decreases the robustness of the topological state and it is thus desirable that the Majorana decay length is significantly smaller than the system size.
 
-\section{Two dimensional platform for Majoranas}
+\section{ Two-dimensional platform for Majoranas}
 
@@
 
-	The earliest devices used to create a seperated pair of Majoranas were nanowires deposited onto a slab of superconducting material.
+    The earliest devices used to create a separate pair of Majoranas were nanowires deposited onto a slab of superconducting material.
     A relatively new proposal is that of creating Majoranas in a planar Josephson junction~\cite{pientka_topological_2017}.
@@
         In Figure \ref{fig:pientka_bandstructure}, the bandstructure is displayed for the SNS system.
-		Note that the gap is lowest at the Rashba/Zeeman split fermi-surface, where the momentum in the x direction equals $k_{F,1}$ or $k_{F,2}$.
-		It is at these momenta that the wavefunctions are completely parallel to the translationally invariant direction, causing weak couipling with the superconductors.
+        Note that the gap is lowest at the Rashba/Zeeman split Fermi-surface, where the momentum in the x-direction equals $k_{F,1}$ or $k_{F,2}$.
+        It is at these momenta that the wavefunctions are completely parallel to the translationally invariant direction, causing weak coupling with the superconductors.
 

### 2019-02-05 thesis_report/conclusion.tex
changes and added comments to conclusion.tex

@@
 \chapter{Conclusion}
-In the studied model, the introduction of a zigzag geometry increases the topological gap by over an order of magnitude, as well as offering a substantial reduction of the Majorana length.
-Additionally, the breaking of BDI symmetry into D symmetry results in a cleaner topological phase.
+In the model we study, the introduction of a zigzag geometry increases the topological gap by several orders of magnitude while simultaneously reducing the Majorana length.
+Additionally, the breaking of a chiral symmetry brings the system from the BDI symmetry class into the D symmetry class, resulting in a cleaner topological phase.  % Bas: how is the symmetry broken?
 Together, these improvements directly affect the robustness of the Majorana state, potentially bringing us closer to reliably create topological devices.
@@
 \comment{With the current quasiclassical analogy, we are not able to explain the improvements of zigzag.}
-The current used quasiclassical analogy, applied in the most lenient form, is not able to explain the increased gap of a zigzag system.
+The current used quasiclassical analogy, applied in the most lenient form, is not able to fully explain the increased gap of a zigzag system.
 Furthermore, numerical simulation points out that the optimal geometry does not always coincide with the minimal trajectory length.
@@
 \comment{Extensions: we omit several physical effects, disorder, electrostatics, etc.}
-In the model used, we omit several physical effects, such as disorder, electrostatics, the orbital effect, etc.
-Apart from experimental verification, further study is required to see whether the conclusions of this model are valid.
+In the model used, we omit several physical effects, such as disorder, electrostatics, the orbital effect, etc.  % Bas: what is etc.? Leave it out or write out the other effects
+Apart from experimental verification, further study is required to see whether the conclusions of this model are valid.  % Bas: waar komt de onzekerheid vandaan? Waarom is er meer verificatie nodig?
 
@@
 \comment{It would be interesting to study what geometry creates an optimal environment for Majorana modes to exist.}
-We have studied sawtooth, snake-like and offset sinusoidal modulation of the semiconductor region, but perhaps a more exotic shape will be optimal.
+We have studied sawtooth, snake-like, and offset sinusoidal modulation of the semiconductor region, but perhaps a more exotic shape will be optimal.
+% Bas: note that research in shape optimization is in progress (Andre)
 A study optimizing the geometry for supporting Majoranas would be an interesting continuation.

### 2019-02-05 thesis_report/introduction.tex
Made adjustments

@@
 	We discern two extremes.
-	In figure \ref{fig:trivial_majoranas}, the situation is displayed where the pairing energy is minimal for Majorana pairs on the same site:
+	In Figure \ref{fig:trivial_majoranas}, the situation is displayed where the pairing energy is minimal for Majorana pairs on the same site:
 	\begin{figure}[htb!]
@@
 
-	In figure \ref{fig:topological_majoranas}, the other extreme is displayed, when the energy is minimal for pairing between of Majoranas from adjacent sites:
+	In Figure \ref{fig:topological_majoranas}, the other extreme is displayed, when the energy is minimal for pairing between of Majoranas from adjacent sites:
 	\begin{figure}[htb!]
@@
 
-	As it is apparent from figure \ref{fig:topological_majoranas}, this would leave two unpaired Majoranas at the ends of the chain.
+	As it is apparent from Figure \ref{fig:topological_majoranas}, this would leave two unpaired Majoranas at the ends of the chain.
 	This is the state we are interested in: the Majorana state, where two Majoranas are separated in space.

### 2019-02-05 thesis_report/theory.tex
Made adjustments

@@
 A topological quantum computer uses pairs of Majorana bound states as its unit of computation (qubit).
-In order to host Majorana modes in a system, one needs a material which has properties from a superconducting material, as well as from a semi-conducting material.
+In order to host Majorana modes in a system, one needs a material which exhibits both superconducting and semiconducting properties.
 As this material does not seem to exist on its own, one creates a heterogeneous system.
@@
 We then focus on what happens in a system where the two are interfaced.
-Following that, we briefly explain what Majoranas are, before introducing the implementation mainly relevant to this thesis.
+Following that, we briefly explain what Majoranas are, before introducing the implementation relevant to this thesis.
 
@@
     The Hamiltonian terms provided in this section are relevant to the electron states.
-    In figure \ref{fig:ham_simple_terms}, the effect of the various terms in the Hamiltonian on the dispersion relation is shown.
+    In Figure \ref{fig:ham_simple_terms}, the effect of the various terms in the Hamiltonian on the dispersion relation is shown.
 
@@
     \caption{Energy dispersion of electrons with different physical effects (spin orbit and magnetic field).
-    The dashed line in the figure with both spin-orbit coupling and Zeeman field corresponds to the case when the magnetic field is not aligned with the spin-orbit direction.}
+    The dashed line in the Figure with both spin-orbit coupling and Zeeman field corresponds to the case when the magnetic field is not aligned with the spin-orbit direction.}
     \label{fig:ham_simple_terms}
@@
     \subsection{Kinetic term}
-        We rewrite the kinetic term in the Schrodinger equation into it's momentum form by noting $- i \partial_x \rightarrow \kx$:
+        We rewrite the kinetic term in the Schrodinger equation into its momentum form by noting $- i \partial_x \rightarrow \kx$:
         \begin{equation}
@@
         \end{equation}
-        In a two-dimensional system, if $l_\text{so}$ is smaller than the length of the system, then spin-orbit interaction will not have a large impact upon the physics.
+        In a system of size $W$ with Rashba spin-orbit coupling, and $l_\text{so} < W$, the Rashba term in the Hamiltonian can be eliminated by a gauge transformation, to first order accuracy.
 \section{Superconducting region}
     The superconductor is responsible for ensuring particle-hole symmetry, as well as providing a `gapped' area in the bandstructure, isolating the zero-energy state.
-    Superconductivity is a very complicated phenomenon, so we again provide only the background required for the understanding of this work.
+    Superconductivity is a very complicated phenomenon, so we provide only the background required for understanding the contents of this thesis.
 
     \subsection{Superconductivity}
-        Superconductivity manifests itself as the complete absence of electrical resistance of a material.
+        Superconductivity manifests itself as the complete absence of electrical resistance in a material.
         It results from the pairing of electrons close to the Fermi-energy, condensing into so-called Cooper pairs.
@@
         The magnitude of the superconducting order parameter, also referred to as the superconducting gap, quantifies the range around the Fermi-energy condensed into Cooper pairs.
-        Because all electrons within a distance of the superconducting order parameter of the Fermi-energy are depleted in this way, charge transport only takes place via these quasiparticles.
+        Because all electrons within a distance of the superconducting order parameter to the Fermi-energy are depleted in this way, charge transport only takes place via these quasiparticles.
         Scattering of these Cooper pairs is not allowed, resulting in perfect conduction.
@@
     \subsection{Superconducting Hamiltonian}
-        For the purpose of creating Majoranas, we are interested in two main aspects of superconductivity: the energy gap surrounding the Fermi energy (due to the depletion of states), and the electron-hole (/particle-hole) symmetry.
+        For the purpose of creating Majoranas, we are interested in two main aspects of superconductivity: the energy gap surrounding the Fermi energy (due to the depletion of states), and the electron-hole (also known as particle-hole) symmetry.
         We are thus not interested in the paired up electrons (Cooper pairs), and only wish to model the electronic (unpaired) modes.
@@
 
-        Note that Eq.\eqref{eq:bdg} describes a block matrix: both $H$ and $\Delta$ can be matrices themselves, where the degrees of freedom correspond to for example spin, or discretized positions.
+        Note that Eq.\eqref{eq:bdg} describes a block matrix: both $H$ and $\Delta$ can be matrices themselves, where the degrees of freedom correspond to spin, for instance, or discretized positions.
         Using this basis, one is able to describe a heterogeneous system, containing both superconducting and normal regions.
@@
         In order to create Majoranas, one needs a material with properties unique to both superconductors and semiconductors.
-        However, if a superconductor is interfaced with a normal conductor, some of the properties belonging to the superconductor transfer to normal material.
+        However, if a superconductor is interfaced with a normal conductor, some of the properties belonging to the superconductor transfer to the normal material.
         This effective transfer of properties to the normal material is known as the proximity effect.
-        The characteristic distance governing the decay of the superconducting behavior is given by the superconducting coherence length, Eq.\eqref{eq:theory_sc_coherence_length}
+        The characteristic distance governing the decay of the superconducting behavior is given by the superconducting coherence length:
 
@@
     When one creates a sandwich, superconductor - normal - superconducting, we speak of an SNS junction.
-    Even when topological phases are not considered -- which are only present if the normal regions meet certain conditions -- both have interesting physics which will be discussed first.
+    Even when topological phases are not considered, which are only present if the normal regions meet certain conditions, both have interesting physics which will be discussed first.
 
@@
         This phenomenon is known as Andreev scattering and occurs due to the coupling of electrons in a superconductor.
-        Although a single electron initially enters the superconductor, it draws another electron (with opposite momentum) into the superconductor: forming a Cooper pair.
+        Although a single electron initially enters the superconductor, it draws another electron (with opposite momentum) into the superconductor, thus forming a Cooper pair.
         The drawn in electron leaves behind a hole in the normal conductor, which essentially backtracks the motion of the initial electron, hence the term retro-reflection.
@@
         An important device in the field of condensed matter physics is the Josephson junction.
-        A Josephson junction consists of a normal region sandwiched in between two superconductors (SNS junction).
+        A Josephson junction consists of a normal region sandwiched by two superconductors (SNS junction).
         The resulting Andreev bound states exhibit interesting physics, making the Josephson junction an important device.
 
-        Although the superconducting phase is relative to the choice of gauge, the difference of phase between two superconductors is, however, a physical quantity.
+        Although the superconducting phase is relative to the choice of gauge, the difference of phase between two superconductors is a physical quantity.
         A difference in superconducting phase in a Josephson junction results in a flow of current between the two superconductors: a supercurrent.
-        The relationship between superconducting phase and current is known as the current-phase relationship, and is for the most simple case a sinusoid.
+        The relationship between the superconducting phase and current is known as the current-phase relationship, and is in the simplest case a sinusoid.
         This relationship can be exploited to control the phase difference: it is a matter of inducing a current.
 
-        An important measure in a Josephson junction is the Thouless energy.
-        In the context of this work, the Thouless energy is inversely proportional to the travel time of an electron in a system, without interacting with the superconductor(s).
-        As an example of its relevance, in an SNS junction with a magnetic field, if the Zeeman field has an energy comparable to the Thouless energy, as the electron traverses the system from superconductor to superconductor, the spin will be flipped.
+        An important measure in a Josephson junction is the Thouless energy, given by Equation~\eqref{eq:theory_E_th}:
+        \begin{equation}
+            E_\text{Th} = \frac{\hbar v_F}{W}
+            \label{eq:theory_E_th}
+        \end{equation}
+        Where $v_F$ is the Fermi velocity, and $W$ is the width (distance between superconductors) of the system.
+
+        As an example of its relevance, consider a SNS junction with a magnetic field such that $E_Z \approx E_\text{Th}$.
+        An electron traversing the system from superconductor to superconductor will, under influence of the magnetic field, have its spin flipped.
 
@@
     In condensed matter physics, topology refers to the study of properties of a system, which are guaranteed by particular symmetries of the Hamiltonian.
-    These symmetries are present within a particular range of parameters, and any variation of those parameters within that range does not destroy these \emph{topologically protected} properties.
+    These symmetries are present for a particular range of parameters such that their variation does not destroy these \emph{topologically protected} properties.
 
@@
     The system is considered to be in its trivial phase if the converse is true.
-    The allocation of a system into one of its phases (in this case two) is quantitatively captured by its topological invariant.
+    The allocation of a system into one of its phases is quantitatively captured by its topological invariant.
     The relevant topological invariant is dependent on the symmetry class the system belongs to.
-    In the case of what is studied in this manuscript, the systems discussed belong to either symmetry class BDI or D.
-    Any system which is in the BDI class is also contained within class D.
+    In the case considered in this thesis, the systems discussed belong in either the symmetry class BDI or D.
+    Any system which is in the BDI class is also contained within the D class.
     The topological invariant of a class D system is binary: $-1$, corresponding to the topological phase, and $1$, corresponding to the trivial phase.
@@
         The Majorana state constitutes a single fermion but is comprised of two Majoranas.
-        In a finite, topological system, these two Majoranas are physically separated, appearing at the edges.
+        In a finite sized topological system, these two Majoranas are physically separated, appearing at the edges.
 
         The lack of interaction, as well as the physical separation of the state, makes it very robust against perturbations, but also difficult to detect.
-        Luckily, the state's presence itself is measurable: the availability of a state contributes to the conduction at that energy.
-        When measuring the conduction through a system with Majoranas present, one should thus encounter a rise in the conductance at zero energy: the zero bias peak.
+        Fortunately, the state's presence itself is measurable: the availability of a state contributes to the conduction at that energy.
+        When measuring the conduction through a system in which Majoranas are present, one should thus encounter a rise in the conductance at zero energy: the zero bias peak.
 
     \subsection{Topological gap}
-        The topological gap is defined as the energy gap between the Majorana state -- conveniently located at zero energy -- and the first available state.
+        The topological gap is defined as the energy gap between the Majorana state, conveniently located at zero energy, and the first available state.
         Its magnitude governs the protection of the system against perturbations causing the system to be lifted out of its ground state: the Majorana state.
@@
     \subsection{Decay/Coherence length}
-        The decay or coherence length of a Majorana pair is an important measure signifying the separation of the two half-particles.
-        A decay length larger or of equal size to the system dimensions will lead to overlap of the Majoranas, diminishing the desired robustness of the state.
-        An overlap of the Majoranas will lead to the system having non-zero energy, its magnitude depending on the amount of overlap.
+        The decay or coherence length of a Majorana pair is an important measure describing the separation of the two half-particles.
+        A decay length larger equal in size to the system dimensions will lead to overlap of the Majoranas, diminishing the desired robustness of the state.
+        An overlap of the Majoranas will result in the system having non-zero energy, its magnitude depending on the amount of overlap.
         A crude estimation of the size of an individual Majorana is:
@@
     \includegraphics[width=0.5\columnwidth]{figures/pientka_system}
-    \caption{System overview. Source\cite{pientka_topological_2017}}
+    \caption{System overview of the paper by Pientka et. al.~\cite{pientka_topological_2017}
+    A magnetic field is directed along the length of the strip, and the separation between the two superconductors is $W$.
+    A superconducting phase difference lifts the mirror-symmetry otherwise present in the system, allowing for the system to enter the topological phase.
+    In a finite system of size $L$, Majoranas (represented by $\gamma$) appear at the ends of the strip.
+    Note that in this system, the two superconducting slabs (blue) are deposited onto the semiconductor, proximitizing the 2DEG below.
+    By doing so, the underlying areas become the effective superconductors, and the entire system is defined within the semiconductor crystal, ensuring virtually perfect NS interfaces.}
     \label{fig:pientka_system}
@@
         As mentioned, the superconducting phase difference plays a critical role in the physics of the device.
-        The topological phase diagram, as a function of magnetic field and superconducting phase, is depicted in Fig. \ref{fig:pientka_phase_diagram}.
+        The topological phase diagram depicted in Figure~\ref{fig:pientka_phase_diagram}, displays the topological phase of the system as a function of magnetic field and superconducting phase.
         Without normal reflection (perfect Andreev reflection), the diagram has a diamond-like shape.
-        The system is always topological when the superconducting phase is $pi$, or when the magnetic field is tuned to $(2N-1)$ times the Thouless energy(Eq. \ref{eq:theory:E_th})
-        \begin{equation}
-            E_\text{Th} = \frac{\hbar^2 \pi^2}{2 \meff \left( 2 W \right)^2}
-            \label{eq:theory_E_th}
-        \end{equation}
+        The system is always topological when the superconducting phase is $\pi$, or when the magnetic field is tuned to $(2N-1)$ times the Thouless energy(Eq. \ref{eq:theory_E_th}).
+        Given the relationship between superconducting current and phase, control of the current allows for switching the system between the trivial phase and the topological phase.
 
@@
         \includegraphics[width=0.5\columnwidth]{figures/pientka_phase_diagram}
-        \caption{Phase vs. Magnetic field. Source\cite{pientka_topological_2017}}
+        \caption{Topological phase diagram as a function of superconducting phase and magnetic field.~\cite{pientka_topological_2017}
+        The diagram has a diamond shape, repeating along the magnetic field axis with a period equal to $2 E_\text{Th}$.
+        }
         \label{fig:pientka_phase_diagram}
@@
         In Figure \ref{fig:pientka_bandstructure}, the bandstructure is displayed for the SNS system.
-        Note that the gap is lowest at the Rashba/Zeeman split Fermi-surface, where the momentum in the x-direction equals $k_{F,1}$ or $k_{F,2}$.
+        Note that the gap attains the lowest value at the Rashba/Zeeman split Fermi-surface, where the momentum in the $x$-direction equals $k_{F,1}$ or $k_{F,2}$.
         It is at these momenta that the wavefunctions are completely parallel to the translationally invariant direction, causing weak coupling with the superconductors.
@@
         \caption{Bandstructure of a straight SNS system~\cite{pientka_topological_2017}.
-        Note that the gap is smallest at $k_{F,1}$ and $k_{F,2}$, which correspond to the two different Fermi momenta.}
+        Note that the gap is minimized when $k_x=k_{F,1}$ and $k_x=k_{F,2}$, which correspond to the Rashba/Zeeman split Fermi momenta.}
         \label{fig:pientka_bandstructure}

### 2019-02-05 thesis_report/title.tex
Made adjustments

--- 2018-09-06 thesis_report/title.tex
@@
 
-to be defended publicly on Tuesday January 1, 2013 at 10:00 AM.
+to be defended publicly on Tuesday February 12, 2019 at 14:30 AM.
 %in het openbaar de verdedigen op dinsdag 1 januari om 10:00 uur.
@@
     Project duration: & \multicolumn{2}{l}{March 1, 2018 -- November 28, 2018} \\
-    Thesis committee: & dr.\ A.\ Akhmerov, & TU Delft, supervisor \\
-        & MSc.\ B.\ Nijholt, & TU Delft \\
+    Thesis committee: & dr.\ A.\ Akhmerov, & TU Delft \\
+                      & Prof.\ dr.\ G.A.\ Steele, & TU Delft \\
+                      & dr.\ M.T.\ Wimmer, & TU Delft \\
 \end{tabular}
@@
 
+The cover is a SEM image of a zigzag SNS junction fabricated and photographed by Fokko de Vries and Qingzhen Wang.
+\bigskip
+
 An electronic version of this thesis is available at \url{http://repository.tudelft.nl/}.
-
 \end{center}

### 2019-02-05 thesis_report/methods.tex
fixed zigzag figures
Added corrections to methods

@@
 \chapter{Methods}\label{chap:methods}
+    This chapter contains the methods used to analyze the properties of zigzag shaped systems.
+    Due to the complex shape of the boundaries in a zigzag system, it is difficult to accurately model using an analytic approach.
+    Because of this, we mostly resort to numeric simulations of the system.
+    However, to isolate the mechanism behind the improvement of the topological gap, we propose an analytic model to give an estimation of the topological gap.
+
+    We first describe the geometry and physical model used in the zigzag system.
+    Subsequently, we discuss the numeric implementation consisting of a tight-binding model.
+    Finally, we describe the analytical model used to estimate the topological gap.
 
@@
 	\comment{We consider a two-dimensional system with zigzag.}
-	We consider a Josephson junction (JJ)(Fig.~\ref{fig:setup}) consisting of a two dimensional strip of semiconductor, with superconductors on both sides.
+	We consider a Josephson junction (JJ)(Figure~\ref{fig:setup}) consisting of a two-dimensional strip of semiconductor, with superconductors on both sides.
 	We modulate the shape of the normal region, which can be either zigzag as depicted, or a more smooth sinusoidal like shape.
-	Similar to the conventional straight system \cite{pientka_topological_2017}, a magnetic field $B_x$ is applied, along the x-axis.
-	We model the system with a BdG Hamiltonian, Eqs.~\eqref{eq:hamiltonian_n}-~\eqref{eq:hamiltonian_s}  ; the normal part has a linear Rashba spin-orbit coupling term characterized by the spin-orbit strength $\alpha$ , and a Zeeman energy $E_z= mu_B g B_x$.
+	Similar to the conventional straight system \cite{pientka_topological_2017}, a magnetic field $B_x$ is applied, along the $x$-axis.
+	We model the system with a BdG Hamiltonian, Eqs.~\eqref{eq:hamiltonian_n}-~\eqref{eq:hamiltonian_s}  ; the normal part has a linear Rashba spin-orbit coupling term characterized by the spin-orbit strength $\alpha$, and a Zeeman energy $E_z= mu_B g B_x$.
 	The superconductor has a superconducting coupling term $\Delta$ with a superconducting phase $\pm\phi/2$ (the phase difference between the superconductors is $\phi$).
 	Both parts have a kinetic term and chemical potential $\mu$ (counted from the bottom spin-orbit band). 
-	For the zigzag geometry, we first consider a sawtooth like pattern where $z_y$ is the amplitude, $z_x$ is the period, and $W$ the width of the junction.
+	For the zigzag geometry, we first consider a sawtooth like pattern where $z_y$ is the amplitude, $z_x$ the period, and $W$ the width of the junction.
 
@@
 	\centering
-	\includegraphics[width=0.5\columnwidth]{images/zigzag.pdf}
+	\includegraphics[width=0.75\columnwidth]{images/zigzag.pdf}
 	\caption{Figure of a zigzag system.
@@
 	$H_\text{K}$ describes the kinetic part of the Hamiltonian, $H_\text{SOI}$ is the spin-orbit term, $H_\text{Z}$ is the Zeeman coupling, and $H_\Delta$ represents the superconducting term.
-	The magnetic field (B) points along the x-axis.
+	The magnetic field (B) points along the $x$-axis.
 	\label{fig:setup}}
@@
 	\comment{The symmetry class of the system is D.}
-	The non-zigzag system is in the symmetry class BDI \cite{pientka_topological_2017}, unless the additional symmetries are broken due to for example a difference in superconducting gap magnitude between the two superconductors.
-	Using the software package Qsymm\cite{varjas_qsymm_2018}, we find that the symmetry class of our system to be D, because we break this chiral/time-reversal symmetry resulting from the mirror symmetric junction.
+	The non-zigzag system is in the symmetry class BDI \cite{pientka_topological_2017}, unless the additional symmetries are broken due to a difference in superconducting gap between the two superconductors, for instance.
+	Using the software package Qsymm\cite{varjas_qsymm_2018}, we find the symmetry class of our system to be D, because we break this chiral/time-reversal symmetry resulting from the mirror symmetric junction.
 
-\section{Tight binding simulation}
+\section{Tight-binding simulation}
 
@@
 	Each site has two orbitals: spin and electron-hole.
-	There are four different types of sites (and thus four different Hamiltonians): the top superconductor, the bottom superconductor, the normal region, and a normal region with an optional potential offset, acting as a barrier to simulate an imperfect NS interface.
-	A schematic of such kwant systems is depicted in Fig.~\ref{fig:kwant_system}.
+	There are four different types of sites (and thus four different Hamiltonians): the top superconductor, the bottom superconductor, the normal region, and another normal region with an optional potential offset, acting as a barrier to simulate an imperfect NS interface.
+	A schematic of such kwant systems is depicted in Figure~\ref{fig:kwant_system}.
 
@@
 	\caption{Figure of different examples of simulated systems in Kwant.
-	Lattice spacing is made bigger to make the discretization visible.
+	The lattice spacing is made bigger to make the discretization visible.
 	The two golden regions are both superconducting, but differ in phase.
@@
 	\comment{We extract the gap by either taking the lowest energy state for an infinite system, or the difference between the lowest two eigenstates.}
-	After the system is specified, we can extract the total Hamiltonian of the system, allowing analysis of the eigenstates.
+	After the system is specified, we can extract the total Hamiltonian, allowing analysis of the eigenstates.
 	For example, calculating the bandstructure of a system is performed by taking a translationally invariant system and calculating the eigenvalues for different momenta.
@@
 	To establish that the elimination of long trajectories is indeed the driving mechanism behind the improvement of the gap, we use an analytical model in an effort to isolate the gap-trajectory dependence.
-	We estimate the gap of the zigzag system by the minimum energy occuring in the Andreev spectrum of a single (diagonal) segment of zigzag (see Fig.~\ref{fig:zigzag_methods}).
+	We estimate the gap of the zigzag system by the minimum energy occuring in the Andreev spectrum of a single (diagonal) segment of zigzag (see Figure~\ref{fig:zigzag_methods}).
 	We define the spectrum of a single zigzag segment by identifying it with the spectrum of an infinite ribbon SNS junction with tilted-magnetic field.
@@
 	Estimating the gap is a two-step process: first, derivation of the Andreev spectrum, and second, taking the absolute minimum of that spectrum over the set of momenta allowed by the specific geometry.
-	An analytic expression for the spectrum is derived using scattering matrix formalism and the Andreev bound state condition\cite{beenakker1991universal, sticlet_robustness_2017}.
-	For the second step, the difficulty lies with identifying the set of allowed momenta in a particular geometry.
+	An analytic expression for the spectrum is derived using scattering matrix formalism and the Andreev bound state condition\cite{beenakker1991universal,sticlet_robustness_2017}.
+	For the second step, the difficulty lies with identifying the set of allowed momenta with a particular geometry.
 
@@
 
-		We derive the spectrum by calculating the scattering matrix for the normal region and applying the Andreev bound state condition for the short junction limit\cite{beenakker_universal_1991,sticlet_robustness_2017}..
+		We derive the spectrum by calculating the scattering matrix for the normal region and applying the Andreev bound state condition for the short junction limit\cite{beenakker_universal_1991,sticlet_robustness_2017}.
 		The short junction limit is valid for $W<\xi$, where $\xi$ is the superconducting coherence length.
@@
 			The `S' region corresponds to the superconductor Hamiltonian without the superconducting term, Eq.~\eqref{eq:ham_smat_superconducting}, `N' to the normal region, Eq.~\eqref{eq:ham_smat_normal}. 
-			The coefficients (corresponding to the scattering problem outlined in Eqs.~\ref{eq:scattering_matrix_problem} and \ref{eq:scattering_equations}) represent the amplitude of the modes present in the system, at a particular energy.
+			The coefficients (corresponding to the scattering problem outlined in Eqs.~\eqref{eq:scattering_matrix_problem} and \eqref{eq:scattering_equations}) represent the amplitude of the modes present in the system, at a particular energy.
 			The different color arrows correspond to the two different spinors in each region.
-			For example, $a_{1,L}$ is the amplitude of the rightmoving incoming mode, $\vec{\psi}_1 \exp\left(i k_{1,L} x\right)$}
+			For example, $a_{1,L}$ is the amplitude of the rightmoving incoming mode, $\vec{\psi}_1 \exp\left(i k_{1,L} x\right)$.}
 			\label{fig:scattering}
@@
 
-			We consider the scattering region as depicted in Fig. \ref{fig:scattering}.
+			We consider the scattering region as depicted in Figure \ref{fig:scattering}.
 			There are three regions in the system, one normal system (N), with Hamiltonian given by Eq.~\eqref{eq:ham_smat_normal}, and two superconducting regions (S), with Hamiltonian given by Eq.~\eqref{eq:ham_smat_superconducting}.
-			Note that Eq.~\eqref{eq:ham_smat_superconducting} region does not include the superconducting term ($\Delta \tau_y$), because we implement Andreev reflection seperately (see Eq.~\eqref{eq:andreev_scat_mat})~\cite{beenakker_universal_1991}: this way we avoid doubling (electron and hole) the dimensionality of the problem.
+			Note that Eq.~\eqref{eq:ham_smat_superconducting} region does not include the superconducting term ($\Delta \tau_y$), because we implement Andreev reflection separately)~\cite{beenakker_universal_1991} (see Eq.~\eqref{eq:andreev_scat_mat}: this way we avoid doubling (electron and hole) the dimensionality of the problem.
 
 			We set the energy of the system, and find the planar waves propogating in each region.
-			Because the plane waves can go in two directions, and the additional degree of freedom introduced due to spin, each region has four propogating waves.
+			Because the plane waves can go in two directions, and due to the additional degree of freedom introduced due to spin, each region has four propogating waves.
 			The idea of the scattering matrix is to set the vector $\vec{a}$, containing the amplitudes of the planar waves coming in to the scattering region, and find the amplitudes of the modes exiting the scattering region.
-			This is captured by a system of linear equations, displayed in Eq.~\eqref{eq:scattering_matrix_problem}.
+			This is captured by a system of linear equations:
 
@@
 
-			In order to find the coefficients of the matrix $S_\text{sns}(\epsilon)$, we take the wavefunction $u(x)$ and apply the boundary equations (continuity and flux conservation): specified in Eqs.~\eqref{eq:scattering_equations} through \eqref{eq:scattering_boundary_eqs}.
-			Note that because we neglect spin-orbit coupling in the x-direction, the velocity operator $\hat{\mathbf{v}}$ can be simplified to the first derivative.
+			In order to find the coefficients of the matrix $S_\text{sns}(\epsilon)$, we take the wavefunction $u(x)$ and apply the boundary equations (continuity and flux conservation) specified in Eqs.~\eqref{eq:scattering_equations} through \eqref{eq:scattering_boundary_eqs}.
+			Note that because we neglect spin-orbit coupling in the $x$-direction, the velocity operator $\hat{\mathbf{v}}$ can be simplified to the first derivative.
 			Although omitted to keep the expression compact, the momenta $k_i, q$ and spinors $\vec{\Psi_{i, L/R}}$ are energy dependent.
@@
 
-			Where $a_{i, L/R}$ are the coefficients of the incoming modes, $b_{i, L/R}$ are those of the outgoing modes, and $d_{i, l/r}$ are the modes in the middle region: see Fig.\ref{fig:scattering}.
+			where $a_{i, L/R}$ are the coefficients of the incoming modes, $b_{i, L/R}$ are those of the outgoing modes, and $d_{i, l/r}$ are the modes in the middle region (see Figure~\ref{fig:scattering}).
 			The symbols $\vec{\Psi}_{n/s, i}$ and $k_i, q$ are respectively the spinors and corresponding momenta belonging to each region.
@@
 
-			The boundary conditions are,
+			The boundary conditions are
 			\begin{align}
@@
 			To solve the system analytically, we use the Short Junction limit: we set $E=0$ in Eq.~\eqref{eq:scattering_matrix_problem}.
-			By applying the boundary conditions and solving the resulting linear system of equations, the resulting solution is given by Eqs.~\eqref{eq:smatrix} through ~\eqref{eq:momenta_short_junction}.
-			\emph{Important note: In order to use the Andreev bound state condition, the scattering matrix must be in the correct basis.
+			By applying the boundary conditions and solving the resulting linear system of equations, the solution is given
+			\footnote{Important note: In order to use the Andreev bound state condition, the scattering matrix must be in the correct basis.
 The relevant basis transformation has already been applied in Eqs.
-~\eqref{eq:smatrix} through ~\eqref{eq:momenta_short_junction}}.\\
+~\eqref{eq:smatrix} through ~\eqref{eq:momenta_short_junction}.}
+			 by Eqs.~\eqref{eq:smatrix} through ~\eqref{eq:momenta_short_junction}.
 
-			Scattering matrix, in block matrix format:
+			The scattering matrix, displayed in block matrix format:
 			\begin{align}
@@
 
-			Subexpressions:
+			The subexpressions used in Equation~\eqref{eq:smatrix} are
 			\begin{align}
@@
 
-			Momenta:
+			Finally, the $y$ momenta are
 			\begin{align}
@@
 		\subsubsection{Resulting spectrum}
-			In order to get the spectrum from the S-matrix [Eq.~\eqref{eq:smatrix}] we use the main result from Ref.~\cite{beenakker1991universal} and start with a determinantal equation for the bound state energies in a SNS-junction:
+			In order to get the spectrum from the S-matrix (Equation~\eqref{eq:smatrix}) we use the main result from Ref.~\cite{beenakker_universal_1991} and start with a determinantal equation for the bound state energies in a SNS-junction:
 
@@
 			\end{equation}
-			Where the Andreev scattering is captured by the matrix in Eq.~\ref{eq:andreev_scat_mat}, where $\phi_1$ and $phi_2$ are the phases of the respective superconductors.
+			Where the Andreev scattering is captured by the matrix in Eq.~\ref{eq:andreev_scat_mat}, where $\phi_1$ and $\phi_2$ are the phases of the respective superconductors.
 
@@
 
-			We rewrite this as a characteristic polynomial problem $\det\left[A-\lambda I\right]=0$, as
+			We rewrite this as a characteristic polynomial problem $\det\left[A-\lambda I\right]=0$
 
@@
 
-			Where $\lambda_i$ are the eigenvalues of $A$.
+			Here, $\lambda_i$ are the eigenvalues of $A$.
 			Inverting $\alpha\left(E\right)\equiv\exp\left(-i\arccos\left(E/\Delta\right)\right)$ yields $\frac{E}{\Delta}=\frac{\alpha^{2}+1}{2\alpha}=\frac{1}{2}\left(\alpha+\alpha^{-1}\right)=\textrm{Re}(\alpha)$, where the last equality holds because $\alpha$ is unitary.
@@
 		\caption{Schematic of the system, along with relevant dimensions, and the quasiclassical approach.
-		The $x^\prime, y^\prime$ axis depicts the rotated frame for the quasiclassical estimate.
+		The $x^\prime, y^\prime$ axes depict the rotated frame for the quasiclassical estimate.
 		The white trajectory indicates the estimate taken for the longest trajectory allowed by a zigzag.
@@
 		We assume that the zigzag is shaped such that there is no straight trajectory possible through the system anymore.
-		The system is depicted in Fig.~\ref{fig:zigzag_methods}, along with the set of axes with $x^\prime$ and $y^\prime$.
-		Note that the magnetic field has an angle $\theta$ with respect to the $x^\prime$ axis.
+		The system is depicted in Figure~\ref{fig:zigzag_methods}, along with the set of axes with $x^\prime$ and $y^\prime$.
+		Note that the magnetic field has an angle $\theta$ with respect to the $x^\prime$-axis.
 		We identify trajectories cut off by the zigzag with a particular range of forbidden momenta.
-		By then analysing the bandstructure of this infinite SNS junction, we can give an estimate the resulting gap of the device.
+		By then analysing the bandstructure of this infinite SNS junction, we can give an estimate on the resulting gap of the device.
 		As the system is only momentum localized in the $x$ direction (the translationally invariant direction), we only control $\kx$.
-		Denoting the set of allowed momenta by $\Omega$, the equation for the estimated topological gap becomes,
+		Denoting the set of allowed momenta by $\Omega$, the equation for the estimated topological gap becomes
 
@@
 		In the infinite system, the long trajectories have a small angle with respect to the $x^\prime$ axis.
-		By defining a minimum angle, we thus can filter out the long trajectories.
-		We define this angle $\beta_\text{min}$ by identifying it with the angle of the longest trajectory from one side of the superconductor to the other: see Fig.~\ref{fig:zigzag_methods}.
-		Note that longer trajectories exist, by `grazing' the concave corners of the zigzag.
+		By defining a minimum angle, we can thus filter out the long trajectories.
+		We define this angle $\beta_\text{min}$ by identifying it with the angle of the longest trajectory from one side of the superconductor to the other (see Figure~\ref{fig:zigzag_methods}).
+		Note that longer do trajectories exist, by `grazing' the concave corners of the zigzag.
 		We suspect that this `grazing' leads to physics which cannot be captured in this simple model, and we thus choose to restrict this method for systems where the chosen trajectory is indeed a good approximation of the longest path.
@@
 
-        We estimate the restriction of the domain for the momentum by geometrically calculating the minimum angle, as depicted in Fig.\ref{fig:zigzag_methods}. The result:
+        We estimate the restriction of the domain for the momentum by geometrically calculating the minimum angle, as depicted in Figure~\ref{fig:zigzag_methods}. The result:
 

### 2019-02-05 paper/snakemajoranas.tex
changes to the paper

@@
 
-\comment{The symmetry class of the system is D.}
-The non-zigzag system is in the symmetry class BDI \cite{pientka2017topological}.
-Using the software package Qsymm\cite{varjas2018qsymm}, we find that the symmetry class of our system to be $\mathcal{D}$ because we break the chiral symmetry $\mathcal{C}$ resulting from the mirror symmetric junction.
-
 \begin{small}
@@
 
-\comment{We discretize the model described in section II and simulate it with Kwant.}
+\comment{We discretize the Hamiltonian and simulate it with Kwant.}
 We discretize our continuum Hamiltonian \eqref{eq:hamiltonian} and implement a tight-binding model using Kwant~\cite{groth_kwant:_2014}.
@@
 The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size increases by more than an order of magnitude.
-This happens because in a straight system long trajectories are possible, these have a momentum that is directed along the strip and consequently, $k_x \approx k_F$.
+This increase happens because in a straight system long trajectories are possible, these have a momentum that is directed along the strip and consequently, $k_x \approx k_F$.
 The smallest gap in a straight system occurs around $k_F$, and because the zigzag cuts off long trajectories, the gap size increases. 
@@
 
-\comment{The introduction of an SN interface at many angles also increases performance.}
+\comment{The introduction of an NS interface at many angles increases the transparency.}
 Additionally, in the presence of normal reflection, due to the presence of NS interfaces at a wide range of angles, the reflected part will eventually scatter with a near perpendicular surface.
@@
 Noting the gap closings and the fact we know the topology for the non-zigzag system, we can infer the topology of the system with zigzag modulation. % Bas: I don't understand what is written here
+
+\comment{The introduction of the zigzag breaks a chiral symmetry, bringing the system from the BDI to the D symmetry class}
+The non-zigzag system is in the symmetry class BDI \cite{pientka2017topological}.
+Using the software package Qsymm\cite{varjas2018qsymm}, we find that the symmetry class of our system to be $\mathcal{D}$ because we break the chiral symmetry $\mathcal{C}$ resulting from the mirror symmetric junction.
 
@@
 
-\comment{We find the Majorana lengths by calculating the slowest decaying mode.}
+\comment{We find the Majorana lengths by fitting an exponential to the wavefunction.}
 Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinusoids.
@@
 
-\comment{We also confirm that the specific shape does not matter.}
+\comment{We confirm that the specific shape and its details do not matter.}
 Also note the similarity between the various shapes, sharp corners or a smoother system, the effect is the same.
@@
 
-\comment{It would be interesting to study what geometry creates an optimal environment for Majorana modes to exist.}
-We have studied sawtooth, snake-like and offset sinusoidal modulation of the semiconductor region, but perhaps a more exotic shape will be optimal.
+\comment{It is interesting to study what geometry creates an optimal environment for Majorana modes to exist.}
+We have studied sawtooth, snake-like, and offset sinusoidal modulation of the semiconductor region, but perhaps a more exotic shape will be optimal.
 A study optimizing the geometry for supporting Majoranas would be an interesting continuation.

### 2019-02-05 paper/snakemajoranas.tex
review on phone

@@
 \comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry. }
-Similar to what is described by Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond-like structure as a function of phase $\phi$ and Zeeman field $E_Z$.
+Similar to what is described by Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond-like shape as a function of phase $\phi$ and Zeeman field $E_Z$.
 We also observe additional gap closings which are due to the BDI symmetry that is present.
-As expected for the zigzag system, the magnitude of the gap is significantly improved, while maintaining the diamond-like shape.
-As the zigzag shape destroys the additional symmetry, moving it to class D, we see a cleaner topological region.
+As expected for the zigzag system, the magnitude of the gap is significantly improved, while preserving the diamond-like shape in parameter space.
+Because the introduction of the zigzag shape moves the system to class D, we see a cleaner topological region due to the absence of the gap closings resulting from the BDI symmetry.
 
@@
 and the subplots (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W$ is the junction width.
-We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
+We observe that once there are no more straight trajectories possible inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
 \label{fig:bandstuctures}}
@@
 \includegraphics[width=0.95\columnwidth]{figures/phasediagrams}
-\caption{Phase diagrams of a straight system (a, b) and zigzag system (c, d), where (a, c) are $E(\mu, B)$ and (b, d) are $E(\phi, B)$.
-We use a generalized eigenvalue problem to find all phase boundaries at once and find the minimal energy gap by finding the minimum in the spectrum: $\min{E(k)}$.
+\caption{Phase diagrams of a straight system (a), (b) and zigzag system (c), (d), where (a), (c) are $E(\mu, B)$ and (b), (d) are $E(\phi, B)$.
+% We use a generalized eigenvalue problem to find all phase boundaries at once and find the minimal energy gap by finding the minimum in the spectrum: $\min{E(k)}$.
 \label{fig:phasediagrams}}
@@
 
+\comment{In a straight system, the Majoranas are very poorly localized.}
+For the ribbon system [Fig.~\ref{fig:wavefunction}(a)], we see that the decay of the density is long compared to the system size.
+The wavefunction extends to the center of the system, resulting in overlapping Majoranas and a non-zero energy of the state.
+Further, the energy of the Majorana state in the straight system is badly septated from the next lowest lying eigenstate.
+Altogether, for the parameters of the system, the Majoranas are very poorly localized and topological protection against perturbations is minimal.
+
 \comment{In a zigzag geometry Majoranas are localized within one segment of zigzag.}
+All of the zigzag type geometries show a reduced coherence length.
+The delocalized nature of the wavefunctions is clearly visible through the density plots.
+Quantitatively, the improvement in the localization of the Majoranas is also distinctly apparent: the energies of the Majorana states are three orders of magnitude lower than the energy of the second lowest-lying wavefunctions.
+As mentioned in the previous section, this can be attributed to the way the gap and velocity factor into the Majorana coherence length.
+
+\comment{We also confirm that the specific shape does not matter.}
+The shape of the wavefunctions does not change significantly depending on the details of the geometry.
+The sharp corners of the sawtooth versus the smooth shape of the snakelike system do not have a significant impact on the shape of the wavefunction and neither do the disordered edges effect the relevant parameters.
 

### 2019-02-05 thesis_report/results.tex
fixed zigzag figures

--- 2019-02-04 thesis_report/results.tex
@@
 		In this chapter, we show how some properties of the system change by the introduction of a zigzag geometry.
-		Additionally, we attempt to isolate the mechanism behind the improved properties by estimating the gap size through the quasiclassical model introduced in chapter \ref{chap:methods}.
+		Additionally, we attempt to isolate the mechanism behind the improved properties by estimating the gap size through the quasiclassical model introduced in Chapter \ref{chap:methods}.
 
@@
 
+			\comment{We calculate the bandstructure for varying amount of zigzag.}
+			We implement a tight-binding version of the model described in Section \ref{sec:physical_picture}.
+			In Figure~\ref{fig:bandstuctures}, the bandstructure for saw-toothed zigzag systems Figure~\ref{fig:zigzag_methods} with varying amplitude is displayed.
+			Because the zigzag has to be modelled using a supercell, we see a folded bandstructure.
+			For the sake of comparison, we take the same cell size for the ribbon structure, so the bandstructure folds in the same way.
+
 			\begin{figure}[!htb]
@@
 			\includegraphics[width=0.55\columnwidth]{figures/bandstructures}
-			\caption{Figure of the bandstuctures corresponding to the system in Fig.~\ref{fig:zigzag_methods}.
+			\caption{Figure of the bandstuctures corresponding to the system in Figure~\ref{fig:zigzag_methods}.
 			Blue lines correspond to $\phi=0$, $B=0$, red lines to $\phi=\pi$, $B = 1$.
-			Thre three subplots are for different amplitudes of zigzag: (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W=200$\si{\nm} is the junction width.
+			The three subplots are for different amplitudes of zigzag: (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W=200$\si{\nm} is the junction width.
 			We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
@@
 
-			\comment{We calculate the bandstructure for varying amount of zigzag.}
-			We implement a tight-binding version of the model described in section \ref{sec:physical_picture}.
-			In figure~\ref{fig:bandstuctures}, the bandstructure for saw-toothed zigzag systems [Fig.~\ref{fig:zigzag_methods}] with varying amplitude is displayed.
-			Because the zigzag has to be modelled using a supercell, we see a folded bandstructure.
-			For comparison's sake, we take the same cell size for the ribbon structure, so the bandstructure folds in the same way.
-
 			\comment{The band structures show that modulation of the geometry increases the gap by an order of magnitude, as well as reduce the group velocity.}
@@
 			This increase happens because the modes where the gap is the smallest when the momentum almost entirely focuses along the strip ($k_x=k_F$), are cut off in a zigzag geometry.
-			There is also a significant reduction of the group velocity where in Fig.~\ref{fig:bandstuctures} (c) the bands are nearly completely flat.
+			There is also a significant reduction of the group velocity where in Figure~\ref{fig:bandstuctures} (c) the bands are nearly completely flat.
 			The size of the gap, together with the velocity, directly relate to the Majorana coherence length (Eq.~\eqref{eq:majorana_coherence_length}), which we discuss in the following section.
@@
 			Finally, in the presence of normal reflection, due to the availability of NS interfaces at a wide range of slopes, a zigzag system has an increased effective transmission.
-			In a zigzag system, the normally reflected part of a wavefunction will eventually intersect a surface with which it is nearly perpendicular to.
+			In a zigzag system, the normally reflected part of a wavefunction will eventually intersect a surface to which it is nearly perpendicular.
 			The transparency of the NS interface thus improves for non-transversal modes.
@@
 			\comment{We calculate the lowest eigenfunction and plot the density.}
-			Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve, and vertically offset sinusoids.
-			In figure~\ref{fig:wavefunctions} displays the wavefunctions superimposed upon their respective geometry including the corresponding Majorana energies $E_M$, as well as $E_1$: the energies corresponding to the next lowest state.
+			Using the tight-binding package Kwant~\cite{groth_kwant_2014}, we model a finite system to compute the Majorana wave function density for different geometries namely, ribbon, zigzag, parallel curve, and vertically offset sinusoids.
+			In Figure~\ref{fig:wavefunctions} displays the wavefunctions superimposed upon their respective geometry including the corresponding Majorana energies $E_M$, as well as $E_1$: the energies corresponding to the next lowest state.
 
@@
 			We observe that $\xi$ for (a) is orders of magnitude longer and $E_\textrm{gap} = E_\textrm{1} - E_M$ orders of magnitude smaller than for (b), (c), and (d), meaning that the details of the geometry do not matter for the improvements to occur.
-			\label{fig:wavefunctions}}
+			The value of the remaining parameters are $\alpha=20$ \si{\milli \eV \nm}, $g=26$, $\meff=0.02$\si{\electronmass}, $\mu=20$ \si{\milli \eV}, $\Delta=1$ \si{\milli \eV}, $B=1$\si{\tesla}, $\phi=2\pi$.
+			}\label{fig:wavefunctions}
 			\end{figure}
@@
 			\comment{In a straight system, the Majoranas are very poorly localized.}
-			For the ribbon system [Fig.~\ref{fig:wavefunction}(a)], we see that the decay of the density is long compared to the system size.
+			For the ribbon system Figure~\ref{fig:wavefunctions}(a), we observe that the decay of the density is long, compared to the size of the system.
 			We see that the wavefunction extends to the centre of the system, not showing the delocalization sought after.
-			Apart from the density, as discussed in chapter \ref{chap:theory}, an overlap of Majoranas leads to a non-zero energy of the state.
-			Taking this into consideration, we see that the energy of the Majorana state in the straight system is only barely below the next lowest lying eigenstate: the Majoranas are very poorly localized and topological protection against perturbations is minimal.
+			Apart from the density, as discussed in Chapter \ref{chap:theory}, an overlap of Majoranas leads to a non-zero energy of the state.
+			Taking this into consideration, it is clear that the energy of the Majorana state in the straight system is only barely below the next lowest lying eigenstate: the Majoranas are very poorly localized and the topological protection against perturbations is minimal.
 
@@
 for magnetic field vs.
-phase difference it is diamond shaped: Fig.~\ref{fig:pientka_phase_diagram}), we can infer the topology of the system with zigzag modulation.
-			In figure ~\ref{fig:phasediagrams}, we plot the energy gap as a function of magnetic field, chemical potential, and the superconducting phase difference for both a straight system [(a) and (b)] and a zigzag system [(c) and (d)].
+phase difference it is diamond shaped: Figure~\ref{fig:pientka_phase_diagram}), we can infer the topology of the system with zigzag modulation.
+			In Figure~\ref{fig:phasediagrams}, we plot the energy gap as a function of magnetic field, chemical potential, and the superconducting phase difference for both a straight system ((a) and (b)) and a zigzag system ((c) and (d)).
 
@@
 			\caption{Phase diagrams of a straight system (a), (b) and zigzag system (c), (d), where (a), (c) are $E(\mu, B)$ and (b), (d) are $E(\phi, B)$.
-			We use a generalized eigenvalue problem to find all phase boundaries at once and find the minimal energy gap by finding the minimum in the spectrum: $\min{E(k)}$.
+			We numerically compute the dispersion of the translationally invariant versions of a straight and zigzag system and take the minimum  $\min{E(k)}$ to obtain the energy gap.
+			The value of the remaining parameters are $\alpha=20$ \si{\milli \eV \nm}, $g=26$, $\meff=0.02$\si{\electronmass}, $\Delta=1$ \si{\milli \eV}.
 			\label{fig:phasediagrams}}
@@
 			Similar to what is described by Pientka et.
-al~\cite{pientka2017topological} (see Fig.~\ref{fig:pientka_phase_diagram}), we see that the straight geometry, as a function of superconducting phase difference and Zeeman field (b), has a diamond-shaped phase diagram.
-			The additional gap closings visible within the diamond are because of the presence of a chiral symmetry which classifies the system as BDI and causes the region of interest, where there is a single pair of Majoranas, to be relatively small.
+al~\cite{pientka_topological_2017}, we see that the straight geometry, as a function of superconducting phase difference and Zeeman field (Figure \ref{fig:phasediagrams}(b)), has a diamond-shaped phase diagram.
+			The additional gap closings visible within the diamond are due to the presence of a chiral symmetry which classifies the system as BDI and causes the region of interest, where there is a single pair of Majoranas, to be relatively small.
 
@@
 		\comment{We compare different techniques to calculate the band structure of a straight system.}
-		We verify the validity of the analytic model described in chapter \ref{chap:methods} and compute the bandstructure of a straight system in a tilted magnetic field.
-		In figure \ref{fig:spectrum_calculation_comparison}, we compare the analytical model with band structures obtained using three different methods, implemented in Kwant.
-		To show that the model has been correctly implemented, we compute the Kwant scattering matrix of the identical model used in the analytics and substitute it into the bound state condition\eqref{eq:bound_state_condition_sjl} (labelled Kwant without SOI SJL).
-		To show the validity of neglecting spin-orbit in the transverse direction, we also compute the scattering matrix including the additional term and again use the bound state condition to obtain the spectrum (labelled Kwant with SOI SJL).
+		We verify the validity of the analytic model described in Chapter \ref{chap:methods} and compute the bandstructure of a straight system in a tilted magnetic field.
+		In Figure~\ref{fig:spectrum_calculation_comparison}, we compare the analytical model with band structures obtained using three different methods, implemented in Kwant.
+		To show that the model has been correctly implemented, we compute the Kwant scattering matrix of the identical model used in the analytics and substitute it into the bound state condition (Equation~\eqref{eq:bound_state_condition_sjl}) (labelled Kwant without SOI SJL).
+		In order to prove the validity of neglecting spin-orbit in the transverse direction, we also compute the scattering matrix including the additional term and again use the bound state condition to obtain the spectrum (labelled Kwant with SOI SJL).
 		We also perform the full calculation of the spectrum by computing the bandstructure of the corresponding Kwant system (labelled Full ribbon Kwant system): this result serves as the benchmark for the other techniques.
@@
 			We attribute this to the loose compliance with the short junction limit: one needs both a long superconducting coherence length, as well as the energies in the spectrum to be near zero.
-			As we find the accuracy of the analytical spectrum to be relatively weak, we continue estimation of the gap in a zigzag system using the spectrum calculated with the full Kwant system.
+			As we find the accuracy of the analytical spectrum to be relatively weak, we the continue estimation of the gap in a zigzag system using the spectrum calculated with the full Kwant system.
 
 		\subsection{Estimation of the gap through momentum cutoff}
-			As explained in chapter \ref{chap:methods}, we estimate the topological gap using a quasiclassical estimate.
-			We keep the ratio $4\dfrac{z_x}{z_y}$ constant and compute the gap as a function of $z_y$.
-			In figure \ref{fig:quasiclassical_approximation}, the result is shown, comparing numerical gap calculations of the full zigzag system (full lines), with the result of the quasiclassical estimation.
+			As explained in chapter \ref{chap:methods}, we estimate the topological gap using a quasiclassical estimate (see Eqs.~\eqref{eq:definition_gap} and \eqref{eq:restriction_momentum}).
+			We keep the ratio $\dfrac{z_x}{z_y}$ constant and compute the gap as a function of $z_y$.
+			In Figure~\ref{fig:quasiclassical_approximation}, the result is shown, comparing numerical gap calculations of the full zigzag system (full lines), with the result of the quasiclassical estimation.
 			Note that the quasi-classics are only valid once the zigzag cuts off all trajectories which extend infinitely.
-			Also important to note is that for the quasiclassical estimate, we set the longest trajectory to be the trajectory that does not include the corners, as depicted in Fig.~\ref{fig:longest_trajectory_wo_corners}
+			It is also important to notice that for the quasiclassical estimate, we set the longest trajectory to be the trajectory that does not include the corners, as depicted in Figure~\ref{fig:quasiclassical_approximation}.
 
@@
 			\centering
-			\includegraphics[width=0.45\columnwidth]{images/longest_trajectory_wo_corners}
+			\includegraphics[width=0.75\columnwidth]{images/longest_trajectory_wo_corners}
 			\caption{Diagram depicting quasiclassical estimate of a zigzag system, but now with the longest trajectory chosen to avoid the corners of the zigzag.}
@@
 			\caption{Comparison of the topological gap computed using a full zigzag system implemented in Kwant with the quasiclassical estimate.
-			The ratio $4\dfrac{z_x}{z_y}$ is kept constant at three different values, and the gap is calculated for varying $z_y$.
+			The ratio $\dfrac{z_x}{z_y}$ is kept constant at three different values, and the gap is calculated for varying $z_y$.
 			The full lines represent  the numerical gap calculations of the full zigzag system, the dashed lines represent the quasiclassical estimation.}
@@
 			This point is different for the three ratios but can be identified by where the gap is largest for the quasiclassical estimate (dashed lines).
-			Increasing $z_y$ further would only allow longer trajectories, which would seem extra undesirable due to the magnetic field not being aligned with the diagonal sections.
+			Increasing $z_y$ further would only allow longer trajectories, which would seem particularly undesirable due to the magnetic field not being aligned with the diagonal sections.
 
@@
 			We also see that the gap declines monotonically with respect to the zigzag amplitude, which is by design: increasing the zigzag amplitude corresponds to increasing the domain of permitted trajectories, and thus the minimum can only decrease.
-			Even so, we see that the decline of the gap with respect to $z_y$ is much quicker than with an actual zigzag.
+			Even so, we observe that the decline of the gap with respect to $z_y$ is much quicker than with an actual zigzag.
 			A possible reason that the quasiclassical model sketches a darker picture than full zigzag, is because in that model, long trajectories also correspond to grazing angles of incidence at the NS interface.

### 2019-02-05 thesis_report/methods.tex
SJL introduced

@@
 
-		We derive the spectrum by calculating the scattering matrix for the normal region and applying the Andreev bound state condition for the short junction limit\cite{beenakker_universal_1991,sticlet_robustness_2017}.
-		The short junction limit is valid for $W<\xi$, where $\xi$ is the superconducting coherence length.
+		We derive the spectrum by calculating the scattering matrix $S(\epsilon)$ for the normal region and applying the Andreev bound state condition (Eq.~\eqref{eq:bound_state_condition_sjl}) for the short junction limit \cite{beenakker_universal_1991,sticlet_robustness_2017}.
+		The short junction limit corresponds to the case where we can neglect the energy dependence of the scattering matrix: $S(\epsilon) \approx S(0)$.
+		This limit is valid for $W<\xi$, where $\xi$ is the superconducting coherence length.
 		For deriviation of the scattering matrix, we neglect SOI in the transverse direction, which is valid for $W<l_\text{so}$.

### 2019-02-05 thesis_report/conclusion.tex
Added structure

@@
 % -*- root: ./report.tex -*-
-\chapter{Conclusion}
+\chapter{Conclusion}\label{chap:conclusion}
 In the model we study, the introduction of a zigzag geometry increases the topological gap by several orders of magnitude while simultaneously reducing the Majorana length.

### 2019-02-05 thesis_report/introduction.tex
Added structure

@@
 	In this thesis we show that the introduction of a zigzag-shaped modulation of the junction region leads to an increased topological gap, as well as the reduction of the Majorana coherence length.
-	Furthermore, we hypothesize that the gap improvement is the result of the elimination of long trajectories
+	Furthermore, we hypothesize that the gap improvement is the result of the elimination of long trajectories.
+	In order to verify this claim, we propose a simplified model of the zigzag system such that we can isolate the dependence of the gap on the length of available trajectories.
+
+	In Chapter \ref{chap:theory}, we give an overview of established theory relevant to the understanding of this thesis.
+	Subsequently, in Chapter \ref{chap:methods} we discuss the various methods used for the analysis of zigzag systems, of which the results are discussed in chapter \ref{chap:results}.
+	Finally, in Chapter \ref{chap:conclusion}, we discuss the findings of this thesis, as well as an outlook on further research to be performed.

### 2019-02-05 paper/snakemajoranas.tex
work on the localization section

@@
 %%██████████████████████████████████████████████████████████████████████████
-\section{Calculating the bandstuctures.}
+\section{Calculating the bandstuctures.}\label{sec:bandstuctures}
 
 \comment{We discretize the Hamiltonian and simulate it with Kwant.}
-We discretize our continuum Hamiltonian \eqref{eq:hamiltonian} and implement a tight-binding model using Kwant~\cite{groth_kwant:_2014}.
+We discretize our continuum Hamiltonian \eqref{eq:hamiltonian} on a square grid and implement a tight-binding model using Kwant~\cite{groth_kwant:_2014}.
 The resulting Hamiltonians are large because instead of having a single slice of sites that is translationally invariant in the $x$-direction, we create a long supercell to make the structure periodic.
@@
 \comment{The band structures show that modulation of the geometry increases the gap by an order of magnitude, as well as reduce the group velocity.}
-The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size increases by more than an order of magnitude.
-This increase happens because in a straight system long trajectories are possible, these have a momentum that is directed along the strip and consequently, $k_x \approx k_F$.
-The smallest gap in a straight system occurs around $k_F$, and because the zigzag cuts off long trajectories, the gap size increases. 
-Besides this, the velocity of the modes greatly reduces, which has a positive effect on the Majorana coherence length, as described later in section XXX. % TODO: add ref
+The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the topological gap increases by more than an order of magnitude.
+On an intuitive level we can understand this because in a straight system long trajectories are possible, these have a momentum that is directed along the strip and consequently, $k_x \approx k_F$.
+Further, the smallest gap in a straight system occurs around $k_F$, and because the zigzag cuts off long trajectories, the gap size increases.
+Besides this, the velocity of the modes greatly reduces, which has a positive effect on the Majorana coherence length, as described later in section \ref{sec:shape_effects}.
 
@@
 As expected for the zigzag system, the magnitude of the gap is significantly improved, while preserving the diamond-like shape in parameter space.
-Because the introduction of the zigzag shape moves the system to class D, we see a cleaner topological region due to the absence of the gap closings resulting from the BDI symmetry.
+Additionally, we see a cleaner topological region due to the absence of the gap closings resulting from the former mentioned chiral symmetry.
 
@@
 %%██████████████████████████████████████████████████████████████████████████
-\section{Localization lengths and shape effects}
+\section{Localization lengths and shape effects}\label{sec:shape_effects}
+
+\comment{We calculate the wave functions and find the Majorana lengths by fitting an exponential.}
+We model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve, and variants of the former with disordered egdes.
+By diagonalizing the Hamiltonian we find the Majorana energy $E_\textrm{M}$ and the energy of the first excited state $E_1$, the lowest and second lowest energies, respectively.
+Using the eigenstates, we calculate the Majorana decay length $\lambda_\textrm{M}$ by fitting an exponential to the desity of the Majorana wavefunction projected on the $x$-axis.
+In figure~\ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.
+All systems have identical Hamiltonian parameters in order to meaningfully compare the effects of the changing geometry.
 
@@
 The wavefunction extends to the center of the system, resulting in overlapping Majoranas and a non-zero energy of the state.
-Further, the energy of the Majorana state in the straight system is badly septated from the next lowest lying eigenstate.
-Altogether, for the parameters of the system, the Majoranas are very poorly localized and topological protection against perturbations is minimal.
+Further, the energy of the Majorana state $E_\textrm{M}$ in the straight system is badly septated from the next lowest lying eigenstate $E_1$.
+Altogether, the increase in the topological gap, but also the before mentioned reduction of the group velocity, result in poorly localized Majoranas and a minimal topological protection against perturbations.
+% XXX: probably put the eq for coherence length here
 
 \comment{In a zigzag geometry Majoranas are localized within one segment of zigzag.}
-All of the zigzag type geometries show a reduced coherence length.
-The delocalized nature of the wavefunctions is clearly visible through the density plots.
+We observe that for zigzag systems the Majorana properties properties improve.
+All of the zigzag type geometries display a reduced coherence length and the delocalized nature of the wavefunctions is improved, as is visible through the density plots.
 Quantitatively, the improvement in the localization of the Majoranas is also distinctly apparent: the energies of the Majorana states are three orders of magnitude lower than the energy of the second lowest-lying wavefunctions.
-As mentioned in the previous section, this can be attributed to the way the gap and velocity factor into the Majorana coherence length.
+As mentioned in section \ref{sec:bandstuctures}, this can be attributed to the way the energy gap and velocity factor into the Majorana coherence length which scales with these parameters $\lambda_\textrm{M}=\hbar\frac{v_\textrm{F}}{\Delta_\textrm{ind}}$.
 
-\comment{We also confirm that the specific shape does not matter.}
+\comment{The specific geometry is not important.}
 The shape of the wavefunctions does not change significantly depending on the details of the geometry.
@@
 
-\comment{We find the Majorana lengths by fitting an exponential to the wavefunction.}
-Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinusoids.
-In figure~\ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.
-For the ribbon system, we see that the Majorana coherence length is relatively large, not showing the delocalized nature sought after.
-All of the zigzag type geometries, however, show significantly reduced coherence length.
-Two effects can explain this: the increase in the topological gap, but also the before mentioned reduction of the group velocity.
-
-\comment{We confirm that the specific shape and its details do not matter.}
-Also note the similarity between the various shapes, sharp corners or a smoother system, the effect is the same.
-
 \begin{figure}[!htb]
 \includegraphics[width=0.95\columnwidth]{figures/wavefunctions}
-\caption{Wavefunctions for different sizes and geometries.
+\caption{Density of wavefunctions $|\psi|^2$ for different sizes and geometries.
 With (a) a straight system, (b) a zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) a system with vertically offset sinusoids.

### 2019-02-05 thesis_report/introduction.tex
added novelty of thesis

@@
 
-	In this thesis we show that the introduction of a zigzag-shaped modulation of the junction region leads to an increased topological gap, as well as the reduction of the Majorana coherence length.
-	Furthermore, we hypothesize that the gap improvement is the result of the elimination of long trajectories.
+\section{Thesis structure}
+	In this thesis we show that the introduction of a zigzag-shaped modulation of the junction region leads to an order of magnitude increase of the topological gap, as well as a significant reduction of the Majorana decay length.
+	The proposed alteration of the geometry has the potential to eliminate the problem of a soft gap, whilst staying compatible with current fabrication methods.
+	Additionally, the reduction of the Majorana decay length allows for shorter systems to produce a higher magnitude of seperation, which is favorable because the coherence length of a material sets a limit for the device size.
+
+	Furthermore, we try to establish the working mechanism behind the improvements: we hypothesize that the gap improvement is the result of the elimination of long trajectories.
 	In order to verify this claim, we propose a simplified model of the zigzag system such that we can isolate the dependence of the gap on the length of available trajectories.
@@
 	Subsequently, in Chapter \ref{chap:methods} we discuss the various methods used for the analysis of zigzag systems, of which the results are discussed in chapter \ref{chap:results}.
-	Finally, in Chapter \ref{chap:conclusion}, we discuss the findings of this thesis, as well as an outlook on further research to be performed.
+	Finally, in Chapter \ref{chap:conclusion} we discuss the findings of this thesis, as well as provide an outlook on further research to be performed.

### 2019-02-05 thesis_report/theory.tex
added novelty of thesis

@@
     Note that in this system, the two superconducting slabs (blue) are deposited onto the semiconductor, proximitizing the 2DEG below.
-    By doing so, the underlying areas become the effective superconductors, and the entire system is defined within the semiconductor crystal, ensuring virtually perfect NS interfaces.}
+    By doing so, the underlying areas become the effective superconductors, and the entire system is defined within the semiconductor crystal, ensuring virtually perfect NS interfaces.\\
+    Image taken from \cite{pientka_topological_2017} licensed under CC BY 4.0.
+    }
     \label{fig:pientka_system}
@@
         \includegraphics[width=0.5\columnwidth]{figures/pientka_phase_diagram}
-        \caption{Topological phase diagram as a function of superconducting phase and magnetic field.~\cite{pientka_topological_2017}
-        The diagram has a diamond shape, repeating along the magnetic field axis with a period equal to $2 E_\text{Th}$.
+        \caption{Topological phase diagram as a function of superconducting phase and magnetic field.
+        The diagram has a diamond shape, repeating along the magnetic field axis with a period equal to $2 E_\text{Th}$.\\
+        Image taken from \cite{pientka_topological_2017} licensed under CC BY 4.0.
         }
@@
         \includegraphics[width=0.5\columnwidth]{figures/pientka_bandstructure}
-        \caption{Bandstructure of a straight SNS system~\cite{pientka_topological_2017}.
-        Note that the gap is minimized when $k_x=k_{F,1}$ and $k_x=k_{F,2}$, which correspond to the Rashba/Zeeman split Fermi momenta.}
+        \caption{Bandstructure of a straight SNS system.
+        Note that the gap is minimized when $k_x=k_{F,1}$ and $k_x=k_{F,2}$, which correspond to the Rashba/Zeeman split Fermi momenta.\\
+        Image taken from \cite{pientka_topological_2017} licensed under CC BY 4.0.
+        }
         \label{fig:pientka_bandstructure}

### 2019-02-05 paper/snakemajoranas.tex
improvements to paper text

@@
 
+Unless noted differently, the parameters of the system are $\alpha=20$ \si{\milli \eV \nm}, $g=26$, $\meff=0.02$\si{\electronmass}, $\mu=20$ \si{\milli \eV}, $\Delta=1$ \si{\milli \eV}.
+
 %%██████████████████████████████████████████████████████████████████████████
@@
 To speed up these expensive simulations we employ an adaptive sampling strategy, using the Python package Adaptive. % TODO: add a citation
+
+\begin{figure}[!htb]
+\includegraphics[width=0.95\columnwidth]{figures/bandstructures}
+\caption{Figure of the bandstuctures corresponding to the system in Fig.~\ref{fig:zigzag_methods}.
+Blue lines correspond to $\phi=0$, $B=0$ and red lines to $\phi=\pi$, $B = \SI{1}{\T}$.
+The three subplots are for different amplitudes of the zigzag, with (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W=200$\si{\nm} is the junction width.
+We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
+\label{fig:bandstuctures}}
+\end{figure}
 
@@
 \begin{figure}[!htb]
-\includegraphics[width=0.95\columnwidth]{figures/bandstructures}
-\caption{Figure of the bandstuctures.
-Where the lines are (blue) $\phi=0$, $B=0$ and (red) $\phi=\pi$, $B \ne 0$.
-and the subplots (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W$ is the junction width.
-We observe that once there are no more straight trajectories possible inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
-\label{fig:bandstuctures}}
-\end{figure}
-
-\begin{figure}[!htb]
 \includegraphics[width=0.95\columnwidth]{figures/phasediagrams}
 \caption{Phase diagrams of a straight system (a), (b) and zigzag system (c), (d), where (a), (c) are $E(\mu, B)$ and (b), (d) are $E(\phi, B)$.
-% We use a generalized eigenvalue problem to find all phase boundaries at once and find the minimal energy gap by finding the minimum in the spectrum: $\min{E(k)}$.
+Phase diagrams of a straight system (a), (b) and zigzag system (c), (d), where (a), (c) are $E(\mu, B)$ and (b), (d) are $E(\phi, B)$.
+We compute the dispersion of the translationally invariant realizations of a straight and saw-toothed zigzag system and find $\min{E(k)}$ to obtain the energy gap.
+% Additionally, use a generalized eigenvalue problem to find all phase boundaries at once.
 \label{fig:phasediagrams}}
@@
 As mentioned in section \ref{sec:bandstuctures}, this can be attributed to the way the energy gap and velocity factor into the Majorana coherence length which scales with these parameters $\lambda_\textrm{M}=\hbar\frac{v_\textrm{F}}{\Delta_\textrm{ind}}$.
+Additionally, the reduction of the Majorana decay length allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.
 
@@
 \includegraphics[width=0.95\columnwidth]{figures/wavefunctions}
-\caption{Density of wavefunctions $|\psi|^2$ for different sizes and geometries.
-With (a) a straight system, (b) a zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) a system with vertically offset sinusoids.
-Inside the figure, we indicate the Majorana length (or coherence length) $\xi$ and the topological energy gap $E_\textrm{gap}.$
-We observe that $\xi$ for (a) is orders of magnitude longer and $E_\textrm{gap}$ orders of magnitude smaller than for (b, c, d), meaning that the details of the geometry do not matter.
-\label{fig:wavefunctions}}
+\caption{Density of wavefunctions $|\psi|^2$ for sizes and geometries.
+With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) similar to (c) but with disordered edges.
+Inside the figure, we indicate the Majorana length (or coherence length) $\lambda_\textrm{M}$ and the topological energy gap $E_\textrm{gap}$.
+We observe that $\xi$ for (a) is significantly longer and $E_\textrm{gap} = E_\textrm{1} - E_M$ orders of magnitude smaller than for (b), (c), and (d), meaning that the details of the geometry do not matter for the improvements to occur.
+The values of the remaining parameters are $\alpha=20$ \si{\milli \eV \nm}, $g=26$, $\meff=0.02$\si{\electronmass}, $\mu=20$ \si{\milli \eV}, $\Delta=1$ \si{\milli \eV}, $B=1$\si{\tesla}, $\phi=2\pi$.\label{fig:wavefunctions}}
 \end{figure}

### 2019-02-05 paper/snakemajoranas.tex
move the topological phase diagram to later in the manuscript
improve the phase diagram text

@@
 %%██████████████████████████████████████████████████████████████████████████
-%%██ Calculating the topological phase diagram
-%%██████████████████████████████████████████████████████████████████████████
-\section{Calculating the topological phase diagram.}
-
-\comment{We calculate the topological phase diagram using the gap size.}
-We calculate the gap $E_\textrm{gap}$ by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{|E(k)|}$.
-Noting the gap closings and the fact we know the topology for the non-zigzag system, we can infer the topology of the system with zigzag modulation. % Bas: I don't understand what is written here
-
-\comment{The introduction of the zigzag breaks a chiral symmetry, bringing the system from the BDI to the D symmetry class}
-The non-zigzag system is in the symmetry class BDI \cite{pientka2017topological}.
-Using the software package Qsymm\cite{varjas2018qsymm}, we find that the symmetry class of our system to be $\mathcal{D}$ because we break the chiral symmetry $\mathcal{C}$ resulting from the mirror symmetric junction.
-
-\comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry. }
-Similar to what is described by Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond-like shape as a function of phase $\phi$ and Zeeman field $E_Z$.
-We also observe additional gap closings which are due to the BDI symmetry that is present.
-As expected for the zigzag system, the magnitude of the gap is significantly improved, while preserving the diamond-like shape in parameter space.
-Additionally, we see a cleaner topological region due to the absence of the gap closings resulting from the former mentioned chiral symmetry.
-
-\begin{figure}[!htb]
-\includegraphics[width=0.95\columnwidth]{figures/phasediagrams}
-\caption{Phase diagrams of a straight system (a), (b) and zigzag system (c), (d), where (a), (c) are $E(\mu, B)$ and (b), (d) are $E(\phi, B)$.
-Phase diagrams of a straight system (a), (b) and zigzag system (c), (d), where (a), (c) are $E(\mu, B)$ and (b), (d) are $E(\phi, B)$.
-We compute the dispersion of the translationally invariant realizations of a straight and saw-toothed zigzag system and find $\min{E(k)}$ to obtain the energy gap.
-% Additionally, use a generalized eigenvalue problem to find all phase boundaries at once.
-\label{fig:phasediagrams}}
-\end{figure}
-
-%%██████████████████████████████████████████████████████████████████████████
 %%██ Analytical estimate
@@
 %%██████████████████████████████████████████████████████████████████████████
+%%██ Calculating the topological phase diagram
+%%██████████████████████████████████████████████████████████████████████████
+\section{Calculating the topological phase diagram.}
+
+\comment{We calculate the topological phase diagram using the gap size.}
+Due to the large size of the system, we are unable to use full spectrum methods (like the Pfaffian) to compute the topological invariant of our system.
+Instead, we calculate the gap by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{|E(k)|}$.
+By both observing the gap closings and knowing the topological phase for the non-zigzag system, we can infer the topology of the system with zigzag modulation.
+In Fig.~\ref{fig:phasediagrams}, we plot the energy gap as a function of magnetic field, chemical potential, $E_\textrm{gap}(B_x, \mu)$; and the superconducting phase difference $E_\textrm{gap}(B_x, \phi)$ for both a straight system [(a) and (b)] and a zigzag system [(c) and (d)].
+
+\comment{The introduction of the zigzag breaks a chiral symmetry, bringing the system from the BDI to the D symmetry class}
+The non-zigzag system is in the symmetry class BDI \cite{pientka2017topological}.
+Using the software package Qsymm\cite{varjas2018qsymm}, we find that the symmetry class of our system to be $\mathcal{D}$ because we break the chiral symmetry $\mathcal{C}$ resulting from the mirror symmetric junction.
+
+\comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry. }
+Similar to what is described by Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond-like shape as a function of phase $\phi$ and Zeeman field $E_Z$.
+We also observe additional gap closings which are due to the BDI symmetry that is present.
+As expected for the zigzag system, the magnitude of the gap is significantly improved, while preserving the diamond-like shape in parameter space.
+Additionally, we see a cleaner topological region due to the absence of the gap closings resulting from the former mentioned chiral symmetry.
+
+\begin{figure}[!htb]
+\includegraphics[width=0.95\columnwidth]{figures/phasediagrams}
+\caption{Phase diagrams of a straight system (a), (b) and zigzag system (c), (d), where (a), (c) are $E(\mu, B)$ and (b), (d) are $E(\phi, B)$.
+Phase diagrams of a straight system (a), (b) and zigzag system (c), (d), where (a), (c) are $E(\mu, B)$ and (b), (d) are $E(\phi, B)$.
+We compute the dispersion of the translationally invariant realizations of a straight and saw-toothed zigzag system and find $\min{E(k)}$ to obtain the energy gap.
+% Additionally, use a generalized eigenvalue problem to find all phase boundaries at once.
+\label{fig:phasediagrams}}
+\end{figure}
+
+%%██████████████████████████████████████████████████████████████████████████
 %%██ Discussion and Conclusions

### 2019-02-05 paper/snakemajoranas.tex
move figures
fix data locations

@@
 \section{Physical picture}
+
+\begin{figure}[!htb]
+\includegraphics[width=0.95\columnwidth]{figures/zigzag.pdf}
+\caption{Setups. Figure of a straight and zigzag system, including trajectories.
+\label{fig:setup}}
+\end{figure}
+
 \comment{We consider a two-dimensional system with zigzag.}
@@
 \end{small}
-
-\begin{figure}[!htb]
-\includegraphics[width=0.95\columnwidth]{figures/zigzag.pdf}
-\caption{Setups. Figure of a straight and zigzag system, including trajectories.
-\label{fig:setup}}
-\end{figure}
 
@@
 
-\comment{The definition of the cutoff... }
+\comment{The definition of the cutoff...}
 
@@
 
+\begin{figure}[!htb]
+\includegraphics[width=0.95\columnwidth]{figures/wavefunctions}
+\caption{Density of wavefunctions $|\psi|^2$ for sizes and geometries.
+With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) similar to (c) but with disordered edges.
+Inside the figure, we indicate the Majorana length (or coherence length) $\lambda_\textrm{M}$ and the topological energy gap $E_\textrm{gap}$.
+We observe that $\xi$ for (a) is significantly longer and $E_\textrm{gap} = E_\textrm{1} - E_M$ orders of magnitude smaller than for (b), (c), and (d), meaning that the details of the geometry do not matter for the improvements to occur.
+The values of the remaining parameters are $\alpha=20$ \si{\milli \eV \nm}, $g=26$, $\meff=0.02$\si{\electronmass}, $\mu=20$ \si{\milli \eV}, $\Delta=1$ \si{\milli \eV}, $B=1$\si{\tesla}, $\phi=2\pi$.\label{fig:wavefunctions}}
+\end{figure}
+
 \comment{We calculate the wave functions and find the Majorana lengths by fitting an exponential.}
@@
 Altogether, the increase in the topological gap, but also the before mentioned reduction of the group velocity, result in poorly localized Majoranas and a minimal topological protection against perturbations.
-% XXX: probably put the eq for coherence length here
+% XXX: probably put the eq for coherence length here?
 
@@
 
-\begin{figure}[!htb]
-\includegraphics[width=0.95\columnwidth]{figures/wavefunctions}
-\caption{Density of wavefunctions $|\psi|^2$ for sizes and geometries.
-With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) similar to (c) but with disordered edges.
-Inside the figure, we indicate the Majorana length (or coherence length) $\lambda_\textrm{M}$ and the topological energy gap $E_\textrm{gap}$.
-We observe that $\xi$ for (a) is significantly longer and $E_\textrm{gap} = E_\textrm{1} - E_M$ orders of magnitude smaller than for (b), (c), and (d), meaning that the details of the geometry do not matter for the improvements to occur.
-The values of the remaining parameters are $\alpha=20$ \si{\milli \eV \nm}, $g=26$, $\meff=0.02$\si{\electronmass}, $\mu=20$ \si{\milli \eV}, $\Delta=1$ \si{\milli \eV}, $B=1$\si{\tesla}, $\phi=2\pi$.\label{fig:wavefunctions}}
-\end{figure}
-
 %%██████████████████████████████████████████████████████████████████████████
@@
 \section{Calculating the topological phase diagram.}
-
-\comment{We calculate the topological phase diagram using the gap size.}
-Due to the large size of the system, we are unable to use full spectrum methods (like the Pfaffian) to compute the topological invariant of our system.
-Instead, we calculate the gap by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{|E(k)|}$.
-By both observing the gap closings and knowing the topological phase for the non-zigzag system, we can infer the topology of the system with zigzag modulation.
-In Fig.~\ref{fig:phasediagrams}, we plot the energy gap as a function of magnetic field, chemical potential, $E_\textrm{gap}(B_x, \mu)$; and the superconducting phase difference $E_\textrm{gap}(B_x, \phi)$ for both a straight system [(a) and (b)] and a zigzag system [(c) and (d)].
-
-\comment{The introduction of the zigzag breaks a chiral symmetry, bringing the system from the BDI to the D symmetry class}
-The non-zigzag system is in the symmetry class BDI \cite{pientka2017topological}.
-Using the software package Qsymm\cite{varjas2018qsymm}, we find that the symmetry class of our system to be $\mathcal{D}$ because we break the chiral symmetry $\mathcal{C}$ resulting from the mirror symmetric junction.
-
-\comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry. }
-Similar to what is described by Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond-like shape as a function of phase $\phi$ and Zeeman field $E_Z$.
-We also observe additional gap closings which are due to the BDI symmetry that is present.
-As expected for the zigzag system, the magnitude of the gap is significantly improved, while preserving the diamond-like shape in parameter space.
-Additionally, we see a cleaner topological region due to the absence of the gap closings resulting from the former mentioned chiral symmetry.
 
@@
 \end{figure}
+
+\comment{We calculate the topological phase diagram using the gap size.}
+Due to the large size of the system, we are unable to use full spectrum methods (like the Pfaffian) to compute the topological invariant of our system.
+Instead, we calculate the energy gap by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{|E(k)|}$.
+By both observing the gap closings and knowing the topological phase for the non-zigzag system, we can infer the topology of the system with zigzag modulation.
+In Fig.~\ref{fig:phasediagrams}, we plot the energy gap as a function of magnetic field, chemical potential, $E_\textrm{gap}(B_x, \mu)$; and the superconducting phase difference $E_\textrm{gap}(B_x, \phi)$ for both a straight system [(a) and (b)] and a zigzag system [(c) and (d)].
+
+\comment{The introduction of the zigzag breaks a chiral symmetry, bringing the system from the BDI to the D symmetry class}
+The non-zigzag system is in the symmetry class BDI \cite{pientka2017topological}.
+Using the software package Qsymm\cite{varjas2018qsymm}, we find that the symmetry class of our system to be $\mathcal{D}$ because we break the chiral symmetry $\mathcal{C}$ resulting from the mirror symmetric junction.
+
+\comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry.}
+Similar to what is described by Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond-like shape as a function of phase $\phi$ and Zeeman field $E_Z$.
+We also observe additional gap closings which are due to the BDI symmetry that is present.
+As expected for the zigzag system, the magnitude of the gap is significantly improved, while preserving the diamond-like shape in parameter space.
+Additionally, we see a cleaner and more stable topological region due to the absence of the gap closings resulting from the former mentioned chiral symmetry.
 

### 2019-02-05 thesis_report/introduction.tex
More adjusting

@@
 	The proposed alteration of the geometry has the potential to eliminate the problem of a soft gap, whilst staying compatible with current fabrication methods.
-	Additionally, the reduction of the Majorana decay length allows for shorter systems to produce a higher magnitude of seperation, which is favorable because the coherence length of a material sets a limit for the device size.
+	Additionally, the reduction of the Majorana decay length allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.
 

### 2019-02-05 thesis_report/results.tex
More adjusting

@@
 			Inside the figure, we indicate the Majorana length (or coherence length) $\lambda_\textrm{M}$ and the topological energy gap $E_\textrm{gap}$.
-			We observe that $\xi$ for (a) is orders of magnitude longer and $E_\textrm{gap} = E_\textrm{1} - E_M$ orders of magnitude smaller than for (b), (c), and (d), meaning that the details of the geometry do not matter for the improvements to occur.
+			We observe that $\xi$ for (a) is significantly longer and $E_\textrm{gap} = E_\textrm{1} - E_M$ orders of magnitude smaller than for (b), (c), and (d), meaning that the details of the geometry do not matter for the improvements to occur.
 			The value of the remaining parameters are $\alpha=20$ \si{\milli \eV \nm}, $g=26$, $\meff=0.02$\si{\electronmass}, $\mu=20$ \si{\milli \eV}, $\Delta=1$ \si{\milli \eV}, $B=1$\si{\tesla}, $\phi=2\pi$.
@@
 
+			Figures \ref{fig:phasediagrams}(a, c) showing $E(\mu, B)$ for both a straight and zigzag system, do not differ much apart from magnitude.
+			The weak dependence of the spectrum on chemical potential is clearly visible for both geometries, and is a feature of the SNS system.
+			The square-root dependence of the Thouless energy on the chemical potential is vaguely visible.
+
 	\section{Finding the mechanism responsible for the increased gap}
@@
 			Note that the quasi-classics are only valid once the zigzag cuts off all trajectories which extend infinitely.
-			It is also important to notice that for the quasiclassical estimate, we set the longest trajectory to be the trajectory that does not include the corners, as depicted in Figure~\ref{fig:quasiclassical_approximation}.
+			It is also important to notice that for the quasiclassical estimate, we set the longest trajectory to be the trajectory that does not include the corners, as depicted in Figure~\ref{fig:longest_trajectory_wo_corners}.
+			This is done because the wavefunction tends to avoid the corners of the zigzag.
+			A possible explanation is that the corners are part of two diagonal elements, which may, under influence of their respective spin-orbit and magnetic field direction, form an energetically unfavorable region for the wavefunction.
 
@@
 			\caption{Diagram depicting quasiclassical estimate of a zigzag system, but now with the longest trajectory chosen to avoid the corners of the zigzag.}
-			\label{fig:quasiclassical_approximation}
+			\label{fig:longest_trajectory_wo_corners}
 			\end{figure}
@@
 			A possible reason that the quasiclassical model sketches a darker picture than full zigzag, is because in that model, long trajectories also correspond to grazing angles of incidence at the NS interface.
-
-			We conclude that the proposed model to estimate the gap does not capture all the physics of the zigzag very well: the model merely gives a lower bound for the topological gap.
+			We conclude that the proposed model to estimate the gap does not capture all the physics of the zigzag very well: further research is required for a more acurate model.

### 2019-02-05 thesis_report/title.tex
More adjusting

@@
     Project duration: & \multicolumn{2}{l}{March 1, 2018 -- November 28, 2018} \\
+    Thesis supervisors: & dr.\ A.\ Akhmerov, & TU Delft \\
+                        & MSc. B.\ Nijholt, & TU Delft \\
     Thesis committee: & dr.\ A.\ Akhmerov, & TU Delft \\

### 2019-02-05 thesis_report/conclusion.tex
edited intro and concl

--- 2019-02-05 thesis_report/conclusion.tex
@@
 % -*- root: ./report.tex -*-
-\chapter{Conclusion}
-In the model we study, the introduction of a zigzag geometry increases the topological gap by several orders of magnitude while simultaneously reducing the Majorana length.
-Additionally, the breaking of a chiral symmetry brings the system from the BDI symmetry class into the D symmetry class, resulting in a cleaner topological phase.  % Bas: how is the symmetry broken?
-Together, these improvements directly affect the robustness of the Majorana state, potentially bringing us closer to reliably create topological devices.
+\chapter{Conclusion}\label{chap:conclusion}
+In the SNS system studied, the introduction of a zigzag geometry increases the topological gap by an order of magnitude, while simultaneously reducing the Majorana decay length.
+Furthermore, the geometric alteration breaks an additional symmetry, bringing the system from the BDI symmetry class into the D symmetry class, resulting in a cleaner topological phase.
+
+Together, these improvements directly affect the robustness of the Majorana state, potentially bringing us closer to be able to reliably create topological devices.
+For instance, the improved topological gap allows for an increased tolerance in device manufacturing, as well as providing a clean background for a hopefully present zero-bias peak.
+Also, the protection of the system against thermal fluctuations has an exponential dependence on the gap size, and is thus increased by many orders of magnitude.
+Furthermore, the reduced Majorana decay length manifests itself in stronger topological protection, and decreases the minimum required coherence length of the semiconductor.
 
 \comment{With the current quasiclassical analogy, we are not able to explain the improvements of zigzag.}
-The current used quasiclassical analogy, applied in the most lenient form, is not able to fully explain the increased gap of a zigzag system.
+The current used quasiclassical analogy, even when applied in a very lenient form, is not able to fully explain the increased gap of a zigzag system.
+A possible reason for the discrepancy is the fact that the quasiclassical model is not able to capture the availability of a wide range of slopes to scatter against: in a straight system, long trajectories coincide with grazing angles.
 Furthermore, numerical simulation points out that the optimal geometry does not always coincide with the minimal trajectory length.
-It is therefore unsure whether the improvement of the gap can be fully attributed to the elimination of long trajectories, or if the arising phenomena are due to other mechanisms.
+This is possibly explained by tunneling of the wavefunction through the superconductor, but as is the case with the grazing angles, further investigation is necessary.
+
 In any case, the improvements are stable under a wide range of parameters, and the topological gap varies gradually as a function of geometry, indicating the effect is not merely coincidental.
-Further study should be devoted to isolating the working principle behind the improvements of the zigzag geometry.
+Although we cannot exclude the possibility that some other process is responsible for the gap improvement, we still expect the driving mechanism to be the suppression of long trajectories.
+We are currently investigating other strategies to confirm this notion.
 
 \comment{Extensions: we omit several physical effects, disorder, electrostatics, etc.}
-In the model used, we omit several physical effects, such as disorder, electrostatics, the orbital effect, etc.  % Bas: what is etc.? Leave it out or write out the other effects
-Apart from experimental verification, further study is required to see whether the conclusions of this model are valid.  % Bas: waar komt de onzekerheid vandaan? Waarom is er meer verificatie nodig?
+In the model used, we omit several physical effects, such as disorder, electrostatics, and the orbital effect.
+Although the same restrictions hold for the straight geometry, it would be interesting to see whether inclusion of these physical effects amends the conclusions of this thesis.
 
@@
 Current fabrication techniques seem compatible with the proposed geometry, and experimental verification should point out whether it holds up to its promise.
-We note that slight modifications to the geometry, for example, to ease measurement, should not have large implications on the physics.
+We note that slight modifications to the geometry, for example, to ease measurement, should not have large implications on the results.
 Currently, experimental groups have already fabricated zigzag devices (e.g. the image on the cover of this thesis), and measurements are underway.
@@
 We have studied sawtooth, snake-like, and offset sinusoidal modulation of the semiconductor region, but perhaps a more exotic shape will be optimal. 
-% Bas: note that research in shape optimization is in progress (Andre)
-A study optimizing the geometry for supporting Majoranas would be an interesting continuation.
+Additionally, although not reported in this thesis, similar results are found for zigzag modulation of classic nanowire systems, where the semiconductor is interfaced with only a single superconductor.
+A study optimizing the geometry for supporting Majoranas would be an interesting continuation, and is currently being undertaken within the group.

### 2019-02-05 thesis_report/introduction.tex
edited intro and concl

@@
 \section{Thesis structure}
-	In this thesis we show that the introduction of a zigzag-shaped modulation of the junction region leads to an order of magnitude increase of the topological gap, as well as a significant reduction of the Majorana decay length.
+	In this thesis we show that the introduction of a zigzag-shaped modulation of the junction leads to an order of magnitude increase of the topological gap, as well as a significant reduction of the Majorana decay length.
 	The proposed alteration of the geometry has the potential to eliminate the problem of a soft gap, whilst staying compatible with current fabrication methods.
-	Additionally, the reduction of the Majorana decay length allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.
+	Additionally, the reduction of the Majorana decay length allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets the limit for the device size.
 
 	Furthermore, we try to establish the working mechanism behind the improvements: we hypothesize that the gap improvement is the result of the elimination of long trajectories.
-	In order to verify this claim, we propose a simplified model of the zigzag system such that we can isolate the dependence of the gap on the length of available trajectories.
+	In order to verify this claim, we propose a simplified model of the zigzag system such that we can isolate the dependence of the gap on the length of the trajectories.
 
 	In Chapter \ref{chap:theory}, we give an overview of established theory relevant to the understanding of this thesis.
-	Subsequently, in Chapter \ref{chap:methods} we discuss the various methods used for the analysis of zigzag systems, of which the results are discussed in chapter \ref{chap:results}.
+	Subsequently, in Chapter \ref{chap:methods} we discuss the various methods used for the analysis of zigzag systems, of which the results are discussed in Chapter \ref{chap:results}.
 	Finally, in Chapter \ref{chap:conclusion} we discuss the findings of this thesis, as well as provide an outlook on further research to be performed.

### 2019-02-05 thesis_report/introduction.tex
only cover and preface

@@
 	By making a computer that is based on quantum states itself, and creating a mapping between those states and the system you want to simulate, this scaling becomes polynomial.
-	Beyond their significance in physics simulations, quantum computers could be used in a more pragmatic way, for implementing cryptography, optimization and search algorithms.
+	Beyond their significance in physics simulations, quantum computers could be used in a more pragmatic way, for implementing cryptography~\cite{nielsen_quantum_2002}, optimization~\cite{han_quantum-inspired_2002} and search algorithms~\cite{grover_fast_1996}.
 	With the potential applications in mind, a lot of resources and effort have been put into building such a quantum computer in the last years.
@@
 	The main problem with most of the quantum computing platforms is that it is very difficult to keep the qubit from decohering.
-	To counteract this, apart from trying to reduce the decoherence rate of the qubit, much effort is put into devising quantum error correction codes: devise strategies such that potential errors can be detected and corrected for.
+	To counteract this, apart from trying to reduce the decoherence rate of the qubit, much effort is put into devising quantum error correction codes~\cite{terhal_quantum_2015}: devise strategies such that potential errors can be detected and corrected for.
 	For topological quantum computers, employing Majorana bound states as qubits, information is encoded in such a way that it is inherently protected against decoherence.
@@
 
-	The inherent protection against decoherence, in part due to the absence of properties such as spin or charge, also makes it notoriously difficult to detect and prove their existence.
+	The inherent protection against decoherence, in part due to the absence of properties such as spin or charge, also makes it notoriously difficult to detect and prove their existence~\cite{beenakker_search_2013}.
 	Perhaps the most direct way to detect their presence is through the observation of a so-called zero bias peak.
@@
 	\comment{The challenges encountered}
-	One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap, where the gap in the density of states is greatly reduced for states with the momentum directed along the length of the strip.
+	One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap~\cite{ren_topological_2018}, where the gap in the density of states is greatly reduced for states with the momentum directed along the length of the strip.
 	From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.

### 2019-02-05 thesis_report/theory.tex
only cover and preface

@@
         \end{equation}
-        In a system of size $W$ with Rashba spin-orbit coupling, and $l_\text{so} < W$, the Rashba term in the Hamiltonian can be eliminated by a gauge transformation, to first order accuracy.
+        In a system of size $W$ with Rashba spin-orbit coupling, and $l_\text{so} < W$, the effect of the Rashba term in the Hamiltonian is negligible~\cite{sticlet_robustness_2017}.
 \section{Superconducting region}
@@
         Superconductivity manifests itself as the complete absence of electrical resistance in a material.
-        It results from the pairing of electrons close to the Fermi-energy, condensing into so-called Cooper pairs.
+        It results from the pairing of electrons close to the Fermi-energy, condensing into so-called Cooper pairs~\cite{nazarov2013advanced}.
         The main parameter defining superconductivity is known as the superconducting order parameter, a complex number.

### 2019-02-05 thesis_report/title.tex
only cover and preface

--- 2019-02-05 thesis_report/title.tex
@@
     Student number: & 4247078 \\
-    Project duration: & \multicolumn{2}{l}{March 1, 2018 -- November 28, 2018} \\
+    Project duration: & \multicolumn{2}{l}{March 1, 2018 -- February 12, 2019} \\
+    \\
+    Thesis supervisors: & dr.\ A.\ Akhmerov, & TU Delft \\
+                        & MSc. B.\ Nijholt, & TU Delft \\
+    \\
     Thesis committee: & dr.\ A.\ Akhmerov, & TU Delft \\
@@
 
-The cover is a SEM image of a zigzag SNS junction fabricated and photographed by Fokko de Vries and Qingzhen Wang.
+\textbf{The cover is a SEM image of a zigzag SNS junction fabricated and photographed by Fokko de Vries and Qingzhen Wang.}
 \bigskip

### 2019-02-05 thesis_report/preface.tex
final report

@@
 
-Preface\ldots
+When I started my thesis, I had been out of the quantum physics world for a year and a half, and, to be honest, did not remember much.
+This meant that I had many basic questions for which I was quite embarrassed that I had the need to ask.
+I was very fortunate to have Bas as a supervisor, who always answered my questions -- however basic -- without making me feel stupid.
+It is quite a rare quality in our little bubble: where we all want to show how smart we are.
+Apart from that personal note, I am also greatly appreciative to the in-depth support and feedback Bas has provided me: I received a great deal of support in programming, writing, and giving comments on my thesis.
+I am also very grateful for setting up the meeting with Anna Keselman, the co-author of the main paper relevant to my thesis, which was very helpful for my understanding.
+
+I would also like to thank Anton and Michael for all the help and discussions, even when I wanted to discuss ideas so vague that the term handwaving sounds too specific.
+It was during one of these discussions that I got the suggestion that long trajectories cause a soft gap, which ultimately led to the idea of the zigzag geometry.
+I am also very grateful for the opportunities I received to meet and present for researchers in our field outside of the group.
+
+In no particular order, I would like to thank:
+Piotr and Sybren for the interesting discussions we had, as well as a fun office atmosphere,
+Joe for the many times you helped me with coding, Pablo for answering many questions and KPM, Daniel for helping me with QSymm, Tómas for helping me go through the hell known as scattering matrices, and Srijit, Fokko and Qing for the interesting discussions we had, and kick-ass SEM photographs.
+
+I am also eternally grateful for the creation of Kwant: my favorite quantum physics sandbox.
+Using Kwant, I was able to go from idea to implementation to simulation within a matter of hours.
+It is truly amazing, and I know for sure that I would have never tried weirdly shaped junctions without it.
+
+I would also like to thank my girlfriend Irina, for proofreading my thesis, and the detailed comments I received.
+I am also very grateful for all the support she gave me, especially in the beginning, when it was quite frustrating, and at the end, when I was stressed.
+
+Finally, I would like to thank my family, who have been extremely supportive of me.
+I am especially grateful for them providing a home where I can always come to rest.
 
@@
     \@author \\
-    Delft, January 2013
+    Delft, February 2019
 \makeatother}

### 2019-02-06 paper/snakemajoranas.tex
add some words
fix LaTeX syntax

@@
 
-Unless noted differently, the parameters of the system are $\alpha=20$ \si{\milli \eV \nm}, $g=26$, $\meff=0.02$\si{\electronmass}, $\mu=20$ \si{\milli \eV}, $\Delta=1$ \si{\milli \eV}.
+Unless noted differently, the parameters of the system are $\alpha=\SI{20}{\milli \eV \nm}$, $g=26$, $\meff=\SI{0.02}{\electronmass}$, $\mu=\SI{20}{\milli \eV}$, $\Delta=\SI{1}{\milli \eV}$.
 
@@
 \caption{Figure of the bandstuctures corresponding to the system in Fig.~\ref{fig:zigzag_methods}.
-Blue lines correspond to $\phi=0$, $B=0$ and red lines to $\phi=\pi$, $B = \SI{1}{\T}$.
-The three subplots are for different amplitudes of the zigzag, with (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W=200$\si{\nm} is the junction width.
-We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
-\label{fig:bandstuctures}}
+Blue lines correspond to $\phi=0$, $B=0$ and red lines to $\phi=\pi$, $B = \SI{1}{T}$.
+The three subplots are for different amplitudes of the zigzag, with (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W=\SI{200}{\nm}$ is the junction width.
+We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.\label{fig:bandstuctures}}
 \end{figure}
@@
 \includegraphics[width=0.95\columnwidth]{figures/wavefunctions}
-\caption{Density of wavefunctions $|\psi|^2$ for sizes and geometries.
+\caption{Density of wavefunctions $\left|\psi\right|^2$ for sizes and geometries.
 With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) similar to (c) but with disordered edges.

### 2019-02-06 paper/snakemajoranas.tex
undefined refs in the paper

@@
 
-Unless noted differently, the parameters of the system are $\alpha=\SI{20}{\milli \eV \nm}$, $g=26$, $\meff=\SI{0.02}{\electronmass}$, $\mu=\SI{20}{\milli \eV}$, $\Delta=\SI{1}{\milli \eV}$.
+Unless noted differently, the parameters of the system are $\alpha=\SI{20}{\meV \nm}$, $g=26$, $\meff=\SI{0.02}{\electronmass}$, $\mu=\SI{20}{\meV}$, $\Delta=\SI{1}{\meV}$.
 
@@
 \includegraphics[width=0.95\columnwidth]{figures/bandstructures}
-\caption{Figure of the bandstuctures corresponding to the system in Fig.~\ref{fig:zigzag_methods}.
+\caption{Figure of the bandstuctures corresponding to the system in Fig.~\ref{fig:setup}.
 Blue lines correspond to $\phi=0$, $B=0$ and red lines to $\phi=\pi$, $B = \SI{1}{T}$.
@@
 We observe that $\xi$ for (a) is significantly longer and $E_\textrm{gap} = E_\textrm{1} - E_M$ orders of magnitude smaller than for (b), (c), and (d), meaning that the details of the geometry do not matter for the improvements to occur.
-The values of the remaining parameters are $\alpha=20$ \si{\milli \eV \nm}, $g=26$, $\meff=0.02$\si{\electronmass}, $\mu=20$ \si{\milli \eV}, $\Delta=1$ \si{\milli \eV}, $B=1$\si{\tesla}, $\phi=2\pi$.\label{fig:wavefunctions}}
+The values of the remaining parameters are $\alpha=\SI{20}{\meV \nm}$, $g=26$, $\meff=\SI{0.02}{\electronmass}$, $\mu=\SI{20}{\meV}$ , $\Delta=\SI{1}{\meV}$ , $B=\SI{1}{\tesla}$, $\phi=2\pi$.\label{fig:wavefunctions}}
 \end{figure}
@@
 \comment{In a straight system, the Majoranas are very poorly localized.}
-For the ribbon system [Fig.~\ref{fig:wavefunction}(a)], we see that the decay of the density is long compared to the system size.
+For the ribbon system [Fig.~\ref{fig:wavefunctions}(a)], we see that the decay of the density is long compared to the system size.
 The wavefunction extends to the center of the system, resulting in overlapping Majoranas and a non-zero energy of the state.

### 2019-02-06 paper/snakemajoranas.tex
reword

@@
 \comment{Majoranas are mostly made in hybrid NS structures.}
-The current experimental effort is focuses on creating pairs of MBSs in hybrid normal-superconductor (NS) structures, where a long strip (or wire) of a semiconductor is interfaced with a \cite{lutchyn_majorana_2010,oreg_helical_2010} superconductor.
+The current experimental effort focuses on creating pairs of MBSs in hybrid normal-superconductor (NS) structures, where a long strip (or wire) of a semiconductor is interfaced with a \cite{lutchyn_majorana_2010,oreg_helical_2010} superconductor.
 Within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple wire), the semiconductor becomes topological while MBSs appear at the ends of the segment.
 Recently, a system with a slight modification has been proposed\cite{pientka2017topological}, where instead of having one superconductor, there are two superconductors, creating a superconductors-normal-superconductor (SNS) junction.
-This adds an extra knob to adjust, the superconducting phase difference $\phi$, and this should make it easier to tune the system into the topological phase.
+The additional superconductor adds an extra knob to adjust, the superconducting phase difference $\phi$, and this should make it easier to tune the system into the topological phase.
 In practice, multiple problems arise making even the observation, let alone the manipulation of Majoranas difficult.
@@
 \comment{The gap is small because of long trajectories.}
-One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap; where the gap in the density of states is greatly reduced for states with the momentum directed along the length of the strip.
+One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap; where the gap in the density of states significantly reduces for states with the momentum directed along the length of the strip.
 From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
@@
 For the zigzag geometry, we first consider a sawtooth-like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
-Later in this manuscript, we show that the exact details of the shape are not important and consider different zigzag geometries also parametrized by $z_x, \; z_y, \; W$.
+Later in this manuscript, we show that the exact details of the shape are not of importance and consider different zigzag geometries also parametrized by $z_x, \; z_y, \; W$.
 
@@
 \comment{We calculate the wave functions and find the Majorana lengths by fitting an exponential.}
-We model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve, and variants of the former with disordered egdes.
-By diagonalizing the Hamiltonian we find the Majorana energy $E_\textrm{M}$ and the energy of the first excited state $E_1$, the lowest and second lowest energies, respectively.
-Using the eigenstates, we calculate the Majorana decay length $\lambda_\textrm{M}$ by fitting an exponential to the desity of the Majorana wavefunction projected on the $x$-axis.
+We model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve, and variants of the former with disordered edges.
+By diagonalizing the Hamiltonian, we find the Majorana energy $E_\textrm{M}$ and the energy of the first excited state $E_1$, the lowest and second lowest energies, respectively.
+Using the eigenstates, we calculate the Majorana decay length $\lambda_\textrm{M}$ by fitting an exponential to the density of the Majorana wavefunction projected on the $x$-axis.
 In figure~\ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.
-All systems have identical Hamiltonian parameters in order to meaningfully compare the effects of the changing geometry.
+All systems have identical Hamiltonian parameters in order to compare the effects of the changing geometry meaningfully.
 
@@
 Further, the energy of the Majorana state $E_\textrm{M}$ in the straight system is badly septated from the next lowest lying eigenstate $E_1$.
-Altogether, the increase in the topological gap, but also the before mentioned reduction of the group velocity, result in poorly localized Majoranas and a minimal topological protection against perturbations.
+Altogether, the increase in the topological gap, but also the before mentioned reduction of the group velocity, result in poorly localized Majoranas and minimal topological protection against perturbations.
 % XXX: probably put the eq for coherence length here?
@@
 \comment{In a zigzag geometry Majoranas are localized within one segment of zigzag.}
-We observe that for zigzag systems the Majorana properties properties improve.
+We observe that for zigzag systems the Majorana properties improve.
 All of the zigzag type geometries display a reduced coherence length and the delocalized nature of the wavefunctions is improved, as is visible through the density plots.
@@
 The shape of the wavefunctions does not change significantly depending on the details of the geometry.
-The sharp corners of the sawtooth versus the smooth shape of the snakelike system do not have a significant impact on the shape of the wavefunction and neither do the disordered edges effect the relevant parameters.
+The sharp corners of the sawtooth versus the smooth shape of the snakelike system do not have a significant impact on the shape of the wavefunction, and neither do the disordered edges affect the relevant parameters.
 
@@
 The non-zigzag system is in the symmetry class BDI \cite{pientka2017topological}.
-Using the software package Qsymm\cite{varjas2018qsymm}, we find that the symmetry class of our system to be $\mathcal{D}$ because we break the chiral symmetry $\mathcal{C}$ resulting from the mirror symmetric junction.
+Using the software package Qsymm\cite{varjas2018qsymm}, we find that the symmetry class of our system to be $\mathcal{D}$ because we break the chiral symmetry $\mathcal{C}$ resulting from the mirror-symmetric junction.
 
@@
 \comment{Current fabrication techniques seem compatible with the proposed geometry, and experimental verification should point out whether it holds up to its promise.}
-Current fabrication techniques seem compatible with the proposed geometry; zigzag devices have already been created.
-Slight modifications to the geometry, for example to ease measurement, should not have significant implications on the physics.
+Current fabrication techniques are compatible with the proposed geometry; zigzag devices have already been fabricated.
+Slight modifications to the geometry, for example, to ease measurement, should not have significant implications on the physics.
 
@@
 We have studied sawtooth, snake-like, and offset sinusoidal modulation of the semiconductor region, but perhaps a more exotic shape will be optimal.
-A study optimizing the geometry for supporting Majoranas would be an interesting continuation.
+A study optimizing the geometry for supporting Majoranas would be an exciting continuation.
 

### 2019-02-06 paper/snakemajoranas.tex
edit conclusions

@@
 As expected for the zigzag system, the magnitude of the gap is significantly improved, while preserving the diamond-like shape in parameter space.
-Additionally, we see a cleaner and more stable topological region due to the absence of the gap closings resulting from the former mentioned chiral symmetry.
+Additionally, we see a cleaner and more stable topological region due to the absence of the gap closings resulting from the aforementioned chiral symmetry.
 
@@
 
-\comment{The zigzag geometry is a useful tool in hardening the gap and decreasing Majorana length, now experimental verification necessary}
-The introduction of a zigzag geometry increases the topological gap by over an order of magnitude, as well as offering a substantial reduction of the Majorana length.
-Additionally, the breaking of BDI symmetry into D symmetry results in a cleaner topological region.
+\comment{The zigzag geometry is a useful tool in hardening the gap and decreasing Majorana length.}
+The introduction of a zigzag geometry increases the topological gap by over an order of magnitude, as well as offering a substantial reduction of the Majorana length, which enables experimentalists to create significantly shorter devices.
+Additionally, the breaking of BDI symmetry into D symmetry results in a cleaner and more stable topological region.
 
-\comment{Current fabrication techniques seem compatible with the proposed geometry, and experimental verification should point out whether it holds up to its promise.}
-Current fabrication techniques are compatible with the proposed geometry; zigzag devices have already been fabricated.
+\comment{Current fabrication techniques are compatible with the proposed geometry, and experimental verification can be near.}
+Current fabrication techniques are compatible with the proposed geometry; zigzag devices have already been fabricated. % XXX: add ref to Fokko's thesis
 Slight modifications to the geometry, for example, to ease measurement, should not have significant implications on the physics.
@@
 \comment{It is interesting to study what geometry creates an optimal environment for Majorana modes to exist.}
-We have studied sawtooth, snake-like, and offset sinusoidal modulation of the semiconductor region, but perhaps a more exotic shape will be optimal.
-A study optimizing the geometry for supporting Majoranas would be an exciting continuation.
+We have studied sawtooth and snake-like geometries of the semiconductor region, but perhaps a more exotic shape will be optimal.
+A study optimizing the geometry's parameters for supporting Majoranas is an exciting continuation of our research.
 
 \comment{Extensions: we omit several physical effects, disorder, electrostatics, etc.}
-We exclude several physical effects, such as disorder, electrostatics, the orbital effect, etc..
-Further study, as well as experimental verification, are required to see whether the conclusions of this model are valid for the real case.
+Finally, we exclude several physical effects, such as disorder, electrostatics, the orbital effect, the finite thickness of the sample, and electron-electron interactions, however, we expect these to be second or higher order effects which will not alter our conclusions.
 

### 2019-02-06 paper/snakemajoranas.tex
make Acknowledgments a section
write down parameters with the figures

@@
 For the zigzag geometry, we first consider a sawtooth-like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
-Later in this manuscript, we show that the exact details of the shape are not of importance and consider different zigzag geometries also parametrized by $z_x, \; z_y, \; W$.
+Later in this manuscript, we show that the exact details of the shape are unimportant and consider different zigzag geometries also parametrized by $z_x, \; z_y, \; W$.
 
@@
 
-Unless noted differently, the parameters of the system are $\alpha=\SI{20}{\meV \nm}$, $g=26$, $\meff=\SI{0.02}{\electronmass}$, $\mu=\SI{20}{\meV}$, $\Delta=\SI{1}{\meV}$.
+Unless noted differently, the Hamiltonian parameters are $\alpha=\SI{20}{\meV \nm}$, $g=26$, $\meff=\SI{0.02}{\electronmass}$, $\mu=\SI{10}{\meV}$, $B=\SI{1}{T}$, $\phi=\pi$, and $\Delta=\SI{1}{\meV}$; and the geometry parameters are $W=\SI{200}{\nm}$, the period of the zigzag $z_x=\SI{1300}{\nm}$, the discretization contant $a=\SI{10}{\nm}$, and the lengths of the superconductors $L_\textrm{SC}=\SI{200}{\nm}$.
 
@@
 The three subplots are for different amplitudes of the zigzag, with (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W=\SI{200}{\nm}$ is the junction width.
-We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.\label{fig:bandstuctures}}
+We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
+The parameters values are as noted below Eq.~\eqref{eq:hamiltonian}.\label{fig:bandstuctures}}
 \end{figure}
@@
 We observe that $\xi$ for (a) is significantly longer and $E_\textrm{gap} = E_\textrm{1} - E_M$ orders of magnitude smaller than for (b), (c), and (d), meaning that the details of the geometry do not matter for the improvements to occur.
-The values of the remaining parameters are $\alpha=\SI{20}{\meV \nm}$, $g=26$, $\meff=\SI{0.02}{\electronmass}$, $\mu=\SI{20}{\meV}$ , $\Delta=\SI{1}{\meV}$ , $B=\SI{1}{\tesla}$, $\phi=2\pi$.\label{fig:wavefunctions}}
+The parameters values are as noted below Eq.~\eqref{eq:hamiltonian}.\label{fig:wavefunctions}}
 \end{figure}
@@
 \comment{We calculate the wave functions and find the Majorana lengths by fitting an exponential.}
-We model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve, and variants of the former with disordered edges.
+We model a finite system to compute the Majorana wave function density for different geometries; ribbon, saw-toothed zigzag, parallel curves, and variants of the latter with disordered edges.
 By diagonalizing the Hamiltonian, we find the Majorana energy $E_\textrm{M}$ and the energy of the first excited state $E_1$, the lowest and second lowest energies, respectively.
@@
 % Additionally, use a generalized eigenvalue problem to find all phase boundaries at once.
+The parameters values are as noted below Eq.~\eqref{eq:hamiltonian}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
+The chemical potential is $\mu=\SI{10}{\meV}$ in (b) and (d) and the superconducting phase is $\phi=\pi$ in (a) and (c).
 \label{fig:phasediagrams}}
@@
 
-\comment{Acknowledgments}
-
+%%██████████████████████████████████████████████████████████████████████████
+%%██ Acknowledgments
+%%██████████████████████████████████████████████████████████████████████████
+\section{Acknowledgments}
 We are grateful to "people" for useful discussions.

### 2019-02-07 paper/snakemajoranas.tex
use TODO tags
improve the abstract

@@
 \begin{abstract}
-We are solving a problem of soft gap in high density SNS Majorana junctions \cite{pientka2017topological}.
-We do this by introducing a zigzag geometry.
-This works because the maximum trajectory length is cut-off due to the geometry and therefore the minimal energy gap is given by a simple formula, which we also verify using numerics.
-In addition to having a large minimum energy gap, the absence of long length trajectories means that the localization length is very short as well.
+We solve the problem of soft gap in high density SNS Majorana junctions \cite{pientka2017topological}.
+Trajectories that do not encounter the superconductor for a long time weaken proximity effect in Josephson junctions.
+A small induced gap becomes then an important obstacle in creating Majorana states.
+We show that a zigzag-shaped geometry eliminates these trajectories, at the same time allowing robust creation of Majorana states with a gap increased by more than an order of magnitude.
 \end{abstract}
@@
 Altogether, the increase in the topological gap, but also the before mentioned reduction of the group velocity, result in poorly localized Majoranas and minimal topological protection against perturbations.
-% XXX: probably put the eq for coherence length here?
+% TODO: probably put the eq for coherence length here?
 
@@
 \comment{Current fabrication techniques are compatible with the proposed geometry, and experimental verification can be near.}
-Current fabrication techniques are compatible with the proposed geometry; zigzag devices have already been fabricated. % XXX: add ref to Fokko's thesis
+Current fabrication techniques are compatible with the proposed geometry; zigzag devices have already been fabricated. % TODO: add ref to Fokko's thesis
 Slight modifications to the geometry, for example, to ease measurement, should not have significant implications on the physics.

### 2019-02-07 paper/snakemajoranas.tex
write down magnetic field in pliot

@@
 Similar to the conventional straight system \cite{pientka2017topological}, a magnetic field $B_x$ perpendicular to the junction is applied.
-We model the system with a BdG Hamiltonian Eq.~\eqref{eq:hamiltonian}; the normal part has a linear Rashba spin-orbit coupling term characterized by $\alpha$ and a Zeeman field with $E_z=\frac{1}{2}mu_B g B_x$.
+We model the system with a BdG Hamiltonian Eq.~\eqref{eq:hamiltonian}; the normal part has a linear Rashba spin-orbit coupling term characterized by $\alpha$ and a Zeeman field with $E_z=\frac{1}{2} \mu_B g B_x$.
 The superconductor has a superconducting coupling term $\Delta$ with a superconducting phase $\exp{\pm i \phi/2}$.

### 2019-02-07 paper/snakemajoranas.tex
align Hamiltonian eq
comment out the analytics and improve the abstract

@@
 \begin{abstract}
-We solve the problem of soft gap in high density SNS Majorana junctions \cite{pientka2017topological}.
-Trajectories that do not encounter the superconductor for a long time weaken proximity effect in Josephson junctions.
-A small induced gap becomes then an important obstacle in creating Majorana states.
-We show that a zigzag-shaped geometry eliminates these trajectories, at the same time allowing robust creation of Majorana states with a gap increased by more than an order of magnitude.
+We solve the problem of the appearance of a soft gap in high-density SNS Majorana junctions \cite{pientka2017topological}.
+Trajectories that do not encounter the superconductor for a long time weaken the proximity effect in Josephson junctions.
+A small induced gap then becomes an essential obstacle in creating Majorana states.
+We show that a zigzag-shaped geometry eliminates these trajectories, at the same time allowing the robust creation of Majorana states with a gap increased by more than an order of magnitude.
 \end{abstract}
@@
 
-\begin{small}
-\begin{align}
-    H = \left(\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right)\tau_z+
-        E_\text{z} \sigma_x+
-        \alpha \left( \ky \sigma_x - \kx \sigma_y \right) \tau_z +
-        \Delta \tau_y
-\end{align}
+\begin{equation}
+\begin{split}
+    H = & \left(\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right)\tau_z \\
+        & + E_\text{z} \sigma_x
+          + \alpha \left( \ky \sigma_x - \kx \sigma_y \right) \tau_z
+          + \Delta \tau_y
+\end{split}
 \label{eq:hamiltonian}
-\end{small}
+\end{equation}
 
@@
 %%██████████████████████████████████████████████████████████████████████████
-\section{Analytical estimate of the band gap}
+% \section{Analytical estimate of the band gap}
 
-\comment{To compute the effect of cutoff consider a single segment of the zigzag and obtain the spectrum analytically (this allows to use translation invariance).}
-We establish that the cutoff of long trajectories is the driving mechanism behind the order of magnitude gap improvement using an analytical approach.
-We derive the Andreev spectrum for a single (diagonal) segment of the zigzag, and define the gap of the system as the minimum of the spectrum occurring before the cutoff corresponding to the particular geometry.
-The system under consideration is thus a ribbon SNS junction with a tilted magnetic field.
+% \comment{To compute the effect of cutoff consider a single segment of the zigzag and obtain the spectrum analytically (this allows to use translation invariance).}
+% We establish that the cutoff of long trajectories is the driving mechanism behind the order of magnitude gap improvement using an analytical approach.
+% We derive the Andreev spectrum for a single (diagonal) segment of the zigzag, and define the gap of the system as the minimum of the spectrum occurring before the cutoff corresponding to the particular geometry.
+% The system under consideration is thus a ribbon SNS junction with a tilted magnetic field.
 
-\comment{The definition of the cutoff...}
+% \comment{The definition of the cutoff...}
 
-\comment{We use a short junction approximation and neglect transverse SO.}
-We derive the spectrum by calculating the scattering matrix for the normal region and applying the Andreev bound state condition for the short junction limit\cite{beenakker1991universal, sticlet_robustness_2017}.
-For derivation of the scattering matrix, we neglect SOI in the transverse direction, which is valid for $W<l_\text{so}$.
-The result is specified in Eqs.~\eqref{eq:smatrix} to~\eqref{eq:momenta_short_junction}.
+% \comment{We use a short junction approximation and neglect transverse SO.}
+% We derive the spectrum by calculating the scattering matrix for the normal region and applying the Andreev bound state condition for the short junction limit\cite{beenakker1991universal, sticlet_robustness_2017}.
+% For derivation of the scattering matrix, we neglect SOI in the transverse direction, which is valid for $W<l_\text{so}$.
+% The result is specified in Eqs.~\eqref{eq:smatrix} to~\eqref{eq:momenta_short_junction}.
 
-\begin{align}
-\label{eq:smatrix}
-    S &= \left(
-    \begin{array}{rr}
-    r_{ll}&t_{rl}\\
-    t_{lr}&r_{rr}\\
-    \end{array}
-    \right) =
-    \left(
-    \begin{array}{rr}
-    \beta_+ & e^{-i q W} \beta_-\\
-    e^{-i q W} \beta_- & e^{-2 i q W} \beta_+\\
-    \end{array}
-    \right)
-    \\
-    \beta_\pm &= \left(
-    \begin{array}{rr}
-    e^{i \nu_{\arg}}\left(\omega^\pm_1 - \omega^\pm_2\right) & (\omega^\pm _1 + \omega^\pm _2)\\
-    -(\omega^\pm _1 + \omega^\pm _2) & e^{-i \nu _{\arg }} \left(\omega^\pm _2 - \omega^\pm _1\right)\\
-    \end{array}
-    \right)\\
-    \omega^\pm_j &= \frac{1}{4} \left(\gamma _{j} \pm \delta _{j}\right)
-\end{align}
+% \begin{align}
+% \label{eq:smatrix}
+%     S &= \left(
+%     \begin{array}{rr}
+%     r_{ll}&t_{rl}\\
+%     t_{lr}&r_{rr}\\
+%     \end{array}
+%     \right) =
+%     \left(
+%     \begin{array}{rr}
+%     \beta_+ & e^{-i q W} \beta_-\\
+%     e^{-i q W} \beta_- & e^{-2 i q W} \beta_+\\
+%     \end{array}
+%     \right)
+%     \\
+%     \beta_\pm &= \left(
+%     \begin{array}{rr}
+%     e^{i \nu_{\arg}}\left(\omega^\pm_1 - \omega^\pm_2\right) & (\omega^\pm _1 + \omega^\pm _2)\\
+%     -(\omega^\pm _1 + \omega^\pm _2) & e^{-i \nu _{\arg }} \left(\omega^\pm _2 - \omega^\pm _1\right)\\
+%     \end{array}
+%     \right)\\
+%     \omega^\pm_j &= \frac{1}{4} \left(\gamma _{j} \pm \delta _{j}\right)
+% \end{align}
 
-\begin{align}
-    \gamma_j &= \frac{q+i k_{j} \tan \left(\frac{W k_{j}}{2}\right)}{q-i k_{j} \tan \left(\frac{W k_{j}}{2}\right)} \\
-    \delta_j &= \frac{q-i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}{q+i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}\\
-    e^{i \nu_{\arg}} &= \frac{E_\text{z} e^{i \theta }-i \alpha  k_x}{\sqrt{E_\text{z}^2+\alpha  k_x \left(\alpha  k_x-2 E_\text{z} \sin (\theta )\right)}}
-\end{align}
+% \begin{align}
+%     \gamma_j &= \frac{q+i k_{j} \tan \left(\frac{W k_{j}}{2}\right)}{q-i k_{j} \tan \left(\frac{W k_{j}}{2}\right)} \\
+%     \delta_j &= \frac{q-i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}{q+i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}\\
+%     e^{i \nu_{\arg}} &= \frac{E_\text{z} e^{i \theta }-i \alpha  k_x}{\sqrt{E_\text{z}^2+\alpha  k_x \left(\alpha  k_x-2 E_\text{z} \sin (\theta )\right)}}
+% \end{align}
 
-\begin{footnotesize}
-\begin{align}
-    q &= \left[ \frac{2 m_\ast}{\hbar ^2}\mu_s - k_x^2 \right]^\frac{1}{2}\\
-    k_1 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n-\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}\\
-    k_2 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n+\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}
-\label{eq:momenta_short_junction}
-\end{align}
-\end{footnotesize}
+% \begin{footnotesize}
+% \begin{align}
+%     q &= \left[ \frac{2 m_\ast}{\hbar ^2}\mu_s - k_x^2 \right]^\frac{1}{2}\\
+%     k_1 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n-\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}\\
+%     k_2 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n+\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}
+% \label{eq:momenta_short_junction}
+% \end{align}
+% \end{footnotesize}
 
-In order to get the spectrum from the S-matrix [Eq.~\eqref{eq:smatrix}] we use the main result from Ref.~\onlinecite{beenakker1991universal} and start with a determinantal equation for the bound state energies in a SNS-junction:
+% In order to get the spectrum from the S-matrix [Eq.~\eqref{eq:smatrix}] we use the main result from Ref.~\onlinecite{beenakker1991universal} and start with a determinantal equation for the bound state energies in a SNS-junction:
 
-\begin{equation}
-\det\left[1+\alpha^{2}\left(E\right)r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)\right]=0
-\end{equation}
+% \begin{equation}
+% \det\left[1+\alpha^{2}\left(E\right)r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)\right]=0
+% \end{equation}
 
-We rewrite this as a characteristic polynomial problem $\det\left[A-\lambda I\right]=0$, as
+% We rewrite this as a characteristic polynomial problem $\det\left[A-\lambda I\right]=0$, as
 
-\begin{equation}
-\det\left[r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)-\frac{-1}{\alpha^{2}\left(E\right)}I\right]=0
-\end{equation}
+% \begin{equation}
+% \det\left[r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)-\frac{-1}{\alpha^{2}\left(E\right)}I\right]=0
+% \end{equation}
 
-with
-\begin{equation}
-\lambda=-\frac{1}{\alpha^{2}\left(E\right)},\;A=r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right).
-\end{equation}
+% with
+% \begin{equation}
+% \lambda=-\frac{1}{\alpha^{2}\left(E\right)},\;A=r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right).
+% \end{equation}
 
-Where $\lambda_i$ are the eigenvalues of $A$.
-Inverting $\alpha\left(E\right)\equiv\exp\left(-i\arccos\left(E/\Delta\right)\right)$ yields $\frac{E}{\Delta}=\frac{\alpha^{2}+1}{2\alpha}=\frac{1}{2}\left(\alpha+\alpha^{-1}\right)=\textrm{Re}(\alpha)$, where the last equality holds because $\alpha$ is unitary.
-Then, since $\alpha$ is only defined in the positive imaginary plane, the energies are $\frac{E_{i}}{\Delta}=\textrm{Re}\left(\sqrt{-1/\lambda_{i}}\right)$ where we take the root which has a positive imaginary part.
-Using this result and Eq.~\eqref{eq:smatrix}, we numerically find the Andreev spectrum.
+% Where $\lambda_i$ are the eigenvalues of $A$.
+% Inverting $\alpha\left(E\right)\equiv\exp\left(-i\arccos\left(E/\Delta\right)\right)$ yields $\frac{E}{\Delta}=\frac{\alpha^{2}+1}{2\alpha}=\frac{1}{2}\left(\alpha+\alpha^{-1}\right)=\textrm{Re}(\alpha)$, where the last equality holds because $\alpha$ is unitary.
+% Then, since $\alpha$ is only defined in the positive imaginary plane, the energies are $\frac{E_{i}}{\Delta}=\textrm{Re}\left(\sqrt{-1/\lambda_{i}}\right)$ where we take the root which has a positive imaginary part.
+% Using this result and Eq.~\eqref{eq:smatrix}, we numerically find the Andreev spectrum.
 
-\comment{The lowest energy at $|k| < k_\textrm{cutoff}$ sets the band gap.}
-We cut off the spectrum at the momentum corresponding to the proposed cutoff in the zigzag, and compare it to the numerically obtained gap for a true zigzag system.
+% \comment{The lowest energy at $|k| < k_\textrm{cutoff}$ sets the band gap.}
+% We cut off the spectrum at the momentum corresponding to the proposed cutoff in the zigzag, and compare it to the numerically obtained gap for a true zigzag system.
 

### 2019-02-07 paper/snakemajoranas.tex
write about disorder vs geometry

@@
 
+\comment{Disorder has a similar effect but one has no control over it.}
+Recently, it has been shown~\cite{haim_double-edge_2018} that having a system with weak disorder can lead to a reduction in the Majorana decay length, similar to what happens with the introduction of a zigzag geometry.
+However, in contrast to introducing weak disorder into a system, changing the geomerty is experimentally much easier to realize and therefore easier to control.
+
 \comment{Current fabrication techniques are compatible with the proposed geometry, and experimental verification can be near.}

### 2019-02-07 paper/snakemajoranas.tex
add citations and remark the experimental realization of the Majo SNS

@@
 \section{Introduction}
-Majorana bound states (MBSs) are a promising candidate to form the basis of a stable platform for topological quantum computing.
+Majorana bound states (MBSs) are a promising candidate to form the basis of a stable platform for topological quantum computing. ~\cite{alicea2012new,beenakker2013search}
 
 \comment{Majoranas are mostly made in hybrid NS structures.}
-The current experimental effort focuses on creating pairs of MBSs in hybrid normal-superconductor (NS) structures, where a long strip (or wire) of a semiconductor is interfaced with a \cite{lutchyn_majorana_2010,oreg_helical_2010} superconductor.
+The current experimental effort ~\cite{mourik_signatures_2012,das_zero-bias_2012,deng_anomalous_2012,churchill_superconductor-nanowire_2013,zhang2018quantized} focuses on creating pairs of MBSs in hybrid normal-superconductor (NS) structures, where a long strip (or wire) of a semiconductor is interfaced with a superconductor.~\cite{lutchyn_majorana_2010,oreg_helical_2010}
 Within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple wire), the semiconductor becomes topological while MBSs appear at the ends of the segment.
@@
 The additional superconductor adds an extra knob to adjust, the superconducting phase difference $\phi$, and this should make it easier to tune the system into the topological phase.
-In practice, multiple problems arise making even the observation, let alone the manipulation of Majoranas difficult.
+Recently, two groups have realized this system experimentally.~\cite{fornieri_evidence_2018,ren_topological_2018}
+In practice, multiple problems arise making even the observation difficult, leaving the manipulation of Majoranas problematic.
 
@@
 Similar to the conventional straight system \cite{pientka2017topological}, a magnetic field $B_x$ perpendicular to the junction is applied.
-We model the system with a BdG Hamiltonian Eq.~\eqref{eq:hamiltonian}; the normal part has a linear Rashba spin-orbit coupling term characterized by $\alpha$ and a Zeeman field with $E_z=\frac{1}{2} \mu_B g B_x$.
-The superconductor has a superconducting coupling term $\Delta$ with a superconducting phase $\exp{\pm i \phi/2}$.
-Both parts have a kinetic term and chemical potential $\mu$.
-For the zigzag geometry, we first consider a sawtooth-like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
-Later in this manuscript, we show that the exact details of the shape are unimportant and consider different zigzag geometries also parametrized by $z_x, \; z_y, \; W$.
-
+We model the system with a Bogoliubov-de Gennes Hamiltonian (BdG) Eq.~\eqref{eq:hamiltonian}; the normal part has a linear Rashba spin-orbit coupling term characterized by $\alpha$ and a Zeeman field with $E_z=\frac{1}{2} \mu_B g B_x$.
+The superconductor has a superconducting coupling term $\Delta$ with the pair of superconductors at an opposite superconducting phase $\exp{\pm i \phi/2}$.
+Both the normal part and the superconducters have a kinetic term and chemical potential $\mu$.
+The complete Hamiltonian has the form
 \begin{equation}
@@
           + \alpha \left( \ky \sigma_x - \kx \sigma_y \right) \tau_z
-          + \Delta \tau_y
+          + \Delta \tau_y.
 \end{split}
@@
 \end{equation}
-
+It acts on the spinor wave function $\Psi={\left(\psi_{e\uparrow},\psi_{e\downarrow},\psi_{\textrm{h}\downarrow},-\psi_{\textrm{h}\uparrow}\right)}^{T}$, where $\psi_e$, $\psi_\textrm{h}$ are its electron and hole components, and $\psi_\uparrow$, $\psi_\downarrow$ are the spin-up and spin-down components.
+The Pauli matrices $\sigma_{i}$ act on the spin degree of freedom and $\tau_{i}$ act on the electron-hole degree of freedom.
+For the zigzag geometry, we first consider a sawtooth-like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
+Later in this manuscript, we show that the exact details of the shape are unimportant and consider different zigzag geometries also parametrized by $z_x, \; z_y, \; W$.
 Unless noted differently, the Hamiltonian parameters are $\alpha=\SI{20}{\meV \nm}$, $g=26$, $\meff=\SI{0.02}{\electronmass}$, $\mu=\SI{10}{\meV}$, $B=\SI{1}{T}$, $\phi=\pi$, and $\Delta=\SI{1}{\meV}$; and the geometry parameters are $W=\SI{200}{\nm}$, the period of the zigzag $z_x=\SI{1300}{\nm}$, the discretization contant $a=\SI{10}{\nm}$, and the lengths of the superconductors $L_\textrm{SC}=\SI{200}{\nm}$.
@@
 \comment{We discretize the Hamiltonian and simulate it with Kwant.}
-We discretize our continuum Hamiltonian \eqref{eq:hamiltonian} on a square grid and implement a tight-binding model using Kwant~\cite{groth_kwant:_2014}.
+We discretize our continuum Hamiltonian [Eq.~\eqref{eq:hamiltonian}] on a square grid and implement a tight-binding model using Kwant~\cite{groth_kwant:_2014}.
 The resulting Hamiltonians are large because instead of having a single slice of sites that is translationally invariant in the $x$-direction, we create a long supercell to make the structure periodic.

### 2019-02-07 paper/snakemajoranas.tex
ref to the parameters

@@
 %%██████████████████████████████████████████████████████████████████████████
-\section{Physical picture}
+\section{Physical picture}\label{sec:physical_picture}
 
@@
 We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
-The parameters values are as noted below Eq.~\eqref{eq:hamiltonian}.\label{fig:bandstuctures}}
+The parameters values are written on the bottom of Sec.~\eqref{sec:physical_picture}.\label{fig:bandstuctures}}
 \end{figure}
@@
 We observe that $\xi$ for (a) is significantly longer and $E_\textrm{gap} = E_\textrm{1} - E_M$ orders of magnitude smaller than for (b), (c), and (d), meaning that the details of the geometry do not matter for the improvements to occur.
-The parameters values are as noted below Eq.~\eqref{eq:hamiltonian}.\label{fig:wavefunctions}}
+The parameters values are written on the bottom of Sec.~\eqref{sec:physical_picture}.\label{fig:wavefunctions}}
 \end{figure}
@@
 % Additionally, use a generalized eigenvalue problem to find all phase boundaries at once.
-The parameters values are as noted below Eq.~\eqref{eq:hamiltonian}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
+The parameters values are written on the bottom of Sec.~\eqref{sec:physical_picture}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
 The chemical potential is $\mu=\SI{10}{\meV}$ in (b) and (d) and the superconducting phase is $\phi=\pi$ in (a) and (c).

### 2019-02-07 paper/snakemajoranas.tex
make variables x,y dependent

@@
 The additional superconductor adds an extra knob to adjust, the superconducting phase difference $\phi$, and this should make it easier to tune the system into the topological phase.
-Recently, two groups have realized this system experimentally.~\cite{fornieri_evidence_2018,ren_topological_2018}
-In practice, multiple problems arise making even the observation difficult, leaving the manipulation of Majoranas problematic.
+Recently, two groups~\cite{fornieri_evidence_2018,ren_topological_2018} have realized this system experimentally.
+In practice, multiple problems arise making even the observation difficult, rendering the manipulation of Majoranas in the near future, unprobable.
 
@@
 One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap; where the gap in the density of states significantly reduces for states with the momentum directed along the length of the strip.
+% TODO: do we cite here?
 From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
@@
 \begin{split}
-    H = & \left(\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right)\tau_z \\
-        & + E_\text{z} \sigma_x
-          + \alpha \left( \ky \sigma_x - \kx \sigma_y \right) \tau_z
-          + \Delta \tau_y.
+    H = & \left[\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right] \tau_z \\
+        & + E_\text{z}(x,y) \sigma_x \\
+        & + \alpha(x,y) \left( \ky \sigma_x - \kx \sigma_y \right) \tau_z
+          + \Delta(x,y) \tau_y.
 \end{split}
@@
 Later in this manuscript, we show that the exact details of the shape are unimportant and consider different zigzag geometries also parametrized by $z_x, \; z_y, \; W$.
+
 Unless noted differently, the Hamiltonian parameters are $\alpha=\SI{20}{\meV \nm}$, $g=26$, $\meff=\SI{0.02}{\electronmass}$, $\mu=\SI{10}{\meV}$, $B=\SI{1}{T}$, $\phi=\pi$, and $\Delta=\SI{1}{\meV}$; and the geometry parameters are $W=\SI{200}{\nm}$, the period of the zigzag $z_x=\SI{1300}{\nm}$, the discretization contant $a=\SI{10}{\nm}$, and the lengths of the superconductors $L_\textrm{SC}=\SI{200}{\nm}$.
@@
 We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
-The parameters values are written on the bottom of Sec.~\eqref{sec:physical_picture}.\label{fig:bandstuctures}}
+The parameters values are written on the bottom of Sec.~\ref{sec:physical_picture}.\label{fig:bandstuctures}}
 \end{figure}
@@
 We observe that $\xi$ for (a) is significantly longer and $E_\textrm{gap} = E_\textrm{1} - E_M$ orders of magnitude smaller than for (b), (c), and (d), meaning that the details of the geometry do not matter for the improvements to occur.
-The parameters values are written on the bottom of Sec.~\eqref{sec:physical_picture}.\label{fig:wavefunctions}}
+The parameters values are written on the bottom of Sec.~\ref{sec:physical_picture}.\label{fig:wavefunctions}}
 \end{figure}
@@
 % Additionally, use a generalized eigenvalue problem to find all phase boundaries at once.
-The parameters values are written on the bottom of Sec.~\eqref{sec:physical_picture}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
+The parameters values are written on the bottom of Sec.~\ref{sec:physical_picture}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
 The chemical potential is $\mu=\SI{10}{\meV}$ in (b) and (d) and the superconducting phase is $\phi=\pi$ in (a) and (c).

### 2019-02-07 paper/snakemajoranas.tex
add data refs

@@
 To speed up these expensive simulations we employ an adaptive sampling strategy, using the Python package Adaptive. % TODO: add a citation
+The entire source code is available in the Supplemental Material~\cite{supp}.  % TODO: update the bib when the data is uploaded
+The resulting raw data are available in Ref.~\onlinecite{data}.  % TODO: update the bib when the data is uploaded
 
@@
 The non-zigzag system is in the symmetry class BDI \cite{pientka2017topological}.
-Using the software package Qsymm\cite{varjas2018qsymm}, we find that the symmetry class of our system to be $\mathcal{D}$ because we break the chiral symmetry $\mathcal{C}$ resulting from the mirror-symmetric junction.
+Using the software package Qsymm\cite{varjas2018qsymm}, we find that the symmetry class of our system to be D because we break the chiral symmetry $\mathcal{C}$ resulting from the mirror-symmetric junction.
 

### 2019-02-07 paper/snakemajoranas.tex
cite Adaptive

@@
 The resulting Hamiltonians are large because instead of having a single slice of sites that is translationally invariant in the $x$-direction, we create a long supercell to make the structure periodic.
-To speed up these expensive simulations we employ an adaptive sampling strategy, using the Python package Adaptive. % TODO: add a citation
+To speed up these expensive simulations we employ an adaptive sampling strategy, using the Python package Adaptive.~\cite{adaptive}
 The entire source code is available in the Supplemental Material~\cite{supp}.  % TODO: update the bib when the data is uploaded

### 2019-02-07 paper/snakemajoranas.tex
fix typo
add lenght of system in the wf plot

@@
 Recently, two groups~\cite{fornieri_evidence_2018,ren_topological_2018} have realized this system experimentally.
-In practice, multiple problems arise making even the observation difficult, rendering the manipulation of Majoranas in the near future, unprobable.
+In practice, multiple problems arise making even the observation difficult, rendering the manipulation of Majoranas in the near future, improbable.
 
@@
 We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
-The parameters values are written on the bottom of Sec.~\ref{sec:physical_picture}.\label{fig:bandstuctures}}
+The parameters values are written at the bottom of Sec.~\ref{sec:physical_picture}.\label{fig:bandstuctures}}
 \end{figure}
@@
 We observe that $\xi$ for (a) is significantly longer and $E_\textrm{gap} = E_\textrm{1} - E_M$ orders of magnitude smaller than for (b), (c), and (d), meaning that the details of the geometry do not matter for the improvements to occur.
-The parameters values are written on the bottom of Sec.~\ref{sec:physical_picture}.\label{fig:wavefunctions}}
+The length of the system is $3L_x=\SI{3900}{\nm}$, the remaining parameters values are written at the bottom of Sec.~\ref{sec:physical_picture}.\label{fig:wavefunctions}}
 \end{figure}
@@
 % Additionally, use a generalized eigenvalue problem to find all phase boundaries at once.
-The parameters values are written on the bottom of Sec.~\ref{sec:physical_picture}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
+The parameters values are written at the bottom of Sec.~\ref{sec:physical_picture}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
 The chemical potential is $\mu=\SI{10}{\meV}$ in (b) and (d) and the superconducting phase is $\phi=\pi$ in (a) and (c).

### 2019-02-07 paper/snakemajoranas.tex
corrections with Tom

@@
 \usepackage{babel}
-\hypersetup{pdfauthor={Quantum Tinkerer},pdftitle={Increasing the topological gap by an order of magnitude through the geomerty for Majorana SNS junctions.}}
+\hypersetup{pdfauthor={Quantum Tinkerer},pdftitle={Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.}}
 
@@
 
-\title{Increasing the topological gap by an order of magnitude through the geometry for Majorana SNS junctions.}
+\title{Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.}
 
@@
 A small induced gap then becomes an essential obstacle in creating Majorana states.
-We show that a zigzag-shaped geometry eliminates these trajectories, at the same time allowing the robust creation of Majorana states with a gap increased by more than an order of magnitude.
+We show that a zigzag-shaped geometry eliminates these trajectories, at the same time allowing the robust creation of Majorana states with a gap increased by more than an order of magnitude and a significantly reduced Majorana decay length.
 \end{abstract}
@@
 Within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple wire), the semiconductor becomes topological while MBSs appear at the ends of the segment.
+
+\comment{A alternative has been proposed (JJ).}
 Recently, a system with a slight modification has been proposed\cite{pientka2017topological}, where instead of having one superconductor, there are two superconductors, creating a superconductors-normal-superconductor (SNS) junction.
@@
 \comment{The gap is small because of long trajectories.}
-One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap; where the gap in the density of states significantly reduces for states with the momentum directed along the length of the strip.
-% TODO: do we cite here?
+One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap~\cite{ren_topological_2018}; where the gap in the density of states significantly reduces for states with the momentum directed along the length of the strip.
 From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
@@
 \comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
-Currently, proposed workarounds are to work at low density \cite{nijholt2015orbital} or to have disorder~\cite{haim_double-edge_2018}, but both have drawbacks.
+Currently, proposed workarounds are to work at low density \cite{nijholt2015orbital} or to have disorder~\cite{haim_double-edge_2018}, but both have drawbacks.  % TODO: mention drawbacks?
 
@@
 For the zigzag geometry, we first consider a sawtooth-like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
+The spatial dependence of $\Delta$, $E_z$, and $\alpha$ is explained in text above.
 Later in this manuscript, we show that the exact details of the shape are unimportant and consider different zigzag geometries also parametrized by $z_x, \; z_y, \; W$.
@@
 Unless noted differently, the Hamiltonian parameters are $\alpha=\SI{20}{\meV \nm}$, $g=26$, $\meff=\SI{0.02}{\electronmass}$, $\mu=\SI{10}{\meV}$, $B=\SI{1}{T}$, $\phi=\pi$, and $\Delta=\SI{1}{\meV}$; and the geometry parameters are $W=\SI{200}{\nm}$, the period of the zigzag $z_x=\SI{1300}{\nm}$, the discretization contant $a=\SI{10}{\nm}$, and the lengths of the superconductors $L_\textrm{SC}=\SI{200}{\nm}$.
+% TODO: Tom: L_sc and Delta not compatible?
 
@@
 We discretize our continuum Hamiltonian [Eq.~\eqref{eq:hamiltonian}] on a square grid and implement a tight-binding model using Kwant~\cite{groth_kwant:_2014}.
-The resulting Hamiltonians are large because instead of having a single slice of sites that is translationally invariant in the $x$-direction, we create a long supercell to make the structure periodic.
+The resulting Hamiltonians are large because instead of having a single slice of sites that is translationally invariant in the $x$-direction, we create a long 2D supercell to make the structure periodic.
 To speed up these expensive simulations we employ an adaptive sampling strategy, using the Python package Adaptive.~\cite{adaptive}
@@
 The wavefunction extends to the center of the system, resulting in overlapping Majoranas and a non-zero energy of the state.
-Further, the energy of the Majorana state $E_\textrm{M}$ in the straight system is badly septated from the next lowest lying eigenstate $E_1$.
+Further, the energy of the Majorana state $E_\textrm{M}$ in the straight system is badly separated from the next lowest lying eigenstate $E_1$.
 Altogether, the increase in the topological gap, but also the before mentioned reduction of the group velocity, result in poorly localized Majoranas and minimal topological protection against perturbations.

### 2019-02-08 paper/snakemajoranas.tex
rewrite the abstract and section I

@@
 \begin{abstract}
-We solve the problem of the appearance of a soft gap in high-density SNS Majorana junctions \cite{pientka2017topological}.
-Trajectories that do not encounter the superconductor for a long time weaken the proximity effect in Josephson junctions.
-A small induced gap then becomes an essential obstacle in creating Majorana states.
+Quasi-particle trajectories in high density SNS junctions that have a large momentum parallel to the junction have a very long flight time.
+These trajectories that do not encounter the superconductor for a long time weaken the proximity effect in Josephson junctions.
+This results in a very small induced gap and a soft gap in Majorana devices.
+We propose to eliminate these long trajectories using a new Majorana device.
 We show that a zigzag-shaped geometry eliminates these trajectories, at the same time allowing the robust creation of Majorana states with a gap increased by more than an order of magnitude and a significantly reduced Majorana decay length.
+Further, we show that to exploit the benefits of this system, the details exact of the geometry are not important.
 \end{abstract}
@@
 \section{Introduction}
-Majorana bound states (MBSs) are a promising candidate to form the basis of a stable platform for topological quantum computing. ~\cite{alicea2012new,beenakker2013search}
-
-\comment{Majoranas are mostly made in hybrid NS structures.}
-The current experimental effort ~\cite{mourik_signatures_2012,das_zero-bias_2012,deng_anomalous_2012,churchill_superconductor-nanowire_2013,zhang2018quantized} focuses on creating pairs of MBSs in hybrid normal-superconductor (NS) structures, where a long strip (or wire) of a semiconductor is interfaced with a superconductor.~\cite{lutchyn_majorana_2010,oreg_helical_2010}
-Within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple wire), the semiconductor becomes topological while MBSs appear at the ends of the segment.
-
-\comment{A alternative has been proposed (JJ).}
-Recently, a system with a slight modification has been proposed\cite{pientka2017topological}, where instead of having one superconductor, there are two superconductors, creating a superconductors-normal-superconductor (SNS) junction.
-The additional superconductor adds an extra knob to adjust, the superconducting phase difference $\phi$, and this should make it easier to tune the system into the topological phase.
-Recently, two groups~\cite{fornieri_evidence_2018,ren_topological_2018} have realized this system experimentally.
-In practice, multiple problems arise making even the observation difficult, rendering the manipulation of Majoranas in the near future, improbable.
+\comment{Hybrid NS structures become topological and are useful for TQC.}
+A hybrid structure containing a semiconductor with strong spin-orbit coupling coupled to a superconductor, inside a magnetic field becomes topological within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple nanowire), while Majorana bound states appear on its edges.~\cite{lutchyn_majorana_2010,oreg_helical_2010}
+Majorana bound states are a promising candidate to form the basis of a stable platform for topological quantum computing. ~\cite{alicea2012new,beenakker2013search}
+The current experimental effort ~\cite{mourik_signatures_2012,das_zero-bias_2012,deng_anomalous_2012,churchill_superconductor-nanowire_2013,zhang2018quantized} focuses on creating pairs of Majorana bound states in hybrid normal-superconductor (NS) nanowires structures.
 
@@
 From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
-Additionally, these long trajectories have long flight times $\tau_f$ and equivalenly small Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$, resulting in a small gap.
-
-\comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
-Currently, proposed workarounds are to work at low density \cite{nijholt2015orbital} or to have disorder~\cite{haim_double-edge_2018}, but both have drawbacks.  % TODO: mention drawbacks?
-
-\comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
-In this paper, we show that introducing a zigzag or snake-like geometry for the semiconductor eliminates these long trajectories and prevents the appearance of a soft gap while also increasing the topological gap by an order of magnitude.
-
-%%██████████████████████████████████████████████████████████████████████████
-%%██ Physical picture
-%%██████████████████████████████████████████████████████████████████████████
-\section{Physical picture}\label{sec:physical_picture}
+Additionally, these long trajectories have long flight times $\tau_f=v_F(\theta) / D$ (see Fig.~\ref{fig:setup}(a)) and equivalenly small Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$, resulting in a small gap.
+% TODO: fix the Eq for tau_f
+This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, so a low filling of the bands is a workaround\cite{nijholt2015orbital}.
+However, low filling requires precise knowledge of the system and might be more sensitive to disorder or microscopic inhomogeneities.
+On the other hand, disorder scatters these long trajectories and introduces a cut-off on the scale of the mean-free path~\cite{haim_double-edge_2018}, however, disorder is impossible to control to a required precision experimentally.
 
@@
 
+\comment{A alternative has been proposed.}
+Recently, a system with a modification has been proposed\cite{pientka2017topological}, where instead of having one superconductor, there are two superconductors, creating a superconductors-normal-superconductor (SNS) junction.
+The additional superconductor adds an extra knob to adjust, the superconducting phase difference $\phi$, and this should make it easier to tune the system into the topological phase.
+Recently, two groups~\cite{fornieri_evidence_2018,ren_topological_2018} have realized this system experimentally.
+In practice, multiple problems arise making even the observation difficult, rendering the manipulation of Majoranas in the near future, improbable.
+
+\comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
+We propose a new experimental setup (see Fig.~\ref{fig:setup}(b)) for the creation of Majoranas that eliminating long trajectories and therefore prevents the appearance of a soft gap, while while also increasing the topological gap by several orders of magnitude, depending on the parameters.
+The setup consists of a zigzag or snake-like geometry for the semiconductor where long trajectories are not possible due to the geometry.
+
+%%██████████████████████████████████████████████████████████████████████████
+%%██ Physical picture
+%%██████████████████████████████████████████████████████████████████████████
+\section{Physical picture}\label{sec:physical_picture}
+
 \comment{We consider a two-dimensional system with zigzag.}
-We consider a Josephson junction (JJ)(Fig.~\ref{fig:setup}) consisting of a two-dimensional strip of semiconductor, with superconductors on both sides.
+We consider a Josephson junction (Fig.~\ref{fig:setup}) consisting of a two-dimensional strip of semiconductor, with superconductors on both sides.
 We modulate the shape of the normal region, which can be either zigzag as depicted, or a more smooth sinusoidal-like shape.

### 2019-02-08 sns_system.py
add specialized algo for short systems

@@ -288,15 +288,21 @@ def make_system(L_m, L_x, L_sc_up, L_sc_down, z_x, z_y, a,
                 mu_from_bottom_of_spin_orbit_bands,
                 k_x_in_sc,
                 wraparound,
+                infinite,
                 current,
                 ns_junction,
                 sc_leads=False,
                 no_phs=False,
                 rough_edge=None):
+    if wraparound and not infinite:
+        raise ValueError('If you want to use wraparound, infinite must be True.')
+    if sc_leads and not infinite or sc_leads and not wraparound:
+        raise ValueError('If you want to use sc_leads, infinite and wraparound must be True.')
 
     ######################
     ## Define templates ##
     ######################
+
     parallel_curve = sawtooth = False
     parallel_curve = (shape == 'parallel_curve')
     sawtooth = (shape == 'sawtooth')
@@ -430,7 +436,7 @@ def make_system(L_m, L_x, L_sc_up, L_sc_down, z_x, z_y, a,
     else:
         #---------------
         # Create builder
-        if wraparound:
+        if infinite:
             syst = kwant.Builder(kwant.TranslationalSymmetry([L_x, 0]))
         else:
             syst = kwant.Builder()
@@ -482,7 +488,7 @@ def make_system(L_m, L_x, L_sc_up, L_sc_down, z_x, z_y, a,
         ## Finalize system ##
         #####################
 
-        if wraparound:
+        if infinite and wraparound:
             syst = kwant.wraparound.wraparound(syst)
             if sc_leads:
                 lead_up = kwant.Builder(kwant.TranslationalSymmetry([L_x, 0], [0, a]))

### 2019-02-08 spectrum.py

@@ -229,3 +229,137 @@ def find_phase_bounds(lead, params, k_x=0, num_bands=20, sigma=0):
     mus[abs(mus.imag) > 1e-14] = np.nan
 
     return mus.real[inds]
+
+
+def cell_mats(lead, params, bias=0):
+    h = lead.cell_hamiltonian(params=params)
+    h -= bias * np.identity(len(h))
+    t = lead.inter_cell_hopping(params=params)
+    return h, t
+
+
+def get_h_k(lead, params):
+    h, t = cell_mats(lead, params)
+    h_k = lambda k: h + t * np.exp(1j * k) + t.T.conj() * np.exp(-1j * k)
+    return h_k
+
+
+def slowest_evan_mode(lead, params):
+    """Find the slowest decaying (evanescent) mode.
+
+    It uses an adapted version of the function kwant.physics.leads.modes,
+    in such a way that it returns the eigenvalues of the translation operator
+    (lamdba = |r|*e^ik). The imaginary part of the wavevector k, is the part
+    that makes it decay. The inverse of this Im(k) is the size of a Majorana
+    bound state. The norm of the eigenvalue that is closest to one is the
+    slowest decaying mode. Also called decay length.
+
+    Parameters:
+    -----------
+    lead : kwant.builder.InfiniteSystem object
+        The finalized infinite system.
+
+    Returns:
+    --------
+    majorana_length : float
+        The length of the Majorana.
+    """
+    h, t = cell_mats(lead, params, bias=0)
+    ev = translation_ev(h, t)
+    norm = ev * ev.conj()
+    idx = np.abs(norm - 1).argmin()
+    a = lattice_constant_from_syst(lead)
+    majorana_length = np.abs(a / np.log(ev[idx]).real)
+    return majorana_length
+
+
+def phase_bounds_operator(lead, params, k_x=0):
+    params['mu'] = 0
+    h, t = cell_mats(lead, params)
+    tk = t * np.exp(1j * k_x)
+    h_k = h + tk + tk.T.conj()
+    sigma_z = np.array([[1, 0], [0, -1]])
+    _operator = np.kron(np.eye(len(h) // 2), sigma_z) @ h_k
+    return _operator
+
+
+def find_phase_bounds(lead, params, k=0, num_bands=20):
+    """Find the phase boundaries.
+    Solve an eigenproblem that finds values of chemical potential at which the
[…]

### 2019-02-08 paper/snakemajoranas.tex
small change
work through comments

@@
 We show that a zigzag-shaped geometry eliminates these trajectories, at the same time allowing the robust creation of Majorana states with a gap increased by more than an order of magnitude and a significantly reduced Majorana decay length.
-Further, we show that to exploit the benefits of this system, the details exact of the geometry are not important.
+Additionally, we show that to exploit the benefits of this system, the details exact of the geometry are not important.
 \end{abstract}
@@
 %%██████████████████████████████████████████████████████████████████████████
-\section{Physical picture}\label{sec:physical_picture}
+\section{Setup}\label{sec:physical_picture}
 
-\comment{We consider a two-dimensional system with zigzag.}
+\comment{We consider a two-dimensional system with zigzag and BdG Hamiltonian.}
 We consider a Josephson junction (Fig.~\ref{fig:setup}) consisting of a two-dimensional strip of semiconductor, with superconductors on both sides.
@@
 
+\comment{The default parameters are ...}
 Unless noted differently, the Hamiltonian parameters are $\alpha=\SI{20}{\meV \nm}$, $g=26$, $\meff=\SI{0.02}{\electronmass}$, $\mu=\SI{10}{\meV}$, $B=\SI{1}{T}$, $\phi=\pi$, and $\Delta=\SI{1}{\meV}$; and the geometry parameters are $W=\SI{200}{\nm}$, the period of the zigzag $z_x=\SI{1300}{\nm}$, the discretization contant $a=\SI{10}{\nm}$, and the lengths of the superconductors $L_\textrm{SC}=\SI{200}{\nm}$.
@@
 %%██████████████████████████████████████████████████████████████████████████
-\section{Calculating the bandstuctures.}\label{sec:bandstuctures}
+\section{Band stuctures}\label{sec:bandstuctures}
 
@@
 To speed up these expensive simulations we employ an adaptive sampling strategy, using the Python package Adaptive.~\cite{adaptive}
-The entire source code is available in the Supplemental Material~\cite{supp}.  % TODO: update the bib when the data is uploaded
-The resulting raw data are available in Ref.~\onlinecite{data}.  % TODO: update the bib when the data is uploaded
+The entire source code and the resulting raw data are available in Ref.~\onlinecite{data}.  % TODO: update the bib when the data is uploaded
 
@@
 %%██████████████████████████████████████████████████████████████████████████
-\section{Calculating the topological phase diagram.}
+\section{Topological phase diagram}
 
@@
 Phase diagrams of a straight system (a), (b) and zigzag system (c), (d), where (a), (c) are $E(\mu, B)$ and (b), (d) are $E(\phi, B)$.
-We compute the dispersion of the translationally invariant realizations of a straight and saw-toothed zigzag system and find $\min{E(k)}$ to obtain the energy gap.
+We compute the dispersion of the translationally invariant realizations of a straight and saw-toothed zigzag system and find $\min \left| {E(k)} \right|$ to obtain the energy gap.
 % Additionally, use a generalized eigenvalue problem to find all phase boundaries at once.

### 2019-02-08 paper/snakemajoranas.tex
lambda_M -> xi_M

@@
 We consider a Josephson junction (Fig.~\ref{fig:setup}) consisting of a two-dimensional strip of semiconductor, with superconductors on both sides.
-We modulate the shape of the normal region, which can be either zigzag as depicted, or a more smooth sinusoidal-like shape.
+We modulate the shape of the normal region, which can be either saw-toothed zigzag as depicted [Fig.~\ref{fig:setup}(b)], or a more smooth sinusoidal-like shape.
 Similar to the conventional straight system \cite{pientka2017topological}, a magnetic field $B_x$ perpendicular to the junction is applied.
@@
 With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) similar to (c) but with disordered edges.
-Inside the figure, we indicate the Majorana length (or coherence length) $\lambda_\textrm{M}$ and the topological energy gap $E_\textrm{gap}$.
-We observe that $\xi$ for (a) is significantly longer and $E_\textrm{gap} = E_\textrm{1} - E_M$ orders of magnitude smaller than for (b), (c), and (d), meaning that the details of the geometry do not matter for the improvements to occur.
+Inside the figure, we indicate the Majorana length (or coherence length) $\xi_\textrm{M}$ and the topological energy gap $E_\textrm{gap}$.
+We observe that $\xi_\textrm{M}$ for (a) is significantly longer and $E_\textrm{gap}$ more than an order of magnitude smaller than for (b), (c), and (d), meaning that the details of the geometry do not matter for the improvements to occur.
 The length of the system is $3L_x=\SI{3900}{\nm}$, the remaining parameters values are written at the bottom of Sec.~\ref{sec:physical_picture}.\label{fig:wavefunctions}}
@@
 By diagonalizing the Hamiltonian, we find the Majorana energy $E_\textrm{M}$ and the energy of the first excited state $E_1$, the lowest and second lowest energies, respectively.
-Using the eigenstates, we calculate the Majorana decay length $\lambda_\textrm{M}$ by fitting an exponential to the density of the Majorana wavefunction projected on the $x$-axis.
+Using the eigenstates, we calculate the Majorana decay length $\xi_\textrm{M}$ by fitting an exponential to the density of the Majorana wavefunction projected on the $x$-axis.
 In figure~\ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.
@@
 Quantitatively, the improvement in the localization of the Majoranas is also distinctly apparent: the energies of the Majorana states are three orders of magnitude lower than the energy of the second lowest-lying wavefunctions.
-As mentioned in section \ref{sec:bandstuctures}, this can be attributed to the way the energy gap and velocity factor into the Majorana coherence length which scales with these parameters $\lambda_\textrm{M}=\hbar\frac{v_\textrm{F}}{\Delta_\textrm{ind}}$.
+As mentioned in section \ref{sec:bandstuctures}, this can be attributed to the way the energy gap and velocity factor into the Majorana coherence length which scales with these parameters $\xi_\textrm{M}=\hbar\frac{v_\textrm{F}}{\Delta_\textrm{ind}}$.
 Additionally, the reduction of the Majorana decay length allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.

### 2019-02-13 paper/snakemajoranas.tex
small changes to the paper

@@
 %%██████████████████████████████████████████████████████████████████████████
-%%██ Calculating the bandstuctures
+%%██ Calculating the band stuctures
 %%██████████████████████████████████████████████████████████████████████████
-\section{Band stuctures}\label{sec:bandstuctures}
+\section{Band stuctures}\label{sec:band_stuctures}
 
@@
 \includegraphics[width=0.95\columnwidth]{figures/bandstructures}
-\caption{Figure of the bandstuctures corresponding to the system in Fig.~\ref{fig:setup}.
-Blue lines correspond to $\phi=0$, $B=0$ and red lines to $\phi=\pi$, $B = \SI{1}{T}$.
-The three subplots are for different amplitudes of the zigzag, with (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W=\SI{200}{\nm}$ is the junction width.
-We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
-The parameters values are written at the bottom of Sec.~\ref{sec:physical_picture}.\label{fig:bandstuctures}}
+\caption{Figure of the band stuctures corresponding to the system in Fig.~\ref{fig:setup} with different zigzag amplitudes.
+The blue lines correspond to $\phi=0$, $B=0$ (trivial phase) and the orange lines to $\phi=\pi$, $B = \SI{1}{T}$ (topological phase).
+The three subplots are for different amplitudes of the zigzag, with (a) a straight system $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W=\SI{200}{\nm}$ is the junction width.
+Subplot (a) has a different scale on the $x$-axis for $k_x < 0$ than the other subplots and displays the unfolded band structure.
+For the right-hand side of (a) ($k_x > 0$), (b), and (c), the folding is the same, such that the velocity $v=\frac{dE}{dk}$ can be compared visually.
+We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$, and thus the $v_\textrm{F}$ decreases.
+As the zigzag amplitude increases the band gap $E_\textrm{gap}$ increases by an order of magnitude.
+The combination of these ensures a significant decrease of the Majorana decay length because $\xi_M \propto \frac{v_\textrm{F}}{E_\textrm{gap}}$
+The parameters values are written at the bottom of Sec.~\ref{sec:physical_picture}.\label{fig:band_stuctures}}
 \end{figure}
@@
 \comment{We calculate the bandstructure for varying amount of zigzag.}
-In figure~\ref{fig:bandstuctures}, the bandstructure for zigzag systems with varying amplitude is displayed.
+In figure~\ref{fig:band_stuctures}, the bandstructure for zigzag systems with varying amplitude is displayed.
 Because the discretized zigzag system is modeled using a supercell, we can only plot a folded bandstructure.
@@
 With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) similar to (c) but with disordered edges.
-Inside the figure, we indicate the Majorana length (or coherence length) $\xi_\textrm{M}$ and the topological energy gap $E_\textrm{gap}$.
+Inside the figure, we indicate the Majorana length (or coherence length) $\xi_\textrm{M}$, the Majorana energy $E_\textrm{M}$ (the energy of the first excited state), and the topological energy gap $E_\textrm{gap}$.
 We observe that $\xi_\textrm{M}$ for (a) is significantly longer and $E_\textrm{gap}$ more than an order of magnitude smaller than for (b), (c), and (d), meaning that the details of the geometry do not matter for the improvements to occur.
@@
 Quantitatively, the improvement in the localization of the Majoranas is also distinctly apparent: the energies of the Majorana states are three orders of magnitude lower than the energy of the second lowest-lying wavefunctions.
-As mentioned in section \ref{sec:bandstuctures}, this can be attributed to the way the energy gap and velocity factor into the Majorana coherence length which scales with these parameters $\xi_\textrm{M}=\hbar\frac{v_\textrm{F}}{\Delta_\textrm{ind}}$.
+As mentioned in section \ref{sec:band_stuctures}, this can be attributed to the way the energy gap and velocity factor into the Majorana coherence length which scales with these parameters $\xi_\textrm{M}=\hbar\frac{v_\textrm{F}}{\Delta_\textrm{ind}}$.
 Additionally, the reduction of the Majorana decay length allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.

### 2019-02-13 paper/snakemajoranas.tex
write about nanowires

@@
 The setup consists of a zigzag or snake-like geometry for the semiconductor where long trajectories are not possible due to the geometry.
+In this paper we will focus on two-dimensional (2D) Josephson junctions, however, a zigzag geometry will also work for nanowires.\footnote{We confirmed this numerically, although it is not included in this paper.}
 
@@
 \comment{We consider a two-dimensional system with zigzag and BdG Hamiltonian.}
-We consider a Josephson junction (Fig.~\ref{fig:setup}) consisting of a two-dimensional strip of semiconductor, with superconductors on both sides.
+We consider a Josephson junction (Fig.~\ref{fig:setup}) consisting of a 2D strip of semiconductor, with superconductors on both sides.
 We modulate the shape of the normal region, which can be either saw-toothed zigzag as depicted [Fig.~\ref{fig:setup}(b)], or a more smooth sinusoidal-like shape.

### 2019-02-18 paper/snakemajoranas.tex
go through the comments again

@@
 %%██████████████████████████████████████████████████████████████████████████
-%%██ Physical picture
+%%██ Setup
 %%██████████████████████████████████████████████████████████████████████████
-\section{Setup}\label{sec:physical_picture}
+\section{Setup}\label{sec:setup}
 
@@
 %%██████████████████████████████████████████████████████████████████████████
-%%██ Calculating the band stuctures
+%%██ Band stuctures
 %%██████████████████████████████████████████████████████████████████████████
@@
 The combination of these ensures a significant decrease of the Majorana decay length because $\xi_M \propto \frac{v_\textrm{F}}{E_\textrm{gap}}$
-The parameters values are written at the bottom of Sec.~\ref{sec:physical_picture}.\label{fig:band_stuctures}}
+The parameters values are written at the bottom of Sec.~\ref{sec:setup}.\label{fig:band_stuctures}}
 \end{figure}
@@
 \comment{The band structures show that modulation of the geometry increases the gap by an order of magnitude, as well as reduce the group velocity.}
-The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the topological gap increases by more than an order of magnitude.
+The introduction of a zigzag has a striking effect: the bands flatten out because of a reduction in velocity and the topological gap increases by more than an order of magnitude.
 On an intuitive level we can understand this because in a straight system long trajectories are possible, these have a momentum that is directed along the strip and consequently, $k_x \approx k_F$.
@@
 We observe that $\xi_\textrm{M}$ for (a) is significantly longer and $E_\textrm{gap}$ more than an order of magnitude smaller than for (b), (c), and (d), meaning that the details of the geometry do not matter for the improvements to occur.
-The length of the system is $3L_x=\SI{3900}{\nm}$, the remaining parameters values are written at the bottom of Sec.~\ref{sec:physical_picture}.\label{fig:wavefunctions}}
+The length of the system is $3L_x=\SI{3900}{\nm}$, the remaining parameters values are written at the bottom of Sec.~\ref{sec:setup}.\label{fig:wavefunctions}}
 \end{figure}
@@
 %%██████████████████████████████████████████████████████████████████████████
-%%██ Calculating the topological phase diagram
+%%██ Topological phase diagram
 %%██████████████████████████████████████████████████████████████████████████
@@
 % Additionally, use a generalized eigenvalue problem to find all phase boundaries at once.
-The parameters values are written at the bottom of Sec.~\ref{sec:physical_picture}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
+The parameters values are written at the bottom of Sec.~\ref{sec:setup}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
 The chemical potential is $\mu=\SI{10}{\meV}$ in (b) and (d) and the superconducting phase is $\phi=\pi$ in (a) and (c).

### 2019-02-19 paper/snakemajoranas.tex
fix xi_M algo and add phase bounds

@@
 \comment{The default parameters are ...}
-Unless noted differently, the Hamiltonian parameters are $\alpha=\SI{20}{\meV \nm}$, $g=26$, $\meff=\SI{0.02}{\electronmass}$, $\mu=\SI{10}{\meV}$, $B=\SI{1}{T}$, $\phi=\pi$, and $\Delta=\SI{1}{\meV}$; and the geometry parameters are $W=\SI{200}{\nm}$, the period of the zigzag $z_x=\SI{1300}{\nm}$, the discretization contant $a=\SI{10}{\nm}$, and the lengths of the superconductors $L_\textrm{SC}=\SI{200}{\nm}$.
+Unless noted differently, the Hamiltonian parameters are $\alpha=\SI{20}{\meV \nm}$, $g=26$, $\meff=\SI{0.02}{\electronmass}$, $\mu=\SI{10}{\meV}$, $B=\SI{1}{T}$, $\phi=\pi$, and $\Delta=\SI{1}{\meV}$; and the geometry parameters are $W=\SI{200}{\nm}$, the period of the zigzag $z_x=\SI{1300}{\nm}$, the discretization contant $a=\SI{10}{\nm}$, and the lengths of the superconductors $L_\textrm{SC}=\SI{300}{\nm}$.
 % TODO: Tom: L_sc and Delta not compatible?
@@
 
-\comment{We calculate the bandstructure for varying amount of zigzag.}
+\comment{We calculate the band structure for varying amount of zigzag.}
 In figure~\ref{fig:band_stuctures}, the bandstructure for zigzag systems with varying amplitude is displayed.
@@
 \end{figure}
+% TODO: add a PHS breaking potential on one edge, this pushes the Majorana away in energy.
 

### 2019-02-19 sns_system.py

@@ -94,7 +94,8 @@ def remove_phs(H):
 @lru_cache()
 def get_template_strings(
         transverse_soi, mu_from_bottom_of_spin_orbit_bands=True,
-        k_x_in_sc=False, with_k_z=False, no_phs=False):
+        k_x_in_sc=False, with_k_z=False, no_phs=False,
+        phs_breaking_potential=False):
     kinetic = "(hbar^2 / (2*m_eff) * (k_y^2 + k_x^2 + k_z^2) - mu {}) * kron(sigma_0, sigma_z)"
     if mu_from_bottom_of_spin_orbit_bands:
         ham_str = kinetic.format("+ m_eff*alpha_middle^2 / (2 * hbar^2)")
@@ -120,7 +121,7 @@ def get_template_strings(
     ham_sc_left += superconductivity.format('left', '-')
     ham_sc_right += superconductivity.format('right', '+')
 
-    zeeman = "+ g_factor_{} * mu_B *( B_x * kron(sigma_x, sigma_0)"
+    zeeman = "+ g_factor_{} * mu_B * (B_x * kron(sigma_x, sigma_0)"
     zeeman += "+ B_y * kron(sigma_y, sigma_0)"
     zeeman += "+ B_z * kron(sigma_z, sigma_0))"
     ham_normal += zeeman.format('middle')
@@ -132,6 +133,9 @@ def get_template_strings(
     if not k_x_in_sc:
         ham_sc_right = ham_sc_right.replace('k_x', '0')
         ham_sc_left = ham_sc_left.replace('k_x', '0')
+
+    if phs_breaking_potential:
+        ham_normal += "+ V_breaking(x) * kron(sigma_0, sigma_0)"
 
     template_strings = dict(ham_barrier=ham_barrier,
                             ham_normal=ham_normal,
@@ -145,9 +149,11 @@ def get_template_strings(
 
 
 @lru_cache()
-def get_templates(a, transverse_soi, mu_from_bottom_of_spin_orbit_bands, k_x_in_sc, no_phs):
+def get_templates(a, transverse_soi, mu_from_bottom_of_spin_orbit_bands,
+    k_x_in_sc, no_phs, phs_breaking_potential):
     template_strings = get_template_strings(
-        transverse_soi, mu_from_bottom_of_spin_orbit_bands, k_x_in_sc, no_phs=no_phs)
+        transverse_soi, mu_from_bottom_of_spin_orbit_bands, 
[…]

### 2019-02-19 spectrum.py

@@ -223,12 +223,12 @@ def find_phase_bounds(lead, params, k_x=0, num_bands=20, sigma=0):
     if num_bands is None:
         mus = np.linalg.eigvals(chemical_potentials.todense())
     else:
-        mus = sla.eigs(chemical_potentials, k=num_bands, sigma=sigma)[0]
+        mus = sla.eigs(chemical_potentials, k=num_bands, sigma=sigma, which='LM')[0]
 
-    inds = np.argsort(mus.real)
-    mus[abs(mus.imag) > 1e-14] = np.nan
+    real_solutions = abs(np.angle(mus)) < 1e-10
 
-    return mus.real[inds]
+    mus[~real_solutions] = np.nan # To ensure it returns the same shape vector
+    return np.sort(mus.real)
 
 
 def cell_mats(lead, params, bias=0):
@@ -242,6 +242,13 @@ def get_h_k(lead, params):
     h, t = cell_mats(lead, params)
     h_k = lambda k: h + t * np.exp(1j * k) + t.T.conj() * np.exp(-1j * k)
     return h_k
+
+
+def lat_from_syst(syst):
+    lats = set(s.family for s in syst.sites)
+    if len(lats) > 1:
+        raise Exception('No unique lattice in the system.')
+    return list(lats)[0]
 
 
 def slowest_evan_mode(lead, params):
@@ -268,47 +275,9 @@ def slowest_evan_mode(lead, params):
     ev = translation_ev(h, t)
     norm = ev * ev.conj()
     idx = np.abs(norm - 1).argmin()
-    a = lattice_constant_from_syst(lead)
+    a = lat_from_syst(lead).prim_vecs[0, 0]
     majorana_length = np.abs(a / np.log(ev[idx]).real)
     return majorana_length
-
-
-def phase_bounds_operator(lead, params, k_x=0):
-    params['mu'] = 0
-    h, t = cell_mats(lead, params)
-    tk = t * np.exp(1j * k_x)
-    h_k = h + tk + tk.T.conj()
-    sigma_z = np.array([[1, 0], [0, -1]])
-    _operator = np.kron(np.eye(len(h) // 2), sigma_z) @ h_k
-    return _operator
-
-
-def find_phase_bounds(lead, params, k=0, num_bands=20):
-    """Find the phase boundaries.
-    Solve an eigenproblem that finds values of chemical potential at which the
-    gap closes at momentum k=0. We are looking for all real solutions of the
[…]

### 2019-02-19 paper/snakemajoranas.tex
mention phase boundaries algo

@@
 \end{figure}
-% TODO: add a PHS breaking potential on one edge, this pushes the Majorana away in energy.
 
@@
 By diagonalizing the Hamiltonian, we find the Majorana energy $E_\textrm{M}$ and the energy of the first excited state $E_1$, the lowest and second lowest energies, respectively.
-Using the eigenstates, we calculate the Majorana decay length $\xi_\textrm{M}$ by fitting an exponential to the density of the Majorana wavefunction projected on the $x$-axis.
+Using the eigenstates, we calculate the Majorana decay length $\xi_\textrm{M}$ by fitting an exponential to the density of a single Majorana wavefunction projected on the $x$-axis.
+To determine $\xi_\textrm{M}$, we artificially break the particle-hole symmetry on one edge by adding a potential $V \sigma_0 \tau_0$ such that one of the Majorana states is pushed into the continuum and the fit to $\exp{\frac{x}{\xi_\textrm{M}}}$ becomes easier.
 In figure~\ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.
@@
 We compute the dispersion of the translationally invariant realizations of a straight and saw-toothed zigzag system and find $\min \left| {E(k)} \right|$ to obtain the energy gap.
-% Additionally, use a generalized eigenvalue problem to find all phase boundaries at once.
+Additionally, in subplot (a) we plot the phase boundaries because they are too narrow to see.
+We do this by solving a generalized eigenvalue problem to find all phase boundaries at once as described in Ref.~\onlinecite{nijholt2015orbital}.
 The parameters values are written at the bottom of Sec.~\ref{sec:setup}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.

### 2019-02-19 paper/snakemajoranas.tex
split up sentence

@@
 Inside the figure, we indicate the Majorana length (or coherence length) $\xi_\textrm{M}$, the Majorana energy $E_\textrm{M}$ (the energy of the first excited state), and the topological energy gap $E_\textrm{gap}$.
-We observe that $\xi_\textrm{M}$ for (a) is significantly longer and $E_\textrm{gap}$ more than an order of magnitude smaller than for (b), (c), and (d), meaning that the details of the geometry do not matter for the improvements to occur.
+We observe that $\xi_\textrm{M}$ for (a) is almost two orders of magnitude longer and $E_\textrm{gap}$ more than an order of magnitude smaller than for (b), (c), and (d).
+The robustness of $E_\textrm{gap}$ and $\xi_\textrm{M}$ across (b), (c), and (d) means that the details of the geometry do not matter for the improvements to occur.
 The length of the system is $3L_x=\SI{3900}{\nm}$, the remaining parameters values are written at the bottom of Sec.~\ref{sec:setup}.\label{fig:wavefunctions}}

### 2019-02-19 paper/snakemajoranas.tex
new abstract

@@
 \begin{abstract}
-Quasi-particle trajectories in high density SNS junctions that have a large momentum parallel to the junction have a very long flight time.
-These trajectories that do not encounter the superconductor for a long time weaken the proximity effect in Josephson junctions.
-This results in a very small induced gap and a soft gap in Majorana devices.
-We propose to eliminate these long trajectories using a new Majorana device.
-We show that a zigzag-shaped geometry eliminates these trajectories, at the same time allowing the robust creation of Majorana states with a gap increased by more than an order of magnitude and a significantly reduced Majorana decay length.
-Additionally, we show that to exploit the benefits of this system, the details exact of the geometry are not important.
+Quasi-particle trajectories in high density superconductor-semiconductor-superconductor junctions that have a large momentum parallel to the junction have a very long flight time, and therefore a small induced superconducting gap.
+Because a large induced gap protects Majorana modes, these long trajectories constrain Majorana devices to low electron density.
+We show that a zigzag-shaped geometry eliminates these trajectories, at the same time allowing the robust creation of Majorana states with both the gap and the Majorana size improved by more than an order of magnitude for realistic parameters.
+In addition to the improved robustness of Majoranas, this new zigzag geometry is insensitive to the geometric details and the device tuning.
 \end{abstract}

### 2019-02-19 paper/snakemajoranas.tex
fixes
* Rephrase the first sentence
* Correct τ_f

@@
 \begin{abstract}
-Quasi-particle trajectories in high density superconductor-semiconductor-superconductor junctions that have a large momentum parallel to the junction have a very long flight time, and therefore a small induced superconducting gap.
+High density superconductor-semiconductor-superconductor junctions have a small induced superconducting gap due to the quasiparticle trajectories with a large momentum parallel to the junction, because these trajectories have a very long flight time.
 Because a large induced gap protects Majorana modes, these long trajectories constrain Majorana devices to low electron density.
-We show that a zigzag-shaped geometry eliminates these trajectories, at the same time allowing the robust creation of Majorana states with both the gap and the Majorana size improved by more than an order of magnitude for realistic parameters.
+We show that a zigzag-shaped geometry eliminates these trajectories, allowing the robust creation of Majorana states with both the induced gap and the Majorana size improved by more than an order of magnitude for realistic parameters.
 In addition to the improved robustness of Majoranas, this new zigzag geometry is insensitive to the geometric details and the device tuning.
@@
 From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
-Additionally, these long trajectories have long flight times $\tau_f=v_F(\theta) / D$ (see Fig.~\ref{fig:setup}(a)) and equivalenly small Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$, resulting in a small gap.
-% TODO: fix the Eq for tau_f
+Additionally, these long trajectories have long flight times $\tau_f \approx W / v_F \sin\theta$ (see Fig.~\ref{fig:setup}(a)) and equivalenly small Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$, resulting in a small gap.
 This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, so a low filling of the bands is a workaround\cite{nijholt2015orbital}.

### 2019-02-19 paper/snakemajoranas.tex
add todos and split up the Hamiltonian

@@
 From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
-Additionally, these long trajectories have long flight times $\tau_f \approx W / v_F \sin\theta$ (see Fig.~\ref{fig:setup}(a)) and equivalenly small Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$, resulting in a small gap.
+Additionally, these long trajectories have long flight times $\tau_f \approx W / v_F \sin\theta$ (see Fig.~\ref{fig:setup}) and equivalenly small Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$, resulting in a small gap.
 This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, so a low filling of the bands is a workaround\cite{nijholt2015orbital}.
@@
 \begin{split}
-    H = & \left[\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right] \tau_z \\
-        & + E_\text{z}(x,y) \sigma_x \\
-        & + \alpha(x,y) \left( \ky \sigma_x - \kx \sigma_y \right) \tau_z
-          + \Delta(x,y) \tau_y.
+    H_\textrm{N} = & \left[\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right] \tau_z
+        + E_\text{z} \sigma_x
+        + \alpha \left( \ky \sigma_x - \kx \sigma_y \right) \tau_z \\
+    \\
+    H_\textrm{SC} = & \left[\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right] \tau_z
+        + \Delta \cos{\frac{\phi}{2}} \tau_x + \Delta \sin{\frac{\phi}{2}} \tau_y.
 \end{split}
@@
 \end{equation}
-It acts on the spinor wave function $\Psi={\left(\psi_{e\uparrow},\psi_{e\downarrow},\psi_{\textrm{h}\downarrow},-\psi_{\textrm{h}\uparrow}\right)}^{T}$, where $\psi_e$, $\psi_\textrm{h}$ are its electron and hole components, and $\psi_\uparrow$, $\psi_\downarrow$ are the spin-up and spin-down components.
+Where $H_\textrm{N}$ and $H_\textrm{SC}$ are the Hamiltonians of the semiconductor and superconductors, respectively.
+They act on the spinor wave function $\Psi={\left(\psi_{e\uparrow},\psi_{e\downarrow},\psi_{\textrm{h}\downarrow},-\psi_{\textrm{h}\uparrow}\right)}^{T}$, where $\psi_e$, $\psi_\textrm{h}$ are its electron and hole components, and $\psi_\uparrow$, $\psi_\downarrow$ are the spin-up and spin-down components.
 The Pauli matrices $\sigma_{i}$ act on the spin degree of freedom and $\tau_{i}$ act on the electron-hole degree of freedom.
-For the zigzag geometry, we first consider a sawtooth-like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
-The spatial dependence of $\Delta$, $E_z$, and $\alpha$ is explained in text above.
+For the zigzag geometry, we first consider a sawtooth-like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction [see Fig.~\ref{fig:setup}(b)].
 Later in this manuscript, we show that the exact details of the shape are unimportant and consider different zigzag geometries also parametrized by $z_x, \; z_y, \; W$.
@@
 The parameters values are written at the bottom of Sec.~\ref{sec:setup}.\label{fig:band_stuctures}}
+% TODO: mention z_x!
 \end{figure}
@@
 We compute the dispersion of the translationally invariant realizations of a straight and saw-toothed zigzag system and find $\min \left| {E(k)} \right|$ to obtain the energy gap.
+% TODO: mention this in main text!
 Additionally, in subplot (a) we plot the phase boundaries because they are too narrow to see.
-We do this by solving a generalized eigenvalue problem to find all phase boundaries at once as described in Ref.~\onlinecite{nijholt2015orbital}.
+We do this by solving a generalized eigenvalue problem to find all phase boundaries at once as described in Ref.~\onlinecite{nijholt2015orbital}.  % TODO: mention in main text
+% TODO: mention distinguish between min E(K) and other algo in main text!
 The parameters values are written at the bottom of Sec.~\ref{sec:setup}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.

### 2019-02-20 paper/snakemajoranas.tex
small review with Anton

@@
 The complete Hamiltonian has the form
-\begin{equation}
-\begin{split}
-    H_\textrm{N} = & \left[\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right] \tau_z
-        + E_\text{z} \sigma_x
-        + \alpha \left( \ky \sigma_x - \kx \sigma_y \right) \tau_z \\
-    \\
+\begin{subequations}
+\begin{align}
+    H_\textrm{N} = & \left[\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu + \alpha \left( \ky \sigma_x - \kx \sigma_y \right) \right] \tau_z
+        + E_\text{z} \sigma_x \\
     H_\textrm{SC} = & \left[\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right] \tau_z
         + \Delta \cos{\frac{\phi}{2}} \tau_x + \Delta \sin{\frac{\phi}{2}} \tau_y.
-\end{split}
+\end{align}
 \label{eq:hamiltonian}
-\end{equation}
+\end{subequations}
 Where $H_\textrm{N}$ and $H_\textrm{SC}$ are the Hamiltonians of the semiconductor and superconductors, respectively.
@@
 Later in this manuscript, we show that the exact details of the shape are unimportant and consider different zigzag geometries also parametrized by $z_x, \; z_y, \; W$.
+
+\comment{We discretize the Hamiltonian and simulate it with Kwant.}
+We discretize our continuum Hamiltonian [Eq.~\eqref{eq:hamiltonian}] on a square grid and implement a tight-binding model using Kwant~\cite{groth_kwant:_2014}.
+To optimize the sampling in important regions of parameter space, we use the Adaptive package.~\cite{adaptive}
+The entire source code and the resulting raw data are available in Ref.~\onlinecite{data}.  % TODO: update the bib when the data is uploaded
 
@@
 
-\comment{We discretize the Hamiltonian and simulate it with Kwant.}
-We discretize our continuum Hamiltonian [Eq.~\eqref{eq:hamiltonian}] on a square grid and implement a tight-binding model using Kwant~\cite{groth_kwant:_2014}.
-The resulting Hamiltonians are large because instead of having a single slice of sites that is translationally invariant in the $x$-direction, we create a long 2D supercell to make the structure periodic.
-To speed up these expensive simulations we employ an adaptive sampling strategy, using the Python package Adaptive.~\cite{adaptive}
-The entire source code and the resulting raw data are available in Ref.~\onlinecite{data}.  % TODO: update the bib when the data is uploaded
-
 \begin{figure}[!htb]
@@
 The blue lines correspond to $\phi=0$, $B=0$ (trivial phase) and the orange lines to $\phi=\pi$, $B = \SI{1}{T}$ (topological phase).
-The three subplots are for different amplitudes of the zigzag, with (a) a straight system $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W=\SI{200}{\nm}$ is the junction width.
+The three subplots are for different amplitudes of the zigzag, with (a) a straight system $z_y=0$, (b) $z_y=\frac{W}{2}$, and (c) $z_y=W$, where $W=\SI{200}{\nm}$ is the junction width.
+On the $x$-axis is the folded lattice momentum where $z_x=\SI{1300}{\nm}$.
 Subplot (a) has a different scale on the $x$-axis for $k_x < 0$ than the other subplots and displays the unfolded band structure.
 For the right-hand side of (a) ($k_x > 0$), (b), and (c), the folding is the same, such that the velocity $v=\frac{dE}{dk}$ can be compared visually.
-We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$, and thus the $v_\textrm{F}$ decreases.
+We observe that once there are no more straight trajectories inside the junction (when $z_y=W$) the spectrum becomes most insensitive to the momentum $k_x$, and thus the $v_\textrm{F}$ decreases.
 As the zigzag amplitude increases the band gap $E_\textrm{gap}$ increases by an order of magnitude.
@@
 \comment{We calculate the band structure for varying amount of zigzag.}
-In figure~\ref{fig:band_stuctures}, the bandstructure for zigzag systems with varying amplitude is displayed.
-Because the discretized zigzag system is modeled using a supercell, we can only plot a folded bandstructure.
-For comparison's sake, we take the same cell size for the ribbon structure such that the bandstructure folds in the same way.
+We diagonalize the supercell Hamiltonian to compute the band structure.
+Because of the large periodicity of the zigzag and the resulting large supercell, the band structure is heavily folded.
+In figure~\ref{fig:band_stuctures} we show the resulting band structures for zigzag systems with a varying amplitude.
 
 \comment{The band structures show that modulation of the geometry increases the gap by an order of magnitude, as well as reduce the group velocity.}
-The introduction of a zigzag has a striking effect: the bands flatten out because of a reduction in velocity and the topological gap increases by more than an order of magnitude.
+The introduction of a zigzag has a striking effect: the bands flatten out and the topological gap increases by more than an order of magnitude.
 On an intuitive level we can understand this because in a straight system long trajectories are possible, these have a momentum that is directed along the strip and consequently, $k_x \approx k_F$.
 Further, the smallest gap in a straight system occurs around $k_F$, and because the zigzag cuts off long trajectories, the gap size increases.
-Besides this, the velocity of the modes greatly reduces, which has a positive effect on the Majorana coherence length, as described later in section \ref{sec:shape_effects}.
+Besides this, the states that exist in different segments have very little overlap and therefore have a very small velocity.
+This reduction in velocity has a positive effect on the Majorana coherence length, as described later in section \ref{sec:shape_effects}.
 
@@
 The robustness of $E_\textrm{gap}$ and $\xi_\textrm{M}$ across (b), (c), and (d) means that the details of the geometry do not matter for the improvements to occur.
-The length of the system is $3L_x=\SI{3900}{\nm}$, the remaining parameters values are written at the bottom of Sec.~\ref{sec:setup}.\label{fig:wavefunctions}}
+The length of the system is $3.5 L_x=\SI{4550}{\nm}$, the remaining parameters values are written at the bottom of Sec.~\ref{sec:setup}.\label{fig:wavefunctions}}
 \end{figure}
@@
 Using the eigenstates, we calculate the Majorana decay length $\xi_\textrm{M}$ by fitting an exponential to the density of a single Majorana wavefunction projected on the $x$-axis.
-To determine $\xi_\textrm{M}$, we artificially break the particle-hole symmetry on one edge by adding a potential $V \sigma_0 \tau_0$ such that one of the Majorana states is pushed into the continuum and the fit to $\exp{\frac{x}{\xi_\textrm{M}}}$ becomes easier.
+To determine $\xi_\textrm{M}$, we use a trick and artificially break the particle-hole symmetry on one edge by adding a potential $V \sigma_0 \tau_0$ such that one of the Majorana states is pushed into the continuum and the fit to $\exp{\frac{x}{\xi_\textrm{M}}}$ becomes easier.
 In figure~\ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.

### 2019-02-20 sns_system.py
Fixed jumps in geometry by removing integer division from the lambda function

@@ -337,7 +337,7 @@ def make_system(L_m, L_x, L_sc_up, L_sc_down, z_x, z_y, a,
         above_shape = above_curve(curve_bottom)
 
     elif sawtooth:
-        _curve = lambda x: 4*z_y/z_x*(x%(z_x//2)) - z_y if x%z_x < z_x//2 else -4*z_y/z_x*(x%(z_x//2)) + z_y
+        _curve = lambda x: 4*z_y/z_x*(x%(z_x/2)) - z_y if x%z_x < z_x/2 else -4*z_y/z_x*(x%(z_x/2)) + z_y
         curve = lambda x: _curve(x+z_x/4)
 
         if z_y is not 0:

### 2019-02-20 sns_system.py
Fixed issue where edge wasn't being filled in. Just iterating through all the sites at x=0 solves it.

@@ -451,7 +451,7 @@ def make_system(L_m, L_x, L_sc_up, L_sc_down, z_x, z_y, a,
 
         #----------
         # Fill edge
-        for y in np.arange(-L_m - z_y, L_m + z_y, a):
+        for y in np.arange(-L_m - L_sc_down, L_m + L_sc_up, a):
             pos = (0, y)
             edge_sites_new = syst.fill(template_edge, edge_shape, pos)
             if len(edge_sites_new) > 0:

### 2019-02-20 paper/snakemajoranas.tex
finish review Sec III

@@
 We discretize our continuum Hamiltonian [Eq.~\eqref{eq:hamiltonian}] on a square grid and implement a tight-binding model using Kwant~\cite{groth_kwant:_2014}.
-To optimize the sampling in important regions of parameter space, we use the Adaptive package.~\cite{adaptive}
+To preferentially sample important regions of parameter space, we use the Adaptive package.~\cite{adaptive}
 The entire source code and the resulting raw data are available in Ref.~\onlinecite{data}.  % TODO: update the bib when the data is uploaded
@@
 \comment{We calculate the band structure for varying amount of zigzag.}
-We diagonalize the supercell Hamiltonian to compute the band structure.
+We apply sparse diagonalization to the supercell Hamiltonian at different momenta $k_x$ to compute the band structure.
 Because of the large periodicity of the zigzag and the resulting large supercell, the band structure is heavily folded.
 In figure~\ref{fig:band_stuctures} we show the resulting band structures for zigzag systems with a varying amplitude.
+The introduction of the zigzag has a striking effect: the bands flatten out and the topological gap increases by more than an order of magnitude.
 
-\comment{The band structures show that modulation of the geometry increases the gap by an order of magnitude, as well as reduce the group velocity.}
-The introduction of a zigzag has a striking effect: the bands flatten out and the topological gap increases by more than an order of magnitude.
-On an intuitive level we can understand this because in a straight system long trajectories are possible, these have a momentum that is directed along the strip and consequently, $k_x \approx k_F$.
-Further, the smallest gap in a straight system occurs around $k_F$, and because the zigzag cuts off long trajectories, the gap size increases.
-Besides this, the states that exist in different segments have very little overlap and therefore have a very small velocity.
-This reduction in velocity has a positive effect on the Majorana coherence length, as described later in section \ref{sec:shape_effects}.
-
-\comment{The introduction of an NS interface at many angles increases the transparency.}
-Additionally, in the presence of normal reflection, due to the presence of NS interfaces at a wide range of angles, the reflected part will eventually scatter with a near perpendicular surface.
-This means that for transversal modes the transparency of the NS interface will increase.
+\comment{Zigzag improves the gap and size because of cutting of trajectories and increasing transparency.}
+This confirms our expectation that the zigzag removes trajectories propagating at grazing angles.
+In the unfolded band structure for a straight system, as seen in Fig.~\ref{fig:bandstructures}(a), the gap in a straight system occurs around $k_F$ and because the zigzag cuts off long trajectories, the gap size increases.
+Besides this, the states from different segments of the zigzag pattern have a negligible overlap and therefore have a vanishing velocity.
+This reduction in velocity strongly reduces the Majorana size, as we discuss in section \ref{sec:shape_effects}.
+Additionally, in the presence of normal reflection, due to the presence of NS interfaces at a wide range of angles, the reflected part eventually scatters with a near perpendicular surface.
+This means that for transversal modes the transparency of the NS interface increases.
 

### 2019-02-21 paper/snakemajoranas.tex
remove Analytical Estimate section
figure improvements
update the phase diagram figure caption

@@
 \begin{figure}[!htb]
-\includegraphics[width=0.95\columnwidth]{figures/zigzag.pdf}
+\includegraphics[width=\columnwidth]{figures/zigzag.pdf}
 \caption{Setups. Figure of a straight and zigzag system, including trajectories.
@@
 \begin{figure}[!htb]
-\includegraphics[width=0.95\columnwidth]{figures/bandstructures}
+\includegraphics[width=\columnwidth]{figures/bandstructures}
 \caption{Figure of the band stuctures corresponding to the system in Fig.~\ref{fig:setup} with different zigzag amplitudes.
@@
 %%██████████████████████████████████████████████████████████████████████████
-%%██ Analytical estimate
-%%██████████████████████████████████████████████████████████████████████████
-% \section{Analytical estimate of the band gap}
-
-% \comment{To compute the effect of cutoff consider a single segment of the zigzag and obtain the spectrum analytically (this allows to use translation invariance).}
-% We establish that the cutoff of long trajectories is the driving mechanism behind the order of magnitude gap improvement using an analytical approach.
-% We derive the Andreev spectrum for a single (diagonal) segment of the zigzag, and define the gap of the system as the minimum of the spectrum occurring before the cutoff corresponding to the particular geometry.
-% The system under consideration is thus a ribbon SNS junction with a tilted magnetic field.
-
-% \comment{The definition of the cutoff...}
-
-% \comment{We use a short junction approximation and neglect transverse SO.}
-% We derive the spectrum by calculating the scattering matrix for the normal region and applying the Andreev bound state condition for the short junction limit\cite{beenakker1991universal, sticlet_robustness_2017}.
-% For derivation of the scattering matrix, we neglect SOI in the transverse direction, which is valid for $W<l_\text{so}$.
-% The result is specified in Eqs.~\eqref{eq:smatrix} to~\eqref{eq:momenta_short_junction}.
-
-% \begin{align}
-% \label{eq:smatrix}
-%     S &= \left(
-%     \begin{array}{rr}
-%     r_{ll}&t_{rl}\\
-%     t_{lr}&r_{rr}\\
-%     \end{array}
-%     \right) =
-%     \left(
-%     \begin{array}{rr}
-%     \beta_+ & e^{-i q W} \beta_-\\
-%     e^{-i q W} \beta_- & e^{-2 i q W} \beta_+\\
-%     \end{array}
-%     \right)
-%     \\
-%     \beta_\pm &= \left(
-%     \begin{array}{rr}
-%     e^{i \nu_{\arg}}\left(\omega^\pm_1 - \omega^\pm_2\right) & (\omega^\pm _1 + \omega^\pm _2)\\
-%     -(\omega^\pm _1 + \omega^\pm _2) & e^{-i \nu _{\arg }} \left(\omega^\pm _2 - \omega^\pm _1\right)\\
-%     \end{array}
-%     \right)\\
-%     \omega^\pm_j &= \frac{1}{4} \left(\gamma _{j} \pm \delta _{j}\right)
-% \end{align}
-
-% \begin{align}
-%     \gamma_j &= \frac{q+i k_{j} \tan \left(\frac{W k_{j}}{2}\right)}{q-i k_{j} \tan \left(\frac{W k_{j}}{2}\right)} \\
-%     \delta_j &= \frac{q-i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}{q+i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}\\
-%     e^{i \nu_{\arg}} &= \frac{E_\text{z} e^{i \theta }-i \alpha  k_x}{\sqrt{E_\text{z}^2+\alpha  k_x \left(\alpha  k_x-2 E_\text{z} \sin (\theta )\right)}}
-% \end{align}
-
-% \begin{footnotesize}
-% \begin{align}
-%     q &= \left[ \frac{2 m_\ast}{\hbar ^2}\mu_s - k_x^2 \right]^\frac{1}{2}\\
-%     k_1 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n-\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}\\
-%     k_2 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n+\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}
-% \label{eq:momenta_short_junction}
-% \end{align}
-% \end{footnotesize}
-
-% In order to get the spectrum from the S-matrix [Eq.~\eqref{eq:smatrix}] we use the main result from Ref.~\onlinecite{beenakker1991universal} and start with a determinantal equation for the bound state energies in a SNS-junction:
-
-% \begin{equation}
-% \det\left[1+\alpha^{2}\left(E\right)r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)\right]=0
-% \end{equation}
-
-% We rewrite this as a characteristic polynomial problem $\det\left[A-\lambda I\right]=0$, as
-
-% \begin{equation}
-% \det\left[r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)-\frac{-1}{\alpha^{2}\left(E\right)}I\right]=0
-% \end{equation}
-
-% with
-% \begin{equation}
-% \lambda=-\frac{1}{\alpha^{2}\left(E\right)},\;A=r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right).
-% \end{equation}
-
-% Where $\lambda_i$ are the eigenvalues of $A$.
-% Inverting $\alpha\left(E\right)\equiv\exp\left(-i\arccos\left(E/\Delta\right)\right)$ yields $\frac{E}{\Delta}=\frac{\alpha^{2}+1}{2\alpha}=\frac{1}{2}\left(\alpha+\alpha^{-1}\right)=\textrm{Re}(\alpha)$, where the last equality holds because $\alpha$ is unitary.
-% Then, since $\alpha$ is only defined in the positive imaginary plane, the energies are $\frac{E_{i}}{\Delta}=\textrm{Re}\left(\sqrt{-1/\lambda_{i}}\right)$ where we take the root which has a positive imaginary part.
-% Using this result and Eq.~\eqref{eq:smatrix}, we numerically find the Andreev spectrum.
-
-% \comment{The lowest energy at $|k| < k_\textrm{cutoff}$ sets the band gap.}
-% We cut off the spectrum at the momentum corresponding to the proposed cutoff in the zigzag, and compare it to the numerically obtained gap for a true zigzag system.
-
-%%██████████████████████████████████████████████████████████████████████████
 %%██ Localization lengths and shape effect
@@
 \begin{figure}[!htb]
-\includegraphics[width=0.95\columnwidth]{figures/wavefunctions}
+\includegraphics[width=\columnwidth]{figures/wavefunctions}
 \caption{Density of wavefunctions $\left|\psi\right|^2$ for sizes and geometries.
@@
 \begin{figure}[!htb]
-\includegraphics[width=0.95\columnwidth]{figures/phasediagrams}
-\caption{Phase diagrams of a straight system (a), (b) and zigzag system (c), (d), where (a), (c) are $E(\mu, B)$ and (b), (d) are $E(\phi, B)$.
-Phase diagrams of a straight system (a), (b) and zigzag system (c), (d), where (a), (c) are $E(\mu, B)$ and (b), (d) are $E(\phi, B)$.
-We compute the dispersion of the translationally invariant realizations of a straight and saw-toothed zigzag system and find $\min \left| {E(k)} \right|$ to obtain the energy gap.
-% TODO: mention this in main text!
-Additionally, in subplot (a) we plot the phase boundaries because they are too narrow to see.
-We do this by solving a generalized eigenvalue problem to find all phase boundaries at once as described in Ref.~\onlinecite{nijholt2015orbital}.  % TODO: mention in main text
-% TODO: mention distinguish between min E(K) and other algo in main text!
-The parameters values are written at the bottom of Sec.~\ref{sec:setup}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
-The chemical potential is $\mu=\SI{10}{\meV}$ in (b) and (d) and the superconducting phase is $\phi=\pi$ in (a) and (c).
+\includegraphics[width=\columnwidth]{figures/phasediagrams}
+\caption{Part the wave function of a straight system (a) and a zigzag system (b) of length $L=\SI{3900}{\nm}$ but only the first period ($\SI{1300}{\nm}$) is plotted.
+The phase diagrams (c) and (d) display $E_\textrm{gap}(B_x, \mu)$ at $\phi=\pi$ and (e) and (f) display $E_\textrm{gap}(B_x, \phi)$ at $\mu=\SI{10}{\meV}$, where $E_\textrm{gap}$ is the smallest gap in the dispersion relation.
+Subplots (c) and (e) correspond to system (a), and (d) and (f) correspond to system (b).
+The brown dot in the phase diagrams indicate the largest gap in the parameter space for the straight system and the parameter values for which the wavefunctions (a) and (b) are plotted.
+Additionally, in subplot (c) we plot the phase boundaries because they are too narrow to see.
+In (a) and (b) we note the Majorana size $\xi_\textrm{M}$ and $E_\textrm{gap}$, and see that both of these are more than an order of magnitude better for the zigzag system, even though these are plotted for the most optimal parameters for the straight system at $\mu=\SI{10}{\meV}$.
+The remaining parameters values are written at the bottom of Sec.~\ref{sec:setup}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
 \label{fig:phasediagrams}}
@@
 \comment{We calculate the topological phase diagram using the gap size.}
-Due to the large size of the system, we are unable to use full spectrum methods (like the Pfaffian) to compute the topological invariant of our system.
-Instead, we calculate the energy gap by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{|E(k)|}$.
+In Fig.~\ref{fig:phasediagrams}, we plot the energy gap as a function of magnetic field, chemical potential, $E_\textrm{gap}(B_x, \mu)$; and the superconducting phase difference $E_\textrm{gap}(B_x, \phi)$ for both a straight system [(c) and (e)] and a zigzag system [(d) and (f)].
+Additionally, we plot the first $\SI{1300}{\nm}$ (one zigzag period) of the wavefunction at the most optimal point in parameter space for the straight system.
+For the straight system we calculate $E_\textrm{gap}$ by performing a binary search in $E$ for the energy at which the propagating modes start to appear.
+Additionally, in Fig.~\ref{fig:phasediagrams}(c) we plot the phase boundaries that we find by solving a generalized eigenvalue problem as described in Ref.~\onlinecite{nijholt2015orbital}.
+Due to the large size of the zigzag supercell, we are unable to use these full spectrum methods to compute these quantities.
+Instead, we calculate $E_\textrm{gap}$ by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{|E(k)|}$.
 By both observing the gap closings and knowing the topological phase for the non-zigzag system, we can infer the topology of the system with zigzag modulation.
-In Fig.~\ref{fig:phasediagrams}, we plot the energy gap as a function of magnetic field, chemical potential, $E_\textrm{gap}(B_x, \mu)$; and the superconducting phase difference $E_\textrm{gap}(B_x, \phi)$ for both a straight system [(a) and (b)] and a zigzag system [(c) and (d)].
 

### 2019-02-21 paper/snakemajoranas.tex
fix figure ref

@@
 This confirms our expectation that the zigzag removes trajectories propagating at grazing angles.
-In the unfolded band structure for a straight system, as seen in Fig.~\ref{fig:bandstructures}(a), the gap in a straight system occurs around $k_F$ and because the zigzag cuts off long trajectories, the gap size increases.
+In the unfolded band structure for a straight system, as seen in Fig.~\ref{fig:band_structures}(a), the gap in a straight system occurs around $k_F$ and because the zigzag cuts off long trajectories, the gap size increases.
 Besides this, the states from different segments of the zigzag pattern have a negligible overlap and therefore have a vanishing velocity.

### 2019-02-21 paper/snakemajoranas.tex
improve text and figure in Sec V

@@
 \comment{We calculate the topological phase diagram using the gap size.}
-In Fig.~\ref{fig:phasediagrams}, we plot the energy gap as a function of magnetic field, chemical potential, $E_\textrm{gap}(B_x, \mu)$; and the superconducting phase difference $E_\textrm{gap}(B_x, \phi)$ for both a straight system [(c) and (e)] and a zigzag system [(d) and (f)].
-Additionally, we plot the first $\SI{1300}{\nm}$ (one zigzag period) of the wavefunction at the most optimal point in parameter space for the straight system.
-For the straight system we calculate $E_\textrm{gap}$ by performing a binary search in $E$ for the energy at which the propagating modes start to appear.
+In Fig.~\ref{fig:phasediagrams} we plot the energy gap as a function of magnetic field, chemical potential, $E_\textrm{gap}(B_x, \mu)$; and the superconducting phase difference $E_\textrm{gap}(B_x, \phi)$ for both a straight system [(c) and (e)] and a zigzag system [(d) and (f)].
+Additionally, we plot the first $\SI{1300}{\nm}$ (one zigzag period) of the wavefunctions [(a) and (b)] at the most optimal point in parameter space for the straight system.
+For the straight system we calculate $E_\textrm{gap}$ by performing a binary search in $E$ for the energy at which the propagating modes start to appear.~\cite{nijholt2015orbital}
 Additionally, in Fig.~\ref{fig:phasediagrams}(c) we plot the phase boundaries that we find by solving a generalized eigenvalue problem as described in Ref.~\onlinecite{nijholt2015orbital}.
@@
 \comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry.}
-Similar to what is described by Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond-like shape as a function of phase $\phi$ and Zeeman field $E_Z$.
+Similar to what is described by Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond-like shape as a function of phase $\phi$ and magnetic field $B_x$.
 We also observe additional gap closings which are due to the BDI symmetry that is present.

### 2019-02-22 paper/snakemajoranas.tex
remove length details, and wf -> Majorana wf
improve fig caption

@@
 \includegraphics[width=\columnwidth]{figures/phasediagrams}
-\caption{Part the wave function of a straight system (a) and a zigzag system (b) of length $L=\SI{3900}{\nm}$ but only the first period ($\SI{1300}{\nm}$) is plotted.
-The phase diagrams (c) and (d) display $E_\textrm{gap}(B_x, \mu)$ at $\phi=\pi$ and (e) and (f) display $E_\textrm{gap}(B_x, \phi)$ at $\mu=\SI{10}{\meV}$, where $E_\textrm{gap}$ is the smallest gap in the dispersion relation.
-Subplots (c) and (e) correspond to system (a), and (d) and (f) correspond to system (b).
-The brown dot in the phase diagrams indicate the largest gap in the parameter space for the straight system and the parameter values for which the wavefunctions (a) and (b) are plotted.
-Additionally, in subplot (c) we plot the phase boundaries because they are too narrow to see.
-In (a) and (b) we note the Majorana size $\xi_\textrm{M}$ and $E_\textrm{gap}$, and see that both of these are more than an order of magnitude better for the zigzag system, even though these are plotted for the most optimal parameters for the straight system at $\mu=\SI{10}{\meV}$.
+\caption{A comparison of a straight device (left panels) and a zigzag one (right panels).
+The top panels show the Majorana wave functions, near the left edge of the system, at the value of $B_x$ for which $E_\textrm{gap}$ is maximized in a straight geometry for $\mu=\SI{10}{\meV}$ and $\phi=\pi$ as well as the values of the gap and the Majorana size.
+The other panels show gap as a function of $\mu$ and $B_x$ at $\phi=\pi$ (middle panels) and as a function of $\phi$ and $B_x$ at $\mu=\SI{10}{\meV}$ (bottom panels).
+The dashed lines and the dot indicate the parameters used in the other panels.
+Additionally, in subplot (c) we overlay the phase boundaries.
 The remaining parameters values are written at the bottom of Sec.~\ref{sec:setup}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
@@
 The introduction of a zigzag geometry increases the topological gap by over an order of magnitude, as well as offering a substantial reduction of the Majorana length, which enables experimentalists to create significantly shorter devices.
+% The Majorana size $\xi_\textrm{M}$ and $E_\textrm{gap}$ are more than an order of magnitude better for the zigzag system, even though these are plotted for the optimal parameters for the straight system at $\mu=\SI{10}{\meV}$.
+% From phase diagram figure
 Additionally, the breaking of BDI symmetry into D symmetry results in a cleaner and more stable topological region.

### 2019-02-22 paper/snakemajoranas.tex
Added updated figure, changed export parameter of inkscape to page instead of drawing, and added subsentence to replace theta

@@
 From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
-Additionally, these long trajectories have long flight times $\tau_f \approx W / v_F \sin\theta$ (see Fig.~\ref{fig:setup}) and equivalenly small Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$, resulting in a small gap.
+Additionally, these long trajectories have long flight times $\tau_f \approx D / v_F$ (see Fig.~\ref{fig:setup}), where $D$ is the length of the trajectory, and equivalenly small Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$, resulting in a small gap.
 This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, so a low filling of the bands is a workaround\cite{nijholt2015orbital}.

### 2019-02-23 paper/snakemajoranas.tex
bottom -> end

@@
 The combination of these ensures a significant decrease of the Majorana decay length because $\xi_M \propto \frac{v_\textrm{F}}{E_\textrm{gap}}$
-The parameters values are written at the bottom of Sec.~\ref{sec:setup}.\label{fig:band_stuctures}}
+The parameters values are written at the end of Sec.~\ref{sec:setup}.\label{fig:band_stuctures}}
 % TODO: mention z_x!
@@
 The robustness of $E_\textrm{gap}$ and $\xi_\textrm{M}$ across (b), (c), and (d) means that the details of the geometry do not matter for the improvements to occur.
-The length of the system is $3.5 L_x=\SI{4550}{\nm}$, the remaining parameters values are written at the bottom of Sec.~\ref{sec:setup}.\label{fig:wavefunctions}}
+The length of the system is $3.5 L_x=\SI{4550}{\nm}$, the remaining parameters values are written at the end of Sec.~\ref{sec:setup}.\label{fig:wavefunctions}}
 \end{figure}
@@
 Additionally, in subplot (c) we overlay the phase boundaries.
-The remaining parameters values are written at the bottom of Sec.~\ref{sec:setup}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
+The remaining parameters values are written at the end of Sec.~\ref{sec:setup}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
 \label{fig:phasediagrams}}

### 2019-02-23 paper/snakemajoranas.tex
write fig 1 caption

@@
 \includegraphics[width=\columnwidth]{figures/zigzag.pdf}
-\caption{Setups. Figure of a straight and zigzag system, including trajectories.
+\caption{Setup of the straight (top) and the zigzag (bottom) SNS junction.
+The yellow areas are the superconductors at a phase difference $\pm \phi / 2$.
+The middle area is the semiconductor of width $W$ and has a magnetic field $B$ in the $x$-direction.
+The modulation of the zigzag is parameterized by its amplitude $z_y$ and period $z_x$.
+Inside the semiconductor we indicate the longest possible trajectory by the red wiggly line.
 \label{fig:setup}}

### 2019-02-23 paper/snakemajoranas.tex
rephrase
fix typos

@@
 The modulation of the zigzag is parameterized by its amplitude $z_y$ and period $z_x$.
-Inside the semiconductor we indicate the longest possible trajectory by the red wiggly line.
+Inside the semiconductor we indicate the longest possible trajectory by the red curve.
 \label{fig:setup}}
@@
 %%██████████████████████████████████████████████████████████████████████████
-\section{Band stuctures}\label{sec:band_stuctures}
+\section{Band stuctures}\label{sec:band_structures}
 
@@
 The combination of these ensures a significant decrease of the Majorana decay length because $\xi_M \propto \frac{v_\textrm{F}}{E_\textrm{gap}}$
-The parameters values are written at the end of Sec.~\ref{sec:setup}.\label{fig:band_stuctures}}
+The parameters values are written at the end of Sec.~\ref{sec:setup}.\label{fig:band_structures}}
 % TODO: mention z_x!
@@
 Because of the large periodicity of the zigzag and the resulting large supercell, the band structure is heavily folded.
-In figure~\ref{fig:band_stuctures} we show the resulting band structures for zigzag systems with a varying amplitude.
+In figure~\ref{fig:band_structures} we show the resulting band structures for zigzag systems with a varying amplitude.
 The introduction of the zigzag has a striking effect: the bands flatten out and the topological gap increases by more than an order of magnitude.
@@
 Quantitatively, the improvement in the localization of the Majoranas is also distinctly apparent: the energies of the Majorana states are three orders of magnitude lower than the energy of the second lowest-lying wavefunctions.
-As mentioned in section \ref{sec:band_stuctures}, this can be attributed to the way the energy gap and velocity factor into the Majorana coherence length which scales with these parameters $\xi_\textrm{M}=\hbar\frac{v_\textrm{F}}{\Delta_\textrm{ind}}$.
+As mentioned in section \ref{sec:band_structures}, this can be attributed to the way the energy gap and velocity factor into the Majorana coherence length which scales with these parameters $\xi_\textrm{M}=\hbar\frac{v_\textrm{F}}{\Delta_\textrm{ind}}$.
 Additionally, the reduction of the Majorana decay length allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.

### 2019-02-24 paper/snakemajoranas.tex
Split sentence explaining long flight times in two

@@
 From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
-Additionally, these long trajectories have long flight times $\tau_f \approx D / v_F$ (see Fig.~\ref{fig:setup}), where $D$ is the length of the trajectory, and equivalenly small Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$, resulting in a small gap.
+Additionally, these long trajectories have long flight times $\tau_f \approx D / v_F$ (see Fig.~\ref{fig:setup}), with $D$ the trajectory length.
+Equivalently, the Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$ are small, resulting in a small gap.
 This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, so a low filling of the bands is a workaround\cite{nijholt2015orbital}.

### 2019-02-25 paper/snakemajoranas.tex
Made system figure smaller
typo fixed

@@
 \begin{figure}[!htb]
-\includegraphics[width=\columnwidth]{figures/zigzag.pdf}
+\centering
+\includegraphics[width=0.75\columnwidth]{figures/zigzag.pdf}
 \caption{Setup of the straight (top) and the zigzag (bottom) SNS junction.
@@
 Recently, it has been shown~\cite{haim_double-edge_2018} that having a system with weak disorder can lead to a reduction in the Majorana decay length, similar to what happens with the introduction of a zigzag geometry.
-However, in contrast to introducing weak disorder into a system, changing the geomerty is experimentally much easier to realize and therefore easier to control.
+However, in contrast to introducing weak disorder into a system, changing the geometry is experimentally much easier to realize and therefore easier to control.
 

### 2019-02-25 paper/snakemajoranas.tex
D -> L_t, to not confuse it with diffusion

@@
 From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
-Additionally, these long trajectories have long flight times $\tau_f \approx D / v_F$ (see Fig.~\ref{fig:setup}), with $D$ the trajectory length.
+Additionally, these long trajectories have long flight times $\tau_f \approx L_\textrm{t} / v_F$ (see Fig.~\ref{fig:setup}), where $L_\textrm{t}$ is the trajectory length.
 Equivalently, the Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$ are small, resulting in a small gap.

### 2019-02-25 paper/snakemajoranas.tex
L_x -> z_x

@@
 The robustness of $E_\textrm{gap}$ and $\xi_\textrm{M}$ across (b), (c), and (d) means that the details of the geometry do not matter for the improvements to occur.
-The length of the system is $3.5 L_x=\SI{4550}{\nm}$, the remaining parameters values are written at the end of Sec.~\ref{sec:setup}.\label{fig:wavefunctions}}
+The length of the system is $3.5 z_x=\SI{4550}{\nm}$, the remaining parameters values are written at the end of Sec.~\ref{sec:setup}.\label{fig:wavefunctions}}
 \end{figure}

### 2019-02-25 paper/snakemajoranas.tex
wave function is two words

@@
 \caption{Setup of the straight (top) and the zigzag (bottom) SNS junction.
-The yellow areas are the superconductors at a phase difference $\pm \phi / 2$.
+The yellow areas are the superconductors at an opposite superconducting phase $\pm \phi / 2$.
 The middle area is the semiconductor of width $W$ and has a magnetic field $B$ in the $x$-direction.
@@
 \begin{figure}[!htb]
-\includegraphics[width=\columnwidth]{figures/wavefunctions}
-\caption{Density of wavefunctions $\left|\psi\right|^2$ for sizes and geometries.
+\includegraphics[width=\columnwidth]{figures/wave functions}
+\caption{Density of wave functions $\left|\psi\right|^2$ for sizes and geometries.
 With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) similar to (c) but with disordered edges.
@@
 The robustness of $E_\textrm{gap}$ and $\xi_\textrm{M}$ across (b), (c), and (d) means that the details of the geometry do not matter for the improvements to occur.
-The length of the system is $3.5 z_x=\SI{4550}{\nm}$, the remaining parameters values are written at the end of Sec.~\ref{sec:setup}.\label{fig:wavefunctions}}
+The length of the system is $3.5 z_x=\SI{4550}{\nm}$, the remaining parameters values are written at the end of Sec.~\ref{sec:setup}.\label{fig:wave_functions}}
 \end{figure}
@@
 \comment{We calculate the wave functions and find the Majorana lengths by fitting an exponential.}
-We model a finite system to compute the Majorana wave function density for different geometries; ribbon, saw-toothed zigzag, parallel curves, and variants of the latter with disordered edges.
-By diagonalizing the Hamiltonian, we find the Majorana energy $E_\textrm{M}$ and the energy of the first excited state $E_1$, the lowest and second lowest energies, respectively.
-Using the eigenstates, we calculate the Majorana decay length $\xi_\textrm{M}$ by fitting an exponential to the density of a single Majorana wavefunction projected on the $x$-axis.
-To determine $\xi_\textrm{M}$, we use a trick and artificially break the particle-hole symmetry on one edge by adding a potential $V \sigma_0 \tau_0$ such that one of the Majorana states is pushed into the continuum and the fit to $\exp{\frac{x}{\xi_\textrm{M}}}$ becomes easier.
-In figure~\ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.
+We model a finite system to compute the Majorana wave function density for different geometries; ribbon, saw-toothed zigzag, parallel curves, and a variant of the latter with disordered edges.
+In figure~\ref{fig:wave_functions} the wave functions are displayed, superimposed upon their respective geometry.
+By diagonalizing the Hamiltonian, we find the Majorana energy $E_\textrm{M}$ and by using the corresponding eigenstate of that lowest energy, we get the wave function.
+To determine $\xi_\textrm{M}$, we use a trick and artificially break the particle-hole symmetry on one edge by adding a potential $V \sigma_0 \tau_0$ such that one of the Majorana states is pushed into the continuum, then the fit to $\exp{\frac{x}{\xi_\textrm{M}}}$ becomes better.
+Using this system, we then find the Majorana decay length $\xi_\textrm{M}$ by fitting an exponential to the density of the single Majorana wave function projected on the $x$-axis.
 All systems have identical Hamiltonian parameters in order to compare the effects of the changing geometry meaningfully.
@@
 \comment{In a straight system, the Majoranas are very poorly localized.}
-For the ribbon system [Fig.~\ref{fig:wavefunctions}(a)], we see that the decay of the density is long compared to the system size.
-The wavefunction extends to the center of the system, resulting in overlapping Majoranas and a non-zero energy of the state.
-Further, the energy of the Majorana state $E_\textrm{M}$ in the straight system is badly separated from the next lowest lying eigenstate $E_1$.
+For the ribbon system [Fig.~\ref{fig:wave_functions}(a)], we see that the decay of the density is long compared to the system size.
+The wave function extends to the center of the system, resulting in overlapping Majoranas and a non-zero energy of the state.
+Further, the energy of the Majorana state $E_\textrm{M}$ in the straight system is high in comparison with the topological gap $E_\textrm{gap}$.
 Altogether, the increase in the topological gap, but also the before mentioned reduction of the group velocity, result in poorly localized Majoranas and minimal topological protection against perturbations.
@@
 We observe that for zigzag systems the Majorana properties improve.
-All of the zigzag type geometries display a reduced coherence length and the delocalized nature of the wavefunctions is improved, as is visible through the density plots.
-Quantitatively, the improvement in the localization of the Majoranas is also distinctly apparent: the energies of the Majorana states are three orders of magnitude lower than the energy of the second lowest-lying wavefunctions.
+All of the zigzag type geometries display a reduced coherence length and the delocalized nature of the wave functions is improved, as is visible through the density plots.
+Quantitatively, the improvement in the localization of the Majoranas is also distinctly apparent: the energies of the Majorana states are three orders of magnitude lower than the energy of the second lowest-lying wave functions.
 As mentioned in section \ref{sec:band_structures}, this can be attributed to the way the energy gap and velocity factor into the Majorana coherence length which scales with these parameters $\xi_\textrm{M}=\hbar\frac{v_\textrm{F}}{\Delta_\textrm{ind}}$.
@@
 \comment{The specific geometry is not important.}
-The shape of the wavefunctions does not change significantly depending on the details of the geometry.
-The sharp corners of the sawtooth versus the smooth shape of the snakelike system do not have a significant impact on the shape of the wavefunction, and neither do the disordered edges affect the relevant parameters.
+The shape of the wave functions does not change significantly depending on the details of the geometry.
+The sharp corners of the sawtooth versus the smooth shape of the snakelike system do not have a significant impact on the shape of the wave function, and neither do the disordered edges affect the relevant parameters.
 
@@
 In Fig.~\ref{fig:phasediagrams} we plot the energy gap as a function of magnetic field, chemical potential, $E_\textrm{gap}(B_x, \mu)$; and the superconducting phase difference $E_\textrm{gap}(B_x, \phi)$ for both a straight system [(c) and (e)] and a zigzag system [(d) and (f)].
-Additionally, we plot the first $\SI{1300}{\nm}$ (one zigzag period) of the wavefunctions [(a) and (b)] at the most optimal point in parameter space for the straight system.
+Additionally, we plot the first $\SI{1300}{\nm}$ (one zigzag period) of the wave functions [(a) and (b)] at the most optimal point in parameter space for the straight system.
 For the straight system we calculate $E_\textrm{gap}$ by performing a binary search in $E$ for the energy at which the propagating modes start to appear.~\cite{nijholt2015orbital}

### 2019-02-25 paper/snakemajoranas.tex
corrections

@@
 \includegraphics[width=0.75\columnwidth]{figures/zigzag.pdf}
-\caption{Setup of the straight (top) and the zigzag (bottom) SNS junction.
-The yellow areas are the superconductors at an opposite superconducting phase $\pm \phi / 2$.
+\caption{The straight (top) and the zigzag (bottom) SNS junction.
+The yellow areas are superconductors with a phase difference $\phi$ between the top and the bottom..
 The middle area is the semiconductor of width $W$ and has a magnetic field $B$ in the $x$-direction.
@@
 \begin{figure}[!htb]
-\includegraphics[width=\columnwidth]{figures/wave functions}
+\includegraphics[width=\columnwidth]{figures/wavefunctions}
 \caption{Density of wave functions $\left|\psi\right|^2$ for sizes and geometries.
@@
 For the ribbon system [Fig.~\ref{fig:wave_functions}(a)], we see that the decay of the density is long compared to the system size.
-The wave function extends to the center of the system, resulting in overlapping Majoranas and a non-zero energy of the state.
+The wave function extends to the center of the system, resulting in highly overlapping Majoranas and a non-zero energy of the state.
 Further, the energy of the Majorana state $E_\textrm{M}$ in the straight system is high in comparison with the topological gap $E_\textrm{gap}$.
-Altogether, the increase in the topological gap, but also the before mentioned reduction of the group velocity, result in poorly localized Majoranas and minimal topological protection against perturbations.
+Altogether, the small topological gap, but also the before mentioned high velocity, result in poorly localized Majoranas and minimal topological protection against perturbations.
 % TODO: probably put the eq for coherence length here?
@@
 All of the zigzag type geometries display a reduced coherence length and the delocalized nature of the wave functions is improved, as is visible through the density plots.
-Quantitatively, the improvement in the localization of the Majoranas is also distinctly apparent: the energies of the Majorana states are three orders of magnitude lower than the energy of the second lowest-lying wave functions.
+Quantitatively, the improvement in the localization of the Majoranas is also distinctly apparent: the energies of the Majorana states are three orders of magnitude lower than the topological gap.
 As mentioned in section \ref{sec:band_structures}, this can be attributed to the way the energy gap and velocity factor into the Majorana coherence length which scales with these parameters $\xi_\textrm{M}=\hbar\frac{v_\textrm{F}}{\Delta_\textrm{ind}}$.

### 2019-02-25 paper/snakemajoranas.tex
improve figure 1 caption

@@
 From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
-Additionally, these long trajectories have long flight times $\tau_f \approx L_\textrm{t} / v_F$ (see Fig.~\ref{fig:setup}), where $L_\textrm{t}$ is the trajectory length.
-Equivalently, the Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$ are small, resulting in a small gap.
+Additionally, these long trajectories have long flight times $\tau_\textrm{f} \approx L_\textrm{t} / v_F$ (see Fig.~\ref{fig:setup}), where $L_\textrm{t}$ is the trajectory length.
+Equivalently, the Thouless energies $E_{\textrm{Th}}=\hbar / \tau_\textrm{f}$ are small, resulting in a small gap.
 This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, so a low filling of the bands is a workaround\cite{nijholt2015orbital}.
@@
 \caption{The straight (top) and the zigzag (bottom) SNS junction.
-The yellow areas are superconductors with a phase difference $\phi$ between the top and the bottom..
-The middle area is the semiconductor of width $W$ and has a magnetic field $B$ in the $x$-direction.
-The modulation of the zigzag is parameterized by its amplitude $z_y$ and period $z_x$.
-Inside the semiconductor we indicate the longest possible trajectory by the red curve.
+The yellow areas are superconductors with a phase difference $\phi$ between the top and the bottom.
+The middle area is the semiconductor of width $W$.
+Only the semiconductor has a magnetic field $B$ pointing in the $x$-direction.
+The zigzag pattern has a peak-to-peak amplitude $z_y$ and a period $2 z_x$.
+A trajectory traveling at a grazing angle (red curve) has a very long flight time $\tau_\textrm{f}$ and a very small induced gap $E_\textrm{gap}$.
+At the same time, the zigzag geometry limits the length of a trajectory therefore lowering $\tau_\textrm{f}$ and increasing $E_\textrm{gap}$.
 \label{fig:setup}}

### 2019-02-25 paper/snakemajoranas.tex
change sentence order

@@
 \caption{The straight (top) and the zigzag (bottom) SNS junction.
+The zigzag pattern has a peak-to-peak amplitude $z_y$ and a period $2 z_x$.
 The yellow areas are superconductors with a phase difference $\phi$ between the top and the bottom.
 The middle area is the semiconductor of width $W$.
-Only the semiconductor has a magnetic field $B$ pointing in the $x$-direction.
-The zigzag pattern has a peak-to-peak amplitude $z_y$ and a period $2 z_x$.
+A magnetic field $B$ pointing in the $x$-direction causes a Zeeman splitting in the semiconductor
 A trajectory traveling at a grazing angle (red curve) has a very long flight time $\tau_\textrm{f}$ and a very small induced gap $E_\textrm{gap}$.

### 2019-02-25 paper/snakemajoranas.tex
Typo fixed

@@
 Majorana bound states are a promising candidate to form the basis of a stable platform for topological quantum computing. ~\cite{alicea2012new,beenakker2013search}
-The current experimental effort ~\cite{mourik_signatures_2012,das_zero-bias_2012,deng_anomalous_2012,churchill_superconductor-nanowire_2013,zhang2018quantized} focuses on creating pairs of Majorana bound states in hybrid normal-superconductor (NS) nanowires structures.
+The current experimental effort ~\cite{mourik_signatures_2012,das_zero-bias_2012,deng_anomalous_2012,churchill_superconductor-nanowire_2013,zhang2018quantized} focuses on creating pairs of Majorana bound states in hybrid normal-superconductor (NS) nanowire structures.
 

### 2019-02-25 paper/snakemajoranas.tex
edit band structure caption

@@
 \includegraphics[width=\columnwidth]{figures/bandstructures}
-\caption{Figure of the band stuctures corresponding to the system in Fig.~\ref{fig:setup} with different zigzag amplitudes.
+\caption{Band stuctures corresponding to the system in Fig.~\ref{fig:setup} with different zigzag amplitudes.
 The blue lines correspond to $\phi=0$, $B=0$ (trivial phase) and the orange lines to $\phi=\pi$, $B = \SI{1}{T}$ (topological phase).
@@
 For the right-hand side of (a) ($k_x > 0$), (b), and (c), the folding is the same, such that the velocity $v=\frac{dE}{dk}$ can be compared visually.
-We observe that once there are no more straight trajectories inside the junction (when $z_y=W$) the spectrum becomes most insensitive to the momentum $k_x$, and thus the $v_\textrm{F}$ decreases.
+We observe that once there are no more straight trajectories inside the junction (when $z_y=W$) the spectrum becomes insensitive to the momentum $k_x$ and equivalently, $v_\textrm{F}$ decreases.
 As the zigzag amplitude increases the band gap $E_\textrm{gap}$ increases by an order of magnitude.
@@
 The parameters values are written at the end of Sec.~\ref{sec:setup}.\label{fig:band_structures}}
-% TODO: mention z_x!
 \end{figure}

### 2019-02-25 paper/snakemajoranas.tex
wf caption rewrite

@@
 \includegraphics[width=\columnwidth]{figures/wavefunctions}
-\caption{Density of wave functions $\left|\psi\right|^2$ for sizes and geometries.
+\caption{Density of Majorana wave functions $\left|\psi\right|^2$ for sizes and geometries.
 With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) similar to (c) but with disordered edges.
 Inside the figure, we indicate the Majorana length (or coherence length) $\xi_\textrm{M}$, the Majorana energy $E_\textrm{M}$ (the energy of the first excited state), and the topological energy gap $E_\textrm{gap}$.
-We observe that $\xi_\textrm{M}$ for (a) is almost two orders of magnitude longer and $E_\textrm{gap}$ more than an order of magnitude smaller than for (b), (c), and (d).
-The robustness of $E_\textrm{gap}$ and $\xi_\textrm{M}$ across (b), (c), and (d) means that the details of the geometry do not matter for the improvements to occur.
+We observe that $\xi_\textrm{M}$ for the straight system is almost two orders of magnitude longer and $E_\textrm{gap}$ more than an order of magnitude smaller than for the zigzag systems.
+The robustness of $E_\textrm{gap}$ and $\xi_\textrm{M}$ across the zigzag geometries means that the details of the geometry do not matter for the improvements to occur.
 The length of the system is $3.5 z_x=\SI{4550}{\nm}$, the remaining parameters values are written at the end of Sec.~\ref{sec:setup}.\label{fig:wave_functions}}

### 2019-02-25 paper/snakemajoranas.tex
no frac inline and text changes

@@
 \includegraphics[width=\columnwidth]{figures/bandstructures}
-\caption{Band stuctures corresponding to the system in Fig.~\ref{fig:setup} with different zigzag amplitudes.
-The blue lines correspond to $\phi=0$, $B=0$ (trivial phase) and the orange lines to $\phi=\pi$, $B = \SI{1}{T}$ (topological phase).
-The three subplots are for different amplitudes of the zigzag, with (a) a straight system $z_y=0$, (b) $z_y=\frac{W}{2}$, and (c) $z_y=W$, where $W=\SI{200}{\nm}$ is the junction width.
-On the $x$-axis is the folded lattice momentum where $z_x=\SI{1300}{\nm}$.
+\caption{Band stuctures of the system in Fig.~\ref{fig:setup}(b) with different zigzag amplitudes.
+The blue lines correspond to a trivial phase ($\phi=0$, $B=0$) and the orange lines to a topological phase ($\phi=\pi$, $B = \SI{1}{T}$).
+The three subplots are for different amplitudes of the zigzag, with (a) a straight system $z_y=0$, (b) $z_y=W/2$, and (c) $z_y=W$, where $W=\SI{200}{\nm}$ is the junction width.
+On the $x$-axis is the Bloch momentum where $z_x=\SI{1300}{\nm}$.
 Subplot (a) has a different scale on the $x$-axis for $k_x < 0$ than the other subplots and displays the unfolded band structure.
-For the right-hand side of (a) ($k_x > 0$), (b), and (c), the folding is the same, such that the velocity $v=\frac{dE}{dk}$ can be compared visually.
+For the right-hand side of (a) ($k_x > 0$), (b), and (c), the folding is the same, such that the velocity $v=dE/dk$ can be compared visually.
 We observe that once there are no more straight trajectories inside the junction (when $z_y=W$) the spectrum becomes insensitive to the momentum $k_x$ and equivalently, $v_\textrm{F}$ decreases.
 As the zigzag amplitude increases the band gap $E_\textrm{gap}$ increases by an order of magnitude.
-The combination of these ensures a significant decrease of the Majorana decay length because $\xi_M \propto \frac{v_\textrm{F}}{E_\textrm{gap}}$
-The parameters values are written at the end of Sec.~\ref{sec:setup}.\label{fig:band_structures}}
+The combination of these ensures a significant decrease of the Majorana decay length because $\xi_M \propto v_\textrm{F}/E_\textrm{gap}$
+The parameter values are written at the end of Sec.~\ref{sec:setup}.\label{fig:band_structures}}
 \end{figure}
@@
 By diagonalizing the Hamiltonian, we find the Majorana energy $E_\textrm{M}$ and by using the corresponding eigenstate of that lowest energy, we get the wave function.
-To determine $\xi_\textrm{M}$, we use a trick and artificially break the particle-hole symmetry on one edge by adding a potential $V \sigma_0 \tau_0$ such that one of the Majorana states is pushed into the continuum, then the fit to $\exp{\frac{x}{\xi_\textrm{M}}}$ becomes better.
+To determine $\xi_\textrm{M}$, we use a trick and artificially break the particle-hole symmetry on one edge by adding a potential $V \sigma_0 \tau_0$ such that one of the Majorana states is pushed into the continuum, then the fit to $\exp{x / \xi_\textrm{M}}$ becomes more robust.
 Using this system, we then find the Majorana decay length $\xi_\textrm{M}$ by fitting an exponential to the density of the single Majorana wave function projected on the $x$-axis.
@@
 Quantitatively, the improvement in the localization of the Majoranas is also distinctly apparent: the energies of the Majorana states are three orders of magnitude lower than the topological gap.
-As mentioned in section \ref{sec:band_structures}, this can be attributed to the way the energy gap and velocity factor into the Majorana coherence length which scales with these parameters $\xi_\textrm{M}=\hbar\frac{v_\textrm{F}}{\Delta_\textrm{ind}}$.
+As mentioned in section \ref{sec:band_structures}, this can be attributed to the way the energy gap and velocity factor into the Majorana coherence length which scales with these parameters $\xi_\textrm{M}=\hbar v_\textrm{F} / \Delta_\textrm{ind}$.
 Additionally, the reduction of the Majorana decay length allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.

### 2019-02-25 paper/snakemajoranas.tex
fix typo

@@
 The robustness of $E_\textrm{gap}$ and $\xi_\textrm{M}$ across the zigzag geometries means that the details of the geometry do not matter for the improvements to occur.
-The length of the system is $3.5 z_x=\SI{4550}{\nm}$, the remaining parameters values are written at the end of Sec.~\ref{sec:setup}.\label{fig:wave_functions}}
+The length of the system is $3.5 z_x=\SI{4550}{\nm}$, the remaining parameter values are written at the end of Sec.~\ref{sec:setup}.\label{fig:wave_functions}}
 \end{figure}
@@
 Additionally, in subplot (c) we overlay the phase boundaries.
-The remaining parameters values are written at the end of Sec.~\ref{sec:setup}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
+The remaining parameter values are written at the end of Sec.~\ref{sec:setup}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
 \label{fig:phasediagrams}}

### 2019-02-25 paper/snakemajoranas.tex
spell check

@@
 \begin{abstract}
-High density superconductor-semiconductor-superconductor junctions have a small induced superconducting gap due to the quasiparticle trajectories with a large momentum parallel to the junction, because these trajectories have a very long flight time.
+High density superconductor-semiconductor-superconductor junctions have a small induced superconducting gap due to the quasiparticle trajectories with a large momentum parallel to the junction because these trajectories have a very long flight time.
 Because a large induced gap protects Majorana modes, these long trajectories constrain Majorana devices to low electron density.
@@
 However, low filling requires precise knowledge of the system and might be more sensitive to disorder or microscopic inhomogeneities.
-On the other hand, disorder scatters these long trajectories and introduces a cut-off on the scale of the mean-free path~\cite{haim_double-edge_2018}, however, disorder is impossible to control to a required precision experimentally.
+On the other hand, disorder scatters these long trajectories and introduces a cut-off on the scale of the mean-free path~\cite{haim_double-edge_2018}; however, disorder is impossible to control to a required precision experimentally.
 
@@
 The zigzag pattern has a peak-to-peak amplitude $z_y$ and a period $2 z_x$.
-The yellow areas are superconductors with a phase difference $\phi$ between the top and the bottom.
+The yellow areas are superconductors with a phase difference of $\phi$ between the top and the bottom.
 The middle area is the semiconductor of width $W$.
@@
 
-\comment{A alternative has been proposed.}
+\comment{An alternative has been proposed.}
 Recently, a system with a modification has been proposed\cite{pientka2017topological}, where instead of having one superconductor, there are two superconductors, creating a superconductors-normal-superconductor (SNS) junction.
@@
 \comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
-We propose a new experimental setup (see Fig.~\ref{fig:setup}(b)) for the creation of Majoranas that eliminating long trajectories and therefore prevents the appearance of a soft gap, while while also increasing the topological gap by several orders of magnitude, depending on the parameters.
+We propose a new experimental setup (see Fig.~\ref{fig:setup}(b)) for the creation of Majoranas that eliminating long trajectories and therefore prevents the appearance of a soft gap, while also increasing the topological gap by several orders of magnitude, depending on the parameters.
 The setup consists of a zigzag or snake-like geometry for the semiconductor where long trajectories are not possible due to the geometry.
-In this paper we will focus on two-dimensional (2D) Josephson junctions, however, a zigzag geometry will also work for nanowires.\footnote{We confirmed this numerically, although it is not included in this paper.}
+In this paper we will focus on two-dimensional (2D) Josephson junctions; however, a zigzag geometry will also work for nanowires.\footnote{We confirmed this numerically, although it is not included in this paper.}
 
@@
 The superconductor has a superconducting coupling term $\Delta$ with the pair of superconductors at an opposite superconducting phase $\exp{\pm i \phi/2}$.
-Both the normal part and the superconducters have a kinetic term and chemical potential $\mu$.
+Both the normal part and the superconductors have a kinetic term and chemical potential $\mu$.
 The complete Hamiltonian has the form
@@
 We observe that once there are no more straight trajectories inside the junction (when $z_y=W$) the spectrum becomes insensitive to the momentum $k_x$ and equivalently, $v_\textrm{F}$ decreases.
-As the zigzag amplitude increases the band gap $E_\textrm{gap}$ increases by an order of magnitude.
+As the zigzag amplitude increases, the band gap $E_\textrm{gap}$ increases by an order of magnitude.
 The combination of these ensures a significant decrease of the Majorana decay length because $\xi_M \propto v_\textrm{F}/E_\textrm{gap}$
@@
 Because of the large periodicity of the zigzag and the resulting large supercell, the band structure is heavily folded.
-In figure~\ref{fig:band_structures} we show the resulting band structures for zigzag systems with a varying amplitude.
+In figure~\ref{fig:band_structures} we show the resulting band structures for zigzag systems with varying amplitude.
 The introduction of the zigzag has a striking effect: the bands flatten out and the topological gap increases by more than an order of magnitude.
@@
 This confirms our expectation that the zigzag removes trajectories propagating at grazing angles.
-In the unfolded band structure for a straight system, as seen in Fig.~\ref{fig:band_structures}(a), the gap in a straight system occurs around $k_F$ and because the zigzag cuts off long trajectories, the gap size increases.
+In the unfolded band structure for a straight system, as seen in Fig.~\ref{fig:band_structures}(a), the gap in a straight system occurs around $k_F$, and because the zigzag cuts off long trajectories, the gap size increases.
 Besides this, the states from different segments of the zigzag pattern have a negligible overlap and therefore have a vanishing velocity.
@@
 \caption{Density of Majorana wave functions $\left|\psi\right|^2$ for sizes and geometries.
-With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) similar to (c) but with disordered edges.
+With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where lines parallel to a sinusoid defines the normal region, and (d) similar to (c) but with disordered edges.
 Inside the figure, we indicate the Majorana length (or coherence length) $\xi_\textrm{M}$, the Majorana energy $E_\textrm{M}$ (the energy of the first excited state), and the topological energy gap $E_\textrm{gap}$.
@@
 In figure~\ref{fig:wave_functions} the wave functions are displayed, superimposed upon their respective geometry.
-By diagonalizing the Hamiltonian, we find the Majorana energy $E_\textrm{M}$ and by using the corresponding eigenstate of that lowest energy, we get the wave function.
+By diagonalizing the Hamiltonian, we find the Majorana energy $E_\textrm{M}$, and by using the corresponding eigenstate of that lowest energy, we get the wave function.
 To determine $\xi_\textrm{M}$, we use a trick and artificially break the particle-hole symmetry on one edge by adding a potential $V \sigma_0 \tau_0$ such that one of the Majorana states is pushed into the continuum, then the fit to $\exp{x / \xi_\textrm{M}}$ becomes more robust.
 Using this system, we then find the Majorana decay length $\xi_\textrm{M}$ by fitting an exponential to the density of the single Majorana wave function projected on the $x$-axis.
-All systems have identical Hamiltonian parameters in order to compare the effects of the changing geometry meaningfully.
+All systems have identical Hamiltonian parameters to compare the effects of the changing geometry meaningfully.
 
@@
 We observe that for zigzag systems the Majorana properties improve.
-All of the zigzag type geometries display a reduced coherence length and the delocalized nature of the wave functions is improved, as is visible through the density plots.
+All of the zigzag type geometries display a reduced coherence length, and the delocalized nature of the wave functions is improved, as is visible through the density plots.
 Quantitatively, the improvement in the localization of the Majoranas is also distinctly apparent: the energies of the Majorana states are three orders of magnitude lower than the topological gap.
@@
 
-\comment{Disorder has a similar effect but one has no control over it.}
+\comment{Disorder has a similar effect, but one has no control over it.}
 Recently, it has been shown~\cite{haim_double-edge_2018} that having a system with weak disorder can lead to a reduction in the Majorana decay length, similar to what happens with the introduction of a zigzag geometry.
@@
 \comment{Extensions: we omit several physical effects, disorder, electrostatics, etc.}
-Finally, we exclude several physical effects, such as disorder, electrostatics, the orbital effect, the finite thickness of the sample, and electron-electron interactions, however, we expect these to be second or higher order effects which will not alter our conclusions.
+Finally, we exclude several physical effects, such as disorder, electrostatics, the orbital effect, the finite thickness of the sample, and electron-electron interactions; however, we expect these to be second or higher order effects which will not alter our conclusions.
 

### 2019-02-25 paper/snakemajoranas.tex
go over todos

@@
 The introduction of a zigzag geometry increases the topological gap by over an order of magnitude, as well as offering a substantial reduction of the Majorana length, which enables experimentalists to create significantly shorter devices.
-% The Majorana size $\xi_\textrm{M}$ and $E_\textrm{gap}$ are more than an order of magnitude better for the zigzag system, even though these are plotted for the optimal parameters for the straight system at $\mu=\SI{10}{\meV}$.
-% From phase diagram figure
+The improvements occur regardless of any particular parameter values, moreover, even when using the parameter values of the optimal gap in the straight system (Fig.~\ref{fig:phasediagrams}), the Majorana size $\xi_\textrm{M}$ and $E_\textrm{gap}$ are still more than an order of magnitude better for the zigzag system.
 Additionally, the breaking of BDI symmetry into D symmetry results in a cleaner and more stable topological region.

### 2019-02-25 paper/snakemajoranas.tex
Majorana decay length -> Majorana size, everywhere

@@
 As the zigzag amplitude increases, the band gap $E_\textrm{gap}$ increases by an order of magnitude.
-The combination of these ensures a significant decrease of the Majorana decay length because $\xi_M \propto v_\textrm{F}/E_\textrm{gap}$
+The combination of these ensures a significant decrease of the Majorana size because $\xi_M \propto v_\textrm{F}/E_\textrm{gap}$
 The parameter values are written at the end of Sec.~\ref{sec:setup}.\label{fig:band_structures}}
@@
 By diagonalizing the Hamiltonian, we find the Majorana energy $E_\textrm{M}$, and by using the corresponding eigenstate of that lowest energy, we get the wave function.
-To determine $\xi_\textrm{M}$, we use a trick and artificially break the particle-hole symmetry on one edge by adding a potential $V \sigma_0 \tau_0$ such that one of the Majorana states is pushed into the continuum, then the fit to $\exp{x / \xi_\textrm{M}}$ becomes more robust.
-Using this system, we then find the Majorana decay length $\xi_\textrm{M}$ by fitting an exponential to the density of the single Majorana wave function projected on the $x$-axis.
+To determine $\xi_\textrm{M}$, we use a trick and artificially break the particle-hole symmetry on one edge by adding a potential $V \sigma_0 \tau_0$ such that one of the Majorana states is pushed into the continuum.
+Using this system, we then find the Majorana size $\xi_\textrm{M}$ by fitting an exponential to the density of the single Majorana wave function projected on the $x$-axis.
 All systems have identical Hamiltonian parameters to compare the effects of the changing geometry meaningfully.
@@
 \comment{In a straight system, the Majoranas are very poorly localized.}
-For the ribbon system [Fig.~\ref{fig:wave_functions}(a)], we see that the decay of the density is long compared to the system size.
+For the straight system [Fig.~\ref{fig:wave_functions}(a)], we see that the decay of the density is long compared to the system size.
 The wave function extends to the center of the system, resulting in highly overlapping Majoranas and a non-zero energy of the state.
@@
 As mentioned in section \ref{sec:band_structures}, this can be attributed to the way the energy gap and velocity factor into the Majorana coherence length which scales with these parameters $\xi_\textrm{M}=\hbar v_\textrm{F} / \Delta_\textrm{ind}$.
-Additionally, the reduction of the Majorana decay length allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.
+Additionally, the reduction of the Majorana size allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.
 
@@
 \comment{Disorder has a similar effect, but one has no control over it.}
-Recently, it has been shown~\cite{haim_double-edge_2018} that having a system with weak disorder can lead to a reduction in the Majorana decay length, similar to what happens with the introduction of a zigzag geometry.
+Recently, it has been shown~\cite{haim_double-edge_2018} that having a system with weak disorder can lead to a reduction in the Majorana size, similar to what happens with the introduction of a zigzag geometry.
 However, in contrast to introducing weak disorder into a system, changing the geometry is experimentally much easier to realize and therefore easier to control.

### 2019-02-25 paper/snakemajoranas.tex
explain how we get xi_M

@@
 By diagonalizing the Hamiltonian, we find the Majorana energy $E_\textrm{M}$, and by using the corresponding eigenstate of that lowest energy, we get the wave function.
-To determine $\xi_\textrm{M}$, we use a trick and artificially break the particle-hole symmetry on one edge by adding a potential $V \sigma_0 \tau_0$ such that one of the Majorana states is pushed into the continuum.
+To determine $\xi_\textrm{M}$ for the zigzag systems, we use a trick and artificially break the particle-hole symmetry on one edge by adding a potential $V \sigma_0 \tau_0$ such that one of the Majorana states is pushed into the continuum.
 Using this system, we then find the Majorana size $\xi_\textrm{M}$ by fitting an exponential to the density of the single Majorana wave function projected on the $x$-axis.
+This method is numerically not feasible for a straight system because the decay length is too long.
+Instead, we find $\xi_\textrm{M}$ through the eigenvalue decomposition of the translation operator at zero energy as described in Ref.~\onlinecite{nijholt2015orbital}.
 All systems have identical Hamiltonian parameters to compare the effects of the changing geometry meaningfully.

### 2019-02-25 paper/snakemajoranas.tex
2z_x -> z_x
add todo
italic et al.

@@
 \caption{The straight (top) and the zigzag (bottom) SNS junction.
-The zigzag pattern has a peak-to-peak amplitude $z_y$ and a period $2 z_x$.
+The zigzag pattern has a peak-to-peak amplitude $z_y$ and a period $z_x$.
 The yellow areas are superconductors with a phase difference of $\phi$ between the top and the bottom.
@@
 As mentioned in section \ref{sec:band_structures}, this can be attributed to the way the energy gap and velocity factor into the Majorana coherence length which scales with these parameters $\xi_\textrm{M}=\hbar v_\textrm{F} / \Delta_\textrm{ind}$.
+% TODO: make this an Eq?
+And Replace Delta_ind by E_gap?
 Additionally, the reduction of the Majorana size allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.
@@
 \comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry.}
-Similar to what is described by Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond-like shape as a function of phase $\phi$ and magnetic field $B_x$.
+Similar to what is described by Pientka \textit{et al.}~\cite{pientka2017topological}, we see that the ribbon topology has a diamond-like shape as a function of phase $\phi$ and magnetic field $B_x$.
 We also observe additional gap closings which are due to the BDI symmetry that is present.

### 2019-02-26 paper/snakemajoranas.tex
rewrite last paragraph of Sec IV

@@
 
-\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag.}
-We observe that for zigzag systems the Majorana properties improve.
-All of the zigzag type geometries display a reduced coherence length, and the delocalized nature of the wave functions is improved, as is visible through the density plots.
-Quantitatively, the improvement in the localization of the Majoranas is also distinctly apparent: the energies of the Majorana states are three orders of magnitude lower than the topological gap.
-As mentioned in section \ref{sec:band_structures}, this can be attributed to the way the energy gap and velocity factor into the Majorana coherence length which scales with these parameters $\xi_\textrm{M}=\hbar v_\textrm{F} / \Delta_\textrm{ind}$.
-% TODO: make this an Eq?
-And Replace Delta_ind by E_gap?
+\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag independent of details}
+We observe that for zigzag systems the Majorana properties improve independent of the details of the specific geometry.
+All of the zigzag type geometries display a significantly reduced Majorana size which improves the localization of the Majorana wave functions as is visible in the density plots.
+The Majorana size $\xi_\textrm{M}$ improves by a factor ~70 and is localized within one segment of the zigzag.
+Further, the topological gap is an order of magnitude lower, and as mentioned in section \ref{sec:band_structures}, this can be attributed to the way the energy gap and velocity factor into the Majorana coherence length which scales with these parameters $\xi_\textrm{M}=\hbar v_\textrm{F} / \Delta_\textrm{ind}$.
 Additionally, the reduction of the Majorana size allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.
-
-\comment{The specific geometry is not important.}
-The shape of the wave functions does not change significantly depending on the details of the geometry.
-The sharp corners of the sawtooth versus the smooth shape of the snakelike system do not have a significant impact on the shape of the wave function, and neither do the disordered edges affect the relevant parameters.
 

### 2019-02-26 paper/snakemajoranas.tex
rewrite more of the last paragraph of Sec IV

@@
 Further, the energy of the Majorana state $E_\textrm{M}$ in the straight system is high in comparison with the topological gap $E_\textrm{gap}$.
-Altogether, the small topological gap, but also the before mentioned high velocity, result in poorly localized Majoranas and minimal topological protection against perturbations.
-% TODO: probably put the eq for coherence length here?
+Altogether, the small topological gap, but also the before mentioned high velocity, result in poorly localized Majoranas and minimal topological protection against perturbations because
+
+\begin{equation}
+\label{eq:xi_M}
+\xi_\textrm{M}=\hbar \frac{v_\textrm{F}}{\Delta_\textrm{ind}}.
+\end{equation}
 
@@
 The Majorana size $\xi_\textrm{M}$ improves by a factor ~70 and is localized within one segment of the zigzag.
-Further, the topological gap is an order of magnitude lower, and as mentioned in section \ref{sec:band_structures}, this can be attributed to the way the energy gap and velocity factor into the Majorana coherence length which scales with these parameters $\xi_\textrm{M}=\hbar v_\textrm{F} / \Delta_\textrm{ind}$.
-Additionally, the reduction of the Majorana size allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.
+Further, the topological gap is an order of magnitude higher, and as mentioned in section \ref{sec:band_structures}, the velocity is an order of magnitude lower.
+Both of these parameters ensure that $\xi_\textrm{M}$ is greatly improved (Eq.~\eqref{eq:xi_M}).
+Finally, the reduction of the Majorana size allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.
 

### 2019-02-26 paper/snakemajoranas.tex
small changes

@@
 \includegraphics[width=\columnwidth]{figures/wavefunctions}
-\caption{Density of Majorana wave functions $\left|\psi\right|^2$ for sizes and geometries.
+\caption{Density of Majorana wave functions $\left| \psi_\textrm{M} \right|^2$ for sizes and geometries.
 With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where lines parallel to a sinusoid defines the normal region, and (d) similar to (c) but with disordered edges.
@@
 We model a finite system to compute the Majorana wave function density for different geometries; ribbon, saw-toothed zigzag, parallel curves, and a variant of the latter with disordered edges.
-In figure~\ref{fig:wave_functions} the wave functions are displayed, superimposed upon their respective geometry.
+In figure~\ref{fig:wave_functions} the Majorana wave function densities $\left| \psi_\textrm{M} \right|^2$ are displayed, superimposed upon their respective geometry.
 By diagonalizing the Hamiltonian, we find the Majorana energy $E_\textrm{M}$, and by using the corresponding eigenstate of that lowest energy, we get the wave function.
@@
 The Majorana size $\xi_\textrm{M}$ improves by a factor ~70 and is localized within one segment of the zigzag.
-Further, the topological gap is an order of magnitude higher, and as mentioned in section \ref{sec:band_structures}, the velocity is an order of magnitude lower.
+Further, the topological gap $E_\textrm{gap}$ is an order of magnitude higher, and as mentioned in section \ref{sec:band_structures}, the velocity $v_\textrm{F}$ is an order of magnitude lower.
 Both of these parameters ensure that $\xi_\textrm{M}$ is greatly improved (Eq.~\eqref{eq:xi_M}).

### 2019-02-26 paper/snakemajoranas.tex
review with Anton part 1

@@
 \comment{Hybrid NS structures become topological and are useful for TQC.}
-A hybrid structure containing a semiconductor with strong spin-orbit coupling coupled to a superconductor, inside a magnetic field becomes topological within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple nanowire), while Majorana bound states appear on its edges.~\cite{lutchyn_majorana_2010,oreg_helical_2010}
+A hybrid structure containing a semiconductor with strong spin-orbit coupling coupled to a superconductor, inside a magnetic field becomes topological within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple nanowire), and Majorana bound states appear on its edges.~\cite{lutchyn_majorana_2010,oreg_helical_2010}
 Majorana bound states are a promising candidate to form the basis of a stable platform for topological quantum computing. ~\cite{alicea2012new,beenakker2013search}
 The current experimental effort ~\cite{mourik_signatures_2012,das_zero-bias_2012,deng_anomalous_2012,churchill_superconductor-nanowire_2013,zhang2018quantized} focuses on creating pairs of Majorana bound states in hybrid normal-superconductor (NS) nanowire structures.
+
+\comment{SNS junctions also work and require smaller field.}
+Recently, a modified setup has been proposed\cite{pientka2017topological}, where instead of having one superconductor, there are two superconductors, creating a superconductor-normal-superconductor (SNS) junction.
+The additional superconductor adds an extra knob to adjust, the superconducting phase difference $\phi$, and this should make it easier to tune the system into the topological phase.
+Recently, two groups~\cite{fornieri_evidence_2018,ren_topological_2018} have realized this system experimentally.
+In practice, multiple problems arise making even the observation difficult, rendering the manipulation of Majoranas in the near future, improbable.
 
@@
 Equivalently, the Thouless energies $E_{\textrm{Th}}=\hbar / \tau_\textrm{f}$ are small, resulting in a small gap.
-This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, so a low filling of the bands is a workaround\cite{nijholt2015orbital}.
-However, low filling requires precise knowledge of the system and might be more sensitive to disorder or microscopic inhomogeneities.
+This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, making a low filling of the bands a possible workaround\cite{nijholt2015orbital}.
+However, low filling requires precise knowledge of the system and is more sensitive to disorder or microscopic inhomogeneities.
 On the other hand, disorder scatters these long trajectories and introduces a cut-off on the scale of the mean-free path~\cite{haim_double-edge_2018}; however, disorder is impossible to control to a required precision experimentally.
@@
 
-\comment{An alternative has been proposed.}
-Recently, a system with a modification has been proposed\cite{pientka2017topological}, where instead of having one superconductor, there are two superconductors, creating a superconductors-normal-superconductor (SNS) junction.
-The additional superconductor adds an extra knob to adjust, the superconducting phase difference $\phi$, and this should make it easier to tune the system into the topological phase.
-Recently, two groups~\cite{fornieri_evidence_2018,ren_topological_2018} have realized this system experimentally.
-In practice, multiple problems arise making even the observation difficult, rendering the manipulation of Majoranas in the near future, improbable.
-
 \comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
-We propose a new experimental setup (see Fig.~\ref{fig:setup}(b)) for the creation of Majoranas that eliminating long trajectories and therefore prevents the appearance of a soft gap, while also increasing the topological gap by several orders of magnitude, depending on the parameters.
+We propose a new experimental setup (see Fig.~\ref{fig:setup}(b)) for the creation of Majoranas that eliminates long trajectories and therefore prevents the appearance of a soft gap, while also increasing the topological gap by more than an orders of magnitude, depending on the parameters.
 The setup consists of a zigzag or snake-like geometry for the semiconductor where long trajectories are not possible due to the geometry.
-In this paper we will focus on two-dimensional (2D) Josephson junctions; however, a zigzag geometry will also work for nanowires.\footnote{We confirmed this numerically, although it is not included in this paper.}
+In this paper we will focus on two-dimensional (2D) Josephson junctions; however, a zigzag geometry will also work with only one superconductor.\footnote{We confirmed this numerically, although it is not included in this paper.}
 
@@
 Similar to the conventional straight system \cite{pientka2017topological}, a magnetic field $B_x$ perpendicular to the junction is applied.
-We model the system with a Bogoliubov-de Gennes Hamiltonian (BdG) Eq.~\eqref{eq:hamiltonian}; the normal part has a linear Rashba spin-orbit coupling term characterized by $\alpha$ and a Zeeman field with $E_z=\frac{1}{2} \mu_B g B_x$.
-The superconductor has a superconducting coupling term $\Delta$ with the pair of superconductors at an opposite superconducting phase $\exp{\pm i \phi/2}$.
-Both the normal part and the superconductors have a kinetic term and chemical potential $\mu$.
-The complete Hamiltonian has the form
+We model the system with a Bogoliubov-de Gennes Hamiltonian (BdG)
 \begin{subequations}
@@
     H_\textrm{N} = & \left[\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu + \alpha \left( \ky \sigma_x - \kx \sigma_y \right) \right] \tau_z
-        + E_\text{z} \sigma_x \\
+        + E_\text{z} \sigma_x, \\
     H_\textrm{SC} = & \left[\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right] \tau_z
@@
 Where $H_\textrm{N}$ and $H_\textrm{SC}$ are the Hamiltonians of the semiconductor and superconductors, respectively.
+Here, the normal part has a linear Rashba spin-orbit coupling term characterized by $\alpha$ and a Zeeman field with $E_z=\frac{1}{2} \mu_B g B_x$.
+The superconductor has a superconducting coupling term $\Delta$ with the pair of superconductors at an opposite superconducting phase $\exp{\pm i \phi/2}$.
+Both the normal part and the superconductors have a kinetic term and chemical potential $\mu$.
+The complete Hamiltonian has the form
 They act on the spinor wave function $\Psi={\left(\psi_{e\uparrow},\psi_{e\downarrow},\psi_{\textrm{h}\downarrow},-\psi_{\textrm{h}\uparrow}\right)}^{T}$, where $\psi_e$, $\psi_\textrm{h}$ are its electron and hole components, and $\psi_\uparrow$, $\psi_\downarrow$ are the spin-up and spin-down components.
 The Pauli matrices $\sigma_{i}$ act on the spin degree of freedom and $\tau_{i}$ act on the electron-hole degree of freedom.
-For the zigzag geometry, we first consider a sawtooth-like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction [see Fig.~\ref{fig:setup}(b)].
+For the zigzag geometry, we first consider a zigzag pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction [see Fig.~\ref{fig:setup}(b)].
 Later in this manuscript, we show that the exact details of the shape are unimportant and consider different zigzag geometries also parametrized by $z_x, \; z_y, \; W$.
@@
 \comment{It is interesting to study what geometry creates an optimal environment for Majorana modes to exist.}
-We have studied sawtooth and snake-like geometries of the semiconductor region, but perhaps a more exotic shape will be optimal.
+We have studied zigzag and snake-like geometries of the semiconductor region, but perhaps a more exotic shape will be optimal.
 A study optimizing the geometry's parameters for supporting Majoranas is an exciting continuation of our research.

### 2019-02-26 paper/snakemajoranas.tex
move a paragraph where it belongs

--- 2019-02-26 paper/snakemajoranas.tex
@@
 \end{figure}
-
-\comment{An alternative has been proposed.}
-Recently, a system with a modification has been proposed\cite{pientka2017topological}, where instead of having one superconductor, there are two superconductors, creating a superconductors-normal-superconductor (SNS) junction.
-The additional superconductor adds an extra knob to adjust, the superconducting phase difference $\phi$, and this should make it easier to tune the system into the topological phase.
-Recently, two groups~\cite{fornieri_evidence_2018,ren_topological_2018} have realized this system experimentally.
-In practice, multiple problems arise making even the observation difficult, rendering the manipulation of Majoranas in the near future, improbable.
 

### 2019-02-26 paper/snakemajoranas.tex
finish reviewing sec IV

--- 2019-02-26 paper/snakemajoranas.tex
@@
 Similar to the conventional straight system \cite{pientka2017topological}, a magnetic field $B_x$ perpendicular to the junction is applied.
-We model the system with a Bogoliubov-de Gennes Hamiltonian (BdG)
+We model the system with a Bogoliubov-de Gennes Hamiltonian (BdG):
 \begin{subequations}
@@
 \end{subequations}
-Where $H_\textrm{N}$ and $H_\textrm{SC}$ are the Hamiltonians of the semiconductor and superconductors, respectively.
-Here, the normal part has a linear Rashba spin-orbit coupling term characterized by $\alpha$ and a Zeeman field with $E_z=\frac{1}{2} \mu_B g B_x$.
-The superconductor has a superconducting coupling term $\Delta$ with the pair of superconductors at an opposite superconducting phase $\exp{\pm i \phi/2}$.
+Here $H_\textrm{N}$ and $H_\textrm{SC}$ are the Hamiltonians of the semiconductor and superconductors, respectively.
+The normal part has a linear Rashba spin-orbit coupling term with strength $\alpha$ and a Zeeman field with $E_z=\frac{1}{2} \mu_B g B_x$.
+The superconductor has a coupling term $\Delta$, and the phases of the superconductors equal to $\pm\phi/2$.
 Both the normal part and the superconductors have a kinetic term and chemical potential $\mu$.
-The complete Hamiltonian has the form
-They act on the spinor wave function $\Psi={\left(\psi_{e\uparrow},\psi_{e\downarrow},\psi_{\textrm{h}\downarrow},-\psi_{\textrm{h}\uparrow}\right)}^{T}$, where $\psi_e$, $\psi_\textrm{h}$ are its electron and hole components, and $\psi_\uparrow$, $\psi_\downarrow$ are the spin-up and spin-down components.
+The BdG Hamiltonian acts on the spinor wave function $\Psi={\left(\psi_{e\uparrow},\psi_{e\downarrow},\psi_{\textrm{h}\downarrow},-\psi_{\textrm{h}\uparrow}\right)}^{T}$, where $\psi_e$, $\psi_\textrm{h}$ are its electron and hole components, and $\psi_\uparrow$, $\psi_\downarrow$ are the spin-up and spin-down components.
 The Pauli matrices $\sigma_{i}$ act on the spin degree of freedom and $\tau_{i}$ act on the electron-hole degree of freedom.
-For the zigzag geometry, we first consider a zigzag pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction [see Fig.~\ref{fig:setup}(b)].
-Later in this manuscript, we show that the exact details of the shape are unimportant and consider different zigzag geometries also parametrized by $z_x, \; z_y, \; W$.
+We consider a zigzag pattern with a period $z_x$, a peak-to-peak amplitude $z_y$, and $W$ the width of the junction [see Fig.~\ref{fig:setup}(b)].
+Later we relax this assumption and show that the exact shape is unimportant.
 
@@
 Unless noted differently, the Hamiltonian parameters are $\alpha=\SI{20}{\meV \nm}$, $g=26$, $\meff=\SI{0.02}{\electronmass}$, $\mu=\SI{10}{\meV}$, $B=\SI{1}{T}$, $\phi=\pi$, and $\Delta=\SI{1}{\meV}$; and the geometry parameters are $W=\SI{200}{\nm}$, the period of the zigzag $z_x=\SI{1300}{\nm}$, the discretization contant $a=\SI{10}{\nm}$, and the lengths of the superconductors $L_\textrm{SC}=\SI{300}{\nm}$.
-% TODO: Tom: L_sc and Delta not compatible?
 
@@
 Because of the large periodicity of the zigzag and the resulting large supercell, the band structure is heavily folded.
-In figure~\ref{fig:band_structures} we show the resulting band structures for zigzag systems with varying amplitude.
+In Fig.~\ref{fig:band_structures} we show the resulting band structures of zigzag systems with varying $z_y$.
 The introduction of the zigzag has a striking effect: the bands flatten out and the topological gap increases by more than an order of magnitude.
@@
 \comment{Zigzag improves the gap and size because of cutting of trajectories and increasing transparency.}
-This confirms our expectation that the zigzag removes trajectories propagating at grazing angles.
-In the unfolded band structure for a straight system, as seen in Fig.~\ref{fig:band_structures}(a), the gap in a straight system occurs around $k_F$, and because the zigzag cuts off long trajectories, the gap size increases.
-Besides this, the states from different segments of the zigzag pattern have a negligible overlap and therefore have a vanishing velocity.
+In the unfolded band structure of a straight system, shown in Fig.~\ref{fig:band_structures}(a), the lowest energy states occur at $k \approx k_F$.
+We interpret the increase of the gap $E_\textrm{gap}$ shown in Fig.~\ref{fig:band_structures}(b) and (c) as an effect of the zigzag geometry removing these long trajectories traveling at grazing angles.
+Besides the increased $E_\textrm{gap}$, the states from different segments of the zigzag pattern have a negligible overlap and therefore have a vanishing velocity.
 This reduction in velocity strongly reduces the Majorana size, as we discuss in section \ref{sec:shape_effects}.
-Additionally, in the presence of normal reflection, due to the presence of NS interfaces at a wide range of angles, the reflected part eventually scatters with a near perpendicular surface.
-This means that for transversal modes the transparency of the NS interface increases.
+Finally, in a zigzag geometry every trajectory encounters a superconductor close to normal incidence.
+Normal incidence has a higher transmission probability for entering the superconductor and therefore a higher Andreev reflection amplitude.
+This provides another mechanism of the gap enhancement.
 
@@
 \comment{We calculate the wave functions and find the Majorana lengths by fitting an exponential.}
-We model a finite system to compute the Majorana wave function density for different geometries; ribbon, saw-toothed zigzag, parallel curves, and a variant of the latter with disordered edges.
-In figure~\ref{fig:wave_functions} the Majorana wave function densities $\left| \psi_\textrm{M} \right|^2$ are displayed, superimposed upon their respective geometry.
+We model a finite system and compute the Majorana wave function in different geometries: ribbon, zigzag, sine-like parallel curves, and a variant of the latter with disordered edges.
 By diagonalizing the Hamiltonian, we find the Majorana energy $E_\textrm{M}$, and by using the corresponding eigenstate of that lowest energy, we get the wave function.
-To determine $\xi_\textrm{M}$ for the zigzag systems, we use a trick and artificially break the particle-hole symmetry on one edge by adding a potential $V \sigma_0 \tau_0$ such that one of the Majorana states is pushed into the continuum.
-Using this system, we then find the Majorana size $\xi_\textrm{M}$ by fitting an exponential to the density of the single Majorana wave function projected on the $x$-axis.
-This method is numerically not feasible for a straight system because the decay length is too long.
-Instead, we find $\xi_\textrm{M}$ through the eigenvalue decomposition of the translation operator at zero energy as described in Ref.~\onlinecite{nijholt2015orbital}.
-All systems have identical Hamiltonian parameters to compare the effects of the changing geometry meaningfully.
+To reduce the finite size effects in determining the Majorana size $\xi_\textrm{M}$ in a zigzag system, we introduce a particle-hole symmetry breaking potential $V \sigma_0 \tau_0$ on one edge, such that one of the Majorana states is pushed away from zero energy.
+We then find $\xi_\textrm{M}$ by fitting an exponential to the density of the single Majorana wave function projected on the $x$-axis.
+In the straight system we use the eigenvalue decomposition of the translation operator at zero energy~\ref{nijholt2015orbital} for performance reasons.
 
-\comment{In a straight system, the Majoranas are very poorly localized.}
-For the straight system [Fig.~\ref{fig:wave_functions}(a)], we see that the decay of the density is long compared to the system size.
-The wave function extends to the center of the system, resulting in highly overlapping Majoranas and a non-zero energy of the state.
-Further, the energy of the Majorana state $E_\textrm{M}$ in the straight system is high in comparison with the topological gap $E_\textrm{gap}$.
-Altogether, the small topological gap, but also the before mentioned high velocity, result in poorly localized Majoranas and minimal topological protection against perturbations because
-
+\comment{In a straight system, the Majoranas are very poorly localized because of small gap and high velocity}
+We show the resulting Majorana wave function densities $\left| \psi_\textrm{M} \right|^2$ in different geometries in Fig.~\ref{fig:wave_functions} using the same Hamiltonian parameter values.
+In the straight system [Fig.~\ref{fig:wave_functions}(a)], we see that the decay of the density is long compared to the system size.
+The small topological gap combined with the high velocity result in a large Majorana size
 \begin{equation}
 \label{eq:xi_M}
-\xi_\textrm{M}=\hbar \frac{v_\textrm{F}}{\Delta_\textrm{ind}}.
+\xi_\textrm{M}=\hbar \frac{v_\textrm{F}}{\Delta_\textrm{ind}},
 \end{equation}
+and therefore a minimal topological protection against perturbations.
+The wave function extends to the center of the system, resulting in highly overlapping Majoranas and a Majorana coupling $E_\textrm{M}$ comparible to $E_\textrm{gap}$.
 
 \comment{In a zigzag geometry Majoranas are localized within one segment of zigzag independent of details}
-We observe that for zigzag systems the Majorana properties improve independent of the details of the specific geometry.
-All of the zigzag type geometries display a significantly reduced Majorana size which improves the localization of the Majorana wave functions as is visible in the density plots.
-The Majorana size $\xi_\textrm{M}$ improves by a factor ~70 and is localized within one segment of the zigzag.
-Further, the topological gap $E_\textrm{gap}$ is an order of magnitude higher, and as mentioned in section \ref{sec:band_structures}, the velocity $v_\textrm{F}$ is an order of magnitude lower.
-Both of these parameters ensure that $\xi_\textrm{M}$ is greatly improved (Eq.~\eqref{eq:xi_M}).
-Finally, the reduction of the Majorana size allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.
+We observe that in zigzag systems the Majorana properties improve independent of specific geometric details.
+All of the zigzag-type geometries have $\xi_\textrm{M}$ improved by a factor $\sim 70$ and have the Majorana wave function localized within one segment of the zigzag.
+Further, the topological gap $E_\textrm{gap}$ is an order of magnitude higher than in the straight junction, and as mentioned in section \ref{sec:band_structures}, the velocity $v_\textrm{F}$ is more than an order of magnitude lower.
 
@@
 Additionally, the breaking of BDI symmetry into D symmetry results in a cleaner and more stable topological region.
+Finally, the reduction of the Majorana size allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.
 

### 2019-02-26 paper/snakemajoranas.tex
finish review with Anton halfway through sec V

@@
 \comment{Hybrid NS structures become topological and are useful for TQC.}
-A hybrid structure containing a semiconductor with strong spin-orbit coupling coupled to a superconductor, inside a magnetic field becomes topological within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple nanowire), and Majorana bound states appear on its edges.~\cite{lutchyn_majorana_2010,oreg_helical_2010}
+A hybrid structure containing a semiconductor with strong spin-orbit coupling coupled to a superconductor, inside a magnetic field becomes topological within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple nanowire), and Majorana bound states appear on its edges~\cite{lutchyn_majorana_2010,oreg_helical_2010}.
 Majorana bound states are a promising candidate to form the basis of a stable platform for topological quantum computing. ~\cite{alicea2012new,beenakker2013search}
@@
 We consider a Josephson junction (Fig.~\ref{fig:setup}) consisting of a 2D strip of semiconductor, with superconductors on both sides.
-We modulate the shape of the normal region, which can be either saw-toothed zigzag as depicted [Fig.~\ref{fig:setup}(b)], or a more smooth sinusoidal-like shape.
+We modulate the shape of the normal region, which can be either zigzag as depicted [Fig.~\ref{fig:setup}(b)], or a more smooth sinusoidal-like shape.
 Similar to the conventional straight system \cite{pientka2017topological}, a magnetic field $B_x$ perpendicular to the junction is applied.
@@
 We discretize our continuum Hamiltonian [Eq.~\eqref{eq:hamiltonian}] on a square grid and implement a tight-binding model using Kwant~\cite{groth_kwant:_2014}.
-To preferentially sample important regions of parameter space, we use the Adaptive package.~\cite{adaptive}
+To preferentially sample important regions of parameter space, we use the Adaptive package~\cite{adaptive}.
 The entire source code and the resulting raw data are available in Ref.~\onlinecite{data}.  % TODO: update the bib when the data is uploaded
@@
 \caption{Density of Majorana wave functions $\left| \psi_\textrm{M} \right|^2$ for sizes and geometries.
-With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where lines parallel to a sinusoid defines the normal region, and (d) similar to (c) but with disordered edges.
+With (a) a straight system, (b) a zigzag system, (c) a system where lines parallel to a sinusoid defines the normal region, and (d) similar to (c) but with disordered edges.
 Inside the figure, we indicate the Majorana length (or coherence length) $\xi_\textrm{M}$, the Majorana energy $E_\textrm{M}$ (the energy of the first excited state), and the topological energy gap $E_\textrm{gap}$.
@@
 \label{eq:xi_M}
-\xi_\textrm{M}=\hbar \frac{v_\textrm{F}}{\Delta_\textrm{ind}},
+\xi_\textrm{M}=\hbar \frac{v_\textrm{F}}{E_\textrm{gap}},
 \end{equation}
@@
 \comment{We calculate the topological phase diagram using the gap size.}
-In Fig.~\ref{fig:phasediagrams} we plot the energy gap as a function of magnetic field, chemical potential, $E_\textrm{gap}(B_x, \mu)$; and the superconducting phase difference $E_\textrm{gap}(B_x, \phi)$ for both a straight system [(c) and (e)] and a zigzag system [(d) and (f)].
-Additionally, we plot the first $\SI{1300}{\nm}$ (one zigzag period) of the wave functions [(a) and (b)] at the most optimal point in parameter space for the straight system.
-For the straight system we calculate $E_\textrm{gap}$ by performing a binary search in $E$ for the energy at which the propagating modes start to appear.~\cite{nijholt2015orbital}
-Additionally, in Fig.~\ref{fig:phasediagrams}(c) we plot the phase boundaries that we find by solving a generalized eigenvalue problem as described in Ref.~\onlinecite{nijholt2015orbital}.
+In Fig.~\ref{fig:phasediagrams} we compare the phase diagrams of the straight and the zigzag junction.
+We plot $E_\textrm{gap}$ as a function of magnetic field, chemical potential, $E_\textrm{gap}(B_x, \mu)$; and the superconducting phase difference $E_\textrm{gap}(B_x, \phi)$ for both a straight system [(c) and (e)] and a zigzag system [(d) and (f)].
+Additionally, we plot the first $\SI{1300}{\nm}$ (one zigzag period) of the wave functions [(a) and (b)] at the optimal point in parameter space for the straight system.
+For the straight system we calculate $E_\textrm{gap}$ by performing a binary search in $E$ for the energy at which the propagating modes start to appear~\cite{nijholt2015orbital}.
+Additionally, in Fig.~\ref{fig:phasediagrams}(c) we plot the phase boundaries obtained by solving a generalized eigenvalue problem~\cite{nijholt2015orbital}.
 Due to the large size of the zigzag supercell, we are unable to use these full spectrum methods to compute these quantities.

### 2019-02-26 paper/snakemajoranas.tex
add ref

@@
 \comment{SNS junctions also work and require smaller field.}
-Recently, a modified setup has been proposed\cite{pientka2017topological}, where instead of having one superconductor, there are two superconductors, creating a superconductor-normal-superconductor (SNS) junction.
-The additional superconductor adds an extra knob to adjust, the superconducting phase difference $\phi$, and this should make it easier to tune the system into the topological phase.
-Recently, two groups~\cite{fornieri_evidence_2018,ren_topological_2018} have realized this system experimentally.
+Recently, a modified setup has been proposed\cite{pientka2017topological,hell2017two} relying on a superconductor-normal-superconductor (SNS) junction to lower the critical magnetic field $B_\textrm{c}$ by introducing a superconducting phase difference $\phi$.
+Two groups~\cite{fornieri_evidence_2018,ren_topological_2018} have realized this system experimentally.
 In practice, multiple problems arise making even the observation difficult, rendering the manipulation of Majoranas in the near future, improbable.

### 2019-02-26 paper/snakemajoranas.tex
add an extra digit
cite private communication and review with Anton

@@
 Recently, a modified setup has been proposed\cite{pientka2017topological,hell2017two} relying on a superconductor-normal-superconductor (SNS) junction to lower the critical magnetic field $B_\textrm{c}$ by introducing a superconducting phase difference $\phi$.
-Two groups~\cite{fornieri_evidence_2018,ren_topological_2018} have realized this system experimentally.
-In practice, multiple problems arise making even the observation difficult, rendering the manipulation of Majoranas in the near future, improbable.
+When both NS interfaces are transparent the SNS junction enters the topological phase at $\phi=\pi$ at any finite $B$ field.
+Two groups~\cite{fornieri_evidence_2018,ren_topological_2018} have realized this system experimentally but did not yet observe a hard induced gap.
 
 \comment{The gap is small because of long trajectories.}
-One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap~\cite{ren_topological_2018}; where the gap in the density of states significantly reduces for states with the momentum directed along the length of the strip.
-From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
-Additionally, these long trajectories have long flight times $\tau_\textrm{f} \approx L_\textrm{t} / v_F$ (see Fig.~\ref{fig:setup}), where $L_\textrm{t}$ is the trajectory length.
-Equivalently, the Thouless energies $E_{\textrm{Th}}=\hbar / \tau_\textrm{f}$ are small, resulting in a small gap.
+One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap; which is the supression of the vanishing of the density of states near zero energy.
+One of the mechanisms giving rise to a soft gap is the reduction of the induced gap for states with the momentum directed along the junction.
+From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor, shown in Fig.~\ref{fig:setup}(a).
+These long trajectories have long flight times $\tau_\textrm{f} \approx L_\textrm{t} / v_F$ (see Fig.~\ref{fig:setup}), where $L_\textrm{t}$ is the trajectory length.
+Equivalently, the Thouless energy of these trajectories $E_{\textrm{Th}}=\hbar / \tau_\textrm{f}$ is small, resulting in a small gap.
 This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, making a low filling of the bands a possible workaround\cite{nijholt2015orbital}.
 However, low filling requires precise knowledge of the system and is more sensitive to disorder or microscopic inhomogeneities.
-On the other hand, disorder scatters these long trajectories and introduces a cut-off on the scale of the mean-free path~\cite{haim_double-edge_2018}; however, disorder is impossible to control to a required precision experimentally.
+On the other hand, disorder scatters these long trajectories and introduces a cutoff on the scale of the mean free path~\cite{haim_double-edge_2018}; however, disorder is impossible to control to a required precision experimentally.
 
@@
 Additionally, in Fig.~\ref{fig:phasediagrams}(c) we plot the phase boundaries obtained by solving a generalized eigenvalue problem~\cite{nijholt2015orbital}.
-Due to the large size of the zigzag supercell, we are unable to use these full spectrum methods to compute these quantities.
-Instead, we calculate $E_\textrm{gap}$ by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{|E(k)|}$.
-By both observing the gap closings and knowing the topological phase for the non-zigzag system, we can infer the topology of the system with zigzag modulation.
+Due to the large size of the zigzag supercell, we are unable to apply these methods to zigzag geometries.
+Instead, we calculate $E_\textrm{gap}$ by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{\left|E(k)\right|}$.
+By both observing the gap closings and knowing the topological phase for the straight system, we then infer the topology of the zigzag system and verify this by calculating the spectrum of the system.
 
-\comment{The introduction of the zigzag breaks a chiral symmetry, bringing the system from the BDI to the D symmetry class}
+\comment{The introduction ofa the zigzag breaks a chiral symmetry, bringing the system from the BDI to the D symmetry class}
 The non-zigzag system is in the symmetry class BDI \cite{pientka2017topological}.
@@
 \comment{Current fabrication techniques are compatible with the proposed geometry, and experimental verification can be near.}
-Current fabrication techniques are compatible with the proposed geometry; zigzag devices have already been fabricated. % TODO: add ref to Fokko's thesis
+Current fabrication techniques are compatible with the proposed geometry; zigzag devices have already been fabricated~\cite{fokko_zigzag}.
 Slight modifications to the geometry, for example, to ease measurement, should not have significant implications on the physics.

### 2019-02-26 paper/snakemajoranas.tex
add authors contributions and review last section

@@
 Instead, we calculate $E_\textrm{gap}$ by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{\left|E(k)\right|}$.
-By both observing the gap closings and knowing the topological phase for the straight system, we then infer the topology of the zigzag system and verify this by calculating the spectrum of the system.
+By both observing the gap closings and comparing to the topological phase diagram of the straight system, we then infer the topology of the zigzag system and verify this by calculating the Majorana wave function of a finite length zigzag.
 
 \comment{The introduction ofa the zigzag breaks a chiral symmetry, bringing the system from the BDI to the D symmetry class}
-The non-zigzag system is in the symmetry class BDI \cite{pientka2017topological}.
-Using the software package Qsymm\cite{varjas2018qsymm}, we find that the symmetry class of our system to be D because we break the chiral symmetry $\mathcal{C}$ resulting from the mirror-symmetric junction.
+The straight system is in the symmetry class BDI \cite{pientka2017topological}.
+Using the software package Qsymm~\cite{varjas2018qsymm}, we find that the zigzag shape modulation violates the chiral symmetry, leaving only the particle-hole symmetry and the reflection symmetry with respect to the $x$-axis.
 
 \comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry.}
-Similar to what is described by Pientka \textit{et al.}~\cite{pientka2017topological}, we see that the ribbon topology has a diamond-like shape as a function of phase $\phi$ and magnetic field $B_x$.
-We also observe additional gap closings which are due to the BDI symmetry that is present.
-As expected for the zigzag system, the magnitude of the gap is significantly improved, while preserving the diamond-like shape in parameter space.
-Additionally, we see a cleaner and more stable topological region due to the absence of the gap closings resulting from the aforementioned chiral symmetry.
+Similar to the findings of Pientka \textit{et al.}~\cite{pientka2017topological}, we see that the straight geometry has a diamond-shaped topological region.
+We also observe additional gap closings due to the BDI symmetry.
+The topological phase diagram of the zigzag system has a qualitatively similar shape but a significantly increased topological gap.
 
@@
 
-\comment{The zigzag geometry is a useful tool in hardening the gap and decreasing Majorana length.}
-The introduction of a zigzag geometry increases the topological gap by over an order of magnitude, as well as offering a substantial reduction of the Majorana length, which enables experimentalists to create significantly shorter devices.
-The improvements occur regardless of any particular parameter values, moreover, even when using the parameter values of the optimal gap in the straight system (Fig.~\ref{fig:phasediagrams}), the Majorana size $\xi_\textrm{M}$ and $E_\textrm{gap}$ are still more than an order of magnitude better for the zigzag system.
-Additionally, the breaking of BDI symmetry into D symmetry results in a cleaner and more stable topological region.
-Finally, the reduction of the Majorana size allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.
-
-\comment{Disorder has a similar effect, but one has no control over it.}
-Recently, it has been shown~\cite{haim_double-edge_2018} that having a system with weak disorder can lead to a reduction in the Majorana size, similar to what happens with the introduction of a zigzag geometry.
-However, in contrast to introducing weak disorder into a system, changing the geometry is experimentally much easier to realize and therefore easier to control.
+\comment{The zigzag geometry is a controllable tool in hardening the gap and decreasing Majorana size.}
+The zigzag geometry increases the topological gap in the high density regime by more than an order of magnitude, as well as substantially reducing of Majorana size.
+The improvements occur in broad range of parameter values, moreover, even using $B_x$ optimal for the straight system in the high density regime (Fig.~\ref{fig:phasediagrams}), the Majorana size $\xi_\textrm{M}$ and $E_\textrm{gap}$ are still more than an order of magnitude better for the zigzag system.
+We expect that the improvement of the device performance will significantly simplify the creation of Majorana devices and the detection of Majorana states.
+The zigzag geometry offers a controllable way to remove long trajectories, unlike disorder~\cite{haim_double-edge_2018} that otherwise has a similar effect.
 
@@
 Current fabrication techniques are compatible with the proposed geometry; zigzag devices have already been fabricated~\cite{fokko_zigzag}.
-Slight modifications to the geometry, for example, to ease measurement, should not have significant implications on the physics.
+We have demonstrated that the unavoidable variation in the experimental device geometry should not have a detrimental impact on the zigzag devices.
 
-\comment{It is interesting to study what geometry creates an optimal environment for Majorana modes to exist.}
-We have studied zigzag and snake-like geometries of the semiconductor region, but perhaps a more exotic shape will be optimal.
-A study optimizing the geometry's parameters for supporting Majoranas is an exciting continuation of our research.
-
-\comment{Extensions: we omit several physical effects, disorder, electrostatics, etc.}
-Finally, we exclude several physical effects, such as disorder, electrostatics, the orbital effect, the finite thickness of the sample, and electron-electron interactions; however, we expect these to be second or higher order effects which will not alter our conclusions.
+\comment{Optimizing the geometry, a more detailed modeling, and a simple analytical estimation are open questions for further research}
+Our work is the first demonstration of the impact of the Majorana device geometry on its performance and it opens a much harder question of finding the optimal geometry.
+A promising approach to tackle this question would rely on constructing a quasiclassical model of the zigzag devices. 
+Finally, we have excluded several important physical effects, such as: disorder, electrostatics, the orbital effect of magnetic field, and the finite thickness of the sample.
+While we expect these phenomena to not influence our qualitative findings, a more detailed simulation should provide a better guidance to future experiments.
 
@@
 
+\section{Author contributions}
+The idea of the zigzag geometry was authored by T.L.
+The code was written by B.N. and extended by T.L.
+The writing of the manuscript was performed by B.N. with input of T.L. and A.A.
+The analysis of the results and planning of the project were performed by all authors.
+
 \bibliographystyle{apsrev4-1}

### 2019-02-26 paper/snakemajoranas.tex
add acknowlegments

@@
 
-\author{Quantum Tinkerer}
+\author{Tom Laeven}
+\author{Bas Nijholt}
+\author{Michael Wimmer}
+\author{Anton R. Akhmerov}
 \affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
@@
 \section{Acknowledgments}
-We are grateful to "people" for useful discussions.
-This work was supported by the Netherlands Organization for Scientific Research (NWO/OCW), as part of the Frontiers of Nanoscience program, the Foundation for Fundamental Research on Matter (FOM), and an ERC Starting Grant STATOPINS 638760.
+We are grateful to D. Varjas, T. Ö. Rosdahl, P. P. Piskunow, F. K. de Vries, S. Goswami, Q. Wang for useful discussions.
+This work was supported by the Netherlands Organization for Scientific Research (NWO/OCW), as part of the Frontiers of Nanoscience program, a NWO VIDI Grant (SW), and an ERC Starting Grant STATOPINS 638760.
 

### 2019-02-26 paper/snakemajoranas.tex
add correct affiliations

@@
 \author{Tom Laeven}
+\affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
+\email[Electronic address: ]{tlaeven@hotmail.com}
 \author{Bas Nijholt}
+\affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
+\email[Electronic address: ]{bas@nijho.lt}
 \author{Michael Wimmer}
+\email[Electronic address: ]{m.t.wimmer@tudelft.nl}
+\affiliation{Kavli Institute of Nanoscience, Delft University of Technology,
+ P.O. Box 4056, 2600 GA Delft, The Netherlands}
+\affiliation{QuTech, Delft University of Technology,
+ P.O. Box 4056, 2600 GA Delft, The Netherlands}
 \author{Anton R. Akhmerov}
 \affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
-\email[Electronic address: ]{quantumtinkerer@tudelft.nl}
+\email[Electronic address: ]{zigzag@antonakhmerov.org}
 
@@
 We are grateful to D. Varjas, T. Ö. Rosdahl, P. P. Piskunow, F. K. de Vries, S. Goswami, Q. Wang for useful discussions.
-This work was supported by the Netherlands Organization for Scientific Research (NWO/OCW), as part of the Frontiers of Nanoscience program, a NWO VIDI Grant (SW), and an ERC Starting Grant STATOPINS 638760.
+This work was supported by the Netherlands Organization for Scientific Research (NWO/OCW), as part of the Frontiers of Nanoscience program, a NWO VIDI Grant (016.Vidi.189.180), and an ERC Starting Grant STATOPINS 638760.
 

### 2019-02-26 paper/snakemajoranas.tex
small changes

@@
 % Uncomment the following line for paragraph descriptions to appear in the file.
-\renewcommand{\comment}{\paragraph}
+% \renewcommand{\comment}{\paragraph}
 
@@
 \author{Tom Laeven}
+\email[Electronic address: ]{tlaeven@hotmail.com}
 \affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
-\email[Electronic address: ]{tlaeven@hotmail.com}
 \author{Bas Nijholt}
+\email[Electronic address: ]{bas@nijho.lt}
 \affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
-\email[Electronic address: ]{bas@nijho.lt}
 \author{Michael Wimmer}
@@
 \author{Anton R. Akhmerov}
+\email[Electronic address: ]{zigzag@antonakhmerov.org}
 \affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
-\email[Electronic address: ]{zigzag@antonakhmerov.org}
 
@@
 \centering
-\includegraphics[width=0.75\columnwidth]{figures/zigzag.pdf}
+\includegraphics[width=0.9\columnwidth]{figures/zigzag.pdf}
 \caption{The straight (top) and the zigzag (bottom) SNS junction.
@@
 The three subplots are for different amplitudes of the zigzag, with (a) a straight system $z_y=0$, (b) $z_y=W/2$, and (c) $z_y=W$, where $W=\SI{200}{\nm}$ is the junction width.
-On the $x$-axis is the Bloch momentum where $z_x=\SI{1300}{\nm}$.
-Subplot (a) has a different scale on the $x$-axis for $k_x < 0$ than the other subplots and displays the unfolded band structure.
+Subplot (a) has a different $x$-scale for $k_x < 0$ from the other subplots and displays the unfolded band structure.
 For the right-hand side of (a) ($k_x > 0$), (b), and (c), the folding is the same, such that the velocity $v=dE/dk$ can be compared visually.
@@
 We then find $\xi_\textrm{M}$ by fitting an exponential to the density of the single Majorana wave function projected on the $x$-axis.
-In the straight system we use the eigenvalue decomposition of the translation operator at zero energy~\ref{nijholt2015orbital} for performance reasons.
+In the straight system we use the eigenvalue decomposition of the translation operator at zero energy~\cite{nijholt2015orbital} for performance reasons.
 

### 2019-02-27 paper/snakemajoranas.tex
sort people
add Joe
spell check

@@
 To preferentially sample important regions of parameter space, we use the Adaptive package~\cite{adaptive}.
-The entire source code and the resulting raw data are available in Ref.~\onlinecite{data}.  % TODO: update the bib when the data is uploaded
+The entire source code and the resulting raw data are available in Ref.~\onlinecite{data}.
 
@@
 This reduction in velocity strongly reduces the Majorana size, as we discuss in section \ref{sec:shape_effects}.
-Finally, in a zigzag geometry every trajectory encounters a superconductor close to normal incidence.
+Finally, in a zigzag geometry, every trajectory encounters a superconductor close to normal incidence.
 Normal incidence has a higher transmission probability for entering the superconductor and therefore a higher Andreev reflection amplitude.
@@
 and therefore a minimal topological protection against perturbations.
-The wave function extends to the center of the system, resulting in highly overlapping Majoranas and a Majorana coupling $E_\textrm{M}$ comparible to $E_\textrm{gap}$.
+The wave function extends to the center of the system, resulting in highly overlapping Majoranas and a Majorana coupling $E_\textrm{M}$ comparable to $E_\textrm{gap}$.
 
@@
 Additionally, we plot the first $\SI{1300}{\nm}$ (one zigzag period) of the wave functions [(a) and (b)] at the optimal point in parameter space for the straight system.
-For the straight system we calculate $E_\textrm{gap}$ by performing a binary search in $E$ for the energy at which the propagating modes start to appear~\cite{nijholt2015orbital}.
+For the straight system, we calculate $E_\textrm{gap}$ by performing a binary search in $E$ for the energy at which the propagating modes start to appear~\cite{nijholt2015orbital}.
 Additionally, in Fig.~\ref{fig:phasediagrams}(c) we plot the phase boundaries obtained by solving a generalized eigenvalue problem~\cite{nijholt2015orbital}.
@@
 
-\comment{The introduction ofa the zigzag breaks a chiral symmetry, bringing the system from the BDI to the D symmetry class}
+\comment{The introduction of a the zigzag breaks a chiral symmetry, bringing the system from the BDI to the D symmetry class}
 The straight system is in the symmetry class BDI \cite{pientka2017topological}.
@@
 The zigzag geometry increases the topological gap in the high density regime by more than an order of magnitude, as well as substantially reducing of Majorana size.
-The improvements occur in broad range of parameter values, moreover, even using $B_x$ optimal for the straight system in the high density regime (Fig.~\ref{fig:phasediagrams}), the Majorana size $\xi_\textrm{M}$ and $E_\textrm{gap}$ are still more than an order of magnitude better for the zigzag system.
+The improvements occur in a broad range of parameter values, moreover, even using $B_x$ optimal for the straight system in the high density regime (Fig.~\ref{fig:phasediagrams}), the Majorana size $\xi_\textrm{M}$ and $E_\textrm{gap}$ are still more than an order of magnitude better for the zigzag system.
 We expect that the improvement of the device performance will significantly simplify the creation of Majorana devices and the detection of Majorana states.
@@
 
-\comment{Optimizing the geometry, a more detailed modeling, and a simple analytical estimation are open questions for further research}
-Our work is the first demonstration of the impact of the Majorana device geometry on its performance and it opens a much harder question of finding the optimal geometry.
+\comment{Optimizing the geometry, more detailed modeling, and a simple analytical estimation are open questions for further research}
+Our work is the first demonstration of the impact of the Majorana device geometry on its performance, and it opens a much harder question of finding the optimal geometry.
 A promising approach to tackle this question would rely on constructing a quasiclassical model of the zigzag devices. 
 Finally, we have excluded several important physical effects, such as: disorder, electrostatics, the orbital effect of magnetic field, and the finite thickness of the sample.
-While we expect these phenomena to not influence our qualitative findings, a more detailed simulation should provide a better guidance to future experiments.
+While we expect these phenomena not to influence our qualitative findings, a more detailed simulation should provide better guidance to future experiments.
 
@@
 \section{Acknowledgments}
-We are grateful to D. Varjas, T. Ö. Rosdahl, P. P. Piskunow, F. K. de Vries, S. Goswami, Q. Wang for useful discussions.
+We are grateful to  S. Goswami, A. Keselman, P. P. Piskunow, T. Ö. Rosdahl, D. Varjas, F. K. de Vries, Q. Wang, and J. B. Weston for useful discussions.
 This work was supported by the Netherlands Organization for Scientific Research (NWO/OCW), as part of the Frontiers of Nanoscience program, a NWO VIDI Grant (016.Vidi.189.180), and an ERC Starting Grant STATOPINS 638760.

### 2019-02-27 paper/snakemajoranas.tex
write the author contributions in active voice

@@
 \section{Author contributions}
-The idea of the zigzag geometry was authored by T.L.
-The code was written by B.N. and extended by T.L.
-The writing of the manuscript was performed by B.N. with input of T.L. and A.A.
-The analysis of the results and planning of the project were performed by all authors.
+T.L authored the idea of the zigzag geometry.
+B.N. wrote the code and it was extended by T.L.
+B.N. performed the writing of the manuscript with input of T.L. and A.A.
+All authors performed the analysis of the results and planning of the project.
 

### 2019-02-27 zigzag.py
copy relevant functions from spectrum.py and sns_system.py to zigzag.py

@@ -1,0 +1,705 @@
+from types import SimpleNamespace
+
+import kwant
+import numpy as np
+import scipy.sparse as sp
+import scipy.sparse.linalg as sla
+
+import cmath
+from math import cos, sin
+import math
+from functools import partial, lru_cache
+import re
+
+import kwant
+import numpy as np
+import scipy.constants
+import scipy.interpolate
+from scipy.optimize import fsolve
+
+import peierls
+import supercurrent
+import supercurrent_matsubara
+from shape import *
+
+
+constants = dict(
+    # effective mass in kg,
+    m_eff=0.023 * scipy.constants.m_e / (scipy.constants.eV * 1e-3) / 1e18,
+    hbar=scipy.constants.hbar / (scipy.constants.eV * 1e-3),
+    mu_B=scipy.constants.physical_constants['Bohr magneton'][0] / (
+        scipy.constants.eV * 1e-3),
+    exp=cmath.exp,
+    cos=cmath.cos,
+    sin=cmath.sin)
+
+
+def create_parallel_sine(distance, z_x, z_y, rough_edge=None):
+    def _parallel_sine(x, distance, z_x, z_y):
+        g       = lambda t: z_y * math.sin(2*np.pi/z_x*t)
+        g_prime = lambda t: z_y * 2*np.pi/z_x*math.cos(2*np.pi/z_x*t)
+        def _x(t):
+            return t - distance*g_prime(t)/np.sqrt(1 + g_prime(t)**2) - x
+
+        def y(t):
+            return g(t) + distance/np.sqrt(1 + g_prime(t)**2)
+
+        t = fsolve(_x, x)
+        return y(t)
+
+    xs = np.linspace(0, z_x, 1000)
+    ys = [_parallel_sine(x, distance, z_x, z_y) for x in xs]
+
+    if rough_edge is not None:
+        X, Y, salt = rough_edge
+
+        # Calculate the unit vector to the sine
+        tck = scipy.interpolate.splrep(xs, ys)
+        dydx = scipy.interpolate.splev(xs, tck, der=1)
+        unit_vectors = 1 / (1 + dydx**2) * np.array([-dydx, np.ones_like(dydx)])
+
+        # Generate a disordered boundary parameterized by (X, Y, salt)
+        rand = lambda i: X * kwant.digest.uniform(str(i), salt=str(salt))
+        rands = [rand(i) for i in range(int(z_x / Y) - 2)]
+        rands = [0, *rands, 0]  # make sure that it starts and ends with 0 (for periodicity)
[…]

### 2019-02-27 zigzag.py
cleanup zigzag.py

@@ -1,27 +1,26 @@
+import cmath
+from functools import lru_cache
+import math
+import re
 from types import SimpleNamespace
 
 import kwant
-import numpy as np
-import scipy.sparse as sp
-import scipy.sparse.linalg as sla
-
-import cmath
-from math import cos, sin
-import math
-from functools import partial, lru_cache
-import re
-
-import kwant
+from kwant.continuum import discretize
 import numpy as np
 import scipy.constants
 import scipy.interpolate
 from scipy.optimize import fsolve
+import scipy.sparse as sp
+import scipy.sparse.linalg as sla
 
 import peierls
 import supercurrent
 import supercurrent_matsubara
 from shape import *
 
+sigma_0 = np.eye(2)
+sigma_z = np.array([[1, 0], [0, -1]])
+s0sz = np.kron(sigma_0, sigma_z)
 
 constants = dict(
     # effective mass in kg,
@@ -36,7 +35,7 @@ constants = dict(
 
 def create_parallel_sine(distance, z_x, z_y, rough_edge=None):
     def _parallel_sine(x, distance, z_x, z_y):
-        g       = lambda t: z_y * math.sin(2*np.pi/z_x*t)
+        g = lambda t: z_y * math.sin(2*np.pi/z_x*t)
         g_prime = lambda t: z_y * 2*np.pi/z_x*math.cos(2*np.pi/z_x*t)
         def _x(t):
             return t - distance*g_prime(t)/np.sqrt(1 + g_prime(t)**2) - x
@@ -98,396 +97,145 @@ def get_template_strings(
 
     spin_orbit = "- alpha_{} * kron(sigma_y, sigma_z) * k_x"
     ham_normal = ham_str + spin_orbit.format('middle')
-    ham_sc_left = ham_str + spin_orbit.format('left')
-    ham_sc_right = ham_str + spin_orbit.format('right')
+    ham_sc_top = ham_str + spin_orbit.format('left')
+    ham_sc_bot = ham_str + spin_orbit.format('right')
 
     if transverse_soi:
         tr_spin_orbit = """+ alpha_{} * kron(sigma_x, sigma_z) * k_y"""
         ham_normal += tr_spin_orbit.format('middle')
-        ham_sc_left += tr_spin_orbit.format('left')
-        ham_sc_right += tr_spin_orbit.format('right')
+        ham_sc_top += tr_spin_orbit.format('left')
+        ham_sc_bot += tr_spin_orbit.format('right')
 
[…]

### 2019-02-27 zigzag.py
cleanup code

@@ -1,8 +1,10 @@
+
 import cmath
 from functools import lru_cache
 import math
 import re
 from types import SimpleNamespace
+import warnings
 
 import kwant
 from kwant.continuum import discretize
@@ -13,14 +15,13 @@ from scipy.optimize import fsolve
 import scipy.sparse as sp
 import scipy.sparse.linalg as sla
 
-import peierls
-import supercurrent
-import supercurrent_matsubara
 from shape import *
+
 
 sigma_0 = np.eye(2)
 sigma_z = np.array([[1, 0], [0, -1]])
 s0sz = np.kron(sigma_0, sigma_z)
+
 
 constants = dict(
     # effective mass in kg,
@@ -31,50 +32,6 @@ constants = dict(
     exp=cmath.exp,
     cos=cmath.cos,
     sin=cmath.sin)
-
-
-def create_parallel_sine(distance, z_x, z_y, rough_edge=None):
-    def _parallel_sine(x, distance, z_x, z_y):
-        g = lambda t: z_y * math.sin(2*np.pi/z_x*t)
-        g_prime = lambda t: z_y * 2*np.pi/z_x*math.cos(2*np.pi/z_x*t)
-        def _x(t):
-            return t - distance*g_prime(t)/np.sqrt(1 + g_prime(t)**2) - x
-
-        def y(t):
-            return g(t) + distance/np.sqrt(1 + g_prime(t)**2)
-
-        t = fsolve(_x, x)
-        return y(t)
-
-    xs = np.linspace(0, z_x, 1000)
-    ys = [_parallel_sine(x, distance, z_x, z_y) for x in xs]
-
-    if rough_edge is not None:
-        X, Y, salt = rough_edge
-
-        # Calculate the unit vector to the sine
-        tck = scipy.interpolate.splrep(xs, ys)
-        dydx = scipy.interpolate.splev(xs, tck, der=1)
-        unit_vectors = 1 / (1 + dydx**2) * np.array([-dydx, np.ones_like(dydx)])
-
-        # Generate a disordered boundary parameterized by (X, Y, salt)
-        rand = lambda i: X * kwant.digest.uniform(str(i), salt=str(salt))
-        rands = [rand(i) for i in range(int(z_x / Y) - 2)]
-        rands = [0, *rands, 0]  # make sure that it starts and ends with 0 (for periodicity)
-        ys_disorder = scipy.interpolate.interp1d(
-            np.linspace(0, z_x, len(rands)), rands, kind='quadratic')(xs)
[…]

### 2019-02-27 zigzag.py
fix bugs

@@ -181,12 +181,9 @@ def get_shapes(shape, a, z_x, z_y, L_m, L_x, L_sc_down, L_sc_up, rough_edge=None
         sc_bot_shape = _middle_shape.inverse()[0:L_x, -L_sc_down - y_offset // 2 - z_y:]
     else:
         raise ValueError('Only "parallel_curve" and "sawtooth" are implemented.')
-    # ------------
-    # Define edge
+
     edge_shape = _middle_shape.edge() * sc_bot_shape.outer_edge() * sc_top_shape.outer_edge()
 
-    # ------------------------
-    # Remove edge from middle
     interior_shape = _middle_shape - edge_shape
     interior_initial_site = (a, a)
 
@@ -448,3 +445,13 @@ def majorana_size(lead, params):
     a = lat_from_syst(lead).prim_vecs[0, 0]
     majorana_length = np.abs(a / np.log(ev[idx]).real)
     return majorana_length
+
+
+def majorana_state(syst, params):
+    energies, wfs = zigzag.spectrum(syst, params, k=2)
+    wfs = wfs[:, energies > 0]
+    energies = energies[energies > 0]
+    i_min = np.argmin(energies)
+    rho = kwant.operator.Density(syst)
+    wf = rho(wfs[:, i_min])
+    return energies[i_min], wf

### 2019-02-27 zigzag.py
clean up plotting

@@ -11,7 +11,7 @@ from kwant.continuum import discretize
 import numpy as np
 import scipy.constants
 import scipy.interpolate
-from scipy.optimize import fsolve
+import scipy.optimize
 import scipy.sparse as sp
 import scipy.sparse.linalg as sla
 
@@ -109,7 +109,7 @@ def create_parallel_sine(distance, z_x, z_y, rough_edge=None):
         def y(t):
             return g(t) + distance / np.sqrt(1 + g_prime(t)**2)
 
-        t = fsolve(_x, x)
+        t = scipy.optimize.fsolve(_x, x)
         return y(t)
 
     xs = np.linspace(0, z_x, 1000)
@@ -368,6 +368,15 @@ def gap(lead, params, tol=1e-6):
     return gap
 
 
+def gap_from_band_structure(lead, params, Ns=31, full_output=False):
+    def energies(k_x):
+        Es = spectrum(lead, dict(params, k_x=float(k_x)), k=4)[0]
+        return np.abs(Es).min()
+
+    return scipy.optimize.brute(energies, ranges=((0, np.pi),),
+        Ns=Ns, full_output=full_output)
+
+
 def phase_bounds_operator(lead, params, k_x=0):
     h_k = lead.hamiltonian_submatrix(params=dict(params, mu=0, k_x=k_x),
                                      sparse=True)
@@ -455,3 +464,26 @@ def majorana_state(syst, params):
     rho = kwant.operator.Density(syst)
     wf = rho(wfs[:, i_min])
     return energies[i_min], wf
+
+
+def fitted_majorana_size(syst, params):
+    wf = majorana_state(syst, params)[1]
+
+    # Project onto the x-axis.
+    xs, ys = np.array([s.pos for s in syst.sites]).T
+    ncols = len(np.where(xs == 0)[0])
+    wf_proj = wf.reshape((-1, ncols)).sum(axis=1)
+    xs = xs.reshape((-1, ncols))[:, 0]
+
+    # Only fit the middle part of the wf.
+    N = len(xs) // 4
+    xs_fit = xs[N:2*N]
+    wf_proj_fit = wf_proj[N:2*N]
+
+    # Do the fit.
+    def flog(x, a, b, x0):
+        return np.log(a) - b * x - x0
+
+    popt, pcov = scipy.optimize.curve_fit(flog, xs_fit, np.log(wf_proj_fit))
+
+    return 1 / popt[1]

### 2019-02-27 zigzag.py
rename L_m -> W

@@ -143,24 +143,24 @@ def create_parallel_sine(distance, z_x, z_y, rough_edge=None):
     return lambda x: parallel_sine(x % z_x)
 
 
-def get_shapes(shape, a, z_x, z_y, L_m, L_x, L_sc_down, L_sc_up, rough_edge=None):
+def get_shapes(shape, a, z_x, z_y, W, L_x, L_sc_down, L_sc_up, rough_edge=None):
     if shape == 'parallel_curve':
         if rough_edge is not None:
             X, Y, salt = rough_edge
 
         curve = create_parallel_sine(0, z_x, z_y, rough_edge=None)
 
-        _curve_top = create_parallel_sine(L_m // 2, z_x, z_y, rough_edge=(X, Y, salt) if rough_edge else None)
+        _curve_top = create_parallel_sine(W // 2, z_x, z_y, rough_edge=(X, Y, salt) if rough_edge else None)
         _below_shape = below_curve(_curve_top)
 
-        _curve_bottom = create_parallel_sine(-L_m // 2, z_x, z_y, rough_edge=(X, Y, -salt) if rough_edge else None)
+        _curve_bottom = create_parallel_sine(-W // 2, z_x, z_y, rough_edge=(X, Y, -salt) if rough_edge else None)
         _above_shape = above_curve(_curve_bottom)
 
         _middle_shape = (_below_shape * _above_shape)[0:L_x, :]
-        sc_top_initial_site = (z_x // 4, L_m // 2 + z_y + L_sc_up // 2)
-        sc_top_shape = _middle_shape.inverse()[0:L_x, :L_sc_up + L_m // 2 + z_y]
-        sc_bot_initial_site = (z_x // 4, -L_m // 2 - z_y - L_sc_down // 2)
-        sc_bot_shape = _middle_shape.inverse()[0:L_x, -L_sc_down - L_m // 2 - z_y:]
+        sc_top_initial_site = (z_x // 4, W // 2 + z_y + L_sc_up // 2)
+        sc_top_shape = _middle_shape.inverse()[0:L_x, :L_sc_up + W // 2 + z_y]
+        sc_bot_initial_site = (z_x // 4, -W // 2 - z_y - L_sc_down // 2)
+        sc_bot_shape = _middle_shape.inverse()[0:L_x, -L_sc_down - W // 2 - z_y:]
     elif shape == 'sawtooth':
         def curve(x):
             x += z_x / 4
[…]

### 2019-02-27 zigzag.py
fix bug

@@ -145,15 +145,16 @@ def create_parallel_sine(distance, z_x, z_y, rough_edge=None):
 
 def get_shapes(shape, a, z_x, z_y, W, L_x, L_sc_down, L_sc_up, rough_edge=None):
     if shape == 'parallel_curve':
-        if rough_edge is not None:
-            X, Y, salt = rough_edge
-
         curve = create_parallel_sine(0, z_x, z_y, rough_edge=None)
 
-        _curve_top = create_parallel_sine(W // 2, z_x, z_y, rough_edge=(X, Y, salt) if rough_edge else None)
+        _curve_top = create_parallel_sine(W // 2, z_x, z_y, rough_edge=rough_edge)
         _below_shape = below_curve(_curve_top)
 
-        _curve_bottom = create_parallel_sine(-W // 2, z_x, z_y, rough_edge=(X, Y, -salt) if rough_edge else None)
+        if rough_edge is not None:  # Change salt for the order boundary
+            X, Y, salt = rough_edge
+            rough_edge = (X, Y, -salt)
+
+        _curve_bottom = create_parallel_sine(-W // 2, z_x, z_y, rough_edge=rough_edge)
         _above_shape = above_curve(_curve_bottom)
 
         _middle_shape = (_below_shape * _above_shape)[0:L_x, :]
@@ -457,7 +458,7 @@ def majorana_size(lead, params):
 
 
 def majorana_state(syst, params):
-    energies, wfs = zigzag.spectrum(syst, params, k=2)
+    energies, wfs = spectrum(syst, params, k=2)
     wfs = wfs[:, energies > 0]
     energies = energies[energies > 0]
     i_min = np.argmin(energies)

### 2019-02-27 zigzag.py
rename gap -> gap_from_modes

@@ -330,7 +330,7 @@ def gap_minimizer(lead, params, energy):
     return np.min(np.abs(norm - 1))
 
 
-def gap(lead, params, tol=1e-6):
+def gap_from_modes(lead, params, tol=1e-6):
     """Finds the gapsize by peforming a binary search of the modes with a
     tolarance of tol.
 

### 2019-02-27 shape.py
clean up further

@@ -106,7 +106,6 @@ def TRANSLATE(shape, vector):
         return shape(translated_site)
     return _shape
 
-
 def below_curve(curve):
     def _shape(site):
         x, y = site.pos

### 2019-02-27 zigzag.py

@@ -379,8 +379,8 @@ def gap_from_band_structure(lead, params, Ns=31, full_output=False):
 
 
 def phase_bounds_operator(lead, params, k_x=0):
-    h_k = lead.hamiltonian_submatrix(params=dict(params, mu=0, k_x=k_x),
-                                     sparse=True)
+    h_k = lead.hamiltonian_submatrix(
+        params=dict(params, mu=0, k_x=k_x), sparse=True)
     sigma_z = sp.csc_matrix(np.array([[1, 0], [0, -1]]))
     _operator = sp.kron(sp.eye(h_k.shape[0] // 2), sigma_z) @ h_k
     return _operator

### 2019-02-27 zigzag.py
do not depend on the shapes.py module

@@ -1,7 +1,9 @@
 
 import cmath
-from functools import lru_cache
+import copy
+import functools
 import math
+import operator
 import re
 from types import SimpleNamespace
 import warnings
@@ -14,8 +16,6 @@ import scipy.interpolate
 import scipy.optimize
 import scipy.sparse as sp
 import scipy.sparse.linalg as sla
-
-from shape import *
 
 
 sigma_0 = np.eye(2)
@@ -38,7 +38,7 @@ def remove_phs(H):
     return re.sub(r'kron\((sigma_[xyz0]), sigma_[xzy0]\)', r'\1', H)
 
 
-@lru_cache()
+@functools.lru_cache()
 def get_template_strings(
         transverse_soi, mu_from_bottom_of_spin_orbit_bands=True,
         k_x_in_sc=False, with_k_z=False, no_phs=False,
@@ -94,6 +94,102 @@ def get_template_strings(
 
     return template_strings
 
+# from shape import Shape
+class Shape:
+    def __init__(self, shape=None):
+        self.shape = shape if shape is not None else lambda site: True
+
+        self._directions = [
+            ('wsite', [-1, 0]), ('esite', [1, 0]),
+            ('nsite', [0, 1]), ('ssite', [0, -1]),
+            ('nwsite', [-1, 1]), ('nesite', [1, 1]),
+            ('swsite', [-1, -1]), ('sesite', [1, -1])
+        ]
+        
+    def __call__(self, site):
+        return self.shape(site)
+
+    def __add__(self, other_shape):
+        shapes = (self.shape, other_shape.shape)
+        union = lambda site: any(shape(site) for shape in shapes)
+        return Shape(union)
+    
+    def __sub__(self, other_shape):
+        shape_A, shape_B = (self.shape, other_shape.shape)
+        difference = lambda site: shape_A(site) and not shape_B(site)
+        return Shape(difference)
+    
+    def __mul__(self, other_shape):
+        shapes = (self.shape, other_shape.shape)
+        intersection = lambda site: all(shape(site) for shape in shapes)
+        return Shape(intersection)
+
+    @staticmethod
+    def slice_func(_slice):
+        def _func(x):
+            y = True
+            if _slice.start is not None:
+                y &= _slice.start <= x
+            if _slice.stop is not None:
+                y &= x < _slice.stop
+            return y
+        return _func
+
[…]

### 2019-02-27 zigzag.py
add shebang

@@ -1,3 +1,4 @@
+#!/usr/bin/env python3
 
 import cmath
 import copy
@@ -16,11 +17,6 @@ import scipy.interpolate
 import scipy.optimize
 import scipy.sparse as sp
 import scipy.sparse.linalg as sla
-
-
-sigma_0 = np.eye(2)
-sigma_z = np.array([[1, 0], [0, -1]])
-s0sz = np.kron(sigma_0, sigma_z)
 
 
 constants = dict(

### 2019-02-27 zigzag.py
fix late binding of lambdas bug

@@ -10,6 +10,7 @@ from types import SimpleNamespace
 import warnings
 
 import kwant
+from kwant.builder import Site
 from kwant.continuum import discretize
 import numpy as np
 import scipy.constants
@@ -90,7 +91,7 @@ def get_template_strings(
 
     return template_strings
 
-# from shape import Shape
+
 class Shape:
     def __init__(self, shape=None):
         self.shape = shape if shape is not None else lambda site: True
@@ -131,29 +132,20 @@ class Shape:
             return y
         return _func
 
-# I don't understand why the following code doesn't work:
-    # def __getitem__(self, item):
-    #     if not isinstance(item, tuple):
-    #         # Make sure that item is iterable
-    #         item = (item,)
-    #     shapes = [Shape(lambda site: self.slice_func(x)(site.pos[i]))
-    #               for i, x in enumerate(item)]
-    #     return functools.reduce(operator.mul, [self] + shapes)
-
     def __getitem__(self, item):
-        if len(item) != 2:
-            raise NotImplementedError(
-                'Can only be used for 2-dimensional slicing.')
-        return (self
-                * Shape(lambda site: self.slice_func(item[0])(site.pos[0]))
-                * Shape(lambda site: self.slice_func(item[1])(site.pos[1])))
+        if not isinstance(item, tuple):
+            # Make sure that item is iterable
+            item = (item,)
+        shapes = [Shape(lambda s, i=i, x=x: self.slice_func(x)(s.pos[i]))
+                  for i, x in enumerate(item)]
+        return functools.reduce(operator.mul, [self] + shapes)
 
     def inverse(self):
         return Shape(lambda site: not self.shape(site))
         
     def edge(self, which='inner'):
         def edge_shape(site):
-            in_shape = lambda x: self.shape(kwant.builder.Site(site.family, site.tag + x))
+            in_shape = lambda x: self.shape(Site(site.family, site.tag + x))
             sites = [in_shape(x) for k, x in self._directions]
             if which == 'inner':
                 return self.shape(site) and not all(sites)
@@ -216,8 +208,8 @@ def create_parallel_sine(distance, z_x, z_y, rough_edge=None):
         unit_vectors = 1 / (1 + dydx**2) * np.array([-dydx, np.ones_like(dydx)])
 
         # Generate a disordered boundary parameterized by (X, Y, salt)
[…]

### 2019-02-27 zigzag.py
remove unused arguments from system

@@ -282,7 +282,7 @@ def get_shapes(shape, a, z_x, z_y, W, L_x, L_sc_down, L_sc_up, rough_edge=None):
 def system(
         W, L_x, L_sc_up, L_sc_down, z_x, z_y, a, shape, transverse_soi,
         mu_from_bottom_of_spin_orbit_bands, k_x_in_sc, wraparound, infinite,
-        current, ns_junction, sc_leads=False, no_phs=False, rough_edge=None,
+        sc_leads=False, no_phs=False, rough_edge=None,
         phs_breaking_potential=False):
     if wraparound and not infinite:
         raise ValueError('If you want to use wraparound, infinite must be True.')

### 2019-02-27 zigzag.py
add comment

@@ -301,6 +301,7 @@ def system(
     syst = kwant.Builder(kwant.TranslationalSymmetry([L_x, 0]) if infinite else None)
 
     for y in np.arange(-W - L_sc_down, W + L_sc_up, a):
+        # Not sure why this loop is needed.
         with warnings.catch_warnings():
             warnings.filterwarnings("ignore")
             syst.fill(template['barrier'], shapes['edge'], (0, y))

### 2019-02-27 paper/snakemajoranas.tex
use B_x consistently

@@
 \comment{The default parameters are ...}
-Unless noted differently, the Hamiltonian parameters are $\alpha=\SI{20}{\meV \nm}$, $g=26$, $\meff=\SI{0.02}{\electronmass}$, $\mu=\SI{10}{\meV}$, $B=\SI{1}{T}$, $\phi=\pi$, and $\Delta=\SI{1}{\meV}$; and the geometry parameters are $W=\SI{200}{\nm}$, the period of the zigzag $z_x=\SI{1300}{\nm}$, the discretization contant $a=\SI{10}{\nm}$, and the lengths of the superconductors $L_\textrm{SC}=\SI{300}{\nm}$.
+Unless noted differently, the Hamiltonian parameters are $\alpha=\SI{20}{\meV \nm}$, $g=26$, $\meff=\SI{0.02}{\electronmass}$, $\mu=\SI{10}{\meV}$, $B_x=\SI{1}{T}$, $\phi=\pi$, and $\Delta=\SI{1}{\meV}$; and the geometry parameters are $W=\SI{200}{\nm}$, the period of the zigzag $z_x=\SI{1300}{\nm}$, the discretization contant $a=\SI{10}{\nm}$, and the lengths of the superconductors $L_\textrm{SC}=\SI{300}{\nm}$.
 
@@
 \caption{Band stuctures of the system in Fig.~\ref{fig:setup}(b) with different zigzag amplitudes.
-The blue lines correspond to a trivial phase ($\phi=0$, $B=0$) and the orange lines to a topological phase ($\phi=\pi$, $B = \SI{1}{T}$).
+The blue lines correspond to a trivial phase ($\phi=0$, $B_x = 0$) and the orange lines to a topological phase ($\phi=\pi$, $B_x = \SI{1}{T}$).
 The three subplots are for different amplitudes of the zigzag, with (a) a straight system $z_y=0$, (b) $z_y=W/2$, and (c) $z_y=W$, where $W=\SI{200}{\nm}$ is the junction width.

### 2019-02-27 zigzag.py
remove unused imports

@@ -1,12 +1,10 @@
 #!/usr/bin/env python3
 
 import cmath
-import copy
 import functools
 import math
 import operator
 import re
-from types import SimpleNamespace
 import warnings
 
 import kwant

### 2019-02-27 zigzag.py
explain the loop

@@ -299,10 +299,13 @@ def system(
     syst = kwant.Builder(kwant.TranslationalSymmetry([L_x, 0]) if infinite else None)
 
     for y in np.arange(-W - L_sc_down, W + L_sc_up, a):
-        # Not sure why this loop is needed.
+        # We're unsure about the location of the barrier
+        # so we loop until we add the sites.
         with warnings.catch_warnings():
             warnings.filterwarnings("ignore")
-            syst.fill(template['barrier'], shapes['edge'], (0, y))
+            sites = syst.fill(template['barrier'], shapes['edge'], (0, y))
+        if sites:
+            break
 
     syst.fill(template['normal'], *shapes['normal'])
 

### 2019-02-27 paper/snakemajoranas.tex
orders -> order

@@
 \comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
-We propose a new experimental setup (see Fig.~\ref{fig:setup}(b)) for the creation of Majoranas that eliminates long trajectories and therefore prevents the appearance of a soft gap, while also increasing the topological gap by more than an orders of magnitude, depending on the parameters.
+We propose a new experimental setup (see Fig.~\ref{fig:setup}(b)) for the creation of Majoranas that eliminates long trajectories and therefore prevents the appearance of a soft gap, while also increasing the topological gap by more than an order of magnitude, depending on the parameters.
 The setup consists of a zigzag or snake-like geometry for the semiconductor where long trajectories are not possible due to the geometry.

### 2019-02-28 zigzag.py
Added docstrings to shape class, and added fix for outer edge

@@ -91,6 +91,24 @@ def get_template_strings(
 
 
 class Shape:
+    """Creates callable object serving as a 'shape' function to be used with kwant.Builder
+    
+    The Shape class supports multiple set operations. Let s1 and s2 be instances of the Shape object, then:
+    s3 = s1*s2 is the intersection of the two shapes, meaning that s3(x) returns True if and only if both s1(x) and s2(x) return True.
+    s3 = s1+s2 is the union of the two shapes, meaning that s3(x) returns True if and only if s1(x) and/or s2(x) returns True.
+    s3 = s1-s2 is the difference of the two shapes, meaning that s3(x) returns True if and only if s1(x) returns True and s2(x) returns False.
+
+    The Shape class also contains some other useful methods to obtain the inverse, the edge, and interior of the shape.
+
+    Using slice indexing one creates rectangular bounds, i.e.:
+    if s = Shape()[:0, :],
+    then s(x, y) returns True if and only if x<=0
+
+    Keyword arguments:
+    shape -- shape function: shape(kwant.Site) -> bool (default always returns True)
+
+    """
+
     def __init__(self, shape=None):
         self.shape = shape if shape is not None else lambda site: True
 
@@ -139,34 +157,47 @@ class Shape:
         return functools.reduce(operator.mul, [self] + shapes)
 
     def inverse(self):
+        """Returns inverse of shape."""
+
         return Shape(lambda site: not self.shape(site))
         
     def edge(self, which='inner'):
+        """Returns edge of a 2D shape.
+        If which is 'inner', the inner edge of the shape is returned, meaning the familiy of sites which lie within the shape, but have at least one neighbor outside of the shape.
+        If which is 'outer', the outer edge of the shape is returned, meaning the familiy of sites which lie outside the shape, but have at least one neighbor inside of the shape.
+        
+        """
+
         def edge_shape(site):
             in_shape = lambda x: self.shape(Site(site.family, site.tag + x))
             sites = [in_shape(x) for k, x in self._directions]
             if which == 'inner':
                 return self.shape(site) and not all(sites)
             elif which == 'outer':
-                return self.shape(site) and any(sites)
+                return not self.shape(site) and any(sites)
         return Shape(edge_shape)
     
     def interior(self):
+        """Returns shape minus its edge."""
+
         return Shape(self - self.edge('inner'))
 
     @classmethod
     def below_curve(cls, curve):
[…]

### 2019-02-28 zigzag.py
small changes to Shape doc-string

@@ -91,22 +91,29 @@ def get_template_strings(
 
 
 class Shape:
-    """Creates callable object serving as a 'shape' function to be used with kwant.Builder
+    """Creates callable object serving as a 'shape' function
+    to be used with `kwant.Builder`.
     
-    The Shape class supports multiple set operations. Let s1 and s2 be instances of the Shape object, then:
-    s3 = s1*s2 is the intersection of the two shapes, meaning that s3(x) returns True if and only if both s1(x) and s2(x) return True.
-    s3 = s1+s2 is the union of the two shapes, meaning that s3(x) returns True if and only if s1(x) and/or s2(x) returns True.
-    s3 = s1-s2 is the difference of the two shapes, meaning that s3(x) returns True if and only if s1(x) returns True and s2(x) returns False.
+    This class supports multiple set operations. Let `s1` and `s2` be
+    instances of the `Shape` object, then:
+    s3 = s1*s2 is the intersection of the two shapes, meaning that s3(x)
+        returns True if and only if both s1(x) and s2(x) return True.
+    s3 = s1+s2 is the union of the two shapes, meaning that s3(x) returns
+        True if and only if s1(x) and/or s2(x) returns True.
+    s3 = s1-s2 is the difference of the two shapes, meaning that s3(x) returns
+        True if and only if s1(x) returns True and s2(x) returns False.
 
-    The Shape class also contains some other useful methods to obtain the inverse, the edge, and interior of the shape.
+    The Shape class also contains some other useful methods to obtain the
+    inverse, the edge, and interior of the shape.
 
     Using slice indexing one creates rectangular bounds, i.e.:
     if s = Shape()[:0, :],
-    then s(x, y) returns True if and only if x<=0
+    then s(x, y) returns True if and only if x<=0.
 
-    Keyword arguments:
-    shape -- shape function: shape(kwant.Site) -> bool (default always returns True)
-
+    Arguments
+    ---------
+    shape : callable, optional
+        shape(kwant.Site) -> bool (default always returns True).
     """
 
     def __init__(self, shape=None):

### 2019-02-28 zigzag.py
add line breaks

@@ -170,9 +170,10 @@ class Shape:
         
     def edge(self, which='inner'):
         """Returns edge of a 2D shape.
-        If which is 'inner', the inner edge of the shape is returned, meaning the familiy of sites which lie within the shape, but have at least one neighbor outside of the shape.
-        If which is 'outer', the outer edge of the shape is returned, meaning the familiy of sites which lie outside the shape, but have at least one neighbor inside of the shape.
-        
+
+        If which is 'inner' ('outer'), the inner (outer) edge of the shape
+        is returned, meaning the familiy of sites which lie inside (outside)
+        the shape, but have at least one neighbor outside (inside) of the shape.
         """
 
         def edge_shape(site):
@@ -191,20 +192,23 @@ class Shape:
 
     @classmethod
     def below_curve(cls, curve):
-        """Returns instance of Shape which returns True if a site (x, y) is such that y < curve(x)."""
+        """Returns instance of Shape which returns True if a site (x, y)
+        is such that y < curve(x)."""
         def _shape(site):
             x, y = site.pos
             return y < curve(x)
         return Shape(_shape)
 
     @classmethod
-        """Returns instance of Shape which returns True if a site (x, y) is such that y >= curve(x)."""
+        """Returns instance of Shape which returns True if a
+        site (x, y) is such that y >= curve(x)."""
     def above_curve(cls, curve):
         return Shape.below_curve(curve).inverse()
 
     @classmethod
     def left_of_curve(cls, curve):
-        """Returns instance of Shape which returns True if a site (x, y) is such that x < curve(y)."""
+        """Returns instance of Shape which returns True if a
+        site (x, y) is such that x < curve(y)."""
         def _shape(site):
             x, y = site.pos
             return x < curve(y)
@@ -212,7 +216,8 @@ class Shape:
 
     @classmethod
     def right_of_curve(cls, curve):
-        """Returns instance of Shape which returns True if a site (x, y) is such that x >= curve(y)."""
+        """Returns instance of Shape which returns True if a site (x, y)
+        is such that x >= curve(y)."""
         return Shape.left_of_curve(curve).inverse()
 
 
@@ -304,7 +309,9 @@ def get_shapes(shape, a, z_x, z_y, W, L_x, L_sc_down, L_sc_up, rough_edge=None):
     else:
         raise ValueError('Only "parallel_curve" and "sawtooth" are implemented.')
     
[…]

### 2019-02-28 zigzag.py
fix bug

@@ -187,7 +187,6 @@ class Shape:
     
     def interior(self):
         """Returns shape minus its edge."""
-
         return Shape(self - self.edge('inner'))
 
     @classmethod
@@ -200,9 +199,9 @@ class Shape:
         return Shape(_shape)
 
     @classmethod
+    def above_curve(cls, curve):
         """Returns instance of Shape which returns True if a
         site (x, y) is such that y >= curve(x)."""
-    def above_curve(cls, curve):
         return Shape.below_curve(curve).inverse()
 
     @classmethod

### 2019-02-28 zigzag.py
use itertools

@@ -2,6 +2,7 @@
 
 import cmath
 import functools
+import itertools
 import math
 import operator
 import re
@@ -118,13 +119,8 @@ class Shape:
 
     def __init__(self, shape=None):
         self.shape = shape if shape is not None else lambda site: True
-
-        self._directions = [
-            ('wsite', [-1, 0]), ('esite', [1, 0]),
-            ('nsite', [0, 1]), ('ssite', [0, -1]),
-            ('nwsite', [-1, 1]), ('nesite', [1, 1]),
-            ('swsite', [-1, -1]), ('sesite', [1, -1])
-        ]
+        prod = itertools.product([-1, 0, 1], repeat=2)
+        self._directions = [tup for tup in prod if tup != (0, 0)]
         
     def __call__(self, site):
         return self.shape(site)
@@ -175,10 +171,9 @@ class Shape:
         is returned, meaning the familiy of sites which lie inside (outside)
         the shape, but have at least one neighbor outside (inside) of the shape.
         """
-
         def edge_shape(site):
             in_shape = lambda x: self.shape(Site(site.family, site.tag + x))
-            sites = [in_shape(x) for k, x in self._directions]
+            sites = [in_shape(x) for x in self._directions]
             if which == 'inner':
                 return self.shape(site) and not all(sites)
             elif which == 'outer':

### 2019-02-28 zigzag.py
test if edge adding algo breaks the tests

@@ -340,12 +340,12 @@ def system(
 
     for y in np.arange(-W - L_sc_down, W + L_sc_up, a):
         # We're unsure about the location of the barrier
-        # so we loop until we add the sites.
+        # so we loop over all possible sites.
         with warnings.catch_warnings():
             warnings.filterwarnings("ignore")
             sites = syst.fill(template['barrier'], shapes['edge'], (0, y))
-        if sites:
-            break
+        # if sites:
+        #     break
 
     syst.fill(template['normal'], *shapes['normal'])
 

### 2019-02-28 zigzag.py
Added docstring for system function

@@ -322,6 +322,51 @@ def system(
         mu_from_bottom_of_spin_orbit_bands, k_x_in_sc, wraparound, infinite,
         sc_leads=False, no_phs=False, rough_edge=None,
         phs_breaking_potential=False):
+    """Create zigzag system
+    
+    Parameters
+    ----------
+    W : float
+        Width of the semiconductor (i.e. contact seperation of the junction)
+    L_x : float
+        Length of the system (x-dimension)
+    L_sc_up : float
+        Minimum width of the top superconductor
+    L_sc_down : float
+        Minimum width of the bottom superconductor
+    z_x : float
+        Period of zigzag
+    z_y : float
+        Amplitude of zigzag
+    a : float
+        Lattice spacing
+    shape : string
+        Can be either 'sawtooth' for zigzag shape, or 'parallel_curve' for a shape formed by curve parallel to a sine curve
+    transverse_soi : bool
+        Toggle Rashba spin-orbit in the y-direction
+    mu_from_bottom_of_spin_orbit_bands : bool
+        Toggle counting chemical potential from bottom of spin orbit band
+    k_x_in_sc : bool
+        Toggle whether superconductor have hopping in the x-directin
+    wraparound : bool
+        Toggle a wraparound system, such that the translational invariance is transformed into the momentum parameter k_x
+    infinite : bool
+        Toggle whether the system contains a z_x periodic translational invariance
+    sc_leads : bool, optional
+        Toggle superconducting leads in y-direction 
+    no_phs : bool, optional
+        Remove particle-hole symmetry by removing electron-hole orbital
+    roug_edge : bool, optional
+        Toggle roughened edges to shape
+    phs_breaking_potential : bool, optional
+        Add particle-hole symmetry breaking potential to allow for a computationally cheaper way to calculate the Majorana decay length.
+
+    Returns
+    -------
+    kwant.builder.FiniteSystem or kwant.builder.InfiniteSystem
+
+    """
+
     if wraparound and not infinite:
         raise ValueError('If you want to use wraparound, infinite must be True.')
     if sc_leads and not infinite or sc_leads and not wraparound:

### 2019-02-28 zigzag.py
fixed typo

@@ -356,7 +356,7 @@ def system(
         Toggle superconducting leads in y-direction 
     no_phs : bool, optional
         Remove particle-hole symmetry by removing electron-hole orbital
-    roug_edge : bool, optional
+    rough_edge : bool, optional
         Toggle roughened edges to shape
     phs_breaking_potential : bool, optional
         Add particle-hole symmetry breaking potential to allow for a computationally cheaper way to calculate the Majorana decay length.

### 2019-02-28 zigzag.py
add docstring for spectrum function

@@ -366,7 +366,6 @@ def system(
     kwant.builder.FiniteSystem or kwant.builder.InfiniteSystem
 
     """
-
     if wraparound and not infinite:
         raise ValueError('If you want to use wraparound, infinite must be True.')
     if sc_leads and not infinite or sc_leads and not wraparound:
@@ -437,6 +436,24 @@ def mumps_eigsh(matrix, k, sigma, **kwargs):
 
 
 def spectrum(syst, params, k=20):
+    """Compute the k smallest magnitude eigenvalues and corresponding eigenvectors of a system
+
+    Parameters
+    ----------
+    syst : kwant.FiniteSystem or kwant.InfiniteSystem
+        System of which the spectrum will be computed
+    params: dict
+        Dictionary containing the parameters
+    k : int
+        Number of eigenvalues to calculate
+
+    Returns
+    -------
+    energies : numpy array
+        Array containing smallest magnitude eigenvalues
+    wfs : numpy array
+        Array containing eigenvectors corresponding to eigenvalues
+    """
     ham = syst.hamiltonian_submatrix(params=params, sparse=True)
     (energies, wfs) = mumps_eigsh(ham, k=k, sigma=0)
     return energies, wfs

### 2019-03-01 zigzag.py
fix line breaks

@@ -327,39 +327,43 @@ def system(
     Parameters
     ----------
     W : float
-        Width of the semiconductor (i.e. contact seperation of the junction)
+        Width of the semiconductor (or contact seperation of the junction.)
     L_x : float
-        Length of the system (x-dimension)
+        Length of the system (x-dimension).
     L_sc_up : float
-        Minimum width of the top superconductor
+        Minimum width of the top superconductor.
     L_sc_down : float
-        Minimum width of the bottom superconductor
+        Minimum width of the bottom superconductor.
     z_x : float
-        Period of zigzag
+        Period of zigzag.
     z_y : float
-        Amplitude of zigzag
+        Amplitude of zigzag.
     a : float
-        Lattice spacing
+        Lattice spacing.
     shape : string
-        Can be either 'sawtooth' for zigzag shape, or 'parallel_curve' for a shape formed by curve parallel to a sine curve
+        Can be either 'sawtooth' for zigzag shape, or 'parallel_curve'
+        for a shape formed by curve parallel to a sine curve.
     transverse_soi : bool
-        Toggle Rashba spin-orbit in the y-direction
+        Toggle Rashba spin-orbit in the y-direction.
     mu_from_bottom_of_spin_orbit_bands : bool
-        Toggle counting chemical potential from bottom of spin orbit band
+        Toggle counting chemical potential from bottom of spin orbit band.
     k_x_in_sc : bool
-        Toggle whether superconductor have hopping in the x-directin
+        Toggle whether superconductor have hopping in the x-direction.
     wraparound : bool
-        Toggle a wraparound system, such that the translational invariance is transformed into the momentum parameter k_x
+        Toggle a wraparound system, such that the translational invariance
+        is transformed into the momentum parameter k_x.
     infinite : bool
-        Toggle whether the system contains a z_x periodic translational invariance
+        Toggle whether the system contains a z_x periodic
+        translational invariance.
     sc_leads : bool, optional
-        Toggle superconducting leads in y-direction 
+        Toggle superconducting leads in y-direction.
     no_phs : bool, optional
-        Remove particle-hole symmetry by removing electron-hole orbital
+        Remove particle-hole symmetry by removing the electron-hole orbital.
     rough_edge : bool, optional
-        Toggle roughened edges to shape
+        Toggle roughened edges to shape.
     phs_breaking_potential : bool, optional
[…]

### 2019-03-01 zigzag.py
remove comment

@@ -392,8 +392,6 @@ def system(
         with warnings.catch_warnings():
             warnings.filterwarnings("ignore")
             sites = syst.fill(template['barrier'], shapes['edge'], (0, y))
-        # if sites:
-        #     break
 
     syst.fill(template['normal'], *shapes['normal'])
 

### 2019-03-01 zigzag.py
fix doc-strings

@@ -442,12 +442,12 @@ def spectrum(syst, params, k=20):
 
     Parameters
     ----------
-    syst : kwant.FiniteSystem or kwant.InfiniteSystem
-        System of which the spectrum will be computed
-    params: dict
-        Dictionary containing the parameters
+    syst : `kwant.FiniteSystem` or `kwant.InfiniteSystem`
+        System of which the spectrum will be computed.
+    params : dict
+        Dictionary containing the parameters.
     k : int
-        Number of eigenvalues to calculate
+        Number of eigenvalues to calculate.
 
     Returns
     -------

### 2019-03-01 zigzag.py
more line fixes

@@ -94,7 +94,7 @@ def get_template_strings(
 class Shape:
     """Creates callable object serving as a 'shape' function
     to be used with `kwant.Builder`.
-    
+
     This class supports multiple set operations. Let `s1` and `s2` be
     instances of the `Shape` object, then:
     s3 = s1*s2 is the intersection of the two shapes, meaning that s3(x)
@@ -121,7 +121,7 @@ class Shape:
         self.shape = shape if shape is not None else lambda site: True
         prod = itertools.product([-1, 0, 1], repeat=2)
         self._directions = [tup for tup in prod if tup != (0, 0)]
-        
+
     def __call__(self, site):
         return self.shape(site)
 
@@ -129,12 +129,12 @@ class Shape:
         shapes = (self.shape, other_shape.shape)
         union = lambda site: any(shape(site) for shape in shapes)
         return Shape(union)
-    
+
     def __sub__(self, other_shape):
         shape_A, shape_B = (self.shape, other_shape.shape)
         difference = lambda site: shape_A(site) and not shape_B(site)
         return Shape(difference)
-    
+
     def __mul__(self, other_shape):
         shapes = (self.shape, other_shape.shape)
         intersection = lambda site: all(shape(site) for shape in shapes)
@@ -163,7 +163,7 @@ class Shape:
         """Returns inverse of shape."""
 
         return Shape(lambda site: not self.shape(site))
-        
+
     def edge(self, which='inner'):
         """Returns edge of a 2D shape.
 
@@ -179,7 +179,7 @@ class Shape:
             elif which == 'outer':
                 return not self.shape(site) and any(sites)
         return Shape(edge_shape)
-    
+
     def interior(self):
         """Returns shape minus its edge."""
         return Shape(self - self.edge('inner'))
@@ -302,7 +302,7 @@ def get_shapes(shape, a, z_x, z_y, W, L_x, L_sc_down, L_sc_up, rough_edge=None):
         sc_bot_shape = _middle_shape.inverse()[0:L_x, -L_sc_down - y_offset // 2 - z_y:]
     else:
         raise ValueError('Only "parallel_curve" and "sawtooth" are implemented.')
-    
+
     edge_shape = (_middle_shape.edge('inner')
                   * sc_bot_shape.edge('outer')
                   * sc_top_shape.edge('outer'))
@@ -323,7 +323,7 @@ def system(
         sc_leads=False, no_phs=False, rough_edge=None,
[…]

### 2019-03-01 zigzag.py
styling

@@ -453,9 +453,9 @@ def spectrum(syst, params, k=20):
     Returns
     -------
     energies : numpy array
-        Array containing smallest magnitude eigenvalues
+        Array containing smallest magnitude eigenvalues.
     wfs : numpy array
-        Array containing eigenvectors corresponding to eigenvalues
+        Array containing eigenvectors corresponding to eigenvalues.
     """
     ham = syst.hamiltonian_submatrix(params=params, sparse=True)
     (energies, wfs) = mumps_eigsh(ham, k=k, sigma=0)

### 2019-03-01 paper/snakemajoranas.tex
address Fokko's abstract comment

@@
 \begin{abstract}
-High density superconductor-semiconductor-superconductor junctions have a small induced superconducting gap due to the quasiparticle trajectories with a large momentum parallel to the junction because these trajectories have a very long flight time.
-Because a large induced gap protects Majorana modes, these long trajectories constrain Majorana devices to low electron density.
+High density superconductor-semiconductor-superconductor junctions have a small induced superconducting gap due to the quasiparticle trajectories with a large momentum parallel to the junction having a very long flight time.
+Because a large induced gap protects Majorana modes, these long trajectories constrain Majorana devices to a low electron density.
 We show that a zigzag-shaped geometry eliminates these trajectories, allowing the robust creation of Majorana states with both the induced gap and the Majorana size improved by more than an order of magnitude for realistic parameters.

### 2019-03-01 paper/snakemajoranas.tex
fix double negation

@@
 \comment{The gap is small because of long trajectories.}
-One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap; which is the supression of the vanishing of the density of states near zero energy.
+One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap; which is the non-zero density of states near zero energy.
 One of the mechanisms giving rise to a soft gap is the reduction of the induced gap for states with the momentum directed along the junction.

### 2019-03-01 paper/snakemajoranas.tex
explain what we mean by topological gap

@@
 \comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
-We propose a new experimental setup (see Fig.~\ref{fig:setup}(b)) for the creation of Majoranas that eliminates long trajectories and therefore prevents the appearance of a soft gap, while also increasing the topological gap by more than an order of magnitude, depending on the parameters.
+We propose a new experimental setup (see Fig.~\ref{fig:setup}(b)) for the creation of Majoranas that eliminates long trajectories and therefore prevents the appearance of a soft gap, while also increasing the topological gap (the smallest gap in the dispersion relation) by more than an order of magnitude, depending on the parameters.
 The setup consists of a zigzag or snake-like geometry for the semiconductor where long trajectories are not possible due to the geometry.

### 2019-03-01 paper/snakemajoranas.tex
make 'small gap' explicit

@@
 These long trajectories have long flight times $\tau_\textrm{f} \approx L_\textrm{t} / v_F$ (see Fig.~\ref{fig:setup}), where $L_\textrm{t}$ is the trajectory length.
-Equivalently, the Thouless energy of these trajectories $E_{\textrm{Th}}=\hbar / \tau_\textrm{f}$ is small, resulting in a small gap.
+Equivalently, the Thouless energy of these trajectories $E_{\textrm{Th}}=\hbar / \tau_\textrm{f}$ is small, resulting in a small gap $E_\textrm{gap} \ll \Delta$.
 This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, making a low filling of the bands a possible workaround\cite{nijholt2015orbital}.
@@
 A magnetic field $B$ pointing in the $x$-direction causes a Zeeman splitting in the semiconductor
-A trajectory traveling at a grazing angle (red curve) has a very long flight time $\tau_\textrm{f}$ and a very small induced gap $E_\textrm{gap}$.
+A trajectory traveling at a grazing angle (red curve) has a very long flight time $\tau_\textrm{f}$ and a very small induced gap $E_\textrm{gap} \ll \Delta$.
 At the same time, the zigzag geometry limits the length of a trajectory therefore lowering $\tau_\textrm{f}$ and increasing $E_\textrm{gap}$.

### 2019-03-01 paper/snakemajoranas.tex
cite 1902.11300

@@
 The straight system is in the symmetry class BDI \cite{pientka2017topological}.
-Using the software package Qsymm~\cite{varjas2018qsymm}, we find that the zigzag shape modulation violates the chiral symmetry, leaving only the particle-hole symmetry and the reflection symmetry with respect to the $x$-axis.
+Using the software package Qsymm~\cite{varjas2018qsymm}, we find that the zigzag shape modulation violates the chiral symmetry~\cite{1902.11300}, leaving only the particle-hole symmetry and the reflection symmetry with respect to the $x$-axis.
 

### 2019-03-01 paper/snakemajoranas.tex
explain the soft gap

@@
 \comment{The gap is small because of long trajectories.}
-One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap; which is the non-zero density of states near zero energy.
+One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap---the power law instead of the exponential suppression of the density of states near zero energy.
 One of the mechanisms giving rise to a soft gap is the reduction of the induced gap for states with the momentum directed along the junction.

### 2019-03-04 paper/snakemajoranas.tex
make note about the asymmetry of the phase diagram
add review refs

@@
 A hybrid structure containing a semiconductor with strong spin-orbit coupling coupled to a superconductor, inside a magnetic field becomes topological within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple nanowire), and Majorana bound states appear on its edges~\cite{lutchyn_majorana_2010,oreg_helical_2010}.
-Majorana bound states are a promising candidate to form the basis of a stable platform for topological quantum computing. ~\cite{alicea2012new,beenakker2013search}
+Majorana bound states are a promising candidate to form the basis of a stable platform for topological quantum computing.
+~\cite{alicea2012new,beenakker2013search,beenakker2016road,leijnse2012introduction}
 The current experimental effort ~\cite{mourik_signatures_2012,das_zero-bias_2012,deng_anomalous_2012,churchill_superconductor-nanowire_2013,zhang2018quantized} focuses on creating pairs of Majorana bound states in hybrid normal-superconductor (NS) nanowire structures.
@@
 The topological phase diagram of the zigzag system has a qualitatively similar shape but a significantly increased topological gap.
+The asymmetry of the phase diagram upon replacing $\phi \rightarrow -\phi$ is consistent with the symmetry of the Hamiltonian, because both inversion and time-reversal change both $\phi \rightarrow -\phi$ and $B_x \rightarrow -B_x$.
 

### 2019-03-04 paper/snakemajoranas.tex
reformat bib file

@@
 \comment{Hybrid NS structures become topological and are useful for TQC.}
-A hybrid structure containing a semiconductor with strong spin-orbit coupling coupled to a superconductor, inside a magnetic field becomes topological within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple nanowire), and Majorana bound states appear on its edges~\cite{lutchyn_majorana_2010,oreg_helical_2010}.
-Majorana bound states are a promising candidate to form the basis of a stable platform for topological quantum computing.
-~\cite{alicea2012new,beenakker2013search,beenakker2016road,leijnse2012introduction}
-The current experimental effort ~\cite{mourik_signatures_2012,das_zero-bias_2012,deng_anomalous_2012,churchill_superconductor-nanowire_2013,zhang2018quantized} focuses on creating pairs of Majorana bound states in hybrid normal-superconductor (NS) nanowire structures.
+A hybrid structure containing a semiconductor with strong spin-orbit coupling coupled to a superconductor, inside a magnetic field becomes topological within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple nanowire), and Majorana bound states appear on its edges~\cite{Lutchyn2010,Oreg2010}.
+Majorana bound states are a promising candidate to form the basis of a stable platform for topological quantum computing. ~\cite{Alicea2012,Beenakker2013,beenakker2016road,leijnse2012introduction}
+The current experimental effort ~\cite{Mourik2012,Das2012,Deng2012,Churchill2013,Zhang2018} focuses on creating pairs of Majorana bound states in hybrid normal-superconductor (NS) nanowire structures.
 
 \comment{SNS junctions also work and require smaller field.}
-Recently, a modified setup has been proposed\cite{pientka2017topological,hell2017two} relying on a superconductor-normal-superconductor (SNS) junction to lower the critical magnetic field $B_\textrm{c}$ by introducing a superconducting phase difference $\phi$.
+Recently, a modified setup has been proposed\cite{Pientka2017,Hell2017} relying on a superconductor-normal-superconductor (SNS) junction to lower the critical magnetic field $B_\textrm{c}$ by introducing a superconducting phase difference $\phi$.
 When both NS interfaces are transparent the SNS junction enters the topological phase at $\phi=\pi$ at any finite $B$ field.
-Two groups~\cite{fornieri_evidence_2018,ren_topological_2018} have realized this system experimentally but did not yet observe a hard induced gap.
+Two groups~\cite{Fornieri2018,Ren2018} have realized this system experimentally but did not yet observe a hard induced gap.
 
@@
 Equivalently, the Thouless energy of these trajectories $E_{\textrm{Th}}=\hbar / \tau_\textrm{f}$ is small, resulting in a small gap $E_\textrm{gap} \ll \Delta$.
-This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, making a low filling of the bands a possible workaround\cite{nijholt2015orbital}.
+This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, making a low filling of the bands a possible workaround\cite{Nijholt2015}.
 However, low filling requires precise knowledge of the system and is more sensitive to disorder or microscopic inhomogeneities.
-On the other hand, disorder scatters these long trajectories and introduces a cutoff on the scale of the mean free path~\cite{haim_double-edge_2018}; however, disorder is impossible to control to a required precision experimentally.
+On the other hand, disorder scatters these long trajectories and introduces a cutoff on the scale of the mean free path~\cite{Haim2018}; however, disorder is impossible to control to a required precision experimentally.
 
@@
 We modulate the shape of the normal region, which can be either zigzag as depicted [Fig.~\ref{fig:setup}(b)], or a more smooth sinusoidal-like shape.
-Similar to the conventional straight system \cite{pientka2017topological}, a magnetic field $B_x$ perpendicular to the junction is applied.
+Similar to the conventional straight system \cite{Pientka2017}, a magnetic field $B_x$ perpendicular to the junction is applied.
 We model the system with a Bogoliubov-de Gennes Hamiltonian (BdG):
@@
 \comment{We discretize the Hamiltonian and simulate it with Kwant.}
-We discretize our continuum Hamiltonian [Eq.~\eqref{eq:hamiltonian}] on a square grid and implement a tight-binding model using Kwant~\cite{groth_kwant:_2014}.
-To preferentially sample important regions of parameter space, we use the Adaptive package~\cite{adaptive}.
-The entire source code and the resulting raw data are available in Ref.~\onlinecite{data}.
+We discretize our continuum Hamiltonian [Eq.~\eqref{eq:hamiltonian}] on a square grid and implement a tight-binding model using Kwant~\cite{Groth2014}.
+To preferentially sample important regions of parameter space, we use the Adaptive package~\cite{Nijholt2019a}.
+The entire source code and the resulting raw data are available in Ref.~\onlinecite{Nijholt2019}.
 
@@
 We then find $\xi_\textrm{M}$ by fitting an exponential to the density of the single Majorana wave function projected on the $x$-axis.
-In the straight system we use the eigenvalue decomposition of the translation operator at zero energy~\cite{nijholt2015orbital} for performance reasons.
+In the straight system we use the eigenvalue decomposition of the translation operator at zero energy~\cite{Nijholt2015} for performance reasons.
 
@@
 Additionally, we plot the first $\SI{1300}{\nm}$ (one zigzag period) of the wave functions [(a) and (b)] at the optimal point in parameter space for the straight system.
-For the straight system, we calculate $E_\textrm{gap}$ by performing a binary search in $E$ for the energy at which the propagating modes start to appear~\cite{nijholt2015orbital}.
-Additionally, in Fig.~\ref{fig:phasediagrams}(c) we plot the phase boundaries obtained by solving a generalized eigenvalue problem~\cite{nijholt2015orbital}.
+For the straight system, we calculate $E_\textrm{gap}$ by performing a binary search in $E$ for the energy at which the propagating modes start to appear~\cite{Nijholt2015}.
+Additionally, in Fig.~\ref{fig:phasediagrams}(c) we plot the phase boundaries obtained by solving a generalized eigenvalue problem~\cite{Nijholt2015}.
 Due to the large size of the zigzag supercell, we are unable to apply these methods to zigzag geometries.
@@
 \comment{The introduction of a the zigzag breaks a chiral symmetry, bringing the system from the BDI to the D symmetry class}
-The straight system is in the symmetry class BDI \cite{pientka2017topological}.
-Using the software package Qsymm~\cite{varjas2018qsymm}, we find that the zigzag shape modulation violates the chiral symmetry~\cite{1902.11300}, leaving only the particle-hole symmetry and the reflection symmetry with respect to the $x$-axis.
+The straight system is in the symmetry class BDI \cite{Pientka2017}.
+Using the software package Qsymm~\cite{Varjas2018}, we find that the zigzag shape modulation violates the chiral symmetry~\cite{Setiawan2019}, leaving only the particle-hole symmetry and the reflection symmetry with respect to the $x$-axis.
 
 \comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry.}
-Similar to the findings of Pientka \textit{et al.}~\cite{pientka2017topological}, we see that the straight geometry has a diamond-shaped topological region.
+Similar to the findings of Pientka \textit{et al.}~\cite{Pientka2017}, we see that the straight geometry has a diamond-shaped topological region.
 We also observe additional gap closings due to the BDI symmetry.
@@
 We expect that the improvement of the device performance will significantly simplify the creation of Majorana devices and the detection of Majorana states.
-The zigzag geometry offers a controllable way to remove long trajectories, unlike disorder~\cite{haim_double-edge_2018} that otherwise has a similar effect.
+The zigzag geometry offers a controllable way to remove long trajectories, unlike disorder~\cite{Haim2018} that otherwise has a similar effect.
 
 \comment{Current fabrication techniques are compatible with the proposed geometry, and experimental verification can be near.}
-Current fabrication techniques are compatible with the proposed geometry; zigzag devices have already been fabricated~\cite{fokko_zigzag}.
+Current fabrication techniques are compatible with the proposed geometry; zigzag devices have already been fabricated~\cite{Vries}.
 We have demonstrated that the unavoidable variation in the experimental device geometry should not have a detrimental impact on the zigzag devices.

### 2019-03-05 paper/snakemajoranas.tex

@@
 A hybrid structure containing a semiconductor with strong spin-orbit coupling coupled to a superconductor, inside a magnetic field becomes topological within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple nanowire), and Majorana bound states appear on its edges~\cite{Lutchyn2010,Oreg2010}.
-Majorana bound states are a promising candidate to form the basis of a stable platform for topological quantum computing. ~\cite{Alicea2012,Beenakker2013,beenakker2016road,leijnse2012introduction}
+Majorana bound states are a promising candidate to form the basis of a stable platform for topological quantum computing. ~\cite{Alicea2012,Beenakker2013,Beenakker2016,Leijnse2012}
 The current experimental effort ~\cite{Mourik2012,Das2012,Deng2012,Churchill2013,Zhang2018} focuses on creating pairs of Majorana bound states in hybrid normal-superconductor (NS) nanowire structures.

### 2019-03-06 paper/snakemajoranas.tex
consistent E_z usage

@@
 \comment{Hybrid NS structures become topological and are useful for TQC.}
-A hybrid structure containing a semiconductor with strong spin-orbit coupling coupled to a superconductor, inside a magnetic field becomes topological within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple nanowire), and Majorana bound states appear on its edges~\cite{Lutchyn2010,Oreg2010}.
+A hybrid structure containing a semiconductor with strong spin-orbit coupling coupled to a superconductor, inside a magnetic field becomes topological within the right parameter regime ($E_\text{Z}^2>\mu^2+\Delta^2$ for a simple nanowire), and Majorana bound states appear on its edges~\cite{Lutchyn2010,Oreg2010}.
 Majorana bound states are a promising candidate to form the basis of a stable platform for topological quantum computing. ~\cite{Alicea2012,Beenakker2013,Beenakker2016,Leijnse2012}
@@
     H_\textrm{N} = & \left[\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu + \alpha \left( \ky \sigma_x - \kx \sigma_y \right) \right] \tau_z
-        + E_\text{z} \sigma_x, \\
+        + E_\text{Z} \sigma_x, \\
     H_\textrm{SC} = & \left[\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right] \tau_z
@@
 Here $H_\textrm{N}$ and $H_\textrm{SC}$ are the Hamiltonians of the semiconductor and superconductors, respectively.
-The normal part has a linear Rashba spin-orbit coupling term with strength $\alpha$ and a Zeeman field with $E_z=\frac{1}{2} \mu_B g B_x$.
+The normal part has a linear Rashba spin-orbit coupling term with strength $\alpha$ and a Zeeman field with $E_\text{Z}=\frac{1}{2} \mu_B g B_x$.
 The superconductor has a coupling term $\Delta$, and the phases of the superconductors equal to $\pm\phi/2$.

### 2019-03-08 paper/snakemajoranas.tex
MR for additonal references intro

@@
 \comment{Hybrid NS structures become topological and are useful for TQC.}
-A hybrid structure containing a semiconductor with strong spin-orbit coupling coupled to a superconductor, inside a magnetic field becomes topological within the right parameter regime ($E_\text{Z}^2>\mu^2+\Delta^2$ for a simple nanowire), and Majorana bound states appear on its edges~\cite{Lutchyn2010,Oreg2010}.
-Majorana bound states are a promising candidate to form the basis of a stable platform for topological quantum computing. ~\cite{Alicea2012,Beenakker2013,Beenakker2016,Leijnse2012}
-The current experimental effort ~\cite{Mourik2012,Das2012,Deng2012,Churchill2013,Zhang2018} focuses on creating pairs of Majorana bound states in hybrid normal-superconductor (NS) nanowire structures.
+A hybrid structure containing a semiconductor with strong spin-orbit coupling coupled to a superconductor can become topological upon application of a magnetic field stronger than a critical field $B_\textrm{crit}$, with Majorana bound states appearing on its edges~\cite{Lutchyn2010,Oreg2010}.
+Majorana bound states are a promising candidate to form the basis of a stable platform for topological quantum computing~\cite{Alicea2012,Beenakker2013,Beenakker2016,Leijnse2012}.
+Much of the experimental effort~\cite{Mourik2012,Das2012,Deng2012,Churchill2013,Zhang2018} currently focuses on creating pairs of Majorana bound states in hybrid normal-superconductor (NS) nanowire structures.
 
@@
 When both NS interfaces are transparent the SNS junction enters the topological phase at $\phi=\pi$ at any finite $B$ field.
-Two groups~\cite{Fornieri2018,Ren2018} have realized this system experimentally but did not yet observe a hard induced gap.
+Two groups~\cite{Fornieri2018,Ren2018} have realized this system experimentally, but did not yet observe a hard induced superconducting gap.
 
 \comment{The gap is small because of long trajectories.}
-One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap---the power law instead of the exponential suppression of the density of states near zero energy.
-One of the mechanisms giving rise to a soft gap is the reduction of the induced gap for states with the momentum directed along the junction.
+An important challenge in creating stable Majoranas is the appearance of a soft gap---a power law, instead of exponential decay of the density of states near zero energy.
+It was shown previously that interface disorder and pairbreaking lead to a soft induced gap~\cite{takei_soft_2013}.
+Even in systems with perfect interfaces and the absence of pairbreaking, states which have their momentum directed along the junction give rise to a soft gap~\cite{de_gennes_1963, beenakker_billiards_2005}.
 From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor, shown in Fig.~\ref{fig:setup}(a).
@@
 We are grateful to  S. Goswami, A. Keselman, P. P. Piskunow, T. Ö. Rosdahl, D. Varjas, F. K. de Vries, Q. Wang, and J. B. Weston for useful discussions.
-This work was supported by the Netherlands Organization for Scientific Research (NWO/OCW), as part of the Frontiers of Nanoscience program, a NWO VIDI Grant (016.Vidi.189.180), and an ERC Starting Grant STATOPINS 638760.
+This work was supported by the Netherlands Organization for Scientific Research (NWO/OCW), as part of the Frontiers of Nanoscience program, two NWO VIDI grants (016.Vidi.189.180 and 680-47-537), and an ERC Starting Grant STATOPINS 638760.
 
@@
 B.N. wrote the code and it was extended by T.L.
-B.N. performed the writing of the manuscript with input of T.L. and A.A.
+B.N. performed the writing of the manuscript with input of T.L., M.W., and A.A.
 All authors performed the analysis of the results and planning of the project.

### 2019-03-11 paper/snakemajoranas.tex
start slight rewrite of intro

--- 2019-03-06 paper/snakemajoranas.tex
@@
 \comment{Hybrid NS structures become topological and are useful for TQC.}
-A hybrid structure containing a semiconductor with strong spin-orbit coupling coupled to a superconductor, inside a magnetic field becomes topological within the right parameter regime ($E_\text{Z}^2>\mu^2+\Delta^2$ for a simple nanowire), and Majorana bound states appear on its edges~\cite{Lutchyn2010,Oreg2010}.
+A hybrid structure containing a semiconductor with strong spin-orbit coupling coupled to a superconductor can become topological upon application of a magnetic field stronger than a critical field $B_\textrm{crit}$, with Majorana bound states appearing on its edges~\cite{Lutchyn2010,Oreg2010}.
 Majorana bound states are a promising candidate to form the basis of a stable platform for topological quantum computing. ~\cite{Alicea2012,Beenakker2013,Beenakker2016,Leijnse2012}
-The current experimental effort ~\cite{Mourik2012,Das2012,Deng2012,Churchill2013,Zhang2018} focuses on creating pairs of Majorana bound states in hybrid normal-superconductor (NS) nanowire structures.
+Much of the experimental effort ~\cite{Mourik2012,Das2012,Deng2012,Churchill2013,Zhang2018} currently focus on creating pairs of Majorana bound states in hybrid normal-superconductor (NS) nanowire structures.
 
@@
 When both NS interfaces are transparent the SNS junction enters the topological phase at $\phi=\pi$ at any finite $B$ field.
-Two groups~\cite{Fornieri2018,Ren2018} have realized this system experimentally but did not yet observe a hard induced gap.
+Two groups~\cite{Fornieri2018,Ren2018} have realized this system experimentally, but did not yet observe a hard induced superconducting gap.
 

### 2019-03-12 paper/snakemajoranas.tex
mention more causes of a soft gap

--- 2019-03-08 paper/snakemajoranas.tex
@@
 \comment{The gap is small because of long trajectories.}
-An important challenge in creating stable Majoranas is the appearance of a soft gap---a power law, instead of exponential decay of the density of states near zero energy.
-It was shown previously that interface disorder and pairbreaking lead to a soft induced gap~\cite{takei_soft_2013}.
-Even in systems with perfect interfaces and the absence of pairbreaking, states which have their momentum directed along the junction give rise to a soft gap~\cite{de_gennes_1963, beenakker_billiards_2005}.
+An important challenge in creating stable Majoranas is the appearance of a soft gap---a power law decay instead of an exponential decay of the density of states near zero energy.~\cite{liu_soft_gap_phenomenology}
+It has been shown that interface disorder, pairbreaking, tunnel barrier to normal leads, temperature, and having multimodes with different transmission probabilities, and dissipation can cause a soft induced gap~\cite{takei_soft_2013,liu_soft_gap_phenomenology,stanescu_soft_gap_2014}.
+However, even without the aforementioned causes, a soft gap would still appear due to states with their momentum parallel to the junction~\cite{de_gennes_1963,beenakker_billiards_2005}.
 From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor, shown in Fig.~\ref{fig:setup}(a).

### 2019-03-12 paper/snakemajoranas.tex
format bibfile

--- 2019-03-08 paper/snakemajoranas.tex
@@
 \comment{The gap is small because of long trajectories.}
-An important challenge in creating stable Majoranas is the appearance of a soft gap---a power law, instead of exponential decay of the density of states near zero energy.
-It was shown previously that interface disorder and pairbreaking lead to a soft induced gap~\cite{takei_soft_2013}.
-Even in systems with perfect interfaces and the absence of pairbreaking, states which have their momentum directed along the junction give rise to a soft gap~\cite{de_gennes_1963, beenakker_billiards_2005}.
+An important challenge in creating stable Majoranas is the appearance of a soft gap---a power law decay instead of an exponential decay of the density of states near zero energy.
+It has been shown that interface disorder, pairbreaking, tunnel barrier to normal leads, temperature, and having multiple modes with different transmission probabilities, and dissipation can cause a soft induced gap~\cite{Takei2013,Liu2017,Stanescu2014}.
+However, even without the aforementioned causes, a soft gap would still appear due to states with their momentum parallel to the junction~\cite{Gennes1963,Beenakker2005}.
 From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor, shown in Fig.~\ref{fig:setup}(a).

### 2019-03-13 paper/snakemajoranas.tex
move discussion of other soft gap papers to "Discussion"

@@
 An important challenge in creating stable Majoranas is the appearance of a soft gap---a power law decay instead of an exponential decay of the density of states near zero energy.
-It has been shown that interface disorder, pairbreaking, tunnel barrier to normal leads, temperature, and having multiple modes with different transmission probabilities, and dissipation can cause a soft induced gap~\cite{Takei2013,Liu2017,Stanescu2014}.
-However, even without the aforementioned causes, a soft gap would still appear due to states with their momentum parallel to the junction~\cite{Gennes1963,Beenakker2005}.
+
+In clean systems, one mechanisms giving rise to a soft gap is the reduction of the
+induced gap for states with the momentum directed along the
+junction~\cite{Gennes1963,Beenakker2005}.
 From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor, shown in Fig.~\ref{fig:setup}(a).
@@
 Equivalently, the Thouless energy of these trajectories $E_{\textrm{Th}}=\hbar / \tau_\textrm{f}$ is small, resulting in a small gap $E_\textrm{gap} \ll \Delta$.
-This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, making a low filling of the bands a possible workaround\cite{Nijholt2015}.
+This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, making a low filling of the bands a possible workaround\cite{Beenakker2005, Nijholt2015}.
 However, low filling requires precise knowledge of the system and is more sensitive to disorder or microscopic inhomogeneities.
-On the other hand, disorder scatters these long trajectories and introduces a cutoff on the scale of the mean free path~\cite{Haim2018}; however, disorder is impossible to control to a required precision experimentally.
+On the other hand, disorder scatters long trajectories and introduces a cutoff on the scale of the mean free path~\cite{Haim2018}; however, disorder is impossible to control to a required precision experimentally.
 
@@
 
+Previously it had been shown that various mechanisms can give rise to a soft gap: interface disorder and pairbreaking,\cite{Takei2013}, a multi-mode tunnel barrier,\cite{Stanescu2014} or temperature and dissipation.\cite{Liu2017} Even in the absence of these effects, long trajectories will lead to a soft gap in the high density limit.
+The zigzag geometry addresses this intrinsic problem.
+
 \comment{Current fabrication techniques are compatible with the proposed geometry, and experimental verification can be near.}

### 2019-03-14 paper/snakemajoranas.tex
Removed typo -- Update snakemajoranas.tex

@@
 
-In clean systems, one mechanisms giving rise to a soft gap is the reduction of the
+In clean systems, one mechanism giving rise to a soft gap is the reduction of the
 induced gap for states with the momentum directed along the

### 2019-03-14 paper/snakemajoranas.tex
rephrase the discussion of other mechanisms

@@
 An important challenge in creating stable Majoranas is the appearance of a soft gap---a power law decay instead of an exponential decay of the density of states near zero energy.
-
-In clean systems, one mechanism giving rise to a soft gap is the reduction of the
-induced gap for states with the momentum directed along the
-junction~\cite{Gennes1963,Beenakker2005}.
+In clean systems soft gap arises due to the reduction of the induced gap for states with the momentum directed along the junction~\cite{Gennes1963,Beenakker2005}.
 From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor, shown in Fig.~\ref{fig:setup}(a).
@@
 We expect that the improvement of the device performance will significantly simplify the creation of Majorana devices and the detection of Majorana states.
-The zigzag geometry offers a controllable way to remove long trajectories, unlike disorder~\cite{Haim2018} that otherwise has a similar effect.
+The zigzag geometry offers a controllable way to remove long trajectories, making it easier to rely on than disorder~\cite{Haim2018}, that otherwise has a similar effect.
 
-Previously it had been shown that various mechanisms can give rise to a soft gap: interface disorder and pairbreaking,\cite{Takei2013}, a multi-mode tunnel barrier,\cite{Stanescu2014} or temperature and dissipation.\cite{Liu2017} Even in the absence of these effects, long trajectories will lead to a soft gap in the high density limit.
-The zigzag geometry addresses this intrinsic problem.
+\comment{Zigzag doesn't do anything against other mechanisms, and therefore it doesn't help to use it ignorantly}
+Soft gap may arise due to other mechanisms that do not involve ballistic trajectories: both interface disorder and pair breaking~\cite{Takei2013} or temperature and dissipation~\cite{Liu2017} may create a soft gap.
+Further in a multimode junction the mode dependence of transmission~\cite{Stanescu2014} may produce subgap conductance similar to that in a device with a soft gap.
+The zigzag geometry has no impact on these alternative phenomena, and it may therefore serve as a tool in distinguishing different mechanisms.
 

### 2019-03-14 paper/snakemajoranas.tex
minor fixes

--- 2019-03-14 paper/snakemajoranas.tex
@@
 \comment{The gap is small because of long trajectories.}
-An important challenge in creating stable Majoranas is the appearance of a soft gap---a power law decay instead of an exponential decay of the density of states near zero energy.
-
-In clean systems, one mechanism giving rise to a soft gap is the reduction of the
-induced gap for states with the momentum directed along the
-junction~\cite{Gennes1963,Beenakker2005}.
+One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap---the power law instead of the exponential suppression of the density of states near zero energy.
+One of the mechanisms giving rise to a soft gap is the reduction of the induced gap for states with the momentum directed along the junction.
 From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor, shown in Fig.~\ref{fig:setup}(a).
@@
 Equivalently, the Thouless energy of these trajectories $E_{\textrm{Th}}=\hbar / \tau_\textrm{f}$ is small, resulting in a small gap $E_\textrm{gap} \ll \Delta$.
-This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, making a low filling of the bands a possible workaround\cite{Beenakker2005, Nijholt2015}.
+This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, making a low filling of the bands a possible workaround\cite{Nijholt2015}.
 However, low filling requires precise knowledge of the system and is more sensitive to disorder or microscopic inhomogeneities.
-On the other hand, disorder scatters long trajectories and introduces a cutoff on the scale of the mean free path~\cite{Haim2018}; however, disorder is impossible to control to a required precision experimentally.
+On the other hand, disorder scatters these long trajectories and introduces a cutoff on the scale of the mean free path~\cite{Haim2018}; however, disorder is impossible to control to a required precision experimentally.
 
@@
 
-Previously it had been shown that various mechanisms can give rise to a soft gap: interface disorder and pairbreaking,\cite{Takei2013}, a multi-mode tunnel barrier,\cite{Stanescu2014} or temperature and dissipation.\cite{Liu2017} Even in the absence of these effects, long trajectories will lead to a soft gap in the high density limit.
-The zigzag geometry addresses this intrinsic problem.
-
 \comment{Current fabrication techniques are compatible with the proposed geometry, and experimental verification can be near.}
@@
 We are grateful to  S. Goswami, A. Keselman, P. P. Piskunow, T. Ö. Rosdahl, D. Varjas, F. K. de Vries, Q. Wang, and J. B. Weston for useful discussions.
-This work was supported by the Netherlands Organization for Scientific Research (NWO/OCW), as part of the Frontiers of Nanoscience program, two NWO VIDI grants (016.Vidi.189.180 and 680-47-537), and an ERC Starting Grant STATOPINS 638760.
+This work was supported by the Netherlands Organization for Scientific Research (NWO/OCW), as part of the Frontiers of Nanoscience program, a NWO VIDI Grant (016.Vidi.189.180), and an ERC Starting Grant STATOPINS 638760.
 
@@
 B.N. wrote the code and it was extended by T.L.
-B.N. performed the writing of the manuscript with input of T.L., M.W., and A.A.
+B.N. performed the writing of the manuscript with input of T.L. and A.A.
 All authors performed the analysis of the results and planning of the project.

### 2019-03-14 paper/snakemajoranas.tex
disorder refs

--- 2019-03-14 paper/snakemajoranas.tex
@@
 However, low filling requires precise knowledge of the system and is more sensitive to disorder or microscopic inhomogeneities.
-On the other hand, disorder scatters long trajectories and introduces a cutoff on the scale of the mean free path~\cite{Haim2018}; however, disorder is impossible to control to a required precision experimentally.
+On the other hand, disorder scatters these long trajectories and introduces a cutoff on the scale of the mean free path~\cite{Golubov1988,Belzig1996,Pilgram2000} which Ref.~\onlinecite{Haim2018} proposes to use to improve Majorana properties; however, disorder is impossible to control to a required precision experimentally.
 

### 2019-03-14 paper/snakemajoranas.tex
change in authors contributions

@@
 Equivalently, the Thouless energy of these trajectories $E_{\textrm{Th}}=\hbar / \tau_\textrm{f}$ is small, resulting in a small gap $E_\textrm{gap} \ll \Delta$.
-This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, making a low filling of the bands a possible workaround\cite{Beenakker2005, Nijholt2015}.
+This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, making a low filling of the bands a possible workaround\cite{Beenakker2005,Nijholt2015}.
 However, low filling requires precise knowledge of the system and is more sensitive to disorder or microscopic inhomogeneities.
@@
 B.N. wrote the code and it was extended by T.L.
-B.N. performed the writing of the manuscript with input of T.L., M.W., and A.A.
+B.N. performed the writing of the manuscript with input of the other authors.
 All authors performed the analysis of the results and planning of the project.

### 2019-03-14 paper/snakemajoranas.tex
remove old figure
use symbols in the abstract

@@
 Because a large induced gap protects Majorana modes, these long trajectories constrain Majorana devices to a low electron density.
-We show that a zigzag-shaped geometry eliminates these trajectories, allowing the robust creation of Majorana states with both the induced gap and the Majorana size improved by more than an order of magnitude for realistic parameters.
+We show that a zigzag-shaped geometry eliminates these trajectories, allowing the robust creation of Majorana states with both the induced gap $E_\textrm{gap}$ and the Majorana size $\xi_\textrm{M}$ improved by more than an order of magnitude for realistic parameters.
 In addition to the improved robustness of Majoranas, this new zigzag geometry is insensitive to the geometric details and the device tuning.

### 2019-03-15 paper/snakemajoranas.tex
fix typo stuctures -> structures
fix sentence in caption

@@
 %%██████████████████████████████████████████████████████████████████████████
-%%██ Band stuctures
+%%██ Band structures
 %%██████████████████████████████████████████████████████████████████████████
-\section{Band stuctures}\label{sec:band_structures}
+\section{Band structures}\label{sec:band_structures}
 
@@
 \includegraphics[width=\columnwidth]{figures/bandstructures}
-\caption{Band stuctures of the system in Fig.~\ref{fig:setup}(b) with different zigzag amplitudes.
+\caption{Band structures of the system in Fig.~\ref{fig:setup}(b) with different zigzag amplitudes.
 The blue lines correspond to a trivial phase ($\phi=0$, $B_x = 0$) and the orange lines to a topological phase ($\phi=\pi$, $B_x = \SI{1}{T}$).
@@
 \includegraphics[width=\columnwidth]{figures/wavefunctions}
-\caption{Density of Majorana wave functions $\left| \psi_\textrm{M} \right|^2$ for sizes and geometries.
+\caption{Density of Majorana wave functions $\left| \psi_\textrm{M} \right|^2$ for different geometries.
 With (a) a straight system, (b) a zigzag system, (c) a system where lines parallel to a sinusoid defines the normal region, and (d) similar to (c) but with disordered edges.

### 2019-08-02 paper/snakemajoranas.tex
adding an appendix with paragraph sentences

@@
 This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, making a low filling of the bands a possible workaround\cite{Beenakker2005,Nijholt2015}.
-However, low filling requires precise knowledge of the system and is more sensitive to disorder or microscopic inhomogeneities.
+However, tuning the system to a low chemical potential requires a precise knowledge of the band positions and makes the device more sensitive to disorder or microscopic inhomogeneities.
 On the other hand, disorder scatters these long trajectories and introduces a cutoff on the scale of the mean free path~\cite{Golubov1988,Belzig1996,Pilgram2000} which Ref.~\onlinecite{Haim2018} proposes to use to improve Majorana properties; however, disorder is impossible to control to a required precision experimentally.
@@
 \label{eq:xi_M}
-\xi_\textrm{M}=\hbar \frac{v_\textrm{F}}{E_\textrm{gap}},
+\xi_\textrm{M}=\hbar \frac{v_\textrm{F}}{E_\textrm{gap}}.
 \end{equation}
-and therefore a minimal topological protection against perturbations.
-The wave function extends to the center of the system, resulting in highly overlapping Majoranas and a Majorana coupling $E_\textrm{M}$ comparable to $E_\textrm{gap}$.
+This result follows from an avoided crossing shape of the dispersion relation near the Fermi momentum.
+Therefore, in straight junctions the wave function extends to the center of the system, resulting in highly overlapping Majoranas and a Majorana coupling $E_\textrm{M}$ comparable to $E_\textrm{gap}$.
 
@@
 \bibliography{snakemajoranas}
+
+\appendix
+
+\section{Zigzag device with a single superconductor}
+
+\comment{The same principle applies to devices with only one superconductor.}
+
+\comment{We run the simulation and observe that the phase diagrams are the same but the zigzag device is still better.}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=0.9\columnwidth]{figures/ns_junction.pdf}
+\caption{Same as Fig.~\ref{fig:phasediagrams} but with one superconductor instead of two.
+\label{fig:ns_junction}}
+\end{figure}
+
+\section{Direction of the magnetic field}
+
+\comment{Short trajectories are less sensitive to the alignment of magnetic field.}
+
+\comment{Zigzag geometry removes the need for precise field alignment.}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=0.9\columnwidth]{figures/tilted_angle_phase_diagram.pdf}
+\caption{A comparison of a straight device (left panels) and a zigzag one (right panels) where the magnetic is rotated.
+% E_gap(B, angle, \phi=\pi)
+\label{fig:tilted_angle_phase_diagram}}
+\end{figure}
+
+\comment{In a realistic device the magnetic field might not be inhomogeneous, but zigzag doesn't care.}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=0.9\columnwidth]{figures/snaking_magnetic_field.pdf}
+\caption{
+% Fig 4. (d) and (f) with snaking B
+\label{fig:snaking_magnetic_field}}
+\end{figure}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=0.9\columnwidth]{figures/bandstructure_of_small_period_zigzag.pdf}
+\caption{The effect of increased transparency.
+% Like Fig 2. (b) plus horizontal dashed lines indicating the gap of zigzag and straight junctions
+\label{fig:bandstructure_of_small_period_zigzag}}
+\end{figure}
+
 \end{document}

### 2019-08-02 paper/referee_responses.md
add a crude draft of the referee response

> # Report of Referee A -- LD17005/Laeven
> The manuscript discusses numerical calculations related to how to improve the energy gap in 2D planar Josephson junctions.
> The manuscript considers 2D SNS junctions within clean-limit BdG tight-binding model, used also in previous studies of the same system. Specific N region geometry is considered, and found to improve the energy gap. The argument why this occurs appears clear, and the results valid. Improving energy gaps likely is useful, but it's less clear this is the main/only problem faced in the experiments.
> The effect of long trajectories in ballistic systems is itself not surprising or new, but optimizing the geometry for this in the specific context of Majorana realizations with planar SNS was apparently not considered before. The closer study of this is the main new contribution here.
> However, the manuscript appears better suited for publication in PRB. Although optimizing parameters in a previously discussed model is interesting and probably useful for future experiments of this type, it does not appear a significant advance of wide interest to a broad audience.

This is a conceptually new idea, overlooked in a very mature field, which makes it exciting and it seems to resonate with a lot of people.
Even though the effect of long trajectories was known to DeGennes, the idea of optimizing the geometry to eliminate long trajectories has not previously been considered even outside of the Majorana context.

> # Report of Referee B -- LD17005/Laeven
> The authors consider a planar Josephson junction in a zigzag geometry and propose it as an improved realization of a one-dimensional topological superconductor. As they show using numerical simulations, the zigzag geometry increases the induced superconducting gap and thereby decreases the spatial size of the Majorana wave functions, making them more protected.
> To the best of my knowledge the idea presented in the paper is novel. In my opinion, this work will influence future experiments, and can help solve the problem of a small topological gap in the planar Josephson junction. Moreover, the paper is well written. Assuming the authors can address the questions and comments listed below, I therefore recommend the publication of the paper in Physical Review Letters.
> My biggest concern has to do with the direction of the magnetic field as it is given in Eq. (1). The magnetic field considered in Eq. (1) does not penetrate the superconductor which is certainly reasonable. I think, however, that this is not consistent with the uniformly-directed magnetic field in the normal region (see B\sigma_x in Eq. (1a)). I would expect that in the zigzag geometry the magnetic field lines would be forced to curve in a zigzag manner to avoid approaching the superconductors in a direct angle. In this case, the direction of the Zeeman term in Eq. (1a) would depend on space. Can the authors give a compelling argument for why this would not affect the main results (or alternatively simulate a spatially-dependent magnetic field)?

The flatness of the superconductors may diminish but in order to consider inhomogeneity, we exaggerate the effect by considering a magnetic field which is always perfectly aligned with the nanowire, corresponding to perfect expulsion.
We have added a section to the appendix and done several simulations to answer these concerns.

> At the end of section III, the authors explain that besides the effect of increasing the gap through eliminating modes traveling at grazing angles, the zigzag geometry has two more effects that causes the Majorana size to decrease: (1) reducing the Fermi velocity, and (2) increasing transmission to the SC. With regards to (1), I would comment that the Fermi velocity that enters the formula \xi=v_F/E_gap is the electron velocity before introducing superconductivity. The fact that the bandstructure becomes flatter is not a testament to the Fermi velocity becoming smaller since superconductivity is already present. With regards to (2), it seems to me that this is exactly the original effect that increases the gap, and should not be counted as a separate effect. Indeed, the transmission of electrons traveling at grazing angles is originally very small (it’s not zero though due to the uncertainty principle), and it becomes bigger since the incident angle is now more direct.

After the Eq. (2) we have added a remark that this equation follows from an avoided crossing shape of the dispersion relation near the Fermi momentum. This relation does not assume anything about the nature of v_F or of E_gap.

The separate two phenomena, we have simulated a straight junction where the boundary is also corrugated so that the incident angle of the grazing trajectories is higher. In Fig. ? we see that the gap is indeed increased due to that phenomenon.

> Some smaller issues:
> Can the authors clarify the following statement from the introduction: “However, low filling requires precise knowledge of the system and is more sensitive to disorder or microscopic inhomogeneities”.

We thank the referee for pointing us to this vague sentence. We have changed it to "However, tuning the system to a low chemical potential requires precise knowledge of the band positions and makes the device more sensitive to disorder or microscopic inhomogeneities."

> In the Discussion section, the authors mention that interface disorder can still cause a soft gap. Wasn’t that simulated in Fig. (3d)? A similar statement is made about a multimode junction. Does this refer to transverse modes in the z direction (perpendicular to the 2DEG)? because the system considered in the paper is indeed a multimode junction (due to the finite size in the y direction - W). Perhaps I didn’t understand the idea of the paragraph.

The reference 29 considers a change in the barrier transparency and a longer correlation length and is therefore not the same. Reference 31 describes a multimode mechanism and is about how the conductance looks rather than about the actual gap.

### 2019-08-12 paper/snakemajoranas.tex
increase fig resolution and add some text

@@
 \comment{The same principle applies to devices with only one superconductor.}
-
-\comment{We run the simulation and observe that the phase diagrams are the same but the zigzag device is still better.}
+In this letter we have focused on SNS junctions and showed that $E_\textrm{gap}$ is significantly increased when going from a straight device to a zigzag device, however, with a single superconductor the same principles still apply, although the effect is less significant.
 
@@
 \centering
-\includegraphics[width=0.9\columnwidth]{figures/ns_junction.pdf}
-\caption{Same as Fig.~\ref{fig:phasediagrams} but with one superconductor instead of two.
+\includegraphics[width=0.9\columnwidth]{figures/phasediagrams_NS.pdf}
+\caption{Same as Fig.~\ref{fig:phasediagrams} (c) and (d) but with one superconductor instead of two.
+We observe that the zigzag geometry also increases the gap in this case.
 \label{fig:ns_junction}}
 \end{figure}
+
+\comment{We run the simulation and observe that the phase diagrams are the same but the zigzag device is still better.}
+We show this through a numerical simulation of a straight and a zigzag device where we compute $E_\textrm{gap}(B_x, \; \mu)$ in Fig.~\ref{fig:ns_junction}.
+Here we see that the order of magnitude increase of $E_\textrm{gap}$ also occurs upon the introducation of a zigzag geometry.
 

### 2019-08-12 paper/snakemajoranas.tex
comment out figures that do not exist
black the notebook

@@
 \includegraphics[width=0.9\columnwidth]{figures/tilted_angle_phase_diagram.pdf}
-\caption{A comparison of a straight device (left panels) and a zigzag one (right panels) where the magnetic is rotated.
-% E_gap(B, angle, \phi=\pi)
+\caption{A comparison of a straight device (a) and a zigzag one (b) where the magnetic field is rotated.
+On the x-axis is the the magnetic field $B$ and on the y-axis is the angle $\theta=\arctan{B_y/B_x}$ in degrees.
+The colormaps and the y-axis have a different scale for both panels.
+We see that the device with the zigzag geometry is much more resilient against a misaligned magnetic field.
 \label{fig:tilted_angle_phase_diagram}}
@@
 
-\begin{figure}[!htb]
-\centering
-\includegraphics[width=0.9\columnwidth]{figures/snaking_magnetic_field.pdf}
-\caption{
-% Fig 4. (d) and (f) with snaking B
-\label{fig:snaking_magnetic_field}}
-\end{figure}
+% \begin{figure}[!htb]
+% \centering
+% \includegraphics[width=0.9\columnwidth]{figures/snaking_magnetic_field.pdf}
+% \caption{
+% % Fig 4. (d) and (f) with snaking B
+% \label{fig:snaking_magnetic_field}}
+% \end{figure}
 
-\begin{figure}[!htb]
-\centering
-\includegraphics[width=0.9\columnwidth]{figures/bandstructure_of_small_period_zigzag.pdf}
-\caption{The effect of increased transparency.
-% Like Fig 2. (b) plus horizontal dashed lines indicating the gap of zigzag and straight junctions
-\label{fig:bandstructure_of_small_period_zigzag}}
-\end{figure}
+% \begin{figure}[!htb]
+% \centering
+% \includegraphics[width=0.9\columnwidth]{figures/bandstructure_of_small_period_zigzag.pdf}
+% \caption{The effect of increased transparency.
+% % Like Fig 2. (b) plus horizontal dashed lines indicating the gap of zigzag and straight junctions
+% \label{fig:bandstructure_of_small_period_zigzag}}
+% \end{figure}
 

### 2019-08-12 dependencies/adaptive_tools.py
black the paper-figure notebook and the code

@@ -15,38 +15,36 @@ import toolz
 
 
 class Learner1D(adaptive.Learner1D):
-
     def save(self, folder, fname, compress=True):
         os.makedirs(folder, exist_ok=True)
         fname = os.path.join(folder, fname)
         _open = gzip.open if compress else open
-        with _open(fname, 'wb') as f:
+        with _open(fname, "wb") as f:
             pickle.dump(self.data, f, protocol=pickle.HIGHEST_PROTOCOL)
 
     def load(self, folder, fname, compress=True):
         _open = gzip.open if compress else open
         fname = os.path.join(folder, fname)
         try:
-            with _open(fname, 'rb') as f:
+            with _open(fname, "rb") as f:
                 self.data = pickle.load(f)
         except FileNotFoundError:
             pass
 
 
 class Learner2D(adaptive.Learner2D):
-
     def save(self, folder, fname, compress=True):
         os.makedirs(folder, exist_ok=True)
         fname = os.path.join(folder, fname)
         _open = gzip.open if compress else open
-        with _open(fname, 'wb') as f:
+        with _open(fname, "wb") as f:
             pickle.dump(self.data, f, protocol=pickle.HIGHEST_PROTOCOL)
 
     def load(self, folder, fname, compress=True):
         _open = gzip.open if compress else open
         fname = os.path.join(folder, fname)
         try:
-            with _open(fname, 'rb') as f:
+            with _open(fname, "rb") as f:
                 self.data = pickle.load(f)
                 self.refresh_stack()
         except FileNotFoundError:
@@ -60,31 +58,33 @@ class Learner2D(adaptive.Learner2D):
 
 
 class BalancingLearner(adaptive.BalancingLearner):
-
-    def save(self, folder, fname_pattern='data_learner_{}.pickle',
-             compress=True):
+    def save(self, folder, fname_pattern="data_learner_{}.pickle", compress=True):
         os.makedirs(folder, exist_ok=True)
         for i, learner in enumerate(self.learners):
-            fname = fname_pattern.format(f'{i:04d}')
+            fname = fname_pattern.format(f"{i:04d}")
             learner.save(folder, fname, compress=compress)
 
-    def load(self, folder, fname_pattern='data_learner_{}.pickle',
-             compress=True):
+    def load(self, folder, fname_pattern="data_learner_{}.pickle", compress=True):
         for i, learner in enumerate(self.learners):
-            fname = fname_pattern.format(f'{i:04d}')
+            fname = fname_pattern.format(f"{i:04d}")
[…]

### 2019-08-12 dependencies/hpc05.py

@@ -24,7 +24,7 @@ def householder_real(x):
     if sigma == 0:
         return (np.zeros(x.shape[0]), 0, x[0])
     else:
-        norm_x = math.sqrt(x[0]**2 + sigma)
+        norm_x = math.sqrt(x[0] ** 2 + sigma)
 
         v = x.copy()
 
@@ -111,22 +111,22 @@ def skew_tridiagonalize(A, overwrite_a=False, calc_q=True):
 
     for i in range(A.shape[0] - 2):
         # Find a Householder vector to eliminate the i-th column
-        v, tau, alpha = householder(A[i + 1:, i])
+        v, tau, alpha = householder(A[i + 1 :, i])
         A[i + 1, i] = alpha
         A[i, i + 1] = -alpha
-        A[i + 2:, i] = 0
-        A[i, i + 2:] = 0
+        A[i + 2 :, i] = 0
+        A[i, i + 2 :] = 0
 
         # Update the matrix block A(i+1:N,i+1:N)
-        w = tau * A[i + 1:, i + 1:] @ v.conj()
-        A[i + 1:, i + 1:] += np.outer(v, w) - np.outer(w, v)
+        w = tau * A[i + 1 :, i + 1 :] @ v.conj()
+        A[i + 1 :, i + 1 :] += np.outer(v, w) - np.outer(w, v)
 
         if calc_q:
             # Accumulate the individual Householder reflections
             # Accumulate them in the form P_1*P_2*..., which is
             # (..*P_2*P_1)^dagger
-            y = tau * Q[:, i + 1:] @ v
-            Q[:, i + 1:] -= np.outer(y, v.conj())
+            y = tau * Q[:, i + 1 :] @ v
+            Q[:, i + 1 :] -= np.outer(y, v.conj())
 
     if calc_q:
         return (np.asmatrix(A), np.asmatrix(Q))
@@ -167,7 +167,7 @@ def skew_LTL(A, overwrite_a=False, calc_L=True, calc_P=True):
     for k in range(n - 2):
         # First, find the largest entry in A[k+1:,k] and
         # permute it to A[k+1,k]
-        kp = k + 1 + np.abs(A[k + 1:, k]).argmax()
+        kp = k + 1 + np.abs(A[k + 1 :, k]).argmax()
 
         # Check if we need to pivot
         if kp != k + 1:
@@ -183,9 +183,9 @@ def skew_LTL(A, overwrite_a=False, calc_L=True, calc_P=True):
 
             if calc_L:
[…]

### 2019-08-12 dependencies/pfaffian.py

@@ -24,7 +24,7 @@ def householder_real(x):
     if sigma == 0:
         return (np.zeros(x.shape[0]), 0, x[0])
     else:
-        norm_x = math.sqrt(x[0]**2 + sigma)
+        norm_x = math.sqrt(x[0] ** 2 + sigma)
 
         v = x.copy()
 
@@ -111,22 +111,22 @@ def skew_tridiagonalize(A, overwrite_a=False, calc_q=True):
 
     for i in range(A.shape[0] - 2):
         # Find a Householder vector to eliminate the i-th column
-        v, tau, alpha = householder(A[i + 1:, i])
+        v, tau, alpha = householder(A[i + 1 :, i])
         A[i + 1, i] = alpha
         A[i, i + 1] = -alpha
-        A[i + 2:, i] = 0
-        A[i, i + 2:] = 0
+        A[i + 2 :, i] = 0
+        A[i, i + 2 :] = 0
 
         # Update the matrix block A(i+1:N,i+1:N)
-        w = tau * A[i + 1:, i + 1:] @ v.conj()
-        A[i + 1:, i + 1:] += np.outer(v, w) - np.outer(w, v)
+        w = tau * A[i + 1 :, i + 1 :] @ v.conj()
+        A[i + 1 :, i + 1 :] += np.outer(v, w) - np.outer(w, v)
 
         if calc_q:
             # Accumulate the individual Householder reflections
             # Accumulate them in the form P_1*P_2*..., which is
             # (..*P_2*P_1)^dagger
-            y = tau * Q[:, i + 1:] @ v
-            Q[:, i + 1:] -= np.outer(y, v.conj())
+            y = tau * Q[:, i + 1 :] @ v
+            Q[:, i + 1 :] -= np.outer(y, v.conj())
 
     if calc_q:
         return (np.asmatrix(A), np.asmatrix(Q))
@@ -167,7 +167,7 @@ def skew_LTL(A, overwrite_a=False, calc_L=True, calc_P=True):
     for k in range(n - 2):
         # First, find the largest entry in A[k+1:,k] and
         # permute it to A[k+1,k]
-        kp = k + 1 + np.abs(A[k + 1:, k]).argmax()
+        kp = k + 1 + np.abs(A[k + 1 :, k]).argmax()
 
         # Check if we need to pivot
         if kp != k + 1:
@@ -183,9 +183,9 @@ def skew_LTL(A, overwrite_a=False, calc_L=True, calc_P=True):
 
             if calc_L:
[…]

### 2019-08-12 distributed_sns.py

@@ -20,9 +20,9 @@ import topology
 from utils import consistent_hash
 
 
-def f_adaptive(xy, keys, params, syst_pars,
-               transverse_soi=True,
-               zeeman_in_superconductor=False):
+def f_adaptive(
+    xy, keys, params, syst_pars, transverse_soi=True, zeeman_in_superconductor=False
+):
     import sns_system
     import topology
 
@@ -32,8 +32,10 @@ def f_adaptive(xy, keys, params, syst_pars,
         params[k] = val
     params[keys[0]], params[keys[1]] = xy
     syst = sns_system.make_sns_system(
-        **syst_pars, transverse_soi=transverse_soi,
-        zeeman_in_superconductor=zeeman_in_superconductor)
+        **syst_pars,
+        transverse_soi=transverse_soi,
+        zeeman_in_superconductor=zeeman_in_superconductor
+    )
     return topology.get_pfaffian(syst, params)
 
 
@@ -79,66 +81,65 @@ def get_list_of_parameter_dictionaries(params_mutable):
     return (iterable_keys, param_list)
 
 
-def pfaffian_function(_, syst_total, syst_wrapped,
-                      syst_junction, syst_pars, params):
+def pfaffian_function(_, syst_total, syst_wrapped, syst_junction, syst_pars, params):
     return topology.get_pfaffian(syst_total, params)
 
 
-def current_function(current_params, syst_total,
-                     syst_wrapped, syst_junction, syst_pars, params):
-    return supercurrent.wrapped_current(syst_pars=syst_pars,
-                                        params=params,
-                                        syst_wrapped=syst_wrapped,
-                                        **current_params)
+def current_function(
+    current_params, syst_total, syst_wrapped, syst_junction, syst_pars, params
+):
+    return supercurrent.wrapped_current(
+        syst_pars=syst_pars, params=params, syst_wrapped=syst_wrapped, **current_params
+    )
 
 
-def energy_gap_function(energy_gap_params, syst_total,
-                        syst_wrapped, syst_junction, syst_pars, params):
+def energy_gap_function(
+    energy_gap_params, syst_total, syst_wrapped, syst_junction, syst_pars, params
+):
     return spectrum.calc_lowest_state((syst_pars, params), syst=syst_total)
 
-def lowest_two_energies(energy_gap_params, syst_total,
-                        syst_wrapped, syst_junction, syst_pars, params):
+
+def lowest_two_energies(
+    energy_gap_params, syst_total, syst_wrapped, syst_junction, syst_pars, params
[…]

### 2019-08-12 formulas.py

@@ -21,4 +21,4 @@ def fermi_velocity(mu, m_eff):
 
 
 def density_to_mu(density, m_eff):
-    return HBAR_MEV**2 * PI * density / (m_eff * M_EV_NM)
+    return HBAR_MEV ** 2 * PI * density / (m_eff * M_EV_NM)

### 2019-08-12 ipynb_filter.py

@@ -14,14 +14,16 @@ from nbconvert.preprocessors import Preprocessor
 
 class RemoveMetadata(Preprocessor):
     def preprocess(self, nb, resources):
-        nb.metadata = {"language_info": {"name": "python",
-                                         "pygments_lexer": "ipython3"}}
+        nb.metadata = {
+            "language_info": {"name": "python", "pygments_lexer": "ipython3"}
+        }
         return nb, resources
 
 
-if __name__ == '__main__':
+if __name__ == "__main__":
     # The filter is getting activated
     import os
+
     git_cmd = 'git config filter.ipynb_filter.clean "jupyter nbconvert --to notebook --config ipynb_filter.py --stdin --stdout"'
     os.system(git_cmd)
 else:
@@ -29,4 +31,8 @@ else:
     c.Exporter.preprocessors = [RemoveMetadata]
     c.ClearOutputPreprocessor.enabled = True
     c.ClearOutputPreprocessor.remove_metadata_fields = [
-        "deletable", "editable", "collapsed", "scrolled"]
+        "deletable",
+        "editable",
+        "collapsed",
+        "scrolled",
+    ]

### 2019-08-12 peierls.py

@@ -2,10 +2,10 @@ import sympy
 import kwant
 
 
-a = sympy.symbols('a')
-phi_0 = sympy.symbols('phi_0')
-ri = sympy.symbols('x_i y_i z_i')
-rj = sympy.symbols('x_j y_j z_j')
+a = sympy.symbols("a")
+phi_0 = sympy.symbols("phi_0")
+ri = sympy.symbols("x_i y_i z_i")
+rj = sympy.symbols("x_j y_j z_j")
 
 
 def get_phase(A, dim):
@@ -27,11 +27,13 @@ def get_phase(A, dim):
     xi, yi, zi = ri
     xj, yj, zj = rj
 
-    t = sympy.symbols('_t_internal_for_integration')
+    t = sympy.symbols("_t_internal_for_integration")
 
-    subs = {x: (1 - t) * xi + t * xj,
-            y: (1 - t) * yi + t * yj,
-            z: (1 - t) * zi + t * zj}
+    subs = {
+        x: (1 - t) * xi + t * xj,
+        y: (1 - t) * yi + t * yj,
+        z: (1 - t) * zi + t * zj,
+    }
 
     output = [xj - xi, yj - yi, zj - zi][:dim]
     for i, Ai in enumerate(A):
@@ -66,7 +68,7 @@ def apply(tb_hamiltonian, coords, *, A, signs=None):
     tb_hamiltonian = tb_hamiltonian.copy()
 
     if not isinstance(A, str):
-        raise ValueError('Vector potential should be a string.')
+        raise ValueError("Vector potential should be a string.")
 
     phase_ij = get_phase(A, dim=len(coords))
     exp = sympy.Symbol("exp")

### 2019-08-12 plotting_results.py

@@ -9,40 +9,60 @@ import numpy as np
 import holoviews as hv
 
 
-def plot_syst(syst_pars=None, params=None, a_new=None,
-              num_lead_cells=4, syst=None, site_colors=None, **args):
+def plot_syst(
+    syst_pars=None,
+    params=None,
+    a_new=None,
+    num_lead_cells=4,
+    syst=None,
+    site_colors=None,
+    **args,
+):
     if syst is None:
-        a = syst_pars['a'] if a_new is None else a_new
-        L_down = syst_pars['L_down']
-        L_m = syst_pars['L_m']
-        L_up = syst_pars['L_up']
-        L_x = syst_pars['L_x']
+        a = syst_pars["a"] if a_new is None else a_new
+        L_down = syst_pars["L_down"]
+        L_m = syst_pars["L_m"]
+        L_up = syst_pars["L_up"]
+        L_x = syst_pars["L_x"]
 
         syst, _ = sns_system.make_sns_system(
-            a=a, L_down=L_down, L_m=L_m, L_up=L_up, L_x=L_x)
-    
+            a=a, L_down=L_down, L_m=L_m, L_up=L_up, L_x=L_x
+        )
+
     if site_colors is None:
         site_colors = {}
-        
+
     def delta(sites):
         colors = []
         for i, site in enumerate(sites):
             site_color = site_colors.get(site)
-            if site_color is None:            
-                site_color = (np.sum(np.abs(syst.hamiltonian(i, i, params=params)) + np.real(syst.hamiltonian(i, i, params=params))
-                       * np.imag(syst.hamiltonian(i, i, params=params))) for i, site in enumerate(sites))
+            if site_color is None:
+                site_color = (
+                    np.sum(
+                        np.abs(syst.hamiltonian(i, i, params=params))
+                        + np.real(syst.hamiltonian(i, i, params=params))
+                        * np.imag(syst.hamiltonian(i, i, params=params))
+                    )
+                    for i, site in enumerate(sites)
+                )
             colors.append(site_color)
         return colors
 
-    return kwant.plot(syst, num_lead_cells=num_lead_cells,
-                      site_color=delta(syst.sites),
-                      fig_size=(5, 5),
-                      show=False, **args)
+    return kwant.plot(
+        syst,
+        num_lead_cells=num_lead_cells,
+        site_color=delta(syst.sites),
[…]

### 2019-08-12 scattering.py

@@ -3,8 +3,8 @@ import sns_system
 
 
 def transparency(syst_junction, params, k_x=0):
-    params['k_x'] = k_x
+    params["k_x"] = k_x
     smatrix = kwant.smatrix(syst_junction, energy=0, params=params)
     # spin accounts for double transmission
     N_prop = smatrix.num_propagating(0)
-    return 1 - 2*smatrix.transmission((0, 0), (0, 0)) / N_prop
+    return 1 - 2 * smatrix.transmission((0, 0), (0, 0)) / N_prop

### 2019-08-12 shape.py

@@ -1,134 +1,173 @@
 import kwant
 
+
 class Shape:
     def __init__(self, shape=None):
         if shape is None:
             self.shape = lambda site: True
         else:
             self.shape = shape
-        
+
     def __call__(self, site):
         return self.shape(site)
-    
+
     def __add__(self, other_shape):
         return Shape(UNION(self.shape, other_shape.shape))
-    
+
     def __sub__(self, other_shape):
         return Shape(DIFFERENCE(self.shape, other_shape.shape))
-    
+
     def __mul__(self, other_shape):
         return Shape(INTERSECTION(self.shape, other_shape.shape))
-    
+
     def inverse(self):
         return Shape(NOT(self.shape))
-        
+
     def edge(self):
         return Shape(EDGE(self.shape))
-    
+
     def outer_edge(self):
         return Shape(OUTER_EDGE(self.shape))
-    
+
     def interior(self):
         return Shape(INTERIOR(self.shape))
-    
+
     def __getitem__(self, i):
         if type(i) is tuple:
             dim = len(i)
-            
+
             if dim == 2:
                 curve_x = slice_func(i[0])
+
                 def _shape_x(site):
                     x, y = site.pos
                     return curve_x(x)
+
                 new_shape = self * Shape(_shape_x)
-                
+
                 curve_y = slice_func(i[1])
+
                 def _shape_y(site):
                     x, y = site.pos
                     return curve_y(y)
+
                 new_shape *= Shape(_shape_y)
-                
+
             elif dim == 3:
                 pass
         else:
             curve = slice_func(i)
+
             def _shape(site):
                 x = site.pos
                 return curve(x)
+
             new_shape = self * Shape(_shape)
-        
+
         return new_shape
-    
+
+
 def NOT(shape):
     """returns not(shape)"""
     return lambda site: not shape(site)
+
 
 def UNION(*shapes):
     """returns shape which is an OR function applied to shapes"""
     return lambda site: any(shape(site) for shape in shapes)
 
+
 def INTERSECTION(*shapes):
     """returns shape which is an AND function applied to shapes"""
     return lambda site: all(shape(site) for shape in shapes)
+
 
 def DIFFERENCE(shape_A, shape_B):
[…]

### 2019-08-12 sns_system.py

@@ -20,38 +20,42 @@ constants = dict(
     # effective mass in kg,
     m_eff=0.023 * scipy.constants.m_e / (scipy.constants.eV * 1e-3) / 1e18,
     hbar=scipy.constants.hbar / (scipy.constants.eV * 1e-3),
-    mu_B=scipy.constants.physical_constants['Bohr magneton'][0] / (
-        scipy.constants.eV * 1e-3),
+    mu_B=scipy.constants.physical_constants["Bohr magneton"][0]
+    / (scipy.constants.eV * 1e-3),
     exp=cmath.exp,
     cos=cmath.cos,
-    sin=cmath.sin)
+    sin=cmath.sin,
+)
 
-dummy_params_raw = dict(g_factor_middle=1,
-                        g_factor_left=2,
-                        g_factor_right=3,
-                        mu=4,
-                        alpha_middle=5,
-                        alpha_left=6,
-                        alpha_right=7,
-                        Delta_left=8,
-                        Delta_right=9,
-                        B=10,
-                        phase=11,
-                        T=12,
-                        V=13)
+dummy_params_raw = dict(
+    g_factor_middle=1,
+    g_factor_left=2,
+    g_factor_right=3,
+    mu=4,
+    alpha_middle=5,
+    alpha_left=6,
+    alpha_right=7,
+    Delta_left=8,
+    Delta_right=9,
+    B=10,
+    phase=11,
+    T=12,
+    V=13,
+)
 
-dummy_params = dict(**constants,
-                    **dummy_params_raw)
+dummy_params = dict(**constants, **dummy_params_raw)
+
 
 def create_parallel_sine(distance, z_x, z_y, rough_edge=None):
     def _parallel_sine(x, distance, z_x, z_y):
-        g       = lambda t: z_y * math.sin(2*np.pi/z_x*t)
-        g_prime = lambda t: z_y * 2*np.pi/z_x*math.cos(2*np.pi/z_x*t)
+        g = lambda t: z_y * math.sin(2 * np.pi / z_x * t)
+        g_prime = lambda t: z_y * 2 * np.pi / z_x * math.cos(2 * np.pi / z_x * t)
+
         def _x(t):
-            return t - distance*g_prime(t)/np.sqrt(1 + g_prime(t)**2) - x
+            return t - distance * g_prime(t) / np.sqrt(1 + g_prime(t) ** 2) - x
 
         def y(t):
[…]

### 2019-08-12 sns_system_no_ph.py

@@ -15,33 +15,39 @@ constants = dict(
     # effective mass in kg,
     m_eff=0.023 * scipy.constants.m_e / (scipy.constants.eV * 1e-3) / 1e18,
     hbar=scipy.constants.hbar / (scipy.constants.eV * 1e-3),
-    mu_B=scipy.constants.physical_constants['Bohr magneton'][0] / (
-        scipy.constants.eV * 1e-3),
+    mu_B=scipy.constants.physical_constants["Bohr magneton"][0]
+    / (scipy.constants.eV * 1e-3),
     exp=cmath.exp,
     cos=cmath.cos,
-    sin=cmath.sin)
+    sin=cmath.sin,
+)
 
-dummy_params_raw = dict(g_factor_middle=1,
-                        g_factor_left=2,
-                        g_factor_right=3,
-                        mu=4,
-                        alpha_middle=5,
-                        alpha_left=6,
-                        alpha_right=7,
-                        Delta_left=8,
-                        Delta_right=9,
-                        B=10,
-                        phase=11,
-                        T=12,
-                        V=13)
+dummy_params_raw = dict(
+    g_factor_middle=1,
+    g_factor_left=2,
+    g_factor_right=3,
+    mu=4,
+    alpha_middle=5,
+    alpha_left=6,
+    alpha_right=7,
+    Delta_left=8,
+    Delta_right=9,
+    B=10,
+    phase=11,
+    T=12,
+    V=13,
+)
 
-dummy_params = dict(**constants,
-                    **dummy_params_raw)
+dummy_params = dict(**constants, **dummy_params_raw)
 
 
 @lru_cache()
 def get_template_strings(
-        transverse_soi, mu_from_bottom_of_spin_orbit_bands=True, k_x_in_sc=False, with_k_z=False):
+    transverse_soi,
+    mu_from_bottom_of_spin_orbit_bands=True,
+    k_x_in_sc=False,
+    with_k_z=False,
+):
     if mu_from_bottom_of_spin_orbit_bands:
         ham_str = "(hbar^2 / (2*m_eff) * (k_y^2 + k_x^2) - mu + m_eff*alpha_middle^2 / (2 * hbar^2)) * sigma_0 "
     else:
@@ -51,19 +57,37 @@ def get_template_strings(
         ham_str += "+ hbar^2 / (2*m_eff) * (k_z^2) * sigma_0"
 
     if transverse_soi:
[…]

### 2019-08-12 spectrum.py

@@ -10,10 +10,15 @@ import sns_system
 
 def dispersion(k_x, k_y, params):
     p = SimpleNamespace(**params)
-    Ekin = (p.hbar**2 / (2 * p.m_eff) * (k_x**2 + k_y**2)
-            - p.mu + p.m_eff * p.alpha_middle**2 / (2 * p.hbar**2))
-    Erest = np.sqrt(p.alpha_middle ** 2 * k_x ** 2 +
-        (p.alpha_middle * k_y - p.g_factor_middle * p.mu_B * p.B) ** 2)
+    Ekin = (
+        p.hbar ** 2 / (2 * p.m_eff) * (k_x ** 2 + k_y ** 2)
+        - p.mu
+        + p.m_eff * p.alpha_middle ** 2 / (2 * p.hbar ** 2)
+    )
+    Erest = np.sqrt(
+        p.alpha_middle ** 2 * k_x ** 2
+        + (p.alpha_middle * k_y - p.g_factor_middle * p.mu_B * p.B) ** 2
+    )
     return Ekin + Erest, Ekin - Erest
 
 
@@ -32,11 +37,11 @@ def mumps_eigsh(matrix, k, sigma, **kwargs):
 
     Please see scipy.sparse.linalg.eigsh for documentation.
     """
-    class LuInv(sla.LinearOperator):
 
+    class LuInv(sla.LinearOperator):
         def __init__(self, matrix):
             instance = kwant.linalg.mumps.MUMPSContext()
-            instance.analyze(matrix, ordering='pord')
+            instance.analyze(matrix, ordering="pord")
             instance.factor(matrix)
             self.solve = instance.solve
             sla.LinearOperator.__init__(self, matrix.dtype, matrix.shape)
@@ -78,7 +83,7 @@ def calc_dos_lowest_state(syst, params, syst_pars):
     energies, wfs = calc_spectrum(syst, params, k=6)
     energy_gap = abs(energies[2]) - abs(energies[0])
     wf = sns_system.to_site_ph_spin(syst_pars, wfs[:, 0])
-    return abs(energies[0]), energy_gap, np.sum(np.abs(wf)**2, axis=2)
+    return abs(energies[0]), energy_gap, np.sum(np.abs(wf) ** 2, axis=2)
 
 
 def translation_ev(h, t, tol=1e6):
@@ -191,8 +196,7 @@ def find_gap_of_lead(lead, params, tol=1e-6):
 
 
 def phase_bounds_operator(lead, params, k_x=0):
[…]

### 2019-08-12 supercurrent.py

@@ -16,8 +16,8 @@ sigz = np.kron(sigma_0, sigma_z)
 
 
 def fermi_dirac(e, params):
-    if params['T'] > 0:
-        beta = 1 / (params['k'] * params['T'])
+    if params["T"] > 0:
+        beta = 1 / (params["k"] * params["T"])
     else:
         return np.double(e <= 0)
     minbetae = np.minimum(100, -beta * e)
@@ -25,21 +25,29 @@ def fermi_dirac(e, params):
 
 
 def wrapped_current(
-        syst_pars, params, tol=0.01, syst_wrapped=None, transverse_soi=True,
-        mu_from_bottom_of_spin_orbit_bands=True, zero_current=1e-15,
-        max_points=1e20):
+    syst_pars,
+    params,
+    tol=0.01,
+    syst_wrapped=None,
+    transverse_soi=True,
+    mu_from_bottom_of_spin_orbit_bands=True,
+    zero_current=1e-15,
+    max_points=1e20,
+):
     if syst_wrapped is None:
         syst_wrapped = sns_system.make_wrapped_system(
-            **syst_pars, transverse_soi=transverse_soi,
-            mu_from_bottom_of_spin_orbit_bands=mu_from_bottom_of_spin_orbit_bands)
+            **syst_pars,
+            transverse_soi=transverse_soi,
+            mu_from_bottom_of_spin_orbit_bands=mu_from_bottom_of_spin_orbit_bands
+        )
 
     cut_tag = 1
-    direction = 'y'
+    direction = "y"
 
     cut_sites = get_cuts(syst_wrapped, cut_tag, direction)
-    current_operator = kwant.operator.Current(syst_wrapped,
-                                              onsite=sigz,
-                                              where=cut_sites)
+    current_operator = kwant.operator.Current(
+        syst_wrapped, onsite=sigz, where=cut_sites
+    )
 
     def f(k):
         p = dict(k_x=k, **params)
@@ -47,40 +55,52 @@ def wrapped_current(
         local_current_operator = current_operator.bind(params=p)
 
         (en, evs) = np.linalg.eigh(ham)
-        I = sum(fermi_dirac(e.real, p) * local_current_operator(ev)
-                for e, ev in zip(en, evs.T))
-        return sum(I) * params['e'] / params['hbar'] / syst_pars['a'] / (2 * np.pi)
+        I = sum(
+            fermi_dirac(e.real, p) * local_current_operator(ev)
+            for e, ev in zip(en, evs.T)
+        )
[…]

### 2019-08-12 supercurrent_matsubara.py

@@ -33,7 +33,7 @@ import numpy as np
 import scipy.optimize
 
 
-def get_cuts(syst, ind=0, direction='x'):
+def get_cuts(syst, ind=0, direction="x"):
     """Get the sites at two postions of the specified cut coordinates.
 
     Parameters
@@ -45,18 +45,18 @@ def get_cuts(syst, ind=0, direction='x'):
     direction : str
         Cut direction, 'x', 'y', or 'z'.
     """
-    direction = 'xyz'.index(direction)
+    direction = "xyz".index(direction)
     l_cut = [site for site in syst.sites() if site.tag[direction] == ind]
     r_cut = [site for site in syst.sites() if site.tag[direction] == ind + 1]
-    assert len(l_cut) == len(
-        r_cut), "x_left and x_right use site.tag not site.pos!"
+    assert len(l_cut) == len(r_cut), "x_left and x_right use site.tag not site.pos!"
     return l_cut, r_cut
 
 
 def add_vlead(syst, norbs, l_cut, r_cut):
     dim = norbs * (len(l_cut) + len(r_cut))
     vlead = kwant.builder.SelfEnergyLead(
-        lambda energy, args: np.zeros((dim, dim)), l_cut + r_cut)
+        lambda energy, args: np.zeros((dim, dim)), l_cut + r_cut
+    )
     syst.leads.append(vlead)
     return syst
 
@@ -66,10 +66,11 @@ def hopping_between_cuts(syst, r_cut, l_cut, electron_blocks):
     l_cut_sites = [syst.sites.index(site) for site in l_cut]
 
     def hopping(syst, params):
-        H = syst.hamiltonian_submatrix(params=params,
-                                       to_sites=l_cut_sites,
-                                       from_sites=r_cut_sites)
+        H = syst.hamiltonian_submatrix(
+            params=params, to_sites=l_cut_sites, from_sites=r_cut_sites
+        )
         return electron_blocks(H)
+
     return hopping
 
 
@@ -86,7 +87,7 @@ def matsubara_frequency(n, params):
     float
         Imaginary energy.
     """
-    return (2 * n + 1) * np.pi * params['k'] * params['T'] * 1j
+    return (2 * n + 1) * np.pi * params["k"] * params["T"] * 1j
 
 
 def null_H(syst, params, n, electron_blocks):
@@ -111,8 +112,9 @@ def null_H(syst, params, n, electron_blocks):
     """
     assert isinstance(syst.leads[0], kwant.builder.SelfEnergyLead)
[…]

### 2019-08-12 utils.py

@@ -45,8 +45,8 @@ def hash_float(obj):
 
 def hash_str(obj):
     m = hashlib.md5()
-    m.update(bytes(obj, 'utf32'))
-    _hash = int.from_bytes(m.digest(), byteorder='little', signed=True)
+    m.update(bytes(obj, "utf32"))
+    _hash = int.from_bytes(m.digest(), byteorder="little", signed=True)
     return _hash
 
 
@@ -73,6 +73,6 @@ def consistent_hash(obj):
         types.FunctionType: hash_function,
         types.BuiltinFunctionType: hash_builtin_function,
         bool: hash_int,
-        functools.partial: hash_partial_function
+        functools.partial: hash_partial_function,
     }
     return hash_funcs[type(obj)](obj)

### 2019-08-12 zigzag.py

@@ -23,22 +23,27 @@ constants = dict(
     # effective mass in kg,
     m_eff=0.023 * scipy.constants.m_e / (scipy.constants.eV * 1e-3) / 1e18,
     hbar=scipy.constants.hbar / (scipy.constants.eV * 1e-3),
-    mu_B=scipy.constants.physical_constants['Bohr magneton'][0] / (
-        scipy.constants.eV * 1e-3),
+    mu_B=scipy.constants.physical_constants["Bohr magneton"][0]
+    / (scipy.constants.eV * 1e-3),
     exp=cmath.exp,
     cos=cmath.cos,
-    sin=cmath.sin)
+    sin=cmath.sin,
+)
 
 
 def remove_phs(H):
-    return re.sub(r'kron\((sigma_[xyz0]), sigma_[xzy0]\)', r'\1', H)
+    return re.sub(r"kron\((sigma_[xyz0]), sigma_[xzy0]\)", r"\1", H)
 
 
 @functools.lru_cache()
 def get_template_strings(
-        transverse_soi, mu_from_bottom_of_spin_orbit_bands=True,
-        k_x_in_sc=False, with_k_z=False, no_phs=False,
-        phs_breaking_potential=False):
+    transverse_soi,
+    mu_from_bottom_of_spin_orbit_bands=True,
+    k_x_in_sc=False,
+    with_k_z=False,
+    no_phs=False,
+    phs_breaking_potential=False,
+):
     kinetic = "(hbar^2 / (2*m_eff) * (k_y^2 + k_x^2 + k_z^2) - mu {}) * kron(sigma_0, sigma_z)"
     if mu_from_bottom_of_spin_orbit_bands:
         ham_str = kinetic.format("+ m_eff*alpha_middle^2 / (2 * hbar^2)")
@@ -46,44 +51,46 @@ def get_template_strings(
         ham_str = kinetic.format("")
 
     if not with_k_z:
-        ham_str = ham_str.replace('k_z', '0')
+        ham_str = ham_str.replace("k_z", "0")
 
     spin_orbit = "- alpha_{} * kron(sigma_y, sigma_z) * k_x"
-    ham_normal = ham_str + spin_orbit.format('middle')
-    ham_sc_top = ham_str + spin_orbit.format('left')
-    ham_sc_bot = ham_str + spin_orbit.format('right')
+    ham_normal = ham_str + spin_orbit.format("middle")
[…]

### 2019-08-13 zigzag.py
commit appendix bandstructure plot before removing it

@@ -431,7 +431,7 @@ def system(
     )
 
     template = {
-        k: discretize(v, coords=("x", "y"), grid_spacing=a)
+        k: discretize(v, coords=("x", "y"), grid=a)
         for k, v in template_strings.items()
     }
 

### 2019-08-13 paper/snakemajoranas.tex
add part with boundary modulation

@@
 
-% \begin{figure}[!htb]
-% \centering
-% \includegraphics[width=0.9\columnwidth]{figures/bandstructure_of_small_period_zigzag.pdf}
-% \caption{The effect of increased transparency.
-% % Like Fig 2. (b) plus horizontal dashed lines indicating the gap of zigzag and straight junctions
-% \label{fig:bandstructure_of_small_period_zigzag}}
-% \end{figure}
+To verify that the change in the interface transparency alone is not sufficient to explain the increase of the topological gap, we have simulated the dispersion of a system with $z_x = z_y = \SI{80}{\nm} \approx v_\textrm{F}$ and $W=\SI{400}{\nm}$, so that the angle of the boundaries is sufficiently large, but the boundary modulation is much smaller than the width.
+We have observed that $E_\textrm{gap}$ became $\SI{6.1}{\mu \eV}$, a 2x increase compared to the straight system.
 

### 2019-08-14 paper/snakemajoranas.tex
finish the appendix part (only Tom's figure is missing

@@
 \comment{Short trajectories are less sensitive to the alignment of magnetic field.}
+Besides short trajectories having a larger $E_\textrm{gap}$, we also find that they are less sensitive to the alignment of the magnetic field.
 
 \comment{Zigzag geometry removes the need for precise field alignment.}
+Because the zigzag geometry cuts off long trajectories---leaving only short trajectories---this device will require a less precise alignment of the magnetic field.
+To show this, we have performed a simulation of a straight and zigzag device where we rotate the field, and the results are in Fig.~\ref{fig:tilted_angle_phase_diagram}.
+We observe that at a $10\circ$ misaligned magnetic field, the zigzag device still has a sizeable gap, wherein the staight device a $1\circ$ misalignment would be detrimental.
 
@@
 \caption{A comparison of a straight device (a) and a zigzag one (b) where the magnetic field is rotated.
-On the x-axis is the the magnetic field $B$ and on the y-axis is the angle $\theta=\arctan{B_y/B_x}$ in degrees.
+On the x-axis is the magnetic field $B$ and on the y-axis is the angle $\theta=\arctan{B_y/B_x}$ in degrees.
 The colormaps and the y-axis have a different scale for both panels.

### 2019-08-14 paper/referee_responses.md
finish draft of the referee response

@@
 
-The flatness of the superconductors may diminish but in order to consider inhomogeneity, we exaggerate the effect by considering a magnetic field which is always perfectly aligned with the nanowire, corresponding to perfect expulsion.
+The flatness of the superconductors may diminish, but in order to consider inhomogeneity, we exaggerate the effect by considering a magnetic field which is always perfectly aligned with the nanowire, corresponding to perfect expulsion.
 We have added a section to the appendix and done several simulations to answer these concerns.
+Specifically, we have done a simulation of a rotating magnetic field and observe that the zigzag device is much more resilient against misaligned magnetic fields than a straight device.
+Additionally, we have done a simulation where the magnetic field follows the curvature of the device as the referee suggested.
+Both these simulations aim to show that the concerns raised by the referee are not a problem.
 
@@
 The separate two phenomena, we have simulated a straight junction where the boundary is also corrugated so that the incident angle of the grazing trajectories is higher.
-In Fig.
-?
-we see that the gap is indeed increased due to that phenomenon.
+In the last paragraph of the appendix we note that the gap is indeed increased (2x) due to that phenomenon, although the order of magnitude change only occurs when the long trajectories are cut of by the geometry.
 

### 2019-09-04 paper/snakemajoranas.tex
add QUANTOX acknowledgment

@@
 We are grateful to  S. Goswami, A. Keselman, P. P. Piskunow, T. Ö. Rosdahl, D. Varjas, F. K. de Vries, Q. Wang, and J. B. Weston for useful discussions.
-This work was supported by the Netherlands Organization for Scientific Research (NWO/OCW), as part of the Frontiers of Nanoscience program, two NWO VIDI grants (016.Vidi.189.180 and 680-47-537), and an ERC Starting Grant STATOPINS 638760.
+This work was supported by the Netherlands Organization for Scientific Research (NWO/OCW), as part of the Frontiers of Nanoscience program, two NWO VIDI grants (016.Vidi.189.180 and 680-47-537), an ERC Starting Grant STATOPINS 638760, and the project Quantox of QuantERA ERA-NET Cofund in Quantum Technologies (Grant Agreement N.
+731473) implemented within the European Union's Horizon 2020 Program.
 

### 2019-09-30 paper/snakemajoranas.tex
update bib keys

@@
 When both NS interfaces are transparent the SNS junction enters the topological phase at $\phi=\pi$ at any finite $B$ field.
-Two groups~\cite{Fornieri2018,Ren2018} have realized this system experimentally, but did not yet observe a hard induced superconducting gap.
+Two groups~\cite{Fornieri2019,Ren2019} have realized this system experimentally, but did not yet observe a hard induced superconducting gap.
 
@@
 Equivalently, the Thouless energy of these trajectories $E_{\textrm{Th}}=\hbar / \tau_\textrm{f}$ is small, resulting in a small gap $E_\textrm{gap} \ll \Delta$.
-This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, making a low filling of the bands a possible workaround\cite{Beenakker2005,Nijholt2015}.
+This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, making a low filling of the bands a possible workaround\cite{Beenakker2005,Nijholt2016}.
 However, tuning the system to a low chemical potential requires a precise knowledge of the band positions and makes the device more sensitive to disorder or microscopic inhomogeneities.
-On the other hand, disorder scatters these long trajectories and introduces a cutoff on the scale of the mean free path~\cite{Golubov1988,Belzig1996,Pilgram2000} which Ref.~\onlinecite{Haim2018} proposes to use to improve Majorana properties; however, disorder is impossible to control to a required precision experimentally.
+On the other hand, disorder scatters these long trajectories and introduces a cutoff on the scale of the mean free path~\cite{Golubov1988,Belzig1996,Pilgram2000} which Ref.~\onlinecite{Haim2019} proposes to use to improve Majorana properties; however, disorder is impossible to control to a required precision experimentally.
 
@@
 We discretize our continuum Hamiltonian [Eq.~\eqref{eq:hamiltonian}] on a square grid and implement a tight-binding model using Kwant~\cite{Groth2014}.
-To preferentially sample important regions of parameter space, we use the Adaptive package~\cite{Nijholt2019a}.
-The entire source code and the resulting raw data are available in Ref.~\onlinecite{Nijholt2019}.
+To preferentially sample important regions of parameter space, we use the Adaptive package~\cite{Nijholt2019}.
+The entire source code and the resulting raw data are available in Ref.~\onlinecite{Laeven2019}.
 
@@
 We then find $\xi_\textrm{M}$ by fitting an exponential to the density of the single Majorana wave function projected on the $x$-axis.
-In the straight system we use the eigenvalue decomposition of the translation operator at zero energy~\cite{Nijholt2015} for performance reasons.
+In the straight system we use the eigenvalue decomposition of the translation operator at zero energy~\cite{Nijholt2016} for performance reasons.
 
@@
 Additionally, we plot the first $\SI{1300}{\nm}$ (one zigzag period) of the wave functions [(a) and (b)] at the optimal point in parameter space for the straight system.
-For the straight system, we calculate $E_\textrm{gap}$ by performing a binary search in $E$ for the energy at which the propagating modes start to appear~\cite{Nijholt2015}.
-Additionally, in Fig.~\ref{fig:phasediagrams}(c) we plot the phase boundaries obtained by solving a generalized eigenvalue problem~\cite{Nijholt2015}.
+For the straight system, we calculate $E_\textrm{gap}$ by performing a binary search in $E$ for the energy at which the propagating modes start to appear~\cite{Nijholt2016}.
+Additionally, in Fig.~\ref{fig:phasediagrams}(c) we plot the phase boundaries obtained by solving a generalized eigenvalue problem~\cite{Nijholt2016}.
 Due to the large size of the zigzag supercell, we are unable to apply these methods to zigzag geometries.
@@
 We expect that the improvement of the device performance will significantly simplify the creation of Majorana devices and the detection of Majorana states.
-The zigzag geometry offers a controllable way to remove long trajectories, making it easier to rely on than disorder~\cite{Haim2018}, that otherwise has a similar effect.
+The zigzag geometry offers a controllable way to remove long trajectories, making it easier to rely on than disorder~\cite{Haim2019}, that otherwise has a similar effect.
 

### 2019-10-02 paper/create_bib_file.py
use create_bib_file.py

@@ -1,0 +1,133 @@
+# Adapted from https://gitlab.kwant-project.org/qt/basnijholt/thesis-bas-nijholt/blob/master/create_bib_file.py
+
+import functools
+import glob
+import os
+from concurrent.futures import ThreadPoolExecutor
+
+import requests
+import yaml
+
+fname_yaml = "zigzag.yaml"
+fname_bib = "zigzag.bib"
+
+
+def edit_raw_bibtex_entry(key, bib_entry):
+    bib_type, *_ = bib_entry.split("{")
+    _, *rest = bib_entry.split(",")
+    rest = ",".join(rest)
+    # Now only modify `rest` because we don't want to touch the key.
+
+    # XXX: I am not sure whether these substitutions are needed.
+    # the problem seemed to be the utf-8 `requests.get` encoding.
+    to_replace = [("ö", r"\"{o}"), ("ü", r"\"{u}"), ("ë", r"\"{e}"), ("ï", r"\"{i}")]
+
+    for old, new in to_replace:
+        rest = rest.replace(old.upper(), new.upper())
+        rest = rest.replace(old.lower(), new.lower())
+
+    to_replace = [
+        (r"a{\r}", r"\r{a}"),  # "Nyga{\r}rd" -> "Nyg\r{a}rd", bug in doi.org
+        ("Josephson", "{J}osephson"),
+        ("Majorana", "{M}ajorana"),
+        ("Andreev", "{A}ndreev"),
+        ("Kramers", "{K}ramers"),
+        ("Kitaev", "{K}itaev"),
+        (
+            r"metastable0and$\uppi$states",
+            r"metastable $0$ and $\pi$ states",
+        ),  # fix for 10.1103/physrevb.63.214512
+        (
+            r"Land{\'{e}}{gFactors}",
+            r"Land{\'{e}} {$g$} Factors",
+        ),  # fix for PhysRevLett.96.026804
+    ]
+
+    journals = [
+        ("Advanced Materials", "Adv. Mater."),
+        ("Annals of Physics", "Ann. Phys."),
+        ("Applied Physics Letters", "Appl. Phys. Lett."),
+        ("JETP Lett", "JETP Lett."),
+        ("Journal de Physique", "J. Phys."),
+        ("Journal of Computational Physics", "J. Comput. Phys."),
+        ("Journal of Experimental and Theoretical Physics", "J. Exp. Theor. Phys."),
+        ("Journal of Low Temperature Physics", "J. Low Temp. Phys."),
+        (
[…]

### 2019-10-04 zigzag.py
add substitutions

@@ -43,6 +43,7 @@ def get_template_strings(
     with_k_z=False,
     no_phs=False,
     phs_breaking_potential=False,
+    substitutions=None,
 ):
     kinetic = "(hbar^2 / (2*m_eff) * (k_y^2 + k_x^2 + k_z^2) - mu {}) * kron(sigma_0, sigma_z)"
     if mu_from_bottom_of_spin_orbit_bands:
@@ -94,6 +95,11 @@ def get_template_strings(
 
     if no_phs:
         template_strings = {k: remove_phs(v) for k, v in template_strings.items()}
+
+    substitutions = substitutions or {}
+    for old, new in substitutions.items():
+        for where in template_strings.key():
+            template_strings[where] = template_strings[where].replace(old, new)
 
     return template_strings
 
@@ -365,6 +371,7 @@ def system(
     no_phs=False,
     rough_edge=None,
     phs_breaking_potential=False,
+    substitutions=None,
 ):
     """Create zigzag system
 
@@ -408,6 +415,8 @@ def system(
     phs_breaking_potential : bool, optional
         Add particle-hole symmetry breaking potential to allow for a
         computationally cheaper way to calculate the Majorana decay length.
+    substitutions : dict, optional
+        Substitutions in the Hamiltonian string.
 
     Returns
     -------
@@ -428,11 +437,11 @@ def system(
         False,
         no_phs,
         phs_breaking_potential,
+        substitutions,
     )
 
     template = {
-        k: discretize(v, coords=("x", "y"), grid=a)
-        for k, v in template_strings.items()
+        k: discretize(v, coords=("x", "y"), grid=a) for k, v in template_strings.items()
     }
 
     shapes = get_shapes(shape, a, z_x, z_y, W, L_x, L_sc_down, L_sc_up, rough_edge)
@@ -732,3 +741,38 @@ def majorana_size_from_fit(syst, params):
     popt, pcov = scipy.optimize.curve_fit(flog, xs_fit, np.log(wf_proj_fit))
 
     return 1 / popt[1]
+
+
+def get_zigzag_direction_vector_function(z_x, z_y, shape, **kwargs):
+    if shape == "parallel_curve":
+
+        def g_prime(t):
[…]

### 2019-10-04 paper/zigzag.tex
fix references
add snaking B field

--- 2019-09-30 paper/snakemajoranas.tex
@@
 \DeclareMathOperator{\re}{Re}
-\newcommand{\kx}{k_x}
-\newcommand{\ky}{k_y}
-\newcommand{\meff}{m_\text{eff}}
 
@@
 \begin{align}
-    H_\textrm{N} = & \left[\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu + \alpha \left( \ky \sigma_x - \kx \sigma_y \right) \right] \tau_z
+    H_\textrm{N} = & \left[\frac{\hbar^2\left(k_x^2 + k_y^2\right)}{2m_\text{eff}} - \mu + \alpha \left( k_y \sigma_x - k_x \sigma_y \right) \right] \tau_z
         + E_\text{Z} \sigma_x, \\
-    H_\textrm{SC} = & \left[\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right] \tau_z
+    H_\textrm{SC} = & \left[\frac{\hbar^2\left(k_x^2 + k_y^2\right)}{2m_\text{eff}} - \mu\right] \tau_z
         + \Delta \cos{\frac{\phi}{2}} \tau_x + \Delta \sin{\frac{\phi}{2}} \tau_y.
@@
 To preferentially sample important regions of parameter space, we use the Adaptive package~\cite{Nijholt2019}.
-The entire source code and the resulting raw data are available in Ref.~\onlinecite{Laeven2019}.
+The entire source code and the resulting raw data are available in Ref.~\onlinecite{Laeven2019b}.
 
 \comment{The default parameters are ...}
-Unless noted differently, the Hamiltonian parameters are $\alpha=\SI{20}{\meV \nm}$, $g=26$, $\meff=\SI{0.02}{\electronmass}$, $\mu=\SI{10}{\meV}$, $B_x=\SI{1}{T}$, $\phi=\pi$, and $\Delta=\SI{1}{\meV}$; and the geometry parameters are $W=\SI{200}{\nm}$, the period of the zigzag $z_x=\SI{1300}{\nm}$, the discretization contant $a=\SI{10}{\nm}$, and the lengths of the superconductors $L_\textrm{SC}=\SI{300}{\nm}$.
+Unless noted differently, the Hamiltonian parameters are $\alpha=\SI{20}{\meV \nm}$, $g=26$, $m_\text{eff}=\SI{0.02}{\electronmass}$, $\mu=\SI{10}{\meV}$, $B_x=\SI{1}{T}$, $\phi=\pi$, and $\Delta=\SI{1}{\meV}$; and the geometry parameters are $W=\SI{200}{\nm}$, the period of the zigzag $z_x=\SI{1300}{\nm}$, the discretization contant $a=\SI{10}{\nm}$, and the lengths of the superconductors $L_\textrm{SC}=\SI{300}{\nm}$.
 
@@
 \bibliographystyle{apsrev4-1}
-\bibliography{snakemajoranas}
+\bibliography{zigzag}
 
@@
 
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=0.9\columnwidth]{figures/snaking_magnetic_field.pdf}
+\caption{
+Band structures where the magnetic field is parallel to the NS interface (orange) and a magnetic field in the $x$-direction (blue) for different values of $z_y$.
+\label{fig:snaking_magnetic_field}}
+\end{figure}
+
 \comment{In a realistic device the magnetic field might not be inhomogeneous, but zigzag doesn't care.}
-
-% \begin{figure}[!htb]
-% \centering
-% \includegraphics[width=0.9\columnwidth]{figures/snaking_magnetic_field.pdf}
-% \caption{
-% % Fig 4. (d) and (f) with snaking B
-% \label{fig:snaking_magnetic_field}}
-% \end{figure}
 

### 2019-10-04 zigzag.py

@@ -96,9 +96,9 @@ def get_template_strings(
     if no_phs:
         template_strings = {k: remove_phs(v) for k, v in template_strings.items()}
 
-    substitutions = substitutions or {}
-    for old, new in substitutions.items():
-        for where in template_strings.key():
+    substitutions = substitutions or ()
+    for old, new in substitutions:
+        for where in template_strings.keys():
             template_strings[where] = template_strings[where].replace(old, new)
 
     return template_strings
@@ -415,7 +415,7 @@ def system(
     phs_breaking_potential : bool, optional
         Add particle-hole symmetry breaking potential to allow for a
         computationally cheaper way to calculate the Majorana decay length.
-    substitutions : dict, optional
+    substitutions : tuple of tuples, optional
         Substitutions in the Hamiltonian string.
 
     Returns

### 2019-10-04 paper/zigzag.tex
add figure to the text
small changes

@@
 To show this, we have performed a simulation of a straight and zigzag device where we rotate the field, and the results are in Fig.~\ref{fig:tilted_angle_phase_diagram}.
-We observe that at a $10\circ$ misaligned magnetic field, the zigzag device still has a sizeable gap, wherein the staight device a $1\circ$ misalignment would be detrimental.
+We observe that at a $10^\circ$ misaligned magnetic field, the zigzag device still has a sizeable gap, wherein the staight device a $1^\circ$ misalignment would be detrimental.
+Additionally, we simulate a device where the magnetic field is parallel to the NS interface and compare it with a field purely in the $x$-direction, the results are in Fig.~\ref{fig:snaking_magnetic_field}.
+From these results we observe that the gap enhancement effect persists.
 
@@
 \caption{A comparison of a straight device (a) and a zigzag one (b) where the magnetic field is rotated.
-On the x-axis is the magnetic field $B$ and on the y-axis is the angle $\theta=\arctan{B_y/B_x}$ in degrees.
-The colormaps and the y-axis have a different scale for both panels.
+On the x-axis is the magnetic field $B$ and on the $y$-axis is the angle $\theta=\arctan{B_y/B_x}$ in degrees.
+The colormaps and the $y$-axis have a different scale for both panels.
 We see that the device with the zigzag geometry is much more resilient against a misaligned magnetic field.

### 2019-10-04 paper/zigzag.tex
reveiw

--- 2019-10-04 paper/zigzag.tex
@@
 The setup consists of a zigzag or snake-like geometry for the semiconductor where long trajectories are not possible due to the geometry.
-In this paper we will focus on two-dimensional (2D) Josephson junctions; however, a zigzag geometry will also work with only one superconductor.\footnote{We confirmed this numerically, although it is not included in this paper.}
 
@@
 \comment{We consider a two-dimensional system with zigzag and BdG Hamiltonian.}
-We consider a Josephson junction (Fig.~\ref{fig:setup}) consisting of a 2D strip of semiconductor, with superconductors on both sides.
+We consider a Josephson junction (Fig.~\ref{fig:setup}) consisting of a 2D strip of semiconductor, with superconductors on both sides~\cite{Pientka2017,Hell2017}.
+(In the App.~\ref{appendix:NS_junction} we demonstrate that similar physics also occurs in devices with a single superconductor.)
 We modulate the shape of the normal region, which can be either zigzag as depicted [Fig.~\ref{fig:setup}(b)], or a more smooth sinusoidal-like shape.
@@
 
-\comment{We calculate the topological phase diagram using the gap size.}
+\comment{We calculate the topological phase diagram.}
 In Fig.~\ref{fig:phasediagrams} we compare the phase diagrams of the straight and the zigzag junction.
@@
 By both observing the gap closings and comparing to the topological phase diagram of the straight system, we then infer the topology of the zigzag system and verify this by calculating the Majorana wave function of a finite length zigzag.
+As a further check, in App.~\ref{appendix:direction_B} we also compute $E_\textrm{gap}$ as function of the angle of magnetic field and observe that the zigzag device protects Majoranas from magnetic field misalignments.
 
@@
 
-\section{Zigzag device with a single superconductor}
+\section{Zigzag device with a single superconductor}\label{appendix:NS_junction}
 
-\comment{The same principle applies to devices with only one superconductor.}
-In this letter we have focused on SNS junctions and showed that $E_\textrm{gap}$ is significantly increased when going from a straight device to a zigzag device, however, with a single superconductor the same principles still apply, although the effect is less significant.
+\comment{We run the simulation and observe that the phase diagrams are the same but the zigzag device is still better.}
+A zigzag-shaped device with a single superconductor shows a similar enhancement of the superconducting gap as the Josephson junction devices.
+We demonstrate this by simulating a straight and a zigzag device and computing $E_\textrm{gap}(B_x, \; \mu)$ in Fig.~\ref{fig:ns_junction}.
+We observe that the order of magnitude increase of $E_\textrm{gap}$ also occurs upon the introduction of a zigzag geometry.
 
@@
 
-\comment{We run the simulation and observe that the phase diagrams are the same but the zigzag device is still better.}
-We show this through a numerical simulation of a straight and a zigzag device where we compute $E_\textrm{gap}(B_x, \; \mu)$ in Fig.~\ref{fig:ns_junction}.
-Here we see that the order of magnitude increase of $E_\textrm{gap}$ also occurs upon the introducation of a zigzag geometry.
-
-\section{Direction of the magnetic field}
-
-\comment{Short trajectories are less sensitive to the alignment of magnetic field.}
-Besides short trajectories having a larger $E_\textrm{gap}$, we also find that they are less sensitive to the alignment of the magnetic field.
+\section{Direction of the magnetic field}\label{appendix:direction_B}
 
 \comment{Zigzag geometry removes the need for precise field alignment.}
-Because the zigzag geometry cuts off long trajectories---leaving only short trajectories---this device will require a less precise alignment of the magnetic field.
-To show this, we have performed a simulation of a straight and zigzag device where we rotate the field, and the results are in Fig.~\ref{fig:tilted_angle_phase_diagram}.
-We observe that at a $10\circ$ misaligned magnetic field, the zigzag device still has a sizeable gap, wherein the staight device a $1\circ$ misalignment would be detrimental.
+Because the zigzag geometry cuts off long trajectories---leaving only short trajectories---this device requires a less precise alignment of the magnetic field.
+To show this, we perform a simulation of a straight and zigzag device with a rotated field (see Fig.~\ref{fig:tilted_angle_phase_diagram}).
+We observe that the zigzag device still has a sizeable gap with a $10^\circ$ misaligned magnetic field, wherea a $1^\circ$ misalignment makes a straight device gapless.
+
+\comment{Likewise a inhomogeneous magnetic field does not matter.}
+Strong screening of the magnetic field by the superconductors may distort the magnetic field pattern.
+To determine whether this effect degrades the device quality, we simulate a device with the magnetic field parallel to the NS interface, shown in Fig.~\ref{fig:syst_snaking_magnetic_field}.
+We find that the resulting gap is comparable to that of a device with the magnetic field purely in the $x$-direction, as shown in Fig.~\ref{fig:snaking_magnetic_field}.
 
@@
 \includegraphics[width=0.9\columnwidth]{figures/tilted_angle_phase_diagram.pdf}
-\caption{A comparison of a straight device (a) and a zigzag one (b) where the magnetic field is rotated.
-On the x-axis is the magnetic field $B$ and on the y-axis is the angle $\theta=\arctan{B_y/B_x}$ in degrees.
-The colormaps and the y-axis have a different scale for both panels.
-We see that the device with the zigzag geometry is much more resilient against a misaligned magnetic field.
+\caption{The topological gap as a function of the magnetic field magnitude $B$ and its angle $\theta=\arctan{B_y/B_x}$ for a straight device (a) and a zigzag device (b).
+Note that the colormaps and the $\theta$-axes differ between panels: the zigzag-shaped device becomes gapless at $\theta$ an order of magnitude larger compared to the straight device.
 \label{fig:tilted_angle_phase_diagram}}
@@
 \centering
-\includegraphics[width=0.9\columnwidth]{figures/snaking_magnetic_field.pdf}
+\includegraphics{figures/syst_snaking_magnetic_field.pdf}
 \caption{
-Band structures where the magnetic field is parallel to the NS interface (orange) and a magnetic field in the $x$-direction (blue) for different values of $z_y$.
+System where the direction of the magnetic field is parallel to the NS interface.
+\label{fig:syst_snaking_magnetic_field}}
+\end{figure}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics{figures/snaking_magnetic_field.pdf}
+\caption{
+Comparison of the zigzag device's band structures with the magnetic field parallel to the NS interface [(a), (orange)] and a magnetic field in the $x$-direction (blue) for different values of $z_y$.
 \label{fig:snaking_magnetic_field}}
@@
 To verify that the change in the interface transparency alone is not sufficient to explain the increase of the topological gap, we have simulated the dispersion of a system with $z_x = z_y = \SI{80}{\nm} \approx v_\textrm{F}$ and $W=\SI{400}{\nm}$, so that the angle of the boundaries is sufficiently large, but the boundary modulation is much smaller than the width.
-We have observed that $E_\textrm{gap}$ became $\SI{6.1}{\mu \eV}$, a 2x increase compared to the straight system.
+We have observed that $E_\textrm{gap}$ becomes $\SI{6.1}{\mu \eV}$, a two-fold increase compared to the straight system.
 

### 2019-10-04 paper/create_bib_file.py
fix refs

@@ -121,10 +121,10 @@ entries = [edit_raw_bibtex_entry(key, bib) for key, bib in zip(dois.keys(), bibs
 with open(fname_bib, "w") as out_file:
     fname = "not_on_crossref.bib"
     out_file.write("@preamble{ {\\providecommand{\\BIBYu}{Yu} } }\n\n")
-    out_file.write(fr"\n% Below is from `{fname}`.\n\n")
+    out_file.write(f"\n% Below is from `{fname}`.\n\n")
     with open(fname) as in_file:
         out_file.write(in_file.read())
-    out_file.write(fr"\n% Below is from `{fname_yaml}`.\n\n")
+    out_file.write(f"\n% Below is from `{fname_yaml}`.\n\n")
     for e in entries:
         for line in e.split("\n"):
             # Remove the url line

### 2019-10-30 paper/zigzag.tex
Minor grammar/interpunctuation fixes

@@
 An important challenge in creating stable Majoranas is the appearance of a soft gap---a power law decay instead of an exponential decay of the density of states near zero energy.
-In clean systems soft gap arises due to the reduction of the induced gap for states with the momentum directed along the junction~\cite{Gennes1963,Beenakker2005}.
+In clean systems a soft gap arises due to the reduction of the induced gap for states with the momentum directed along the junction~\cite{Gennes1963,Beenakker2005}.
 From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor, shown in Fig.~\ref{fig:setup}(a).
-These long trajectories have long flight times $\tau_\textrm{f} \approx L_\textrm{t} / v_F$ (see Fig.~\ref{fig:setup}), where $L_\textrm{t}$ is the trajectory length.
+These long trajectories have long flight times $\tau_\textrm{f} \approx L_\textrm{t} / v_\textrm{F}$ (see Fig.~\ref{fig:setup}), where $L_\textrm{t}$ is the trajectory length and $v_\textrm{F}$ the Fermi velocity.
 Equivalently, the Thouless energy of these trajectories $E_{\textrm{Th}}=\hbar / \tau_\textrm{f}$ is small, resulting in a small gap $E_\textrm{gap} \ll \Delta$.
@@
 The middle area is the semiconductor of width $W$.
-A magnetic field $B$ pointing in the $x$-direction causes a Zeeman splitting in the semiconductor
+A magnetic field $B$ pointing in the $x$-direction causes a Zeeman splitting in the semiconductor.
 A trajectory traveling at a grazing angle (red curve) has a very long flight time $\tau_\textrm{f}$ and a very small induced gap $E_\textrm{gap} \ll \Delta$.
-At the same time, the zigzag geometry limits the length of a trajectory therefore lowering $\tau_\textrm{f}$ and increasing $E_\textrm{gap}$.
+At the same time, the zigzag geometry limits the length of a trajectory, therefore lowering $\tau_\textrm{f}$ and increasing $E_\textrm{gap}$.
 \label{fig:setup}}
@@
 In Fig.~\ref{fig:phasediagrams} we compare the phase diagrams of the straight and the zigzag junction.
-We plot $E_\textrm{gap}$ as a function of magnetic field, chemical potential, $E_\textrm{gap}(B_x, \mu)$; and the superconducting phase difference $E_\textrm{gap}(B_x, \phi)$ for both a straight system [(c) and (e)] and a zigzag system [(d) and (f)].
+We plot $E_\textrm{gap}$ as a function of magnetic field and chemical potential ($E_\textrm{gap}(B_x, \mu)$), and of magnetic field and superconducting phase difference ($E_\textrm{gap}(B_x, \phi)$) for both a straight system [(c) and (e)] and a zigzag system [(d) and (f)].
 Additionally, we plot the first $\SI{1300}{\nm}$ (one zigzag period) of the wave functions [(a) and (b)] at the optimal point in parameter space for the straight system.
@@
 \comment{The zigzag geometry is a controllable tool in hardening the gap and decreasing Majorana size.}
-The zigzag geometry increases the topological gap in the high density regime by more than an order of magnitude, as well as substantially reducing of Majorana size.
+The zigzag geometry increases the topological gap in the high density regime by more than an order of magnitude, as well as substantially reduces Majorana size.
 The improvements occur in a broad range of parameter values, moreover, even using $B_x$ optimal for the straight system in the high density regime (Fig.~\ref{fig:phasediagrams}), the Majorana size $\xi_\textrm{M}$ and $E_\textrm{gap}$ are still more than an order of magnitude better for the zigzag system.
@@
 A promising approach to tackle this question would rely on constructing a quasiclassical model of the zigzag devices.
-Finally, we have excluded several important physical effects, such as: disorder, electrostatics, the orbital effect of magnetic field, and the finite thickness of the sample.
+Finally, we have neglected several important physical effects, such as: disorder, electrostatics, the orbital effect of magnetic field, and the finite thickness of the sample.
 While we expect these phenomena not to influence our qualitative findings, a more detailed simulation should provide better guidance to future experiments.
@@
 \caption{
-System where the direction of the magnetic field is parallel to the NS interface.
+The magnetic field pattern emulating strong screening by the superconductors.
 \label{fig:syst_snaking_magnetic_field}}
@@
 \caption{
-Comparison of the zigzag device's band structures with the magnetic field parallel to the NS interface [(a), (orange)] and a magnetic field in the $x$-direction (blue) for different values of $z_y$.
+Comparison of the zigzag device's band structures with the magnetic field following the shape of the junction (orange) (see Fig.~\ref{fig:syst_snaking_magnetic_field}) and a magnetic field in the $x$-direction (blue) for different values of $z_y$.
 \label{fig:snaking_magnetic_field}}
@@
 \comment{In a realistic device the magnetic field might not be inhomogeneous, but zigzag doesn't care.}
-
-To verify that the change in the interface transparency alone is not sufficient to explain the increase of the topological gap, we have simulated the dispersion of a system with $z_x = z_y = \SI{80}{\nm} \approx v_\textrm{F}$ and $W=\SI{400}{\nm}$, so that the angle of the boundaries is sufficiently large, but the boundary modulation is much smaller than the width.
-We have observed that $E_\textrm{gap}$ becomes $\SI{6.1}{\mu \eV}$, a two-fold increase compared to the straight system.
+The change in the interface transparency alone is not sufficient to explain the increase of the topological gap.
+To verify this, we compute the dispersion of a system with $z_x = z_y = \SI{80}{\nm} \approx v_\textrm{F}$ and $W=\SI{400}{\nm}$, so that the angle of the boundaries is sufficiently large, but the boundary modulation is much smaller than the width.
+We observe that $E_\textrm{gap}$ becomes $\SI{6.1}{\mu \eV}$, a two-fold increase compared to the straight system, not the order of magnitude increase resulting from the cutting off of long trajectories.
 

### 2019-10-30 paper/zigzag.tex
extra appendix section for interface transparency vs path length with a bit more explanation

@@
 
-\comment{In a realistic device the magnetic field might not be inhomogeneous, but zigzag doesn't care.}
-The change in the interface transparency alone is not sufficient to explain the increase of the topological gap.
+\section{Interface transparency vs. path length cut-off}
+
+The zigzag geometry both increases the interface transparency (as particles typically hit the superconductoer
+closer to normal incidence) as well as sets an upper limit to the trajectory length.
+Here we show that the change in the interface transparency alone is not sufficient to explain the increase of the topological gap.
 To verify this, we compute the dispersion of a system with $z_x = z_y = \SI{80}{\nm} \approx v_\textrm{F}$ and $W=\SI{400}{\nm}$, so that the angle of the boundaries is sufficiently large, but the boundary modulation is much smaller than the width.

### 2019-11-29 paper/referee_responses.md
edit referee response with Anton

--- 2019-08-02 paper/referee_responses.md
@@
 The closer study of this is the main new contribution here.
+
+We thank the referee for the positive evaluation, however, we would like to emphasize that geometry optimization was not considered as a method of gap engineering in Josephson junctions in any context, not just in the Majorana devices.
+
 > However, the manuscript appears better suited for publication in PRB.
@@
 
-This is a conceptually new idea, overlooked in a very mature field, which makes it exciting and it seems to resonate with a lot of people.
-Even though the effect of long trajectories was known to DeGennes, the idea of optimizing the geometry to eliminate long trajectories has not previously been considered even outside of the Majorana context.
+Our work reports an idea of adjusting the geometry as a way of influencing a phenomenon that is known for decades.
+That this was overlooked for so long, in a very mature field, is in our opinion what makes it exciting and interesting.
+Further, we predict a change in the device properties by more than an order of magnitude.
+This is a substantial advancement in the field of Majorana devices and therefore, makes our work satisfy the PRL criterion of importance.
 
@@
 Assuming the authors can address the questions and comments listed below, I therefore recommend the publication of the paper in Physical Review Letters.
+
+We thank the referee for the positive assessment of our work.
+
 > My biggest concern has to do with the direction of the magnetic field as it is given in Eq.
@@
 
-The flatness of the superconductors may diminish but in order to consider inhomogeneity, we exaggerate the effect by considering a magnetic field which is always perfectly aligned with the nanowire, corresponding to perfect expulsion.
-We have added a section to the appendix and done several simulations to answer these concerns.
+We have performed a systematic investigation of the influence of the magnetic field direction on the device properties.
+Because all the quasiparticle states are strongly coupled to the superconductor in the zigzag geometry, we observe that the magnetic field does not need to be aligned with the junction direction nearly as precisely as in a straight junction.
+Specifically, we observe that even a 10-degree misalignment yields an induced gap of an order of magnitude larger than the gap in a straight junction with a perfectly aligned field.
+We have also verified that a position-dependent magnetic field does not degrade the device performance.
+We have reported these results these findings in the main text and added the detailed information in the appendix.
+We thank the referee for the suggestion to investigate this phenomenon.
 
@@
 
-After the Eq.
-(2) we have added a remark that this equation follows from an avoided crossing shape of the dispersion relation near the Fermi momentum.
-This relation does not assume anything about the nature of v_F or of E_gap.
+After the Eq. (2), we have added a remark that this equation follows from an avoided crossing shape of the dispersion relation near the Fermi momentum.
+This relation does not assume anything about the nature of v_F or E_gap.
 
-The separate two phenomena, we have simulated a straight junction where the boundary is also corrugated so that the incident angle of the grazing trajectories is higher.
-In Fig.
-?
-we see that the gap is indeed increased due to that phenomenon.
+In order to distinguish the effect of the increased interface transparency from the effect of removing long trajectories, we have performed an additional simulation of a device with the same angle of the zigzag boundaries, but a much smaller amplitude of the modulation.
+While we do observe a gap enhancement in this device, consistent with the mechanism (2) mentioned by the referee, this enhancement is much smaller than in the device with a large modulation.
+Therefore, we conclude that the two mechanisms are independent, however, the removal of the long trajectories is the dominant mechanism for the gap enhancement.
+We have added the details of the additional simulation to the supplementary information.
 
@@
 
-The reference 29 considers a change in the barrier transparency and a longer correlation length and is therefore not the same.
-Reference 31 describes a multimode mechanism and is about how the conductance looks rather than about the actual gap.
+The reference 28 considers a variation in the coupling strength between a semiconductor and a superconductor that has a correlation length longer than the induced coherence length.
+This scenario is therefore, very different from the short length scale roughness that we considered in Fig. 3(d).
+Reference 30 describes a multimode mechanism and is about how the conductance looks rather than about the actual gap.

### 2019-11-29 paper/create_bib_file.py
use yaml2bib 🧠

@@ -1,194 +1,0 @@
-import contextlib
-import functools
-import glob
-import os
-from concurrent.futures import ThreadPoolExecutor
-
-import diskcache
-import requests
-import yaml
-from crossref.restful import Etiquette, Works
-from tqdm import tqdm
-
-bibs = ['zigzag.yaml']
-bib_files = ["not_on_crossref.bib"]
-output = "zigzag.bib"
-
-works = Works(etiquette=Etiquette("publist", contact_email="basnijholt@gmail.com"))
-
-TO_REPLACE = [
-    (r"a{\r}", r"\r{a}"),  # "Nyga{\r}rd" -> "Nyg\r{a}rd", bug in doi.org
-    ("Josephson", "{J}osephson"),
-    ("Majorana", "{M}ajorana"),
-    ("Andreev", "{A}ndreev"),
-    ("Kramers", "{K}ramers"),
-    ("Kitaev", "{K}itaev"),
-    (
-        r"metastable0and$\uppi$states",
-        r"metastable $0$ and $\pi$ states",
-    ),  # fix for 10.1103/physrevb.63.214512
-    (
-        r"Land{\'{e}}{gFactors}",
-        r"Land{\'{e}} {$g$} Factors",
-    ),  # fix for PhysRevLett.96.026804
-    (
-        r"apx$\mathplus$ipysuperconductor",
-        r"a $p_x + i p_y$ superconductor",
-    ),  # fix for 10.1103/physrevb.73.220502
-    (
-        r"apx$\mathplus${ipySuperfluid}",
-        r"$p_x + i p_y$ superfluid",
-    ),  # fix for 10.1103/physrevlett.98.010506
-]
-
-
-JOURNALS = [
-    ("Advanced Materials", "Adv. Mater."),
-    ("Annals of Physics", "Ann. Phys."),
-    ("Applied Physics Letters", "Appl. Phys. Lett."),
-    ("JETP Lett", "JETP Lett."),
-    ("Journal de Physique", "J. Phys."),
-    ("Journal of Computational Physics", "J. Comput. Phys."),
-    ("Journal of Experimental and Theoretical Physics", "J. Exp. Theor. Phys."),
-    ("Journal of Low Temperature Physics", "J. Low Temp. Phys."),
-    ("Journal of Physics A: Mathematical and Theoretical", "J. Phys. A: Math. Theor."),
[…]

### 2020-01-06 paper/zigzag.tex
rewrite the conclusions

--- 2019-10-30 paper/zigzag.tex
@@
 From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor, shown in Fig.~\ref{fig:setup}(a).
-These long trajectories have long flight times $\tau_\textrm{f} \approx L_\textrm{t} / v_\textrm{F}$ (see Fig.~\ref{fig:setup}), where $L_\textrm{t}$ is the trajectory length and $v_\textrm{F}$ the Fermi velocity.
+These long trajectories have long flight times $\tau_\textrm{f} \approx L_\textrm{t} / v_\textrm{F}$ (see Fig.~\ref{fig:setup}), where $L_\textrm{t}$ is the trajectory length and $v_\textrm{F}$ the electron Fermi velocity.
 Equivalently, the Thouless energy of these trajectories $E_{\textrm{Th}}=\hbar / \tau_\textrm{f}$ is small, resulting in a small gap $E_\textrm{gap} \ll \Delta$.
@@
 For the right-hand side of (a) ($k_x > 0$), (b), and (c), the folding is the same, such that the velocity $v=dE/dk$ can be compared visually.
-We observe that once there are no more straight trajectories inside the junction (when $z_y=W$) the spectrum becomes insensitive to the momentum $k_x$ and equivalently, $v_\textrm{F}$ decreases.
-As the zigzag amplitude increases, the band gap $E_\textrm{gap}$ increases by an order of magnitude.
-The combination of these ensures a significant decrease of the Majorana size because $\xi_M \propto v_\textrm{F}/E_\textrm{gap}$
-The parameter values are written at the end of Sec.~\ref{sec:setup}.\label{fig:band_structures}}
+Once there are no more straight trajectories inside the junction (when $z_y=W$) the spectrum becomes insensitive to the momentum $k_x$ and equivalently, the quasiparticle velocity $v$ decreases.
+When the zigzag amplitude increases, the band gap $E_\textrm{gap}$ increases by an order of magnitude.
+The combination of these ensures a significant decrease of the Majorana size $\xi_\textrm{M} \propto v/E_\textrm{gap}$.
+The parameter values are listed at the end of Sec.~\ref{sec:setup}.\label{fig:band_structures}}
 \end{figure}
@@
 We interpret the increase of the gap $E_\textrm{gap}$ shown in Fig.~\ref{fig:band_structures}(b) and (c) as an effect of the zigzag geometry removing these long trajectories traveling at grazing angles.
-Besides the increased $E_\textrm{gap}$, the states from different segments of the zigzag pattern have a negligible overlap and therefore have a vanishing velocity.
+Besides the increased $E_\textrm{gap}$, the states from different segments of the zigzag pattern have a negligible overlap and therefore have a vanishing quasiparticle velocity $v$.
 This reduction in velocity strongly reduces the Majorana size, as we discuss in section \ref{sec:shape_effects}.
@@
 The robustness of $E_\textrm{gap}$ and $\xi_\textrm{M}$ across the zigzag geometries means that the details of the geometry do not matter for the improvements to occur.
-The length of the system is $3.5 z_x=\SI{4550}{\nm}$, the remaining parameter values are written at the end of Sec.~\ref{sec:setup}.\label{fig:wave_functions}}
+The length of the system is $3.5 z_x=\SI{4550}{\nm}$, the remaining parameter values are listed at the end of Sec.~\ref{sec:setup}.\label{fig:wave_functions}}
 \end{figure}
@@
 In the straight system [Fig.~\ref{fig:wave_functions}(a)], we see that the decay of the density is long compared to the system size.
-The small topological gap combined with the high velocity result in a large Majorana size
+This is a result of the small topological gap combined with the quasiparticle velocity $v \approx v_\textrm{F}$ yielding a large Majorana size
 \begin{equation}
 \label{eq:xi_M}
-\xi_\textrm{M}=\hbar \frac{v_\textrm{F}}{E_\textrm{gap}}.
+\xi_\textrm{M}=\hbar \frac{v}{E_\textrm{gap}}.
 \end{equation}
@@
 All of the zigzag-type geometries have $\xi_\textrm{M}$ improved by a factor $\sim 70$ and have the Majorana wave function localized within one segment of the zigzag.
-Further, the topological gap $E_\textrm{gap}$ is an order of magnitude higher than in the straight junction, and as mentioned in section \ref{sec:band_structures}, the velocity $v_\textrm{F}$ is more than an order of magnitude lower.
+Further, the topological gap $E_\textrm{gap}$ is an order of magnitude higher than in the straight junction, and as mentioned in section \ref{sec:band_structures}, the quasiparticle velocity $v$ is more than an order of magnitude lower.
 
@@
 Additionally, in subplot (c) we overlay the phase boundaries.
-The remaining parameter values are written at the end of Sec.~\ref{sec:setup}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
+The remaining parameter values are listed at the end of Sec.~\ref{sec:setup}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
 \label{fig:phasediagrams}}
@@
 \comment{The zigzag geometry is a controllable tool in hardening the gap and decreasing Majorana size.}
-The zigzag geometry increases the topological gap in the high density regime by more than an order of magnitude, as well as substantially reduces Majorana size.
-The improvements occur in a broad range of parameter values, moreover, even using $B_x$ optimal for the straight system in the high density regime (Fig.~\ref{fig:phasediagrams}), the Majorana size $\xi_\textrm{M}$ and $E_\textrm{gap}$ are still more than an order of magnitude better for the zigzag system.
+The zigzag geometry increases the topological gap in the high-density regime by more than an order of magnitude, and substantially reduces Majorana size.
+The improvements occur in a broad range of parameter values, moreover, even using $B_x$ optimal for the straight system in the high-density regime (Fig.~\ref{fig:phasediagrams}), the Majorana size $\xi_\textrm{M}$ and $E_\textrm{gap}$ are still more than an order of magnitude better for the zigzag system.
 We expect that the improvement of the device performance will significantly simplify the creation of Majorana devices and the detection of Majorana states.
-The zigzag geometry offers a controllable way to remove long trajectories, making it easier to rely on than disorder~\cite{Haim2019}, that otherwise has a similar effect.
+Additionally, it offers a controllable way to remove long trajectories, making it easier to rely on than disorder~\cite{Haim2019}, which has a similar effect.
 
 \comment{Zigzag doesn't do anything against other mechanisms, and therefore it doesn't help to use it ignorantly}
-Soft gap may arise due to other mechanisms that do not involve ballistic trajectories: both interface disorder and pair breaking~\cite{Takei2013} or temperature and dissipation~\cite{Liu2017} may create a soft gap.
-Further in a multimode junction the mode dependence of transmission~\cite{Stanescu2014} may produce subgap conductance similar to that in a device with a soft gap.
-The zigzag geometry has no impact on these alternative phenomena, and it may therefore serve as a tool in distinguishing different mechanisms.
+A soft gap may arise due to mechanisms that do not involve ballistic trajectories: both interface disorder and pair-breaking~\cite{Takei2013} or temperature and dissipation~\cite{Liu2017} may create a soft gap.
+Further, in a multimode junction, the dependence of transmission~\cite{Stanescu2014} may produce a subgap conductance similar to that in a device with a soft gap.
+The zigzag geometry has no impact on these alternative phenomena, and it may therefore serve as a tool to distinguish different mechanisms.
+
+\comment{Optimizing the geometry, more detailed modeling, and a simple analytical estimation are open questions for further research}
+Our work is the first demonstration of the impact of the Majorana device geometry on its performance, and it opens a possible research avenue of finding the optimal geometry.
+A promising approach to tackle this question would rely on constructing a quasiclassical model of the zigzag devices.
+Finally, we neglected several important physical effects, such as disorder, electrostatics, the orbital effect of the magnetic field, and the finite thickness of the sample.
+Although we do not expect these phenomena influence our qualitative findings, a more detailed simulation should provide better guidance to future experiments.
 
 \comment{Current fabrication techniques are compatible with the proposed geometry, and experimental verification can be near.}
-Current fabrication techniques are compatible with the proposed geometry; zigzag devices have already been fabricated~\cite{Vries}.
-We have demonstrated that the unavoidable variation in the experimental device geometry should not have a detrimental impact on the zigzag devices.
-
-\comment{Optimizing the geometry, more detailed modeling, and a simple analytical estimation are open questions for further research}
-Our work is the first demonstration of the impact of the Majorana device geometry on its performance, and it opens a much harder question of finding the optimal geometry.
-A promising approach to tackle this question would rely on constructing a quasiclassical model of the zigzag devices.
-Finally, we have neglected several important physical effects, such as: disorder, electrostatics, the orbital effect of magnetic field, and the finite thickness of the sample.
-While we expect these phenomena not to influence our qualitative findings, a more detailed simulation should provide better guidance to future experiments.
+The zigzag geometry is within reach of the standard fabrication techniques as demonstrated by an ongoing experimental project~\cite{Vries}.
+Further, according to our simulations, the zigzag devices should be robust against the unavoidable variation in the experimental device geometry.
+We therefore expect, that the new approach to controlling the proximity superconductivity by means of modifying the geometry will become a commonly used technique.
 
@@
 
-\comment{In a realistic device the magnetic field might not be inhomogeneous, but zigzag doesn't care.}
+\section{Interface transparency vs.~path length cut-off}
+
+The zigzag geometry both increases the interface transparency (because particles typically hit the superconductor
+closer to normal incidence) as well as sets an upper limit to the trajectory length.
 The change in the interface transparency alone is not sufficient to explain the increase of the topological gap.
-To verify this, we compute the dispersion of a system with $z_x = z_y = \SI{80}{\nm} \approx v_\textrm{F}$ and $W=\SI{400}{\nm}$, so that the angle of the boundaries is sufficiently large, but the boundary modulation is much smaller than the width.
+To verify this, we compute the dispersion of a system with $z_x = z_y = \SI{80}{\nm}$ comparable to the Fermi wavelength $\lambda_\textrm{F}$ and $W=\SI{400}{\nm}$, so that the angle of the boundaries is sufficiently large, but the boundary modulation is much smaller than the width.
 We observe that $E_\textrm{gap}$ becomes $\SI{6.1}{\mu \eV}$, a two-fold increase compared to the straight system, not the order of magnitude increase resulting from the cutting off of long trajectories.

### 2020-01-06 paper/zigzag.tex
make the difference between Fermi velocities clear
We both write`t_f = L / v_F` and `E_Th = hbar / t_f`, so `E_Th = hbar v_F / L`.
Also, combining it with `xi_M \propto v_F / E_gap` it seems like the velocity drops out.
However, we are talking about two different Fermi velocities and it is good to clarify this.

@@
 \comment{The zigzag geometry is a controllable tool in hardening the gap and decreasing Majorana size.}
-The zigzag geometry increases the topological gap in the high-density regime by more than an order of magnitude, and substantially reduces Majorana size.
-The improvements occur in a broad range of parameter values, moreover, even using $B_x$ optimal for the straight system in the high-density regime (Fig.~\ref{fig:phasediagrams}), the Majorana size $\xi_\textrm{M}$ and $E_\textrm{gap}$ are still more than an order of magnitude better for the zigzag system.
+The zigzag geometry increases the topological gap in the high density regime by more than an order of magnitude, as well as substantially reduces Majorana size.
+The improvements occur in a broad range of parameter values, moreover, even using $B_x$ optimal for the straight system in the high density regime (Fig.~\ref{fig:phasediagrams}), the Majorana size $\xi_\textrm{M}$ and $E_\textrm{gap}$ are still more than an order of magnitude better for the zigzag system.
 We expect that the improvement of the device performance will significantly simplify the creation of Majorana devices and the detection of Majorana states.
-Additionally, it offers a controllable way to remove long trajectories, making it easier to rely on than disorder~\cite{Haim2019}, which has a similar effect.
+The zigzag geometry offers a controllable way to remove long trajectories, making it easier to rely on than disorder~\cite{Haim2019}, that otherwise has a similar effect.
 
 \comment{Zigzag doesn't do anything against other mechanisms, and therefore it doesn't help to use it ignorantly}
-A soft gap may arise due to mechanisms that do not involve ballistic trajectories: both interface disorder and pair-breaking~\cite{Takei2013} or temperature and dissipation~\cite{Liu2017} may create a soft gap.
-Further, in a multimode junction, the dependence of transmission~\cite{Stanescu2014} may produce a subgap conductance similar to that in a device with a soft gap.
-The zigzag geometry has no impact on these alternative phenomena, and it may therefore serve as a tool to distinguish different mechanisms.
+A soft gap may arise due to other mechanisms that do not involve ballistic trajectories: both interface disorder and pair breaking~\cite{Takei2013} or temperature and dissipation~\cite{Liu2017} may create a soft gap.
+Further in a multimode junction the mode dependence of transmission~\cite{Stanescu2014} may produce subgap conductance similar to that in a device with a soft gap.
+The zigzag geometry has no impact on these alternative phenomena, and it may therefore serve as a tool in distinguishing different mechanisms.
+
+\comment{Current fabrication techniques are compatible with the proposed geometry, and experimental verification can be near.}
+Current fabrication techniques are compatible with the proposed geometry; zigzag devices have already been fabricated~\cite{Vries}.
+We have demonstrated that the unavoidable variation in the experimental device geometry should not have a detrimental impact on the zigzag devices.
 
 \comment{Optimizing the geometry, more detailed modeling, and a simple analytical estimation are open questions for further research}
-Our work is the first demonstration of the impact of the Majorana device geometry on its performance, and it opens a possible research avenue of finding the optimal geometry.
+Our work is the first demonstration of the impact of the Majorana device geometry on its performance, and it opens a much harder question of finding the optimal geometry.
 A promising approach to tackle this question would rely on constructing a quasiclassical model of the zigzag devices.
-Finally, we neglected several important physical effects, such as disorder, electrostatics, the orbital effect of the magnetic field, and the finite thickness of the sample.
-Although we do not expect these phenomena influence our qualitative findings, a more detailed simulation should provide better guidance to future experiments.
-
-\comment{Current fabrication techniques are compatible with the proposed geometry, and experimental verification can be near.}
-The zigzag geometry is within reach of the standard fabrication techniques as demonstrated by an ongoing experimental project~\cite{Vries}.
-Further, according to our simulations, the zigzag devices should be robust against the unavoidable variation in the experimental device geometry.
-We therefore expect, that the new approach to controlling the proximity superconductivity by means of modifying the geometry will become a commonly used technique.
+Finally, we have neglected several important physical effects, such as: disorder, electrostatics, the orbital effect of magnetic field, and the finite thickness of the sample.
+While we expect these phenomena not to influence our qualitative findings, a more detailed simulation should provide better guidance to future experiments.
 

### 2020-01-31 paper/referee_responses.md
dear editor
Comment on first referee response

@@
+Dear Daniel Ucko,
+
+We would like to resubmit the manuscript where we have made revisions to answer both of referee's questions.
+
+We have attached a LaTeX-diff that shows the changes we made to the manuscript.
+Additionally, we have attached a pdf with responses to the referees.
+
+Sincerely,
+
+The authors
+
 > # Report of Referee A -- LD17005/Laeven
@@
 We thank the referee for the positive evaluation, however, we would like to emphasize that geometry optimization was not considered as a method of gap engineering in Josephson junctions in any context, not just in the Majorana devices.
-
+TODO: Can we add that multiple experimental efforts are underway? 
 > However, the manuscript appears better suited for publication in PRB.

### 2020-01-31 paper/referee_responses.md
edit referee_responses.md

--- 2019-11-29 paper/referee_responses.md
@@
-> # Report of Referee A -- LD17005/Laeven
+Dear Daniel Ucko,
+
+We would like to resubmit our revised manuscript where we address the referees' remarks.
+We also address the referees' questions, point by point, below.
+Finally, we also list the changes we have made to the manuscript.
+
+Sincerely,  
+The authors
+
+## Report of Referee A -- LD17005/Laeven
 > The manuscript discusses numerical calculations related to how to improve the energy gap in 2D planar Josephson junctions.
@@
 
-We thank the referee for the positive evaluation, however, we would like to emphasize that geometry optimization was not considered as a method of gap engineering in Josephson junctions in any context, not just in the Majorana devices.
+We thank the referee for the overall positive evaluation.
+However, the referee's description seems to imply that the idea of optimizing the geometry of Josephson junction was known in other contexts.
+To the best of our knowledge this is not the case, and this method was not considered in any context, not just in the Majorana devices.
 
@@
 Further, we predict a change in the device properties by more than an order of magnitude.
-This is a substantial advancement in the field of Majorana devices and therefore, makes our work satisfy the PRL criterion of importance.
+This is a substantial advance in the field of Majorana devices and therefore, makes our work satisfy the PRL criterion of importance.
+The high degree of interest within the community is indicated by the ongoing experimental efforts of four independent experimental research groups, for example see [this March Meeting abstract](http://meetings.aps.org/Meeting/MAR20/Session/L60.6).
 
-> # Report of Referee B -- LD17005/Laeven
+## Report of Referee B -- LD17005/Laeven
 > The authors consider a planar Josephson junction in a zigzag geometry and propose it as an improved realization of a one-dimensional topological superconductor.
@@
 Reference 30 describes a multimode mechanism and is about how the conductance looks rather than about the actual gap.
+
+## List of changes
+*

### 2020-02-08 paper/referee_responses.md
Add changelog

@@
 ## List of changes
-*
+Apart from some minor grammatical and spelling errors, the amendments we made are:
+* Rephrased section II.
+* In section IV, we reformulated the following sentences:
+  * >~~To reduce the finite size effects in determining the Majorana size $\xi_\textrm{M}$ in a zigzag system, we introduce a particle-hole symmetry breaking potential $V \sigma_0 \tau_0$ on one edge, such that one of the Majorana states is pushed away from zero energy.~~ When determining the Majorana size $\xi_\textrm{M}$ in a zigzag system, we reduce the finite size effects by introducing a particle-hole symmetry breaking potential $V \sigma_0 \tau_0$ on one edge, such that one of the Majorana states is pushed away from zero energy.
+  * >~~The small topological gap combined with the high velocity result in a large Majorana size~~ This is a result of the small topological gap combined with the quasiparticle velocity $v \approx v_\textrm{F}$ yielding a large Majorana size
+  * >~~The wave function extends to the center of the system, resulting in highly overlapping Majoranas and a Majorana coupling $E_\textrm{M}$ comparable to $E_\textrm{gap}$.~~ This result follows from an avoided crossing shape of the dispersion relation near the Fermi momentum.
+Therefore, in straight junctions the wave function extends to the center of the system, resulting in highly overlapping Majoranas and a Majorana coupling $E_\textrm{M}$ comparable to $E_\textrm{gap}$.
+* In section V we refer to Appendix B where we compare the effects of magnetic field misalignment between a zigzag and a straight geometry.
+* In section V we removed the sentence "We also observe additional gap closings due to the BDI symmetry."
+* In section VI we moved the paragraph regarding experimental verification to the end.
+* We added the following Appendices:
+  * Appendix A, which details the implementation of a zigzag geometry in a device with a single superconductor.
+  * Appendix B, which outlines the robustness of the topological gap in a zigzag device under misaligned magnetic field.
+  * Appendix C, which demonstrates that the increased transparency of the NS interface alone does not explain the order of magnitude increase in topological gap.

### 2020-02-08 paper/referee_responses.md
Minor tweaks

@@
 ## List of changes
-Apart from some minor grammatical and spelling errors, the amendments we made are:
-* Rephrased section II.
+Apart from some minor changes regarding grammar and spelling, the following changes were made:
+* We rephrased section II.
 * In section IV, we reformulated the following sentences:
@@
 Therefore, in straight junctions the wave function extends to the center of the system, resulting in highly overlapping Majoranas and a Majorana coupling $E_\textrm{M}$ comparable to $E_\textrm{gap}$.
-* In section V we refer to Appendix B where we compare the effects of magnetic field misalignment between a zigzag and a straight geometry.
-* In section V we removed the sentence "We also observe additional gap closings due to the BDI symmetry."
-* In section VI we moved the paragraph regarding experimental verification to the end.
+* In section V we added a sentence referring to Appendix B where we compare the effects of magnetic field misalignment between a zigzag and a straight geometry.
+* In section V we removed the sentence "We also observe additional gap closings due to the BDI symmetry.".
+* In section VI we moved the paragraph regarding experimental verification to the end of the section.
 * We added the following Appendices:
-  * Appendix A, which details the implementation of a zigzag geometry in a device with a single superconductor.
-  * Appendix B, which outlines the robustness of the topological gap in a zigzag device under misaligned magnetic field.
-  * Appendix C, which demonstrates that the increased transparency of the NS interface alone does not explain the order of magnitude increase in topological gap.
+  * Appendix A, detailing the implementation of a zigzag geometry in a device with a single superconductor.
+  * Appendix B, outlining the robustness of the topological gap in a zigzag device under misaligned magnetic field.
+  * Appendix C, deminstrating that the increased transparency of the NS interface alone does not explain the order of magnitude increase in topological gap.

### 2020-02-10 paper/referee_responses.md
fix typos in "List of changes"

@@
   * Appendix A, detailing the implementation of a zigzag geometry in a device with a single superconductor.
-  * Appendix B, outlining the robustness of the topological gap in a zigzag device under misaligned magnetic field.
-  * Appendix C, deminstrating that the increased transparency of the NS interface alone does not explain the order of magnitude increase in topological gap.
+  * Appendix B, outlining the robustness of the topological gap in a zigzag device under a misaligned magnetic field.
+  * Appendix C, demonstrating that the increased transparency of the NS interface alone does not explain the order of magnitude increase in the topological gap.

### 2020-02-10 paper/referee_responses.md

@@
 (1) does not penetrate the superconductor which is certainly reasonable.
-I think, however, that this is not consistent with the uniformly-directed magnetic field in the normal region (see B\sigma_x in Eq.
+I think, however, that this is not consistent with the uniformly-directed magnetic field in the normal region (see $B\sigma_x$ in Eq.
 (1a)).
@@
 > At the end of section III, the authors explain that besides the effect of increasing the gap through eliminating modes traveling at grazing angles, the zigzag geometry has two more effects that causes the Majorana size to decrease: (1) reducing the Fermi velocity, and (2) increasing transmission to the SC.
-With regards to (1), I would comment that the Fermi velocity that enters the formula \xi=v_F/E_gap is the electron velocity before introducing superconductivity.
+With regards to (1), I would comment that the Fermi velocity that enters the formula $\xi=v_F/E_{gap}$ is the electron velocity before introducing superconductivity.
 The fact that the bandstructure becomes flatter is not a testament to the Fermi velocity becoming smaller since superconductivity is already present.
@@
 After the Eq. (2), we have added a remark that this equation follows from an avoided crossing shape of the dispersion relation near the Fermi momentum.
-This relation does not assume anything about the nature of v_F or E_gap.
+This relation does not assume anything about the nature of $v_F$ or $E_{gap}$.
 

### 2020-02-10 paper/referee_responses.md
fix markdown

@@
 Apart from some minor changes regarding grammar and spelling, the following changes were made:
+
 * We rephrased section II.
 * In section IV, we reformulated the following sentences:
+
   * >~~To reduce the finite size effects in determining the Majorana size $\xi_\textrm{M}$ in a zigzag system, we introduce a particle-hole symmetry breaking potential $V \sigma_0 \tau_0$ on one edge, such that one of the Majorana states is pushed away from zero energy.~~ When determining the Majorana size $\xi_\textrm{M}$ in a zigzag system, we reduce the finite size effects by introducing a particle-hole symmetry breaking potential $V \sigma_0 \tau_0$ on one edge, such that one of the Majorana states is pushed away from zero energy.
@@
 Therefore, in straight junctions the wave function extends to the center of the system, resulting in highly overlapping Majoranas and a Majorana coupling $E_\textrm{M}$ comparable to $E_\textrm{gap}$.
+
 * In section V we added a sentence referring to Appendix B where we compare the effects of magnetic field misalignment between a zigzag and a straight geometry.
@@
 * We added the following Appendices:
+
   * Appendix A, detailing the implementation of a zigzag geometry in a device with a single superconductor.

### 2020-02-12 paper/referee_responses.md
Change Daniel to Doctor
add footnote and hyperlink coloring for referee response

@@
+---
+urlcolor: blue
+geometry:
+  margin=1in
+---
 Dear Daniel Ucko,
@@
 This is a substantial advance in the field of Majorana devices and therefore, makes our work satisfy the PRL criterion of importance.
-The high degree of interest within the community is indicated by the ongoing experimental efforts of four independent experimental research groups, for example see [this March Meeting abstract](http://meetings.aps.org/Meeting/MAR20/Session/L60.6).
+The high degree of interest within the community is indicated by the ongoing experimental efforts of four independent experimental research groups, for example see [this March Meeting abstract](http://meetings.aps.org/Meeting/MAR20/Session/L60.6)[^1].
+
+[^1]: http://meetings.aps.org/Meeting/MAR20/Session/L60.6
 

### 2020-03-10 paper/appendix.tex
Move appendix to separate file

--- 2020-01-06 paper/zigzag.tex
@@
 \pdfoutput=1
+\usepackage{xr}
+\externaldocument{zigzag}
 \usepackage[utf8]{inputenc}
@@
 \begin{document}
-
-\title{Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.}
-
-\author{Tom Laeven}
-\email[Electronic address: ]{tlaeven@hotmail.com}
-\affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
-\author{Bas Nijholt}
-\email[Electronic address: ]{bas@nijho.lt}
-\affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
-\author{Michael Wimmer}
-\email[Electronic address: ]{m.t.wimmer@tudelft.nl}
-\affiliation{Kavli Institute of Nanoscience, Delft University of Technology,
- P.O. Box 4056, 2600 GA Delft, The Netherlands}
-\affiliation{QuTech, Delft University of Technology,
- P.O. Box 4056, 2600 GA Delft, The Netherlands}
-\author{Anton R. Akhmerov}
-\email[Electronic address: ]{zigzag@antonakhmerov.org}
-\affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
-
-\date{\today}
-\begin{abstract}
-High density superconductor-semiconductor-superconductor junctions have a small induced superconducting gap due to the quasiparticle trajectories with a large momentum parallel to the junction having a very long flight time.
-Because a large induced gap protects Majorana modes, these long trajectories constrain Majorana devices to a low electron density.
-We show that a zigzag-shaped geometry eliminates these trajectories, allowing the robust creation of Majorana states with both the induced gap $E_\textrm{gap}$ and the Majorana size $\xi_\textrm{M}$ improved by more than an order of magnitude for realistic parameters.
-In addition to the improved robustness of Majoranas, this new zigzag geometry is insensitive to the geometric details and the device tuning.
-\end{abstract}
-
-\maketitle
-
-%%██████████████████████████████████████████████████████████████████████████
-%%██ Introduction
-%%██████████████████████████████████████████████████████████████████████████
-\section{Introduction}
-\comment{Hybrid NS structures become topological and are useful for TQC.}
-A hybrid structure containing a semiconductor with strong spin-orbit coupling coupled to a superconductor can become topological upon application of a magnetic field stronger than a critical field $B_\textrm{crit}$, with Majorana bound states appearing on its edges~\cite{Lutchyn2010,Oreg2010}.
-Majorana bound states are a promising candidate to form the basis of a stable platform for topological quantum computing~\cite{Alicea2012,Beenakker2013,Beenakker2016,Leijnse2012}.
-Much of the experimental effort~\cite{Mourik2012,Das2012,Deng2012,Churchill2013,Zhang2018} currently focuses on creating pairs of Majorana bound states in hybrid normal-superconductor (NS) nanowire structures.
-
-\comment{SNS junctions also work and require smaller field.}
-Recently, a modified setup has been proposed\cite{Pientka2017,Hell2017} relying on a superconductor-normal-superconductor (SNS) junction to lower the critical magnetic field $B_\textrm{c}$ by introducing a superconducting phase difference $\phi$.
-When both NS interfaces are transparent the SNS junction enters the topological phase at $\phi=\pi$ at any finite $B$ field.
-Two groups~\cite{Fornieri2019,Ren2019} have realized this system experimentally, but did not yet observe a hard induced superconducting gap.
-
-\comment{The gap is small because of long trajectories.}
-An important challenge in creating stable Majoranas is the appearance of a soft gap---a power law decay instead of an exponential decay of the density of states near zero energy.
-In clean systems a soft gap arises due to the reduction of the induced gap for states with the momentum directed along the junction~\cite{Gennes1963,Beenakker2005}.
-From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor, shown in Fig.~\ref{fig:setup}(a).
-These long trajectories have long flight times $\tau_\textrm{f} \approx L_\textrm{t} / v_\textrm{F}$ (see Fig.~\ref{fig:setup}), where $L_\textrm{t}$ is the trajectory length and $v_\textrm{F}$ the electron Fermi velocity.
-Equivalently, the Thouless energy of these trajectories $E_{\textrm{Th}}=\hbar / \tau_\textrm{f}$ is small, resulting in a small gap $E_\textrm{gap} \ll \Delta$.
-This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, making a low filling of the bands a possible workaround\cite{Beenakker2005,Nijholt2016}.
-However, tuning the system to a low chemical potential requires a precise knowledge of the band positions and makes the device more sensitive to disorder or microscopic inhomogeneities.
-On the other hand, disorder scatters these long trajectories and introduces a cutoff on the scale of the mean free path~\cite{Golubov1988,Belzig1996,Pilgram2000} which Ref.~\onlinecite{Haim2019} proposes to use to improve Majorana properties; however, disorder is impossible to control to a required precision experimentally.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[width=0.9\columnwidth]{figures/zigzag.pdf}
-\caption{The straight (top) and the zigzag (bottom) SNS junction.
-The zigzag pattern has a peak-to-peak amplitude $z_y$ and a period $z_x$.
-The yellow areas are superconductors with a phase difference of $\phi$ between the top and the bottom.
-The middle area is the semiconductor of width $W$.
-A magnetic field $B$ pointing in the $x$-direction causes a Zeeman splitting in the semiconductor.
-A trajectory traveling at a grazing angle (red curve) has a very long flight time $\tau_\textrm{f}$ and a very small induced gap $E_\textrm{gap} \ll \Delta$.
-At the same time, the zigzag geometry limits the length of a trajectory, therefore lowering $\tau_\textrm{f}$ and increasing $E_\textrm{gap}$.
-\label{fig:setup}}
-\end{figure}
-
-\comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
-We propose a new experimental setup (see Fig.~\ref{fig:setup}(b)) for the creation of Majoranas that eliminates long trajectories and therefore prevents the appearance of a soft gap, while also increasing the topological gap (the smallest gap in the dispersion relation) by more than an order of magnitude, depending on the parameters.
-The setup consists of a zigzag or snake-like geometry for the semiconductor where long trajectories are not possible due to the geometry.
-
-%%██████████████████████████████████████████████████████████████████████████
-%%██ Setup
-%%██████████████████████████████████████████████████████████████████████████
-\section{Setup}\label{sec:setup}
-
-\comment{We consider a two-dimensional system with zigzag and BdG Hamiltonian.}
-We consider a Josephson junction (Fig.~\ref{fig:setup}) consisting of a 2D strip of semiconductor, with superconductors on both sides~\cite{Pientka2017,Hell2017}.
-(In the App.~\ref{appendix:NS_junction} we demonstrate that similar physics also occurs in devices with a single superconductor.)
-We modulate the shape of the normal region, which can be either zigzag as depicted [Fig.~\ref{fig:setup}(b)], or a more smooth sinusoidal-like shape.
-Similar to the conventional straight system \cite{Pientka2017}, a magnetic field $B_x$ perpendicular to the junction is applied.
-We model the system with a Bogoliubov-de Gennes Hamiltonian (BdG):
-\begin{subequations}
-\begin{align}
-    H_\textrm{N} = & \left[\frac{\hbar^2\left(k_x^2 + k_y^2\right)}{2m_\text{eff}} - \mu + \alpha \left( k_y \sigma_x - k_x \sigma_y \right) \right] \tau_z
-        + E_\text{Z} \sigma_x, \\
-    H_\textrm{SC} = & \left[\frac{\hbar^2\left(k_x^2 + k_y^2\right)}{2m_\text{eff}} - \mu\right] \tau_z
-        + \Delta \cos{\frac{\phi}{2}} \tau_x + \Delta \sin{\frac{\phi}{2}} \tau_y.
-\end{align}
-\label{eq:hamiltonian}
-\end{subequations}
-Here $H_\textrm{N}$ and $H_\textrm{SC}$ are the Hamiltonians of the semiconductor and superconductors, respectively.
-The normal part has a linear Rashba spin-orbit coupling term with strength $\alpha$ and a Zeeman field with $E_\text{Z}=\frac{1}{2} \mu_B g B_x$.
-The superconductor has a coupling term $\Delta$, and the phases of the superconductors equal to $\pm\phi/2$.
-Both the normal part and the superconductors have a kinetic term and chemical potential $\mu$.
-The BdG Hamiltonian acts on the spinor wave function $\Psi={\left(\psi_{e\uparrow},\psi_{e\downarrow},\psi_{\textrm{h}\downarrow},-\psi_{\textrm{h}\uparrow}\right)}^{T}$, where $\psi_e$, $\psi_\textrm{h}$ are its electron and hole components, and $\psi_\uparrow$, $\psi_\downarrow$ are the spin-up and spin-down components.
-The Pauli matrices $\sigma_{i}$ act on the spin degree of freedom and $\tau_{i}$ act on the electron-hole degree of freedom.
-We consider a zigzag pattern with a period $z_x$, a peak-to-peak amplitude $z_y$, and $W$ the width of the junction [see Fig.~\ref{fig:setup}(b)].
-Later we relax this assumption and show that the exact shape is unimportant.
-
-\comment{We discretize the Hamiltonian and simulate it with Kwant.}
-We discretize our continuum Hamiltonian [Eq.~\eqref{eq:hamiltonian}] on a square grid and implement a tight-binding model using Kwant~\cite{Groth2014}.
-To preferentially sample important regions of parameter space, we use the Adaptive package~\cite{Nijholt2019}.
-The entire source code and the resulting raw data are available in Ref.~\onlinecite{Laeven2019b}.
-
-\comment{The default parameters are ...}
-Unless noted differently, the Hamiltonian parameters are $\alpha=\SI{20}{\meV \nm}$, $g=26$, $m_\text{eff}=\SI{0.02}{\electronmass}$, $\mu=\SI{10}{\meV}$, $B_x=\SI{1}{T}$, $\phi=\pi$, and $\Delta=\SI{1}{\meV}$; and the geometry parameters are $W=\SI{200}{\nm}$, the period of the zigzag $z_x=\SI{1300}{\nm}$, the discretization contant $a=\SI{10}{\nm}$, and the lengths of the superconductors $L_\textrm{SC}=\SI{300}{\nm}$.
-
-%%██████████████████████████████████████████████████████████████████████████
-%%██ Band structures
-%%██████████████████████████████████████████████████████████████████████████
-\section{Band structures}\label{sec:band_structures}
-
-\begin{figure}[!htb]
-\includegraphics[width=\columnwidth]{figures/bandstructures}
-\caption{Band structures of the system in Fig.~\ref{fig:setup}(b) with different zigzag amplitudes.
-The blue lines correspond to a trivial phase ($\phi=0$, $B_x = 0$) and the orange lines to a topological phase ($\phi=\pi$, $B_x = \SI{1}{T}$).
-The three subplots are for different amplitudes of the zigzag, with (a) a straight system $z_y=0$, (b) $z_y=W/2$, and (c) $z_y=W$, where $W=\SI{200}{\nm}$ is the junction width.
-Subplot (a) has a different $x$-scale for $k_x < 0$ from the other subplots and displays the unfolded band structure.
-For the right-hand side of (a) ($k_x > 0$), (b), and (c), the folding is the same, such that the velocity $v=dE/dk$ can be compared visually.
-Once there are no more straight trajectories inside the junction (when $z_y=W$) the spectrum becomes insensitive to the momentum $k_x$ and equivalently, the quasiparticle velocity $v$ decreases.
-When the zigzag amplitude increases, the band gap $E_\textrm{gap}$ increases by an order of magnitude.
-The combination of these ensures a significant decrease of the Majorana size $\xi_\textrm{M} \propto v/E_\textrm{gap}$.
-The parameter values are listed at the end of Sec.~\ref{sec:setup}.\label{fig:band_structures}}
-\end{figure}
-
-\comment{We calculate the band structure for varying amount of zigzag.}
-We apply sparse diagonalization to the supercell Hamiltonian at different momenta $k_x$ to compute the band structure.
-Because of the large periodicity of the zigzag and the resulting large supercell, the band structure is heavily folded.
-In Fig.~\ref{fig:band_structures} we show the resulting band structures of zigzag systems with varying $z_y$.
-The introduction of the zigzag has a striking effect: the bands flatten out and the topological gap increases by more than an order of magnitude.
-
-\comment{Zigzag improves the gap and size because of cutting of trajectories and increasing transparency.}
-In the unfolded band structure of a straight system, shown in Fig.~\ref{fig:band_structures}(a), the lowest energy states occur at $k \approx k_F$.
-We interpret the increase of the gap $E_\textrm{gap}$ shown in Fig.~\ref{fig:band_structures}(b) and (c) as an effect of the zigzag geometry removing these long trajectories traveling at grazing angles.
-Besides the increased $E_\textrm{gap}$, the states from different segments of the zigzag pattern have a negligible overlap and therefore have a vanishing quasiparticle velocity $v$.
-This reduction in velocity strongly reduces the Majorana size, as we discuss in section \ref{sec:shape_effects}.
-Finally, in a zigzag geometry, every trajectory encounters a superconductor close to normal incidence.
-Normal incidence has a higher transmission probability for entering the superconductor and therefore a higher Andreev reflection amplitude.
-This provides another mechanism of the gap enhancement.
-
-%%██████████████████████████████████████████████████████████████████████████
-%%██ Localization lengths and shape effect
-%%██████████████████████████████████████████████████████████████████████████
-\section{Localization lengths and shape effects}\label{sec:shape_effects}
-
-\begin{figure}[!htb]
-\includegraphics[width=\columnwidth]{figures/wavefunctions}
-\caption{Density of Majorana wave functions $\left| \psi_\textrm{M} \right|^2$ for different geometries.
-With (a) a straight system, (b) a zigzag system, (c) a system where lines parallel to a sinusoid defines the normal region, and (d) similar to (c) but with disordered edges.
-Inside the figure, we indicate the Majorana length (or coherence length) $\xi_\textrm{M}$, the Majorana energy $E_\textrm{M}$ (the energy of the first excited state), and the topological energy gap $E_\textrm{gap}$.
-We observe that $\xi_\textrm{M}$ for the straight system is almost two orders of magnitude longer and $E_\textrm{gap}$ more than an order of magnitude smaller than for the zigzag systems.
-The robustness of $E_\textrm{gap}$ and $\xi_\textrm{M}$ across the zigzag geometries means that the details of the geometry do not matter for the improvements to occur.
-The length of the system is $3.5 z_x=\SI{4550}{\nm}$, the remaining parameter values are listed at the end of Sec.~\ref{sec:setup}.\label{fig:wave_functions}}
-\end{figure}
-
-\comment{We calculate the wave functions and find the Majorana lengths by fitting an exponential.}
-We model a finite system and compute the Majorana wave function in different geometries: ribbon, zigzag, sine-like parallel curves, and a variant of the latter with disordered edges.
-By diagonalizing the Hamiltonian, we find the Majorana energy $E_\textrm{M}$, and by using the corresponding eigenstate of that lowest energy, we get the wave function.
-To reduce the finite size effects in determining the Majorana size $\xi_\textrm{M}$ in a zigzag system, we introduce a particle-hole symmetry breaking potential $V \sigma_0 \tau_0$ on one edge, such that one of the Majorana states is pushed away from zero energy.
-We then find $\xi_\textrm{M}$ by fitting an exponential to the density of the single Majorana wave function projected on the $x$-axis.
-In the straight system we use the eigenvalue decomposition of the translation operator at zero energy~\cite{Nijholt2016} for performance reasons.
-
-\comment{In a straight system, the Majoranas are very poorly localized because of small gap and high velocity}
-We show the resulting Majorana wave function densities $\left| \psi_\textrm{M} \right|^2$ in different geometries in Fig.~\ref{fig:wave_functions} using the same Hamiltonian parameter values.
-In the straight system [Fig.~\ref{fig:wave_functions}(a)], we see that the decay of the density is long compared to the system size.
-This is a result of the small topological gap combined with the quasiparticle velocity $v \approx v_\textrm{F}$ yielding a large Majorana size
-\begin{equation}
-\label{eq:xi_M}
-\xi_\textrm{M}=\hbar \frac{v}{E_\textrm{gap}}.
-\end{equation}
-This result follows from an avoided crossing shape of the dispersion relation near the Fermi momentum.
-Therefore, in straight junctions the wave function extends to the center of the system, resulting in highly overlapping Majoranas and a Majorana coupling $E_\textrm{M}$ comparable to $E_\textrm{gap}$.
-
-\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag independent of details}
-We observe that in zigzag systems the Majorana properties improve independent of specific geometric details.
-All of the zigzag-type geometries have $\xi_\textrm{M}$ improved by a factor $\sim 70$ and have the Majorana wave function localized within one segment of the zigzag.
-Further, the topological gap $E_\textrm{gap}$ is an order of magnitude higher than in the straight junction, and as mentioned in section \ref{sec:band_structures}, the quasiparticle velocity $v$ is more than an order of magnitude lower.
-
-%%██████████████████████████████████████████████████████████████████████████
-%%██ Topological phase diagram
-%%██████████████████████████████████████████████████████████████████████████
-\section{Topological phase diagram}
-
-\begin{figure}[!htb]
-\includegraphics[width=\columnwidth]{figures/phasediagrams}
-\caption{A comparison of a straight device (left panels) and a zigzag one (right panels).
-The top panels show the Majorana wave functions, near the left edge of the system, at the value of $B_x$ for which $E_\textrm{gap}$ is maximized in a straight geometry for $\mu=\SI{10}{\meV}$ and $\phi=\pi$ as well as the values of the gap and the Majorana size.
-The other panels show gap as a function of $\mu$ and $B_x$ at $\phi=\pi$ (middle panels) and as a function of $\phi$ and $B_x$ at $\mu=\SI{10}{\meV}$ (bottom panels).
-The dashed lines and the dot indicate the parameters used in the other panels.
-Additionally, in subplot (c) we overlay the phase boundaries.
-The remaining parameter values are listed at the end of Sec.~\ref{sec:setup}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
-\label{fig:phasediagrams}}
-\end{figure}
-
-\comment{We calculate the topological phase diagram.}
-In Fig.~\ref{fig:phasediagrams} we compare the phase diagrams of the straight and the zigzag junction.
-We plot $E_\textrm{gap}$ as a function of magnetic field and chemical potential ($E_\textrm{gap}(B_x, \mu)$), and of magnetic field and superconducting phase difference ($E_\textrm{gap}(B_x, \phi)$) for both a straight system [(c) and (e)] and a zigzag system [(d) and (f)].
-Additionally, we plot the first $\SI{1300}{\nm}$ (one zigzag period) of the wave functions [(a) and (b)] at the optimal point in parameter space for the straight system.
-For the straight system, we calculate $E_\textrm{gap}$ by performing a binary search in $E$ for the energy at which the propagating modes start to appear~\cite{Nijholt2016}.
-Additionally, in Fig.~\ref{fig:phasediagrams}(c) we plot the phase boundaries obtained by solving a generalized eigenvalue problem~\cite{Nijholt2016}.
-Due to the large size of the zigzag supercell, we are unable to apply these methods to zigzag geometries.
-Instead, we calculate $E_\textrm{gap}$ by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{\left|E(k)\right|}$.
-By both observing the gap closings and comparing to the topological phase diagram of the straight system, we then infer the topology of the zigzag system and verify this by calculating the Majorana wave function of a finite length zigzag.
-As a further check, in App.~\ref{appendix:direction_B} we also compute $E_\textrm{gap}$ as function of the angle of magnetic field and observe that the zigzag device protects Majoranas from magnetic field misalignments.
-
-\comment{The introduction of a the zigzag breaks a chiral symmetry, bringing the system from the BDI to the D symmetry class}
-The straight system is in the symmetry class BDI \cite{Pientka2017}.
-Using the software package Qsymm~\cite{Varjas2018}, we find that the zigzag shape modulation violates the chiral symmetry~\cite{Setiawan2019}, leaving only the particle-hole symmetry and the reflection symmetry with respect to the $x$-axis.
-
-\comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry.}
-Similar to the findings of Pientka \textit{et al.}~\cite{Pientka2017}, we see that the straight geometry has a diamond-shaped topological region.
-We also observe additional gap closings due to the BDI symmetry.
-The topological phase diagram of the zigzag system has a qualitatively similar shape but a significantly increased topological gap.
-The asymmetry of the phase diagram upon replacing $\phi \rightarrow -\phi$ is consistent with the symmetry of the Hamiltonian, because both inversion and time-reversal change both $\phi \rightarrow -\phi$ and $B_x \rightarrow -B_x$.
-
-%%██████████████████████████████████████████████████████████████████████████
-%%██ Discussion and Conclusions
-%%██████████████████████████████████████████████████████████████████████████
-\section{Discussion and Conclusions}
-
-\comment{The zigzag geometry is a controllable tool in hardening the gap and decreasing Majorana size.}
-The zigzag geometry increases the topological gap in the high density regime by more than an order of magnitude, as well as substantially reduces Majorana size.
-The improvements occur in a broad range of parameter values, moreover, even using $B_x$ optimal for the straight system in the high density regime (Fig.~\ref{fig:phasediagrams}), the Majorana size $\xi_\textrm{M}$ and $E_\textrm{gap}$ are still more than an order of magnitude better for the zigzag system.
-We expect that the improvement of the device performance will significantly simplify the creation of Majorana devices and the detection of Majorana states.
-The zigzag geometry offers a controllable way to remove long trajectories, making it easier to rely on than disorder~\cite{Haim2019}, that otherwise has a similar effect.
-
-\comment{Zigzag doesn't do anything against other mechanisms, and therefore it doesn't help to use it ignorantly}
-A soft gap may arise due to other mechanisms that do not involve ballistic trajectories: both interface disorder and pair breaking~\cite{Takei2013} or temperature and dissipation~\cite{Liu2017} may create a soft gap.
-Further in a multimode junction the mode dependence of transmission~\cite{Stanescu2014} may produce subgap conductance similar to that in a device with a soft gap.
-The zigzag geometry has no impact on these alternative phenomena, and it may therefore serve as a tool in distinguishing different mechanisms.
-
-\comment{Current fabrication techniques are compatible with the proposed geometry, and experimental verification can be near.}
-Current fabrication techniques are compatible with the proposed geometry; zigzag devices have already been fabricated~\cite{Vries}.
-We have demonstrated that the unavoidable variation in the experimental device geometry should not have a detrimental impact on the zigzag devices.
-
-\comment{Optimizing the geometry, more detailed modeling, and a simple analytical estimation are open questions for further research}
-Our work is the first demonstration of the impact of the Majorana device geometry on its performance, and it opens a much harder question of finding the optimal geometry.
-A promising approach to tackle this question would rely on constructing a quasiclassical model of the zigzag devices.
-Finally, we have neglected several important physical effects, such as: disorder, electrostatics, the orbital effect of magnetic field, and the finite thickness of the sample.
-While we expect these phenomena not to influence our qualitative findings, a more detailed simulation should provide better guidance to future experiments.
-
-%%██████████████████████████████████████████████████████████████████████████
-%%██ Acknowledgments
-%%██████████████████████████████████████████████████████████████████████████
-\section{Acknowledgments}
-We are grateful to  S. Goswami, A. Keselman, P. P. Piskunow, T. Ö. Rosdahl, D. Varjas, F. K. de Vries, Q. Wang, and J. B. Weston for useful discussions.
-This work was supported by the Netherlands Organization for Scientific Research (NWO/OCW), as part of the Frontiers of Nanoscience program, two NWO VIDI grants (016.Vidi.189.180 and 680-47-537), an ERC Starting Grant STATOPINS 638760, and the project Quantox of QuantERA ERA-NET Cofund in Quantum Technologies (Grant Agreement N.
-731473) implemented within the European Union's Horizon 2020 Program.
-
-\section{Author contributions}
-T.L authored the idea of the zigzag geometry.
-B.N. wrote the code and it was extended by T.L.
-B.N. performed the writing of the manuscript with input of the other authors.
-All authors performed the analysis of the results and planning of the project.
-
-\bibliographystyle{apsrev4-1}
-\bibliography{zigzag}
 

### 2020-03-10 paper/zigzag.tex
Move appendix to separate file

--- 2020-01-06 paper/zigzag.tex
@@
 (In the App.~\ref{appendix:NS_junction} we demonstrate that similar physics also occurs in devices with a single superconductor.)
-We modulate the shape of the normal region, which can be either zigzag as depicted [Fig.~\ref{fig:setup}(b)], or a more smooth sinusoidal-like shape.
-Similar to the conventional straight system \cite{Pientka2017}, a magnetic field $B_x$ perpendicular to the junction is applied.
-We model the system with a Bogoliubov-de Gennes Hamiltonian (BdG):
+We modulate the shape of the normal region to be either zigzag as depicted [Fig.~\ref{fig:setup}(b)] or a more smooth sinusoidal-like shape.
+Similar to the straight system \cite{Pientka2017}, we apply a magnetic field $B_x$ along the $x$-axis.
+The Bogoliubov-de Gennes Hamiltonians $H_\textrm{N}$ and $H_\textrm{SC}$ of the normal region and the superconducting region are
 \begin{subequations}
@@
 \end{subequations}
-Here $H_\textrm{N}$ and $H_\textrm{SC}$ are the Hamiltonians of the semiconductor and superconductors, respectively.
-The normal part has a linear Rashba spin-orbit coupling term with strength $\alpha$ and a Zeeman field with $E_\text{Z}=\frac{1}{2} \mu_B g B_x$.
-The superconductor has a coupling term $\Delta$, and the phases of the superconductors equal to $\pm\phi/2$.
-Both the normal part and the superconductors have a kinetic term and chemical potential $\mu$.
-The BdG Hamiltonian acts on the spinor wave function $\Psi={\left(\psi_{e\uparrow},\psi_{e\downarrow},\psi_{\textrm{h}\downarrow},-\psi_{\textrm{h}\uparrow}\right)}^{T}$, where $\psi_e$, $\psi_\textrm{h}$ are its electron and hole components, and $\psi_\uparrow$, $\psi_\downarrow$ are the spin-up and spin-down components.
+Here, $k_x$ and $k_y$ are the momentum components of the wavevector, $\mu$ is the chemical potential, and $m_\textrm{eff}$ is the effective electron mass.
+The strength of the Rashba spin-orbit coupling is $\alpha$ and a Zeeman splitting $E_\text{Z}=\frac{1}{2} \mu_B g B_x$.
+The superconductor has a coupling strength $\Delta$, and the phases of the superconductors are $\pm\phi/2$.
+The Hamiltonian acts on the spinor wave function $\Psi={\left(\psi_{e\uparrow},\psi_{e\downarrow},\psi_{\textrm{h}\downarrow},-\psi_{\textrm{h}\uparrow}\right)}^{T}$, where $\psi_e$, $\psi_\textrm{h}$ are its electron and hole components, and $\psi_\uparrow$, $\psi_\downarrow$ are the spin-up and spin-down components.
 The Pauli matrices $\sigma_{i}$ act on the spin degree of freedom and $\tau_{i}$ act on the electron-hole degree of freedom.
@@
 Unless noted differently, the Hamiltonian parameters are $\alpha=\SI{20}{\meV \nm}$, $g=26$, $m_\text{eff}=\SI{0.02}{\electronmass}$, $\mu=\SI{10}{\meV}$, $B_x=\SI{1}{T}$, $\phi=\pi$, and $\Delta=\SI{1}{\meV}$; and the geometry parameters are $W=\SI{200}{\nm}$, the period of the zigzag $z_x=\SI{1300}{\nm}$, the discretization contant $a=\SI{10}{\nm}$, and the lengths of the superconductors $L_\textrm{SC}=\SI{300}{\nm}$.
+Our results only weakly depend on the material parameters.
 
@@
 By diagonalizing the Hamiltonian, we find the Majorana energy $E_\textrm{M}$, and by using the corresponding eigenstate of that lowest energy, we get the wave function.
-To reduce the finite size effects in determining the Majorana size $\xi_\textrm{M}$ in a zigzag system, we introduce a particle-hole symmetry breaking potential $V \sigma_0 \tau_0$ on one edge, such that one of the Majorana states is pushed away from zero energy.
+When determining the Majorana size $\xi_\textrm{M}$ in a zigzag system, we reduce the finite size effects by introducing a particle-hole symmetry breaking potential $V \sigma_0 \tau_0$ on one edge, such that one of the Majorana states is pushed away from zero energy.
 We then find $\xi_\textrm{M}$ by fitting an exponential to the density of the single Majorana wave function projected on the $x$-axis.
@@
 
-\comment{The introduction of a the zigzag breaks a chiral symmetry, bringing the system from the BDI to the D symmetry class}
-The straight system is in the symmetry class BDI \cite{Pientka2017}.
-Using the software package Qsymm~\cite{Varjas2018}, we find that the zigzag shape modulation violates the chiral symmetry~\cite{Setiawan2019}, leaving only the particle-hole symmetry and the reflection symmetry with respect to the $x$-axis.
-
 \comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry.}
-Similar to the findings of Pientka \textit{et al.}~\cite{Pientka2017}, we see that the straight geometry has a diamond-shaped topological region.
-We also observe additional gap closings due to the BDI symmetry.
+Similar to the findings of Pientka \textit{et al.}~\cite{Pientka2017}, we see that the straight geometry has a diamond-shaped topological region in $(\phi, B_x)$ space.
 The topological phase diagram of the zigzag system has a qualitatively similar shape but a significantly increased topological gap.
@@
 
-\appendix
-
-\section{Zigzag device with a single superconductor}\label{appendix:NS_junction}
-
-\comment{We run the simulation and observe that the phase diagrams are the same but the zigzag device is still better.}
-A zigzag-shaped device with a single superconductor shows a similar enhancement of the superconducting gap as the Josephson junction devices.
-We demonstrate this by simulating a straight and a zigzag device and computing $E_\textrm{gap}(B_x, \; \mu)$ in Fig.~\ref{fig:ns_junction}.
-We observe that the order of magnitude increase of $E_\textrm{gap}$ also occurs upon the introduction of a zigzag geometry.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[width=0.9\columnwidth]{figures/phasediagrams_NS.pdf}
-\caption{Same as Fig.~\ref{fig:phasediagrams} (c) and (d) but with one superconductor instead of two.
-We observe that the zigzag geometry also increases the gap in this case.
-\label{fig:ns_junction}}
-\end{figure}
-
-\section{Direction of the magnetic field}\label{appendix:direction_B}
-
-\comment{Zigzag geometry removes the need for precise field alignment.}
-Because the zigzag geometry cuts off long trajectories---leaving only short trajectories---this device requires a less precise alignment of the magnetic field.
-To show this, we perform a simulation of a straight and zigzag device with a rotated field (see Fig.~\ref{fig:tilted_angle_phase_diagram}).
-We observe that the zigzag device still has a sizeable gap with a $10^\circ$ misaligned magnetic field, wherea a $1^\circ$ misalignment makes a straight device gapless.
-
-\comment{Likewise a inhomogeneous magnetic field does not matter.}
-Strong screening of the magnetic field by the superconductors may distort the magnetic field pattern.
-To determine whether this effect degrades the device quality, we simulate a device with the magnetic field parallel to the NS interface, shown in Fig.~\ref{fig:syst_snaking_magnetic_field}.
-We find that the resulting gap is comparable to that of a device with the magnetic field purely in the $x$-direction, as shown in Fig.~\ref{fig:snaking_magnetic_field}.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[width=0.9\columnwidth]{figures/tilted_angle_phase_diagram.pdf}
-\caption{The topological gap as a function of the magnetic field magnitude $B$ and its angle $\theta=\arctan{B_y/B_x}$ for a straight device (a) and a zigzag device (b).
-Note that the colormaps and the $\theta$-axes differ between panels: the zigzag-shaped device becomes gapless at $\theta$ an order of magnitude larger compared to the straight device.
-\label{fig:tilted_angle_phase_diagram}}
-\end{figure}
-
-\begin{figure}[!htb]
-\centering
-\includegraphics{figures/syst_snaking_magnetic_field.pdf}
-\caption{
-The magnetic field pattern emulating strong screening by the superconductors.
-\label{fig:syst_snaking_magnetic_field}}
-\end{figure}
-
-\begin{figure}[!htb]
-\centering
-\includegraphics{figures/snaking_magnetic_field.pdf}
-\caption{
-Comparison of the zigzag device's band structures with the magnetic field following the shape of the junction (orange) (see Fig.~\ref{fig:syst_snaking_magnetic_field}) and a magnetic field in the $x$-direction (blue) for different values of $z_y$.
-\label{fig:snaking_magnetic_field}}
-\end{figure}
-
-\section{Interface transparency vs.~path length cut-off}
-
-The zigzag geometry both increases the interface transparency (because particles typically hit the superconductor
-closer to normal incidence) as well as sets an upper limit to the trajectory length.
-The change in the interface transparency alone is not sufficient to explain the increase of the topological gap.
-To verify this, we compute the dispersion of a system with $z_x = z_y = \SI{80}{\nm}$ comparable to the Fermi wavelength $\lambda_\textrm{F}$ and $W=\SI{400}{\nm}$, so that the angle of the boundaries is sufficiently large, but the boundary modulation is much smaller than the width.
-We observe that $E_\textrm{gap}$ becomes $\SI{6.1}{\mu \eV}$, a two-fold increase compared to the straight system, not the order of magnitude increase resulting from the cutting off of long trajectories.
-
 \end{document}

### 2020-05-19 zigzag.py
remove markers added by Jupyter notebook

@@ -21,7 +21,6 @@ import scipy.sparse as sp
 import scipy.sparse.linalg as sla
 
 
-# +
 constants = dict(
     # effective mass in kg,
     m_eff=0.023 * scipy.constants.m_e / (scipy.constants.eV * 1e-3) / 1e18,
@@ -39,9 +38,6 @@ SI_constants = dict(
     meV=scipy.constants.eV * 1e-3,
     m_eff=0.023 * scipy.constants.m_e,
 )
-
-
-# -
 
 
 def remove_phs(H):
@@ -791,7 +787,6 @@ def quiver_plot_B(syst, params, step=1):
     return plt.quiver(xs[::step], ys[::step], np.real(bs)[::step], -np.imag(bs)[::step])
 
 
-# +
 def calc_k_F(mu, SI_constants=SI_constants):
     """Argument in SI units"""
     c = SI_constants

### 2020-05-20 paper/zigzag.tex
Also add externaldocument (appendix) to zigzag.tex
add disorder paragraph

@@
 On the other hand, disorder scatters these long trajectories and introduces a cutoff on the scale of the mean free path~\cite{Golubov1988,Belzig1996,Pilgram2000} which Ref.~\onlinecite{Haim2019} proposes to use to improve Majorana properties; however, disorder is impossible to control to a required precision experimentally.
+In App.~\ref{appendix:mfp_vs_gap} we compare the size of $E_\textrm{gap}$ as a function of the mean free path $l_e$ for zigzag and straight systems at $\phi=0$ and $\phi=\pi$; and confirm that the zigzag geometry and disorder both increase $E_\textrm{gap}$ through a similar mechanism.
 
@@
 
+\appendix
+
+\section{Zigzag devices and disorder}\label{appendix:mfp_vs_gap}
+
+\comment{We compare $E_\textrm{gap}(l_e)$ for zigzag and straight systems at $\phi=0$ and $\phi=\pi$; and confirm that the zigzag and disorder both increase $E_\textrm{gap}$ through a similar mechanism.}
+The right amount of disorder scatters long trajectories improves the Majorana properties~\onlinecite{Haim2019}, similar to the zigzag geometry cutting off these long trajectories.
+We simulate devices with disorder---parameterized by its mean free path $l_e$---and calculate $E_\textrm{gap}(l_e)$ for straight and zigzag devices at different phases and magnetic fields, see Fig.~\ref{fig:mfp_vs_gap}.
+For the parameters we chose, at $\phi=0$ we observe that an optimal value of $l_e$ results in an enhancement that is at best equal to that of the zigzag device.
+At $\phi=\pi$ we observe that zigzag outperforms disorder.
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=0.9\columnwidth]{figures/mfp_vs_gap.pdf}
+\caption{Comparison of the gap of zigzag devices (dashed lines) and straight devices (solid lines) as function of mean free path $l_e$.
+\label{fig:mfp_vs_gap}}
+\end{figure}
+
+\section{Zigzag device with a single superconductor}\label{appendix:NS_junction}
+
+\comment{We run the simulation and observe that the phase diagrams are the same but the zigzag device is still better.}
+A zigzag-shaped device with a single superconductor shows a similar enhancement of the superconducting gap as the Josephson junction devices.
+We demonstrate this by simulating a straight and a zigzag device and computing $E_\textrm{gap}(B_x, \; \mu)$ in Fig.~\ref{fig:ns_junction}.
+We observe that the order of magnitude increase of $E_\textrm{gap}$ also occurs upon the introduction of a zigzag geometry.
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=0.9\columnwidth]{figures/phasediagrams_NS.pdf}
+\caption{Same as Fig.~\ref{fig:phasediagrams} (c) and (d) but with one superconductor instead of two.
+We observe that the zigzag geometry also increases the gap in this case.
+\label{fig:ns_junction}}
+\end{figure}
+
+\section{Direction of the magnetic field}\label{appendix:direction_B}
+
+\comment{Zigzag geometry removes the need for precise field alignment.}
+Because the zigzag geometry cuts off long trajectories---leaving only short trajectories---this device requires a less precise alignment of the magnetic field.
+To show this, we perform a simulation of a straight and zigzag device with a rotated field (see Fig.~\ref{fig:tilted_angle_phase_diagram}).
+We observe that the zigzag device still has a sizeable gap with a $10^\circ$ misaligned magnetic field, wherea a $1^\circ$ misalignment makes a straight device gapless.
+
+\comment{Likewise a inhomogeneous magnetic field does not matter.}
+Strong screening of the magnetic field by the superconductors may distort the magnetic field pattern.
+To determine whether this effect degrades the device quality, we simulate a device with the magnetic field parallel to the NS interface, shown in Fig.~\ref{fig:syst_snaking_magnetic_field}.
+We find that the resulting gap is comparable to that of a device with the magnetic field purely in the $x$-direction, as shown in Fig.~\ref{fig:snaking_magnetic_field}.
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=0.9\columnwidth]{figures/tilted_angle_phase_diagram.pdf}
+\caption{The topological gap as a function of the magnetic field magnitude $B$ and its angle $\theta=\arctan{B_y/B_x}$ for a straight device (a) and a zigzag device (b).
+Note that the colormaps and the $\theta$-axes differ between panels: the zigzag-shaped device becomes gapless at $\theta$ an order of magnitude larger compared to the straight device.
+\label{fig:tilted_angle_phase_diagram}}
+\end{figure}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics{figures/syst_snaking_magnetic_field.pdf}
+\caption{
+The magnetic field pattern emulating strong screening by the superconductors.
+\label{fig:syst_snaking_magnetic_field}}
+\end{figure}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics{figures/snaking_magnetic_field.pdf}
+\caption{
+Comparison of the zigzag device's band structures with the magnetic field following the shape of the junction (orange) (see Fig.~\ref{fig:syst_snaking_magnetic_field}) and a magnetic field in the $x$-direction (blue) for different values of $z_y$.
+\label{fig:snaking_magnetic_field}}
+\end{figure}
+
+\section{Interface transparency vs.~path length cut-off}
+
+The zigzag geometry both increases the interface transparency (because particles typically hit the superconductor
+closer to normal incidence) as well as sets an upper limit to the trajectory length.
+The change in the interface transparency alone is not sufficient to explain the increase of the topological gap.
+To verify this, we compute the dispersion of a system with $z_x = z_y = \SI{80}{\nm}$ comparable to the Fermi wavelength $\lambda_\textrm{F}$ and $W=\SI{400}{\nm}$, so that the angle of the boundaries is sufficiently large, but the boundary modulation is much smaller than the width.
+We observe that $E_\textrm{gap}$ becomes $\SI{6.1}{\mu \eV}$, a two-fold increase compared to the straight system, not the order of magnitude increase resulting from the cutting off of long trajectories.
+
 \end{document}

### 2020-05-20 paper/zigzag.tex
rephrase

@@
 \comment{We compare $E_\textrm{gap}(l_e)$ for zigzag and straight systems at $\phi=0$ and $\phi=\pi$; and confirm that the zigzag and disorder both increase $E_\textrm{gap}$ through a similar mechanism.}
-The right amount of disorder scatters long trajectories improves the Majorana properties~\onlinecite{Haim2019}, similar to the zigzag geometry cutting off these long trajectories.
+The right amount of disorder improves the Majorana properties~\onlinecite{Haim2019} and scatters long trajectories in a similar fashion to the zigzag geometry cutting off long trajectories.
 We simulate devices with disorder---parameterized by its mean free path $l_e$---and calculate $E_\textrm{gap}(l_e)$ for straight and zigzag devices at different phases and magnetic fields, see Fig.~\ref{fig:mfp_vs_gap}.

### 2020-05-20 paper/zigzag.tex
use cite

--- 2020-05-20 paper/zigzag.tex
@@
 \comment{We compare $E_\textrm{gap}(l_e)$ for zigzag and straight systems at $\phi=0$ and $\phi=\pi$; and confirm that the zigzag and disorder both increase $E_\textrm{gap}$ through a similar mechanism.}
-The right amount of disorder scatters long trajectories improves the Majorana properties~\onlinecite{Haim2019}, similar to the zigzag geometry cutting off these long trajectories.
+The right amount of disorder improves the Majorana properties~\cite{Haim2019} and scatters long trajectories in a similar fashion to the zigzag geometry cutting off long trajectories.
 We simulate devices with disorder---parameterized by its mean free path $l_e$---and calculate $E_\textrm{gap}(l_e)$ for straight and zigzag devices at different phases and magnetic fields, see Fig.~\ref{fig:mfp_vs_gap}.

### 2020-06-05 paper/zigzag.tex
add zigzag -> zigzag geometry

@@
 For the parameters we chose, at $\phi=0$ we observe that an optimal value of $l_e$ results in an enhancement that is at best equal to that of the zigzag device.
-At $\phi=\pi$ we observe that zigzag outperforms disorder.
+At $\phi=\pi$ we observe that zigzag geometry outperforms disorder.
 
@@
 \caption{Comparison of the gap of zigzag devices (dashed lines) and straight devices (solid lines) as function of mean free path $l_e$.
+Each $E_\textrm{gap}$ value is averaged over 40 disorder realizations and is calculated using a translationally invariant system where the unit-cell is $L_x=3z_x$, with $z_x=\SI{1300}{\nm}$.
 \label{fig:mfp_vs_gap}}

### 2020-06-16 paper/appendix.tex

@@
 
+\section{Zigzag devices and disorder}\label{appendix:mfp_vs_gap}
+
+\comment{We compare $E_\textrm{gap}(l_e)$ for zigzag and straight systems at $\phi=0$ and $\phi=\pi$; and confirm that the zigzag and disorder both increase $E_\textrm{gap}$ through a similar mechanism.}
+The right amount of disorder improves the Majorana properties~\cite{Haim2019} and scatters long trajectories in a similar fashion to the zigzag geometry cutting off long trajectories.
+We simulate devices with disorder---parameterized by its mean free path $l_e$---and calculate $E_\textrm{gap}(l_e)$ for straight and zigzag devices at different phases and magnetic fields, see Fig.~\ref{fig:mfp_vs_gap}.
+For the parameters we chose, at $\phi=0$ we observe that an optimal value of $l_e$ results in an enhancement that is at best equal to that of the zigzag device.
+At $\phi=\pi$ we observe that zigzag geometry outperforms disorder.
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=0.9\columnwidth]{figures/mfp_vs_gap.pdf}
+\caption{Comparison of the gap of zigzag devices (dashed lines) and straight devices (solid lines) as function of mean free path $l_e$.
+Each $E_\textrm{gap}$ value is averaged over 40 disorder realizations and is calculated using a translationally invariant system where the unit-cell is $L_x=3z_x$, with $z_x=\SI{1300}{\nm}$.
+\label{fig:mfp_vs_gap}}
+\end{figure}
+
 \section{Zigzag device with a single superconductor}\label{appendix:NS_junction}

### 2020-06-16 paper/zigzag.tex

--- 2020-05-20 paper/zigzag.tex
@@
 \usepackage{babel}
+\usepackage{xr}
+\externaldocument{appendix}
+
 \hypersetup{pdfauthor={Quantum Tinkerer},pdftitle={Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.}}
@@
 
-\appendix
-
-\section{Zigzag devices and disorder}\label{appendix:mfp_vs_gap}
-
-\comment{We compare $E_\textrm{gap}(l_e)$ for zigzag and straight systems at $\phi=0$ and $\phi=\pi$; and confirm that the zigzag and disorder both increase $E_\textrm{gap}$ through a similar mechanism.}
-The right amount of disorder improves the Majorana properties~\cite{Haim2019} and scatters long trajectories in a similar fashion to the zigzag geometry cutting off long trajectories.
-We simulate devices with disorder---parameterized by its mean free path $l_e$---and calculate $E_\textrm{gap}(l_e)$ for straight and zigzag devices at different phases and magnetic fields, see Fig.~\ref{fig:mfp_vs_gap}.
-For the parameters we chose, at $\phi=0$ we observe that an optimal value of $l_e$ results in an enhancement that is at best equal to that of the zigzag device.
-At $\phi=\pi$ we observe that zigzag outperforms disorder.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[width=0.9\columnwidth]{figures/mfp_vs_gap.pdf}
-\caption{Comparison of the gap of zigzag devices (dashed lines) and straight devices (solid lines) as function of mean free path $l_e$.
-\label{fig:mfp_vs_gap}}
-\end{figure}
-
-\section{Zigzag device with a single superconductor}\label{appendix:NS_junction}
-
-\comment{We run the simulation and observe that the phase diagrams are the same but the zigzag device is still better.}
-A zigzag-shaped device with a single superconductor shows a similar enhancement of the superconducting gap as the Josephson junction devices.
-We demonstrate this by simulating a straight and a zigzag device and computing $E_\textrm{gap}(B_x, \; \mu)$ in Fig.~\ref{fig:ns_junction}.
-We observe that the order of magnitude increase of $E_\textrm{gap}$ also occurs upon the introduction of a zigzag geometry.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[width=0.9\columnwidth]{figures/phasediagrams_NS.pdf}
-\caption{Same as Fig.~\ref{fig:phasediagrams} (c) and (d) but with one superconductor instead of two.
-We observe that the zigzag geometry also increases the gap in this case.
-\label{fig:ns_junction}}
-\end{figure}
-
-\section{Direction of the magnetic field}\label{appendix:direction_B}
-
-\comment{Zigzag geometry removes the need for precise field alignment.}
-Because the zigzag geometry cuts off long trajectories---leaving only short trajectories---this device requires a less precise alignment of the magnetic field.
-To show this, we perform a simulation of a straight and zigzag device with a rotated field (see Fig.~\ref{fig:tilted_angle_phase_diagram}).
-We observe that the zigzag device still has a sizeable gap with a $10^\circ$ misaligned magnetic field, wherea a $1^\circ$ misalignment makes a straight device gapless.
-
-\comment{Likewise a inhomogeneous magnetic field does not matter.}
-Strong screening of the magnetic field by the superconductors may distort the magnetic field pattern.
-To determine whether this effect degrades the device quality, we simulate a device with the magnetic field parallel to the NS interface, shown in Fig.~\ref{fig:syst_snaking_magnetic_field}.
-We find that the resulting gap is comparable to that of a device with the magnetic field purely in the $x$-direction, as shown in Fig.~\ref{fig:snaking_magnetic_field}.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[width=0.9\columnwidth]{figures/tilted_angle_phase_diagram.pdf}
-\caption{The topological gap as a function of the magnetic field magnitude $B$ and its angle $\theta=\arctan{B_y/B_x}$ for a straight device (a) and a zigzag device (b).
-Note that the colormaps and the $\theta$-axes differ between panels: the zigzag-shaped device becomes gapless at $\theta$ an order of magnitude larger compared to the straight device.
-\label{fig:tilted_angle_phase_diagram}}
-\end{figure}
-
-\begin{figure}[!htb]
-\centering
-\includegraphics{figures/syst_snaking_magnetic_field.pdf}
-\caption{
-The magnetic field pattern emulating strong screening by the superconductors.
-\label{fig:syst_snaking_magnetic_field}}
-\end{figure}
-
-\begin{figure}[!htb]
-\centering
-\includegraphics{figures/snaking_magnetic_field.pdf}
-\caption{
-Comparison of the zigzag device's band structures with the magnetic field following the shape of the junction (orange) (see Fig.~\ref{fig:syst_snaking_magnetic_field}) and a magnetic field in the $x$-direction (blue) for different values of $z_y$.
-\label{fig:snaking_magnetic_field}}
-\end{figure}
-
-\section{Interface transparency vs.~path length cut-off}
-
-The zigzag geometry both increases the interface transparency (because particles typically hit the superconductor
-closer to normal incidence) as well as sets an upper limit to the trajectory length.
-The change in the interface transparency alone is not sufficient to explain the increase of the topological gap.
-To verify this, we compute the dispersion of a system with $z_x = z_y = \SI{80}{\nm}$ comparable to the Fermi wavelength $\lambda_\textrm{F}$ and $W=\SI{400}{\nm}$, so that the angle of the boundaries is sufficiently large, but the boundary modulation is much smaller than the width.
-We observe that $E_\textrm{gap}$ becomes $\SI{6.1}{\mu \eV}$, a two-fold increase compared to the straight system, not the order of magnitude increase resulting from the cutting off of long trajectories.
-
 \end{document}

### 2020-06-19 paper/referee_responses_round_2.md
add referee_responses_round_2.md

---
urlcolor: blue
geometry:
  margin=1in
---

Dear Dr. Samindranath Mitra,

We would like to resubmit our minimally revised manuscript where we address the referee B's remarks.
We also address the two questions below.
The only change we have made to the manuscript is the addition of a paragraph to the Supplemental Material: "Zigzag devices and disorder".

Sincerely,  
The authors

## Second Report of Referee B -- LD17005/Laeven

> I have read the report of Referee A and the reply to both reports by the authors. I'm satisfied with the authors' reply to my comments and with the changes made. I believe this work will have an impact on upcoming experiments in topological superconductivity in the near future. I therefore recommend the publication of the paper in PRL.

We thank the referee for the recommendation.

## Report of Referee C -- LD17005/Laeven

> I read with interest the manuscript entitled “Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions” by Tom Laeven et al. together with the others referees reports. The Authors propose new geometry of Josephson – zigzag or sine-like shaped - which enhances size of induced topological gap by more than order of magnitude comparing to the standard straight geometry. This results in shorter coherence length of the “Majoranas” and in turns leads to increase of robustness against disorder which is of great interest for physical implementation. In my opinion Authors managed to fully answer the other referees questions.
> In order to judge if paper is appropriate for PRL let’s analyze the results in the light of PRL's acceptance criteria. The work should:
> 1) Open a new research area, or a new avenue within an established area.
> The work does not open new research area
> 2) Solve, or make essential steps towards solving, a critical problem.
> I think that proposing a new geometry (zigzag, sine type) of Josephson junction which enhances the induced topological gap of the system by more than order of magnitude can be considered as “making essential steps towards solving, a critical problem.” It is worth to mention that proposed setup has been already realized experimentally http://meetings.aps.org/Meeting/MAR20/Session/L60.6.
> 3) Introduce new techniques or methodologies with significant impact.
> The work does not really present new techniques or methodologies...
> 4) Be of unusual intrinsic interest to PRL's broad audience.
> The work touches rather specific and greatly explored field of Majorana based systems.
> Overall I think the manuscript matches criteria 2) and this should be sufficient for publication in PRL, thus I can recommend the paper for publication if the Authors could answer and clarify the following matter:
> i) Is it important that in proposed setup (Figure 3) the zigzag/sine-like geometry pattern of normal region has a reflection symmetry with respect to x=x_M axis, where x_M denotes middle of the system in the x direction? I wonder if taking zigzag pattern, for which middle of the junction in y direction is different at two ends of the system (e.g. by taking scenario with zigzag endings like on Fig. 1), would affect the size of induced gap and presence of Majoranas significantly?
> ii) I wonder if combing the effects of zigzag geometry and weak disorder presented in ref [22] (Arbel Haim and Ady Stern Phys. Rev. Lett. 122, (2019)) could further increase the size of induced gap?

We would like to thank referee C for his/her evaluation. To answer the questions, we have performed two numerical simulations.

Specifically, to determine whether the ends of the zigzag region matter we have created systems that end before a full zigzag period (see the attached figure). We observe that this does not influence any of our conclusions. We believe this was expected as we make the argument that the proposed mechanism for the gap increase (cutting off of long trajectories) is not influenced by its endings.

To answer the question regarding the combination of disorder and zigzag, we have simulated a straight and zigzag system for an increasing mean free path and calculated the average energy gap (averaged over disorder realizations). For the parameters we chose, at ϕ=0 we observe that an optimal value of the mean free path results in an enhancement that is at best equal to that of the zigzag device. At ϕ=π, we observe that zigzag geometry outperforms disorder. We have added a paragraph to the appendix of the manuscript that describes our findings.

## List of changes

The following changes were made:

* Added a paragraph to the Supplemental Material: "Zigzag devices and disorder".
* Refer to this paragraph in the main text.

### 2020-06-19 paper/referee_responses_round_2.md
fix formatting

@@
 In my opinion Authors managed to fully answer the other referees questions.
+
 > In order to judge if paper is appropriate for PRL let’s analyze the results in the light of PRL's acceptance criteria. The work should:
+
 > 1) Open a new research area, or a new avenue within an established area.
+
 > The work does not open new research area
+
 > 2) Solve, or make essential steps towards solving, a critical problem.
+
 > I think that proposing a new geometry (zigzag, sine type) of Josephson junction which enhances the induced topological gap of the system by more than order of magnitude can be considered as “making essential steps towards solving, a critical problem.” It is worth to mention that proposed setup has been already realized experimentally http://meetings.aps.org/Meeting/MAR20/Session/L60.6.
+
 > 3) Introduce new techniques or methodologies with significant impact.
+
 > The work does not really present new techniques or methodologies...
+
 > 4) Be of unusual intrinsic interest to PRL's broad audience.
+
 > The work touches rather specific and greatly explored field of Majorana based systems.
 > Overall I think the manuscript matches criteria 2) and this should be sufficient for publication in PRL, thus I can recommend the paper for publication if the Authors could answer and clarify the following matter:
-> i) Is it important that in proposed setup (Figure 3) the zigzag/sine-like geometry pattern of normal region has a reflection symmetry with respect to x=x_M axis, where x_M denotes middle of the system in the x direction?
-I wonder if taking zigzag pattern, for which middle of the junction in y direction is different at two ends of the system (e.g.
+
+> i) Is it important that in proposed setup (Figure 3) the zigzag/sine-like geometry pattern of normal region has a reflection symmetry with respect to $x=x_M$ axis, where $x_M$ denotes middle of the system in the $x$ direction?
+I wonder if taking zigzag pattern, for which middle of the junction in $y$ direction is different at two ends of the system (e.g.
 by taking scenario with zigzag endings like on Fig.
 1), would affect the size of induced gap and presence of Majoranas significantly?
+
 > ii) I wonder if combing the effects of zigzag geometry and weak disorder presented in ref [22] (Arbel Haim and Ady Stern Phys. Rev. Lett. 122, (2019)) could further increase the size of induced gap?
@@
 To answer the question regarding the combination of disorder and zigzag, we have simulated a straight and zigzag system for an increasing mean free path and calculated the average energy gap (averaged over disorder realizations).
-For the parameters we chose, at ϕ=0 we observe that an optimal value of the mean free path results in an enhancement that is at best equal to that of the zigzag device.
-At ϕ=π, we observe that zigzag geometry outperforms disorder.
+For the parameters we chose, at $\phi=0$ we observe that an optimal value of the mean free path results in an enhancement that is at best equal to that of the zigzag device.
+At $\phi=\pi$, we observe that zigzag geometry outperforms disorder.
 We have added a paragraph to the appendix of the manuscript that describes our findings.

### 2020-06-19 paper/referee_responses_round_2.md
add different quote block style

@@
   margin=1in
+header-includes:
+- \usepackage{tcolorbox}
+- \newtcolorbox{myquote}{colback=gray!5!white, colframe=gray!75!black}
+- \renewenvironment{quote}{\begin{myquote}}{\end{myquote}}
 ---
@@
 In my opinion Authors managed to fully answer the other referees questions.
-
+>
 > In order to judge if paper is appropriate for PRL let’s analyze the results in the light of PRL's acceptance criteria. The work should:
-
+>
 > 1) Open a new research area, or a new avenue within an established area.
-
+>
 > The work does not open new research area
-
+>
 > 2) Solve, or make essential steps towards solving, a critical problem.
-
+>
 > I think that proposing a new geometry (zigzag, sine type) of Josephson junction which enhances the induced topological gap of the system by more than order of magnitude can be considered as “making essential steps towards solving, a critical problem.” It is worth to mention that proposed setup has been already realized experimentally http://meetings.aps.org/Meeting/MAR20/Session/L60.6.
-
+>
 > 3) Introduce new techniques or methodologies with significant impact.
-
+>
 > The work does not really present new techniques or methodologies...
-
+>
 > 4) Be of unusual intrinsic interest to PRL's broad audience.
-
+>
 > The work touches rather specific and greatly explored field of Majorana based systems.
 > Overall I think the manuscript matches criteria 2) and this should be sufficient for publication in PRL, thus I can recommend the paper for publication if the Authors could answer and clarify the following matter:
-
+>
 > i) Is it important that in proposed setup (Figure 3) the zigzag/sine-like geometry pattern of normal region has a reflection symmetry with respect to $x=x_M$ axis, where $x_M$ denotes middle of the system in the $x$ direction?
@@
 1), would affect the size of induced gap and presence of Majoranas significantly?
-
+>
 > ii) I wonder if combing the effects of zigzag geometry and weak disorder presented in ref [22] (Arbel Haim and Ady Stern Phys. Rev. Lett. 122, (2019)) could further increase the size of induced gap?

### 2020-06-19 paper/referee_responses_round_2.md
reword the editor response

@@
 
-We would like to resubmit our minimally revised manuscript where we address the referee B's remarks.
+We would like to resubmit our revised manuscript where we address the referee C's remarks, for which we have done a whole set of new simulations.
+We have added one of these simulations' result as a paragraph to the Supplemental Material: "Zigzag devices and disorder".
 We also address the two questions below.
-The only change we have made to the manuscript is the addition of a paragraph to the Supplemental Material: "Zigzag devices and disorder".
 
